### 2015-03-12 paper.tex
Added article templates

\documentclass[12pt]{amsart}
\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools}
\usepackage[utf8]{inputenc}
\usepackage[hypertex]{hyperref}
\usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
\usepackage[all]{xy}

\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
\DeclareFieldFormat[article]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\DeclareFieldFormat[inproceedings]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\addbibresource{paper.bib}

\textwidth 16cm 
\textheight 22cm 
\headheight 0.5cm 
\evensidemargin 0.3cm 
\oddsidemargin 0.2cm

\numberwithin{equation}{section}
\newcounter{thmcounter} \newcounter{lemmacounter}
\newtheorem{thm}[thmcounter]{Theorem}
\newtheorem{prop}[thmcounter]{Proposition}
\newtheorem{cor}[thmcounter]{Corollary}
\newtheorem{lemma}[lemmacounter]{Lemma}
\theoremstyle{definition}
\newtheorem{rem}[equation]{Remark}
\newtheorem{example}[equation]{Example}
\newtheorem{dfn}[equation]{Definition}
\newtheorem{notation}[equation]{Notation}

\newcommand{\K}{\operatorname{\mathrm{K}}}
\newcommand{\GG}{\operatorname{\mathrm{G}}}
\newcommand{\St}{\operatorname{\mathrm{St}}}
\newcommand{\G}{\operatorname{\mathrm{G}}}
\newcommand{\E}{\operatorname{\mathrm{E}}}
\newcommand{\M}{\operatorname{\mathrm{M}}}
\newcommand{\sr}{\operatorname{\mathrm{sr}}}
\newcommand{\Um}{\operatorname{\mathrm{Um}}}
\newcommand{\rk}{\operatorname{\mathrm{rk}}}
\newcommand{\rA}{\mathrm{A}}
\newcommand{\rB}{\mathrm{B}}
\newcommand{\rC}{\mathrm{C}} 
\newcommand{\rD}{\mathrm{D}} 
\newcommand{\rE}{\mathrm{E}}

\title{Relative parabolic factorizations of Chevalley groups}
\keywords {Chevalley groups, relative subgroups, stability for $\K_1 $. {\em Mathematical Subject Classification (2010):} 20G35, 19B14}
\author {Sergey Sinchuk, Andrei Smolensky}
\email {sinchukss {\it at} yandex.ru,\ andrei.smolensky {\it at} gmail.com}
\date {\today}

\begin{document}

\begin{abstract} \end{abstract}

\maketitle

\section {Introduction}\label{intro}

\subsection{Acknowledgements}
Authors of the present paper acknowledge financial support from Russian Science Foundation grant 14-11-00297.

\section {Preliminaries}\label{prelim}

\printbibliography

\end{document}

### 2015-03-16 bass-kolster.tex
added draft for Bass-Kolster

\begin{thm}\label{thm:BassKolster}
Let $\Phi$ be a classical ($\rA,\rB,\rC,\rD$) root system of rank $\geqslant2$, $\Delta<\Phi$ its terminal subsystem of the same type, $(R,I)$ a commutative ring and its ideal, satisfying the following assumption:
\begin{itemize}
\item $\Phi=\rA_\ell$: $\operatorname{sr}(R,I)\leqslant\ell+1$,
\item $\Phi=\rB_\ell$: $\operatorname{asr}(R,I)\leqslant\ell$,
\item $\Phi=\rC_\ell$: $\operatorname{sr}(R,I)\leqslant2\ell$,
\item $\Phi=\rD_\ell$: $\operatorname{asr}(R,I)\leqslant\ell$.
\end{itemize}
Then the principal congruence subgroup $G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
\[ G(\Phi,R,I)=U(\Sigma^+,I)\ U(\Sigma^-,I)\cdot Z\cdot U(\Sigma^-,I)\ U(\Sigma^+,I)\cdot G(\Delta,R,I), \]
where $\Sigma^\pm=\Phi^\pm\setminus\Delta$ and $Z=\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \}$.
\end{thm}

$\Phi$ a root system, $\Delta\subset\Phi$ a terminal subsystem, $R$ a ring, $I\lhd R$.

(!) $G(\Phi,R,I)=G(\Delta,R,I)\cdot E(\Phi,R,I)$.

\textbf{TODO:} reformat all of the below into one subsection (math in section titles does not work with hyperref, apparently)

\subsection{$\rA_n$}

Assuming $sr(R,I)\leqslant n$.

Working with the first column, $(1+r_1,r_2,\ldots,r_n,r_{n+1})^t\in Umd(n+1,R,I)$, $r_i\in I$. Find $c_1,\ldots,c_n\in I$ such that $(1+r_1+c_1r_{n+1},r_2+c_2r_{n+1},\ldots,r_n+c_nr_{n+1})\in Umd(n,R,I)$ and apply $n$ corresponding upper transformations.
Now find $c_1,\ldots,c_n\in R$ such that $c_1(1+r_1)+c_2r_2+\ldots+c_nr_n=1$, then for $c_i'=c_i\cdot(r_1-r_{n+1})\in I$ one has $c_1'(1+r_1)+c_2'r_2+\ldots+c_n'r_n=r_1-r_{n+1}$. Apply $n$ lower transformations to add $c_i'r_i$ to $r_{n+1}$, so that $r_{n+1}\mapsto r_1$. Now apply $z_\gamma$, $\gamma=-\alpha_\mathrm{max}$. $z_\gamma(-r_1,1)=x_{-\gamma}(1)\cdot x_\gamma(-r_1)\cdot x_{-\gamma}(-1)$. So
\[
\begin{pmatrix}
1+r_1 \\ \vdots \\ r_1
\end{pmatrix}
\xmapsto{x_{-\gamma}(-1)}
\begin{pmatrix}
1\\ \vdots \\ r_1
\end{pmatrix}
\xmapsto{x_\gamma(-r_1)}
\begin{pmatrix}
1\\ \vdots \\ 0
\end{pmatrix}
\xmapsto{x_{-\gamma}(1)}
\begin{pmatrix}
1\\ \vdots \\ 0
\end{pmatrix}.
\]
Now applying $n-1$ lower transformations at level $I$ make the first column trivial. $n$ more transformation will make first row trivial. Thus $n+n+1+(n-1)+n=4n$ transformations will give a matrix from $G(\Delta,R,I)$.

\subsection{$\rC_n$}

\textbf{TODO:} shorten this twice (at least)

Assuming $sr(R,I)\leqslant 2n$.
First column: $(1+r_1,r_2,\ldots,r_n,r_{-n},\ldots,r_{-1})^t\in Umd(2n,R,I)$. Find $c_1,\ldots,c_{-2}\in I$ such that $(1+r_1+c_1r_{-1},\ldots,r_{-2}+c_{-2}r_{-2})=(1+r_1',\ldots,r_{-1}')\in Umd(2n-1,R,I)$. First add $c_{-i}r_{-1}$ to $r_{-i}$, so that
\[
\begin{pmatrix}
1+r_1 \\ r_i \\ r_{-i} \\ r_{-1}
\end{pmatrix}
\mapsto
\begin{pmatrix}
1+r_1+\sum c_{-i}r_i\\ r_i \\ r_{-i}+c_{-i}r_{-1} \\ r_{-1}
\end{pmatrix}=
\begin{pmatrix}
1+r_{11} \\ r_i \\ r_{-i}' \\ r_{-1}
\end{pmatrix}.
\]
Denote $\mathfrak{a}=\sum r_{-i}'R\unlhd R$. Now add $c_ir_{-1}$ to $r_i$:
\[
\begin{pmatrix}
1+r_{11} \\ r_i' \\ r_{-i}' \\ r_{-1}
\end{pmatrix}
\mapsto
\begin{pmatrix}
1+r_{11}+a \\ r_i+c_ir_{-1} \\ r_{-i}' \\ r_{-1}
\end{pmatrix}=
\begin{pmatrix}
1+r_{12} \\ r_i' \\ r_{-i}' \\ r_{-1}
\end{pmatrix},
\ a\in\mathfrak{a}.
\]
Finally, add $\left(c_1+\sum_{j=2}^n c_jc_{-j}\right)r_{-1}$ to the first row:
\begin{multline*}
\left(1+r_1+\sum c_{-i}r_i+a\right)+\left(c_1r_{-1}+\sum c_jc_{-j}r_{-1}\right)=\\
=(1+r_1+c_1r_{-1})+\sum c_{-i}(r_i+c_ir_{-1})+a=\\
=1+r_1'+\sum c_{-i}r_i'+a=1+r_1''.
\end{multline*}
Note that $\langle 1+r_1'',r_2',\ldots,r_{-2}'\rangle=\langle 1+r_1',r_2',\ldots,r_{-2}'\rangle$, so we made the first $2n-1$ elements to form a unimodular column.

Find $c_1,\ldots,c_{-2}\in I$ such that $c_1(1+r_1)+c_2r_2+\ldots+c_{-2}r_{-2}=r_1-r_{-1}$. Add $c_{-i}r_i$ to $r_{-1}$:
\[
\begin{pmatrix}
1+r_1 \\ r_i \\ r_{-i} \\ r_{-1}
\end{pmatrix}
\mapsto
\begin{pmatrix}
1+r_1 \\ r_i+c_{-i}r_1 \\ r_{-i} \\ r_{-1}+\sum s_{-i}r_{-i}
\end{pmatrix}=
\begin{pmatrix}
1+r_1 \\ r_i' \\ r_{-i} \\ r_{-11}
\end{pmatrix}.
\]
Then add $c_ir_i'=c_i(r_1+c_{-i}r_{-i})$ to $r_{-11}$:
\[
1+r_1\mapsto 1+r_1,\quad r_{-11}\mapsto r_{-1}+\sum c_{-i}r_{-i}+\sum c_i(r_i+c_{-i}r_1)=r_{-12}.
\]
Next add $(c_1-\sum c_ic_{-i})(1+r_1)$ to $r_{-12}$:
\begin{multline*}
r_{-12}\mapsto r_{-1}+\sum c_{-i}r_{-i}+\sum c_i(r_i+c_{-i}(1+r_1))-\sum c_ic_{-i}(1+r_1)=\\=r_{-1}+c_1(1+r_1)+\sum(c_ir_i+c_{-i}r_{-i})=r_{-1}+(r_1-r_{-1})=r_1.
\end{multline*}
Again, as in case of $\rA_n$, apply $z_\gamma(-r_1,1)$ with $\gamma=-\alpha_\mathrm{max}$.
\[
\begin{pmatrix}1+r_1 \\ \vdots \\ r_1\end{pmatrix}
\xmapsto{x_{-\gamma}(-1)}
\begin{pmatrix}1 \\ \vdots \\ r_1\end{pmatrix}
\xmapsto{x_\gamma(-r_1)}
\begin{pmatrix}1 \\ \vdots \\ 0\end{pmatrix}
\xmapsto{x_{-\gamma}(1)}
\begin{pmatrix}1 \\ \vdots \\ 0\end{pmatrix}.
\]
Now apply $2n-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum (r_i+r_{-i})$ to $r_{-1}$, so by one more transformation one can make the first column trivial. The same can be done with the first row, so in total we used $8n-3$ transformations.

\subsection{$\rB_n$}
\subsection{$\rD_n$}

### 2015-03-16 congrsubgr-boundgen.tex
added draft for Bass-Kolster

\subsection{Relative stable rank 1}
\begin{lemma}\label{lemma:srRI1}
If $sr(R,I)=1$, the width of $SL(2,R,I)$ with respect to $z_\alpha$ does not exceed $4$.
\end{lemma}
\begin{proof}

Let $A=\begin{pmatrix}a & b \\ c & d\end{pmatrix}\in SL(2,R,I)$. First column is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$. Multiply $A$ by $x_{12}(z)$ from left to obtain invertible element in the upper left corner. Applying $x_{21}(-c/a)$ from left and $x_{12}(-b/a)$ from right, we obtain a diagonal matrix. Thus
\begin{multline*}
A=x_{12}(-z)\cdot x_{21}(c/a)\cdot
\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
\cdot x_{12}(b/a)=\\
=x_{12}(-z)\cdot
\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
\cdot x_{21}(y) \cdot x_{12}(b/a),
\end{multline*}
where all the coefficients in transvections lie in $I$ and $\varepsilon\in 1+I$. The above formula is a relative version of Gauss decomposition.
Note that
\begin{multline*}
\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix} =
\begin{pmatrix} 1 & -1 \\ 0 & 1 \end{pmatrix}
\begin{pmatrix} 1 & 0 \\ 1-\varepsilon & 1 \end{pmatrix}
\begin{pmatrix} 1 & 1/\varepsilon \\ 0 & 1 \end{pmatrix}
\begin{pmatrix} 1 & 0 \\ \varepsilon^2-\varepsilon & 1 \end{pmatrix} =\\=
\begin{pmatrix} 1 & -1 \\ 0 & 1 \end{pmatrix}
\begin{pmatrix} 1 & 0 \\ 1-\varepsilon & 1 \end{pmatrix}
\begin{pmatrix} 1 & 1+z \\ 0 & 1 \end{pmatrix}
\begin{pmatrix} 1 & 1/\varepsilon-1-z \\ 0 & 1 \end{pmatrix}
\begin{pmatrix} 1 & 0 \\ \varepsilon^2-\varepsilon & 1 \end{pmatrix},
\end{multline*}
therefore
\[
A=z_{21}(1-\varepsilon,-1-z)\cdot x_{12}(1/\varepsilon-1-z)\cdot x_{21}(\varepsilon^2-\varepsilon+y)\cdot x_{12}(b/a). \qedhere
\]
\end{proof}

\subsection{Dedekind rings of arithmetic type}
\subsubsection{Number field case}
\paragraph{$\mathbb{Z}[\sfrac{1}{p}]$.}
\textbf{TODO:} Insert here Moree's lemma on primitive roots
\begin{lemma}\label{lemma:Z1p}
Assume GRH. If $R=\mathbb{Z}[\sfrac{1}{p}]$ and $I\lhd R$, the width of $SL(2,R,I)$ does not exceed $6$.
\end{lemma}
\begin{proof}
$I\lhd\mathbb{Z}[\sfrac{1}{p}]$, $I=(m)$, $m\in\mathbb{Z}$, $p\nmid m$.

\[ g=\begin{pmatrix}
x & y \\ z & w
\end{pmatrix},\quad x =p^\alpha a,\quad y =p^\beta bm, \]
where $a,b\in\mathbb{Z}$, $p\nmid a,b$ and $\alpha,\beta\in\mathbb{Z}$.

\textsc{Case 1:} $\alpha\geqslant\beta$. Since $p^{\alpha-\beta}a\perp bm^2$ and $p\perp bm^2$, there exist infinitely many rational primes $q$ of the form $p^{\alpha-\beta}a+bm^2k$, such that $p$ is a primitive root modulo $q$. One may choose $q$ prime to $b$. Then
\[ g_1=g\cdot x_{21}(mk) =
\begin{pmatrix} p^\beta q & p^\beta bm \\ * & * \end{pmatrix}.\]
$\exists u\geqslant 1: p^u\equiv b\mod q$, say $p^u=b+lq$. Then
\[ g_2 = g_1\cdot x_{12}(ml) =
\begin{pmatrix} p^\beta q & mp^{\beta+u} \\ * & * \end{pmatrix}. \]
$g_2\equiv 1\mod m$, thus $p^\beta q=1+cm$.
\begin{align*}
g_3 = & g_2\cdot x_{21}\left(\dfrac{-c}{p^{\beta+u}}\right) =
\begin{pmatrix} 1 & mp^{\beta+u} \\ * & * \end{pmatrix}, \\
g_4 = & g_3\cdot x_{12}(-mp^{\beta+u}) =
\begin{pmatrix} 1 & 0 \\ * & * \end{pmatrix}, \\
g_5 = & g_4\cdot x_{21}\left(\dfrac{c}{p^{\beta+u}}\right) =
\begin{pmatrix} 1 & 0 \\ * & * \end{pmatrix}.
\end{align*}
Note that $g_5=g_2\cdot z_{12}\left(-mp^{\beta+u},\dfrac{c}{p^{\beta+u}}\right)$ and that two other coefficients in transvections are multiples of $m$. Thus in this case the length of $g$ does not exceed $4$: $g=x_{21}z_{12}x_{12}x_{21}$.

\textsc{Case 2:} $\alpha<\beta$. Since $\mathbb{Z}[\sfrac{1}{p}]/I$ is finite, $\exists k>0$ such that $p^k\equiv 1\mod I$. One can choose $k>\beta-\alpha$. Then $k+\alpha>-k+\beta$ and
\[ g\cdot h(p^k) =
\begin{pmatrix} p^\alpha a & p^\beta bm \\ * & * \end{pmatrix}
\begin{pmatrix} p^k & 0 \\ 0 & p^{-k} \end{pmatrix}=
\begin{pmatrix} p^{k+\alpha} a & p^{-k+\beta} bm \\ * & * \end{pmatrix}.
\]
One can apply Case 1 fot the latter, so
$g=x_{21}z_{12}x_{12}x_{21}h^{-1}$,
and $x_{12}h^{-1}$ can be processed in the same way, as in Lemma \ref{lemma:srRI1}:
$g=x_{21}z_{12}x_{12}\cdot z_{12}x_{21}x_{12}$.
\end{proof}

### 2015-03-16 paper.tex
added draft for Bass-Kolster

@@
 \documentclass[12pt]{amsart}
-\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools}
+\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac}
 \usepackage[utf8]{inputenc}
-\usepackage[hypertex]{hyperref}
+%\usepackage{hyperref}
 \usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
@@
 
-\newcommand{\K}{\operatorname{\mathrm{K}}}
-\newcommand{\GG}{\operatorname{\mathrm{G}}}
-\newcommand{\St}{\operatorname{\mathrm{St}}}
-\newcommand{\G}{\operatorname{\mathrm{G}}}
-\newcommand{\E}{\operatorname{\mathrm{E}}}
-\newcommand{\M}{\operatorname{\mathrm{M}}}
-\newcommand{\sr}{\operatorname{\mathrm{sr}}}
-\newcommand{\Um}{\operatorname{\mathrm{Um}}}
-\newcommand{\rk}{\operatorname{\mathrm{rk}}}
-\newcommand{\rA}{\mathrm{A}}
-\newcommand{\rB}{\mathrm{B}}
-\newcommand{\rC}{\mathrm{C}} 
-\newcommand{\rD}{\mathrm{D}} 
-\newcommand{\rE}{\mathrm{E}}
+\DeclareMathOperator{\K}{K}
+\DeclareMathOperator{\G}{G}
+\DeclareMathOperator{\St}{St}
+\DeclareMathOperator{\E}{E}
+\DeclareMathOperator{\M}{M}
+\DeclareMathOperator{\sr}{sr}
+\DeclareMathOperator{\asr}{asr}
+\DeclareMathOperator{\Um}{Um}
+\DeclareMathOperator{\rk}{rk}
+\newcommand{\rA}{\mathsf{A}}
+\newcommand{\rB}{\mathsf{B}}
+\newcommand{\rC}{\mathsf{C}} 
+\newcommand{\rD}{\mathsf{D}} 
+\newcommand{\rE}{\mathsf{E}}
 
 \title{Relative parabolic factorizations of Chevalley groups}
-\keywords {Chevalley groups, relative subgroups, stability for $\K_1 $. {\em Mathematical Subject Classification (2010):} 20G35, 19B14}
+\keywords {Chevalley groups, relative subgroups, stability for $\K_1$. {\em Mathematical Subject Classification (2010):} 20G35, 19B14}
 \author {Sergey Sinchuk, Andrei Smolensky}
@@
 
-\section {Introduction}\label{intro}
+\section {Introduction}\label{sec:intro}
 
@@
 
-\section {Preliminaries}\label{prelim}
+\section {Preliminaries}\label{sec:prelim}
+
+\section{Bass---Kolster decomposition}\label{sec:bass-kolster}
+\input{bass-kolster}
+
+\section{Bounded generation}\label{sec:boundgen}
+\input{congrsubgr-boundgen}
 

### 2015-03-20 paper.tex
Added lemma from the thesis

@@
 \usepackage[utf8]{inputenc}
-%\usepackage{hyperref}
+\usepackage{hyperref}
 \usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
@@
 \DeclareMathOperator{\E}{E}
+\DeclareMathOperator{\EP}{EP}
+\DeclareMathOperator{\U}{U}
 \DeclareMathOperator{\M}{M}
@@
 \newcommand{\rE}{\mathsf{E}}
+
+\def\ssub#1{\mathchoice
+   {_{\lower2pt\hbox{$\scriptstyle #1$}}}
+   {_{\lower2pt\hbox{$\scriptstyle #1$}}}
+   {_{\lower1.5pt\hbox{$\scriptscriptstyle #1$}}}
+   {_{\!\lower1.5pt\hbox{$\scriptscriptstyle #1$}}}}
 
@@
 \section {Preliminaries}\label{sec:prelim}
+For any collection of subsets $H_1,\ldots, H_n$ of a group $G$ we denote by $H_1\ldots H_n$ their Minkowski set-product,
+i.\,e. the set consisting of arbitrary products $h_1\ldots h_n$ of elements $h_i\in H_i$. In particular, the equality
+$G = H_1\cdot\ldots\cdot H_n$ means that every element $g\in G$ can be presented as a product $h_1\ldots h_n$ for $h_i\in H_i$.
+
+The following theorem is the main result of \cite{S}.
+\begin{thm}\label{theorem:Stepanov}
+Let $\Phi$ be a reduced irreducible root system and let $S$ be any parabolic subset of roots of $\Phi$ with special part $\Sigma_S$.
+Then $\E(\Phi, R, I)$ is generated by the following two families of elements:
+\begin{itemize}
+ \item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
+ \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$. \end{itemize} \end{thm}
+\begin{proof} See \cite[Theorem~3.4]{S}. \end{proof}
 
@@
 
+\section{Relative Dennis-Vaserstein decomposition} \label{sec:dennis-vaserstein}
+\input{dennis-vaserstein}
+
 \printbibliography

### 2015-03-20 dennis-vaserstein.tex
Part of previous commit

Throughout the present section we denote by $\EP_s(R, I)$ the subgroup $\E(\Delta_s, R, I) \cdot \U(\Sigma_s, I)$, $1 \leq s \leq n$.
Set $\EP_s := \EP_s(R, R) = \E(\Delta_s, R) \cdot \U(\Sigma_s, R)$.

Let $i$, $j$ be two distinct indices $1\leq i,j \leq n$. From Levi decomposition it follows that the following four subsets of $\E(\Phi, R, I)$ are equal to each other:
\begin{multline}\nonumber \U(\Phi, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_i, R, I) \cdot \EP_j(R, I) = \U(\Sigma_i, I)\cdot \U(\Sigma^-_i, I) \cdot \E(\Delta_i, R, I) \cdot \EP_j(R, I) = \\
= \EP_i(R, I) \cdot \E(\Delta_j, R, I) \cdot \U(\Sigma_j^-, I)\cdot \U(\Sigma_j, I) = \EP_i(R, I) \cdot \U(\Sigma^-_i\cap \Sigma^-_j, I) \cdot \EP_j(R, I). \end{multline}
Denote by $A_{ij}$ any of the equal subsets from the previous formula. 
Clearly, $A_{ij}$ is invariant with respect to conjugation by root subgroups $X_{\alpha\ssub{k}}$ for $1\leq k\leq n$ and $X_{-\alpha\ssub{k}}$ for $k\neq i,j$.

\begin{lemma}\label{lemma:dv_unipotent} For any $1\leq i\leq n$ the following statements hold. \begin{enumerate} 
\item $\U(\Phi^\pm, I) = X_{\pm\alpha\ssub{i}}(I)\cdot \U(\Phi^\pm\setminus\{\pm\alpha\ssub{i}\}, I) = \U(\Phi^\pm\setminus\{\pm\alpha\ssub{i}\}, I)\cdot X_{\pm\alpha\ssub{i}}(I).$
\item For any $\xi\in R$ one has $x_{\mp\alpha\ssub{i}}(\xi)\cdot \U(\Phi^\pm\setminus\{\alpha_i\}, I)\cdot x_{\mp\alpha\ssub{i}}(\xi)^{-1} \subseteq \U(\Phi^\pm, I).$
\item $\U(\Sigma_i, I)\cdot \U(\Sigma^-_i, I) \subseteq \U(\Sigma_i\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{i}}(I) \cdot X_{-\alpha\ssub{i}}(I)$.
\end{enumerate} \end{lemma}
\begin{proof}
 The first two statements follow from Chevalley commutator formula. The last statement is a consequence of the first two.
\end{proof}

\begin{lemma}\label{Stein_reduction} 
Suppose that there exists a subset $\widetilde{L_r} \subseteq \E(\Delta_r, R, I)$ satisfying the following two conditions:
\begin{enumerate}[label=(\alph*)] 
 \item\label{stein_cond1} One has $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} = \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I).$
 \item\label{stein_cond2} There is an inclusion $X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \EP_s(R, I).$
\end{enumerate}
Then the set $A_{rs}$ is invariant with respect to
\begin{itemize}
 \item conjugation by elements of $\EP_s$;
 \item left multiplication by elements of $X_{-\alpha\ssub{r}}(I)$.
\end{itemize} \end{lemma}
\begin{proof} Set $A':=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(\Phi, R, I).$
From condition~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A'$.

Let us check the first statement of the lemma. The subgroup $\EP_s$ is generated by root subgroups $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$,
therefore we only need to show that $A'$ is invariant with respect to conjugation by $X_{-\alpha\ssub{r}}$.

From Lemma~\ref{lemma:dv_unipotent} it follows that
\begin{multline}\nonumber A'^{X_{-\alpha\ssub{r}}} \subseteq (\U(\Sigma_r\setminus \{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I))^{X_{-\alpha\ssub{r}}} \subseteq \\
\subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot (X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r})^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I). \end{multline}
On the other hand, from condition~\ref{stein_cond2} it follows that:
\begin{multline}\nonumber 
X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \subseteq
X_{\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I)) \subseteq \\ \subseteq
\widetilde{L_r} \cdot \U(\Sigma_r^+, I) \cdot \EP_s(R, I) \subseteq \widetilde{L_r} \cdot \EP_s(R, I). \end{multline}
Thus we obtain the first statement of the lemma:
\begin{multline}\nonumber 
 A'^{X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq \\ \subseteq
 \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \cdot \EP_s(R, I) = A'. \end{multline}

The proof of the second part of the lemma is similar to the case just analyzed. \end{proof}

### 2015-03-22 bass-kolster.tex
Small fixes for BK

@@
 \begin{itemize}
-\item $\Phi=\rA_\ell$: $\operatorname{sr}(R,I)\leqslant\ell+1$,
-\item $\Phi=\rB_\ell$: $\operatorname{asr}(R,I)\leqslant\ell$,
-\item $\Phi=\rC_\ell$: $\operatorname{sr}(R,I)\leqslant2\ell$,
-\item $\Phi=\rD_\ell$: $\operatorname{asr}(R,I)\leqslant\ell$.
+\item $\Phi=\rA_\ell$: $\sr(R,I)\leqslant\ell+1$,
+\item $\Phi=\rB_\ell$: $\asr(R,I)\leqslant\ell$,
+\item $\Phi=\rC_\ell$: $\sr(R,I)\leqslant2\ell$,
+\item $\Phi=\rD_\ell$: $\asr(R,I)\leqslant\ell$.
 \end{itemize}
-Then the principal congruence subgroup $G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
-\[ G(\Phi,R,I)=U(\Sigma^+,I)\ U(\Sigma^-,I)\cdot Z\cdot U(\Sigma^-,I)\ U(\Sigma^+,I)\cdot G(\Delta,R,I), \]
-where $\Sigma^\pm=\Phi^\pm\setminus\Delta$ and $Z=\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \}$.
+Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
+\[ \G(\Phi,R,I)=\U(\Sigma^+,I)\ \U(\Sigma^-,I)\cdot \Z\cdot \U(\Sigma^-,I)\ \U(\Sigma^+,I)\cdot \G(\Delta,R,I), \]
+where $\Sigma^\pm=\Phi^\pm\setminus\Delta$ and $\Z=\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \}$.
 \end{thm}
+\begin{proof}
+\textsc{Case $\Phi=\rA_\ell$:}
+For $g\in\G(\rA_\ell,R,I)$ let $(1+r_1,r_2,\ldots,r_\ell,r_{\ell+1})^t\in\Um(\ell+1,R,I)$, $r_i\in I$ be its first column.
+One can add the last entry to the first $\ell$ with some coefficients from $I$ to make then form a unimodular column of length $\ell$.
+Then $\ell$ lower transformations (with coefficients from $I$) can make the last entry equal $r_1$.
+Now apply $z_\gamma(-r_1,1)$, $\gamma=-\alpha_{\max}$:
+\begin{multline*}
+(1+r_1,r_2,\ldots,r_\ell,r_1)^t\xmapsto{x_{-\gamma}(-1)}(1,r_2,\ldots,r_\ell,r_1)^t\xmapsto{x_\gamma(-r_1)}\\\longmapsto(1,r_2,\ldots,r_\ell,0)^t\xmapsto{x_{-\gamma}(1)}(1,r_2,\ldots,r_\ell,0)^t.
+\end{multline*}
+Now $\ell-1$ lower transformations eliminates all the remaining entries in the first column, while $\ell$ more upper ones will make the first row trivial.
 
-$\Phi$ a root system, $\Delta\subset\Phi$ a terminal subsystem, $R$ a ring, $I\lhd R$.
-
-(!) $G(\Phi,R,I)=G(\Delta,R,I)\cdot E(\Phi,R,I)$.
-
-\textbf{TODO:} reformat all of the below into one subsection (math in section titles does not work with hyperref, apparently)
-
-\subsection{$\rA_n$}
-
-Assuming $sr(R,I)\leqslant n$.
-
-Working with the first column, $(1+r_1,r_2,\ldots,r_n,r_{n+1})^t\in Umd(n+1,R,I)$, $r_i\in I$.
-Find $c_1,\ldots,c_n\in I$ such that $(1+r_1+c_1r_{n+1},r_2+c_2r_{n+1},\ldots,r_n+c_nr_{n+1})\in Umd(n,R,I)$ and apply $n$ corresponding upper transformations.
-Now find $c_1,\ldots,c_n\in R$ such that $c_1(1+r_1)+c_2r_2+\ldots+c_nr_n=1$, then for $c_i'=c_i\cdot(r_1-r_{n+1})\in I$ one has $c_1'(1+r_1)+c_2'r_2+\ldots+c_n'r_n=r_1-r_{n+1}$.
-Apply $n$ lower transformations to add $c_i'r_i$ to $r_{n+1}$, so that $r_{n+1}\mapsto r_1$.
-Now apply $z_\gamma$, $\gamma=-\alpha_\mathrm{max}$.
-$z_\gamma(-r_1,1)=x_{-\gamma}(1)\cdot x_\gamma(-r_1)\cdot x_{-\gamma}(-1)$.
-So
-\[
-\begin{pmatrix}
-1+r_1 \\ \vdots \\ r_1
-\end{pmatrix}
-\xmapsto{x_{-\gamma}(-1)}
-\begin{pmatrix}
-1\\ \vdots \\ r_1
-\end{pmatrix}
-\xmapsto{x_\gamma(-r_1)}
-\begin{pmatrix}
-1\\ \vdots \\ 0
-\end{pmatrix}
-\xmapsto{x_{-\gamma}(1)}
-\begin{pmatrix}
-1\\ \vdots \\ 0
-\end{pmatrix}.
-\]
-Now applying $n-1$ lower transformations at level $I$ make the first column trivial.
-$n$ more transformation will make first row trivial.
-Thus $n+n+1+(n-1)+n=4n$ transformations will give a matrix from $G(\Delta,R,I)$.
-
-\subsection{$\rC_n$}
-
-\textbf{TODO:} shorten this twice (at least)
-
-Assuming $sr(R,I)\leqslant 2n$.
-First column: $(1+r_1,r_2,\ldots,r_n,r_{-n},\ldots,r_{-1})^t\in Umd(2n,R,I)$.
-Find $c_1,\ldots,c_{-2}\in I$ such that $(1+r_1+c_1r_{-1},\ldots,r_{-2}+c_{-2}r_{-2})=(1+r_1',\ldots,r_{-1}')\in Umd(2n-1,R,I)$.
-First add $c_{-i}r_{-1}$ to $r_{-i}$, so that
+\textsc{Case $\Phi=\rC_\ell$:}
+First column: $(1+r_1,r_2,\ldots,r_\ell,r_{-\ell},\ldots,r_{-1})^t\in\Um(2\ell,R,I)$.
+Find $c_1,\ldots,c_{-2}\in I$ such that $(1+r_1+c_1r_{-1},\ldots,r_{-2}+c_{-2}r_{-1})=(1+r_1',\ldots,r_{-2}')\in\Um(2\ell-1,R,I)$.
+First add $c_{-i}r_{-1}$ to $r_{-i}$ for $-i=-\ell,\ldots,-2$, so that
 \[
@@
 \end{pmatrix}
-\mapsto
+\longmapsto
 \begin{pmatrix}
-1+r_1+\sum c_{-i}r_i\\ r_i \\ r_{-i}+c_{-i}r_{-1} \\ r_{-1}
+1+r_1+\sum_{i=2}^\ell c_{-i}r_i\\ r_i \\ r_{-i}+c_{-i}r_{-1} \\ r_{-1}
 \end{pmatrix}=
@@
 1+r_{11} \\ r_i \\ r_{-i}' \\ r_{-1}
-\end{pmatrix}.
+\end{pmatrix},\quad i=2,\ldots,\ell.
 \]
-Denote $\mathfrak{a}=\sum r_{-i}'R\unlhd R$. Now add $c_ir_{-1}$ to $r_i$:
+Denote $\mathfrak{a}=\sum_{i=-\ell}^{-2} r_i'R\unlhd R$. Now add $c_ir_{-1}$ to $r_i$ for $i=2,\ldots,\ell$:
 \[
@@
 \end{pmatrix}
-\mapsto
+\longmapsto
 \begin{pmatrix}
@@
 1+r_{12} \\ r_i' \\ r_{-i}' \\ r_{-1}
-\end{pmatrix},
-\ a\in\mathfrak{a}.
+\end{pmatrix},\quad
+\begin{matrix*}[l]
+a\in\mathfrak{a}\\
+i=2,\ldots,\ell
+\end{matrix*}
 \]
-Finally, add $\left(c_1+\sum_{j=2}^n c_jc_{-j}\right)r_{-1}$ to the first row:
+Finally, add $\left(c_1+\sum_{i=2}^\ell c_ic_{-i}\right)r_{-1}$ to the first row:
 \begin{multline*}
-\left(1+r_1+\sum c_{-i}r_i+a\right)+\left(c_1r_{-1}+\sum c_jc_{-j}r_{-1}\right)=\\
-=(1+r_1+c_1r_{-1})+\sum c_{-i}(r_i+c_ir_{-1})+a=\\
-=1+r_1'+\sum c_{-i}r_i'+a=1+r_1''.
+\left(1+r_1+\sum\nolimits_{i=2}^\ell c_{-i}r_i+a\right)+\left(c_1r_{-1}+\sum\nolimits_{i=2}^\ell c_ic_{-i}r_{-1}\right)=\\
+=(1+r_1+c_1r_{-1})+\sum\nolimits_{i=2}^\ell c_{-i}(r_i+c_ir_{-1})+a=\\
+=1+r_1'+\sum\nolimits_{i=2}^\ell c_{-i}r_i'+a=1+r_1''.
 \end{multline*}
-Note that $\langle 1+r_1'',r_2',\ldots,r_{-2}'\rangle=\langle 1+r_1',r_2',\ldots,r_{-2}'\rangle$, so we made the first $2n-1$ elements to form a unimodular column.
+Note that $\langle 1+r_1'',r_2',\ldots,r_{-2}'\rangle=\langle 1+r_1',r_2',\ldots,r_{-2}'\rangle$, so we made the first $2\ell-1$ elements form a unimodular column.
 
-Find $c_1,\ldots,c_{-2}\in I$ such that $c_1(1+r_1)+c_2r_2+\ldots+c_{-2}r_{-2}=r_1-r_{-1}$. Add $c_{-i}r_i$ to $r_{-1}$:
+Now we may assume that the first column $(1+r_1,\ldots,r_{-1})^t$ has its first $2\ell-1$ entries unimodular.
+Find $c_1,\ldots,c_{-2}\in I$ such that $c_1(1+r_1)+c_2r_2+\ldots+c_{-2}r_{-2}=r_1-r_{-1}$.
+Add $c_{-i}r_i$ to $r_{-1}$, $i=2,\ldots,\ell$:
 \[
@@
 \end{pmatrix}
-\mapsto
+\longmapsto
 \begin{pmatrix}
-1+r_1 \\ r_i+c_{-i}r_1 \\ r_{-i} \\ r_{-1}+\sum s_{-i}r_{-i}
+1+r_1 \\ r_i+c_{-i}r_1 \\ r_{-i} \\ r_{-1}+\sum_{i=2}^\ell c_{-i}r_{-i}
 \end{pmatrix}=
@@
 1+r_1 \\ r_i' \\ r_{-i} \\ r_{-11}
-\end{pmatrix}.
+\end{pmatrix},\quad i=2,\ldots,\ell.
 \]
-Then add $c_ir_i'=c_i(r_1+c_{-i}r_{-i})$ to $r_{-11}$:
+Then add $c_ir_i'=c_i(r_1+c_{-i}r_{-i})$, $i=2,\ldots,\ell$ to $r_{-11}$:
 \[
-1+r_1\mapsto 1+r_1,\quad r_{-11}\mapsto r_{-1}+\sum c_{-i}r_{-i}+\sum c_i(r_i+c_{-i}r_1)=r_{-12}.
+1+r_1\longmapsto 1+r_1,\quad r_{-11}\longmapsto r_{-1}+\sum_{i=2}^\ell c_{-i}r_{-i}+\sum_{i=2}^\ell c_i(r_i+c_{-i}r_1)=r_{-12}.
 \]
-Next add $(c_1-\sum c_ic_{-i})(1+r_1)$ to $r_{-12}$:
+Next add $(c_1-\sum_{i=2}^\ell c_ic_{-i})(1+r_1)$ to $r_{-12}$:
 \begin{multline*}
-r_{-12}\mapsto r_{-1}+\sum c_{-i}r_{-i}+\sum c_i(r_i+c_{-i}(1+r_1))-\sum c_ic_{-i}(1+r_1)=\\=r_{-1}+c_1(1+r_1)+\sum(c_ir_i+c_{-i}r_{-i})=r_{-1}+(r_1-r_{-1})=r_1.
+r_{-12}\mapsto r_{-1}+\sum_{i=2}^\ell c_{-i}r_{-i}+\sum_{i=2}^\ell c_i(r_i+c_{-i}(1+r_1))+c_1(1+r_1)-\sum_{i=2}^\ell c_ic_{-i}(1+r_1)=\\=r_{-1}+c_1(1+r_1)+\sum_{i=2}^\ell(c_ir_i+c_{-i}r_{-i})=r_{-1}+(r_1-r_{-1})=r_1.
 \end{multline*}
@@
 \]
-Now apply $2n-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum (r_i+r_{-i})$ to $r_{-1}$, so by one more transformation one can make the first column trivial.
-The same can be done with the first row, so in total we used $8n-3$ transformations.
-
-\subsection{$\rB_n$}
-\subsection{$\rD_n$}
+Now apply $2\ell-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum_{i=2}^\ell (r_i+r_{-i})$ to $r_{-1}$, so by one more transformation one can make the first column trivial.
+The same can be done with the first row, so in total we used $8\ell-3$ transformations.
+\end{proof}
+%\subsection{$\rB_n$}
+%\subsection{$\rD_n$}

### 2015-03-22 dennis-vaserstein.tex

@@
 
+\subsection{Main reduction.}
 Let $i$, $j$ be two distinct indices $1\leq i,j \leq n$. From Levi decomposition it follows that the following four subsets of $\E(\Phi, R, I)$ are equal to each other:
@@
 
+\begin{lemma}\label{lemma:conj_lemma} Let $G$ be a group, $H\leq G$ be a subgroup and $A, B\subseteq G$ be two subsets.
+Assume that $A$ is invariant with respect to left multiplication by elements of $B$ and conjugation by elements of the subgroup $H$.
+Then $A$ is invariant with respect to left multiplication by elements of the set $B^H = \{b^h \vert b\in B, h\in H\}$. \end{lemma}
+\begin{proof} $b^h \cdot A \subseteq h^{-1}\cdot b \cdot h \cdot A \subseteq h^{-1} \cdot b \cdot A \cdot h \subseteq h^{-1} \cdot A \cdot h \subseteq A. \qedhere$ \end{proof}
+
 \begin{lemma}\label{Stein_reduction} 
@@
 \end{enumerate}
-Then the set $A_{rs}$ is invariant with respect to
+Then $A_{rs} = \E(\Phi, R, I)$. \end{lemma}
+\begin{proof} Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(\Phi, R, I).$
+From condition~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A$.
+
+The first step of the proof is to show that $A_{rs}$ is invariant with respect to conjugation by the root subgroup $X_{-\alpha\ssub{r}}$ 
+and left multiplication by elements of $X_{-\alpha\ssub{r}}(I)$. To prove this, observe first that from Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} it follows that
+\begin{multline}\nonumber 
+A \subseteq \U(\Sigma_r\setminus \{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\ 
+\subseteq \U(\Sigma_r\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\
+\subseteq \U(\Sigma_r\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I)  \cdot \EP_s(R, I) \subseteq \\
+\subseteq \U(\Sigma_r\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I). \end{multline}
+Now it remains to apply Lemma~\ref{lemma:dv_unipotent} once again:
+\begin{equation}\nonumber A^{X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq A. \end{equation}
+\begin{equation}\nonumber X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq A. \end{equation}
+
+  Notice that the subgroup $\EP_s$ is generated by root subgroups $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$,
+therefore in fact we have just proved that $A$ is invariant with respect to conjugation by all elements of $\EP_s$.
+
+Now we are ready to prove the needed equality. By virtue of Theorem~\ref{theorem:Stepanov} it suffices to show that
+$A$ is invariant with respect to left multiplication by elements of the following two families:
 \begin{itemize}
- \item conjugation by elements of $\EP_s$;
- \item left multiplication by elements of $X_{-\alpha\ssub{r}}(I)$.
-\end{itemize} \end{lemma}
-\begin{proof} Set $A':=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(\Phi, R, I).$
-From condition~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A'$.
-
-Let us check the first statement of the lemma. The subgroup $\EP_s$ is generated by root subgroups $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$,
-therefore we only need to show that $A'$ is invariant with respect to conjugation by $X_{-\alpha\ssub{r}}$.
-
-From Lemma~\ref{lemma:dv_unipotent} it follows that
-\begin{multline}\nonumber A'^{X_{-\alpha\ssub{r}}} \subseteq (\U(\Sigma_r\setminus \{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I))^{X_{-\alpha\ssub{r}}} \subseteq \\
-\subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot (X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r})^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I). \end{multline}
-On the other hand, from condition~\ref{stein_cond2} it follows that:
-\begin{multline}\nonumber 
-X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \subseteq
-X_{\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I)) \subseteq \\ \subseteq
-\widetilde{L_r} \cdot \U(\Sigma_r^+, I) \cdot \EP_s(R, I) \subseteq \widetilde{L_r} \cdot \EP_s(R, I). \end{multline}
-Thus we obtain the first statement of the lemma:
-\begin{multline}\nonumber 
- A'^{X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq \\ \subseteq
- \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \cdot \EP_s(R, I) = A'. \end{multline}
-
-The proof of the second part of the lemma is similar to the case just analyzed. \end{proof}
+ \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
+ \item $x_{\beta}(s)$, $s \in I$, $\beta \in \Phi$. \end{itemize}
+In fact, thanks to Lemma~\ref{lemma:conj_lemma} it suffices to prove this statement only for the second family.
+Moreover, we can additionally assume $\beta\in \Sigma_r^-$.
+%TODO: To be continued 
+\end{proof}

### 2015-04-03 paper.tex
Small fixes for BK
Stability conditions section
Added some intro on stable ranks

@@
 \documentclass[12pt]{amsart}
-\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac}
+\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac, cite}
 \usepackage[utf8]{inputenc}
@@
 \DeclareMathOperator{\U}{U}
+\DeclareMathOperator{\X}{X}
+\DeclareMathOperator{\Z}{Z}
 \DeclareMathOperator{\M}{M}
 \DeclareMathOperator{\sr}{sr}
+\DeclareMathOperator{\Rad}{Rad}
+\DeclareMathOperator{\SR}{SR}
 \DeclareMathOperator{\asr}{asr}
+%TODO: Replace Um with Ums/Umd where possible
 \DeclareMathOperator{\Um}{Um}
+\DeclareMathOperator{\Ums}{Ums}
+\DeclareMathOperator{\Umd}{Umd}
 \DeclareMathOperator{\rk}{rk}
@@
 
+\section{Stability conditions}\label{sec:stability-conditions}
+\input{stability-conditions}
+
 \section{Bass---Kolster decomposition}\label{sec:bass-kolster}
@@
 
-\section{Relative Dennis-Vaserstein decomposition} \label{sec:dennis-vaserstein}
+\section{Relative Dennis-Vaserstein decomposition}\label{sec:dennis-vaserstein}
 \input{dennis-vaserstein}

### 2015-04-03 stability-conditions.tex
Added some intro on stable ranks

As we will be mainly concerned with applications to stability of $K_1$ of Chevalley groups, our treatment of stability conditions is restricted to the case of commutative $R$. 
We refer the reader to~\cite{Ba64, Va69, Va71} for a more general exposition.

\subsection{Stable rank}
Recall the definition of {\it stable rank} introduced by H.~Bass and L.~Vaserstein (see~\cite{Ba64, Va69}).
\begin{dfn} Recall that a row $a=(a_1,\ldots, a_n)\in {}^n\!R$ is called {\it $I$-unimodular} if elements $a_1-1, a_2, \ldots, a_n$ are contained in $I$ while $a_1, a_2, \ldots, a_n$ generate $R$ as an ideal.\end{dfn}
A column $b \in R^n$ will be called $I$-unimodular if its transpose $b^t$ is an $I$- unimodular row. We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n,R,I)$ (resp. $\Ums(n,R,I)$).
When $R=I$ we refer to $R$-unimodular rows and columns as simply unimodular.

\begin{lemma} \label{lemma:relstrlemma} For any $I$-unimodular row $a=(a_1, \ldots, a_n)$ there exists $I$-unimodular column $b=(b_1,\ldots, b_n)^T$ such that $ab = \sum\limits_{i=1}^n a_i b_i = 1$. \end{lemma}

\begin {dfn} An $I$-unimodular row $a=(a_1,\ldots a_{n+1})$ is called {\it stable} if one can choose $b_1,\ldots, b_n\in R$ such that
row $(a_1 + a_{n+1}b_1,\ldots, a_{n}+ a_{n+1}b_n)$ is also $I$-unimodular. if, moreover, elements $b_1,\ldots, b_n$ can be chosen from  $I$ then such $a$ will be called {\it $I$-stable}. \end{dfn}

We say that a pair $(R, I)$ satisfies stable range condition $\SR_n(R, I)$ if any $I$-unimodular row of length $n+1$ is stable.
\begin{lemma}\label{lemma:relstrlemma2}\strut\begin{enumerate}\item The condition $\SR_n(R, I)$ implies $\SR_m(R,I)$ for any $m\geq n$.
\item The condition $\SR_n(R, I)$ implies that any $I$-unimodular row of length $n+1$ is $I$-stable.\end{enumerate}\end{lemma}

By definition, the {\it relative stable rank} $\sr(R, I)$ of a pair $(R, I)$ is the smallest natural number $n$ such that condition $\SR_n(R, I)$ holds.
If $\SR_n(R, I)$ is not satisfied for any $n>0$ we set $\sr(R, I)=\infty$.

The following proposition summarizes basic properties of stable ranks.
\begin{prop} \label{prop:sr_properties} Let $R$ be arbitary commutative unital ring and let $I\trianglelefteq R$ be its ideal.
 \begin{itemize}
  \item For any ideal $J\trianglelefteq R$, $J\subseteq I$ one has $$\sr(R, I)\leq\sr(R),\quad \sr(R/J, I/J)\leq \sr(R, I).$$
  \item Stable rank of a direct product of rings is equal to the maximum of stable ranks of its factors: $$\sr(\prod\limits_{i=1}^n R_i) = \max\limits_{i=1}^n\left(\sr(R_i)\right).$$
  \item Stable rank does not change after taking quotient modulo nil-radical: $\sr(R)=\sr(R/\Rad(R))$.
 \end{itemize}\end{prop} \begin{proof} See~\cite{Va71}. \end{proof}

\begin{example} Since the stable rank of a field is one, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$. \end{example}

\subsection{Absolute stable rank}

%TODO: $\asr(R,I)$

### 2015-04-04 stability-conditions.tex
Given definition of asr

@@
 \subsection{Absolute stable rank}
+For a row $a=(a_1,\ldots, a_n) \in {}^n\!R$ denote by $\mathfrak{I}(u)$ the intersection of ideals of $R$ containing $a_1, \ldots, a_n$.
+It is easy to see that a row $a\in R^n$ is unimodular iff $\mathfrak{I}(u)=R$. 
+Clearly, for any $g\in\GL(n, R)$ one has $\mathfrak{I}(u\cdot g)=\mathfrak{I}(u)$.
 
-%TODO: $\asr(R,I)$
+A ring $R$ is said to satisfy condition $\ASR_{n}(R)$ if for any row $(a_1,\ldots,a_{n+1})^t\in {}^{n+1}\!R$ 
+one can find elements $b_1,\ldots b_n\in R$ such that $$\mathfrak{I}(a_1+b_1a_{n+1},\ldots,a_n+b_na_{n+1})^t= \mathfrak{I}(a_1,\ldots,a_{n+1})^t.$$
+It is easy to see that $\ASR_m(R)$ implies $\ASR_n(R)$ for any $n\ge m$. 
+By definition, the {\it absolute stable rank \/} $\asr(R)$ is the smallest natural $n$ such that $\ASR_n(R)$ holds.
+Similarly, we set $\asr(R)=\infty$ if $\ASR_n(R)$ does not hold for any $n$.
+
+Let $R$ be a commutative ring. We denote by $\Max(R)$ its {\it maximum spectrum} i.e. the set of maximal ideals of $R$ equipped with Zariski topology.
+The following result gives an upper estimate for the absolute stable rank.~\cite[Theorem~2.3]{EO}, \cite[Theorem~3.7]{MKV}).
+\begin{thm} Let $R$ be a commutative ring whose maximum spectrum 
+$\Max(R)$ can be covered with a finite family of subsets $X_1\ldots, X_m$ such that the topological dimension of every subset $X_i$
+does not exceed some number $d$. Then $\asr(A)\leq d+1$. \end{thm}
+Clearly one has \begin{equation}\nonumber \sr(R)\leq \asr(R)\leq \dim(\Max(R))+1\leq \dim(\Spec(R))+1.\end{equation}

### 2015-04-04 stability-conditions.tex
Introduced notion of relative asr

@@
 
-A ring $R$ is said to satisfy condition $\ASR_{n}(R)$ if for any row $(a_1,\ldots,a_{n+1})^t\in {}^{n+1}\!R$ 
+A ring $R$ is said to satisfy condition $\ASR_{n}(R, I)$ if for any row $a$ such that $a_1-1,\ldots,a_{n+1}\in I$ 
 one can find elements $b_1,\ldots b_n\in R$ such that $$\mathfrak{I}(a_1+b_1a_{n+1},\ldots,a_n+b_na_{n+1})^t= \mathfrak{I}(a_1,\ldots,a_{n+1})^t.$$
-It is easy to see that $\ASR_m(R)$ implies $\ASR_n(R)$ for any $n\ge m$. 
-By definition, the {\it absolute stable rank \/} $\asr(R)$ is the smallest natural $n$ such that $\ASR_n(R)$ holds.
-Similarly, we set $\asr(R)=\infty$ if $\ASR_n(R)$ does not hold for any $n$.
+It is easy to see that $\ASR_m(R, I)$ implies $\ASR_n(R, I)$ for any $n\ge m$. 
+By definition, the {\it absolute relative stable rank} $\asr(R, I)$ is the smallest natural $n$ such that $\ASR_n(R, I)$ holds.
+Similarly, we set $\asr(R, I)=\infty$ if such $n$ does not exist. 
+When $I=R$ we call $\asr(R, R)$ simply {\it absolute stable rank} of $R$ and denote it by $\asr(R)$.
 
@@
 does not exceed some number $d$. Then $\asr(A)\leq d+1$. \end{thm}
-Clearly one has \begin{equation}\nonumber \sr(R)\leq \asr(R)\leq \dim(\Max(R))+1\leq \dim(\Spec(R))+1.\end{equation}
+Clearly one has \begin{equation}\nonumber \sr(R, I)\leq \asr(R, I)\leq \asr(R) \leq \dim(\Max(R))+1\leq \dim(\Spec(R))+1.\end{equation}

### 2015-04-04 congrsubgr-boundgen.tex
Added lemma from the thesis
Make the bounded generation section readable

@@
-\subsection{Relative stable rank 1}
+We now give an application of the above decomposition to the problem of bounded generation.
+\begin{dfn}
+Given a group $G$ and a set of generators $X$ (for simplicity we assume $X=X^{-1}$ and $1\in X$), one says that the width of $G$ with respect to $X$ equals $N$, if $G=X^N$, i.e.
+every element of $G$ can be represented as a product of at most $N$ generators from $X$.
+\end{dfn}
 \begin{lemma}\label{lemma:srRI1}
-If $sr(R,I)=1$, the width of $SL(2,R,I)$ with respect to $z_\alpha$ does not exceed $4$.
+If $\sr(R,I)=1$, the width of $\SL(2,R,I)$ with respect to $z_\alpha$ does not exceed $4$.
 \end{lemma}
 \begin{proof}
-
-Let $A=\begin{pmatrix}a & b \\ c & d\end{pmatrix}\in SL(2,R,I)$.
-First column is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
-Multiply $A$ by $x_{12}(z)$ from left to obtain invertible element in the upper left corner.
-Applying $x_{21}(-c/a)$ from left and $x_{12}(-b/a)$ from right, we obtain a diagonal matrix.
+Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}\in\SL(2,R,I)$.
+The first column is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
+Multiply $A$ by $x_{12}(z)$ from the left to obtain an invertible element in the upper left corner.
+Applying $x_{21}(-c/a)$ from the left and $x_{12}(-b/a)$ from the right, we obtain a diagonal matrix.
 Thus
@@
 \end{proof}
-
-\subsection{Dedekind rings of arithmetic type}
-\subsubsection{Number field case}
-\paragraph{$\mathbb{Z}[\sfrac{1}{p}]$.}
-\textbf{TODO:} Insert here Moree's lemma on primitive roots
+\begin{rem}
+In the above lemma one can restrict himself to the generators of the form $x_\alpha(s)$ and $z_\alpha(s,1)$, $s\in I$, and have an estimate of $5$ factors.
+It might be useful since $\left\{z_\alpha(s,1)\mid s\in I\right\}=\X_\alpha(I)^{x_\alpha(1)}$ if a $1$-parameter subgroup.
+\end{rem}
+\begin{lemma}
+Let $p$ be a rational prime, $c\perp d$ two coprime integers and $p\perp d$.
+Then under the assumption of the Generalized Riemann Hypothesis there exist infinitely many primes $q\equiv c\pmod{d}$, such that $p$ is a primitive root modulo $q$.
+\end{lemma}
 \begin{lemma}\label{lemma:Z1p}
-Assume GRH. If $R=\mathbb{Z}[\sfrac{1}{p}]$ and $I\lhd R$, the width of $SL(2,R,I)$ does not exceed $6$.
+Assume GRH. If $R=\mathbb{Z}[\sfrac{1}{p}]$ and $I\lhd R$, the width of $\SL(2,R,I)$ does not exceed $6$.
 \end{lemma}
 \begin{proof}
-$I\lhd\mathbb{Z}[\sfrac{1}{p}]$, $I=(m)$, $m\in\mathbb{Z}$, $p\nmid m$.
-
-\[ g=\begin{pmatrix}
-x & y \\ z & w
-\end{pmatrix},\quad x =p^\alpha a,\quad y =p^\beta bm, \]
-where $a,b\in\mathbb{Z}$, $p\nmid a,b$ and $\alpha,\beta\in\mathbb{Z}$.
-
+Write $I=(m)$ for some $m\in\mathbb{Z}$, $p\nmid m$. Fix $g\in\SL(2,R,I)$:
+\[ g=\begin{pmatrix}x & y \\ z & w\end{pmatrix},\quad
+\begin{matrix*}[l]
+x=p^\alpha a,\quad & a,b,\alpha,\beta\in\mathbb{Z}, \\ y=p^\beta bm, & p\nmid a,b.
+\end{matrix*}\]
 \textsc{Case 1:} $\alpha\geqslant\beta$.
@@
 \begin{pmatrix} p^\beta q & p^\beta bm \\ * & * \end{pmatrix}.\]
-$\exists u\geqslant 1: p^u\equiv b\mod q$, say $p^u=b+lq$. Then
+There exists $u\geqslant 1$ such that $p^u\equiv b\pmod q$, say $p^u=b+lq$. Then
 \[ g_2 = g_1\cdot x_{12}(ml) =
 \begin{pmatrix} p^\beta q & mp^{\beta+u} \\ * & * \end{pmatrix}. \]
-$g_2\equiv 1\mod m$, thus $p^\beta q=1+cm$.
+$g_2\equiv 1\pmod m$, thus $p^\beta q=1+cm$ for some $c$.
 \begin{align*}
@@
 \begin{pmatrix} 1 & mp^{\beta+u} \\ * & * \end{pmatrix}, \\
-g_4 = & g_3\cdot x_{12}(-mp^{\beta+u}) =
+g_4 = & g_3\cdot x_{12}\left(-mp^{\beta+u}\right) =
 \begin{pmatrix} 1 & 0 \\ * & * \end{pmatrix}, \\
@@
 \end{align*}
-Note that $g_5=g_2\cdot z_{12}\left(-mp^{\beta+u},\dfrac{c}{p^{\beta+u}}\right)$ and that two other coefficients in transvections are multiples of $m$.
+Note that $g_5=g_2\cdot z_{12}\left(-mp^{\beta+u},c/p^{\beta+u}\right)$ and that the two other coefficients in the transvections are multiples of $m$.
 Thus in this case the length of $g$ does not exceed $4$: $g=x_{21}z_{12}x_{12}x_{21}$.
 
-\textsc{Case 2:} $\alpha<\beta$. Since $\mathbb{Z}[\sfrac{1}{p}]/I$ is finite, $\exists k>0$ such that $p^k\equiv 1\mod I$. One can choose $k>\beta-\alpha$. Then $k+\alpha>-k+\beta$ and
-\[ g\cdot h(p^k) =
+\textsc{Case 2:} $\alpha<\beta$. Since $\mathbb{Z}[\sfrac{1}{p}]/I$ is finite, there exists $k>0$ such that $p^k\equiv 1\pmod I$. One can choose $k>\beta-\alpha$. Then $k+\alpha>-k+\beta$ and
+\[ g\cdot h\left(p^k\right) =
 \begin{pmatrix} p^\alpha a & p^\beta bm \\ * & * \end{pmatrix}

### 2015-04-04 congrsubgr-boundgen.tex
Bounded generation for general Hasse domains

@@
 \]
-One can apply Case 1 fot the latter, so
+One can apply Case 1 for the latter, so
 $g=x_{21}z_{12}x_{12}x_{21}h^{-1}$,
@@
 \end{proof}
+Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type, defined by a finite set $S$ of places of some global field, and $I$ an ideal in $\mathcal{O}_S$.
+It is shown in [?] that $E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$.
+From this one immediately gets the bounded generation for $\G(\Phi,R,I)$.
+
+Assume for simplicity that $\K_1(\Phi,\mathcal{O}_S,I)=1$.
+\begin{lemma}
+If $\rk\Phi\geqslant2$, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to $z_\alpha$.
+\end{lemma}
+\begin{proof}
+Because of the Bass---Kolster decomposition it suffices to express every element $g$ of $\SL(2,\mathcal{O}_S,I)$ as a product of a bounded number of generators in a group of rank $2$. Write
+\[ g=\begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2,\mathcal{O}_S,I),\quad a,b,c,d\in I. \]
+
+The condition $\det(g)=1$ implies $a+d=bc-ad\in I^2$.
+
+$G(I,I)$ denotes the Vaserstein's congruence subgroup
+\[ G(I,I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2,\mathcal{O}_S,I)\;\middle|\; a,d\in I^2,\ b,c\in I \right\}. \]
+Note that $g\cdot z_{21}(a,1)\in G(I,I)$. Indeed,
+\[
+\begin{pmatrix}
+1+a & b \\ c & 1+d
+\end{pmatrix} \xmapsto{\cdot z_{21}(a,1)}
+\begin{pmatrix}
+1+ba-a^2 & b-a-ba-a^2 \\ c+a+ad-ac & 1+bc-ac
+\end{pmatrix} \in G(I,I).
+\]
+Now for a matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)\in\G(2,\mathcal{O}_S,I^2)$.
+Since for root systems $\Phi\neq\rC_\ell$ with $\rk\Phi\geqslant2$ one has $\E(\Phi,\mathcal{O}_S,I^2)\leqslant\E(\Phi,I)$, we are done for all groups but symplectic.
+
+\textbf{TODO:} What happens for $\rC_\ell$?
+\end{proof}

### 2015-04-04 congrsubgr-boundgen.tex
Some references and small fixes

@@
 \end{rem}
+The following lemma is a corollary of Theorems~5.7 and 5.8 of \cite{LenMorStePrimitiveRoot}.
 \begin{lemma}
@@
 \end{lemma}
+One can modify Lemma~6 of \cite{VavSmSuUnitrEng} (see also \cite{VseUnitrZ1p}) in the following way:
 \begin{lemma}\label{lemma:Z1p}
@@
 Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type, defined by a finite set $S$ of places of some global field, and $I$ an ideal in $\mathcal{O}_S$.
-It is shown in [?] that $E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$.
+It is shown in \cite{TavgenThesis} that $E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$.
 From this one immediately gets the bounded generation for $\G(\Phi,R,I)$.
@@
 
-$G(I,I)$ denotes the Vaserstein's congruence subgroup
-\[ G(I,I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2,\mathcal{O}_S,I)\;\middle|\; a,d\in I^2,\ b,c\in I \right\}. \]
+Define the Vaserstein's congruence subgroup as
+\[ G(I,I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2,\mathcal{O}_S)\;\middle|\; a,d\in I^2,\ b,c\in I \right\}. \]
 Note that $g\cdot z_{21}(a,1)\in G(I,I)$. Indeed,

### 2015-04-04 paper.tex
Given definition of asr
Make the bounded generation section readable
Some references and small fixes

@@
 \documentclass[12pt]{amsart}
-\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac, cite}
+\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac}
+\usepackage{hyperref}
 \usepackage[utf8]{inputenc}
-\usepackage{hyperref}
 \usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
@@
 \DeclareMathOperator{\G}{G}
+\DeclareMathOperator{\GL}{GL}
+\DeclareMathOperator{\SL}{SL}
 \DeclareMathOperator{\St}{St}
@@
 \DeclareMathOperator{\M}{M}
+\DeclareMathOperator{\SR}{SR}
 \DeclareMathOperator{\sr}{sr}
 \DeclareMathOperator{\Rad}{Rad}
-\DeclareMathOperator{\SR}{SR}
+\DeclareMathOperator{\Max}{Max}
+\DeclareMathOperator{\Spec}{Spec}
+\DeclareMathOperator{\ASR}{ASR}
 \DeclareMathOperator{\asr}{asr}
-%TODO: Replace Um with Ums/Umd where possible
+%TODO: Deprecate Um -- Use Ums/Umd whenever possible
 \DeclareMathOperator{\Um}{Um}
@@
 
-\begin{abstract} \end{abstract}
+%\begin{abstract} \end{abstract}
 
@@
 
-\section {Introduction}\label{sec:intro}
+\section{Introduction}\label{sec:intro}
 
@@
 
-\section {Preliminaries}\label{sec:prelim}
+\section{Preliminaries}\label{sec:prelim}
 For any collection of subsets $H_1,\ldots, H_n$ of a group $G$ we denote by $H_1\ldots H_n$ their Minkowski set-product,

### 2015-04-05 stability-conditions.tex
Typesetting, fixes and examples for Stability conditions section

--- 2015-04-03 stability-conditions.tex
@@
 Recall the definition of {\it stable rank} introduced by H.~Bass and L.~Vaserstein (see~\cite{Ba64, Va69}).
-\begin{dfn} Recall that a row $a=(a_1,\ldots, a_n)\in {}^n\!R$ is called {\it $I$-unimodular} if elements $a_1-1, a_2, \ldots, a_n$ are contained in $I$ while $a_1, a_2, \ldots, a_n$ generate $R$ as an ideal.\end{dfn}
-A column $b \in R^n$ will be called $I$-unimodular if its transpose $b^t$ is an $I$- unimodular row.
-We denote the set of all $I$-unimodular rows (resp.
-columns) by $\Umd(n,R,I)$ (resp.
-$\Ums(n,R,I)$).
-When $R=I$ we refer to $R$-unimodular rows and columns as simply unimodular.
+\begin{dfn}
+Recall that a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ is called {\it $I$-unimodular} if elements $a_1-1,a_2,\ldots,a_n$ are contained in $I$ while $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal.
+\end{dfn}
+A column $b \in R^n$ will be called $I$-unimodular if its transpose $b^t$ is an $I$-unimodular row. We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n,R,I)$ (resp. $\Ums(n,R,I)$).
+When $R=I$ we refer to $R$-unimodular rows and columns as unimodular.
 
-\begin{lemma} \label{lemma:relstrlemma} For any $I$-unimodular row $a=(a_1, \ldots, a_n)$ there exists $I$-unimodular column $b=(b_1,\ldots, b_n)^T$ such that $ab = \sum\limits_{i=1}^n a_i b_i = 1$.
+\begin{lemma}\label{lemma:relstrlemma}
+For any $I$-unimodular row $a=(a_1,\ldots,a_n)$ there exists $I$-unimodular column $b=(b_1,\ldots,b_n)^t$ such that $ab=\sum\limits_{i=1}^n a_i b_i=1$.
 \end{lemma}
 
-\begin {dfn} An $I$-unimodular row $a=(a_1,\ldots a_{n+1})$ is called {\it stable} if one can choose $b_1,\ldots, b_n\in R$ such that
-row $(a_1 + a_{n+1}b_1,\ldots, a_{n}+ a_{n+1}b_n)$ is also $I$-unimodular. if, moreover, elements $b_1,\ldots, b_n$ can be chosen from  $I$ then such $a$ will be called {\it $I$-stable}. \end{dfn}
+\begin {dfn} An $I$-unimodular row $a=(a_1,\ldots a_{n+1})$ is called {\it stable} if one can choose $b_1,\ldots,b_n\in R$ such that the row $(a_1+a_{n+1}b_1,\ldots,a_n+a_{n+1}b_n)$ is also $I$-unimodular.
+If, moreover, elements $b_1,\ldots,b_n$ can be chosen from  $I$ then such $a$ will be called {\it $I$-stable}.
+\end{dfn}
 
-We say that a pair $(R, I)$ satisfies stable range condition $\SR_n(R, I)$ if any $I$-unimodular row of length $n+1$ is stable.
-\begin{lemma}\label{lemma:relstrlemma2}\strut\begin{enumerate}\item The condition $\SR_n(R, I)$ implies $\SR_m(R,I)$ for any $m\geq n$.
-\item The condition $\SR_n(R, I)$ implies that any $I$-unimodular row of length $n+1$ is $I$-stable.\end{enumerate}\end{lemma}
+We say that a pair $(R,I)$ satisfies stable range condition $\SR_n(R,I)$ if any $I$-unimodular row of length $n+1$ is stable.
+\begin{lemma}\label{lemma:relstrlemma2}\strut
+\begin{enumerate}
+\item The condition $\SR_n(R,I)$ implies $\SR_m(R,I)$ for any $m\geqslant n$.
+\item The condition $\SR_n(R,I)$ implies that any $I$-unimodular row of length $n+1$ is $I$-stable.
+\end{enumerate}
+\end{lemma}
 
-By definition, the {\it relative stable rank} $\sr(R, I)$ of a pair $(R, I)$ is the smallest natural number $n$ such that condition $\SR_n(R, I)$ holds.
-If $\SR_n(R, I)$ is not satisfied for any $n>0$ we set $\sr(R, I)=\infty$.
+By definition, the {\it relative stable rank} $\sr(R,I)$ of a pair $(R,I)$ is the smallest natural number $n$ such that condition $\SR_n(R,I)$ holds.
+If no such $n$ exists, we set $\sr(R,I)=\infty$.
 
-The following proposition summarizes basic properties of stable ranks.
-\begin{prop} \label{prop:sr_properties} Let $R$ be arbitary commutative unital ring and let $I\trianglelefteq R$ be its ideal.
+The following proposition summarizes the basic properties of stable ranks.
+\begin{prop} \label{prop:sr_properties}
+Let $R$ be arbitrary commutative unital ring and let $I\trianglelefteq R$ be its ideal.
 \begin{itemize}
-  \item For any ideal $J\trianglelefteq R$, $J\subseteq I$ one has $$\sr(R, I)\leq\sr(R),\quad \sr(R/J, I/J)\leq \sr(R, I).$$
-  \item Stable rank of a direct product of rings is equal to the maximum of stable ranks of its factors: $$\sr(\prod\limits_{i=1}^n R_i) = \max\limits_{i=1}^n\left(\sr(R_i)\right).$$
-  \item Stable rank does not change after taking quotient modulo nil-radical: $\sr(R)=\sr(R/\Rad(R))$.
- \end{itemize}\end{prop} \begin{proof} See~\cite{Va71}. \end{proof}
+\item For any ideal $J\trianglelefteq R$, $J\subseteq I$ one has 
+\[ \sr(R,I)\leqslant\sr(R),\quad\sr(R/J,I/J)\leqslant\sr(R,I). \]
+\item Stable rank of a direct product of rings is equal to the maximum of stable ranks of its factors:
+\[ \sr\left(\prod\limits_{i=1}^n R_i\right)=\max\limits_{i=1}^n\left(\sr(R_i)\right). \]
+\item Stable rank does not change after taking quotient modulo the nil-radical: $\sr(R)=\sr(R/\Rad(R))$.
+\end{itemize}
+\end{prop}
+\begin{proof} See~\cite{Va71}. \end{proof}
 
-\begin{example} Since the stable rank of a field is one, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$. \end{example}
+\begin{example}
+Since the stable rank of a field is one, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$.
+\end{example}
+\begin{example}
+Other examples of rings of stable rank $1$ include boolean rings, the ring of algebraic integers, the ring of entire functions, the disk-algebra.
+\end{example}
+\begin{example}
+If $J$ is the Jacobson radical of $R$, one has $\sr(R,J)=1$.
+\end{example}
 
 \subsection{Absolute stable rank}
+For a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ denote by $\mathfrak{I}(u)$ the intersection of ideals of $R$ containing $a_1,\ldots,a_n$.
+It is easy to see that a row $a\in R^n$ is unimodular if and only if $\mathfrak{I}(u)=R$. 
+Clearly, for any $g\in\GL(n,R)$ one has $\mathfrak{I}(u\cdot g)=\mathfrak{I}(u)$.
 
-%TODO: $\asr(R,I)$
+A ring $R$ is said to satisfy condition $\ASR_{n}(R,I)$ if for any row $a$ such that $a_1-1,\ldots,a_{n+1}\in I$ one can find elements $b_1,\ldots b_n\in R$ such that
+\[ \mathfrak{I}(a_1+b_1a_{n+1},\ldots,a_n+b_na_{n+1})^t = \mathfrak{I}(a_1,\ldots,a_{n+1})^t. \]
+It is easy to see that $\ASR_m(R,I)$ implies $\ASR_n(R,I)$ for any $n\geqslant m$. 
+By definition, the {\it absolute relative stable rank} $\asr(R,I)$ is the smallest natural $n$ such that $\ASR_n(R, I)$ holds.
+Similarly, we set $\asr(R,I)=\infty$ if no such $n$ exists.
+When $I=R$ we call $\asr(R, R)$ simply the {\it absolute stable rank} of $R$ and denote it by $\asr(R)$.
+
+Let $R$ be a commutative ring. We denote by $\Max(R)$ its {\it maximum spectrum} i.e. the set of maximal ideals of $R$ equipped with Zariski topology.
+The following result gives an upper estimate for the absolute stable rank.~\cite[Theorem~2.3]{EO}, \cite[Theorem~3.7]{MKV}).
+\begin{thm}
+Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets $X_1\ldots, X_m$ such that the topological dimension of every subset $X_i$ does not exceed some number $d$.
+Then $\asr(A)\leqslant d+1$.
+\end{thm}
+Clearly one has
+\[ \sr(R,I)\leqslant\asr(R,I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]

### 2015-04-07 congrsubgr-boundgen.tex
BMS reference

@@
 \end{proof}
-Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type, defined by a finite set $S$ of places of some global field, and $I$ an ideal in $\mathcal{O}_S$.
+Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type, defined by a finite set $S$ of places of some global field $k$, and $I$ an ideal in $\mathcal{O}_S$.
+In case $k$ has a real embedding, then $\K_1(\Phi,\mathcal{O}_S,I)=1$ for any ideal $I\trianglelefteq\mathcal{O}_S$ and any root system $\Phi$ of rank $\geqslant2$ (see~\cite{BassMilnorSerre}).
 It is shown in \cite{TavgenThesis} that $E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$.
 From this one immediately gets the bounded generation for $\G(\Phi,R,I)$.
-
-Assume for simplicity that $\K_1(\Phi,\mathcal{O}_S,I)=1$.
 \begin{lemma}
-If $\rk\Phi\geqslant2$, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to $z_\alpha$.
+If $\rk\Phi\geqslant2$ and $k$ has a real embedding, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to $z_\alpha$.
 \end{lemma}

### 2015-04-11 bass-kolster.tex
Some references and small fixes
BK for B_l, preliminary incomplete version

@@
 \begin{itemize}
-\item $\Phi=\rA_\ell$: $\sr(R,I)\leqslant\ell+1$,
-\item $\Phi=\rB_\ell$: $\asr(R,I)\leqslant\ell$,
+\item $\Phi=\rA_\ell$: $\sr(R,I)\leqslant\ell$,
+\item $\Phi=\rB_\ell$: $\asr(R,I)\leqslant\ell-1$,
 \item $\Phi=\rC_\ell$: $\sr(R,I)\leqslant2\ell$,
-\item $\Phi=\rD_\ell$: $\asr(R,I)\leqslant\ell$.
+\item $\Phi=\rD_\ell$: $\asr(R,I)\leqslant\ell-1$.
 \end{itemize}
@@
 The same can be done with the first row, so in total we used $8\ell-3$ transformations.
+
+\textsc{Case $\Phi=\rB_\ell$:}
+Let $(1+r_1,r_2,\dots,r_\ell,r_0,r_{-\ell},\dots,r_{-1})^t\in\Ums(2\ell+1,R,I)$ be the first column of $g$.
+Find $c_1,\dots,c_\ell\in I$ (\textbf{can we?}) such that $(1+r_1+c_1r_0,\dots,r_\ell+c_\ell r_0,r_{-\ell},\dots,r_{-1})$ is unimodular.
+Apply $x_{\beta_k}(c_k)$ with $\beta_k=\alpha_k+\dots+\alpha_\ell$ for all $k=1,\dots,\ell$, and denote the resulting column by $(1+r_1',\dots,r'_{-1})^t$.
+Note that $r'_i$ is not necessary equal to $r_i+c_ir_0$.
+Denote also $\mathfrak{a}=r_{-\ell}R+\dots+r_{-1}R$, then one has $r'_{-\ell}R+\dots+r'_{-1}R=\mathfrak{a}$ and the ideal, generated by $1+r'_1,\dots,r'_\ell$ and $\mathfrak{a}$, is the whole $R$.
+
+Now $(1+r'_1,\dots,r'_\ell)^t$ is unimodular modulo $\mathfrak{a}$ and lies in the vector representation of $\G(\langle\alpha_1,\dots,\alpha_{\ell-1}\rangle)$ of type $\rA_{\ell-1}$.
+One can apply the case $\Phi=\rA_{\ell-1}$ to the pair $(R/\mathfrak{a},I/\mathfrak{a})$ and find $3\ell$ transformations that will transform the first half of the column into some $(1+s_1,s_2,\dots,s_\ell)^t$ which is congruent to $(1,0,\dots,0)^t$ modulo $\mathfrak{a}$.
+$(s_{-\ell},\dots,s_{-1})^t$ will denote these result of these transformations on $(r'_{-\ell},\dots,r_{-1})^t$.
+
+Since $\asr(R,I)\leqslant\ell$, there exist $c_{-\ell},\dots,c_{-2}$ such for $\mathfrak{b}=\langle s_{-\ell}+c_{-\ell}s_{-1},\dots,s_{-2}+c_{-2}s_{-1}\rangle$ one has $\mathfrak{I}(\mathfrak{b})=\mathfrak{I}(\mathfrak{a})$.
 \end{proof}
-%\subsection{$\rB_n$}
-%\subsection{$\rD_n$}

### 2015-04-11 dennis-vaserstein.tex

@@
 \begin{lemma}\label{Stein_reduction}
-Suppose that there exists a subset $\widetilde{L_r} \subseteq \E(\Delta_r, R, I)$ satisfying the following two conditions:
+Let $\Phi_l = \rA_l, \rD_l, \rE_6, \rE_7$. If $\Phi\neq \rE_7$ set $s:=1$ otherwise set $s:=7$. 
+Let $r$ be any other natural number not equal to $s$.
+Assume that there exists a subset $\widetilde{L_r} \subseteq \E(\Delta_r, R, I)$ satisfying the following two conditions:
 \begin{enumerate}[label=(\alph*)] 
@@
 $A$ is invariant with respect to left multiplication by elements of the following two families:
-\begin{itemize}
- \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
+\begin{itemize} \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
  \item $x_{\beta}(s)$, $s \in I$, $\beta \in \Phi$. \end{itemize}
-In fact, thanks to Lemma~\ref{lemma:conj_lemma} it suffices to prove this statement only for the second family.
-Moreover, we can additionally assume $\beta\in \Sigma_r^-$.
-%TODO: To be continued 
-\end{proof}
+Thanks to Lemma~\ref{lemma:conj_lemma} it suffices to check the required statement only for the second family of elements.
+Denote by $S$ the set of all roots $\alpha$ of $\Phi$ for which one has $X_{\alpha}(I)\cdot A_{rs}\subseteq A_{rs}$.
+It remains to prove that $S$ coincides with $\Phi$. We already know that $\Phi^+ \subseteq S$.
+
+Notice that the Weyl group $W(\Delta_s)$ acts transitively on $\Delta_s$, therefore in view of~\ref{rel:R3} the subgroup
+$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leq \EP_s$ acts transitively on the set of root subgroups $X_\alpha(I)$, $\alpha\in \Delta_s$.
+Since $-\alpha_r\in S$ this implies that that $\Delta_s\subseteq S$.
+
+Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$. Our assumptions on $\Phi$ guarantee that $m_s(\alpha)=1$, 
+hence every two roots $\alpha, \beta \in \Sigma^-_s$ have the same $s$-shape (i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
+By Lemma~\ref{lemma:abs} $W(\Delta_s)$ interchanges $\alpha$ and $\beta$. %if their length is equal.
+Since $\alpha_s \in S$ the argument similar to the one above implies $\Sigma^-_s\subseteq S$. This completes the proof of the lemma. \end{proof}

### 2015-04-11 paper.tex

@@
 \DeclareMathOperator{\sr}{sr}
+\DeclareMathOperator{\shape}{shape}
 \DeclareMathOperator{\Rad}{Rad}
@@
 
+\subsection{Chevalley groups}
+Our exposition of Chevalley groups is standard and follows (...).
+\textbf{TODO: Write more about Chevalley groups}
+
+Recall that elementary root unipotents $t_{\alpha}(\xi)$, $x\in R$, $\alpha\in\Phi$ satisfy the following set of relations called Steinberg relations.
+\begin{equation}\label{rel:add} t_\alpha(s) t_\alpha(t) = t_\alpha(s+t), \end{equation} 
+\begin{equation}\label{rel:CCF} [t_\alpha(s),  t_\beta(t)] = \left(\prod\limits t_{i\alpha + j\beta}(N_{\alpha,\beta, i, j}s^i t^j)\right),\quad \alpha\neq-\beta, N_{\alpha, \beta, i, j}\in\mathbb{Z}.\end{equation}
+The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
+The integers $N_{\alpha, \beta, i, j}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.
+
+For $\xi\in R^*$ set $w_\alpha(\xi) := x_\alpha(\xi) x_{-\alpha}(-\xi^{-1}) x_{\alpha}(\xi).$
+If $\rk(\Phi)\geq 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
+\begin{equation}\label{rel:R3} w_\alpha(\xi) t_{\beta}(s) w_\alpha(\xi)^{-1} =
+t_{\sigma\ssub{\alpha}\beta} (\eta_{\alpha, \beta}\xi^{-\langle\beta,\alpha \rangle} s),\ \xi,s\in R. \end{equation}
+
+Let $\Pi=\{\alpha_1, \ldots, \alpha_l\}$ be a basis of $\Phi$. Denote by $\Phi^+$ and $\Phi^-$ subsets of positive and negative roots with respect to $\Pi$.
+Denote by $m_i(\alpha)$ the coefficient of $\beta$ in the expansion of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum\limits_{i=1}^n m_i(\alpha) \alpha_i$.
+
+A root subset $S\subseteq \Phi$ is called {\it parabolic} (resp. {\it reductive}, resp. {\it special}) if $\Phi=S \cup -S$ (resp. $S = -S$, resp. $S \cap -S=\varnothing$).
+Any parabolic subset $S \subseteq \Phi$ can be decomposed into the disjoint union of its reductive and special part, i.e. 
+$S = \Sigma_S \sqcup \Delta_S$, where $\Sigma_S \cap (-\Sigma_S) = \varnothing$, $\Delta_S = -\Delta_S$.
+
+We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\alpha, \alpha)$.
+Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all reflections $\sigma_\alpha$ where $\sigma_\alpha(\beta)=\beta-\langle\alpha,\beta \rangle\cdot \alpha$.
+For $S\subseteq \Phi$ denote by $W(S)$ the subgroup of $W(\Phi)$ generated by $\sigma_\alpha$ for $\alpha\in S$.
+
+Let $J\subseteq \Pi$ be a subset of simple roots. 
+For a root $\beta = \sum d_i\alpha_i \in \Phi$ set $\shape(J, \beta):=\sum\limits_{i\in J}d_i \alpha_i$.
+Set $$\Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\},\quad \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha)\in\Phi^\pm \}.$$
+Clearly, $\Delta_J$ is a reductive subset of roots while $\Sigma^\pm_J$ are special subsets.
+
+\begin{lemma}\label{lemma:abs} Let $\alpha, \beta \in \Sigma^\pm_J$ be two roots having the same length such that $\shape(J,\alpha)=\shape(J,\beta)\neq 0$.
+Then $\alpha$ and $\beta$ are conjugate under the action of $W(\Delta_J)$. \end{lemma} \begin{proof} See~\cite[Lemma~1]{ABS}. \end{proof}
+
+\subsection{Relative elementary subgroup}
 The following theorem is the main result of \cite{S}.
@@
  \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$. \end{itemize} \end{thm}
-\begin{proof} See \cite[Theorem~3.4]{S}. \end{proof}
+\begin{proof} See~\cite[Theorem~3.4]{S}. \end{proof}
 

### 2015-04-12 stability-conditions.tex
Absolute stable rank rewritten + typesetting fixes

@@
 \subsection{Stable rank}
-Recall the definition of {\it stable rank} introduced by H.~Bass and L.~Vaserstein (see~\cite{Ba64, Va69}).
+Recall the definition of \emph{stable rank} introduced by H.~Bass and L.~Vaserstein (see~\cite{Ba64, Va69}).
 \begin{dfn}
-Recall that a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ is called {\it $I$-unimodular} if elements $a_1-1,a_2,\ldots,a_n$ are contained in $I$ while $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal.
+Recall that a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ is called \emph{$I$-unimodular} if elements $a_1-1,a_2,\ldots,a_n$ are contained in $I$ while $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal.
 \end{dfn}
@@
 When $R=I$ we refer to $R$-unimodular rows and columns as unimodular.
-
 \begin{lemma}\label{lemma:relstrlemma}
@@
 \end{lemma}
-
-\begin {dfn} An $I$-unimodular row $a=(a_1,\ldots a_{n+1})$ is called {\it stable} if one can choose $b_1,\ldots,b_n\in R$ such that the row $(a_1+a_{n+1}b_1,\ldots,a_n+a_{n+1}b_n)$ is also $I$-unimodular.
-If, moreover, elements $b_1,\ldots,b_n$ can be chosen from  $I$ then such $a$ will be called {\it $I$-stable}.
+\begin {dfn} An $I$-unimodular row $a=(a_1,\ldots a_{n+1})$ is called \emph{stable} if one can choose $b_1,\ldots,b_n\in R$ such that the row $(a_1+a_{n+1}b_1,\ldots,a_n+a_{n+1}b_n)$ is also $I$-unimodular.
+If, moreover, elements $b_1,\ldots,b_n$ can be chosen from  $I$ then such $a$ will be called \emph{$I$-stable}.
 \end{dfn}
-
 We say that a pair $(R,I)$ satisfies stable range condition $\SR_n(R,I)$ if any $I$-unimodular row of length $n+1$ is stable.
@@
 \end{lemma}
-
 By definition, the {\it relative stable rank} $\sr(R,I)$ of a pair $(R,I)$ is the smallest natural number $n$ such that condition $\SR_n(R,I)$ holds.
@@
 \begin{proof} See~\cite{Va71}. \end{proof}
-
 \begin{example}
@@
 \subsection{Absolute stable rank}
-For a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ denote by $\mathfrak{I}(u)$ the intersection of ideals of $R$ containing $a_1,\ldots,a_n$.
-It is easy to see that a row $a\in R^n$ is unimodular if and only if $\mathfrak{I}(u)=R$. 
-Clearly, for any $g\in\GL(n,R)$ one has $\mathfrak{I}(u\cdot g)=\mathfrak{I}(u)$.
+For a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ denote by $\mathfrak{J}(a)$ the intersection of all maximal ideals of $R$ containing $a_1,\ldots,a_n$.
+It is easy to see that a row $a\in R^n$ is unimodular if and only if $\mathfrak{J}(a)=R$. 
+Clearly, for any $g\in\GL(n,R)$ one has $\mathfrak{J}(a\cdot g)=\mathfrak{J}(a)$.
+\begin{dfn}
+We say that a pair $(R,I)$ satisfies $\ASR_n(R,I)$ if it satisfies $\SR(R,I)$ and, moreover, for any row $a=(a_1,\ldots,a_{n+1})\in I^n$ there exist $b_1,\ldots,b_n\in I$ such that
+\[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+b_1a_{n+1},\ldots,a_n+b_na_{n+1}).\]
+It is easy to see that $\ASR_m(R,I)$ implies $\ASR_n(R,I)$ for any $n\geqslant m$.
+The \emph{absolute relative stable rank} $\asr(R,I)$ is the smallest natural $n$ such that $\ASR_n(R, I)$ holds.
+Similarly, we set $\asr(R,I)=\infty$ if no such $n$ exists.
+When $I=R$ we call $\asr(R, R)$ simply the \emph{absolute stable rank} of $R$ and denote it by $\asr(R)$.
+\end{dfn}
+The following reformulation of the absolute stable rank condition was noted by A.~Bak.
+\begin{lemma}
+$R$ satisfies $\ASR_n(R)$ if and only if for any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Ums(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for any $t\in R$.
+\end{lemma}
+\begin{proof}
+Assume first that $\ASR_n(R)$ holds.
+Then for the row $(a_1,\ldots,a_n,d)$ there exist $c_1,\ldots,c_n$ such that $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a_1+c_1d,\ldots,a_n+c_nd)$.
+Therefore $a_1+c_1d,\ldots,a_n+c_nd$ together with $b$ generate the unit ideal.
+Of course, one could replace $b$ with $b+td$ from the very start.
 
-A ring $R$ is said to satisfy condition $\ASR_{n}(R,I)$ if for any row $a$ such that $a_1-1,\ldots,a_{n+1}\in I$ one can find elements $b_1,\ldots b_n\in R$ such that
-\[ \mathfrak{I}(a_1+b_1a_{n+1},\ldots,a_n+b_na_{n+1})^t = \mathfrak{I}(a_1,\ldots,a_{n+1})^t. \]
-It is easy to see that $\ASR_m(R,I)$ implies $\ASR_n(R,I)$ for any $n\geqslant m$. 
-By definition, the {\it absolute relative stable rank} $\asr(R,I)$ is the smallest natural $n$ such that $\ASR_n(R, I)$ holds.
-Similarly, we set $\asr(R,I)=\infty$ if no such $n$ exists.
-When $I=R$ we call $\asr(R, R)$ simply the {\it absolute stable rank} of $R$ and denote it by $\asr(R)$.
-
-Let $R$ be a commutative ring. We denote by $\Max(R)$ its {\it maximum spectrum} i.e. the set of maximal ideals of $R$ equipped with Zariski topology.
-The following result gives an upper estimate for the absolute stable rank.~\cite[Theorem~2.3]{EO}, \cite[Theorem~3.7]{MKV}).
+Now, given an arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!R$, consider a unimodular row $(a_1,\ldots,a_n,1,d)\in\Ums(n+2,R)$. There exist $c_1,\ldots,c_n$ such that
+\[(a'_1,\ldots,a'_n,1+td)=(a_1+c_1d,\ldots,a_n+c_nd,1+td)\]
+is unimodular for any $t\in R$.
+Suppose there exist a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that $a'_1,\ldots,a'_n\in\mathfrak{m}$ but some of $d,a_i\notin\mathfrak{m}$.
+Clearly, $d\notin\mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$).
+On the other hand, $1+td\notin\mathfrak{m}$, therefore in the residue field $R/\mathfrak{m}$ one has $1+\bar{t}\bar{d}\neq0$ for any $t$, but $\bar{d}\neq0$ and one can take $\bar{t}=-1/\bar{d}$.
+\end{proof}
+Let $R$ be a commutative ring. We denote by $\Max(R)$ its \emph{maximum spectrum} i.e. the set of maximal ideals of $R$ equipped with Zariski topology.
+The following result gives an upper estimate for the absolute stable rank (see~\cite[Theorem~2.3]{EO}, \cite[Theorem~3.7]{MKV}).
 \begin{thm}

### 2015-04-13 stability-conditions.tex
ASR small fixes

@@
 \begin{dfn}
-Recall that a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ is called \emph{$I$-unimodular} if elements $a_1-1,a_2,\ldots,a_n$ are contained in $I$ while $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal.
+A row $a=(a_1,\ldots,a_n)\in{}^n\!R$ is called \emph{$I$-unimodular} if it equals $(1,0,\ldots,0)$ modulo $I$ and $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal.
 \end{dfn}
@@
 \begin{dfn}
-We say that a pair $(R,I)$ satisfies $\ASR_n(R,I)$ if it satisfies $\SR(R,I)$ and, moreover, for any row $a=(a_1,\ldots,a_{n+1})\in I^n$ there exist $b_1,\ldots,b_n\in I$ such that
+We say that a pair $(R,I)$ satisfies $\ASR_n(R,I)$ if it satisfies $\SR_n(R,I)$ and, moreover, for any row $a=(a_1,\ldots,a_{n+1})\in I^n$ there exist $b_1,\ldots,b_n\in I$ such that
 \[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+b_1a_{n+1},\ldots,a_n+b_na_{n+1}).\]
@@
 
-Now, given an arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!R$, consider a unimodular row $(a_1,\ldots,a_n,1,d)\in\Ums(n+2,R)$. There exist $c_1,\ldots,c_n$ such that
+Now, given an arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!R$, consider a unimodular row
+\[ (a_1,\ldots,a_n,1,d)\in\Ums(n+2,R). \]
+There exist $c_1,\ldots,c_n$ such that
 \[(a'_1,\ldots,a'_n,1+td)=(a_1+c_1d,\ldots,a_n+c_nd,1+td)\]
@@
 On the other hand, $1+td\notin\mathfrak{m}$, therefore in the residue field $R/\mathfrak{m}$ one has $1+\bar{t}\bar{d}\neq0$ for any $t$, but $\bar{d}\neq0$ and one can take $\bar{t}=-1/\bar{d}$.
+Hence no such $\mathfrak{m}$ exists and $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a'_1,\ldots,a'_n)$.
 \end{proof}

### 2015-04-16 stability-conditions.tex
Minor fixes

@@
 
-The following proposition summarizes the basic properties of stable ranks.
+The following proposition summarizes basic properties of stable ranks.
 \begin{prop} \label{prop:sr_properties}
-Let $R$ be arbitrary commutative unital ring and let $I\trianglelefteq R$ be its ideal.
-\begin{itemize}
-\item For any ideal $J\trianglelefteq R$, $J\subseteq I$ one has 
-\[ \sr(R,I)\leqslant\sr(R),\quad\sr(R/J,I/J)\leqslant\sr(R,I). \]
-\item Stable rank of a direct product of rings is equal to the maximum of stable ranks of its factors:
-\[ \sr\left(\prod\limits_{i=1}^n R_i\right)=\max\limits_{i=1}^n\left(\sr(R_i)\right). \]
-\item Stable rank does not change after taking quotient modulo the nil-radical: $\sr(R)=\sr(R/\Rad(R))$.
-\end{itemize}
+Let $R$ be arbitrary commutative unital ring and let $I\trianglelefteq R$ be an ideal.
+\begin{enumerate}
+\item For any ideal $J\subseteq I$ one has $\sr(R,I)\leqslant\sr(R)$, $\sr(R/J,I/J)\leqslant\sr(R,I)$.
+\item One has $\sr\left(\prod\limits_{i=1}^n R_i\right)=\max\limits_{i=1}^n\left(\sr(R_i)\right).$
+\item Let $J$ denote the Jacobson radical of $R$, then one has $\sr(R)=\sr(R/J)$ and $\sr(R, J) = 1$.
+\end{enumerate}
 \end{prop}
-\begin{proof} See~\cite{Va71}. \end{proof}
+\begin{proof} See~\cite{Va71}. 
+\textbf{TODO: Add reference for the latter fact}.
+%TODO:
+\end{proof}
 \begin{example}
-Since the stable rank of a field is one, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$.
-\end{example}
-\begin{example}
-Other examples of rings of stable rank $1$ include boolean rings, the ring of algebraic integers, the ring of entire functions, the disk-algebra.
-\end{example}
-\begin{example}
-If $J$ is the Jacobson radical of $R$, one has $\sr(R,J)=1$.
+Since the stable rank of a field equals $1$, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$.
+Other examples of rings of stable rank $1$ are provided by boolean rings, the ring of algebraic integers, the ring of entire functions, the disk-algebra.
 \end{example}
@@
 \begin{dfn}
-We say that a pair $(R,I)$ satisfies $\ASR_n(R,I)$ if it satisfies $\SR_n(R,I)$ and, moreover, for any row $a=(a_1,\ldots,a_{n+1})\in I^n$ there exist $b_1,\ldots,b_n\in I$ such that
+We say that a pair $(R,I)$ satisfies $\ASR_n(R,I)$ if it satisfies $\SR_n(R,I)$ and, moreover, 
+for any row $a=(a_1,\ldots,a_{n+1})\in I^n$ there exist $b_1,\ldots,b_n\in I$ such that
 \[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+b_1a_{n+1},\ldots,a_n+b_na_{n+1}).\]
 It is easy to see that $\ASR_m(R,I)$ implies $\ASR_n(R,I)$ for any $n\geqslant m$. 
-The \emph{absolute relative stable rank} $\asr(R,I)$ is the smallest natural $n$ such that $\ASR_n(R, I)$ holds.
+By definition, the \emph{absolute relative stable rank} $\asr(R,I)$ is the smallest natural $n$ such that $\ASR_n(R, I)$ holds. 
 Similarly, we set $\asr(R,I)=\infty$ if no such $n$ exists.
@@
 The following reformulation of the absolute stable rank condition was noted by A.~Bak.
-\begin{lemma}
-$R$ satisfies $\ASR_n(R)$ if and only if for any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Ums(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for any $t\in R$.
+\begin{lemma} For a commutative ring $R$ the following statements are equivalent:
+\begin{enumerate}
+ \item\label{asr_Stein} $R$ satisfies $\ASR_n(R)$;
+ \item\label{asr_Bak} For any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Ums(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for all $t\in R$.
+\end{enumerate}
 \end{lemma}
@@
 
-Now, given an arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!R$, consider a unimodular row
-\[ (a_1,\ldots,a_n,1,d)\in\Ums(n+2,R). \]
-There exist $c_1,\ldots,c_n$ such that
-\[(a'_1,\ldots,a'_n,1+td)=(a_1+c_1d,\ldots,a_n+c_nd,1+td)\]
-is unimodular for any $t\in R$.
-Suppose there exist a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that $a'_1,\ldots,a'_n\in\mathfrak{m}$ but some of $d,a_i\notin\mathfrak{m}$.
+To show the converse take arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!R$ and consider the unimodular row $(a_1,\ldots,a_n,1,d)\in\Ums(n+2,R).$
+There exist $c_1,\ldots,c_n$ such that \[(a'_1,\ldots,a'_n,1+td)=(a_1+c_1d,\ldots,a_n+c_nd,1+td)\] is unimodular for all $t\in R$.
+Suppose that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that $a'_1,\ldots,a'_n\in\mathfrak{m}$ but at least one of the elements $d$, $a_i$ is not in $\mathfrak{m}$.
 Clearly, $d\notin\mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$).
-On the other hand, $1+td\notin\mathfrak{m}$, therefore in the residue field $R/\mathfrak{m}$ one has $1+\bar{t}\bar{d}\neq0$ for any $t$, but $\bar{d}\neq0$ and one can take $\bar{t}=-1/\bar{d}$.
-Hence no such $\mathfrak{m}$ exists and $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a'_1,\ldots,a'_n)$.
+On the other hand, $1+td\notin\mathfrak{m}$, hence the inequality $1+\bar{t}\bar{d}\neq0$ in the residue field $R/\mathfrak{m}$ may not hold for arbitrary $\bar{t}$ (take e.g. $\bar{t}=-1/\bar{d}$).
+This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a'_1,\ldots,a'_n)$.
 \end{proof}
+
 Let $R$ be a commutative ring. We denote by $\Max(R)$ its \emph{maximum spectrum} i.e. the set of maximal ideals of $R$ equipped with Zariski topology.

### 2015-04-16 bass-kolster.tex
Bass-Kolster for B_l finished

@@
 Let $(1+r_1,r_2,\dots,r_\ell,r_0,r_{-\ell},\dots,r_{-1})^t\in\Ums(2\ell+1,R,I)$ be the first column of $g$.
-Find $c_1,\dots,c_\ell\in I$ (\textbf{can we?}) such that $(1+r_1+c_1r_0,\dots,r_\ell+c_\ell r_0,r_{-\ell},\dots,r_{-1})$ is unimodular.
+Find $c_1,\dots,c_\ell\in I$ such that $(1+r_1+c_1r_0,\dots,r_\ell+c_\ell r_0,r_{-\ell},\dots,r_{-1})$ is unimodular.
 Apply $x_{\beta_k}(c_k)$ with $\beta_k=\alpha_k+\dots+\alpha_\ell$ for all $k=1,\dots,\ell$, and denote the resulting column by $(1+r_1',\dots,r'_{-1})^t$.
@@
 
-Since $\asr(R,I)\leqslant\ell$, there exist $c_{-\ell},\dots,c_{-2}$ such for $\mathfrak{b}=\langle s_{-\ell}+c_{-\ell}s_{-1},\dots,s_{-2}+c_{-2}s_{-1}\rangle$ one has $\mathfrak{I}(\mathfrak{b})=\mathfrak{I}(\mathfrak{a})$.
+Since $\asr(R,I)\leqslant\ell-1$, there exist $c_{-\ell},\dots,c_{-2}$ such for
+\[ \mathfrak{b}=\langle s_{-\ell}+c_{-\ell}s_{-1},\dots,s_{-2}+c_{-2}s_{-1}\rangle=\langle s'_{-\ell},\ldots,s'_{-2}\rangle \]
+one has $\mathfrak{I}(\mathfrak{b})=\mathfrak{I}(\mathfrak{a})$.
+So $(1+s_1,s'_{-\ell},\ldots,s'_{-2})^t\in\Ums(\ell,R,I)$ and can be shortened to some $(1+s''_1,s''_{-\ell},\ldots,s''_{-3})\in\Ums(\ell-1,R,I)$ with the help of $x_{\beta_i}$, $\beta_i=\alpha_2+\ldots+\alpha_i$, and $x_{\alpha_{\max}}$.
+Then one use $z_{\alpha_{\max}}$ to put $s''_1$ in position $-2$ and repeat endging of the previous cases.
 \end{proof}

### 2015-04-18 dennis-vaserstein.tex
Minor fixes
Rewriting Dennis-Vaserstein decomposition section

@@
 Throughout the present section we denote by $\EP_s(R, I)$ the subgroup $\E(\Delta_s, R, I) \cdot \U(\Sigma_s, I)$, $1 \leq s \leq n$.
+%TODO: Add Levi decomposition to preliminaries
+%TODO: Introduce notation for U(S, R)
 Set $\EP_s := \EP_s(R, R) = \E(\Delta_s, R) \cdot \U(\Sigma_s, R)$.
 
-\subsection{Main reduction.}
-Let $i$, $j$ be two distinct indices $1\leq i,j \leq n$. From Levi decomposition it follows that the following four subsets of $\E(\Phi, R, I)$ are equal to each other:
-\begin{multline}\nonumber \U(\Phi, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_i, R, I) \cdot \EP_j(R, I) = \U(\Sigma_i, I)\cdot \U(\Sigma^-_i, I) \cdot \E(\Delta_i, R, I) \cdot \EP_j(R, I) = \\
-= \EP_i(R, I) \cdot \E(\Delta_j, R, I) \cdot \U(\Sigma_j^-, I)\cdot \U(\Sigma_j, I) = \EP_i(R, I) \cdot \U(\Sigma^-_i\cap \Sigma^-_j, I) \cdot \EP_j(R, I). \end{multline}
-Denote by $A_{ij}$ any of the equal subsets from the previous formula. 
-Clearly, $A_{ij}$ is invariant with respect to conjugation by root subgroups $X_{\alpha\ssub{k}}$ for $1\leq k\leq n$ and $X_{-\alpha\ssub{k}}$ for $k\neq i,j$.
+Let $\Phi$ be an irreducible root system of rank $\ell$.
+Let $r$, $s$ be two distinct indices $1\leq r,s \leq \ell$.
+From Levi decomposition it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
+\begin{multline}\nonumber \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = 
+\U(\Sigma_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
+= \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s, I) = 
+\EP_i(R, I) \cdot \U(\Sigma^-_r\cap \Sigma^-_s, I) \cdot \EP_s(R, I). \end{multline}
+Denote by $A_{rs}$ any of the equal subsets from the previous formula.
+
+\begin{thm}\label{theorem:relative_dv}
+The relative elementary subgroup $\E(\Phi, R, I)$ coincides with $A_{rs}$ under the following assumptions on $(R, I)$.
+  \begin{center}
+    \begin{tabular}{| l | l | l | l | l |} \hline
+    № & $\Phi$ & $\{r,s\}$ & ring condition \\ \hline
+    1 & $\rA_\ell$, $\ell\geq 2$ & $\{1, \ell\}$ & $\sr(I) \leq \ell-1$ \\ \hline
+    2 & $\rD_\ell$, $\ell\geq 4$ & $\{1, \ell\}$ & $\sr(I) \leq \ell-2$ \\ \hline    
+    3 & $\rE_\ell$, $\ell=6,7,8$ & $\{2, \ell\}$ & $\sr(I) \leq \ell-3$ \\ \hline     
+    4 & $\rE_\ell$, $\ell=6,7,8$ & $\{1, \ell\}$ & $\asr(R, I)\leq \ell-2$ \\ \hline    
+    5 & $\rB_\ell$, $\ell\geq 3$ & $\{1, \ell\}$ & $\sr(I) \leq \ell-2$ \\ \hline
+    \end{tabular} \end{center} 
+\end{thm}
+The proof of Theorem~\ref{theorem:relative_dv} occupies the rest of this section.
+
+Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
+This action induces an action of $\E(\Phi, R)$ on the set $\mathfrak{S}$ of all subsets of $\E(\Phi, R, I)$.
+On the other hand, $\E(\Phi, R, I)$ acts on $\mathfrak{S}$ by left multiplication.
+Denote by $N_{rs}$ and $L_{rs}$) stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
+In other words $$N_{rs} = \{ g\in \E(\Phi, R) \mid g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \};\quad L_{rs}= \{ g\in \E(\Phi, R, I) \mid g \cdot A_{rs} \subseteq A_{rs} \}.$$
+
+It is easy to see that $N_{rs}$ normalizes $L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+$$h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq A_{rs}^g \subseteq A_{rs}.$$
 
@@
 \item $\U(\Phi^\pm, I) = X_{\pm\alpha\ssub{i}}(I)\cdot \U(\Phi^\pm\setminus\{\pm\alpha\ssub{i}\}, I) = \U(\Phi^\pm\setminus\{\pm\alpha\ssub{i}\}, I)\cdot X_{\pm\alpha\ssub{i}}(I).$
-\item For any $\xi\in R$ one has $x_{\mp\alpha\ssub{i}}(\xi)\cdot \U(\Phi^\pm\setminus\{\alpha_i\}, I)\cdot x_{\mp\alpha\ssub{i}}(\xi)^{-1} \subseteq \U(\Phi^\pm, I).$
-\item $\U(\Sigma_i, I)\cdot \U(\Sigma^-_i, I) \subseteq \U(\Sigma_i\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{i}}(I) \cdot X_{-\alpha\ssub{i}}(I)$.
+\item For any $\xi\in R$ one has $\U(\Phi^\pm\setminus\{\alpha_i\}, I)^{x_{\mp\alpha\ssub{i}}(\xi)^{-1}} \subseteq \U(\Phi^\pm, I).$
+\item $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{i}}(I) \cdot X_{-\alpha\ssub{i}}(I)$.
 \end{enumerate} \end{lemma}
 \begin{proof}
- The first two statements follow from Chevalley commutator formula. The last statement is a consequence of the first two.
+ The first two statements easily follow from Chevalley commutator formula while the third one is a formal consequence of the first two.
 \end{proof}
 
-\begin{lemma}\label{lemma:conj_lemma} Let $G$ be a group, $H\leq G$ be a subgroup and $A, B\subseteq G$ be two subsets.
-Assume that $A$ is invariant with respect to left multiplication by elements of $B$ and conjugation by elements of the subgroup $H$.
-Then $A$ is invariant with respect to left multiplication by elements of the set $B^H = \{b^h \vert b\in B, h\in H\}$. \end{lemma}
-\begin{proof} $b^h \cdot A \subseteq h^{-1}\cdot b \cdot h \cdot A \subseteq h^{-1} \cdot b \cdot A \cdot h \subseteq h^{-1} \cdot A \cdot h \subseteq A. \qedhere$ \end{proof}
-
+The following lemma is a relative version of the main reduction used by M.~Stein in~\cite{St78} for the proof of Dennis--Vaserstein decomposition.
 \begin{lemma}\label{Stein_reduction}
-Let $\Phi_l = \rA_l, \rD_l, \rE_6, \rE_7$. If $\Phi\neq \rE_7$ set $s:=1$ otherwise set $s:=7$. 
-Let $r$ be any other natural number not equal to $s$.
-Assume that there exists a subset $\widetilde{L_r} \subseteq \E(\Delta_r, R, I)$ satisfying the following two conditions:
+Assume that there exists a subset $\widetilde{L_r} \subseteq \E(\Delta_r, R, I)$ with the following properties:
 \begin{enumerate}[label=(\alph*)] 
  \item\label{stein_cond1} One has $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} = \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I).$
- \item\label{stein_cond2} There is an inclusion $X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \EP_s(R, I).$
+ \item\label{stein_cond2} One has $X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \EP_s(R, I).$
 \end{enumerate}
-Then $A_{rs} = \E(\Phi, R, I)$. \end{lemma}
+Then $X_{-\alpha_r}(I) \subseteq L_{rs}$ and $\EP_s \subseteq N_{rs}.$
+\end{lemma}
 \begin{proof} Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(\Phi, R, I).$
 From condition~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A$.
+Observe that from Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} it follows that
+\begin{multline}\nonumber 
+A \subseteq \U(\Phi^+\setminus \{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\ 
+\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\
+\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I)  \cdot \EP_s(R, I) \subseteq \\
+\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I). \end{multline}
+In order to prove the first statement apply Lemma~\ref{lemma:dv_unipotent} once again:
+\begin{equation}\nonumber A^{X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq A. \end{equation}
+\begin{equation}\nonumber X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) = A. \end{equation}
+Notice that $X_{\alpha\ssub{k}}$ for $1\leq k\leq \ell$ and $X_{-\alpha\ssub{k}}$ for $k\neq r,s$ fix $A_{rs}$.
+Since $\EP_s$ is generated by $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$ we get the second part of the statement.
+\end{proof}
 
-The first step of the proof is to show that $A_{rs}$ is invariant with respect to conjugation by the root subgroup $X_{-\alpha\ssub{r}}$ 
-and left multiplication by elements of $X_{-\alpha\ssub{r}}(I)$. To prove this, observe first that from Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} it follows that
-\begin{multline}\nonumber 
-A \subseteq \U(\Sigma_r\setminus \{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\ 
-\subseteq \U(\Sigma_r\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\
-\subseteq \U(\Sigma_r\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I)  \cdot \EP_s(R, I) \subseteq \\
-\subseteq \U(\Sigma_r\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I). \end{multline}
-Now it remains to apply Lemma~\ref{lemma:dv_unipotent} once again:
-\begin{equation}\nonumber A^{X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq A. \end{equation}
-\begin{equation}\nonumber X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq A. \end{equation}
+%Let $\Phi_l = \rA_l, \rD_l, \rE_6, \rE_7$. If $\Phi\neq \rE_7$ set $s:=1$ otherwise set $s:=7$. 
+%Let $r$ be any other natural number not equal to $s$.
+%The first step of the proof is to show that $A_{rs}$ is invariant with respect to conjugation by the root subgroup $X_{-\alpha\ssub{r}}$ 
+%and left multiplication by elements of $X_{-\alpha\ssub{r}}(I)$. To prove this,
 
-Notice that the subgroup $\EP_s$ is generated by root subgroups $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$,
-therefore in fact we have just proved that $A$ is invariant with respect to conjugation by all elements of $\EP_s$.
-
-Now we are ready to prove the needed equality. By virtue of Theorem~\ref{theorem:Stepanov} it suffices to show that
-$A$ is invariant with respect to left multiplication by elements of the following two families:
+Now we are ready to prove the needed equality.
+By virtue of Theorem~\ref{theorem:Stepanov} it suffices to show that $A$ is invariant with respect to left multiplication by elements of the following two families:
 \begin{itemize} \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
@@
 By Lemma~\ref{lemma:abs} $W(\Delta_s)$ interchanges $\alpha$ and $\beta$. %if their length is equal.
-Since $\alpha_s \in S$ the argument similar to the one above implies $\Sigma^-_s\subseteq S$. This completes the proof of the lemma. \end{proof}
+Since $\alpha_s \in S$ the argument similar to the one above implies $\Sigma^-_s\subseteq S$. This completes the proof of the lemma.

### 2015-04-18 paper.tex
Rewriting Dennis-Vaserstein decomposition section

@@
 \documentclass[12pt]{amsart}
-\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac}
+\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac, amsthm, amsfonts, amstext}
 \usepackage{hyperref}
@@
 
-\section{Relative Dennis-Vaserstein decomposition}\label{sec:dennis-vaserstein}
+\section{Relative Dennis-Vaserstein decompositions}\label{sec:dennis-vaserstein}
 \input{dennis-vaserstein}

### 2015-04-18 dennis-vaserstein.tex
More fixes

@@
 
-Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
+\subsection{Main reduction.} Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
 This action induces an action of $\E(\Phi, R)$ on the set $\mathfrak{S}$ of all subsets of $\E(\Phi, R, I)$.
 On the other hand, $\E(\Phi, R, I)$ acts on $\mathfrak{S}$ by left multiplication.
-Denote by $N_{rs}$ and $L_{rs}$) stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
+Denote by $N_{rs}$ and $L_{rs}$ stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
 In other words $$N_{rs} = \{ g\in \E(\Phi, R) \mid g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \};\quad L_{rs}= \{ g\in \E(\Phi, R, I) \mid g \cdot A_{rs} \subseteq A_{rs} \}.$$
@@
 
-The following lemma is a relative version of the main reduction used by M.~Stein in~\cite{St78} for the proof of Dennis--Vaserstein decomposition.
+The following lemma is a relative version of the main reduction used by M.~Stein in~\cite{St78} for the proof of the absolute Dennis--Vaserstein decomposition.
 \begin{lemma}\label{Stein_reduction}
@@
 \begin{enumerate}[label=(\alph*)] 
- \item\label{stein_cond1} One has $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} = \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I).$
+ \item\label{stein_cond1} One has $\U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r}.$
  \item\label{stein_cond2} One has $X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \EP_s(R, I).$
@@
 \subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I). \end{multline}
-In order to prove the first statement apply Lemma~\ref{lemma:dv_unipotent} once again:
+Applying Lemma~\ref{lemma:dv_unipotent} we get that:
 \begin{equation}\nonumber A^{X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq A. \end{equation}
 \begin{equation}\nonumber X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) = A. \end{equation}
-Notice that $X_{\alpha\ssub{k}}$ for $1\leq k\leq \ell$ and $X_{-\alpha\ssub{k}}$ for $k\neq r,s$ fix $A_{rs}$.
-Since $\EP_s$ is generated by $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$ we get the second part of the statement.
+To prove the second part of the statement observe first that $\EP_s$ is generated by $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$
+(this follows e.g. from~\cite[Lemma~2.1]{S}).
+We have just shown that $X_{-\alpha_r}\subseteq N_{rs}$ whereas inclusions $X_{\alpha\ssub{k}} \subseteq N_{rs}$ for $\ 1\leq k\leq \ell$ and $X_{-\alpha\ssub{k}} \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
 \end{proof}
+
+\subsection{The use of stability conditions.}
 

### 2015-04-18 paper.tex
Added some text about representations

@@
 
+In this paper we work with irreducible representations of Chevalley groups corresponding to the highest weight
+$\varpi_1$ (in the case of a classical $\Phi_l$) or $\varpi_l$ (in the case $\Phi_l=\rE_l$). 
+The former are the natural vector representations of classical groups acting on free modules $V=R^n$ of dimension 
+$n=l+1, 2l+1, 2l,2l$ for $\Phi=\rA_l,\rB_l,\rC_l,\rD_l$.
+The latter representations have dimension $n=27, 56, 248$ for $l=6,7,8$.
+
+For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda(\pi)$ the set of weights of $\pi$.
+It will be convenient to use standard numbering for elements of $\Lambda(\pi)$ in the case when $\Phi$ is classical and $\pi$ is a vector representation (cp.~\cite[§1B]{St78}):
+$$\begin{array}{cll}
+  1,2,\ldots, l+1 & \text{in the case} & \Phi =\rA_l, \\
+  1,2,\ldots l, 0, -l,\ldots, -2, -1 & \text{in the case} & \Phi =\rB_l, \\
+  1,2,\ldots l, -l,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_l, \rD_l. \\
+\end{array}$$
+In particular, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ and so on.
+
+\subsection{Elementary subgroup}
+
 Recall that elementary root unipotents $t_{\alpha}(\xi)$, $x\in R$, $\alpha\in\Phi$ satisfy the following set of relations called Steinberg relations.
@@
 
-\subsection{Relative elementary subgroup}
 The following theorem is the main result of \cite{S}.
@@
 
-\section{Bass---Kolster decomposition}\label{sec:bass-kolster}
+\section{Relative Bass---Kolster decomposition}\label{sec:bass-kolster}
 \input{bass-kolster}
+
+\section{Relative Dennis-Vaserstein decompositions}\label{sec:dennis-vaserstein}
+\input{dennis-vaserstein}
 
@@
 
-\section{Relative Dennis-Vaserstein decompositions}\label{sec:dennis-vaserstein}
-\input{dennis-vaserstein}
-
 \printbibliography

### 2015-04-18 stability-conditions.tex
Added some text about representations

@@
 Suppose that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that $a'_1,\ldots,a'_n\in\mathfrak{m}$ but at least one of the elements $d$, $a_i$ is not in $\mathfrak{m}$.
-Clearly, $d\notin\mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$).
-On the other hand, $1+td\notin\mathfrak{m}$, hence the inequality $1+\bar{t}\bar{d}\neq0$ in the residue field $R/\mathfrak{m}$ may not hold for arbitrary $\bar{t}$ (take e.g. $\bar{t}=-1/\bar{d}$).
+Clearly, $d\notin\mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$ contrary to the assumption).
+On the other hand, $1+td\notin\mathfrak{m}$,
+hence the inequality $1+\bar{t}\bar{d}\neq0$ in the residue field $R/\mathfrak{m}$ may not hold for arbitrary $\bar{t}$ 
+(take e.g. $\bar{t}=-1/\bar{d}$).
 This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a'_1,\ldots,a'_n)$.
@@
 \[ \sr(R,I)\leqslant\asr(R,I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
+
+The following lemma illustrates a typical application of stability conditions.
+\begin{lemma} \label{lemma:uraction} 
+Let $\Phi=\rA_\ell, \rD_\ell$. Denote by $\pi$ the vector representation of $\G(\Phi, R)$ on $V=R^n$.
+Assume that one of the following conditions holds:
+\begin{itemize}
+ \item $\Phi=\rA_\ell$, $\Gamma=\{ k+1, \ldots, \ell+1\} \subset \Lambda(\pi)$ and $\sr(I)\leq k\leq \ell$;
+ \item $\Phi=\rD_\ell$, $\Gamma=\{-l,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(R, I)\leq \ell-1$. 
+\end{itemize}
+Then for any unimodular column $v\in \Ums(n, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yx \cdot v)_\lambda = 0$ for $\lambda\in \Gamma$.
+\end{lemma}
+
+%Let $\sr(I)\leq l-1$, then for any unimodular column $v\in R^l=V$ there exist
+%matrices $x=\left(\begin{smallmatrix} e_{l-1}& * \\ 0 & 1 \end{smallmatrix}\right)$, $y=\left(\begin{smallmatrix} e_{l-1}& 0 \\ *& 1 \end{smallmatrix}\right)$
+%such that the $l$-th cooordinate of the vector $yx\cdot v$ is zero.\end{lemma}
+
+%Denote by $p$ the matrix which has $1$'s along its secondary diagonal and zeroes elsewhere. Call a matrix $a\in\M(l, R)$ {\it antipersymmetric} if $pa^tp = a$.
+%\begin{lemma}\label{LambdaS_lemma} Assume that $\asr(R)\leq l-1$, then for any columns $u^+, u^-\in R^l$ such that $(u^+, u^-)^t\in R^{2l}$ is unimodular there exists
+%an antipersymmetric matrix $a\in\M(l, R)$ such that $u^+ + au^- \in R^l$ is unimodular. \end{lemma}
+%\begin{proof} The statement of the lemma is a special case of \cite[Th.~1.2]{BPT} applied to $R$ viewed as a form ring with trivial involution and zero form parameter. \end{proof}
+
+%Denote by $H$ the hyperbolic embedding $H:\GL(l, R)\rightarrow\mathrm{O}(2l, R)$ of a general linear group into the even-dimensional orthogonal group,
+%i.\,e. the map which sends $g$ to $\left(\begin{smallmatrix} g & 0 \\ 0 & p(g^{t})^{-1}p \end{smallmatrix}\right)$.
+%\begin{lemma}\label{asrLemma} Assume that $\asr(R)\leq l-1$. Then for any unimodular column $v\in R^{2l}=V$ there exist orthogonal matrices 
+%$x=\left(\begin{smallmatrix} e_l & * \\ 0 & e_l \end{smallmatrix}\right)$, $y=\left(\begin{smallmatrix} e_l & 0 \\ * & e_l \end{smallmatrix}\right)$
+%such that $(yx\cdot v)_k=0$ for $k=-l,\ldots, -1.$ \end{lemma}
+%\begin{proof}
+% Applying Lemma~\ref{LambdaS_lemma} we obtain $x=\left(\begin{smallmatrix} e_l & a \\ 0 & e_l \end{smallmatrix}\right)$ such
+% that the first $l$ coor\-dinates of $x\cdot v$ form a unimodular column of height $l$.
+
+% The group $\E(l, R)$ acts transitively on the set of unimodular columns of height $l$, therefore
+% we can choose an appropriate $g\in\E(l, R)$ such that $$H(g)x\cdot v= (1,0,\ldots, 0,*,\ldots *)^t,$$
+% where the number of stars equals $l$.
+% Choose $y'=\left(\begin{smallmatrix} e_l & 0 \\ * & e_l \end{smallmatrix}\right)$ such that $y'H(g)x\cdot v = e_1 = (1,0,\ldots, 0)^t$.
+% Clearly $y=y'^{H(g)}$ is an orthogonal matrix of the required form and $$yx\cdot v = y'^{H(g)} x\cdot v = H(g)^{-1} e_1 = (*,\ldots, *,0,\ldots, 0)^t.$$
+% \end{proof}

### 2015-04-19 dennis-vaserstein.tex
Minor fixes

@@
 Let $r$, $s$ be two distinct indices $1\leq r,s \leq \ell$.
-From Levi decomposition it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
+From Levi decomposition it follows that
 \begin{multline}\nonumber \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = 
@@
 = \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s, I) = 
-\EP_i(R, I) \cdot \U(\Sigma^-_r\cap \Sigma^-_s, I) \cdot \EP_s(R, I). \end{multline}
+\EP_r(R, I) \cdot \U(\Sigma^-_r\cap \Sigma^-_s, I) \cdot \EP_s(R, I). \end{multline}
 Denote by $A_{rs}$ any of the equal subsets from the previous formula.
@@
     \begin{tabular}{| l | l | l | l | l |} \hline
-    № & $\Phi$ & $\{r,s\}$ & ring condition \\ \hline
-    1 & $\rA_\ell$, $\ell\geq 2$ & $\{1, \ell\}$ & $\sr(I) \leq \ell-1$ \\ \hline
-    2 & $\rD_\ell$, $\ell\geq 4$ & $\{1, \ell\}$ & $\sr(I) \leq \ell-2$ \\ \hline    
-    3 & $\rE_\ell$, $\ell=6,7,8$ & $\{2, \ell\}$ & $\sr(I) \leq \ell-3$ \\ \hline     
-    4 & $\rE_\ell$, $\ell=6,7,8$ & $\{1, \ell\}$ & $\asr(R, I)\leq \ell-2$ \\ \hline    
-    5 & $\rB_\ell$, $\ell\geq 3$ & $\{1, \ell\}$ & $\sr(I) \leq \ell-2$ \\ \hline
+    № & $\Phi$ & $(r,s)$ & ring condition \\ \hline
+    1 & $\rA_\ell$, $\ell\geq 2$ & $(1, \ell)$ & $\sr(I) \leq \ell-1$ \\ \hline
+    2 & $\rD_\ell$, $\ell\geq 4$ & $(1, \ell)$ & $\sr(I) \leq \ell-2$ \\ \hline    
+    3 & $\rE_\ell$, $\ell=6,7,8$ & $(2, \ell)$ & $\sr(I) \leq \ell-3$ \\ \hline     
+    4 & $\rE_\ell$, $\ell=6,7,8$ & $(1, \ell)$ & $\asr(R, I)\leq \ell-2$ \\ \hline    
+    5 & $\rB_\ell$, $\ell\geq 3$ & $(1, \ell)$ & $\sr(I) \leq \ell-2$ \\ \hline
     \end{tabular} \end{center} 
@@
 \begin{equation}\nonumber X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) = A. \end{equation}
-To prove the second part of the statement observe first that $\EP_s$ is generated by $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$
-(this follows e.g. from~\cite[Lemma~2.1]{S}).
-We have just shown that $X_{-\alpha_r}\subseteq N_{rs}$ whereas inclusions $X_{\alpha\ssub{k}} \subseteq N_{rs}$ for $\ 1\leq k\leq \ell$ and $X_{-\alpha\ssub{k}} \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
+To prove the second part of the statement observe first that $\EP_s$ is generated by $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$.
+%TODO: Find proper reference for this fact
+We have just shown that $X_{-\alpha_r}\subseteq N_{rs}$.
+On the other hand, inclusions $X_{\alpha\ssub{k}} \subseteq N_{rs}$ for $\ 1\leq k\leq \ell$ and $X_{-\alpha\ssub{k}} \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
 \end{proof}
-
-\subsection{The use of stability conditions.}
-
-%Let $\Phi_l = \rA_l, \rD_l, \rE_6, \rE_7$. If $\Phi\neq \rE_7$ set $s:=1$ otherwise set $s:=7$. 
-%Let $r$ be any other natural number not equal to $s$.
-%The first step of the proof is to show that $A_{rs}$ is invariant with respect to conjugation by the root subgroup $X_{-\alpha\ssub{r}}$ 
-%and left multiplication by elements of $X_{-\alpha\ssub{r}}(I)$. To prove this,
 

### 2015-04-19 stability-conditions.tex
Minor fixes

--- 2015-04-16 stability-conditions.tex
@@
 \[ \sr(R,I)\leqslant\asr(R,I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
+
+The following lemma illustrates a typical application of stability conditions.
+\begin{lemma} \label{lemma:uraction} 
+Let $\Phi=\rA_\ell, \rD_\ell$. Denote by $\pi$ standard vector representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1,2\ell$.
+Assume that one of the following conditions holds:
+\begin{itemize}
+ \item $\Phi=\rA_\ell$, $\Gamma=\{ k+1, \ldots, \ell+1\} \subset \Lambda(\pi)$ and $\sr(I)\leq k\leq \ell$;
+ \item $\Phi=\rD_\ell$, $\Gamma=\{-l,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(R, I)\leq \ell-1$. 
+\end{itemize}
+Then for any $I$-unimodular column $v\in \Ums(n, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yx \cdot v)_\lambda = 0$ for $\lambda\in \Gamma$.
+\end{lemma}
+\textbf{TODO: Write proof of this lemma}
+%TODO:

### 2015-04-21 paper.tex
Added lemma on relative asr condition

@@
 For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda(\pi)$ the set of weights of $\pi$.
-It will be convenient to use standard numbering for elements of $\Lambda(\pi)$ in the case when $\Phi$ is classical and $\pi$ is a vector representation (cp.~\cite[§1B]{St78}):
+It will be convenient to use standard numbering for weights of representation $\pi$ in the case when $\Phi$ is classical and $\pi$ is a vector representation (cp.~\cite[§1B]{St78}):
 $$\begin{array}{cll}
@@
 \subsection{Elementary subgroup}
-
 Recall that elementary root unipotents $t_{\alpha}(\xi)$, $x\in R$, $\alpha\in\Phi$ satisfy the following set of relations called Steinberg relations.
@@
 t_{\sigma\ssub{\alpha}\beta} (\eta_{\alpha, \beta}\xi^{-\langle\beta,\alpha \rangle} s),\ \xi,s\in R. \end{equation}
+where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S~13]{VP} for more details on $\eta_{\alpha, \beta}$).
 
+\begin{rem} Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
+In this situation it will be convenient for us to write $t_{\lambda_1,\lambda_2}(\xi)$ instead of $t_{\lambda_1-\lambda_2}(\xi)$.
+In particular, for $\Phi=\rA_\ell$ we have $t_{1,2}(\xi)=t_{2-1}(\xi)=t_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = t_{\alpha_1}(\xi)$. \end{rem}
+
+\subsection{Root systems}
 Let $\Pi=\{\alpha_1, \ldots, \alpha_l\}$ be a basis of $\Phi$. Denote by $\Phi^+$ and $\Phi^-$ subsets of positive and negative roots with respect to $\Pi$.

### 2015-04-21 stability-conditions.tex
Added lemma on relative asr condition

@@
 \begin{enumerate}
- \item\label{asr_Stein} $R$ satisfies $\ASR_n(R)$;
+ \item\label{asr_Stein} $R$ satisfies $\ASR_n(R, R)$;
  \item\label{asr_Bak} For any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Ums(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for all $t\in R$.
@@
 
-The following lemma illustrates a typical application of stability conditions.
+The next lemma illustrates a typical application of the absolute relative stability condition.
+Let $v\in R^{2\ell}$ be a vector of the standard vector representation of $\G(\rD_\ell, R)$.
+It will be convenient for us to denote by $v^+$ and $v^-$ the upper and lower halves of $v$ i.e. $v^+=(v_1,\ldots, v_\ell)^t$, $v^-=(v_{-\ell},\ldots, v_{-1})^t$.
+\begin{lemma}\label{lemma:asrUnip}
+ Let $\Phi=\rD_\ell$ and assume that $\asr(R, I)\leq \ell -1$. Then for any $I$-unimodular column $v=(v^+, v^-)^t\in\Ums(2\ell, R, I)$
+ there exist $g\in\U(\Sigma^+_\ell, I)$ such that $(v\cdot g)^+ \in \Ums(\ell, R, I)$.
+\end{lemma}
+\begin{proof} Denote by $J$ the ideal of $R$ spanned by entries of $v^-$. Clearly, $J \leq I$.
+By Proposition~\ref{prop:sr_properties} $\sr(I/J) \leq \ell-1$ and therefore
+the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, R/J, I/J)$. 
+This implies existence of $h\in \E(\Delta_\ell, R, I)$ such that for $v' = v\cdot h$ one has $(v')^+ \equiv e_1$ modulo $J$.
+
+By hypothesis, we can find $c_2,\ldots, c_\ell\in I$ such that for $v''=v'\cdot \prod\limits_{i=2}^{\ell}t_{-1, -i}(c_i)$ one has
+$\mathfrak{J}(v''_{-\ell},\ldots, v''_{-2}) = \mathfrak{J}(v'^-)$. Clearly, $v''_1$ is still congruent to $1$ modulo $J$, therefore 
+$(v''_1, v''_{-\ell},\ldots, v''_{-1})$ is $I$-unimodular. Now, applying condition $\sr(I) \leq \ell-1$ once again we find
+$d_1,d_3,\ldots, d_{\ell}\in I$ such that for $v'''=v''\cdot t_{-2,1}(d_1) \cdot \prod\limits_{i=3}^{\ell} t_{-2,-i}(d_i)$
+the entries $(v'''_1, v'''_{-\ell},\ldots, v'''_{-3})$ form a $I$-unimodular column.
+
+We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v'''_1+\sum\limits_{i=3}^\ell f_i v'''_{-i} = 1$.
+Set $\xi = v'''_1-v'''_2-1 \in I$, $v^4=v'''\cdot t_{1,2}(\xi f_1) \cdot \prod\limits_{i=3}^\ell t_{-i,2}(\xi i_k)$.
+Clearly $v^4_1 = v'''_1$ and $v^4_2 = v'''_1-1$, therefore $v^{4+}$ is $I$-unimodular.
+Summarizing the above, we have found $g\in \EP_\ell(R, I)$ such that $v^4=v\cdot g$
+and assertion of the lemma immediately follows from Levi decomposition. \end{proof}
+
 \begin{lemma} \label{lemma:uraction} 

### 2015-04-21 stability-conditions.tex
Rewritten stable ranks section

@@
-As we will be mainly concerned with applications to stability of $K_1$ of Chevalley groups, our treatment of stability conditions is restricted to the case of commutative $R$. 
-We refer the reader to~\cite{Ba64, Va69, Va71} for a more general exposition.
+As we will be mainly concerned with applications to stability of $K_1$ of Chevalley groups, our treatment of stability conditions is restricted to the case of commutative $R$
+notwithstanding with the fact that the majority of constructions related to stable range conditions can be defined in a more general non-commutative setting (see e.g.~\cite{Ba64, Va69, Va71}).
 
@@
 Recall the definition of \emph{stable rank} introduced by H.~Bass and L.~Vaserstein (see~\cite{Ba64, Va69}).
-\begin{dfn}
-A row $a=(a_1,\ldots,a_n)\in{}^n\!R$ is called \emph{$I$-unimodular} if it equals $(1,0,\ldots,0)$ modulo $I$ and $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal.
-\end{dfn}
-A column $b \in R^n$ will be called $I$-unimodular if its transpose $b^t$ is an $I$-unimodular row. We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n,R,I)$ (resp. $\Ums(n,R,I)$).
-When $R=I$ we refer to $R$-unimodular rows and columns as unimodular.
-\begin{lemma}\label{lemma:relstrlemma}
-For any $I$-unimodular row $a=(a_1,\ldots,a_n)$ there exists $I$-unimodular column $b=(b_1,\ldots,b_n)^t$ such that $ab=\sum\limits_{i=1}^n a_i b_i=1$.
-\end{lemma}
-\begin {dfn} An $I$-unimodular row $a=(a_1,\ldots a_{n+1})$ is called \emph{stable} if one can choose $b_1,\ldots,b_n\in R$ such that the row $(a_1+a_{n+1}b_1,\ldots,a_n+a_{n+1}b_n)$ is also $I$-unimodular.
-If, moreover, elements $b_1,\ldots,b_n$ can be chosen from  $I$ then such $a$ will be called \emph{$I$-stable}.
-\end{dfn}
-We say that a pair $(R,I)$ satisfies stable range condition $\SR_n(R,I)$ if any $I$-unimodular row of length $n+1$ is stable.
-\begin{lemma}\label{lemma:relstrlemma2}\strut
-\begin{enumerate}
-\item The condition $\SR_n(R,I)$ implies $\SR_m(R,I)$ for any $m\geqslant n$.
-\item The condition $\SR_n(R,I)$ implies that any $I$-unimodular row of length $n+1$ is $I$-stable.
-\end{enumerate}
-\end{lemma}
-By definition, the {\it relative stable rank} $\sr(R,I)$ of a pair $(R,I)$ is the smallest natural number $n$ such that condition $\SR_n(R,I)$ holds.
-If no such $n$ exists, we set $\sr(R,I)=\infty$.
+\begin{dfn} A row $a\in{}^n\!R$ is called \emph{$I$-unimodular} if it is congruent to $e_1$ modulo $I$ and its components $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal. \end{dfn}
+A column $b \in R^n$ will be called $I$-unimodular if its transpose $b^t$ is an $I$-unimodular row.
+We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n,R,I)$ (resp. $\Ums(n,R,I)$).
+When $R=I$ we refer to $R$-unimodular rows and columns as simply unimodular.
+
+It is not hard to show that for a $I$-unimodular row $a$ there exists an $I$-unimodular column $b$ such that $ab=1$ (see~\cite[\S~2]{Va69}).
+
+An $I$-unimodular row $a=(a_1,\ldots a_{n+1})$ is called \emph{stable} if one can choose $b_1,\ldots,b_n\in I$ such that the row $(a_1+a_{n+1}b_1,\ldots,a_n+a_{n+1}b_n)$ is also $I$-unimodular. 
+We say that $I$ satisfies stable range condition $\SR_n(I)$ if any $I$-unimodular row of length $n+1$ is stable.
+It is easy to see that $\SR_n(I)$ implies $\SR_m(I)$ for any $m\geqslant n$. It is also clear that validity of $\SR_n(I)$ does not depend on the ambient ring $R$.
+
+By definition, the {\it stable rank} of $I$ is the smallest natural $n$ such that $\SR_n(I)$ holds.
+We denote the stable rank of $I$ by $\sr(I)$, we set $\sr(I)=\infty$ if no such $n$ exists.
 
@@
 \end{prop}
-\begin{proof} See~\cite{Va71}. 
+\begin{proof} See~\cite{Va71}, \cite[Theorem~2.3]{Va69}. 
 \textbf{TODO: Add reference for the latter fact}.
@@
 By Proposition~\ref{prop:sr_properties} $\sr(I/J) \leq \ell-1$ and therefore
-the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, R/J, I/J)$. 
+the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, R/J, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
 This implies existence of $h\in \E(\Delta_\ell, R, I)$ such that for $v' = v\cdot h$ one has $(v')^+ \equiv e_1$ modulo $J$.

### 2015-04-21 stability-conditions.tex
Minor fixes

@@
 
-The next lemma illustrates a typical application of the absolute relative stability condition.
+The next lemma is an immediate consequence of the definition of stable rank.
+\begin{lemma}\label{lemma:srUnip} Let $v\in\Ums(n, R, I)$ be a unimodular column. Assume that $\sr(I)\leq n-m$ for some $1\leq m \leq n$.
+Then one can find a matrix $a\in \M(n-m,m,I)$ such that the column $(e_{n-m},a)v\in \Ums(n-m, R, I)$. \end{lemma}
+
 Let $v\in R^{2\ell}$ be a vector of the standard vector representation of $\G(\rD_\ell, R)$.
@@
  Let $\Phi=\rD_\ell$ and assume that $\asr(R, I)\leq \ell -1$. Then for any $I$-unimodular column $v=(v^+, v^-)^t\in\Ums(2\ell, R, I)$
- there exist $g\in\U(\Sigma^+_\ell, I)$ such that $(v\cdot g)^+ \in \Ums(\ell, R, I)$.
+ there exist $g\in\U(\Sigma^+_\ell, I)$ such that $(g \cdot v)^+ \in \Ums(\ell, R, I)$.
 \end{lemma}
@@
 the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, R/J, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
-This implies existence of $h\in \E(\Delta_\ell, R, I)$ such that for $v' = v\cdot h$ one has $(v')^+ \equiv e_1$ modulo $J$.
+This implies existence of $h\in \E(\Delta_\ell, R, I)$ such that for $v' = h \cdot v$ one has $(v')^+ \equiv e_1$ modulo $J$.
 
@@
 $(v''_1, v''_{-\ell},\ldots, v''_{-1})$ is $I$-unimodular. Now, applying condition $\sr(I) \leq \ell-1$ once again we find
-$d_1,d_3,\ldots, d_{\ell}\in I$ such that for $v'''=v''\cdot t_{-2,1}(d_1) \cdot \prod\limits_{i=3}^{\ell} t_{-2,-i}(d_i)$
+$d_1,d_3,\ldots, d_{\ell}\in I$ such that for $v'''=t_{-2,1}(d_1) \cdot \prod\limits_{i=3}^{\ell} t_{-2,-i}(d_i) \cdot v''$
 the entries $(v'''_1, v'''_{-\ell},\ldots, v'''_{-3})$ form a $I$-unimodular column.
@@
 We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v'''_1+\sum\limits_{i=3}^\ell f_i v'''_{-i} = 1$.
-Set $\xi = v'''_1-v'''_2-1 \in I$, $v^4=v'''\cdot t_{1,2}(\xi f_1) \cdot \prod\limits_{i=3}^\ell t_{-i,2}(\xi i_k)$.
+Set $\xi = v'''_1-v'''_2-1 \in I$, $v^4=t_{1,2}(\xi f_1) \cdot \prod\limits_{i=3}^\ell t_{-i,2}(\xi i_k) \cdot v'''$.
 Clearly $v^4_1 = v'''_1$ and $v^4_2 = v'''_1-1$, therefore $v^{4+}$ is $I$-unimodular.
-Summarizing the above, we have found $g\in \EP_\ell(R, I)$ such that $v^4=v\cdot g$
+Summarizing the above, we have found $g\in \EP_\ell(R, I)$ such that $v^4=g \cdot v$
 and assertion of the lemma immediately follows from Levi decomposition. \end{proof}

### 2015-04-22 bass-kolster.tex
Added lemma on relative asr condition
Fixed proof of Bass-Kolster for Bl, Dl

--- 2015-03-22 bass-kolster.tex
@@
 \begin{thm}\label{thm:BassKolster}
-Let $\Phi$ be a classical ($\rA,\rB,\rC,\rD$) root system of rank $\geqslant2$, $\Delta<\Phi$ its terminal subsystem of the same type, $(R,I)$ a commutative ring and its ideal, satisfying the following assumption:
+Let $\Phi$ be a classical root system of rank $\geqslant2$, let $R$ be arbitary commutative ring and $I$ be an ideal, satisfying the following condition:
 \begin{itemize}
-\item $\Phi=\rA_\ell$: $\sr(R,I)\leqslant\ell+1$,
-\item $\Phi=\rB_\ell$: $\asr(R,I)\leqslant\ell$,
-\item $\Phi=\rC_\ell$: $\sr(R,I)\leqslant2\ell$,
-\item $\Phi=\rD_\ell$: $\asr(R,I)\leqslant\ell$.
+\item $\Phi=\rA_\ell$: $\sr(I)\leqslant\ell$,
+\item $\Phi=\rB_\ell$: $\asr(R,I)\leqslant\ell-1$,
+\item $\Phi=\rC_\ell$: $\sr(I)\leqslant2\ell$,
+\item $\Phi=\rD_\ell$: $\asr(R,I)\leqslant\ell-1$.
 \end{itemize}
 Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
-\[ \G(\Phi,R,I)=\U(\Sigma^+,I)\ \U(\Sigma^-,I)\cdot \Z\cdot \U(\Sigma^-,I)\ \U(\Sigma^+,I)\cdot \G(\Delta,R,I), \]
+\[\G(\Phi,R,I)=\U(\Sigma^+,I)\ \U(\Sigma^-,I)\cdot \Z\cdot \U(\Sigma^-,I)\ \U(\Sigma^+,I)\cdot \G(\Delta,R,I), \]
 where $\Sigma^\pm=\Phi^\pm\setminus\Delta$ and $\Z=\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \}$.
@@
 \begin{proof}
+Let $g$ be an element of $\G(\Phi, R, I)$ and $e_1$ be the highest weight vector of the standard vector representation of $\G(\Phi, R, I)$.
+It is clear that vector $v=g\cdot e_1$ is $I$-unimodular.
+
 \textsc{Case $\Phi=\rA_\ell$:}
@@
 The same can be done with the first row, so in total we used $8\ell-3$ transformations.
+
+\textsc{Case $\Phi=\rD_\ell$.} 
+By Lemma~\ref{lemma:asrUnip} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'^+$ of vector $v'=h_1\cdot v$ is $I$-unimodular.
+Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, R, I)$, where
+$v''=h_2 \cdot t_{1,2}(c_1) \cdot v'$, $h_2=\prod\limits_{i=3}^\ell t_{i,2}(c_i)$.
+
+We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v''_1+\sum\limits_{i=3}^\ell f_i v''_{i} = 1$.
+Set $\xi = v''_1-v''_{-2}-1 \in I$, $h_3 = t_{1,-2}(\xi f_1) \cdot \prod\limits_{i=3}^\ell t_{i,-2}(\xi f_i)$, $v'''=h_3 \cdot v''$.
+Clearly, $v'''_{-2}=v'''_1-1$, therefore for $v_4 = z_{-\alpha_{max}}(-v'''_{-2}, 1) \cdot v'''$ one has $v^4_1 = 1$, as required.
+On the other hand, $t_{1,2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, while $ h_3 \cdot h_2 \in \U(\Phi^-, I)$.
+
+\textsc{Case $\Phi=\rB_\ell$:} Subdivide $v\in \Ums(2\ell+1, R, I)$ as $v=(v^+, v_0, v^-)\in R^\ell\times R\times R^\ell$.
+Set $J = \mathfrak{J}(v^-) \leq I$.
+Since $\sr(I/J)\leq l$ we can find $c_1,\dots,c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod\limits_{i=1}^\ell t_{0, i}(c_i) \in \U(\Phi^+, I)$
+one has $\bar{v'}^+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, R/J, I/J)$ and, therefore, $(v'^+, v'^-) \in \Ums(2\ell, R, I)$.
+Now, it remains to repeat the argument for $\Phi=\rD_l$ (clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ with respect to the obvious embedding $\rD_\ell\subseteq\rB_\ell$).
+
+%Let $(1+r_1,r_2,\dots,r_\ell,r_0,r_{-\ell},\dots,r_{-1})^t\in\Ums(2\ell+1,R,I)$ be the first column of $g$. 
+%Find $c_1,\dots,c_\ell\in I$ such that $(1+r_1+c_1r_0,\dots,r_\ell+c_\ell r_0,r_{-\ell},\dots,r_{-1})$ is unimodular. 
+%Apply $x_{\beta_k}(c_k)$ with $\beta_k=\alpha_k+\dots+\alpha_\ell$ for all $k=1,\dots,\ell$, and denote the resulting column by 
+%$(1+r_1',\dots,r'_{-1})^t$.
+
+%Note that $r'_i$ is not necessary equal to $r_i+c_ir_0$. 
+%Denote also $\mathfrak{a}=r_{-\ell}R+\dots+r_{-1}R$, then one has $r'_{-\ell}R+\dots+r'_{-1}R=\mathfrak{a}$ and the ideal,
+%generated by $1+r'_1,\dots,r'_\ell$ and $\mathfrak{a}$, is the whole $R$.
+
+%Now $(1+r'_1,\dots,r'_\ell)^t$ is unimodular modulo $\mathfrak{a}$ and lies in the vector representation of $\G(\langle\alpha_1,\dots,\alpha_{\ell-1}\rangle)$ of type $\rA_{\ell-1}$.
+One can apply the case $\Phi=\rA_{\ell-1}$ to the pair $(R/\mathfrak{a},I/\mathfrak{a})$ and find $3\ell$ transformations that will transform the first half of the column into some $(1+s_1,s_2,\dots,s_\ell)^t$ which is congruent to $(1,0,\dots,0)^t$ modulo $\mathfrak{a}$.
+$(s_{-\ell},\dots,s_{-1})^t$ will denote these result of these transformations on $(r'_{-\ell},\dots,r_{-1})^t$.
+
+%Since $\asr(R,I)\leqslant\ell-1$, there exist $c_{-\ell},\dots,c_{-2}$ such for
+%\[ \mathfrak{b}=\langle s_{-\ell}+c_{-\ell}s_{-1},\dots,s_{-2}+c_{-2}s_{-1}\rangle=\langle s'_{-\ell},\ldots,s'_{-2}\rangle \]
+%one has $\mathfrak{I}(\mathfrak{b})=\mathfrak{I}(\mathfrak{a})$. So $(1+s_1,s'_{-\ell},\ldots,s'_{-2})^t\in\Ums(\ell,R,I)$ and can be shortened to some 
+%$(1+s''_1,s''_{-\ell},\ldots,s''_{-3})\in\Ums(\ell-1,R,I)$ with the help of $x_{\beta_i}$, $\beta_i=\alpha_2+\ldots+\alpha_i$, and $x_{\alpha_{\max}}$.
+%Then one use $z_{\alpha_{\max}}$ to put $s''_1$ in position $-2$ and repeat endging of the previous cases.
 \end{proof}
-%\subsection{$\rB_n$}
-%\subsection{$\rD_n$}

### 2015-04-22 paper.tex
Minor fixes
Fixed proof of Bass-Kolster for Bl, Dl

@@
 
-\subsection{Chevalley groups}
-Our exposition of Chevalley groups is standard and follows (...).
-\textbf{TODO: Write more about Chevalley groups}
-
-In this paper we work with irreducible representations of Chevalley groups corresponding to the highest weight
-$\varpi_1$ (in the case of a classical $\Phi_l$) or $\varpi_l$ (in the case $\Phi_l=\rE_l$). 
-The former are the natural vector representations of classical groups acting on free modules $V=R^n$ of dimension 
-$n=l+1, 2l+1, 2l,2l$ for $\Phi=\rA_l,\rB_l,\rC_l,\rD_l$.
-The latter representations have dimension $n=27, 56, 248$ for $l=6,7,8$.
-
-For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda(\pi)$ the set of weights of $\pi$.
-It will be convenient to use standard numbering for weights of representation $\pi$ in the case when $\Phi$ is classical and $\pi$ is a vector representation (cp.~\cite[§1B]{St78}):
-$$\begin{array}{cll}
-  1,2,\ldots, l+1 & \text{in the case} & \Phi =\rA_l, \\
-  1,2,\ldots l, 0, -l,\ldots, -2, -1 & \text{in the case} & \Phi =\rB_l, \\
-  1,2,\ldots l, -l,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_l, \rD_l. \\
-\end{array}$$
-In particular, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ and so on.
-
-\subsection{Elementary subgroup}
-Recall that elementary root unipotents $t_{\alpha}(\xi)$, $x\in R$, $\alpha\in\Phi$ satisfy the following set of relations called Steinberg relations.
-\begin{equation}\label{rel:add} t_\alpha(s) t_\alpha(t) = t_\alpha(s+t), \end{equation} 
-\begin{equation}\label{rel:CCF} [t_\alpha(s),  t_\beta(t)] = \left(\prod\limits t_{i\alpha + j\beta}(N_{\alpha,\beta, i, j}s^i t^j)\right),\quad \alpha\neq-\beta, N_{\alpha, \beta, i, j}\in\mathbb{Z}.\end{equation}
-The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
-The integers $N_{\alpha, \beta, i, j}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.
-
-For $\xi\in R^*$ set $w_\alpha(\xi) := x_\alpha(\xi) x_{-\alpha}(-\xi^{-1}) x_{\alpha}(\xi).$
-If $\rk(\Phi)\geq 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
-\begin{equation}\label{rel:R3} w_\alpha(\xi) t_{\beta}(s) w_\alpha(\xi)^{-1} =
-t_{\sigma\ssub{\alpha}\beta} (\eta_{\alpha, \beta}\xi^{-\langle\beta,\alpha \rangle} s),\ \xi,s\in R. \end{equation}
-where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S~13]{VP} for more details on $\eta_{\alpha, \beta}$).
-
-\begin{rem} Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
-In this situation it will be convenient for us to write $t_{\lambda_1,\lambda_2}(\xi)$ instead of $t_{\lambda_1-\lambda_2}(\xi)$.
-In particular, for $\Phi=\rA_\ell$ we have $t_{1,2}(\xi)=t_{2-1}(\xi)=t_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = t_{\alpha_1}(\xi)$. \end{rem}
-
 \subsection{Root systems}
@@
 
-The following theorem is the main result of \cite{S}.
+\subsection{Chevalley groups}
+Our exposition of Chevalley groups is standard and follows (...).
+\textbf{TODO: Write more about Chevalley groups}
+
+In this paper we work with irreducible representations of Chevalley groups corresponding to the highest weight
+$\varpi_1$ (in the case of a classical $\Phi_l$) or $\varpi_l$ (in the case $\Phi_\ell=\rE_\ell$). 
+The former are the natural vector representations of classical groups acting on free modules $V=R^n$ of dimension 
+$n=\ell+1, 2\ell+1, 2\ell,2\ell$ for $\Phi=\rA_\ell,\rB_\ell,\rC_\ell,\rD_\ell$.
+The latter representations have dimension $n=27, 56, 248$ for $\ell=6,7,8$.
+
+For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda(\pi)$ the set of weights of $\pi$.
+It will be convenient to use standard numbering for weights of representation $\pi$ in the case when $\Phi$ is classical and $\pi$ is a vector representation (cp.~\cite[§1B]{St78}):
+$$\begin{array}{cll}
+  1,2,\ldots, l+1 & \text{in the case} & \Phi =\rA_l, \\
+  1,2,\ldots l, 0, -\ell,\ldots, -2, -1 & \text{in the case} & \Phi =\rB_\ell, \\
+  1,2,\ldots l, -\ell,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
+\end{array}$$
+In particular, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ and so on.
+
+\subsection{Elementary subgroup}
+Recall that elementary root unipotents $t_{\alpha}(\xi)$, $x\in R$, $\alpha\in\Phi$ satisfy the following set of relations called Steinberg relations.
+\begin{equation}\label{rel:add} t_\alpha(s) t_\alpha(t) = t_\alpha(s+t), \end{equation} 
+\begin{equation}\label{rel:CCF} [t_\alpha(s),  t_\beta(t)] = \left(\prod\limits t_{i\alpha + j\beta}(N_{\alpha,\beta, i, j}s^i t^j)\right),\quad \alpha\neq-\beta, N_{\alpha, \beta, i, j}\in\mathbb{Z}.\end{equation}
+The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
+The integers $N_{\alpha, \beta, i, j}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.
+
+For $\xi\in R^*$ set $w_\alpha(\xi) := x_\alpha(\xi) x_{-\alpha}(-\xi^{-1}) x_{\alpha}(\xi).$
+If $\rk(\Phi)\geq 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
+\begin{equation}\label{rel:R3} w_\alpha(\xi) t_{\beta}(s) w_\alpha(\xi)^{-1} =
+t_{\sigma\ssub{\alpha}\beta} (\eta_{\alpha, \beta}\xi^{-\langle\beta,\alpha \rangle} s),\ \xi,s\in R. \end{equation}
+where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S~13]{VP} for more details on $\eta_{\alpha, \beta}$).
+
+\begin{rem} Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
+In this situation it will be convenient for us to write $t_{\lambda_1,\lambda_2}(\xi)$ instead of $t_{\lambda_1-\lambda_2}(\xi)$.
+In particular, for $\Phi=\rA_\ell$ we have $t_{1,2}(\xi)=t_{1-2}(\xi)=t_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = t_{\alpha_1}(\xi)$. \end{rem}
+
+The following theorem is one of the main results of \cite{S} (see~\cite[Theorem~3.4]{S}).
 \begin{thm}\label{theorem:Stepanov}
@@
  \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$. \end{itemize} \end{thm}
-\begin{proof} See~\cite[Theorem~3.4]{S}. \end{proof}
 

### 2015-04-22 bass-kolster.tex
Minor fixes

@@
 It is clear that vector $v=g\cdot e_1$ is $I$-unimodular.
+%TODO: Mention Chevalley---Matsumoto lemma in the introduction
+In view of Chevalley---Matsumoto lemma it suffices to show that $\Z \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ contains an element $g$ whose matrix entry at position $(1,1)$ is equal to $1$.
+We will need to analyze several cases.
 
 \textsc{Case $\Phi=\rA_\ell$:}
-For $g\in\G(\rA_\ell,R,I)$ let $(1+r_1,r_2,\ldots,r_\ell,r_{\ell+1})^t\in\Um(\ell+1,R,I)$, $r_i\in I$ be its first column.
+Denote $v=(1+r_1,r_2,\ldots,r_\ell,r_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
 One can add the last entry to the first $\ell$ with some coefficients from $I$ to make then form a unimodular column of length $\ell$.
@@
 \textsc{Case $\Phi=\rC_\ell$:}
-First column: $(1+r_1,r_2,\ldots,r_\ell,r_{-\ell},\ldots,r_{-1})^t\in\Um(2\ell,R,I)$.
-Find $c_1,\ldots,c_{-2}\in I$ such that $(1+r_1+c_1r_{-1},\ldots,r_{-2}+c_{-2}r_{-1})=(1+r_1',\ldots,r_{-2}')\in\Um(2\ell-1,R,I)$.
+Denote $v=(1+r_1,r_2,\ldots,r_\ell,r_{-\ell},\ldots,r_{-1})^t\in\Ums(2\ell,R,I)$.
+Find $c_1,\ldots,c_{-2}\in I$ such that $(1+r_1+c_1r_{-1},\ldots,r_{-2}+c_{-2}r_{-1})=(1+r_1',\ldots,r_{-2}')\in\Ums(2\ell-1,R,I)$.
 First add $c_{-i}r_{-1}$ to $r_{-i}$ for $-i=-\ell,\ldots,-2$, so that
-\[
-\begin{pmatrix}
+\[ \begin{pmatrix}
 1+r_1 \\ r_i \\ r_{-i} \\ r_{-1}
@@
 1+r_{11} \\ r_i \\ r_{-i}' \\ r_{-1}
-\end{pmatrix},\quad i=2,\ldots,\ell.
-\]
+\end{pmatrix},\quad i=2,\ldots,\ell. \]
 Denote $\mathfrak{a}=\sum_{i=-\ell}^{-2} r_i'R\unlhd R$. Now add $c_ir_{-1}$ to $r_i$ for $i=2,\ldots,\ell$:
-\[
-\begin{pmatrix}
+\[ \begin{pmatrix}
 1+r_{11} \\ r_i' \\ r_{-i}' \\ r_{-1}
@@
 i=2,\ldots,\ell
-\end{matrix*}
-\]
+\end{matrix*} \]
 Finally, add $\left(c_1+\sum_{i=2}^\ell c_ic_{-i}\right)r_{-1}$ to the first row:
@@
 Add $c_{-i}r_i$ to $r_{-1}$, $i=2,\ldots,\ell$:
-\[
-\begin{pmatrix}
+\[ \begin{pmatrix}
 1+r_1 \\ r_i \\ r_{-i} \\ r_{-1}
@@
 1+r_1 \\ r_i' \\ r_{-i} \\ r_{-11}
-\end{pmatrix},\quad i=2,\ldots,\ell.
-\]
+\end{pmatrix},\quad i=2,\ldots,\ell. \]
 Then add $c_ir_i'=c_i(r_1+c_{-i}r_{-i})$, $i=2,\ldots,\ell$ to $r_{-11}$:
-\[
-1+r_1\longmapsto 1+r_1,\quad r_{-11}\longmapsto r_{-1}+\sum_{i=2}^\ell c_{-i}r_{-i}+\sum_{i=2}^\ell c_i(r_i+c_{-i}r_1)=r_{-12}.
-\]
+\[ 1+r_1\longmapsto 1+r_1,\quad r_{-11}\longmapsto r_{-1}+\sum_{i=2}^\ell c_{-i}r_{-i}+\sum_{i=2}^\ell c_i(r_i+c_{-i}r_1)=r_{-12}. \]
 Next add $(c_1-\sum_{i=2}^\ell c_ic_{-i})(1+r_1)$ to $r_{-12}$:
@@
 Again, as in case of $\rA_n$, apply $z_\gamma(-r_1,1)$ with $\gamma=-\alpha_\mathrm{max}$.
-\[
-\begin{pmatrix}1+r_1 \\ \vdots \\ r_1\end{pmatrix}
+\[ \begin{pmatrix}1+r_1 \\ \vdots \\ r_1\end{pmatrix}
 \xmapsto{x_{-\gamma}(-1)}
@@
 \xmapsto{x_{-\gamma}(1)}
-\begin{pmatrix}1 \\ \vdots \\ 0\end{pmatrix}.
-\]
-Now apply $2\ell-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum_{i=2}^\ell (r_i+r_{-i})$ to $r_{-1}$, so by one more transformation one can make the first column trivial.
+\begin{pmatrix}1 \\ \vdots \\ 0\end{pmatrix}. \]
+Now apply $2\ell-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum_{i=2}^\ell (r_i+r_{-i})$ to $r_{-1}$,
+so by one more transformation one can make the first column trivial. 
 The same can be done with the first row, so in total we used $8\ell-3$ transformations.
@@
 \textsc{Case $\Phi=\rB_\ell$:} Subdivide $v\in \Ums(2\ell+1, R, I)$ as $v=(v^+, v_0, v^-)\in R^\ell\times R\times R^\ell$.
-Set $J = \mathfrak{J}(v^-) \leq I$.
+Denote by $J\leq I$ the ideal spanned by components of $v^-$.
 Since $\sr(I/J)\leq l$ we can find $c_1,\dots,c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod\limits_{i=1}^\ell t_{0, i}(c_i) \in \U(\Phi^+, I)$
-one has $\bar{v'}^+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, R/J, I/J)$ and, therefore, $(v'^+, v'^-) \in \Ums(2\ell, R, I)$.
-Now, it remains to repeat the argument for $\Phi=\rD_l$ (clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ with respect to the obvious embedding $\rD_\ell\subseteq\rB_\ell$).
-
-%Let $(1+r_1,r_2,\dots,r_\ell,r_0,r_{-\ell},\dots,r_{-1})^t\in\Ums(2\ell+1,R,I)$ be the first column of $g$. 
-%Find $c_1,\dots,c_\ell\in I$ such that $(1+r_1+c_1r_0,\dots,r_\ell+c_\ell r_0,r_{-\ell},\dots,r_{-1})$ is unimodular. 
-%Apply $x_{\beta_k}(c_k)$ with $\beta_k=\alpha_k+\dots+\alpha_\ell$ for all $k=1,\dots,\ell$, and denote the resulting column by 
-%$(1+r_1',\dots,r'_{-1})^t$.
-
-%Note that $r'_i$ is not necessary equal to $r_i+c_ir_0$. 
-%Denote also $\mathfrak{a}=r_{-\ell}R+\dots+r_{-1}R$, then one has $r'_{-\ell}R+\dots+r'_{-1}R=\mathfrak{a}$ and the ideal,
-%generated by $1+r'_1,\dots,r'_\ell$ and $\mathfrak{a}$, is the whole $R$.
-
-%Now $(1+r'_1,\dots,r'_\ell)^t$ is unimodular modulo $\mathfrak{a}$ and lies in the vector representation of $\G(\langle\alpha_1,\dots,\alpha_{\ell-1}\rangle)$ of type $\rA_{\ell-1}$.
-One can apply the case $\Phi=\rA_{\ell-1}$ to the pair $(R/\mathfrak{a},I/\mathfrak{a})$ and find $3\ell$ transformations that will transform the first half of the column into some $(1+s_1,s_2,\dots,s_\ell)^t$ which is congruent to $(1,0,\dots,0)^t$ modulo $\mathfrak{a}$.
-$(s_{-\ell},\dots,s_{-1})^t$ will denote these result of these transformations on $(r'_{-\ell},\dots,r_{-1})^t$.
-
-%Since $\asr(R,I)\leqslant\ell-1$, there exist $c_{-\ell},\dots,c_{-2}$ such for
-%\[ \mathfrak{b}=\langle s_{-\ell}+c_{-\ell}s_{-1},\dots,s_{-2}+c_{-2}s_{-1}\rangle=\langle s'_{-\ell},\ldots,s'_{-2}\rangle \]
-%one has $\mathfrak{I}(\mathfrak{b})=\mathfrak{I}(\mathfrak{a})$. So $(1+s_1,s'_{-\ell},\ldots,s'_{-2})^t\in\Ums(\ell,R,I)$ and can be shortened to some 
-%$(1+s''_1,s''_{-\ell},\ldots,s''_{-3})\in\Ums(\ell-1,R,I)$ with the help of $x_{\beta_i}$, $\beta_i=\alpha_2+\ldots+\alpha_i$, and $x_{\alpha_{\max}}$.
-%Then one use $z_{\alpha_{\max}}$ to put $s''_1$ in position $-2$ and repeat endging of the previous cases.
-\end{proof}
+one has $\bar{v'}^+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, R/J, I/J)$ and, therefore, $(v'^+, v'^-) \in \Ums(2\ell, R, I)$ and one can repeat the argument for the case $\Phi=\rD_l$.
+(clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ with respect natural embedding $\rD_\ell\subseteq\rB_\ell$). \end{proof}

### 2015-04-22 bass-kolster.tex
Written down lemma on the action of unipotent radicals

@@
 Since $\sr(I/J)\leq l$ we can find $c_1,\dots,c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod\limits_{i=1}^\ell t_{0, i}(c_i) \in \U(\Phi^+, I)$
-one has $\bar{v'}^+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, R/J, I/J)$ and, therefore, $(v'^+, v'^-) \in \Ums(2\ell, R, I)$ and one can repeat the argument for the case $\Phi=\rD_l$.
-(clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ with respect natural embedding $\rD_\ell\subseteq\rB_\ell$). \end{proof}
+one has $\bar{v'}^+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, R/J, I/J)$ and, therefore, $(v'^+, v'^-) \in \Ums(2\ell, R, I)$.
+Now one can finish the proof by repeating the argument for the case $\Phi=\rD_l$.
+(clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ under the natural embedding $\rD_\ell\subseteq\rB_\ell$). \end{proof}

### 2015-04-22 dennis-vaserstein.tex
Minor fixes
Written down lemma on the action of unipotent radicals

@@
     2 & $\rD_\ell$, $\ell\geq 4$ & $(1, \ell)$ & $\sr(I) \leq \ell-2$ \\ \hline    
-    3 & $\rE_\ell$, $\ell=6,7,8$ & $(2, \ell)$ & $\sr(I) \leq \ell-3$ \\ \hline     
-    4 & $\rE_\ell$, $\ell=6,7,8$ & $(1, \ell)$ & $\asr(R, I)\leq \ell-2$ \\ \hline    
+    3 & $\rE_\ell$, $\ell=6,7$ & $(2, \ell)$ & $\sr(I) \leq \ell-3$ \\ \hline     
+    4 & $\rE_\ell$, $\ell=6,7$ & $(1, \ell)$ & $\asr(R, I)\leq \ell-2$ \\ \hline    
     5 & $\rB_\ell$, $\ell\geq 3$ & $(1, \ell)$ & $\sr(I) \leq \ell-2$ \\ \hline
@@
 The following lemma is a relative version of the main reduction used by M.~Stein in~\cite{St78} for the proof of the absolute Dennis--Vaserstein decomposition.
-\begin{lemma}\label{Stein_reduction}
+\begin{lemma}\label{lemma:Stein_reduction}
 Assume that there exists a subset $\widetilde{L_r} \subseteq \E(\Delta_r, R, I)$ with the following properties:
@@
 
-Now we are ready to prove the needed equality.
-By virtue of Theorem~\ref{theorem:Stepanov} it suffices to show that $A$ is invariant with respect to left multiplication by elements of the following two families:
+\begin{proof}[Proof of Theorem~\ref{theorem:relative_dv}]
+We first show that under specified assumptions on $(R, I)$ one can satisfy the conditions of Lemma~\ref{lemma:Stein_reduction}.
+%TODO: Specify how we apply Lemma~\ref{lemma:uraction}
+
+Notice that By virtue of Theorem~\ref{theorem:Stepanov} it suffices to show that $A_{rs}$ is invariant with respect to left multiplication by elements of the following two families:
 \begin{itemize} \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
@@
 Thanks to Lemma~\ref{lemma:conj_lemma} it suffices to check the required statement only for the second family of elements.
+
+Now we are ready to prove the needed equality.
 Denote by $S$ the set of all roots $\alpha$ of $\Phi$ for which one has $X_{\alpha}(I)\cdot A_{rs}\subseteq A_{rs}$.
@@
 Since $\alpha_s \in S$ the argument similar to the one above implies $\Sigma^-_s\subseteq S$. This completes the proof of the lemma. 
+\end{proof}

### 2015-04-22 stability-conditions.tex
Fixed proof of Bass-Kolster for Bl, Dl
Written down lemma on the action of unipotent radicals

@@
 We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v'''_1+\sum\limits_{i=3}^\ell f_i v'''_{-i} = 1$.
-Set $\xi = v'''_1-v'''_2-1 \in I$, $v^4=t_{1,2}(\xi f_1) \cdot \prod\limits_{i=3}^\ell t_{-i,2}(\xi i_k) \cdot v'''$.
-Clearly $v^4_1 = v'''_1$ and $v^4_2 = v'''_1-1$, therefore $v^{4+}$ is $I$-unimodular.
+Set $\xi = v'''_1-v'''_2-1 \in I$, $v^4=t_{1,2}(\xi f_1) \cdot \prod\limits_{i=3}^\ell t_{-i,2}(\xi f_i) \cdot v'''$.
+Clearly $v^4_2 = v^4_1-1$, therefore $v^{4+}$ is $I$-unimodular.
 Summarizing the above, we have found $g\in \EP_\ell(R, I)$ such that $v^4=g \cdot v$
@@
 \end{itemize}
-Then for any $I$-unimodular column $v\in \Ums(n, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yx \cdot v)_\lambda = 0$ for $\lambda\in \Gamma$.
+Then for any $I$-unimodular column $g\in \G(\Phi, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yxg \cdot e_1)_\lambda = 0$ for $\lambda\in \Gamma$.
 \end{lemma}
-\textbf{TODO: Write proof of this lemma}
-%TODO:
+\begin{proof}
+\textsc{Case $\Phi=\rD_\ell$.} From the proof of Lemma~\ref{lemma:asrUnip} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=g\cdot v$ one has $v'_2=v'_1-1\in I$.
+Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$ and, therefore by Chevalley---Matsumoto lemma there exists $h_2 \in \U(\Phi^-, I)$ such that 
+$g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fix $e_1$.
+Using Levi decomposition we can rewrite $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
+Now, it is clear that $x$, $y$ are the desired elements.
+\end{proof}

### 2015-04-22 dennis-vaserstein.tex
Minor changes
Rewritten proof of relative DV-decomposition

@@
     \begin{tabular}{| l | l | l | l | l |} \hline
-    № & $\Phi$ & $(r,s)$ & ring condition \\ \hline
-    1 & $\rA_\ell$, $\ell\geq 2$ & $(1, \ell)$ & $\sr(I) \leq \ell-1$ \\ \hline
-    2 & $\rD_\ell$, $\ell\geq 4$ & $(1, \ell)$ & $\sr(I) \leq \ell-2$ \\ \hline    
-    3 & $\rE_\ell$, $\ell=6,7$ & $(2, \ell)$ & $\sr(I) \leq \ell-3$ \\ \hline     
-    4 & $\rE_\ell$, $\ell=6,7$ & $(1, \ell)$ & $\asr(R, I)\leq \ell-2$ \\ \hline    
-    5 & $\rB_\ell$, $\ell\geq 3$ & $(1, \ell)$ & $\sr(I) \leq \ell-2$ \\ \hline
+    № & $\Phi$ & $(s,r)$ & ring condition \\ \hline
+    1. & $\rA_\ell$, $\ell\geq 2$ & $(1, \ell)$ & $\sr(I) \leq \ell-1$ \\ \hline
+    2. & $\rB_\ell$, $\ell\geq 3$ & $(1, \ell)$ & $\sr(I) \leq \ell-1$ \\ \hline
+    3. & $\rD_\ell$, $\ell\geq 4$ & $(1, \ell)$ & $\sr(I) \leq \ell-2$ \\ \hline    
+    4. & $\rE_\ell$, $\ell=6,7$ & $(\ell, 2)$ & $\sr(I) \leq \ell-3$ \\ \hline     
+    5. & $\rE_\ell$, $\ell=6,7$ & $(\ell, 1)$ & $\asr(R, I)\leq \ell-2$ \\ \hline    
     \end{tabular} \end{center} 
@@
 
-\subsection{Main reduction.} Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
+Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
 This action induces an action of $\E(\Phi, R)$ on the set $\mathfrak{S}$ of all subsets of $\E(\Phi, R, I)$.
@@
 \begin{proof}[Proof of Theorem~\ref{theorem:relative_dv}]
-We first show that under specified assumptions on $(R, I)$ one can satisfy the conditions of Lemma~\ref{lemma:Stein_reduction}.
-%TODO: Specify how we apply Lemma~\ref{lemma:uraction}
+We first show that under specified assumptions on $(R, I)$ one can meet the conditions of Lemma~\ref{lemma:Stein_reduction}.
+Consider the following two subsets of $\Lambda(\pi)$:
+$$\Gamma = \varpi_s- (\Sigma_s^+\cap \Delta_r),\quad \Gamma_0 = \{\lambda \in \Gamma \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$$
+Clearly, $\Gamma$ is the set of weights of an irreducible representation of $\G(\Delta_r, R)$ corresponding to the same highest weight $\varpi_s$.
+The subsystem $\Delta_r$ has type $\rA_{\ell-1}$ in all cases except the last one.
+It is also clear that $|\Gamma_0|=1$ for $\Phi=\rA_\ell, \rB_\ell$, $|\Gamma_0|=2$ for $\Phi=\rD_\ell$, $|\Gamma_0|=3$ for $\Phi=\rE_\ell$ and $r=2$.
+In the case $\Phi=\rE_\ell$, $r=2$ the subsystem $\Delta_r$ has type $\rD_{\ell-1}$ and $|\Gamma_0|=\ell-1$.
 
-Notice that By virtue of Theorem~\ref{theorem:Stepanov} it suffices to show that $A_{rs}$ is invariant with respect to left multiplication by elements of the following two families:
+Let $\widetilde{L_r}$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma_0$.
+In any of specified cases the assumption on $(R, I)$ allows us to apply Lemma~\ref{lemma:uraction} to the subsystem $\Delta_r$ and find
+$x\in\U(\Delta_r\cap\Phi^+, I)$, $y\in \U(\Delta_r\cap\Phi^-, I)$ such that $yx\cdot g \in \widetilde{L_r}$.
+This proves the first condition of Lemma~\ref{lemma:Stein_reduction}, indeed:
+$$ \U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} \cdot (yxg) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r}.$$
+To prove the second condition notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in\widetilde{L_r}$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ and, therefore,
+$$X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \E(\Delta_s, R, I) \subseteq \EP_s(R, I).$$
+
+From now on we can assume that the statement of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
+Notice that in view of Theorem~\ref{theorem:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:
 \begin{itemize} \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
 \item $x_{\beta}(s)$, $s \in I$, $\beta \in \Phi$. \end{itemize}
-Thanks to Lemma~\ref{lemma:conj_lemma} it suffices to check the required statement only for the second family of elements.
+Since $\EP_s \subseteq N_{rs}$ it suffices to check inclusions only for the second family of elements.
+We already know that $\U^+(\Phi, I) \subseteq L_{rs}$.
 
-Now we are ready to prove the needed equality.
-Denote by $S$ the set of all roots $\alpha$ of $\Phi$ for which one has $X_{\alpha}(I)\cdot A_{rs}\subseteq A_{rs}$.
-It remains to prove that $S$ coincides with $\Phi$. We already know that $\Phi^+ \subseteq S$.
+Notice that the Weyl group $W(\Delta_s)$ acts transitively on $\Delta_s$, therefore in view of relation~\ref{rel:R3} the subgroup
+$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leq \EP_s$ acts transitively on the set of root subgroups $X_\alpha(I)$, $\alpha\in \Delta_s$.
+Since $X_{-\alpha\ssub{r}}(I) \subseteq L_{rs}$ we get that that $\U(\Delta_s \cap \Phi^-, I)\subseteq L_{rs}$.
 
-Notice that the Weyl group $W(\Delta_s)$ acts transitively on $\Delta_s$, therefore in view of~\ref{rel:R3} the subgroup
-$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leq \EP_s$ acts transitively on the set of root subgroups $X_\alpha(I)$, $\alpha\in \Delta_s$.
-Since $-\alpha_r\in S$ this implies that that $\Delta_s\subseteq S$.
-
-Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$. Our assumptions on $\Phi$ guarantee that $m_s(\alpha)=1$, 
-hence every two roots $\alpha, \beta \in \Sigma^-_s$ have the same $s$-shape (i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
-By Lemma~\ref{lemma:abs} $W(\Delta_s)$ interchanges $\alpha$ and $\beta$. %if their length is equal.
-Since $\alpha_s \in S$ the argument similar to the one above implies $\Sigma^-_s\subseteq S$. This completes the proof of the lemma. 
+Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$. Our assumptions on $\Phi$ guarantee that $m_s(\widetilde{\alpha})=1$, 
+and, consequently, every two roots $\alpha, \beta \in \Sigma^-_s$ have the same $s$-shape (i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
+By Lemma~\ref{lemma:abs} $W(\Delta_s)$ interchanges $\alpha$ and $\beta$ if their length is equal (which is the case if we assume additionally $\Phi\neq \rB_\ell$).
+Since $X_{\alpha\ssub{s}} \subseteq L_{rs}$ the argument similar to the one above implies $\U(\Sigma^-_s, I)\subseteq L_{rs}$.
+This completes the proof of the theorem for $\Phi\neq \rB_\ell$. 
+%TODO:
+\textbf{TODO: Finish the proof for $\Phi=\rB_\ell$.}
 \end{proof}

### 2015-04-22 stability-conditions.tex
Rewritten proof of relative DV-decomposition

@@
 \end{itemize}
-Then for any $I$-unimodular column $g\in \G(\Phi, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yxg \cdot e_1)_\lambda = 0$ for $\lambda\in \Gamma$.
+Then for any $I$-unimodular column $g\in \G(\Phi, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yxg \cdot v^+)_\lambda = 0$ for $\lambda\in \Gamma$.
 \end{lemma}
 \begin{proof}
+\textsc{Case $\Phi=\rA_\ell$.} \textbf{TODO: Write proof for this case.}
+
 \textsc{Case $\Phi=\rD_\ell$.} From the proof of Lemma~\ref{lemma:asrUnip} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=g\cdot v$ one has $v'_2=v'_1-1\in I$.
 Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$ and, therefore by Chevalley---Matsumoto lemma there exists $h_2 \in \U(\Phi^-, I)$ such that 
-$g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fix $e_1$.
+$g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fix $v^+$.
 Using Levi decomposition we can rewrite $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
-Now, it is clear that $x$, $y$ are the desired elements.
+It is clear that $x$, $y$ are the desired elements.
 \end{proof}

### 2015-04-24 congrsubgr-boundgen.tex
Bounded generation for Sp over Hasse domains

@@
 From this one immediately gets the bounded generation for $\G(\Phi,R,I)$.
+
+We will use the following
+\begin{lemma}[{\cite[Corollary~3.3]{S}}]
+Let $\Phi$ be a root system of rank $\geqslant2$, $R$ a commutative ring and $I\trianglelefteq R$ its ideal.
+If $\Phi\neq\rC_\ell$, then $\E\left(\Phi,R,I^2\right)\leqslant\E(\Phi,I)$, otherwise, $\E\left(\Phi,R,II^{\indexbox{2}}\right)\leqslant\E(\Phi,I)$.
+\end{lemma}
+Here $I^{\indexbox{2}}$ stand for the ideal generated by all squares.
+So $I^2$ is generated by the elements of the form $ab$ for all $a,b\in I$, while $II^{\indexbox{2}}$ is generated by all elements of the form $a^2b$ for $a,b\in I$.
 \begin{lemma}
@@
 \[ G(I,I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2,\mathcal{O}_S)\;\middle|\; a,d\in I^2,\ b,c\in I \right\}. \]
-Note that $g\cdot z_{21}(a,1)\in G(I,I)$. Indeed,
+Note that $g_1=g\cdot z_{21}(a,1)\in G(I,I)$. Indeed,
 \[
@@
 \]
-Now for a matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)\in\G(2,\mathcal{O}_S,I^2)$.
-Since for root systems $\Phi\neq\rC_\ell$ with $\rk\Phi\geqslant2$ one has $\E(\Phi,\mathcal{O}_S,I^2)\leqslant\E(\Phi,I)$, we are done for all groups but symplectic.
+Now for a matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)\in\SL(2,\mathcal{O}_S,I^2)$.
+For any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$ one has $\E\left(\Phi,\mathcal{O}_S,I^2\right)\leqslant\E(\Phi,I)$, and this shows that $g$ has a bounded expression in terms of $z_\alpha$.
 
-\textbf{TODO:} What happens for $\rC_\ell$?
+In case $\Phi=\rC_\ell$, one can compute
+\[ \det(g_1)=a^3d-3a^2bc+a^2bd+ab^2c+a^3+a^2b+a^2d+2abc-abd+1 \]
+to see that $2abc-abd\in II^{\indexbox{2}}$, so
+\[ g_2=x_{21}(-a-c)\cdot g_1\cdot x_{12}(a-b)\equiv
+\begin{pmatrix}
+1+ab-a^2 & -ab-a^2 \\ ad-ac-abc & 1-ab+a^2
+\end{pmatrix}\bmod II^{\indexbox{2}}. \]
+Now for $g_3=g_2\cdot z_{12}\left(a^2-ab,1\right)$ one has
+\begin{align*}
+& g_3\equiv\begin{pmatrix} 1 & -2ab \\ -abc-a^2+ab-ac+ad & 1 \end{pmatrix}\bmod II^{\indexbox{2}},\\
+& g_4=x_{12}(2ab)\cdot g_3\equiv x_{21}\left(-abc-a^2+ab-ac+ad\right)\bmod II^{\indexbox{2}}.
+\end{align*}
+Thus $g_4\cdot x_{21}(*)\in\SL\left(2,\mathcal{O}_S,II^{\indexbox{2}}\right)\leqslant\E(\rC_\ell,I)$ and can be expressed as a bounded product of $x_\alpha$.
 \end{proof}

### 2015-04-24 paper.tex
Rewritten proof of relative DV-decomposition
Bounded generation for Sp over Hasse domains
Small fixes

@@
 \DeclareMathOperator{\Spec}{Spec}
+\DeclareMathOperator{\Stab}{Stab}
 \DeclareMathOperator{\ASR}{ASR}
@@
 \newcommand{\rE}{\mathsf{E}}
+
+\makeatletter
+\newcommand{\indexbox}[1]{\text{\fboxsep=.1em\fbox{\m@th$\displaystyle#1$}}}
+\makeatother
 
@@
 
-\begin{lemma}\label{lemma:abs} Let $\alpha, \beta \in \Sigma^\pm_J$ be two roots having the same length such that $\shape(J,\alpha)=\shape(J,\beta)\neq 0$.
-Then $\alpha$ and $\beta$ are conjugate under the action of $W(\Delta_J)$. \end{lemma} \begin{proof} See~\cite[Lemma~1]{ABS}. \end{proof}
+\begin{lemma}[{\cite[Lemma~1]{ABS}}]\label{lemma:abs}
+Let $\alpha, \beta \in \Sigma^\pm_J$ be two roots having the same length such that $\shape(J,\alpha)=\shape(J,\beta)\neq 0$.
+Then $\alpha$ and $\beta$ are conjugate under the action of $W(\Delta_J)$.
+\end{lemma}
 
@@
 
+In what follows we also assume that there is some basis $E=\{e_\lambda\}_{\lambda\in\Lambda(\pi)}$ fixed for every representation $V$.
+We denote by $v^+$ the basis vector corresponding to highest weight. 
+Using the the above notation for classical $\Phi$ we have $v^+=e_1$.
+%TODO: State Matsumoto lemma and Chevalley-Matsumoto lemma
+
 \subsection{Elementary subgroup}
@@
 t_{\sigma\ssub{\alpha}\beta} (\eta_{\alpha, \beta}\xi^{-\langle\beta,\alpha \rangle} s),\ \xi,s\in R. \end{equation}
-where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S~13]{VP} for more details on $\eta_{\alpha, \beta}$).
+where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S13]{VP} for more details on $\eta_{\alpha, \beta}$).
 

### 2015-04-28 stability-conditions.tex
Small fixes
Relative ASR Bak-like

@@
 Clearly, for any $g\in\GL(n,R)$ one has $\mathfrak{J}(a\cdot g)=\mathfrak{J}(a)$.
-\begin{dfn}
-We say that a pair $(R,I)$ satisfies $\ASR_n(R,I)$ if it satisfies $\SR_n(R,I)$ and, moreover, 
-for any row $a=(a_1,\ldots,a_{n+1})\in I^n$ there exist $b_1,\ldots,b_n\in I$ such that
-\[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+b_1a_{n+1},\ldots,a_n+b_na_{n+1}).\]
+\begin{dfn}\label{dfn:j-stable}
+We say that a row $a=(a_1,\ldots,a_{n+1})\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable, if there exist $c_1,\ldots,c_n\in I$ such that
+\[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1},\ldots,a_n+c_na_{n+1}).\]
+\end{dfn}
+\begin{dfn}\label{dfn:asr}
+We say that a pair $(R,I)$ satisfies $\ASR_n(R,I)$ if satisfies $\SR_n(R,I)$ and, moreover, any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable.
+
 It is easy to see that $\ASR_m(R,I)$ implies $\ASR_n(R,I)$ for any $n\geqslant m$. 
@@
 \end{lemma}
+%\begin{proof}
+%Assume first that $\ASR_n(R)$ holds.
+%Then for the row $(a_1,\ldots,a_n,d)$ there exist $c_1,\ldots,c_n$ such that $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a_1+c_1d,\ldots,a_n+c_nd)$. 
+%Therefore $a_1+c_1d,\ldots,a_n+c_nd$ together with $b$ generate the unit ideal.
+%Of course, one could replace $b$ with $b+td$ from the very start.
+%
+%To show the converse take arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!R$ and consider the unimodular row $(a_1,\ldots,a_n,1,d)\in\Ums(n+2,R).$
+%There exist $c_1,\ldots,c_n$ such that \[(a'_1,\ldots,a'_n,1+td)=(a_1+c_1d,\ldots,a_n+c_nd,1+td)\] is unimodular for all $t\in R$.
+%Suppose that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that $a'_1,\ldots,a'_n\in\mathfrak{m}$ but at least one of the elements $d$, $a_i$ is not in $\mathfrak{m}$.
+%Clearly, $d\notin\mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$ contrary to the assumption).
+%On the other hand, $1+td\notin\mathfrak{m}$,
+%hence the inequality $1+\bar{t}\bar{d}\neq0$ in the residue field $R/\mathfrak{m}$ may not hold for arbitrary $\bar{t}$ 
+%(take e.g. $\bar{t}=-1/\bar{d}$).
+%This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a'_1,\ldots,a'_n)$.
+%\end{proof}
+
+We will use use the following version of the relative absolute stable rank condition.
+\begin{lemma}\label{lemma:relative-asr-unimod}
+For a commutative ring $R$ and its ideal $I$ the following two statements are equivalent:
+\begin{enumerate}
+\item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable;
+\item\label{asr-bak-like} For any $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Ums(n+s,R,I)$ there exist $c_1,\ldots,c_n\in I$ such that $(b+b',a_1+c_1d,\ldots,a_n+c_nd)$ is $I$-unimodular for any $b'\in J$, where $J=\langle a_1,\ldots,a_n,d \rangle$.
+\end{enumerate}
+\end{lemma}
 \begin{proof}
-Assume first that $\ASR_n(R)$ holds.
-Then for the row $(a_1,\ldots,a_n,d)$ there exist $c_1,\ldots,c_n$ such that $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a_1+c_1d,\ldots,a_n+c_nd)$. 
-Therefore $a_1+c_1d,\ldots,a_n+c_nd$ together with $b$ generate the unit ideal.
-Of course, one could replace $b$ with $b+td$ from the very start.
+Assume first that any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable. In particular for a given unimodular row $(b,a_1,\ldots,a_n,d)\in\Ums(n+s,R,I)$ there exist $c_1,\ldots,c_n$ such that
+\[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1},\ldots,a_n+c_na_{n+1}).\]
+Therefore $(b,a_1+c_1d,\ldots,a_n+c_nd)$ is also unimodular. Of course, for any $b'\in J$ one could replace $b$ with $b+b'$ from the very start.
 
-To show the converse take arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!R$ and consider the unimodular row $(a_1,\ldots,a_n,1,d)\in\Ums(n+2,R).$
-There exist $c_1,\ldots,c_n$ such that \[(a'_1,\ldots,a'_n,1+td)=(a_1+c_1d,\ldots,a_n+c_nd,1+td)\] is unimodular for all $t\in R$.
+To show the converse take arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!I$ and consider the $I$-unimodular row $(1,a_1,\ldots,a_n,d)\in\Ums(n+2,R,I).$
+There exist $c_1,\ldots,c_n$ such that
+\[ (1+b',a'_1,\ldots,a'_n)=(1+b',a_1+c_1d,\ldots,a_n+c_nd) \]
+is unimodular for any $b'\in J$.
 Suppose that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that $a'_1,\ldots,a'_n\in\mathfrak{m}$ but at least one of the elements $d$, $a_i$ is not in $\mathfrak{m}$.
 Clearly, $d\notin\mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$ contrary to the assumption).
-On the other hand, $1+td\notin\mathfrak{m}$,
-hence the inequality $1+\bar{t}\bar{d}\neq0$ in the residue field $R/\mathfrak{m}$ may not hold for arbitrary $\bar{t}$ 
-(take e.g. $\bar{t}=-1/\bar{d}$).
-This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a'_1,\ldots,a'_n)$.
+Note that $1+b'\notin\mathfrak{m}$, so the equation $1+\bar{b}'=0$ can not hold in the residue field $R/\mathfrak{m}$.
+But for $t\in R$ such that $\bar{t}=-1/\bar{d}$ one can take $b'=td\in J$, a contradiction to $1+\bar{b}'\neq0$.
+Hence no such $\mathfrak{m}$ exists and $\mathfrak{J}(a'_1,\ldots,a'_n)=\mathfrak{J}(a_1,\ldots,a_n,d)$.
 \end{proof}
@@
 The next lemma is an immediate consequence of the definition of stable rank.
-\begin{lemma}\label{lemma:srUnip} Let $v\in\Ums(n, R, I)$ be a unimodular column. Assume that $\sr(I)\leq n-m$ for some $1\leq m \leq n$.
+\begin{lemma}\label{lemma:srUnip} Let $v\in\Ums(n, R, I)$ be a unimodular column. Assume that $\sr(I)\leq n-m$ for some $1\leqslant m < n$.
 Then one can find a matrix $a\in \M(n-m,m,I)$ such that the column $(e_{n-m},a)v\in \Ums(n-m, R, I)$. \end{lemma}

### 2015-04-28 bass-kolster.tex
Bass---Kolster for C_l shortened

@@
 \textsc{Case $\Phi=\rC_\ell$:}
-Denote $v=(1+r_1,r_2,\ldots,r_\ell,r_{-\ell},\ldots,r_{-1})^t\in\Ums(2\ell,R,I)$.
-Find $c_1,\ldots,c_{-2}\in I$ such that $(1+r_1+c_1r_{-1},\ldots,r_{-2}+c_{-2}r_{-1})=(1+r_1',\ldots,r_{-2}')\in\Ums(2\ell-1,R,I)$.
-First add $c_{-i}r_{-1}$ to $r_{-i}$ for $-i=-\ell,\ldots,-2$, so that
-\[ \begin{pmatrix}
-1+r_1 \\ r_i \\ r_{-i} \\ r_{-1}
-\end{pmatrix}
-\longmapsto
-\begin{pmatrix}
-1+r_1+\sum_{i=2}^\ell c_{-i}r_i\\ r_i \\ r_{-i}+c_{-i}r_{-1} \\ r_{-1}
-\end{pmatrix}=
-\begin{pmatrix}
-1+r_{11} \\ r_i \\ r_{-i}' \\ r_{-1}
-\end{pmatrix},\quad i=2,\ldots,\ell. \]
-Denote $\mathfrak{a}=\sum_{i=-\ell}^{-2} r_i'R\unlhd R$. Now add $c_ir_{-1}$ to $r_i$ for $i=2,\ldots,\ell$:
-\[ \begin{pmatrix}
-1+r_{11} \\ r_i' \\ r_{-i}' \\ r_{-1}
-\end{pmatrix}
-\longmapsto
-\begin{pmatrix}
-1+r_{11}+a \\ r_i+c_ir_{-1} \\ r_{-i}' \\ r_{-1}
-\end{pmatrix}=
-\begin{pmatrix}
-1+r_{12} \\ r_i' \\ r_{-i}' \\ r_{-1}
-\end{pmatrix},\quad
-\begin{matrix*}[l]
-a\in\mathfrak{a}\\
-i=2,\ldots,\ell
-\end{matrix*} \]
-Finally, add $\left(c_1+\sum_{i=2}^\ell c_ic_{-i}\right)r_{-1}$ to the first row:
-\begin{multline*}
-\left(1+r_1+\sum\nolimits_{i=2}^\ell c_{-i}r_i+a\right)+\left(c_1r_{-1}+\sum\nolimits_{i=2}^\ell c_ic_{-i}r_{-1}\right)=\\
-=(1+r_1+c_1r_{-1})+\sum\nolimits_{i=2}^\ell c_{-i}(r_i+c_ir_{-1})+a=\\
-=1+r_1'+\sum\nolimits_{i=2}^\ell c_{-i}r_i'+a=1+r_1''.
-\end{multline*}
-Note that $\langle 1+r_1'',r_2',\ldots,r_{-2}'\rangle=\langle 1+r_1',r_2',\ldots,r_{-2}'\rangle$, so we made the first $2\ell-1$ elements form a unimodular column.
+Denote $v=(v^+,v^-)^t\in\Ums(2\ell,R,I)$. Find $c_1,\ldots,c_{-2}\in I$ such that $(v_1+c_1v_{-1},\ldots,v_{-2}+c_{-2}v_{-1})=(v_1',\ldots,v_{-2}')$ is unimodular.
 
-Now we may assume that the first column $(1+r_1,\ldots,r_{-1})^t$ has its first $2\ell-1$ entries unimodular.
-Find $c_1,\ldots,c_{-2}\in I$ such that $c_1(1+r_1)+c_2r_2+\ldots+c_{-2}r_{-2}=r_1-r_{-1}$.
-Add $c_{-i}r_i$ to $r_{-1}$, $i=2,\ldots,\ell$:
-\[ \begin{pmatrix}
-1+r_1 \\ r_i \\ r_{-i} \\ r_{-1}
-\end{pmatrix}
-\longmapsto
-\begin{pmatrix}
-1+r_1 \\ r_i+c_{-i}r_1 \\ r_{-i} \\ r_{-1}+\sum_{i=2}^\ell c_{-i}r_{-i}
-\end{pmatrix}=
-\begin{pmatrix}
-1+r_1 \\ r_i' \\ r_{-i} \\ r_{-11}
-\end{pmatrix},\quad i=2,\ldots,\ell. \]
-Then add $c_ir_i'=c_i(r_1+c_{-i}r_{-i})$, $i=2,\ldots,\ell$ to $r_{-11}$:
-\[ 1+r_1\longmapsto 1+r_1,\quad r_{-11}\longmapsto r_{-1}+\sum_{i=2}^\ell c_{-i}r_{-i}+\sum_{i=2}^\ell c_i(r_i+c_{-i}r_1)=r_{-12}. \]
-Next add $(c_1-\sum_{i=2}^\ell c_ic_{-i})(1+r_1)$ to $r_{-12}$:
-\begin{multline*}
-r_{-12}\mapsto r_{-1}+\sum_{i=2}^\ell c_{-i}r_{-i}+\sum_{i=2}^\ell c_i(r_i+c_{-i}(1+r_1))+c_1(1+r_1)-\sum_{i=2}^\ell c_ic_{-i}(1+r_1)=\\=r_{-1}+c_1(1+r_1)+\sum_{i=2}^\ell(c_ir_i+c_{-i}r_{-i})=r_{-1}+(r_1-r_{-1})=r_1.
-\end{multline*}
-Again, as in case of $\rA_n$, apply $z_\gamma(-r_1,1)$ with $\gamma=-\alpha_\mathrm{max}$.
-\[ \begin{pmatrix}1+r_1 \\ \vdots \\ r_1\end{pmatrix}
-\xmapsto{x_{-\gamma}(-1)}
-\begin{pmatrix}1 \\ \vdots \\ r_1\end{pmatrix}
-\xmapsto{x_\gamma(-r_1)}
-\begin{pmatrix}1 \\ \vdots \\ 0\end{pmatrix}
-\xmapsto{x_{-\gamma}(1)}
-\begin{pmatrix}1 \\ \vdots \\ 0\end{pmatrix}. \]
-Now apply $2\ell-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum_{i=2}^\ell (r_i+r_{-i})$ to $r_{-1}$,
+First add $c_{-i}v_{-1}$ to $v_{-i}$ for $-i=-\ell,\ldots,-2$, this will also add something to $v_1$.
+
+Then add $c_iv_{-1}$ to $v_i$ for $i=2,\ldots,\ell$.
+So far we have made the entries from $i=2,\ldots,-2$ equal to $v_i+c_iv_{-1}$, and one more upper transformation (corresponding to the highest root) will make the first entry equal to $v_1+c_1v_{-1}$ (note that the coefficient for that addition lies in $I$).
+
+Now we can assume that the first $2\ell-1$ entries of $v$ are unimodular and find $c_1,\ldots,c_{-2}\in I$ such that $c_1v_1+\ldots+c_{-2}v_{-2}=v_1-v_{-1}$.
+Add $c_{-i}v_i$ to $v_{-1}$, $i=2,\ldots,\ell$:
+\[ (v_1,v_2\ldots,v_\ell,v_{-\ell},\ldots,v_{-2},v_{-1})^t\longmapsto (v_1,v'_2\ldots,v'_\ell,v_{-\ell},\ldots,v_{-2},v'_{-1})^t. \]
+Then add $c_iv_i'=c_i(v_1+c_{-i}v_{-i})$, $i=2,\ldots,\ell$ to the last entry:
+\[ v_1\longmapsto v_1,\quad v'_{-1}\longmapsto v_{-1}+\sum_{i=2}^\ell c_{-i}v_{-i}+\sum_{i=2}^\ell c_i(v_i+c_{-i}v_1)=v''_{-1}. \]
+Next add $\left(c_1-\sum_{i=2}^\ell c_ic_{-i}\right)v_1$ to $v''_{-1}$ to get $v_1$ in position $-1$.
+Again, as in case of $\rA_n$, apply $z_\gamma(-v_1,1)$ with $\gamma=-\alpha_\mathrm{max}$, to get $1$ as the first entry and $0$ as the last.
+
+Now apply $2\ell-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum_{i=2}^\ell (v_i+v_{-i})$ to $v_{-1}$,
 so by one more transformation one can make the first column trivial. 

### 2015-04-28 bass-kolster.tex
BK small fixes

@@
 \begin{thm}\label{thm:BassKolster}
-Let $\Phi$ be a classical root system of rank $\geqslant2$, let $R$ be arbitary commutative ring and $I$ be an ideal, satisfying the following condition:
+Let $\Phi$ be a classical root system of rank $\geqslant2$, let $R$ be arbitary commutative ring and $I$ be an ideal, satisfying the following assumption:
 \begin{itemize}
@@
 \item $\Phi=\rB_\ell$: $\asr(R,I)\leqslant\ell-1$,
-\item $\Phi=\rC_\ell$: $\sr(I)\leqslant2\ell$,
+\item $\Phi=\rC_\ell$: $\sr(I)\leqslant2\ell-1$,
 \item $\Phi=\rD_\ell$: $\asr(R,I)\leqslant\ell-1$.
@@
 \[\G(\Phi,R,I)=\U(\Sigma^+,I)\ \U(\Sigma^-,I)\cdot \Z\cdot \U(\Sigma^-,I)\ \U(\Sigma^+,I)\cdot \G(\Delta,R,I), \]
-where $\Sigma^\pm=\Phi^\pm\setminus\Delta$ and $\Z=\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \}$.
+where $\Sigma^\pm=\Phi^\pm\setminus\Delta$ and $\Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \right\}$.
 \end{thm}

### 2015-04-29 stability-conditions.tex
Fixes to stability conditions

--- 2015-04-22 stability-conditions.tex
@@
 Clearly, for any $g\in\GL(n,R)$ one has $\mathfrak{J}(a\cdot g)=\mathfrak{J}(a)$.
-\begin{dfn}
-We say that a pair $(R,I)$ satisfies $\ASR_n(R,I)$ if it satisfies $\SR_n(R,I)$ and, moreover, 
-for any row $a=(a_1,\ldots,a_{n+1})\in I^n$ there exist $b_1,\ldots,b_n\in I$ such that
-\[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+b_1a_{n+1},\ldots,a_n+b_na_{n+1}).\]
-It is easy to see that $\ASR_m(R,I)$ implies $\ASR_n(R,I)$ for any $n\geqslant m$. 
-By definition, the \emph{absolute relative stable rank} $\asr(R,I)$ is the smallest natural $n$ such that $\ASR_n(R, I)$ holds. 
-Similarly, we set $\asr(R,I)=\infty$ if no such $n$ exists.
-When $I=R$ we call $\asr(R, R)$ simply the \emph{absolute stable rank} of $R$ and denote it by $\asr(R)$.
+%TODO: Think whether a more standard term could be used instead of ``J-stable''.
+\begin{dfn}\label{dfn:j-stable}
+We say that a row $a=(a_1,\ldots,a_{n+1})\in{}^{n+1}\!I$ is {\it $\mathfrak{J}$-stable}, if there exist $c_1,\ldots,c_n\in I$ such that
+$\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1},\ldots,a_n+c_na_{n+1}).$
 \end{dfn}
-The following reformulation of the absolute stable rank condition was noted by A.~Bak.
-\begin{lemma} For a commutative ring $R$ the following statements are equivalent:
+\begin{dfn}\label{dfn:asr}
+We say that an ideal $I$ satisfies condition $\ASR_n(I)$ if it satisfies $\SR_n(I)$ and, moreover, any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable.
+Below we will see that, as suggested by the notation, condition $\ASR_n(I)$ does not depend on the ambient ring $R$.
+
+It is easy to see that $\ASR_m(I)$ implies $\ASR_n(I)$ for any $n\geqslant m$. 
+By definition, the \emph{absolute relative stable rank} $\asr(I)$ is the smallest natural $n$ such that $\ASR_n(I)$ holds. 
+Similarly to the case of usual stable rank, we set $\asr(I)=\infty$ if no such $n$ exists.
+%Not needed:
+%When $I=R$ we call $\asr(R, R)$ simply the \emph{absolute stable rank} of $R$ and denote it by $\asr(R)$.
+\end{dfn}
+
+We will use use the following version of the relative absolute stable rank condition.
+\begin{lemma}\label{lemma:relative-asr-unimod}
+For a commutative ring $R$ and an ideal $I \leq R$ the following statements are equivalent:
 \begin{enumerate}
- \item\label{asr_Stein} $R$ satisfies $\ASR_n(R, R)$;
- \item\label{asr_Bak} For any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Ums(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for all $t\in R$.
+\item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable;
+\item\label{asr-bak-like} For any $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Ums(n+2,R,I)$ there exist $c_1,\ldots,c_n\in I$ 
+ such that $(b+b',a_1+c_1d,\ldots,a_n+c_nd)$ is $I$-unimodular for any $b'\in J$, where $J=\langle a_1,\ldots,a_n,d \rangle$.
 \end{enumerate}
@@
 \begin{proof}
-Assume first that $\ASR_n(R)$ holds.
-Then for the row $(a_1,\ldots,a_n,d)$ there exist $c_1,\ldots,c_n$ such that $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a_1+c_1d,\ldots,a_n+c_nd)$. 
-Therefore $a_1+c_1d,\ldots,a_n+c_nd$ together with $b$ generate the unit ideal.
-Of course, one could replace $b$ with $b+td$ from the very start.
+Assume first that any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable. 
+In particular for a given unimodular row $(b,a_1,\ldots,a_n,d)\in\Ums(n+2,R,I)$ there exist $c_1,\ldots,c_n$ such that
+\[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1},\ldots,a_n+c_na_{n+1}).\]
+Therefore $(b,a_1+c_1d,\ldots,a_n+c_nd)$ is also unimodular. Of course, for any $b'\in J$ one could replace $b$ with $b+b'$ from the very start.
 
-To show the converse take arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!R$ and consider the unimodular row $(a_1,\ldots,a_n,1,d)\in\Ums(n+2,R).$
-There exist $c_1,\ldots,c_n$ such that \[(a'_1,\ldots,a'_n,1+td)=(a_1+c_1d,\ldots,a_n+c_nd,1+td)\] is unimodular for all $t\in R$.
-Suppose that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that $a'_1,\ldots,a'_n\in\mathfrak{m}$ but at least one of the elements $d$, $a_i$ is not in $\mathfrak{m}$.
-Clearly, $d\notin\mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$ contrary to the assumption).
-On the other hand, $1+td\notin\mathfrak{m}$,
-hence the inequality $1+\bar{t}\bar{d}\neq0$ in the residue field $R/\mathfrak{m}$ may not hold for arbitrary $\bar{t}$ 
-(take e.g. $\bar{t}=-1/\bar{d}$).
-This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a_1,\ldots,a_n,d)=\mathfrak{J}(a'_1,\ldots,a'_n)$.
+To show the converse take arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!I$ and consider $I$-unimodular row $(1,a_1,\ldots,a_n,d)\in\Ums(n+2,R,I).$
+By hypothesis, there exist $c_1,\ldots,c_n$ such that \[ (1+b',a'_1,\ldots,a'_n)=(1+b',a_1+c_1d,\ldots,a_n+c_nd) \] is unimodular for any $b'\in J$.
+Assume that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that all $a'_1,\ldots,a'_n$ are contained in $\mathfrak{m}$
+ but at least one of the elements $d$, $a_i$ is not.
+Clearly then we must have $d\notin\mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$ contrary to the assumption).
+Notice that unimodularity condition implies that $1+b'\notin\mathfrak{m}$ for any $b'\in J$.
+
+Consider $t\in R$ such that its image $\bar{t}$ in the residue field $R/\mathfrak{m}$ equals $-1/\bar{d}$.
+Clearly $b'=t \cdot d \in J$ while $\bar{1} + \bar{b'} = \bar{0}$. Thus we arrive at a contradiction.
+This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a'_1,\ldots,a'_n)=\mathfrak{J}(a_1,\ldots,a_n,d)$.
 \end{proof}
+
+As a particular case of the above lemma we obtain the following equivalent reformulation of
+the absolute stable rank condition $\asr(R)$.
+\begin{cor}[A.~Bak, cf.~\cite{Pl98}] For a commutative ring $R$ the following statements are equivalent:
+\begin{enumerate}
+ \item\label{asr_Stein} $R$ satisfies $\ASR_n(R)$;
+ \item\label{asr_Bak} For any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Ums(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for all $t\in R$.
+\end{enumerate}
+\end{cor}
 

### 2015-04-29 stability-conditions.tex
Fixes in stability conditions

@@
 
-\subsection{Stable rank}
-Recall the definition of \emph{stable rank} introduced by H.~Bass and L.~Vaserstein (see~\cite{Ba64, Va69}).
-\begin{dfn} A row $a\in{}^n\!R$ is called \emph{$I$-unimodular} if it is congruent to $e_1$ modulo $I$ and its components $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal. \end{dfn}
-A column $b \in R^n$ will be called $I$-unimodular if its transpose $b^t$ is an $I$-unimodular row.
-We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n,R,I)$ (resp. $\Ums(n,R,I)$).
+\subsection{Relative stable rank}
+Throughout this subsection we recall basic definitions and notation pertaining to the concept of stable rank introduced by H.~Bass and L.~Vaserstein in 1960s (see~\cite{Ba64, Va69}).
+
+Recall that a row $a\in{}^n\!R$ is called \emph{$I$-unimodular} if it is congruent to $e_1$ modulo $I$ and its components $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal.
+A column $b \in R^n$ is called $I$-unimodular if its transpose $b^t$ is an $I$-unimodular row.
+We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n, I)$ (resp. $\Ums(n, I)$).
 When $R=I$ we refer to $R$-unimodular rows and columns as simply unimodular.
@@
 We say that $I$ satisfies stable range condition $\SR_n(I)$ if any $I$-unimodular row of length $n+1$ is stable.
-It is easy to see that $\SR_n(I)$ implies $\SR_m(I)$ for any $m\geqslant n$. It is also clear that validity of $\SR_n(I)$ does not depend on the ambient ring $R$.
-
-By definition, the {\it stable rank} of $I$ is the smallest natural $n$ such that $\SR_n(I)$ holds.
-We denote the stable rank of $I$ by $\sr(I)$, we set $\sr(I)=\infty$ if no such $n$ exists.
+It is easy to see that $\SR_n(I)$ implies $\SR_m(I)$ for any $m\geqslant n$. 
+It is also clear that condition $\SR_n(I)$ does not depend on the choice of ambient ring $R$.
+By definition, the {\it stable rank} of $I$ (denoted $\sr(I)$) is the smallest natural $n$ such that $\SR_n(I)$ holds (we set $\sr(I)=\infty$ if no such $n$ exists).
 
@@
 \begin{enumerate}
-\item For any ideal $J\subseteq I$ one has $\sr(R,I)\leqslant\sr(R)$, $\sr(R/J,I/J)\leqslant\sr(R,I)$.
+\item For any ideal $J\subseteq I$ one has $\sr(J)\leqslant\sr(I)$, $\sr(I/J)\leqslant\sr(I)$.
 \item One has $\sr\left(\prod\limits_{i=1}^n R_i\right)=\max\limits_{i=1}^n\left(\sr(R_i)\right).$
-\item Let $J$ denote the Jacobson radical of $R$, then one has $\sr(R)=\sr(R/J)$ and $\sr(R, J) = 1$.
+\item Let $J$ denote the Jacobson radical of $R$, then one has $\sr(R)=\sr(R/J)$.
 \end{enumerate}
 \end{prop}
-\begin{proof} See~\cite{Va71}, \cite[Theorem~2.3]{Va69}. 
-\textbf{TODO: Add reference for the latter fact}.
-%TODO:
+\begin{proof} See~\cite[Theorem~2.3]{Va69}, \cite{Va71}. 
 \end{proof}
@@
 
-\subsection{Absolute stable rank}
+\subsection{Relativization of absolute stable rank condition}
 For a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ denote by $\mathfrak{J}(a)$ the intersection of all maximal ideals of $R$ containing $a_1,\ldots,a_n$.
@@
 Clearly, for any $g\in\GL(n,R)$ one has $\mathfrak{J}(a\cdot g)=\mathfrak{J}(a)$.
-%TODO: Think whether a more standard term could be used instead of ``J-stable''.
 \begin{dfn}\label{dfn:j-stable}
@@
 We say that an ideal $I$ satisfies condition $\ASR_n(I)$ if it satisfies $\SR_n(I)$ and, moreover, any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable.
-Below we will see that, as suggested by the notation, condition $\ASR_n(I)$ does not depend on the ambient ring $R$.
+\end{dfn}
 
@@
 Similarly to the case of usual stable rank, we set $\asr(I)=\infty$ if no such $n$ exists.
-%Not needed:
-%When $I=R$ we call $\asr(R, R)$ simply the \emph{absolute stable rank} of $R$ and denote it by $\asr(R)$.
-\end{dfn}
 
-We will use use the following version of the relative absolute stable rank condition.
+A priori our definition of condition $\ASR_n(I)$ depends on the ambient ring $R$.
+Below we will see that, in fact, there is no such dependence.
 \begin{lemma}\label{lemma:relative-asr-unimod}
 For a commutative ring $R$ and an ideal $I \leq R$ the following statements are equivalent:
-\begin{enumerate}
-\item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable;
-\item\label{asr-bak-like} For any $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Ums(n+2,R,I)$ there exist $c_1,\ldots,c_n\in I$ 
- such that $(b+b',a_1+c_1d,\ldots,a_n+c_nd)$ is $I$-unimodular for any $b'\in J$, where $J=\langle a_1,\ldots,a_n,d \rangle$.
+\begin{enumerate} \item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable;
+\item\label{asr-bak-like} For any $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Umd(n+2,I)$ there exist $c_1,\ldots,c_n\in I$ 
+ such that $(b+b',a_1+c_1d,\ldots,a_n+c_nd)$ is $I$-unimodular for any $b'\in J$, where $J=I \cdot a_1 + \ldots + I \cdot a_n + I \cdot d\leq I$.
 \end{enumerate} 
@@
 Assume first that any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable. 
-In particular for a given unimodular row $(b,a_1,\ldots,a_n,d)\in\Ums(n+2,R,I)$ there exist $c_1,\ldots,c_n$ such that
+In particular for a given $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Umd(n+2,I)$ there exist $c_1,\ldots,c_n$ such that
 \[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1},\ldots,a_n+c_na_{n+1}).\]
-Therefore $(b,a_1+c_1d,\ldots,a_n+c_nd)$ is also unimodular. Of course, for any $b'\in J$ one could replace $b$ with $b+b'$ from the very start.
+Therefore $(b,a_1+c_1d,\ldots,a_n+c_nd)$ is also unimodular. Of course, for any $b'\in J$ we could replace $b$ with $b+b'$ from the very start.
 
-To show the converse take arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!I$ and consider $I$-unimodular row $(1,a_1,\ldots,a_n,d)\in\Ums(n+2,R,I).$
-By hypothesis, there exist $c_1,\ldots,c_n$ such that \[ (1+b',a'_1,\ldots,a'_n)=(1+b',a_1+c_1d,\ldots,a_n+c_nd) \] is unimodular for any $b'\in J$.
+To show the converse take arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!I$ and consider $I$-unimodular row $(1,a_1,\ldots,a_n,d)\in\Umd(n+2,I).$
+By hypothesis, there exist $c_1,\ldots,c_n$ such that \[ v=(1+b',a'_1,\ldots,a'_n)=(1+b',a_1+c_1d,\ldots,a_n+c_nd) \] is unimodular for any $b'\in J$.
 Assume that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that all $a'_1,\ldots,a'_n$ are contained in $\mathfrak{m}$
  but at least one of the elements $d$, $a_i$ is not.
-Clearly then we must have $d\notin\mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$ contrary to the assumption).
-Notice that unimodularity condition implies that $1+b'\notin\mathfrak{m}$ for any $b'\in J$.
-
-Consider $t\in R$ such that its image $\bar{t}$ in the residue field $R/\mathfrak{m}$ equals $-1/\bar{d}$.
-Clearly $b'=t \cdot d \in J$ while $\bar{1} + \bar{b'} = \bar{0}$. Thus we arrive at a contradiction.
+Clearly then $d\notin\mathfrak{m}$ and $I\not\subseteq \mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$ contrary to the assumption).
+Now we can find $t\in I$ such that its image $\bar{t}$ in the residue field $R/\mathfrak{m}$ equals $-\bar{1}/\bar{d}$.
+We get that $1 + b' \in \mathfrak{m}$ for $b'=td\in J$ which contradicts unimodularity of $v$.
 This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a'_1,\ldots,a'_n)=\mathfrak{J}(a_1,\ldots,a_n,d)$.
@@
 
-As a particular case of the above lemma we obtain the following equivalent reformulation of
-the absolute stable rank condition $\asr(R)$.
-\begin{cor}[A.~Bak, cf.~\cite{Pl98}] For a commutative ring $R$ the following statements are equivalent:
+Obviously, the second statement of Lemma~\ref{lemma:relative-asr-unimod} does not depend on $R$, hence, as suggested by the notation, $\asr(I)$ is independent of $R$.
+As another corollary of Lemma~\ref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$ (cf.~\cite[\S~1]{Pl98}).
+\begin{cor}[A.~Bak] For a commutative ring $R$ the following statements are equivalent:
 \begin{enumerate}
  \item\label{asr_Stein} $R$ satisfies $\ASR_n(R)$;
- \item\label{asr_Bak} For any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Ums(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for all $t\in R$.
+ \item\label{asr_Bak} For any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Umd(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for all $t\in R$.
 \end{enumerate}
@@
 
+\subsection{Action of unipotent radicals}
 The next lemma is an immediate consequence of the definition of stable rank.
-\begin{lemma}\label{lemma:srUnip} Let $v\in\Ums(n, R, I)$ be a unimodular column. Assume that $\sr(I)\leq n-m$ for some $1\leqslant m < n$.
-Then one can find a matrix $a\in \M(n-m,m,I)$ such that the column $(e_{n-m},a)v\in \Ums(n-m, R, I)$. \end{lemma}
+\begin{lemma}\label{lemma:srUnip} Let $v\in\Ums(n, I)$ be a unimodular column. Assume that $\sr(I)\leq n-m$ for some $1\leqslant m < n$.
+Then one can find a matrix $a\in \M(n-m,m,I)$ such that the column $(e_{n-m},a)v\in \Ums(n-m, I)$. \end{lemma}
 
@@
 By Proposition~\ref{prop:sr_properties} $\sr(I/J) \leq \ell-1$ and therefore
-the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, R/J, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
+the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
 This implies existence of $h\in \E(\Delta_\ell, R, I)$ such that for $v' = h \cdot v$ one has $(v')^+ \equiv e_1$ modulo $J$.

### 2015-04-30 bass-kolster.tex
Rewritten BK and stability conditions

--- 2015-04-28 bass-kolster.tex
@@
 \begin{thm}\label{thm:BassKolster}
-Let $\Phi$ be a classical root system of rank $\geqslant2$, let $R$ be arbitary commutative ring and $I$ be an ideal, satisfying the following condition:
-\begin{itemize}
-\item $\Phi=\rA_\ell$: $\sr(I)\leqslant\ell$,
-\item $\Phi=\rB_\ell$: $\asr(R,I)\leqslant\ell-1$,
-\item $\Phi=\rC_\ell$: $\sr(I)\leqslant2\ell$,
-\item $\Phi=\rD_\ell$: $\asr(R,I)\leqslant\ell-1$.
-\end{itemize}
-Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
-\[\G(\Phi,R,I)=\U(\Sigma^+,I)\ \U(\Sigma^-,I)\cdot \Z\cdot \U(\Sigma^-,I)\ \U(\Sigma^+,I)\cdot \G(\Delta,R,I), \]
-where $\Sigma^\pm=\Phi^\pm\setminus\Delta$ and $\Z=\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \}$.
+Let $\Phi$ be a classical root system of rank $\ell\geqslant2$, let $R$ be arbitary commutative ring and $I$ be an ideal, satisfying one of the following assumptions:
+\newline \indent \begin{tabular}{l l l}      
+\textbullet & $\Phi = \rA_\ell$, $\ell\geq 2$, & $\sr(I) \leqslant \ell$; \\     
+\textbullet & $\Phi = \rB_\ell$, $\rD_\ell$ $\ell\geq 3$,  & $\asr(I) \leqslant \ell-1$; \\ 
+\textbullet & $\Phi = \rC_\ell$, $\ell\geq 2$, & $\sr(I) \leqslant 2\ell-1$; \\ 
+\end{tabular}
+
+\noindent Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
+\[\G(\Phi,R,I)=\U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I)\cdot \U(\Sigma_1^+,I)\cdot \Z\cdot \U(\Sigma_1^-,I)\cdot \U(\Sigma_1^+,I)\cdot \G(\Delta_1,R,I), \]
+where $\Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \right\}$.
 \end{thm}
 \begin{proof}
-Let $g$ be an element of $\G(\Phi, R, I)$ and $e_1$ be the highest weight vector of the standard vector representation of $\G(\Phi, R, I)$.
-It is clear that vector $v=g\cdot e_1$ is $I$-unimodular.
-%TODO: Mention Chevalley---Matsumoto lemma in the introduction
-In view of Chevalley---Matsumoto lemma it suffices to show that $\Z \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ contains an element $g$ whose matrix entry at position $(1,1)$ is equal to $1$.
+Let $g$ be an element of $\G(\Phi, R, I)$. It is clear that vector $v=g\cdot v^+$ is $I$-unimodular.
+In view of relative Chevalley---Matsumoto lemma it suffices to show that $\Z \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ contains an element $g$ whose matrix entry at position $(1,1)$ is equal to $1$.
 We will need to analyze several cases.
@@
 Denote $v=(1+r_1,r_2,\ldots,r_\ell,r_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
-One can add the last entry to the first $\ell$ with some coefficients from $I$ to make then form a unimodular column of length $\ell$.
+One can add the last entry to the first $\ell$ with some coefficients from $I$ to make them form a unimodular column of length $\ell$.
 Then $\ell$ lower transformations (with coefficients from $I$) can make the last entry equal $r_1$.
@@
 \end{multline*}
-Now $\ell-1$ lower transformations eliminates all the remaining entries in the first column, while $\ell$ more upper ones will make the first row trivial.
 
 \textsc{Case $\Phi=\rC_\ell$:}
-Denote $v=(v^+,v^-)^t\in\Ums(2\ell,R,I)$. Find $c_1,\ldots,c_{-2}\in I$ such that $(v_1+c_1v_{-1},\ldots,v_{-2}+c_{-2}v_{-1})=(v_1',\ldots,v_{-2}')$ is unimodular.
+Denote $v=(v^+,v^-)^t\in\Ums(2\ell,R,I)$. 
+Find $c_1,\ldots, c_\ell, c_{-\ell},\ldots, c_{-2}\in I$ such that $(v_1+c_1v_{-1},\ldots,v_{-2}+c_{-2}v_{-1})=(v_1',\ldots,v_{-2}')$ is $I$-unimodular.
 
@@
 Again, as in case of $\rA_n$, apply $z_\gamma(-v_1,1)$ with $\gamma=-\alpha_\mathrm{max}$, to get $1$ as the first entry and $0$ as the last.
-
-Now apply $2\ell-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum_{i=2}^\ell (v_i+v_{-i})$ to $v_{-1}$,
-so by one more transformation one can make the first column trivial. 
-The same can be done with the first row, so in total we used $8\ell-3$ transformations.
 
@@
 (clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ under the natural embedding $\rD_\ell\subseteq\rB_\ell$). \end{proof}
+
+\begin{rem} %TODO:
+\textbf{TODO: Calculate the exact number of $z_\alpha$'s involved in the decomposition}
+
+\textsc{$\Phi=\rA_\ell$}
+Now $\ell-1$ lower transformations eliminates all the remaining entries in the first column, while $\ell$ more upper ones will make the first row trivial.
+
+\textsc{$\Phi=\rC_\ell$}
+Now apply $2\ell-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum_{i=2}^\ell (v_i+v_{-i})$ to $v_{-1}$, 
+so by one more transformation one can make the first column trivial. 
+The same can be done with the first row, so in total we used $8\ell-3$ transformations.
+
+\end{rem}

### 2015-04-30 dennis-vaserstein.tex
Rewritten BK and stability conditions

@@
 \begin{thm}\label{theorem:relative_dv}
-The relative elementary subgroup $\E(\Phi, R, I)$ coincides with $A_{rs}$ under the following assumptions on $(R, I)$.
-  \begin{center}
-    \begin{tabular}{| l | l | l | l | l |} \hline
-    № & $\Phi$ & $(s,r)$ & ring condition \\ \hline
-    1. & $\rA_\ell$, $\ell\geq 2$ & $(1, \ell)$ & $\sr(I) \leq \ell-1$ \\ \hline
-    2. & $\rB_\ell$, $\ell\geq 3$ & $(1, \ell)$ & $\sr(I) \leq \ell-1$ \\ \hline
-    3. & $\rD_\ell$, $\ell\geq 4$ & $(1, \ell)$ & $\sr(I) \leq \ell-2$ \\ \hline    
-    4. & $\rE_\ell$, $\ell=6,7$ & $(\ell, 2)$ & $\sr(I) \leq \ell-3$ \\ \hline     
-    5. & $\rE_\ell$, $\ell=6,7$ & $(\ell, 1)$ & $\asr(R, I)\leq \ell-2$ \\ \hline    
-    \end{tabular} \end{center} 
+The relative elementary subgroup $\E(\Phi, R, I)$ coincides with $A_{rs}$ under the following assumptions on $I$:
+\newline \indent \begin{tabular}{l l l l l l}      
+\textbullet & $\Phi = \rA_\ell$, $\rB_\ell$, $\ell\geq 2$ & $s = 1$, & $r = \ell$, & $\sr(I) \leq \ell-1$; \\     
+\textbullet & $\Phi = \rD_\ell$, $\ell\geq 4$, & $s=1$, & $r=\ell$, & $\sr(I) \leq \ell-2$; \\ 
+\textbullet & $\Phi = \rE_\ell$, $\ell=6,7$, & $s=\ell$, & $r=2$, & $\sr(I) \leq \ell-3$; \\ 
+\textbullet & $\Phi = \rE_\ell$, $\ell=6,7$, & $s=\ell$, & $r=1$, & $\asr(I)\leq \ell-2$. \\ 
+\end{tabular}
 \end{thm}
@@
 \begin{proof}[Proof of Theorem~\ref{theorem:relative_dv}]
-We first show that under specified assumptions on $(R, I)$ one can meet the conditions of Lemma~\ref{lemma:Stein_reduction}.
+We first show that under specified assumptions on $I$ one can meet the conditions of Lemma~\ref{lemma:Stein_reduction}.
 Consider the following two subsets of $\Lambda(\pi)$:

### 2015-04-30 paper.tex
Fixes in stability conditions
Rewritten BK and stability conditions

@@
 \end{array}$$
-In particular, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ and so on.
+For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ and so on.
 
@@
 In this situation it will be convenient for us to write $t_{\lambda_1,\lambda_2}(\xi)$ instead of $t_{\lambda_1-\lambda_2}(\xi)$.
-In particular, for $\Phi=\rA_\ell$ we have $t_{1,2}(\xi)=t_{1-2}(\xi)=t_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = t_{\alpha_1}(\xi)$. \end{rem}
+For example, for $\Phi=\rA_\ell$ we have $t_{1,2}(\xi)=t_{1-2}(\xi)=t_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = t_{\alpha_1}(\xi)$. \end{rem}
 
@@
 
-\section{Relative Bass---Kolster decomposition}\label{sec:bass-kolster}
+\section{Relative parabolic factorizations}
+\subsection{Relative Bass---Kolster decompositions}\label{sec:bass-kolster}
 \input{bass-kolster}
-
-\section{Relative Dennis-Vaserstein decompositions}\label{sec:dennis-vaserstein}
+\subsection{Relative Dennis-Vaserstein decompositions}\label{sec:dennis-vaserstein}
 \input{dennis-vaserstein}

### 2015-04-30 stability-conditions.tex
Rewritten BK and stability conditions

@@
 \begin{thm}
-Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets $X_1\ldots, X_m$ such that the topological dimension of every subset $X_i$ does not exceed some number $d$.
+Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets 
+$X_1\ldots, X_m$ such that the topological dimension of every subset $X_i$ does not exceed some number $d$. 
 Then $\asr(A)\leqslant d+1$.
 \end{thm}
+%TODO: Elaborate
 Clearly one has
-\[ \sr(R,I)\leqslant\asr(R,I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
+\[\sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
 
 \subsection{Action of unipotent radicals}
-The next lemma is an immediate consequence of the definition of stable rank.
-\begin{lemma}\label{lemma:srUnip} Let $v\in\Ums(n, I)$ be a unimodular column. Assume that $\sr(I)\leq n-m$ for some $1\leqslant m < n$.
-Then one can find a matrix $a\in \M(n-m,m,I)$ such that the column $(e_{n-m},a)v\in \Ums(n-m, I)$. \end{lemma}
-
 Let $v\in R^{2\ell}$ be a vector of the standard vector representation of $\G(\rD_\ell, R)$.
@@
 \begin{lemma} \label{lemma:uraction} 
-Let $\Phi=\rA_\ell, \rD_\ell$. Denote by $\pi$ standard vector representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1,2\ell$.
+Let $\Phi=\rA_\ell, \rD_\ell$. Denote by $\pi$ the standard vector representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1,2\ell$.
 Assume that one of the following conditions holds:
@@
  \item $\Phi=\rA_\ell$, $\Gamma=\{ k+1, \ldots, \ell+1\} \subset \Lambda(\pi)$ and $\sr(I)\leq k\leq \ell$;
- \item $\Phi=\rD_\ell$, $\Gamma=\{-l,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(R, I)\leq \ell-1$. 
+ \item $\Phi=\rD_\ell$, $\Gamma=\{-l,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(I)\leq \ell-1$. 
 \end{itemize}
-Then for any $I$-unimodular column $g\in \G(\Phi, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yxg \cdot v^+)_\lambda = 0$ for $\lambda\in \Gamma$.
+Then for $g\in \G(\Phi, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yxg \cdot v^+)_\lambda = 0$ for $\lambda\in \Gamma$.
 \end{lemma}
-\begin{proof}
-\textsc{Case $\Phi=\rA_\ell$.} \textbf{TODO: Write proof for this case.}
+\begin{proof} Denote by $v$ the image of the highest weight vector $v^+$ under $g$.
+
+\textsc{Case $\Phi=\rA_\ell$.} From the definition of the relative stable rank it follows that we can find 
+$x= \left(\begin{smallmatrix} e_k & a \\ * & e_{n-k} \end{smallmatrix}\right) \in \U(\Sigma_k^+, I)$ such that 
+the upper $k$ components of $v'= x \cdot v$ form an $I$-unimodular column. 
+Now, to obtain zeroes at desired positions it remains to subtract from $v'_{k+1},\ldots, v'_{\ell+1}$ suitable multiples of $v'_1,\ldots v'_k$.
+Clearly, this operation corresponds to the left multiplication by some element $y\in\U(\Sigma_k^-, I)$.
 

### 2015-05-01 bass-kolster.tex
BK for A_l, C_l fixes

@@
 Let $g$ be an element of $\G(\Phi, R, I)$. It is clear that vector $v=g\cdot v^+$ is $I$-unimodular.
-In view of relative Chevalley---Matsumoto lemma it suffices to show that $\Z \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ contains an element $g$ whose matrix entry at position $(1,1)$ is equal to $1$.
+In view of relative Chevalley---Matsumoto decomposition it suffices to show that $\Z \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ contains an element whose matrix entry at position $(1,1)$ is equal to $1$.
 We will need to analyze several cases.
@@
 \textsc{Case $\Phi=\rA_\ell$:}
-Denote $v=(1+r_1,r_2,\ldots,r_\ell,r_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
+Denote $v=(1+v_1,v_2,\ldots,v_\ell,v_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
 One can add the last entry to the first $\ell$ with some coefficients from $I$ to make them form a unimodular column of length $\ell$.
-Then $\ell$ lower transformations (with coefficients from $I$) can make the last entry equal $r_1$.
-Now apply $z_\gamma(-r_1,1)$, $\gamma=-\alpha_{\max}$:
+Then $\ell$ lower transformations (with coefficients from $I$) can make the last entry equal to $v_1$.
+Now apply $z_\gamma(-v_1,1)$, $\gamma=-\alpha_{\max}$:
 \begin{multline*}
-(1+r_1,r_2,\ldots,r_\ell,r_1)^t\xmapsto{x_{-\gamma}(-1)}(1,r_2,\ldots,r_\ell,r_1)^t\xmapsto{x_\gamma(-r_1)}\\\longmapsto(1,r_2,\ldots,r_\ell,0)^t\xmapsto{x_{-\gamma}(1)}(1,r_2,\ldots,r_\ell,0)^t.
+(1+v_1,v_2,\ldots,v_\ell,v_1)^t\xmapsto{x_{-\gamma}(-1)}(1,v_2,\ldots,v_\ell,v_1)^t\xmapsto{x_\gamma(-v_1)}\\\longmapsto(1,v_2,\ldots,v_\ell,0)^t\xmapsto{x_{-\gamma}(1)}(1,v_2,\ldots,v_\ell,0)^t.
 \end{multline*}
@@
 
-Now we can assume that the first $2\ell-1$ entries of $v$ are unimodular and find $c_1,\ldots,c_{-2}\in I$ such that $c_1v_1+\ldots+c_{-2}v_{-2}=v_1-v_{-1}$.
+Now we can assume that the first $2\ell-1$ entries of $v$ are unimodular and find $c_1,\ldots,c_{-2}\in I$ such that $c_1v_1+\ldots+c_{-2}v_{-2}=(v_1-1)-v_{-1}$.
 Add $c_{-i}v_i$ to $v_{-1}$, $i=2,\ldots,\ell$:
@@
 \[ v_1\longmapsto v_1,\quad v'_{-1}\longmapsto v_{-1}+\sum_{i=2}^\ell c_{-i}v_{-i}+\sum_{i=2}^\ell c_i(v_i+c_{-i}v_1)=v''_{-1}. \]
-Next add $\left(c_1-\sum_{i=2}^\ell c_ic_{-i}\right)v_1$ to $v''_{-1}$ to get $v_1$ in position $-1$.
-Again, as in case of $\rA_n$, apply $z_\gamma(-v_1,1)$ with $\gamma=-\alpha_\mathrm{max}$, to get $1$ as the first entry and $0$ as the last.
+Next add $\left(c_1-\sum_{i=2}^\ell c_ic_{-i}\right)v_1$ to $v''_{-1}$ to get $v_1-1$ in position $-1$.
+Again, as in case of $\rA_n$, apply $z_\gamma(1-v_1,1)$ with $\gamma=-\alpha_\mathrm{max}$, to get $1$ as the first entry and $0$ as the last.
 
 \textsc{Case $\Phi=\rD_\ell$.} 
-By Lemma~\ref{lemma:asrUnip} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'^+$ of vector $v'=h_1\cdot v$ is $I$-unimodular.
+By Lemma~\ref{lemma:asrUnip} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'^+$ of the vector $v'=h_1\cdot v$ is $I$-unimodular.
 Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, R, I)$, where
@@
 \textbf{TODO: Calculate the exact number of $z_\alpha$'s involved in the decomposition}
-
-\textsc{$\Phi=\rA_\ell$}
-Now $\ell-1$ lower transformations eliminates all the remaining entries in the first column, while $\ell$ more upper ones will make the first row trivial.
-
-\textsc{$\Phi=\rC_\ell$}
-Now apply $2\ell-2$ lower transformation to obtain zeroes on positions $i=2,\ldots,-2$, that will also add $\sum_{i=2}^\ell (v_i+v_{-i})$ to $v_{-1}$, 
-so by one more transformation one can make the first column trivial. 
-The same can be done with the first row, so in total we used $8\ell-3$ transformations.
-
 \end{rem}

### 2015-05-04 dennis-vaserstein.tex
Minor changes

@@
 From condition~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A$.
-Observe that from Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} it follows that
+Observe first that Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} imply
 \begin{multline}\nonumber 
@@
 \subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I). \end{multline}
-Applying Lemma~\ref{lemma:dv_unipotent} we get that:
+Now applying Lemma~\ref{lemma:dv_unipotent} we get the following inclusions:
 \begin{equation}\nonumber A^{X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq A. \end{equation}
@@
 
-From now on we can assume that the statement of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
+From now on we can assume that the conlcusion of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
 Notice that in view of Theorem~\ref{theorem:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:

### 2015-05-04 stability-conditions.tex
Minor changes

@@
-As we will be mainly concerned with applications to stability of $K_1$ of Chevalley groups, our treatment of stability conditions is restricted to the case of commutative $R$
-notwithstanding with the fact that the majority of constructions related to stable range conditions can be defined in a more general non-commutative setting (see e.g.~\cite{Ba64, Va69, Va71}).
+In this section we define stability conditions used in the statements of decomposition results from section~\ref{sec:factorizations}.
+First, we recall the notion of stable rank of a ring without unit introduced by L.~Vaserstein in~\cite{Va69, Va71}.
+As we are mainly concerned with Chevalley groups, our exposition of stable ranks is neccessarily limited to the case of a commutative ring.
+Our next goal is to define the relative version of the absolute stable rank condition which generalizes the definition of~\cite{EO, MKV}.
+In the end of this section we state several technical lemmas describing the action of certain unipotent radicals on unimodular columns under stability conditions.
 
 \subsection{Relative stable rank}
-Throughout this subsection we recall basic definitions and notation pertaining to the concept of stable rank introduced by H.~Bass and L.~Vaserstein in 1960s (see~\cite{Ba64, Va69}).
-
 Recall that a row $a\in{}^n\!R$ is called \emph{$I$-unimodular} if it is congruent to $e_1$ modulo $I$ and its components $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal.
@@
 It is easy to see that $\SR_n(I)$ implies $\SR_m(I)$ for any $m\geqslant n$. 
-It is also clear that condition $\SR_n(I)$ does not depend on the choice of ambient ring $R$.
+It is also clear that condition $\SR_n(I)$ does not depend on the choice of the ambient ring $R$.
 By definition, the {\it stable rank} of $I$ (denoted $\sr(I)$) is the smallest natural $n$ such that $\SR_n(I)$ holds (we set $\sr(I)=\infty$ if no such $n$ exists).
@@
 Since the stable rank of a field equals $1$, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$.
-Other examples of rings of stable rank $1$ are provided by boolean rings, the ring of algebraic integers, the ring of entire functions, the disk-algebra.
+Other examples of rings of stable rank $1$ are provided by boolean rings, the ring of algebraic integers, the ring of entire functions, the disk-algebra, etc.
 \end{example}
@@
 
-A priori our definition of condition $\ASR_n(I)$ depends on the ambient ring $R$.
+A priori our definition of condition $\ASR_n(I)$ depends on $R$.
 Below we will see that, in fact, there is no such dependence.

### 2015-05-06 bass-kolster.tex
Minor changes
Fixed statement of Bass-Kolster; improved treatment of representations

@@
 \textbullet & $\Phi = \rA_\ell$, $\ell\geq 2$, & $\sr(I) \leqslant \ell$; \\     
-\textbullet & $\Phi = \rB_\ell$, $\rD_\ell$ $\ell\geq 3$,  & $\asr(I) \leqslant \ell-1$; \\ 
 \textbullet & $\Phi = \rC_\ell$, $\ell\geq 2$, & $\sr(I) \leqslant 2\ell-1$; \\ 
-\end{tabular}
+\textbullet & $\Phi = \rB_\ell$, $\rD_\ell$ $\ell\geq 3$,  & $\asr(I) \leqslant \ell-1$. \end{tabular}
 
 \noindent Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
-\[\G(\Phi,R,I)=\U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I)\cdot \U(\Sigma_1^+,I)\cdot \Z\cdot \U(\Sigma_1^-,I)\cdot \U(\Sigma_1^+,I)\cdot \G(\Delta_1,R,I), \]
+\[\G(\Phi,R,I)=  \G(\Delta_1,R,I)\cdot \U(\Sigma_1^+,I)\cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I)\cdot\Z \cdot \U(\Phi^-,I)\cdot \U(\Phi^+,I), \]
 where $\Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \right\}$.
@@
 Let $g$ be an element of $\G(\Phi, R, I)$. It is clear that vector $v=g\cdot v^+$ is $I$-unimodular.
-In view of relative Chevalley---Matsumoto decomposition it suffices to show that $\Z \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ contains an element whose matrix entry at position $(1,1)$ is equal to $1$.
-We will need to analyze several cases.
+By relative Chevalley---Matsumoto lemma it suffices to show that the set $\Z \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ contains an element $h$ such that $\mu_1(h\cdot v^+)=1$, $\mu_{\varpi\ssub{1} - \alpha\ssub{max}}(h \cdot v^+)=0$.
+We find such $h$ by analyzing several cases.
 
 \textsc{Case $\Phi=\rA_\ell$:}
-Denote $v=(1+v_1,v_2,\ldots,v_\ell,v_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
+Set $v=(1+v_1,v_2,\ldots,v_\ell,v_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
 One can add the last entry to the first $\ell$ with some coefficients from $I$ to make them form a unimodular column of length $\ell$.

### 2015-05-06 paper.tex
Minor changes
Fixed statement of Bass-Kolster; improved treatment of representations

@@
 $n=\ell+1, 2\ell+1, 2\ell,2\ell$ for $\Phi=\rA_\ell,\rB_\ell,\rC_\ell,\rD_\ell$.
-The latter representations have dimension $n=27, 56, 248$ for $\ell=6,7,8$.
+The latter representations have dimension $n=27, 56$ for $\ell=6,7$.
 
-For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda(\pi)$ the set of weights of $\pi$.
-It will be convenient to use standard numbering for weights of representation $\pi$ in the case when $\Phi$ is classical and $\pi$ is a vector representation (cp.~\cite[§1B]{St78}):
+For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda(\pi)$ the set of weights of $\pi$ and by $V_\lambda$ the weight subspace corresponding to $\lambda\in\Lambda(\pi)$.
+For any of the representations described above (with the sole exception of $(\rE_8, \varpi_8)$) all weight subspaces $V_\lambda$ are one-dimensional. 
+This allows us to choose some basis $E_\pi=\{e_\lambda\}_{\lambda\in\Lambda(\pi)}$.
+
+It will be convenient to use standard numbering for the weights of natural representations of classical groups (cp.~\cite[§1B]{St78}):
 $$\begin{array}{cll}
@@
 
-In what follows we also assume that there is some basis $E=\{e_\lambda\}_{\lambda\in\Lambda(\pi)}$ fixed for every representation $V$.
-We denote by $v^+$ the basis vector corresponding to highest weight. 
-Using the the above notation for classical $\Phi$ we have $v^+=e_1$.
+For a weight $\lambda\in \Lambda(\pi)$ we denote by $\mu_{\lambda}\colon V\rightarrow R$ the coordinate function corresponding $\lambda$.
+In other words, $\mu_\lambda(v)$ is the coefficient of the basis vector $e_\lambda$ in the expansion of $v\in V$ in $E_\pi$.
+We denote by $v^+$ the basis vector corresponding to highest weight. Using the above notation for classical $\Phi$ we have $v^+=e_1$.
 %TODO: State Matsumoto lemma and Chevalley-Matsumoto lemma
@@
 
-\section{Relative parabolic factorizations}
+\section{Relative parabolic factorizations} \label{sec:factorizations}
 \subsection{Relative Bass---Kolster decompositions}\label{sec:bass-kolster}

### 2015-05-06 stability-conditions.tex
Fixed statement of Bass-Kolster; improved treatment of representations

@@
-In this section we define stability conditions used in the statements of decomposition results from section~\ref{sec:factorizations}.
-First, we recall the notion of stable rank of a ring without unit introduced by L.~Vaserstein in~\cite{Va69, Va71}.
-As we are mainly concerned with Chevalley groups, our exposition of stable ranks is neccessarily limited to the case of a commutative ring.
+In this section we define stability conditions used in the statements of our decomposition theorems from section~\ref{sec:factorizations}.
+First, we recall the notion of the stable rank of an ideal introduced by L.~Vaserstein in~\cite{Va69, Va71}.
+As we are mainly concerned with applications to Chevalley groups, our exposition of stable ranks is neccessarily limited to commutative rings.
 Our next goal is to define the relative version of the absolute stable rank condition which generalizes the definition of~\cite{EO, MKV}.

### 2015-05-06 bass-kolster.tex
Minor fixes

@@
 Let $g$ be an element of $\G(\Phi, R, I)$. It is clear that vector $v=g\cdot v^+$ is $I$-unimodular.
-By relative Chevalley---Matsumoto lemma it suffices to show that the set $\Z \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ contains an element $h$ such that $\mu_1(h\cdot v^+)=1$, $\mu_{\varpi\ssub{1} - \alpha\ssub{max}}(h \cdot v^+)=0$.
+First of all, notice that it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that $(g'\cdot v^+)_{1} = 1 + (g'\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}$.
+Indeed, multiplying 
+By relative Chevalley---Matsumoto lemma it suffices to show that the set $\Z \cdot  \cdot g$ contains an element $h$ such that
+$\mu_1(h\cdot v^+)=1$, $\mu_{\varpi\ssub{1} - \alpha\ssub{max}}(h \cdot v^+)=0$.
 We find such $h$ by analyzing several cases.

### 2015-05-06 paper.tex
Minor fixes

@@
 $$\begin{array}{cll}
-  1,2,\ldots, l+1 & \text{in the case} & \Phi =\rA_l, \\
-  1,2,\ldots l, 0, -\ell,\ldots, -2, -1 & \text{in the case} & \Phi =\rB_\ell, \\
-  1,2,\ldots l, -\ell,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
+  1,2,\ldots, \ell+1 & \text{in the case} & \Phi =\rA_\ell, \\
+  1,2,\ldots \ell, 0, -\ell,\ldots, -2, -1 & \text{in the case} & \Phi =\rB_\ell, \\
+  1,2,\ldots \ell, -\ell,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
 \end{array}$$
-For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ and so on.
+For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ etc.
 
-For a weight $\lambda\in \Lambda(\pi)$ we denote by $\mu_{\lambda}\colon V\rightarrow R$ the coordinate function corresponding $\lambda$.
-In other words, $\mu_\lambda(v)$ is the coefficient of the basis vector $e_\lambda$ in the expansion of $v\in V$ in $E_\pi$.
-We denote by $v^+$ the basis vector corresponding to highest weight. Using the above notation for classical $\Phi$ we have $v^+=e_1$.
+For a weight $\lambda\in \Lambda(\pi)$ we denote by $(-)_\lambda\colon V\rightarrow R$ the coordinate function corresponding to $\lambda$.
+In other words,  $v_\lambda$ is the coefficient of the basis vector $e_\lambda$ in the expansion of $v$ in $E_\pi$. 
+Obviously, $v=\sum_{\lambda\in \Lambda(\pi)} v_\lambda e_\lambda$.
+We denote by $v^+$ the basis vector corresponding to highest weight.
+For classical $\Phi$ we have $v^+=e_1$.
 %TODO: State Matsumoto lemma and Chevalley-Matsumoto lemma
@@
 \subsection{Elementary subgroup}
-Recall that elementary root unipotents $t_{\alpha}(\xi)$, $x\in R$, $\alpha\in\Phi$ satisfy the following set of relations called Steinberg relations.
+Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $t_{\alpha}(\xi)$ of $\G_sc(\Phi, R)$ called {\it elementary root unipotents}.
+These elements satisfy well-known Steinberg relations.
 \begin{equation}\label{rel:add} t_\alpha(s) t_\alpha(t) = t_\alpha(s+t), \end{equation} 
@@
 
-The following theorem is one of the main results of \cite{S} (see~\cite[Theorem~3.4]{S}).
+Let $I\leq R$ be an ideal. Denote by $\E(\Phi, I)$ the subgroup of $\G_{sc}(\Phi, R)$ generated by all elements $t_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$.
+In the case $I=R$ the subgroup $\E(\Phi, R)$ is called the {\it elementary subgroup} of the Chevalley group $\G_{sc}(\Phi, R)$.
+
+Denote by $z_\alpha(s, \xi)$ the element $x_\alpha(s)^{t\ssub{-\alpha}(\xi)}$.
+
+\begin{thm}[L.~Vaserstein, J.~Tits] The relative elementary subgroup $\E(\Phi, R, I)$ is generated by elements $z_\alpha(s, \xi)$, $\alpha\in \Phi$, $s\in I$, $\xi\in R$.
+\end{thm}
+
+In fact, one can choose a more economical set of generators for the elementary subgroup (see~\cite[Theorem~3.4]{S}).
 \begin{thm}\label{theorem:Stepanov}
@@
 \begin{itemize}
- \item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
+ \item $t_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
  \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$. \end{itemize} \end{thm}

### 2015-05-07 bass-kolster.tex
Improved exposition; fixed notational inconsistencies

--- 2015-05-06 bass-kolster.tex
@@
 \begin{proof}
-Let $g$ be an element of $\G(\Phi, R, I)$. It is clear that vector $v=g\cdot v^+$ is $I$-unimodular.
-By relative Chevalley---Matsumoto lemma it suffices to show that the set $\Z \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ contains an element $h$ such that $\mu_1(h\cdot v^+)=1$, $\mu_{\varpi\ssub{1} - \alpha\ssub{max}}(h \cdot v^+)=0$.
-We find such $h$ by analyzing several cases.
+Let $g$ be an element of $\G(\Phi, R, I)$. Set $v=g \cdot v^+\in\Ums(n, I)$.
 
-\textsc{Case $\Phi=\rA_\ell$:}
-Set $v=(1+v_1,v_2,\ldots,v_\ell,v_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
-One can add the last entry to the first $\ell$ with some coefficients from $I$ to make them form a unimodular column of length $\ell$.
-Then $\ell$ lower transformations (with coefficients from $I$) can make the last entry equal to $v_1$.
-Now apply $z_\gamma(-v_1,1)$, $\gamma=-\alpha_{\max}$:
-\begin{multline*}
-(1+v_1,v_2,\ldots,v_\ell,v_1)^t\xmapsto{x_{-\gamma}(-1)}(1,v_2,\ldots,v_\ell,v_1)^t\xmapsto{x_\gamma(-v_1)}\\\longmapsto(1,v_2,\ldots,v_\ell,0)^t\xmapsto{x_{-\gamma}(1)}(1,v_2,\ldots,v_\ell,0)^t.
-\end{multline*}
+First of all, notice that in each of the cases it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that 
+\begin{equation} \label{eq1} (g'\cdot v^+)_{1} = 1 + s \text{ and } (g'\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}} = s\ \text{for some}\ s\in I. \end{equation}
+Indeed, set $g'' = z_{-\alpha\ssub{max}}(-s, 1) \cdot g'$.
+Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}=0$ and the conclusion of the theorem follows from Lemma~\ref{lemma:Chevalley-Matsumoto}.
 
-\textsc{Case $\Phi=\rC_\ell$:}
-Denote $v=(v^+,v^-)^t\in\Ums(2\ell,R,I)$. 
-Find $c_1,\ldots, c_\ell, c_{-\ell},\ldots, c_{-2}\in I$ such that $(v_1+c_1v_{-1},\ldots,v_{-2}+c_{-2}v_{-1})=(v_1',\ldots,v_{-2}')$ is $I$-unimodular.
+\textsc{Case $\Phi=\rA_\ell$, $n=\ell + 1$:}
+%Set $v=(1+v_1,v_2,\ldots,v_\ell,v_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
+Thanks to the relative stable rank condition one can add suitable multiples of the last component $v_{\ell+1}$ to the first $\ell$ components of $v$ so that the upper $\ell$ coefficients of the resulting vector $v'$ form an $I$-unimodular column of length $\ell$.
+Then multiplying $v'$ by a suitable $y\in \U(\Sigma_\ell^-, I)$ we get the equalities of~\ref{eq1}.
+
+\textsc{Case $\Phi=\rC_\ell$, $n=2\ell$:}
+%TODO: Rewrite this.
+Subdivide $v\in V$ as in the beginning of section~\ref{sec:ur-action} i.e. $v = (v_+,v_-)^t\in\Ums(2\ell,R,I)$.
+
+Clearly, we can find $c_1,\ldots, c_\ell, c_{-\ell},\ldots, c_{-2}\in I$ such that 
+$(v_1+c_1v_{-1},\ldots,v_{-2}+c_{-2}v_{-1})=(v_1',\ldots,v_{-2}')$ is $I$-unimodular.
 
@@
 \textsc{Case $\Phi=\rD_\ell$.} 
-By Lemma~\ref{lemma:asrUnip} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'^+$ of the vector $v'=h_1\cdot v$ is $I$-unimodular.
-Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, R, I)$, where
+By Lemma~\ref{lemma:asrUnip} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of the vector $v'=h_1\cdot v$ is $I$-unimodular.
+Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
 $v''=h_2 \cdot t_{1,2}(c_1) \cdot v'$, $h_2=\prod\limits_{i=3}^\ell t_{i,2}(c_i)$.
@@
 Set $\xi = v''_1-v''_{-2}-1 \in I$, $h_3 = t_{1,-2}(\xi f_1) \cdot \prod\limits_{i=3}^\ell t_{i,-2}(\xi f_i)$, $v'''=h_3 \cdot v''$.
-Clearly, $v'''_{-2}=v'''_1-1$, therefore for $v_4 = z_{-\alpha_{max}}(-v'''_{-2}, 1) \cdot v'''$ one has $v^4_1 = 1$, as required.
-On the other hand, $t_{1,2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, while $ h_3 \cdot h_2 \in \U(\Phi^-, I)$.
+%Clearly, $v'''_{-2}=v'''_1-1$, therefore for $v_4 = z_{-\alpha_{max}}(-v'''_{-2}, 1) \cdot v'''$ one has $v^4_1 = 1$, as required.
+Clearly, $t_{1,2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, while $ h_3 \cdot h_2 \in \U(\Phi^-, I)$.
 
-\textsc{Case $\Phi=\rB_\ell$:} Subdivide $v\in \Ums(2\ell+1, R, I)$ as $v=(v^+, v_0, v^-)\in R^\ell\times R\times R^\ell$.
-Denote by $J\leq I$ the ideal spanned by components of $v^-$.
+\textsc{Case $\Phi=\rB_\ell$:} Subdivide $v\in \Ums(2\ell+1, R, I)$ as $v=(v_+, v_0, v_-)\in R^\ell\times R\times R^\ell$.
+Denote by $J\leq I$ the ideal spanned by components of $v_-$.
 Since $\sr(I/J)\leq l$ we can find $c_1,\dots,c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod\limits_{i=1}^\ell t_{0, i}(c_i) \in \U(\Phi^+, I)$
-one has $\bar{v'}^+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, R/J, I/J)$ and, therefore, $(v'^+, v'^-) \in \Ums(2\ell, R, I)$.
+one has $\bar{v'}_+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, R/J, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, R, I)$.
 Now one can finish the proof by repeating the argument for the case $\Phi=\rD_l$.

### 2015-05-07 paper.tex
Improved exposition; fixed notational inconsistencies

@@
 
+%TODO: Rewrite this using better terminology.
 For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda(\pi)$ the set of weights of $\pi$ and by $V_\lambda$ the weight subspace corresponding to $\lambda\in\Lambda(\pi)$.
@@
 For a weight $\lambda\in \Lambda(\pi)$ we denote by $(-)_\lambda\colon V\rightarrow R$ the coordinate function corresponding to $\lambda$.
-In other words,  $v_\lambda$ is the coefficient of the basis vector $e_\lambda$ in the expansion of $v$ in $E_\pi$. 
-Obviously, $v=\sum_{\lambda\in \Lambda(\pi)} v_\lambda e_\lambda$.
+In other words,  $v_\lambda$ is the coefficient of the basis vector $e_\lambda$ in the expansion of $v$ in $E_\pi$, i.e. $v=\sum_{\lambda\in \Lambda(\pi)} v_\lambda e_\lambda$.
 We denote by $v^+$ the basis vector corresponding to highest weight.
 For classical $\Phi$ we have $v^+=e_1$.
-%TODO: State Matsumoto lemma and Chevalley-Matsumoto lemma
+
+The lemma is a relative version of the classical result sometimes called Chevalley---Matsumoto decomposition.
+%TODO: Recheck the statement of the lemma; finish the proof.
+\begin{lemma}\label{lemma:Chevalley-Matsumoto}
+Let $\pi$ be the fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
+Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then 
+$g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
+\end{lemma} \begin{proof}  For $I=R$ the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}). \end{proof}
 
 \subsection{Elementary subgroup}
-Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $t_{\alpha}(\xi)$ of $\G_sc(\Phi, R)$ called {\it elementary root unipotents}.
+Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $t_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
 These elements satisfy well-known Steinberg relations.
@@
 
-Let $I\leq R$ be an ideal. Denote by $\E(\Phi, I)$ the subgroup of $\G_{sc}(\Phi, R)$ generated by all elements $t_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$.
-In the case $I=R$ the subgroup $\E(\Phi, R)$ is called the {\it elementary subgroup} of the Chevalley group $\G_{sc}(\Phi, R)$.
+Let $I\leq R$ be an ideal. Denote by $\E(\Phi, I)$ the subgroup of $\G_{sc}(\Phi, R)$ generated by elementary root unipotents $t_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$.
+In the special case $I=R$ the subgroup $\E(\Phi, R)$ is called the {\it elementary subgroup} of the Chevalley group $\G_{sc}(\Phi, R)$.
+Taddei's theorem asserts that $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geq 2$.
 
-Denote by $z_\alpha(s, \xi)$ the element $x_\alpha(s)^{t\ssub{-\alpha}(\xi)}$.
+We denote by $\E(\Phi, R, I)$ the normal closure of $\E(\Phi, I)$ in $\E(\Phi, R)$, in other words $\E(\Phi, R, I) = \E(\Phi, I)^{\E(\Phi, R)}$.
+Denote by $z_\alpha(s, \xi)$ the element $t_\alpha(s)^{t\ssub{-\alpha}(\xi)}$.
+The following result of L.~Vaserstein and J.~Tits describes a set of generators of $\E(\Phi, R, I)$ (see e.\,g.~\cite[Theorem~2]{Va86}).
 
-\begin{thm}[L.~Vaserstein, J.~Tits] The relative elementary subgroup $\E(\Phi, R, I)$ is generated by elements $z_\alpha(s, \xi)$, $\alpha\in \Phi$, $s\in I$, $\xi\in R$.
+\begin{thm} Let $\Phi$ be an irreducible root system of rank $\geq 2$, then the relative elementary subgroup $\E(\Phi, R, I)$
+is generated by elements $z_\alpha(s, \xi)$, $\alpha\in \Phi$, $s\in I$, $\xi\in R$.
 \end{thm}
 
-In fact, one can choose a more economical set of generators for the elementary subgroup (see~\cite[Theorem~3.4]{S}).
+In fact, one can choose a more economical set of generators for $\E(\Phi, R, I)$ (see~\cite[Theorem~3.4]{S}).
 \begin{thm}\label{theorem:Stepanov}
-Let $\Phi$ be a reduced irreducible root system and let $S$ be any parabolic subset of roots of $\Phi$ with special part $\Sigma_S$.
+Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S$ be any parabolic subset of roots of $\Phi$ with special part $\Sigma_S$.
 Then $\E(\Phi, R, I)$ is generated by the following two families of elements:

### 2015-05-07 stability-conditions.tex
Improved exposition; fixed notational inconsistencies

@@
 First, we recall the notion of the stable rank of an ideal introduced by L.~Vaserstein in~\cite{Va69, Va71}.
-As we are mainly concerned with applications to Chevalley groups, our exposition of stable ranks is neccessarily limited to commutative rings.
-Our next goal is to define the relative version of the absolute stable rank condition which generalizes the definition of~\cite{EO, MKV}.
-In the end of this section we state several technical lemmas describing the action of certain unipotent radicals on unimodular columns under stability conditions.
+As we will be mainly concerned with applications to Chevalley groups, our exposition of stable ranks is neccessarily limited to commutative rings.
+The main goal of the subsection~\ref{sec:rel-asr} is to define the relative version of the absolute stable rank condition which generalizes the definition of~\cite{EO, MKV}.
+Finally, in the end of this section we state several technical lemmas describing the action of certain unipotent radicals on unimodular columns under stability conditions.
 
@@
 
-\subsection{Relativization of absolute stable rank condition}
+\subsection{Relative absolute stable rank}\label{sec:rel-asr}
 For a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ denote by $\mathfrak{J}(a)$ the intersection of all maximal ideals of $R$ containing $a_1,\ldots,a_n$.
@@
 \end{thm}
-%TODO: Elaborate
+%TODO: Add more comments?
 Clearly one has
@@
 
-\subsection{Action of unipotent radicals}
-Let $v\in R^{2\ell}$ be a vector of the standard vector representation of $\G(\rD_\ell, R)$.
-It will be convenient for us to denote by $v^+$ and $v^-$ the upper and lower halves of $v$ i.e. $v^+=(v_1,\ldots, v_\ell)^t$, $v^-=(v_{-\ell},\ldots, v_{-1})^t$.
+\subsection{Action of unipotent radicals}\label{sec:ur-action}
+Let $v\in V=R^{2\ell}$ be a vector of the natural representation of $\G(\rD_\ell, R)$.
+Denote by $v_+$ and $v_-$ the upper and the lower halves of $v$ i.e. $v_+=(v_1,\ldots, v_\ell)^t$, $v_-=(v_{-\ell},\ldots, v_{-1})^t$.
 \begin{lemma}\label{lemma:asrUnip}
- Let $\Phi=\rD_\ell$ and assume that $\asr(R, I)\leq \ell -1$. Then for any $I$-unimodular column $v=(v^+, v^-)^t\in\Ums(2\ell, R, I)$
- there exist $g\in\U(\Sigma^+_\ell, I)$ such that $(g \cdot v)^+ \in \Ums(\ell, R, I)$.
+ Let $\Phi=\rD_\ell$ and assume that $\asr(I)\leq \ell -1$. 
+ Then for any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$
+ there exist $g\in\U(\Sigma^+_\ell, I)$ such that $(g \cdot v)_+ \in \Ums(\ell, I)$.
 \end{lemma}
-\begin{proof} Denote by $J$ the ideal of $R$ spanned by entries of $v^-$. Clearly, $J \leq I$.
-By Proposition~\ref{prop:sr_properties} $\sr(I/J) \leq \ell-1$ and therefore
+\begin{proof} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \leq I$.
+By Proposition~\ref{prop:sr_properties} $\sr(I/J) \leq \ell-1$ therefore
 the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
-This implies existence of $h\in \E(\Delta_\ell, R, I)$ such that for $v' = h \cdot v$ one has $(v')^+ \equiv e_1$ modulo $J$.
+This implies existence of $h\in \E(\Delta_\ell, R, I)$ such that for $v' = h \cdot v$ and $i=1,\ldots, \ell$ one has $v'_i \equiv \delta_{i1} \mod J$.
 
-By hypothesis, we can find $c_2,\ldots, c_\ell\in I$ such that for $v''=v'\cdot \prod\limits_{i=2}^{\ell}t_{-1, -i}(c_i)$ one has
-$\mathfrak{J}(v''_{-\ell},\ldots, v''_{-2}) = \mathfrak{J}(v'^-)$. Clearly, $v''_1$ is still congruent to $1$ modulo $J$, therefore 
-$(v''_1, v''_{-\ell},\ldots, v''_{-1})$ is $I$-unimodular. Now, applying condition $\sr(I) \leq \ell-1$ once again we find
-$d_1,d_3,\ldots, d_{\ell}\in I$ such that for $v'''=t_{-2,1}(d_1) \cdot \prod\limits_{i=3}^{\ell} t_{-2,-i}(d_i) \cdot v''$
-the entries $(v'''_1, v'''_{-\ell},\ldots, v'''_{-3})$ form a $I$-unimodular column.
+Clearly, $(v'_1,v'_{-\ell},\ldots, v'_{-1})$ is $I$-unimodular.
+Applying statement~\ref{asr-bak-like} of Lemma~\ref{lemma:relative-asr-unimod} we find $c_2,\ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}t_{-i, -1}(c_i)\cdot v'$ one has
+$(v''_1, v''_{-\ell},\ldots, v''_{-2})\in\Ums(\ell+1, I)$.
+%$\mathfrak{J}(v''_{-\ell},\ldots, v''_{-2}) = \mathfrak{J}(v'^-)$. Clearly, $v''_1$ is still congruent to $1$ modulo $J$, therefore 
+%$(v''_1, v''_{-\ell},\ldots, v''_{-2})$ is $I$-unimodular. 
+Now, applying condition $\sr(I) \leq \ell-1$ once again we find
+$d_1,d_3,\ldots, d_{\ell}\in I$ such that the entries $(v'''_1, v'''_{-\ell},\ldots, v'''_{-3})$
+of $v'''=t_{-2,1}(d_1) \cdot \prod_{i=3}^{\ell} t_{-2,-i}(d_i) \cdot v''$ form a $I$-unimodular column.
 
-We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v'''_1+\sum\limits_{i=3}^\ell f_i v'''_{-i} = 1$.
-Set $\xi = v'''_1-v'''_2-1 \in I$, $v^4=t_{1,2}(\xi f_1) \cdot \prod\limits_{i=3}^\ell t_{-i,2}(\xi f_i) \cdot v'''$.
-Clearly $v^4_2 = v^4_1-1$, therefore $v^{4+}$ is $I$-unimodular.
+We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v'''_1+\sum_{i=3}^\ell f_i v'''_{-i} = 1$.
+Set $\xi = v'''_1-v'''_2-1 \in I$, $v^4=t_{1,2}(\xi f_1) \cdot \prod_{i=3}^\ell t_{-i,2}(\xi f_i) \cdot v'''$.
+Clearly $v^4_2 = v^4_1-1$, therefore $v^4_+$ is $I$-unimodular.
 Summarizing the above, we have found $g\in \EP_\ell(R, I)$ such that $v^4=g \cdot v$

### 2015-05-11 subsystem-factorizations.tex
Preliminary version for subsystem factorizations

One of the reasons to study parabolic factorizations is that they provide an easy way to obtain subsystem factorizations, that is a decomposition of a given Chevalley group into a product of some of its subsystem subgroups. Among such decompositions one is of particular interest, namely the $\rA_n$-factorization. Those, in turn, come in two denominations:
\begin{itemize}
\item $\SL_2$-factorizations, see~\cite{LiebNikShaSL2,VavKovSL2};
\item $\SL_n$-factorizations for $n$ submaximal, see~\cite{NikProdDecomp}.
\end{itemize}
The main result of \cite{NikProdDecomp} is the following
\begin{thm*}
Let $G$ be a classical Chevalley group of rank $n+1$ over a finite field. Then $G$ equals the product of at most $200$ conjugates of an $\SL_{n+1}$ subgroup.
\end{thm*}
The above theorem holds for the twisted classical groups as well.

\cite{NikProdDecomp} also contains a proof that over a field $\SL(n+1,F)$ is a product of four copies of $\SL(n,F)$. In fact, this is true for any Hermitian ring (for example, any PID qualifies).

The following lemma is a reformulation of Proposition~1 from \cite{NikProdDecomp}:
\begin{lemma}
Let $\Phi$ be a root system of rank $\ell$, $\Delta<\Phi$ an $\rA_{\ell-1}$-subsystem, $\Sigma\subset\Phi^+$ a closed set of positive roots and $\Psi_1,\ldots,\Psi_K\subset\Phi$ be sets of roots such that:
\begin{enumerate}
\item For any $\alpha\in\Delta^+$ and for any $i=1,\ldots,K$, the elementary root unipotent $x_\alpha$ does not commute with at most one of $x_\beta$, $\beta\in\Psi_i$;
\item $\Sigma\subset\Delta^++\bigcup_{i=1}^K\Psi_i$.
\end{enumerate} 
Then $\U(\Sigma)\subset\prod_{i=1}^{K}\left[\U(\Delta^+),a_i\right]$, where $a_i=\prod_{\beta\in\Psi_i}x_\beta(1)$.
\end{lemma}
Of course, each of the commutators in the statement of the Lemma can be written in the reversed order.

Now starting from a unitriangular factorization, one can express $\U(\Phi^\pm)=\U(\Delta^\pm)\U(\Sigma^\pm)$ for $\Sigma^\pm=\Phi^\pm\setminus\Delta$, then cover each of $\U(\Sigma^\pm)$ with a product of conjugates of $\U(\Delta^\pm)$, and put all the factors together.

However, one can start from a parabolic decomposition, which might already have a large $\rA_n$-factor, namely the Levi subgroup of a given parabolic.

Over a ring $R$ of stable rank $1$ one has a decomposition $\G(\Phi,R)=P_\alpha\U_\alpha^-P_\alpha$, where $\U_\alpha^-=\U(\Sigma_\alpha^-)$ is the unipotent radical of the parabolic subgroup $P_\alpha^-$. This follows immediately from the Gauss decomposition. Choosing $\alpha\in\Pi$ so that $\Delta=\Delta_\alpha$ is of type $\rA$, we find suitable $\Psi_1,\ldots,\Psi_K$ and see that $\G(\Phi,R)=\G(\Delta_\alpha)\U(\Sigma_\alpha)\U(\Sigma_\alpha^-)\U(\Sigma_\alpha)$ is a product of $1+3\cdot\lfloor K/2\rfloor+(K\bmod2)$ conjugated of $\G(\Delta_\alpha)$.

### 2015-05-12 bass-kolster.tex
Fixed Bass-Kolster

@@
 %Set $v=(1+v_1,v_2,\ldots,v_\ell,v_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
-Thanks to the relative stable rank condition one can add suitable multiples of the last component $v_{\ell+1}$ to the first $\ell$ components of $v$ so that the upper $\ell$ coefficients of the resulting vector $v'$ form an $I$-unimodular column of length $\ell$.
-Then multiplying $v'$ by a suitable $y\in \U(\Sigma_\ell^-, I)$ we get the equalities of~\ref{eq1}.
+Thanks to the relative stable rank condition one can add suitable multiples of the last component $v_{\ell+1}$ to the first $\ell$ components of $v$ so that the upper
+$\ell$ coefficients of the resulting vector $v'$ form an $I$-unimodular column of length $\ell$.
+Now multiplying $v'$ by a suitable $y\in \U(\Sigma_\ell^-, I)$ we obtain equalities~\ref{eq1}.
 
 \textsc{Case $\Phi=\rC_\ell$, $n=2\ell$:}
-%TODO: Rewrite this.
-Subdivide $v\in V$ as in the beginning of section~\ref{sec:ur-action} i.e. $v = (v_+,v_-)^t\in\Ums(2\ell,R,I)$.
+Notice that column $(v_1,\ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
+Applying condition $\sr(I)\leq 2\ell-1$ wes find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
+By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for $h_1 = t_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} t_{i,-1}(c_i) \in \U(\Sigma_\ell, I)$.
 
-Clearly, we can find $c_1,\ldots, c_\ell, c_{-\ell},\ldots, c_{-2}\in I$ such that 
-$(v_1+c_1v_{-1},\ldots,v_{-2}+c_{-2}v_{-1})=(v_1',\ldots,v_{-2}')$ is $I$-unimodular.
+We can find $f_1, f_2,\ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
+Set $\xi = v''_1-v''_{-1}-1 \in I$, $h_2 = \prod_{i=1}^{-2} t_{-1,i}(\xi \cdot f_i) \in \U(\Sigma_\ell, I)$.
+Now it is clear that $v'' = h_2 \cdot v'$ satisfies equalities~\ref{eq1}.
 
-First add $c_{-i}v_{-1}$ to $v_{-i}$ for $-i=-\ell,\ldots,-2$, this will also add something to $v_1$.
+%Now we can assume that the first $2\ell-1$ entries of $v$ are unimodular and find $c_1,\ldots,c_{-2}\in I$ such that $c_1v_1+\ldots+c_{-2}v_{-2}=(v_1-1)-v_{-1}$.
+Add $c_{-i}v_i$ to $v_{-1}$, $i=2,\ldots,\ell$:
+%\[ (v_1,v_2\ldots,v_\ell,v_{-\ell},\ldots,v_{-2},v_{-1})^t\longmapsto (v_1,v'_2\ldots,v'_\ell,v_{-\ell},\ldots,v_{-2},v'_{-1})^t. \]
+%Then add $c_iv_i'=c_i(v_1+c_{-i}v_{-i})$, $i=2,\ldots,\ell$ to the last entry:
+%\[ v_1\longmapsto v_1,\quad v'_{-1}\longmapsto v_{-1}+\sum_{i=2}^\ell c_{-i}v_{-i}+\sum_{i=2}^\ell c_i(v_i+c_{-i}v_1)=v''_{-1}. \]
+%Next add $\left(c_1-\sum_{i=2}^\ell c_ic_{-i}\right)v_1$ to $v''_{-1}$ to get $v_1-1$ in position $-1$.
+%Again, as in case of $\rA_n$, apply $z_\gamma(1-v_1,1)$ with $\gamma=-\alpha_\mathrm{max}$, to get $1$ as the first entry and $0$ as the last.
 
-Then add $c_iv_{-1}$ to $v_i$ for $i=2,\ldots,\ell$.
-So far we have made the entries from $i=2,\ldots,-2$ equal to $v_i+c_iv_{-1}$, and one more upper transformation (corresponding to the highest root) will make the first entry equal to $v_1+c_1v_{-1}$ (note that the coefficient for that addition lies in $I$).
+\textsc{Case $\Phi=\rD_\ell$, $n= 2\ell$.} 
+By Lemma~\ref{lemma:asrUnip} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of $v'=h_1 \cdot v$ is $I$-unimodular.
+Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
+$v''=h_2 \cdot t_{1,2}(c_1) \cdot v'$, $h_2=\prod_{i=3}^\ell t_{i,2}(c_i)$.
 
-Now we can assume that the first $2\ell-1$ entries of $v$ are unimodular and find $c_1,\ldots,c_{-2}\in I$ such that $c_1v_1+\ldots+c_{-2}v_{-2}=(v_1-1)-v_{-1}$.
-Add $c_{-i}v_i$ to $v_{-1}$, $i=2,\ldots,\ell$:
-\[ (v_1,v_2\ldots,v_\ell,v_{-\ell},\ldots,v_{-2},v_{-1})^t\longmapsto (v_1,v'_2\ldots,v'_\ell,v_{-\ell},\ldots,v_{-2},v'_{-1})^t. \]
-Then add $c_iv_i'=c_i(v_1+c_{-i}v_{-i})$, $i=2,\ldots,\ell$ to the last entry:
-\[ v_1\longmapsto v_1,\quad v'_{-1}\longmapsto v_{-1}+\sum_{i=2}^\ell c_{-i}v_{-i}+\sum_{i=2}^\ell c_i(v_i+c_{-i}v_1)=v''_{-1}. \]
-Next add $\left(c_1-\sum_{i=2}^\ell c_ic_{-i}\right)v_1$ to $v''_{-1}$ to get $v_1-1$ in position $-1$.
-Again, as in case of $\rA_n$, apply $z_\gamma(1-v_1,1)$ with $\gamma=-\alpha_\mathrm{max}$, to get $1$ as the first entry and $0$ as the last.
-
-\textsc{Case $\Phi=\rD_\ell$.} 
-By Lemma~\ref{lemma:asrUnip} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of the vector $v'=h_1\cdot v$ is $I$-unimodular.
-Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
-$v''=h_2 \cdot t_{1,2}(c_1) \cdot v'$, $h_2=\prod\limits_{i=3}^\ell t_{i,2}(c_i)$.
-
-We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v''_1+\sum\limits_{i=3}^\ell f_i v''_{i} = 1$.
-Set $\xi = v''_1-v''_{-2}-1 \in I$, $h_3 = t_{1,-2}(\xi f_1) \cdot \prod\limits_{i=3}^\ell t_{i,-2}(\xi f_i)$, $v'''=h_3 \cdot v''$.
+We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v''_1+\sum_{i=3}^\ell f_i v''_{i} = 1$.
+Set $\xi = v''_1-v''_{-2}-1 \in I$, $h_3 = t_{1,-2}(\xi f_1) \cdot \prod_{i=3}^\ell t_{i,-2}(\xi f_i)$, $v'''=h_3 \cdot v''$.
 %Clearly, $v'''_{-2}=v'''_1-1$, therefore for $v_4 = z_{-\alpha_{max}}(-v'''_{-2}, 1) \cdot v'''$ one has $v^4_1 = 1$, as required.
@@
 
-\textsc{Case $\Phi=\rB_\ell$:} Subdivide $v\in \Ums(2\ell+1, R, I)$ as $v=(v_+, v_0, v_-)\in R^\ell\times R\times R^\ell$.
+\textsc{Case $\Phi=\rB_\ell$, $n=2\ell+1$:} Subdivide $v\in \Ums(2\ell+1, I)$ as $v=(v_+, v_0, v_-)\in R^\ell\times R\times R^\ell$.
 Denote by $J\leq I$ the ideal spanned by components of $v_-$.
-Since $\sr(I/J)\leq l$ we can find $c_1,\dots,c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod\limits_{i=1}^\ell t_{0, i}(c_i) \in \U(\Phi^+, I)$
-one has $\bar{v'}_+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, R/J, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, R, I)$.
-Now one can finish the proof by repeating the argument for the case $\Phi=\rD_l$.
-(clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ under the natural embedding $\rD_\ell\subseteq\rB_\ell$). \end{proof}
+Since $\sr(I/J)\leq \ell$ we can find $c_1,\dots,c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell t_{i, 0}(c_i) \in \U(\Phi^+, I)$
+one has $\bar{v'}_+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, I)$.
+Now the proof can be finished by repeating the argument for the case $\Phi=\rD_l$ (applied to the subset of long roots of $\rB_\ell$).
+%(clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ under the natural embedding $\rD_\ell\subseteq\rB_\ell$). 
+\end{proof}
 

### 2015-05-12 dennis-vaserstein.tex
Improved exposition; fixed notational inconsistencies
Fixed Bass-Kolster

@@
 \begin{thm}\label{theorem:relative_dv}
-The relative elementary subgroup $\E(\Phi, R, I)$ coincides with $A_{rs}$ under the following assumptions on $I$:
-\newline \indent \begin{tabular}{l l l l l l}      
-\textbullet & $\Phi = \rA_\ell$, $\rB_\ell$, $\ell\geq 2$ & $s = 1$, & $r = \ell$, & $\sr(I) \leq \ell-1$; \\     
-\textbullet & $\Phi = \rD_\ell$, $\ell\geq 4$, & $s=1$, & $r=\ell$, & $\sr(I) \leq \ell-2$; \\ 
-\textbullet & $\Phi = \rE_\ell$, $\ell=6,7$, & $s=\ell$, & $r=2$, & $\sr(I) \leq \ell-3$; \\ 
-\textbullet & $\Phi = \rE_\ell$, $\ell=6,7$, & $s=\ell$, & $r=1$, & $\asr(I)\leq \ell-2$. \\ 
+The relative elementary subgroup $\E(\Phi, R, I)$ coincides with the subset $A_{rs}$ under the following assumptions on $I$:
+\newline \indent \begin{tabular}{l l l l l}
+\textbullet & $\Phi = \rA_\ell$, $\rB_\ell$, $\ell\geq 2$, & $(s, r)=(1, \ell)$, & $\sr(I) \leq \ell-1$; \\     
+\textbullet & $\Phi = \rD_\ell$, $\ell\geq 4$,             & $(s, r)=(1, \ell)$, & $\sr(I) \leq \ell-2$; \\ 
+\textbullet & $\Phi = \rE_\ell$, $\ell=6,7$,               & $(s, r)=(\ell, 2)$, & $\sr(I) \leq \ell-3$; \\ 
+\textbullet & $\Phi = \rE_\ell$, $\ell=6,7$,               & $(s, r)=(\ell, 1)$, & $\asr(I)\leq \ell-2$. \\ 
 \end{tabular}
@@
 
+%TODO: PICK AS L_r!!!
 Let $\widetilde{L_r}$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma_0$.

### 2015-05-12 stability-conditions.tex
Fixed Bass-Kolster

@@
 \begin{lemma} \label{lemma:uraction} 
-Let $\Phi=\rA_\ell, \rD_\ell$. Denote by $\pi$ the standard vector representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1,2\ell$.
+Let $\Phi=\rA_\ell, \rD_\ell$. Denote by $\pi$ the natural representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1,2\ell$.
 Assume that one of the following conditions holds:
@@
  \item $\Phi=\rA_\ell$, $\Gamma=\{ k+1, \ldots, \ell+1\} \subset \Lambda(\pi)$ and $\sr(I)\leq k\leq \ell$;
- \item $\Phi=\rD_\ell$, $\Gamma=\{-l,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(I)\leq \ell-1$. 
+ \item $\Phi=\rD_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(I)\leq \ell-1$. 
 \end{itemize}
@@
 
-\textsc{Case $\Phi=\rD_\ell$.} From the proof of Lemma~\ref{lemma:asrUnip} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=g\cdot v$ one has $v'_2=v'_1-1\in I$.
-Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$ and, therefore by Chevalley---Matsumoto lemma there exists $h_2 \in \U(\Phi^-, I)$ such that 
-$g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fix $v^+$.
-Using Levi decomposition we can rewrite $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
+\textsc{Case $\Phi=\rD_\ell$.} From the proof of Lemma~\ref{lemma:asrUnip} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.
+Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$ hence by Chevalley---Matsumoto lemma there exists $h_2 \in \U(\Phi^-, I)$ such that the element
+$g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fixes $v^+$. 
+Using Levi decomposition we can write $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
 It is clear that $x$, $y$ are the desired elements.

### 2015-05-13 bass-kolster.tex
Minor fixes

@@
+The next theorem is a relative version of the so called Bass---Kolster decomposition (cf.~\cite[Theorem~2.1]{St78}).
 \begin{thm}\label{thm:BassKolster}
@@
 \noindent Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
-\[\G(\Phi,R,I)=  \G(\Delta_1,R,I)\cdot \U(\Sigma_1^+,I)\cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I)\cdot\Z \cdot \U(\Phi^-,I)\cdot \U(\Phi^+,I), \]
+\[\G(\Phi,R,I)=  \G(\Delta_1,R,I)\cdot \U(\Sigma_1,I)\cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I)\cdot\Z \cdot \U(\Phi^-,I)\cdot \U(\Phi^+,I), \]
 where $\Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \right\}$.
@@
 \begin{proof}
+
 Let $g$ be an element of $\G(\Phi, R, I)$. Set $v=g \cdot v^+\in\Ums(n, I)$. 
-
-First of all, notice that in each of the cases it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that 
+Notice that in each of the cases it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that 
 \begin{equation} \label{eq1} (g'\cdot v^+)_{1} = 1 + s \text{ and } (g'\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}} = s\ \text{for some}\ s\in I. \end{equation}
@@
 Notice that column $(v_1,\ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
-Applying condition $\sr(I)\leq 2\ell-1$ wes find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
+Applying condition $\sr(I)\leq 2\ell-1$ we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
 By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for $h_1 = t_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} t_{i,-1}(c_i) \in \U(\Sigma_\ell, I)$.
@@
 We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v''_1+\sum_{i=3}^\ell f_i v''_{i} = 1$.
-Set $\xi = v''_1-v''_{-2}-1 \in I$, $h_3 = t_{1,-2}(\xi f_1) \cdot \prod_{i=3}^\ell t_{i,-2}(\xi f_i)$, $v'''=h_3 \cdot v''$.
+As before, set $\xi = v''_1-v''_{-2}-1 \in I$, $h_3 = t_{1,-2}(\xi f_1) \cdot \prod_{i=3}^\ell t_{i,-2}(\xi f_i)$, $v'''=h_3 \cdot v''$.
 %Clearly, $v'''_{-2}=v'''_1-1$, therefore for $v_4 = z_{-\alpha_{max}}(-v'''_{-2}, 1) \cdot v'''$ one has $v^4_1 = 1$, as required.
@@
 
-\begin{rem} %TODO:
-\textbf{TODO: Calculate the exact number of $z_\alpha$'s involved in the decomposition}
-\end{rem}
+Using standard elementary calculations we can decrease the number of elementary root unipotents involved in the decomposition of the previous theorem.
+
+\begin{cor}
+In the assumptions and notation of Theorem~\ref{thm:BassKolster} one can write
+\[\G(\Phi,R,I)=  \G(\Delta_1,R,I)\cdot \U(\Sigma_1,I)\cdot \U(\Sigma_1^-,I)\cdot\Z \cdot \U(\Sigma^-_1,I)\cdot \U(\Sigma_1, I).\]
+\end{cor}

### 2015-05-13 dennis-vaserstein.tex
Minor fixes

@@
 
-\begin{thm}\label{theorem:relative_dv}
+The main result of this subsection is the following theorem which is a relative analogue of Dennis---Vaserstein decomposition~\cite[Theorem~2.5]{St78}.
+
+\begin{thm}\label{thm:DennisVaserstein}
 The relative elementary subgroup $\E(\Phi, R, I)$ coincides with the subset $A_{rs}$ under the following assumptions on $I$:
@@
 \end{thm}
-The proof of Theorem~\ref{theorem:relative_dv} occupies the rest of this section.
+The proof of Theorem~\ref{thm:DennisVaserstein} occupies the rest of this section.
 
@@
 
-\begin{proof}[Proof of Theorem~\ref{theorem:relative_dv}]
+\begin{proof}[Proof of Theorem~\ref{thm:DennisVaserstein}]
 We first show that under specified assumptions on $I$ one can meet the conditions of Lemma~\ref{lemma:Stein_reduction}.

### 2015-05-13 paper.tex
Preliminary version for subsystem factorizations
Fixed Bass-Kolster
Minor fixes

@@
 \newtheorem{notation}[equation]{Notation}
+
+\newtheorem*{thm*}{Theorem}
+\newtheorem*{lemma*}{Lemma}
 
@@
 \section{Relative parabolic factorizations} \label{sec:factorizations}
+%TODO: Add references to works of Dennis, Bass, Vaserstein, Suslin etc.
+In this section we formulate and prove relative versions of decompositions from~\cite{St78} which will be our main technical tools throughout the next section.
+
 \subsection{Relative Bass---Kolster decompositions}\label{sec:bass-kolster}
 \input{bass-kolster}
-\subsection{Relative Dennis-Vaserstein decompositions}\label{sec:dennis-vaserstein}
+\subsection{Relative Dennis---Vaserstein decompositions}\label{sec:dennis-vaserstein}
 \input{dennis-vaserstein}
 
-\section{Bounded generation}\label{sec:boundgen}
+\section{Applications}\label{sec:applications}
+\subsection{Bounded generation}\label{sec:boundgen}
 \input{congrsubgr-boundgen}
+\subsection{Subsystem factorizations}\label{sec:subsysfact}
+\input{subsystem-factorizations}
 

### 2015-05-20 bass-kolster.tex
Fixed minor error

@@
 Applying condition $\sr(I)\leq 2\ell-1$ we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
-By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for $h_1 = t_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} t_{i,-1}(c_i) \in \U(\Sigma_\ell, I)$.
+By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for $h_1 = t_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} t_{i,-1}(c_i) \in \U(\Sigma_1, I)$.
 
 We can find $f_1, f_2,\ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
-Set $\xi = v''_1-v''_{-1}-1 \in I$, $h_2 = \prod_{i=1}^{-2} t_{-1,i}(\xi \cdot f_i) \in \U(\Sigma_\ell, I)$.
-Now it is clear that $v'' = h_2 \cdot v'$ satisfies equalities~\ref{eq1}.
+%TODO: Determine exact sign
+Set $\xi = v''_1-v''_{-1}-1 \in I$, $h_2 = t_{-1,1}(\xi f_1 \pm \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}) \cdot \prod_{i=2}^{-2} t_{-1,i}(\xi f_i) \in \U(\Sigma_1, I)$.
+Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\ref{eq1}.
 

### 2015-05-22 bass-kolster.tex
Minor fixes

@@
 \noindent Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
-\[\G(\Phi,R,I)=  \G(\Delta_1,R,I)\cdot \U(\Sigma_1,I)\cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I)\cdot\Z \cdot \U(\Phi^-,I)\cdot \U(\Phi^+,I), \]
+\[\G(\Phi,R,I)=  \U(\Phi^+,I) \cdot \U(\Phi^-,I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I)\]
 where $\Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \right\}$.
@@
 Applying condition $\sr(I)\leq 2\ell-1$ we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
-By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for $h_1 = t_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} t_{i,-1}(c_i) \in \U(\Sigma_1, I)$.
+By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for $h_1 = t_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} t_{i,-1}(c_i) \in \U(\Sigma_1^-, I)$.
 
@@
 
-Using standard elementary calculations we can decrease the number of elementary root unipotents involved in the decomposition of the previous theorem.
+We can estimate the number of elementary root unipotents involved in the decomposition of the previous theorem.
+\begin{lemma}
+In the assumptions and notation of Theorem~\ref{thm:BassKolster} one can write any element $g$ of 
+$\G(\Phi,R,I)$ as a product of an element of $\G(\Delta_1,R,I)$, element $z_{-\alpha}(s, 1)$ for some $s\in I$ and $n(\Phi)$ elementary unipotents $t_{\alpha_i}(s_i)$, where
+\begin{itemize}
+ \item $n(\rA_\ell)= 4 \ell -1$;
+ \item $n(\rC_\ell)= 8 \ell - 5$;
+ \item $n(\rD_\ell)= $
+\end{itemize}
 
-\begin{cor}
-In the assumptions and notation of Theorem~\ref{thm:BassKolster} one can write
-\[\G(\Phi,R,I)=  \G(\Delta_1,R,I)\cdot \U(\Sigma_1,I)\cdot \U(\Sigma_1^-,I)\cdot\Z \cdot \U(\Sigma^-_1,I)\cdot \U(\Sigma_1, I).\]
-\end{cor}
+\cdot \U(\Sigma_1,I)\cdot \U(\Sigma_1^-,I)\cdot\Z \cdot \U(\Sigma^-_1,I)\cdot \U(\Sigma_1, I).\]
+\end{lemma}

### 2015-05-22 bass-kolster.tex
Written effective bounds for Bass-Kolster

@@
 
-We can estimate the number of elementary root unipotents involved in the decomposition of the previous theorem.
-\begin{lemma}
-In the assumptions and notation of Theorem~\ref{thm:BassKolster} one can write any element $g$ of 
-$\G(\Phi,R,I)$ as a product of an element of $\G(\Delta_1,R,I)$, element $z_{-\alpha}(s, 1)$ for some $s\in I$ and $n(\Phi)$ elementary unipotents $t_{\alpha_i}(s_i)$, where
-\begin{itemize}
- \item $n(\rA_\ell)= 4 \ell -1$;
- \item $n(\rC_\ell)= 8 \ell - 5$;
- \item $n(\rD_\ell)= $
-\end{itemize}
+It is easy to see that the proof of the above theorem is effective and gives an estimate of the total number of elementary root unipotents involved in the decomposition.
+\begin{cor}
+In the assumptions and notation of Theorem~\ref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
+can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $n(\Phi)$ elementary root unipotents $t_{\alpha}(s)$ of level $I$, where
+$n(\rA_\ell)= 4 \ell - 1$, $n(\rB_\ell)= 8 \ell - 5$, $n(\rC_\ell)= 8 \ell - 5$, $n(\rD_\ell)= 8 \ell - 9$. \end{cor}
+\begin{proof}
+The estimates stated above can be obtain by careful analysis of the proof of the previous theorem.
+Moreover, the estimates for $\Phi=\rA_\ell, \rC_\ell$ are immediate.
+In the case $\Phi=\rD_\ell$ the proof of Theorem~\ref{thm:BassKolster} implies 
+\begin{multline}\nonumber
+\G(\Phi,R,I)=  \U(\Sigma_\ell,I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1,I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z  \cdot \\ \cdot \U(\Sigma_1^-,I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I).
+\end{multline}
+We can present an element $g$ of $\U(\Sigma_\ell, I)$ as a product of $g_1 \in \U((\Sigma_1 \cup \Sigma_2) \cap \Sigma_\ell)$ and $g_2\in \U(\Sigma_\ell\cap\Delta_1\cap\Delta_2)$.
+An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one) and therefore can be safely moved to the right.
+On the other hand, $g_1$ is a product of at most $2\ell-3$ elementary unipotents, while the width of $\U(\Sigma_1^\pm, I)$ and $\U(\Sigma_2^-\cap\Delta_1)$ in elementary unipotents does not exceed $2\ell-2$ and $2\ell-4$, respectively.
+Summing up these upper bounds we obtain
+$$n(\rD_\ell)\leq (2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9.$$
 
-\cdot \U(\Sigma_1,I)\cdot \U(\Sigma_1^-,I)\cdot\Z \cdot \U(\Sigma^-_1,I)\cdot \U(\Sigma_1, I).\]
-\end{lemma}
+The estimate for the case $\Phi=\rB_\ell$ can be obtained by a similar argument. \end{proof}

### 2015-05-23 bass-kolster.tex
Minor changes

@@
 \begin{proof}
-The estimates stated above can be obtain by careful analysis of the proof of the previous theorem.
-Moreover, the estimates for $\Phi=\rA_\ell, \rC_\ell$ are immediate.
-In the case $\Phi=\rD_\ell$ the proof of Theorem~\ref{thm:BassKolster} implies 
+The above estimates can be obtained by a careful analysis of the proof of the previous theorem.
+Cases $\Phi=\rA_\ell, \rC_\ell$ are immediate.
+In the case $\Phi=\rD_\ell$ the proof of Theorem~\ref{thm:BassKolster} implies that
 \begin{multline}\nonumber
-\G(\Phi,R,I)=  \U(\Sigma_\ell,I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1,I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z  \cdot \\ \cdot \U(\Sigma_1^-,I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I).
+\G(\Phi,R,I) =  \U(\Sigma_\ell,I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1,I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z  \cdot \\ \cdot \U(\Sigma_1^-,I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I).
 \end{multline}
@@
 Summing up these upper bounds we obtain
-$$n(\rD_\ell)\leq (2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9.$$
+$$n(\rD_\ell) = (2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9.$$
 
-The estimate for the case $\Phi=\rB_\ell$ can be obtained by a similar argument. \end{proof}
+The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}

### 2015-05-23 dennis-vaserstein.tex
Minor changes

@@
-Throughout the present section we denote by $\EP_s(R, I)$ the subgroup $\E(\Delta_s, R, I) \cdot \U(\Sigma_s, I)$, $1 \leq s \leq n$.
-%TODO: Add Levi decomposition to preliminaries
-%TODO: Introduce notation for U(S, R)
-Set $\EP_s := \EP_s(R, R) = \E(\Delta_s, R) \cdot \U(\Sigma_s, R)$.
-
 Let $\Phi$ be an irreducible root system of rank $\ell$.
@@
 
-From now on we can assume that the conlcusion of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
+From now on we can assume that the conclusion of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
 Notice that in view of Theorem~\ref{theorem:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:

### 2015-05-23 paper.tex
Minor changes

@@
 
-The lemma is a relative version of the classical result sometimes called Chevalley---Matsumoto decomposition.
+The following lemma is a relative version of the classical result sometimes called Chevalley---Matsumoto decomposition.
 %TODO: Recheck the statement of the lemma; finish the proof.
@@
 
+Set $\EP_s(R, I) = \E(\Delta_s, R, I) \cdot \U(\Sigma_s, I)$, $1 \leq s \leq n$.
+It is easy to see that $\EP_s(R, I)$ is a subgroup.
+ Throughout the present section we denote by
+%TODO: Add Levi decomposition to preliminaries
+%TODO: Introduce notation for U(S, R)
+Set $\EP_s := \EP_s(R, R) = \E(\Delta_s, R) \cdot \U(\Sigma_s, R)$.
+
 \section{Stability conditions}\label{sec:stability-conditions}

### 2015-05-24 bass-kolster.tex
Introduced some notation

@@
 \end{multline}
-We can present an element $g$ of $\U(\Sigma_\ell, I)$ as a product of $g_1 \in \U((\Sigma_1 \cup \Sigma_2) \cap \Sigma_\ell)$ and $g_2\in \U(\Sigma_\ell\cap\Delta_1\cap\Delta_2)$.
-An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one) and therefore can be safely moved to the right.
+We can present an element $g$ of $\U(\Sigma_\ell, I)$ as a product of $g_1 \in \U(\Sigma_{\{1,2\}} \cap \Sigma_\ell)$ and $g_2\in \U(\Delta_{\{1,2\}}\cap \Sigma_\ell)$.
+An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one) and therefore can be moved to the right-hand side of the formula.
 On the other hand, $g_1$ is a product of at most $2\ell-3$ elementary unipotents, while the width of $\U(\Sigma_1^\pm, I)$ and $\U(\Sigma_2^-\cap\Delta_1)$ in elementary unipotents does not exceed $2\ell-2$ and $2\ell-4$, respectively.

### 2015-05-24 paper.tex
Introduced some notation

--- 2015-05-13 paper.tex
@@
 \title{Relative parabolic factorizations of Chevalley groups}
-\keywords {Chevalley groups, relative subgroups, stability for $\K_1$. {\em Mathematical Subject Classification (2010):} 20G35, 19B14}
+\keywords {Chevalley groups, relative subgroups, stability for $\K_1$. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
 \author {Sergey Sinchuk, Andrei Smolensky}
@@
 Clearly, $\Delta_J$ is a reductive subset of roots while $\Sigma^\pm_J$ are special subsets.
+For two disjoint subsets $I, J\subseteq \Pi$ one has $\Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J$ while $\Delta_{I\cup J} = \Delta_I \cap \Delta_J$.
 
@@
 
+For a special subset of roots $S\subseteq \Phi$ we denote by $\U(S, I)$ the subgroup spanned by all $t_{\alpha}(s)$ for $s\in I$, $\alpha\in S$.
+The subgroup $\U(\Sigma_J, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I)$ is a subgroup. 
+The following two equalities will be referred to in the sequel as {\it Levi decomposition}: 
+$$\EP_J(R, I) = \U(\Sigma_J, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I).$$
+
 \section{Stability conditions}\label{sec:stability-conditions}

### 2015-05-24 dennis-vaserstein.tex
Fixed DV decomposition

@@
 The proof of Theorem~\ref{thm:DennisVaserstein} occupies the rest of this section.
-
 Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
@@
 Denote by $N_{rs}$ and $L_{rs}$ stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
-In other words $$N_{rs} = \{ g\in \E(\Phi, R) \mid g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \};\quad L_{rs}= \{ g\in \E(\Phi, R, I) \mid g \cdot A_{rs} \subseteq A_{rs} \}.$$
+$$N_{rs} = \{ g\in \E(\Phi, R) \mid g \cdot A_{rs} \cdot g^{-1} = A_{rs} \};\quad L_{rs}= \{ g\in \E(\Phi, R, I) \mid g \cdot A_{rs} = A_{rs} \}.$$
 
@@
 From condition~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A$.
-Observe first that Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} imply
+Observe first that Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} together imply
 \begin{multline}\nonumber 
@@
 It is also clear that $|\Gamma_0|=1$ for $\Phi=\rA_\ell, \rB_\ell$, $|\Gamma_0|=2$ for $\Phi=\rD_\ell$, $|\Gamma_0|=3$ for $\Phi=\rE_\ell$ and $r=2$.
-In the case $\Phi=\rE_\ell$, $r=2$ the subsystem $\Delta_r$ has type $\rD_{\ell-1}$ and $|\Gamma_0|=\ell-1$.
+In the case $\Phi=\rE_\ell$, $r=1$ the subsystem $\Delta_r$ has type $\rD_{\ell-1}$ and $|\Gamma_0|=\ell-1$.
 
@@
 $$ \U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} \cdot (yxg) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r}.$$
-To prove the second condition notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in\widetilde{L_r}$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ and, therefore,
+To prove the second condition notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in\widetilde{L_r}$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
 $$X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \E(\Delta_s, R, I) \subseteq \EP_s(R, I).$$
@@
 \item $x_{\beta}(s)$, $s \in I$, $\beta \in \Phi$. \end{itemize}
-Since $\EP_s \subseteq N_{rs}$ it suffices to check inclusions only for the second family of elements.
-We already know that $\U^+(\Phi, I) \subseteq L_{rs}$.
+Since $\EP_s \subseteq N_{rs}$ inclusions for the first family of elements follow from those for the second one.
+We already know that $\U(\Phi^+, I) \subseteq L_{rs}$ hence it only suffices to show $\U(\Phi^-, I) \subseteq L_{rs}$.
 
 Notice that the Weyl group $W(\Delta_s)$ acts transitively on $\Delta_s$, therefore in view of relation~\ref{rel:R3} the subgroup
-$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leq \EP_s$ acts transitively on the set of root subgroups $X_\alpha(I)$, $\alpha\in \Delta_s$.
-Since $X_{-\alpha\ssub{r}}(I) \subseteq L_{rs}$ we get that that $\U(\Delta_s \cap \Phi^-, I)\subseteq L_{rs}$.
+$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leq \EP_s$ acts transitively on the set of root subgroups $X_\alpha(I)$, $\alpha\in \Delta_s$
+and we get that that $\U(\Delta_s \cap \Phi^-, I)\subseteq L_{rs}$.
 
-Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$. Our assumptions on $\Phi$ guarantee that $m_s(\widetilde{\alpha})=1$, 
-and, consequently, every two roots $\alpha, \beta \in \Sigma^-_s$ have the same $s$-shape (i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
-By Lemma~\ref{lemma:abs} $W(\Delta_s)$ interchanges $\alpha$ and $\beta$ if their length is equal (which is the case if we assume additionally $\Phi\neq \rB_\ell$).
-Since $X_{\alpha\ssub{s}} \subseteq L_{rs}$ the argument similar to the one above implies $\U(\Sigma^-_s, I)\subseteq L_{rs}$.
+%Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$.
+By our assumptions on $\Phi$ we have $m_s(\alpha\ssub{\mathrm{max}})=1$ hence every two roots $\alpha, \beta \in \Sigma^-_s$ 
+have the same $s$-shape and
+%(i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
+hence by Lemma~\ref{lemma:abs} are interchanged under the action of $W(\Delta_s)$ if their length is equal. % $\alpha$ and $\beta$ if their length is equal.
+%By the same argument as above we get that $W(\Delta_s)$.
+Since $X_{\alpha\ssub{s}} \subseteq L_{rs}$ by the same argument as above we get $\U({\Sigma^-_s}^>, I)\subseteq L_{rs}$.
 This completes the proof of the theorem for $\Phi\neq \rB_\ell$.
-%TODO:
-\textbf{TODO: Finish the proof for $\Phi=\rB_\ell$.}
+
+In the case $\Phi=\rB_\ell$ we have to show additionally that $X_{-\alpha^<_{\mathrm{max}}}(I) \leq L_{rs}$, where $\alpha^<_{\mathrm{max}}$
+denotes the maximal short root of $\rB_\ell$.
+By Chevalley commutator formula we have:
+$$t_{-{\alpha^<_{\mathrm{max}}}}(s) = t_{-1,0}(s) = t_{1,-2}(s) \cdot {}^{t_{-2, 0}(1)}\!t_{-1,-2}(-s) \cdot t_{-1, 2}(\xi),\ s\in I.$$
+On the other hand, $t_{-2,0}(1) \in \EP_s$ while we have already shown $X_{-1,-2}(I), X_{-1, 2}(I) \subseteq L_{rs}$.
+This concludes the proof of the theorem.
 \end{proof}

### 2015-05-30 dennis-vaserstein.tex
Added some introduction and stated some theorems

@@
 %Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$.
-By our assumptions on $\Phi$ we have $m_s(\alpha\ssub{\mathrm{max}})=1$ hence every two roots $\alpha, \beta \in \Sigma^-_s$ 
+By our assumptions on $\Phi$ we have $m_s(\alpha\ssub{\mathrm{max}})=1$ hence every two roots $\alpha, \beta \in \Sigma^-_s$ of the same length
 have the same $s$-shape and
 %(i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
-hence by Lemma~\ref{lemma:abs} are interchanged under the action of $W(\Delta_s)$ if their length is equal. % $\alpha$ and $\beta$ if their length is equal.
+hence by Lemma~\ref{lemma:abs} are interchanged under the action of $W(\Delta_s)$. % $\alpha$ and $\beta$ if their length is equal.
 %By the same argument as above we get that $W(\Delta_s)$.
@@
 By Chevalley commutator formula we have:
-$$t_{-{\alpha^<_{\mathrm{max}}}}(s) = t_{-1,0}(s) = t_{1,-2}(s) \cdot {}^{t_{-2, 0}(1)}\!t_{-1,-2}(-s) \cdot t_{-1, 2}(\xi),\ s\in I.$$
+$$t_{-{\alpha^<_{\mathrm{max}}}}(s) = t_{-1,0}(s) = t_{1,-2}(s) \cdot t_{-1,-2}(-s)^{t_{-2, 0}(-1)} \cdot t_{-1, 2}(\xi),\ s\in I.$$
 On the other hand, $t_{-2,0}(1) \in \EP_s$ while we have already shown $X_{-1,-2}(I), X_{-1, 2}(I) \subseteq L_{rs}$.

### 2015-05-30 paper.tex
Added some introduction and stated some theorems

@@
 \DeclareMathOperator{\Spec}{Spec}
+\DeclareMathOperator{\Spin}{Spin}
 \DeclareMathOperator{\Stab}{Stab}
@@
 \section{Introduction}\label{sec:intro}
+Let $\Phi$ be a reduced irreducible root system.
+
+\begin{thm} Let $I$ be an ideal of a commutative ring $R$ such that
+\begin{itemize} \item either $\sr(I) = 1$;
+ \item or $R = p^{-1}\cdot \mathbb{Z}$ for some prime $p$. \end{itemize}
+In the latter case assume additionally that Generalized Riemann Hypothesis holds.
+Then for any $\Phi$ the length of the congruence subgroup $\G(\Phi, R, I)$ does not exceed $C_1|\Phi| + C_2$. \end{thm}
+%TODO: Write explicit estimate for C_1 and C_2.
+The theorem above generalizes one of the results of \cite{VavSmSuUnitrEng} where such bounds were obtained in the absolute case (i.e. when $I=R$).
+
+The next our main result concerns subsystem factorizations of Chevalley groups formulated in terms of submaximal subgroups of type $\rA_\ell$.
+The case when $R=I$ is a field this question was studied by N.~Nikolov in \cite{NikProdDecomp}. 
+\begin{thm*} Let $G$ be a classical Chevalley group (of normal or twisted type) of rank $n$ over a finite field.
+Then $G$ equals the product of at most $200$ conjugates of $\SL_n$. \end{thm*}
+
+It is also classically known that over arbitrary field $F$ the group $\SL(n+1, F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
+On the other hand, from the classical Dennis---Vaserstein theorem (see~\cite{Va69} and \cite[Lemma~2.1]{ST76})
+it follows that $\SL_{n+1}(R, I)$ is a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leq n-1$.
+Using another Dennis---Vaserstein type factorization we obtain the following result.
+\begin{thm} Assume that $\sr(I) = 2$ then the group $\Spin_{2\ell}(R, I)=\G_{sc}(\rD_\ell, R, I)$ is a product of at most $C$ copies of subgroups of type $\rA_{\ell-1}$. \end{thm}
+
+Another applications of parabolic factorizations developed in this paper are subsystem factorizations in terms of subgroups of type $\rA_1$.
+The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
+More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
+In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies similar factorization with $N=3|\Phi^+|$ factors for arbitrary field $F$.
+In fact, Gauss decomposition (see~\cite{Sm12}) implies similar factorization for the elementary subgroup $\E(\Phi, R)$ with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.
+
+\begin{thm} Let $I$ be an ideal of a commutative ring $R$ such that $\sr(R)\leq n$, where
+\begin{itemize}
+ \item $n=1$ and $\Phi$ is either classical or of type $\rE_\ell$;
+ \item $n=2, 3$ and $\Phi$ is simply laced.
+\end{itemize}
+Then $\G(\Phi, R, I)$ is a product of at most $q_{n}(\Phi)$ copies of $\SL_{n+1}(R, I)$, where each $q_{n}(\Phi)$, $n=1,2,3$ is a quadratic function of $\rk(\Phi)$ given in Table~XXX.
+\end{thm}
 

### 2015-05-31 paper.tex
Introduction extended

@@
 \DeclareMathOperator{\EP}{EP}
+\DeclareMathOperator{\Par}{P}
+\DeclareMathOperator{\B}{B}
 \DeclareMathOperator{\U}{U}
@@
 \section{Introduction}\label{sec:intro}
-Let $\Phi$ be a reduced irreducible root system.
+In the present paper we study parabolic decompositions of Chevalley groups and their principal congruence subgroups.
+By a parabolic decomposition we mean a decomposition of a group $G$ into a product of some of its subgroups, where the subgroups in question are either parabolic or related to those in some way (mostly the unipotent radicals or their parts).
+We are interested in the following three versions of parabolic factorizations:
+\begin{itemize}
+\item Bass---Kolster decomposition $\G(\Phi,R) = \Par_i\U_i^-\U_i\U_i^-$;
+\item Dennis---Vaserstein decomposition $\G(\Phi,R)=\Par_r\U_{rs}^-\Par_s$;
+\item Gauss decomposition $\E(\Phi,R)=\B\U^-U$.
+\end{itemize}
+%TODO: Insert some links to VIP's papers :)
 
+The interest for parabolic factorizations comes from the following two considerations.
+
+The first is related to the fact that over rings of small dimension there is a variety of well-known tools, such as Bruhat decomposition over fields, Gauss decomposition with prescribed semisimple part over local rings, short unitriangular factorizations, etc.
+For each particular analytic or arithmetic setting there is a specific decomposition theorem (Iwasawa, Cartan and Iwahori decompositions to mention a few).
+So while groups over small-dimensional rings enjoy plenty of useful factorizations, none of those generalize to rings of large dimension.
+An this is exactly where parabolic decompositions enter the scene, as they hold for groups over rings satisfying very mild conditions such as the stable rank.
+
+The second is that even for rings of small dimension parabolic factorizations prove useful for applications, see below.
+
+We prove the relative versions of the three decompositions listed above (here the word "relative" refers to the principal congruence subgroups).
+
+%TODO: Insert the statements of our decompositions
+
+The first applications is the problem of bounded generation, where we use Bass---Kolster and Gauss decompositions to reduce the problem to the groups of small rank, where one can do some straightforward calculations.
+We obtain the following two theorems.
 \begin{thm} Let $I$ be an ideal of a commutative ring $R$ such that
 \begin{itemize} \item either $\sr(I) = 1$;
- \item or $R = p^{-1}\cdot \mathbb{Z}$ for some prime $p$. \end{itemize}
+ \item or $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$. \end{itemize}
 In the latter case assume additionally that Generalized Riemann Hypothesis holds.
-Then for any $\Phi$ the length of the congruence subgroup $\G(\Phi, R, I)$ does not exceed $C_1|\Phi| + C_2$. \end{thm}
+Then for any $\Phi$ the with of the congruence subgroup $\G(\Phi, R, I)$ with respect to $z_\alpha$ does not exceed $C_1|\Phi| + C_2$. \end{thm}
 %TODO: Write explicit estimate for C_1 and C_2.
-The theorem above generalizes one of the results of \cite{VavSmSuUnitrEng} where such bounds were obtained in the absolute case (i.e. when $I=R$).
+The theorem above generalizes extends the results of \cite{VavSmSuUnitrEng}, where such bounds were obtained in the absolute case (i.e. when $I=R$).
+\begin{thm}
+Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type in some global field $k$ having a real embedding.
+If $\rk\Phi\geqslant2$, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to $z_\alpha$.
+\end{thm}
 
-The next our main result concerns subsystem factorizations of Chevalley groups formulated in terms of submaximal subgroups of type $\rA_\ell$.
+The second application concerns subsystem factorizations of Chevalley groups formulated in terms of submaximal subgroups of type $\rA_\ell$.
 The case when $R=I$ is a field this question was studied by N.~Nikolov in \cite{NikProdDecomp}. 
@@
 More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
-In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies similar factorization with $N=3|\Phi^+|$ factors for arbitrary field $F$.
+In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
 In fact, Gauss decomposition (see~\cite{Sm12}) implies similar factorization for the elementary subgroup $\E(\Phi, R)$ with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.

### 2015-06-04 gauss.tex
Relative Gauss decomposition

\begin{thm}
Assume that for every terminal subsystem $\Delta$ the corresponding relative elementary subgroup admits the following decomposition:
\[ \E(\Delta,R,I)=\Hh(\Delta,R,I)\U^+(\Delta,I)\ldots\U^\pm(\Delta,I) \]
with $N$ triangular factors. Then the ambient relative elementary subgroup admits a decomposition
\[ \E(\Phi,R,I)=\Hh(\Phi,R,I)\U^+(\Phi,I)\ldots\U^\pm(\Phi,I) \]
of the same length $N$.
\end{thm}
\begin{proof}
Consider a set $Y=\Hh(\Phi,R,I)\U^+(\Phi,I)\ldots\U^\pm(\Phi,I)$. To show that $Y=\E(\Phi,R,I)$ one has to show that
\begin{enumerate}
\item $XY\subseteq Y$ for some set $X$ that generates $E(\Phi,R,I)$ as a \emph{normal} subgroup of $\E(\Phi,R)$;
\item $Y^{\E(\Phi,R)}\subseteq Y$, so that $Y$ is indeed normalized by $E(\Phi,R)$.
\end{enumerate}
We will take $X=\left\{x_\alpha(\xi)\mid\alpha\in\Pi,\ \xi\in I \right\}$. The set $X^{\E(\Phi,R)}$ contains elements $x_\alpha(\xi)$ for all $\alpha\in\Phi$ (since every root is conjugated to a fundamental one under the action of Weyl group, and the torus normalizer is contained in $\E(\Phi,R)$). Therefore $\E(\Phi,I)\subseteq\langle X\rangle^{\E(\Phi,R)}$ Now obviously $XY\subseteq Y$, since $\Hh(\Phi,R,I)$ normalizes each of $\X_\alpha(I)$, and for any $\alpha\in\Phi^+$ one has $\X_\alpha(I)\in\U(\Phi,I)$.

As for the second part, we use the fact that $\E(\Phi,R)$ is generated by $\left\{x_\alpha(\xi)\mid\alpha\in\pm\Pi,\ \xi\in R\right\}$. Fix a root $\alpha\in\pm\Pi$. It falls into one of the terminal subsystems, say $\Delta$. We expand $Y$ as follows:
\[ Y=\Hh(\Phi,R,I)\cdot\U(\Delta,I)\ldots\U^\pm(\Delta,I)\cdot\U(\Sigma,I)\ldots\U^\pm(\Sigma,I). \]
Here $\Sigma=\Phi^+\setminus\Delta$. Now
\begin{multline*}
x_\alpha(\xi)\cdot Y\cdot x_\alpha(-\xi) = x_\alpha(\xi)\cdot\E(\Delta,R,I)\cdot\U(\Sigma,I)\ldots\U^\pm(\Sigma,I)\cdot x_\alpha(-\xi) =\\
= x_\alpha(\xi)\cdot\E(\Delta,R,I)\cdot x_\alpha(-\xi)\cdot\U(\Sigma,I)\ldots\U^\pm(\Sigma,I) = Y.\qedhere
\end{multline*}
\end{proof}

### 2015-06-04 gauss.tex
Theorem labeled

@@
-\begin{thm}
+\begin{thm}\label{thm:Gauss}
 Assume that for every terminal subsystem $\Delta$ the corresponding relative elementary subgroup admits the following decomposition:

### 2015-07-28 paper.tex
Relative Gauss decomposition
Rewritten the introduction

--- 2015-05-30 paper.tex
@@
 \documentclass[12pt]{amsart}
-\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac, amsthm, amsfonts, amstext}
-\usepackage{hyperref}
+\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac, amsthm, amsfonts, amstext, hyperref}
 \usepackage[utf8]{inputenc}
@@
 \DeclareMathOperator{\EP}{EP}
+\DeclareMathOperator{\Par}{P}
+\DeclareMathOperator{\B}{B}
+\DeclareMathOperator{\Hh}{H}
 \DeclareMathOperator{\U}{U}
@@
 \section{Introduction}\label{sec:intro}
-Let $\Phi$ be a reduced irreducible root system.
+Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system.
+Denote by $G=\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over $R$ and let $\E(\Phi, R)$ denote its elementary subgroup, 
+ i.\,e. the group generated by root unipotents $t_\alpha(\xi)$, $ $ see~\cite{VP, St78, S}.
+For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the relative Chevalley group (or the principal congruence subgroup) of level $I$, 
+i.\,e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection.
 
+The main goal of the present paper is to study parabolic factorizations of Chevalley groups and their analogues for principal congruence subgroups $\G(\Phi, R, I)$.
+By a parabolic factorization we mean a decomposition of $G$ into a product of several parabolic and unipotent subgroups.
+To be more specific, we study relative versions of the following three kinds of decompositions:
+\begin{itemize}
+\item Gauss decomposition i.\,e. decomposition of the form $\E(\Phi,R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup,
+      and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
+\item Bass---Kolster decomposition --- $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
+      $\Par_i$ is the maximal parabolic subgroup of $\G$ corresponding to $i$-th vertex of the Dynkin diagram of $\Phi$ and 
+      $\U_i$, $\U_i^-$ are the unipotent radicals associated with it;
+\item Dennis---Vaserstein decomposition --- $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$.
+\end{itemize}
+%TODO: Insert some links to VIP's papers :)
+
+There are two main reasons to study parabolic factorizations.
+Recall that a number of various factorizations of $\G$ are known over rings having small dimension.
+For example, Bruhat decomposition is the key instrument in the study of linear groups over fields, 
+ while Gauss decomposition and unitriangular factorizations are useful tools in the study of groups over local rings.
+Moreover, for each particular analytic or arithmetic setting there is a special decomposition theorem (Iwasawa, Cartan and Iwahori decompositions, to mention a few).
+Unfortunately, neither of these decompositions can be carried over to rings of higher dimension.
+The advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of a milder ring-theoretic assumption such as stable range condition.
+
+Another advantage of parabolic factorizations is that they prove useful in the study of asymptotical properties of Chevalley groups.
+The following theorem is the first such application. 
 \begin{thm} Let $I$ be an ideal of a commutative ring $R$ such that
 \begin{itemize} \item either $\sr(I) = 1$;
- \item or $R = p^{-1}\cdot \mathbb{Z}$ for some prime $p$. \end{itemize}
+ \item or $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$. \end{itemize}
 In the latter case assume additionally that Generalized Riemann Hypothesis holds.
-Then for any $\Phi$ the length of the congruence subgroup $\G(\Phi, R, I)$ does not exceed $C_1|\Phi| + C_2$. \end{thm}
-%TODO: Write explicit estimate for C_1 and C_2.
-The theorem above generalizes one of the results of \cite{VavSmSuUnitrEng} where such bounds were obtained in the absolute case (i.e. when $I=R$).
+Then for any $\Phi$ the width of the congruence subgroup $\G(\Phi, R, I)$ with respect to $z_\alpha$ does not exceed $C_1|\Phi| + C_2$. \end{thm}
+\noindent In the proof of the above theorem we use Bass---Kolster decomposition to reduce to the case $\Phi=\rA_1$ which then can be settled directly.
+Notice that the particular case $I=R$ of the above theorem was demonstrated in~\cite{VavSmSuUnitrEng}.
 
-The next our main result concerns subsystem factorizations of Chevalley groups formulated in terms of submaximal subgroups of type $\rA_\ell$.
+\begin{thm}
+Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type in some global field $k$ having a real embedding.
+If $\rk\Phi\geqslant2$, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to $z_\alpha$.
+\end{thm}
+
+The second application concerns subsystem factorizations of Chevalley groups formulated in terms of submaximal subgroups of type $\rA_\ell$.
 The case when $R=I$ is a field this question was studied by N.~Nikolov in \cite{NikProdDecomp}. 
@@
 Another applications of parabolic factorizations developed in this paper are subsystem factorizations in terms of subgroups of type $\rA_1$.
-The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
+The case of a finite field $R=F$ was settled by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
 More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
-In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies similar factorization with $N=3|\Phi^+|$ factors for arbitrary field $F$.
+In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
 In fact, Gauss decomposition (see~\cite{Sm12}) implies similar factorization for the elementary subgroup $\E(\Phi, R)$ with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.
@@
 \input{dennis-vaserstein}
+\subsection{Relative Gauss decomposition}\label{sec:gauss}
+\input{gauss}
 

### 2015-07-29 paper.tex
Small fixes in the introduction

@@
       and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
-\item Bass---Kolster decomposition --- $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
+\item Bass---Kolster decomposition $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
       $\Par_i$ is the maximal parabolic subgroup of $\G$ corresponding to $i$-th vertex of the Dynkin diagram of $\Phi$ and 
       $\U_i$, $\U_i^-$ are the unipotent radicals associated with it;
-\item Dennis---Vaserstein decomposition --- $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$.
+\item Dennis---Vaserstein decomposition $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$.
 \end{itemize}
@@
 Unfortunately, neither of these decompositions can be carried over to rings of higher dimension.
-The advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of a milder ring-theoretic assumption such as stable range condition.
+The advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of milder ring-theoretic assumptions such as the stable range condition.
 
@@
 \noindent In the proof of the above theorem we use Bass---Kolster decomposition to reduce to the case $\Phi=\rA_1$ which then can be settled directly.
-Notice that the particular case $I=R$ of the above theorem was demonstrated in~\cite{VavSmSuUnitrEng}.
+Notice that the particular case $I=R$ of the above theorem was demonstrated in~\cite{VavSmSuUnitrEng} (see also \cite{VseUnitrZ1p}).
 
@@
 Another applications of parabolic factorizations developed in this paper are subsystem factorizations in terms of subgroups of type $\rA_1$.
-The case of a finite field $R=F$ was settled by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
+The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
 More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
 In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
-In fact, Gauss decomposition (see~\cite{Sm12}) implies similar factorization for the elementary subgroup $\E(\Phi, R)$ with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.
+In fact, Gauss decomposition (see~\cite{Sm12}) implies a similar factorization for the elementary subgroup $\E(\Phi, R)$ with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.
 

### 2015-07-29 paper.tex
Small fixes in the "Chevalley group" section

@@
 
-In this paper we work with irreducible representations of Chevalley groups corresponding to the highest weight
-$\varpi_1$ (in the case of a classical $\Phi_l$) or $\varpi_l$ (in the case $\Phi_\ell=\rE_\ell$). 
-The former are the natural vector representations of classical groups acting on free modules $V=R^n$ of dimension 
-$n=\ell+1, 2\ell+1, 2\ell,2\ell$ for $\Phi=\rA_\ell,\rB_\ell,\rC_\ell,\rD_\ell$.
-The latter representations have dimension $n=27, 56$ for $\ell=6,7$.
+In this paper we work with the irreducible representations of Chevalley groups corresponding to the highest weight
+$\varpi_1$ (in the case of a classical $\Phi_\ell$) or $\varpi_\ell$ (in the case $\Phi_\ell=\rE_\ell$). 
+The former are the natural vector representations of the classical groups acting on the free modules $V=R^n$ of dimension 
+$n=\ell+1, 2\ell+1, 2\ell,2\ell$ for $\Phi=\rA_\ell,\rB_\ell,\rC_\ell,\rD_\ell$ respectively.
+The latter are the microweight representations of dimension $n=27, 56$ for $\ell=6,7$.
 
 %TODO: Rewrite this using better terminology.
-For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda(\pi)$ the set of weights of $\pi$ and by $V_\lambda$ the weight subspace corresponding to $\lambda\in\Lambda(\pi)$.
+For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $V_\lambda$ the weight subspace corresponding to $\lambda\in\Lambda$.
 For any of the representations described above (with the sole exception of $(\rE_8, \varpi_8)$) all weight subspaces $V_\lambda$ are one-dimensional. 
-This allows us to choose some basis $E_\pi=\{e_\lambda\}_{\lambda\in\Lambda(\pi)}$.
+This allows us to choose a basis $E_\pi=\{e_\lambda\}_{\lambda\in\Lambda}$.
 
-It will be convenient to use standard numbering for the weights of natural representations of classical groups (cp.~\cite[§1B]{St78}):
-$$\begin{array}{cll}
+It will be convenient to use the standard numbering for the weights of the natural representations of the classical groups (cp.~\cite[§1B]{St78}):
+\[\begin{array}{cll}
   1,2,\ldots, \ell+1 & \text{in the case} & \Phi =\rA_\ell, \\
@@
   1,2,\ldots \ell, -\ell,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
-\end{array}$$
+\end{array}\]
 For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ etc.
 
-For a weight $\lambda\in \Lambda(\pi)$ we denote by $(-)_\lambda\colon V\rightarrow R$ the coordinate function corresponding to $\lambda$.
-In other words,  $v_\lambda$ is the coefficient of the basis vector $e_\lambda$ in the expansion of $v$ in $E_\pi$, i.e. $v=\sum_{\lambda\in \Lambda(\pi)} v_\lambda e_\lambda$.
-We denote by $v^+$ the basis vector corresponding to highest weight.
+For a weight $\lambda\in \Lambda$ we denote by $(-)_\lambda\colon V\to R$ the coordinate function corresponding to $\lambda$.
+In other words,  $v_\lambda$ is the coefficient of the basis vector $e_\lambda$ in the expansion of $v$ in $E_\pi$, i.e. $v=\sum_{\lambda\in \Lambda} v_\lambda e_\lambda$.
+We denote by $v^+$ the basis vector corresponding to the highest weight.
 For classical $\Phi$ we have $v^+=e_1$.
@@
 \subsection{Elementary subgroup}
-Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $t_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
-These elements satisfy well-known Steinberg relations.
-\begin{equation}\label{rel:add} t_\alpha(s) t_\alpha(t) = t_\alpha(s+t), \end{equation} 
-\begin{equation}\label{rel:CCF} [t_\alpha(s),  t_\beta(t)] = \left(\prod\limits t_{i\alpha + j\beta}(N_{\alpha,\beta, i, j}s^i t^j)\right),\quad \alpha\neq-\beta, N_{\alpha, \beta, i, j}\in\mathbb{Z}.\end{equation}
+Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
+These elements satisfy the well-known Steinberg relations:
+\begin{equation}\label{rel:add}
+x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \end{equation} 
+\begin{equation}\label{rel:CCF}
+\left[x_\alpha(s),  x_\beta(t)\right] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}.
+\end{equation}
 The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
-The integers $N_{\alpha, \beta, i, j}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.
+The integers $N_{\alpha\beta ij}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.
 
-For $\xi\in R^*$ set $w_\alpha(\xi) := x_\alpha(\xi) x_{-\alpha}(-\xi^{-1}) x_{\alpha}(\xi).$
+For $\xi\in R^*$ set $w_\alpha(\xi) = x_\alpha(\xi) x_{-\alpha}(-\xi^{-1}) x_{\alpha}(\xi).$
 If $\rk(\Phi)\geq 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
-\begin{equation}\label{rel:R3} w_\alpha(\xi) t_{\beta}(s) w_\alpha(\xi)^{-1} =
-t_{\sigma\ssub{\alpha}\beta} (\eta_{\alpha, \beta}\xi^{-\langle\beta,\alpha \rangle} s),\ \xi,s\in R. \end{equation}
+\begin{equation}\label{rel:R3}
+w_\alpha(\xi) x_{\beta}(s) w_\alpha(\xi)^{-1} =
+x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\xi^{-\langle\beta,\alpha \rangle} s\right),\quad \xi,s\in R.
+\end{equation}
 where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S13]{VP} for more details on $\eta_{\alpha, \beta}$).
@@
 \begin{rem} Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
-In this situation it will be convenient for us to write $t_{\lambda_1,\lambda_2}(\xi)$ instead of $t_{\lambda_1-\lambda_2}(\xi)$.
-For example, for $\Phi=\rA_\ell$ we have $t_{1,2}(\xi)=t_{1-2}(\xi)=t_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = t_{\alpha_1}(\xi)$. \end{rem}
+In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
+For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$. \end{rem}
 
-Let $I\leq R$ be an ideal. Denote by $\E(\Phi, I)$ the subgroup of $\G_{sc}(\Phi, R)$ generated by elementary root unipotents $t_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$.
+Let $I\leq R$ be an ideal. Denote by $\E(\Phi, I)$ the subgroup of $\G_{sc}(\Phi, R)$ generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$.
 In the special case $I=R$ the subgroup $\E(\Phi, R)$ is called the {\it elementary subgroup} of the Chevalley group $\G_{sc}(\Phi, R)$.
-Taddei's theorem asserts that $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geq 2$.
+Taddei's theorem asserts that $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$.
 
 We denote by $\E(\Phi, R, I)$ the normal closure of $\E(\Phi, I)$ in $\E(\Phi, R)$, in other words $\E(\Phi, R, I) = \E(\Phi, I)^{\E(\Phi, R)}$.
-Denote by $z_\alpha(s, \xi)$ the element $t_\alpha(s)^{t\ssub{-\alpha}(\xi)}$.
+Denote by $z_\alpha(s, \xi)$ the element $x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$.
 The following result of L.~Vaserstein and J.~Tits describes a set of generators of $\E(\Phi, R, I)$ (see e.\,g.~\cite[Theorem~2]{Va86}).
@@
 \begin{thm} Let $\Phi$ be an irreducible root system of rank $\geq 2$, then the relative elementary subgroup $\E(\Phi, R, I)$
-is generated by elements $z_\alpha(s, \xi)$, $\alpha\in \Phi$, $s\in I$, $\xi\in R$.
+is generated by the elements $z_\alpha(s, \xi)$, $\alpha\in \Phi$, $s\in I$, $\xi\in R$.
 \end{thm}
@@
 \begin{thm}\label{theorem:Stepanov}
-Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S$ be any parabolic subset of roots of $\Phi$ with special part $\Sigma_S$.
-Then $\E(\Phi, R, I)$ is generated by the following two families of elements:
+Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S$ be any parabolic subset of roots of $\Phi$ with the special part $\Sigma_S$.
+Then $\E(\Phi, R, I)$ is generated by the union of the following two families of elements:
 \begin{itemize}
- \item $t_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
+ \item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
  \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$. \end{itemize} \end{thm}
 
-For a special subset of roots $S\subseteq \Phi$ we denote by $\U(S, I)$ the subgroup spanned by all $t_{\alpha}(s)$ for $s\in I$, $\alpha\in S$.
+For a special subset of roots $S\subseteq \Phi$ we denote by $\U(S, I)$ the subgroup spanned by all $x_{\alpha}(s)$ for $s\in I$, $\alpha\in S$.
 The subgroup $\U(\Sigma_J, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I)$ is a subgroup. 

### 2015-07-31 gauss.tex
Rewritten paragraph about Gauss decompositions

--- 2015-06-04 gauss.tex
@@
-\begin{thm}
-Assume that for every terminal subsystem $\Delta$ the corresponding relative elementary subgroup admits the following decomposition:
-\[ \E(\Delta,R,I)=\Hh(\Delta,R,I)\U^+(\Delta,I)\ldots\U^\pm(\Delta,I) \]
-with $N$ triangular factors. Then the ambient relative elementary subgroup admits a decomposition
-\[ \E(\Phi,R,I)=\Hh(\Phi,R,I)\U^+(\Phi,I)\ldots\U^\pm(\Phi,I) \]
-of the same length $N$.
+\begin{thm}\label{thm:Gauss}
+Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1, \Delta_\ell$ be
+two reductive subsystems of $\Phi$ corresponding to endnodes of the Dynkin diagram of $\Phi$.
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1,\ell$ admit unitriangular decomposition with $N$ triangular factors:
+\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I), i=1,\ell. \]
+Then the group $\E(\Phi, R, I)$ admits decomposition with the same number of factors:
+\begin{equation} \nonumber\E(\Phi, R, I) = \Hh(\Phi,R,I) \cdot \U(\Phi^+,I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm,I). \end{equation}
 \end{thm}
 \begin{proof}
-Consider a set $Y=\Hh(\Phi,R,I)\U^+(\Phi,I)\ldots\U^\pm(\Phi,I)$. To show that $Y=\E(\Phi,R,I)$ one has to show that
+Denote by $Y$ the product of subgroups in the right-hand side of the above equality.
+To show that $Y=\E(\Phi,R,I)$ it suffices to check that
 \begin{enumerate}
-\item $XY\subseteq Y$ for some set $X$ that generates $E(\Phi,R,I)$ as a \emph{normal} subgroup of $\E(\Phi,R)$;
-\item $Y^{\E(\Phi,R)}\subseteq Y$, so that $Y$ is indeed normalized by $E(\Phi,R)$.
+\item $Y$ is normalized by $\E(\Phi,R)$, i.\,e. $Y^{\E(\Phi,R)}\subseteq Y$;
+\item there exists a set $X$ generating $\E(\Phi,R,I)$ as a \emph{normal} subgroup of $\E(\Phi,R)$ such that $XY\subseteq Y$.
 \end{enumerate}
-We will take $X=\left\{x_\alpha(\xi)\mid\alpha\in\Pi,\ \xi\in I \right\}$.
-The set $X^{\E(\Phi,R)}$ contains elements $x_\alpha(\xi)$ for all $\alpha\in\Phi$ (since every root is conjugated to a fundamental one under the action of Weyl group, and the torus normalizer is contained in $\E(\Phi,R)$).
-Therefore $\E(\Phi,I)\subseteq\langle X\rangle^{\E(\Phi,R)}$ Now obviously $XY\subseteq Y$, since $\Hh(\Phi,R,I)$ normalizes each of $\X_\alpha(I)$, and for any $\alpha\in\Phi^+$ one has $\X_\alpha(I)\in\U(\Phi,I)$.
+To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for $\alpha\in \pm \Pi$, $\xi\in R$.
+Take any root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or $i=\ell$ and we can expand $Y$ as
+\[ Y=\Hh(\Phi,R,I) \cdot \U(\Delta_i^+,I) \cdot \ldots \cdot \U^\pm(\Delta_i,I) \cdot \U(\Sigma_i^+,I) \cdot \ldots \cdot \U(\Sigma_i^\pm,I). \]
+For every  $h \in \Hh(\Phi, R, I)$ one has $h^{x_\alpha(\xi)} = h \cdot x_\alpha(\xi)^h x_\alpha(-\xi) = h \cdot x_\alpha(s)$ for some $s\in I$, therefore by the assumption of the theorem
+\begin{multline*}
+Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi,R,I) \cdot X_{\alpha}(I) \cdot \E(\Delta_i,R,I)^{x_\alpha(\xi)} \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) =\\
+= \Hh(\Phi, R, I) \cdot \E(\Delta_i,R,I) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) = Y.
+\end{multline*}
 
-As for the second part, we use the fact that $\E(\Phi,R)$ is generated by $\left\{x_\alpha(\xi)\mid\alpha\in\pm\Pi,\ \xi\in R\right\}$.
-Fix a root $\alpha\in\pm\Pi$.
-It falls into one of the terminal subsystems, say $\Delta$.
-We expand $Y$ as follows:
-\[ Y=\Hh(\Phi,R,I)\cdot\U(\Delta,I)\ldots\U^\pm(\Delta,I)\cdot\U(\Sigma,I)\ldots\U^\pm(\Sigma,I). \]
-Here $\Sigma=\Phi^+\setminus\Delta$. Now
-\begin{multline*}
-x_\alpha(\xi)\cdot Y\cdot x_\alpha(-\xi) = x_\alpha(\xi)\cdot\E(\Delta,R,I)\cdot\U(\Sigma,I)\ldots\U^\pm(\Sigma,I)\cdot x_\alpha(-\xi) =\\
-= x_\alpha(\xi)\cdot\E(\Delta,R,I)\cdot x_\alpha(-\xi)\cdot\U(\Sigma,I)\ldots\U^\pm(\Sigma,I) = Y.\qedhere
-\end{multline*}
+Now set $X=\left\{x_\alpha(\xi)\mid\alpha\in\Pi,\ \xi\in I \right\}$. 
+Every root is a conjugate of a simple root under the action of $W(\Phi)$.
+Since $\E(\Phi,R)$ contains the normalizer of the torus, the set $X^{\E(\Phi,R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi)$, $\alpha\in\Phi, \xi\in I \rangle$.
+Finally, inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi,R,I)$ normalizes every root subgroup $X_\alpha(I)$.
+
 \end{proof}

### 2015-07-31 dennis-vaserstein.tex
Small fixes and formatting in DV

@@
 From Levi decomposition it follows that
-\begin{multline}\nonumber \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = 
-\U(\Sigma_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
-= \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s, I) = 
-\EP_r(R, I) \cdot \U(\Sigma^-_r\cap \Sigma^-_s, I) \cdot \EP_s(R, I). \end{multline}
+\begin{multline*}
+\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
+= \U(\Sigma_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \hspace{5em} \\
+\hspace{5em} = \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s, I) = \\
+= \EP_r(R, I) \cdot \U(\Sigma^-_r\cap \Sigma^-_s, I) \cdot \EP_s(R, I).
+\end{multline*}
 Denote by $A_{rs}$ any of the equal subsets from the previous formula.
@@
 The relative elementary subgroup $\E(\Phi, R, I)$ coincides with the subset $A_{rs}$ under the following assumptions on $I$:
-\newline \indent \begin{tabular}{l l l l l}
-\textbullet & $\Phi = \rA_\ell$, $\rB_\ell$, $\ell\geq 2$, & $(s, r)=(1, \ell)$, & $\sr(I) \leq \ell-1$; \\     
-\textbullet & $\Phi = \rD_\ell$, $\ell\geq 4$,             & $(s, r)=(1, \ell)$, & $\sr(I) \leq \ell-2$; \\ 
-\textbullet & $\Phi = \rE_\ell$, $\ell=6,7$,               & $(s, r)=(\ell, 2)$, & $\sr(I) \leq \ell-3$; \\ 
-\textbullet & $\Phi = \rE_\ell$, $\ell=6,7$,               & $(s, r)=(\ell, 1)$, & $\asr(I)\leq \ell-2$. \\ 
-\end{tabular}
+\[\begin{array}{l@{\quad}l@{\quad}l@{\quad}c}
+\Phi = \rA_\ell, \rB_\ell,\ \ell\geqslant 2, & (s, r)=(1, \ell), & \sr(I) \leqslant \ell-1; \\     
+\Phi = \rD_\ell,\ \ell\geqslant 4,           & (s, r)=(1, \ell), & \sr(I) \leqslant \ell-2; \\ 
+\Phi = \rE_\ell,\ \ell=6,7,             & (s, r)=(\ell, 2), & \sr(I) \leqslant \ell-3; \\ 
+\Phi = \rE_\ell,\ \ell=6,7,             & (s, r)=(\ell, 1), & \asr(I)\leqslant \ell-2.
+\end{array}\]
 \end{thm}
@@
 Denote by $N_{rs}$ and $L_{rs}$ stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
-$$N_{rs} = \{ g\in \E(\Phi, R) \mid g \cdot A_{rs} \cdot g^{-1} = A_{rs} \};\quad L_{rs}= \{ g\in \E(\Phi, R, I) \mid g \cdot A_{rs} = A_{rs} \}.$$
+\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} = A_{rs} \right\},\quad L_{rs}= \left\{ g\in \E(\Phi, R, I)\ \middle|\ g \cdot A_{rs} = A_{rs} \right\}. \]
 
@@
 
-\begin{lemma}\label{lemma:dv_unipotent} For any $1\leq i\leq n$ the following statements hold. \begin{enumerate} 
-\item $\U(\Phi^\pm, I) = X_{\pm\alpha\ssub{i}}(I)\cdot \U(\Phi^\pm\setminus\{\pm\alpha\ssub{i}\}, I) = \U(\Phi^\pm\setminus\{\pm\alpha\ssub{i}\}, I)\cdot X_{\pm\alpha\ssub{i}}(I).$
-\item For any $\xi\in R$ one has $\U(\Phi^\pm\setminus\{\alpha_i\}, I)^{x_{\mp\alpha\ssub{i}}(\xi)^{-1}} \subseteq \U(\Phi^\pm, I).$
-\item $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{i}}(I) \cdot X_{-\alpha\ssub{i}}(I)$.
-\end{enumerate} \end{lemma}
+\begin{lemma}\label{lemma:dv_unipotent}
+For any $1\leq i\leq n$ the following statements hold (together with their analogues for $\Phi^-$).
+\begin{enumerate} 
+\item $\U(\Phi^+, I) = \X_{\alpha\ssub{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I) = \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I)\cdot \X_{\alpha\ssub{i}}(I)$.
+\item For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha\ssub{i}}(\xi)} \subseteq \U(\Phi^+, I)$.
+\item $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot \X_{\alpha\ssub{i}}(I) \cdot \X_{-\alpha\ssub{i}}(I)$.
+\end{enumerate}
+\end{lemma}
 \begin{proof}
@@
  \item\label{stein_cond1} One has $\U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r}.$
- \item\label{stein_cond2} One has $X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \EP_s(R, I).$
+ \item\label{stein_cond2} One has $\X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \EP_s(R, I).$
 \end{enumerate}
-Then $X_{-\alpha_r}(I) \subseteq L_{rs}$ and $\EP_s \subseteq N_{rs}.$
+Then $\X_{-\alpha_r}(I) \subseteq L_{rs}$ and $\EP_s \subseteq N_{rs}.$
 \end{lemma}
 \begin{proof} Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(\Phi, R, I).$
-From condition~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A$.
+From assumption~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A$.
 Observe first that Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} together imply
-\begin{multline}\nonumber 
-A \subseteq \U(\Phi^+\setminus \{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\ 
-\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{r}}(I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\
+\begin{multline*}
+A \subseteq \U(\Phi^+\setminus \{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \X_{\alpha\ssub{r}}(I) \cdot \X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\ 
+\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \X_{\alpha\ssub{r}}(I) \cdot \X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\
 \subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I)  \cdot \EP_s(R, I) \subseteq \\
-\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I). \end{multline}
+\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I).
+\end{multline*}
 Now applying Lemma~\ref{lemma:dv_unipotent} we get the following inclusions:
-\begin{equation}\nonumber A^{X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq A. \end{equation}
-\begin{equation}\nonumber X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) = A. \end{equation}
-To prove the second part of the statement observe first that $\EP_s$ is generated by $X_{\alpha\ssub{i}}$ for $1\leq i\leq n$ and $X_{-\alpha\ssub{i}}$ for $i\neq s$.
+\begin{align*}
+& A^{\X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{\X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq A; \\
+& \X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot \X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) = A.
+\end{align*}
+To prove the second part of the statement observe first that $\EP_s$ is generated by $\X_{\alpha\ssub{i}}$ for $1\leqslant i\leqslant n$ and $\X_{-\alpha\ssub{i}}$ for $i\neq s$.
 %TODO: Find proper reference for this fact
-We have just shown that $X_{-\alpha_r}\subseteq N_{rs}$.
-On the other hand, inclusions $X_{\alpha\ssub{k}} \subseteq N_{rs}$ for $\ 1\leq k\leq \ell$ and $X_{-\alpha\ssub{k}} \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
+We have just shown that $\X_{-\alpha_r}\subseteq N_{rs}$.
+On the other hand, inclusions $\X_{\alpha\ssub{k}} \subseteq N_{rs}$ for $\ 1\leqslant k\leqslant \ell$ and $\X_{-\alpha\ssub{k}} \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
 \end{proof}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:DennisVaserstein}]
-We first show that under specified assumptions on $I$ one can meet the conditions of Lemma~\ref{lemma:Stein_reduction}.
+We first show that the assumed stability conditions on $I$ imply the assumptions of Lemma~\ref{lemma:Stein_reduction}.
 Consider the following two subsets of $\Lambda(\pi)$:
 $$\Gamma = \varpi_s- (\Sigma_s^+\cap \Delta_r),\quad \Gamma_0 = \{\lambda \in \Gamma \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$$
-Clearly, $\Gamma$ is the set of weights of an irreducible representation of $\G(\Delta_r, R)$ corresponding to the same highest weight $\varpi_s$.
+With the choice of $s$ as in the assumption, $\Gamma$ is the set of weights of an irreducible representation of $\G(\Delta_r, R)$ corresponding to the same highest weight $\varpi_s$.
 The subsystem $\Delta_r$ has type $\rA_{\ell-1}$ in all cases except the last one.
-It is also clear that $|\Gamma_0|=1$ for $\Phi=\rA_\ell, \rB_\ell$, $|\Gamma_0|=2$ for $\Phi=\rD_\ell$, $|\Gamma_0|=3$ for $\Phi=\rE_\ell$ and $r=2$.
-In the case $\Phi=\rE_\ell$, $r=1$ the subsystem $\Delta_r$ has type $\rD_{\ell-1}$ and $|\Gamma_0|=\ell-1$.
+It is also clear that $|\Gamma_0|=1$ for $\Phi=\rA_\ell, \rB_\ell$, $|\Gamma_0|=2$ for $\Phi=\rD_\ell$, and $|\Gamma_0|=3$ in case $\Phi=\rE_\ell$ and $r=2$.
+If $\Phi=\rE_\ell$, $r=1$, the subsystem $\Delta_r$ has type $\rD_{\ell-1}$ and $|\Gamma_0|=\ell-1$.
 
@@
 Let $\widetilde{L_r}$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma_0$.
-In any of specified cases the assumption on $(R, I)$ allows us to apply Lemma~\ref{lemma:uraction} to the subsystem $\Delta_r$ and find
+In any of  the specified cases the assumption on $I$ allows us to apply Lemma~\ref{lemma:uraction} to the subsystem $\Delta_r$ and find
 $x\in\U(\Delta_r\cap\Phi^+, I)$, $y\in \U(\Delta_r\cap\Phi^-, I)$ such that $yx\cdot g \in \widetilde{L_r}$.
 This proves the first condition of Lemma~\ref{lemma:Stein_reduction}, indeed:
-$$ \U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} \cdot (yxg) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r}.$$
-To prove the second condition notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in\widetilde{L_r}$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
-$$X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \E(\Delta_s, R, I) \subseteq \EP_s(R, I).$$
+\[ \U(\Sigma^+_r, I) \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \U(\Phi^-, I) \widetilde{L_r}. \]
+To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in\widetilde{L_r}$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
+\[ \X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \E(\Delta_s, R, I) \subseteq \EP_s(R, I). \]
 
@@
 \item $x_{\beta}(s)$, $s \in I$, $\beta \in \Phi$. \end{itemize}
-Since $\EP_s \subseteq N_{rs}$ inclusions for the first family of elements follow from those for the second one.
-We already know that $\U(\Phi^+, I) \subseteq L_{rs}$ hence it only suffices to show $\U(\Phi^-, I) \subseteq L_{rs}$.
+Since $\EP_s \subseteq N_{rs}$, the inclusions for the first family of elements follow from those for the second one.
+We already know that $\U(\Phi^+, I) \subseteq L_{rs}$, hence it only suffices to show $\U(\Phi^-, I) \subseteq L_{rs}$.
 
 Notice that the Weyl group $W(\Delta_s)$ acts transitively on $\Delta_s$, therefore in view of relation~\ref{rel:R3} the subgroup
-$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leq \EP_s$ acts transitively on the set of root subgroups $X_\alpha(I)$, $\alpha\in \Delta_s$
+$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leqslant \EP_s$ acts transitively on the set of root subgroups $\X_\alpha(I)$, $\alpha\in \Delta_s$
 and we get that that $\U(\Delta_s \cap \Phi^-, I)\subseteq L_{rs}$.
@@
 %Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$.
-By our assumptions on $\Phi$ we have $m_s(\alpha\ssub{\mathrm{max}})=1$ hence every two roots $\alpha, \beta \in \Sigma^-_s$ of the same length
+By our assumptions on $\Phi$ we have $m_s(\alpha\ssub{\mathrm{max}})=1$, hence every two roots $\alpha, \beta \in \Sigma^-_s$ of the same length
 have the same $s$-shape and
 %(i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
-hence by Lemma~\ref{lemma:abs} are interchanged under the action of $W(\Delta_s)$. % $\alpha$ and $\beta$ if their length is equal.
+hence by Lemma~\ref{lemma:abs} are interchanged by the action of $W(\Delta_s)$. % $\alpha$ and $\beta$ if their length is equal.
 %By the same argument as above we get that $W(\Delta_s)$.
-Since $X_{\alpha\ssub{s}} \subseteq L_{rs}$ by the same argument as above we get $\U({\Sigma^-_s}^>, I)\subseteq L_{rs}$.
+Since $\X_{\alpha\ssub{s}} \subseteq L_{rs}$ by the same argument as above, we get $\U({\Sigma^-_s}^>, I)\subseteq L_{rs}$.
 This completes the proof of the theorem for $\Phi\neq \rB_\ell$.
 
-In the case $\Phi=\rB_\ell$ we have to show additionally that $X_{-\alpha^<_{\mathrm{max}}}(I) \leq L_{rs}$, where $\alpha^<_{\mathrm{max}}$
+In the case $\Phi=\rB_\ell$ we have to show additionally that $\X_{-\alpha^<_{\mathrm{max}}}(I) \leqslant L_{rs}$, where $\alpha^<_{\mathrm{max}}$
 denotes the maximal short root of $\rB_\ell$.
-By Chevalley commutator formula we have:
-$$t_{-{\alpha^<_{\mathrm{max}}}}(s) = t_{-1,0}(s) = t_{1,-2}(s) \cdot t_{-1,-2}(-s)^{t_{-2, 0}(-1)} \cdot t_{-1, 2}(\xi),\ s\in I.$$
-On the other hand, $t_{-2,0}(1) \in \EP_s$ while we have already shown $X_{-1,-2}(I), X_{-1, 2}(I) \subseteq L_{rs}$.
+By Chevalley commutator formula we have
+\[ x_{-{\alpha^<_{\mathrm{max}}}}(s) = x_{-1,0}(s) = x_{1,-2}(s) \cdot x_{-1,-2}(-s)^{x_{-2, 0}(-1)} \cdot x_{-1, 2}(\xi),\ s\in I. \]
+On the other hand, $x_{-2,0}(1) \in \EP_s$, and we have already shown $\X_{-1,-2}(I), \X_{-1, 2}(I) \subseteq L_{rs}$.
 This concludes the proof of the theorem.

### 2015-07-31 gauss.tex
Fixes for Gauss

@@
 Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1, \Delta_\ell$ be
-two reductive subsystems of $\Phi$ corresponding to endnodes of the Dynkin diagram of $\Phi$.
-Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1,\ell$ admit unitriangular decomposition with $N$ triangular factors:
-\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I), i=1,\ell. \]
-Then the group $\E(\Phi, R, I)$ admits decomposition with the same number of factors:
-\begin{equation} \nonumber\E(\Phi, R, I) = \Hh(\Phi,R,I) \cdot \U(\Phi^+,I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm,I). \end{equation}
+two reductive subsystems of $\Phi$ corresponding to the endnodes of the Dynkin diagram of $\Phi$.
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1,\ell$ admit triangular decomposition with $N$ triangular factors:
+\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I),\quad i=1,\ell. \]
+Then the group $\E(\Phi, R, I)$ admits the decomposition with the same number of factors:
+\[ \E(\Phi, R, I) = \Hh(\Phi,R,I) \cdot \U(\Phi^+,I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm,I). \]
 \end{thm}
@@
 \end{enumerate}
-To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for $\alpha\in \pm \Pi$, $\xi\in R$.
-Take any root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or $i=\ell$ and we can expand $Y$ as
+To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for any $\alpha\in \pm \Pi$, $\xi\in R$.
+Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or $i=\ell$ and we can expand $Y$ as
 \[ Y=\Hh(\Phi,R,I) \cdot \U(\Delta_i^+,I) \cdot \ldots \cdot \U^\pm(\Delta_i,I) \cdot \U(\Sigma_i^+,I) \cdot \ldots \cdot \U(\Sigma_i^\pm,I). \]
-For every  $h \in \Hh(\Phi, R, I)$ one has $h^{x_\alpha(\xi)} = h \cdot x_\alpha(\xi)^h x_\alpha(-\xi) = h \cdot x_\alpha(s)$ for some $s\in I$, therefore by the assumption of the theorem
+For every  $h \in \Hh(\Phi, R, I)$ one has $x_\alpha(\xi)\cdot h = h\cdot x_\alpha(\zeta)$ for some $\zeta\in I$, therefore by the assumption of the theorem
 \begin{multline*}
-Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi,R,I) \cdot X_{\alpha}(I) \cdot \E(\Delta_i,R,I)^{x_\alpha(\xi)} \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) =\\
+Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi,R,I) \cdot \X_{\alpha}(I) \cdot \E(\Delta_i,R,I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) =\\
 = \Hh(\Phi, R, I) \cdot \E(\Delta_i,R,I) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) = Y.
@@
 
-Now set $X=\left\{x_\alpha(\xi)\mid\alpha\in\Pi,\ \xi\in I \right\}$. 
-Every root is a conjugate of a simple root under the action of $W(\Phi)$.
-Since $\E(\Phi,R)$ contains the normalizer of the torus, the set $X^{\E(\Phi,R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi)$, $\alpha\in\Phi, \xi\in I \rangle$.
-Finally, inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi,R,I)$ normalizes every root subgroup $X_\alpha(I)$.
-
+Now set $X=\left\{x_\alpha(\xi)\ \middle|\ \alpha\in\Pi,\ \xi\in I \right\}$. 
+Every root is a conjugate of some fundamental root under the action of $W(\Phi)$.
+Since $\E(\Phi,R)$ contains the normalizer of the torus, the set $X^{\E(\Phi,R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi),\  \alpha\in\Phi,\ \xi\in I \rangle$.
+Finally, the inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi,R,I)$ normalizes every root subgroup $\X_\alpha(I)$.
 \end{proof}

### 2015-07-31 paper.tex
Relative torus is relative elementary + small fixes

@@
 These elements satisfy the well-known Steinberg relations:
-\begin{equation}\label{rel:add}
-x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \end{equation} 
-\begin{equation}\label{rel:CCF}
-\left[x_\alpha(s),  x_\beta(t)\right] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}.
-\end{equation}
+\begin{align}
+& x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \label{rel:add}\\
+& \left[x_\alpha(s),  x_\beta(t)\right] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
+\end{align} 
 The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
@@
 
-For $\xi\in R^*$ set $w_\alpha(\xi) = x_\alpha(\xi) x_{-\alpha}(-\xi^{-1}) x_{\alpha}(\xi).$
-If $\rk(\Phi)\geq 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
+For $\varepsilon\in R^*$ set $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_{\alpha}(\varepsilon).$
+If $\rk(\Phi)\geqslant 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
 \begin{equation}\label{rel:R3}
-w_\alpha(\xi) x_{\beta}(s) w_\alpha(\xi)^{-1} =
-x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\xi^{-\langle\beta,\alpha \rangle} s\right),\quad \xi,s\in R.
+w_\alpha(\varepsilon) x_{\beta}(\xi) w_\alpha(\varepsilon)^{-1} =
+x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\cdot\varepsilon^{-\langle\beta,\alpha \rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R.
 \end{equation}
 where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S13]{VP} for more details on $\eta_{\alpha, \beta}$).
+
+We also define $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w(-1)$. Then
+\[ h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R. \]
 
@@
 \item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
- \item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$. \end{itemize} \end{thm}
+\item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
+\end{itemize}
+\end{thm}
 
@@
 The following two equalities will be referred to in the sequel as {\it Levi decomposition}: 
-$$\EP_J(R, I) = \U(\Sigma_J, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I).$$
+\[ \EP_J(R, I) = \U(\Sigma_J, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I). \]
+
+Denote by $\Hh(\Phi,R)$ the subgroup generated by all $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$. Then set
+\[ \Hh(\Phi,R,I) = \Hh(\Phi,R)\cap\G(\Phi,R,I)=\langle h_\alpha(\varepsilon),\ \alpha\in\Phi,\ \varepsilon\in R^*\cap(1+I)\rangle. \]
+\begin{lemma}
+$\Hh(\Phi,R,I)\leqslant\E(\Phi,R,I)$.
+\end{lemma}
+\begin{proof}
+Set $\varepsilon=1+s$, $s\in I$ and write
+\begin{multline*}
+h_\alpha(1+s) = x_\alpha\left(-1\middle)\, x_{-\alpha}\middle(-s\middle)\, x_\alpha\middle((1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right) = \\
+= x_\alpha\left((1+s)^{-1}-1\middle)\, z_{-\alpha}\middle(-s,(1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right).
+\end{multline*}
+It remains to note that $(1+s)^{-1}\in 1+I$ and so all the factors lie in $\E(\Phi,R,I)$.
+\end{proof}
 

### 2015-08-02 congrsubgr-boundgen.tex
Fixes for bounded generation
Modified beginning of Bounded Generation section

@@
-We now give an application of the above decomposition to the problem of bounded generation.
+We now give an application of parabolic factorizations to the problem of bounded generation.
 \begin{dfn} 
-Given a group $G$ and a set of generators $X$ (for simplicity we assume $X=X^{-1}$ and $1\in X$), one says that the width of $G$ with respect to $X$ equals $N$, if $G=X^N$, i.e.
-every element of $G$ can be represented as a product of at most $N$ generators from $X$.
-\end{dfn}
+Let $G$ be an abstract group with a generating set $X \subset G$. %(for simplicity we assume $X=X^{-1}$ and $1\in X$),
+One defines {\it the width of $G$ with respect to $X$} as the smallest natural number $N$ such that 
+ every element of $G$ is a product of at most $N$ elements of $X$, i.\,e. $G=X^N$. \end{dfn}
+
 \begin{lemma}\label{lemma:srRI1}
-If $\sr(R,I)=1$, the width of $\SL(2,R,I)$ with respect to $z_\alpha$ does not exceed $4$.
+Suppose that $\sr(I)=1$, then the width of $\SL(2,R,I)$ with respect to generators $z_\alpha(s, \xi)$ of Theorem~\ref{theorem:Tits-Vaserstein} does not exceed $4$.
 \end{lemma}
 \begin{proof}
-Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}\in\SL(2,R,I)$.
-The first column is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
-Multiply $A$ by $x_{12}(z)$ from the left to obtain an invertible element in the upper left corner.
-Applying $x_{21}(-c/a)$ from the left and $x_{12}(-b/a)$ from the right, we obtain a diagonal matrix.
-Thus
-\begin{multline*}
-A=x_{12}(-z)\cdot x_{21}(c/a)\cdot
+Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}\in\SL(2,R,I)$ be an element of $\SL(2, R, I)$.
+The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
+Multiplying $A$ on the left by $x_{12}(z)$ we get matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible top-left corner element $a'$.
+After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we obtain a diagonal matrix. 
+Thus we obtain relative Gauss decomposition of $A$
+\begin{equation}\nonumber
+A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
 \begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
-\cdot x_{12}(b/a)=\\
-=x_{12}(-z)\cdot
+\cdot x_{12}(b'/a')=x_{12}(-z)\cdot
 \begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
-\cdot x_{21}(y) \cdot x_{12}(b/a),
-\end{multline*}
-where all the coefficients in transvections lie in $I$ and $\varepsilon\in 1+I$. The above formula is a relative version of Gauss decomposition.
-Note that
+\cdot x_{21}(y) \cdot x_{12}(b'/a'),
+\end{equation}
+where $\varepsilon\in 1+I$ and $y\in I$. Direct calculation shows that
 \begin{multline*}
@@
 therefore
-\[
-A=z_{21}(1-\varepsilon,-1-z)\cdot x_{12}(1/\varepsilon-1-z)\cdot x_{21}(\varepsilon^2-\varepsilon+y)\cdot x_{12}(b/a). \qedhere
-\]
+\[ A=z_{21}(1-\varepsilon,-1-z)\cdot x_{12}(1/\varepsilon-1-z)\cdot x_{21}(\varepsilon^2-\varepsilon+y)\cdot x_{12}(b'/a'). \qedhere \]
 \end{proof}
+
 \begin{rem}
-In the above lemma one can restrict himself to the generators of the form $x_\alpha(s)$ and $z_\alpha(s,1)$, $s\in I$, and have an estimate of $5$ factors.
-It might be useful since $\left\{z_\alpha(s,1)\mid s\in I\right\}=\X_\alpha(I)^{x_\alpha(1)}$ if a $1$-parameter subgroup.
+Notice tht the proof of the above Lemma also shows that the width of $\SL(2, R, I)$ respect to generators of the form $x_\alpha(s)$ and $z_\alpha(s,1)$, $s\in I$ does not exceed $5$.
+This estimate is useful since $X_\alpha(I)^{x_{-\alpha}(1)} = \left\{z_\alpha(s,1)\mid s\in I\right\}$ are $1$-parameter subgroups.
 \end{rem}
+
 The following lemma is a corollary of Theorems~5.7 and 5.8 of \cite{LenMorStePrimitiveRoot}.
@@
 Let $p$ be a rational prime, $c\perp d$ two coprime integers and $p\perp d$.
-Then under the assumption of the Generalized Riemann Hypothesis there exist infinitely many primes $q\equiv c\pmod{d}$, such that $p$ is a primitive root modulo $q$.
+Then under the assumption of the Generalized Riemann Hypothesis there exist infinitely many primes $q\equiv c\pmod{d}$ such that $p$ is a primitive root modulo $q$.
 \end{lemma}
-One can modify Lemma~6 of \cite{VavSmSuUnitrEng} (see also \cite{VseUnitrZ1p}) in the following way:
+
+One can modify Lemma~6 of \cite{VavSmSuUnitrEng} in the following way (cf. also \cite{VseUnitrZ1p}):
+
 \begin{lemma}\label{lemma:Z1p}
-Assume GRH. If $R=\mathbb{Z}[\sfrac{1}{p}]$ and $I\lhd R$, the width of $\SL(2,R,I)$ does not exceed $6$.
+Assume that GRH holds. If $R=\mathbb{Z}[\sfrac{1}{p}]$ and $I\lhd R$, then the width of $\SL(2,R,I)$ does not exceed $6$.
 \end{lemma}
+
 \begin{proof}
@@
 \]
-Now for a matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)\in\SL(2,\mathcal{O}_S,I^2)$.
+Now for a matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)\in\SL\left(2,\mathcal{O}_S,I^2\right)$.
 For any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$ one has $\E\left(\Phi,\mathcal{O}_S,I^2\right)\leqslant\E(\Phi,I)$, and this shows that $g$ has a bounded expression in terms of $z_\alpha$.

### 2015-08-02 gauss.tex
Torus conjugate action fix in Gauss
Modified beginning of Bounded Generation section

@@
 To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for any $\alpha\in \pm \Pi$, $\xi\in R$.
-Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or $i=\ell$ and we can expand $Y$ as
+Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or $i=\ell$ and we can expand $Y$ as follows:
 \[ Y=\Hh(\Phi,R,I) \cdot \U(\Delta_i^+,I) \cdot \ldots \cdot \U^\pm(\Delta_i,I) \cdot \U(\Sigma_i^+,I) \cdot \ldots \cdot \U(\Sigma_i^\pm,I). \]
-For every  $h \in \Hh(\Phi, R, I)$ one has $x_\alpha(\xi)\cdot h = h\cdot x_\alpha(\zeta)$ for some $\zeta\in I$, therefore by the assumption of the theorem
+For every  $h \in \Hh(\Phi, R, I)$ one has for some $s\in I$
+\[ x_\alpha(\xi)\cdot h = h\cdot x_\alpha((1+s)\xi)=h\cdot x_\alpha(\xi)\,x_\alpha(s\xi). \]
+
+Therefore by the assumption of the theorem
 \begin{multline*}
-Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi,R,I) \cdot \X_{\alpha}(I) \cdot \E(\Delta_i,R,I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) =\\
+Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi,R,I) \cdot x_\alpha(-\xi) X_{\alpha}(I) \cdot \E(\Delta_i,R,I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) =\\
 = \Hh(\Phi, R, I) \cdot \E(\Delta_i,R,I) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) = Y.

### 2015-08-02 paper.tex
Microtype package on. Let's see what it brings.
Some fine kerning
Modified beginning of Bounded Generation section

@@
 \usepackage[all]{xy}
+\usepackage[activate={true,nocompatibility}]{microtype}
 
@@
 Let $\Pi=\{\alpha_1, \ldots, \alpha_l\}$ be a basis of $\Phi$. Denote by $\Phi^+$ and $\Phi^-$ subsets of positive and negative roots with respect to $\Pi$.
-Denote by $m_i(\alpha)$ the coefficient of $\beta$ in the expansion of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum\limits_{i=1}^n m_i(\alpha) \alpha_i$.
+Denote by $m_i(\alpha)$ the coefficient of $\beta$ in the expansion of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
 
@@
 
-\subsection{Elementary subgroup}
+\subsection{Elementary subgroup}\label{sec:elementary}
 Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
@@
 \begin{align}
-& x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \label{rel:add}\\
+& \phantom{\left[{}\vphantom{x_\beta(t)}\right.}
+x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \label{rel:add}\\
 & \left[x_\alpha(s),  x_\beta(t)\right] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
@@
 
-\begin{thm} Let $\Phi$ be an irreducible root system of rank $\geq 2$, then the relative elementary subgroup $\E(\Phi, R, I)$
+\begin{thm}\label{theorem:Tits-Vaserstein} Let $\Phi$ be an irreducible root system of rank $\geq 2$, then the relative elementary subgroup $\E(\Phi, R, I)$
 is generated by the elements $z_\alpha(s, \xi)$, $\alpha\in \Phi$, $s\in I$, $\xi\in R$.

### 2015-08-03 congrsubgr-boundgen.tex
Slightly modified Bounded Generation Section up to Lemma 12

@@
 \begin{lemma}\label{lemma:srRI1}
-Suppose that $\sr(I)=1$, then the width of $\SL(2,R,I)$ with respect to generators $z_\alpha(s, \xi)$ of Theorem~\ref{theorem:Tits-Vaserstein} does not exceed $4$.
+Let $I$ be an ideal of $R$ such that $\sr(I)=1$. The following statements are true.
+\begin{enumerate}
+ \item The width of $\SL(2, R, I)$ with respect to generators $z_\alpha(s, \xi)$ of Theorem~\ref{theorem:Tits-Vaserstein} does not exceed $4$.
+ \item The width of $\SL(2, R, I)$ with respect to $1$-parameter subgroups of the form $X_\alpha(I)$ and $X_\alpha(I)^{x_{-\alpha}(1)} = \left\{z_\alpha(s,1)\mid s\in I\right\}$ does not exceed $5$.
+\end{enumerate}
 \end{lemma}
@@
 Multiplying $A$ on the left by $x_{12}(z)$ we get matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible top-left corner element $a'$.
-After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we obtain a diagonal matrix. 
+After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
 Thus we obtain relative Gauss decomposition of $A$
@@
 therefore
-\[ A=z_{21}(1-\varepsilon,-1-z)\cdot x_{12}(1/\varepsilon-1-z)\cdot x_{21}(\varepsilon^2-\varepsilon+y)\cdot x_{12}(b'/a'). \qedhere \]
+\[ A=z_{21}(1-\varepsilon,-1-z)\cdot x_{12}(1/\varepsilon-1-z)\cdot x_{21}(\varepsilon^2-\varepsilon+y)\cdot x_{12}(b'/a'), \]
+which simultaneously implies both statements of the lemma.
 \end{proof}
-
-\begin{rem}
-Notice tht the proof of the above Lemma also shows that the width of $\SL(2, R, I)$ respect to generators of the form $x_\alpha(s)$ and $z_\alpha(s,1)$, $s\in I$ does not exceed $5$.
-This estimate is useful since $X_\alpha(I)^{x_{-\alpha}(1)} = \left\{z_\alpha(s,1)\mid s\in I\right\}$ are $1$-parameter subgroups.
-\end{rem}
 
@@
 \begin{lemma}
-Let $p$ be a rational prime, $c\perp d$ two coprime integers and $p\perp d$.
-Then under the assumption of the Generalized Riemann Hypothesis there exist infinitely many primes $q\equiv c\pmod{d}$ such that $p$ is a primitive root modulo $q$.
+Let $p$ be a rational prime, let $c$, $d$ be a pair of coprime integers such that $p \perp d$.
+Then under the assumption of Generalized Riemann Hypothesis there exist infinitely many primes $q\equiv c\pmod{d}$ such that $p$ is a primitive root modulo $q$.
 \end{lemma}
 
-One can modify Lemma~6 of \cite{VavSmSuUnitrEng} in the following way (cf. also \cite{VseUnitrZ1p}):
+The following lemma is a relative version of \cite[Lemma~6]{VavSmSuUnitrEng} (cf. also \cite{VseUnitrZ1p}):
 
 \begin{lemma}\label{lemma:Z1p}
-Assume that GRH holds. If $R=\mathbb{Z}[\sfrac{1}{p}]$ and $I\lhd R$, then the width of $\SL(2,R,I)$ does not exceed $6$.
+Let $R=\mathbb{Z}[\sfrac{1}{p}]$ and let $I$ be an ideal of $R$.
+Under the assumption of GRH the width of $\SL(2,R,I)$ with respect to generators $z_\alpha(s, \xi)$ of Theorem~\ref{theorem:Tits-Vaserstein} does not exceed $6$.
 \end{lemma}
@@
 \begin{proof}
-Write $I=(m)$ for some $m\in\mathbb{Z}$, $p\nmid m$. Fix $g\in\SL(2,R,I)$:
-\[ g=\begin{pmatrix}x & y \\ z & w\end{pmatrix},\quad
-\begin{matrix*}[l]
-x=p^\alpha a,\quad & a,b,\alpha,\beta\in\mathbb{Z}, \\ y=p^\beta bm, & p\nmid a,b.
-\end{matrix*}\]
+Clearly, $I$ is a principal ideal generated by some $m\in\mathbb{Z}$ not divisible by $p$.
+Let $g$ be an element of $\SL(2,R,I)$. Write
+\[ g=\begin{pmatrix}x & y \\ z & w\end{pmatrix},\ \text{for}\ x=p^\alpha a,\ y=p^\beta bm,\ \text{where}\ a,b,\alpha,\beta\in\mathbb{Z},\ p\nmid a,b. \]
+
 \textsc{Case 1:} $\alpha\geqslant\beta$. 
-Since $p^{\alpha-\beta}a\perp bm^2$ and $p\perp bm^2$, there exist infinitely many rational primes $q$ of the form $p^{\alpha-\beta}a+bm^2k$, such that $p$ is a primitive root modulo $q$.
-One may choose $q$ prime to $b$.
-Then
+Since $p^{\alpha-\beta}a\perp bm^2$ and $p\perp bm^2$, there exist infinitely many rational primes $q$ of the form $p^{\alpha-\beta}a+bm^2k$,
+such that $p$ is a primitive root modulo $q$. 
+Without loss of generality we may assume that $q$ is prime to $b$. 
+Write
 \[ g_1=g\cdot x_{21}(mk) =
@@
 \begin{pmatrix} p^\beta q & mp^{\beta+u} \\ * & * \end{pmatrix}. \]
-$g_2\equiv 1\pmod m$, thus $p^\beta q=1+cm$ for some $c$.
+Since $g_2\equiv 1\pmod m$, we can write $p^\beta q=1+cm$ for some $c$.
 \begin{align*}
@@
 \end{align*}
-Note that $g_5=g_2\cdot z_{12}\left(-mp^{\beta+u},c/p^{\beta+u}\right)$ and that the two other coefficients in the transvections are multiples of $m$.
-Thus in this case the length of $g$ does not exceed $4$: $g=x_{21}z_{12}x_{12}x_{21}$.
+Notice that $g_5=g_2\cdot z_{12}\left(-mp^{\beta+u},c/p^{\beta+u}\right)$ hence $g=x_{21} \cdot z_{12} \cdot x_{12} \cdot x_{21}$
+and the length of $g$ does not exceed $4$.
 
-\textsc{Case 2:} $\alpha<\beta$. Since $\mathbb{Z}[\sfrac{1}{p}]/I$ is finite, there exists $k>0$ such that $p^k\equiv 1\pmod I$. One can choose $k>\beta-\alpha$. Then $k+\alpha>-k+\beta$ and
-\[ g\cdot h\left(p^k\right) =
+\textsc{Case 2:} $\alpha<\beta$. 
+Since $\mathbb{Z}[\sfrac{1}{p}]/I$ is finite, there exists $k>0$ such that $p^k\equiv 1\pmod I$.
+One can choose $k>\beta-\alpha$.
+Then $k+\alpha>-k+\beta$ and
+\[ g\cdot h_{12}\left(p^k\right) =
 \begin{pmatrix} p^\alpha a & p^\beta bm \\ * & * \end{pmatrix}
 \begin{pmatrix} p^k & 0 \\ 0 & p^{-k} \end{pmatrix}=
-\begin{pmatrix} p^{k+\alpha} a & p^{-k+\beta} bm \\ * & * \end{pmatrix}.
-\]
-One can apply Case 1 for the latter, so
-$g=x_{21}z_{12}x_{12}x_{21}h^{-1}$,
-and $x_{12}h^{-1}$ can be processed in the same way, as in Lemma \ref{lemma:srRI1}:
-$g=x_{21}z_{12}x_{12}\cdot z_{12}x_{21}x_{12}$.
+\begin{pmatrix} p^{k+\alpha} a & p^{-k+\beta} bm \\ * & * \end{pmatrix}. \]
+We find ourselves in the situation of Case 1, therefore we can write $g=x_{21} \cdot z_{12} \cdot x_{12} \cdot x_{21} \cdot h_{12}$.
+Finally, using the same token as in Lemma~\ref{lemma:srRI1} we get that $g=x_{21} \cdot z_{12} \cdot x_{12} \cdot z_{12} \cdot x_{21} \cdot x_{12}$.
 \end{proof}
-Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type, defined by a finite set $S$ of places of some global field $k$, and $I$ an ideal in $\mathcal{O}_S$.
-In case $k$ has a real embedding, then $\K_1(\Phi,\mathcal{O}_S,I)=1$ for any ideal $I\trianglelefteq\mathcal{O}_S$ and any root system $\Phi$ of rank $\geqslant2$ (see~\cite{BassMilnorSerre}).
-It is shown in \cite{TavgenThesis} that $E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$.
-From this one immediately gets the bounded generation for $\G(\Phi,R,I)$.
+Let $k$ be a global field and let $S$ be a finite set of places on $k$.
+Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type defined by $S$ and let $I$ be any ideal of $\mathcal{O}_S$.
+Recall from~\cite{BassMilnorSerre} that if $k$ has a real embedding then $\K_1(\Phi,\mathcal{O}_S,I)$ is trivial for any root system $\Phi$ of rank $\geqslant2$ and arbitrary ideal $I$.
+It is shown in \cite{TavgenThesis} that $\E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$.
 
-We will use the following
-\begin{lemma}[{\cite[Corollary~3.3]{S}}]
-Let $\Phi$ be a root system of rank $\geqslant2$, $R$ a commutative ring and $I\trianglelefteq R$ its ideal.
-If $\Phi\neq\rC_\ell$, then $\E\left(\Phi,R,I^2\right)\leqslant\E(\Phi,I)$, otherwise, $\E\left(\Phi,R,II^{\indexbox{2}}\right)\leqslant\E(\Phi,I)$.
-\end{lemma}
-Here $I^{\indexbox{2}}$ stand for the ideal generated by all squares.
-So $I^2$ is generated by the elements of the form $ab$ for all $a,b\in I$, while $II^{\indexbox{2}}$ is generated by all elements of the form $a^2b$ for $a,b\in I$.
+Now it is easy to derive bounded generation property for $\G(\Phi,\mathcal{O}_S,I)$ from the above statements.
 \begin{lemma}

### 2015-08-03 paper.tex
Slightly modified Bounded Generation Section up to Lemma 12

@@
 
+\begin{lemma}[{\cite[Corollary~3.3]{S}}]
+Let $\Phi$ be a root system of rank $\geqslant2$, let $R$ be a commutative ring and $I\trianglelefteq R$ be its ideal.
+If $\Phi\neq\rC_\ell$ then $\E\left(\Phi,R,I^2\right)\leqslant\E(\Phi,I)$, otherwise $\E\left(\Phi,R,II^{\indexbox{2}}\right)\leqslant\E(\Phi,I)$.
+\end{lemma}
+Here $I^{\indexbox{2}}$ stands for the ideal generated by squares $a^2$, where $a\in I$.
+Recall also that $I^2$ is generated by products $ab$ for all $a,b\in I$.
+Clearly, $II^{\indexbox{2}}$ is generated by elements of the form $a^2b$ for $a,b\in I$.
+
 \section{Stability conditions}\label{sec:stability-conditions}

### 2015-08-03 paper.tex
Chevalley-Matsumoto proof finished and placed in a different place

@@
 
-The following lemma is a relative version of the classical result sometimes called Chevalley---Matsumoto decomposition.
-%TODO: Recheck the statement of the lemma; finish the proof.
-\begin{lemma}\label{lemma:Chevalley-Matsumoto}
-Let $\pi$ be the fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
-Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then 
-$g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
-\end{lemma} \begin{proof}  For $I=R$ the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}). \end{proof}
-
 \subsection{Elementary subgroup}\label{sec:elementary}
@@
 
+The following lemma is a relative version of the classical result sometimes called Chevalley---Matsumoto decomposition.
+\begin{lemma}\label{lemma:Chevalley-Matsumoto}
+Let $\pi$ be the fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
+Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then 
+$g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
+\end{lemma}
+\begin{proof}
+For $I=R$ the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}).
+So we can write $g=u_1\cdot g'\cdot u_2$, where $u_1\in\U(\Sigma_s^-,R)$, $u_2\in\U(\Sigma_s^+,R)$ and $g'\in\G(\Delta_s,R)$.
+Since $g\in\G(\Phi,R,I)$, the vector $gv^+$ is $I$-unimodular.
+On the other hand, $g'u_2v^+=v^+$, so $u_1\in\G(\Phi,R,I)\cap\U(\Sigma_s^-,R)=\U(\Sigma_s^-,I)$.
+Now $g'u_2\in\left(\G(\Delta_s,R)\U(\Sigma_s^+,R)\right)\cap\G(\Phi,R,I)$, and by Levi decomposition $u_2\in\U(\Sigma_s^+,I)$, $g'\in\G(\Delta_s,R,I)$.
+\end{proof}
+
 Denote by $\Hh(\Phi,R)$ the subgroup generated by all $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$. Then set

### 2015-08-03 congrsubgr-boundgen.tex
Slightly modified Lemma 13

@@
 \end{proof}
-Let $k$ be a global field and let $S$ be a finite set of places on $k$.
+
+For the rest of this subsection $k$ denotes a global field. We assume that there is some finite set of places $S$ chosen on $k$. 
 Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type defined by $S$ and let $I$ be any ideal of $\mathcal{O}_S$.
-Recall from~\cite{BassMilnorSerre} that if $k$ has a real embedding then $\K_1(\Phi,\mathcal{O}_S,I)$ is trivial for any root system $\Phi$ of rank $\geqslant2$ and arbitrary ideal $I$.
-It is shown in \cite{TavgenThesis} that $\E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$.
 
-Now it is easy to derive bounded generation property for $\G(\Phi,\mathcal{O}_S,I)$ from the above statements.
+%Now it is easy to derive bounded generation property for $\G(\Phi,\mathcal{O}_S,I)$ from the above statements.
 \begin{lemma}
-If $\rk\Phi\geqslant2$ and $k$ has a real embedding, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to $z_\alpha$.
+Let $\Phi$ be a classical root system of rank $\geqslant 2$.
+If $k$ has a real embedding, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to generators $z_\alpha(s, \xi)$ of Theorem~\ref{theorem:Tits-Vaserstein}.
 \end{lemma}
 \begin{proof}
-Because of the Bass---Kolster decomposition it suffices to express every element $g$ of $\SL(2,\mathcal{O}_S,I)$ as a product of a bounded number of generators in a group of rank $2$. Write
-\[ g=\begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2,\mathcal{O}_S,I),\quad a,b,c,d\in I. \]
+Recall from~\cite{BassMilnorSerre} that if $k$ has a real embedding then $\K_1(\Phi,\mathcal{O}_S,I)$ is trivial for any root system $\Phi$ of rank $\geqslant2$ and arbitrary ideal $I$.
 
-The condition $\det(g)=1$ implies $a+d=bc-ad\in I^2$.
+First of all, notice that $\asr(I) \leq \asr(\mathcal{O}_S) \leq 2$. 
+By Theorem~\ref{thm:BassKolster} we can present any element of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators $z_\alpha(s, \xi)$ and one element of $G_0=\G(\rA_1, \mathcal{O}_S, I)=\SL(2,\mathcal{O}_S,I)$.
+Consequently, to prove the statement of the lemma it suffices to express every element $g = \begin{psmallmatrix}1+a & b \\ c & 1+d \end{psmallmatrix} \in G_0$ as a product of a finite number of generators contained in some rank $2$ subgroup of $G$ containing $G_0$.
 
-Define the Vaserstein's congruence subgroup as
+From $\det(g)=1$ we conclude that $a+d=bc-ad\in I^2$. 
+Recall that Vaserstein's congruence subgroup is defined as
 \[ G(I,I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2,\mathcal{O}_S)\;\middle|\; a,d\in I^2,\ b,c\in I \right\}. \]
-Note that $g_1=g\cdot z_{21}(a,1)\in G(I,I)$. Indeed,
-\[
-\begin{pmatrix}
-1+a & b \\ c & 1+d
-\end{pmatrix} \xmapsto{\cdot z_{21}(a,1)}
-\begin{pmatrix}
-1+ba-a^2 & b-a-ba-a^2 \\ c+a+ad-ac & 1+bc-ac
-\end{pmatrix} \in G(I,I).
-\]
-Now for a matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)\in\SL\left(2,\mathcal{O}_S,I^2\right)$.
-For any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$ one has $\E\left(\Phi,\mathcal{O}_S,I^2\right)\leqslant\E(\Phi,I)$, and this shows that $g$ has a bounded expression in terms of $z_\alpha$.
+Notice that $g_1=g\cdot z_{21}(a,1)$ is contained in $G(I,I)$, indeed
+\[ \begin{pmatrix} 1+a & b \\ c & 1+d \end{pmatrix} \cdot \begin{pmatrix} 1-a & -a \\ a & 1+a \end{pmatrix} = \begin{pmatrix} 1+ba-a^2 & b-a-ba-a^2 \\ c+a+ad-ac & 1+bc-ac \end{pmatrix} \in G(I,I). \]
+For any matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)$ lies in $\SL\left(2,\mathcal{O}_S,I^2\right)$.
+By Lemma~\ref{lemma:Stepanov-ideal} the group $\E\left(\Phi,\mathcal{O}_S,I^2\right)$ is contained in $\E(\Phi,I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
+Under the assumptions of the lemma it is shown in~\cite{TavgenThesis} that $\E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$ therefore $g$ has bounded length with respect to $z_\alpha$.
 
-In case $\Phi=\rC_\ell$, one can compute
-\[ \det(g_1)=a^3d-3a^2bc+a^2bd+ab^2c+a^3+a^2b+a^2d+2abc-abd+1 \]
-to see that $2abc-abd\in II^{\indexbox{2}}$, so
+In remains to consider the case $\Phi=\rC_\ell$. First of all, notice that $2abc-abd\in II^{\indexbox{2}}$, indeed
+\[ \det(g_1)=a^3d-3a^2bc+a^2bd+ab^2c+a^3+a^2b+a^2d+2abc-abd+1. \]
+Consequently, we have that
 \[ g_2=x_{21}(-a-c)\cdot g_1\cdot x_{12}(a-b)\equiv
@@
 \end{pmatrix}\bmod II^{\indexbox{2}}. \]
-Now for $g_3=g_2\cdot z_{12}\left(a^2-ab,1\right)$ one has
+Now for $g_3=g_2\cdot z_{12}\left(a^2-ab,1\right)$ we have that
 \begin{align*}
@@
 \end{align*}
-Thus $g_4\cdot x_{21}(*)\in\SL\left(2,\mathcal{O}_S,II^{\indexbox{2}}\right)\leqslant\E(\rC_\ell,I)$ and can be expressed as a bounded product of $x_\alpha$.
+Thus $g_4\cdot x_{21}(*)\in\SL\left(2,\mathcal{O}_S,II^{\indexbox{2}}\right)$ is contained in $\E(\rC_\ell,I)$ by Lemma~\ref{lemma:Stepanov-ideal} and therefore can be expressed as a bounded product of $x_\alpha$.
 \end{proof}

### 2015-08-03 paper.tex
Slightly modified Lemma 13

@@
 
-\begin{lemma}[{\cite[Corollary~3.3]{S}}]
+\begin{lemma}[{\cite[Corollary~3.3]{S}}]\label{lemma:Stepanov-ideal}
 Let $\Phi$ be a root system of rank $\geqslant2$, let $R$ be a commutative ring and $I\trianglelefteq R$ be its ideal.

### 2015-08-04 congrsubgr-boundgen.tex
Slightly modified proof of Lemma 13

@@
 \begin{proof}
-Recall from~\cite{BassMilnorSerre} that if $k$ has a real embedding then $\K_1(\Phi,\mathcal{O}_S,I)$ is trivial for any root system $\Phi$ of rank $\geqslant2$ and arbitrary ideal $I$.
-
 First of all, notice that $\asr(I) \leq \asr(\mathcal{O}_S) \leq 2$. 
@@
 For any matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)$ lies in $\SL\left(2,\mathcal{O}_S,I^2\right)$.
+Recall that if $k$ has a real embedding then $\G(\Phi, \mathcal{O}_S,I) = \E(\Phi, \mathcal{O}_S, I)$ for any ideal $I$ by virtue of \cite[Corollary~4.5]{Ma69} and \cite[Theorem~3.6]{BassMilnorSerre}.
+
 By Lemma~\ref{lemma:Stepanov-ideal} the group $\E\left(\Phi,\mathcal{O}_S,I^2\right)$ is contained in $\E(\Phi,I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
-Under the assumptions of the lemma it is shown in~\cite{TavgenThesis} that $\E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$ therefore $g$ has bounded length with respect to $z_\alpha$.
+Notice that under the assumptions of the lemma it is known that $\E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$, see~\cite[Theorem~3.3]{TavgenThesis}.
 

### 2015-08-05 paper.tex
Slightly modified proof of Lemma 13
Various fixes

@@
 \DeclareFieldFormat[inproceedings]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+\DeclareFieldFormat[thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
 \addbibresource{paper.bib}
@@
 The following theorem is the first such application.
-\begin{thm} Let $I$ be an ideal of a commutative ring $R$ such that
-\begin{itemize} \item either $\sr(I) = 1$;
- \item or $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$. \end{itemize}
-In the latter case assume additionally that Generalized Riemann Hypothesis holds.
-Then for any $\Phi$ the width of the congruence subgroup $\G(\Phi, R, I)$ with respect to $z_\alpha$ does not exceed $C_1|\Phi| + C_2$. \end{thm}
+
+Let $G$ be an abstract group with a generating set $X \subset G$. %(for simplicity we assume $X=X^{-1}$ and $1\in X$),
+One defines {\it the width of $G$ with respect to $X$} as the smallest natural number $N=w(G,X)$ such that every element of $G$ is a product of at most $N$ elements of $X$.
+
+The relative elementary group $\E(\Phi,R,I)$ is generated by certain elements $z_\alpha(s,\xi)$, see Theorem~\ref{theorem:Tits-Vaserstein}.
+The width $w(\E(\Phi,R),\mathcal{X})$, where $\mathcal{X}$ is the set of all elementary generators $x_\alpha(\xi)$, has been studied extensively \cite{?}.
+Denote by $\mathcal{Z}$ the set of all $z_\alpha(s,\xi)$.
+
+\begin{thm} Let $\Phi$ be a root system, and let $I$ be an ideal of a commutative ring $R$.
+\begin{enumerate}
+\item If $\sr(I) = 1$, then $w(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+3\rk\Phi$;
+\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$, and $\Phi$ is classical, then under the assumption of the Generalized Riemann Hypothesis $w(\E(\Phi,R,I),\mathcal{Z})\leqslant ???$;
+\item If $\mathcal{O}_S$ is a Dedekind ring of arithmetic type in some global field $k$ having a real embedding and $\rk\Phi\geqslant2$, then $w(\G(\Phi,\mathcal{O}_S,I),\mathcal{Z})$ is finite.
+\end{enumerate}
+\end{thm}
+\begin{proof}
+content...
+\end{proof}
 \noindent In the proof of the above theorem we use Bass---Kolster decomposition to reduce to the case $\Phi=\rA_1$ which then can be settled directly.
 Notice that the particular case $I=R$ of the above theorem was demonstrated in~\cite{VavSmSuUnitrEng} (see also \cite{VseUnitrZ1p}).
-
-\begin{thm}
-Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type in some global field $k$ having a real embedding.
-If $\rk\Phi\geqslant2$, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to $z_\alpha$.
-\end{thm}
 
@@
 Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then 
-$g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
+\[ g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I). \]
 \end{lemma}
 \begin{proof}
-For $I=R$ the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}).
-So we can write $g=u_1\cdot g'\cdot u_2$, where $u_1\in\U(\Sigma_s^-,R)$, $u_2\in\U(\Sigma_s^+,R)$ and $g'\in\G(\Delta_s,R)$.
-Since $g\in\G(\Phi,R,I)$, the vector $gv^+$ is $I$-unimodular.
+In the absolute case ($I=R$) the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}.
+Thus we can write $g=u_1\cdot g'\cdot u_2$, where $u_1\in\U(\Sigma_s^-,R)$, $u_2\in\U(\Sigma_s^+,R)$ and $g'\in\G(\Delta_s,R)$.
+Since $g$ lies in $\G(\Phi,R,I)$, the vector $gv^+$ is $I$-unimodular.
 On the other hand, $g'u_2v^+=v^+$, so $u_1\in\G(\Phi,R,I)\cap\U(\Sigma_s^-,R)=\U(\Sigma_s^-,I)$.
-Now $g'u_2\in\left(\G(\Delta_s,R)\U(\Sigma_s^+,R)\right)\cap\G(\Phi,R,I)$, and by Levi decomposition $u_2\in\U(\Sigma_s^+,I)$, $g'\in\G(\Delta_s,R,I)$.
+The matrix $g'u_2$ is an element of $\left(\G(\Delta_s,R)\U(\Sigma_s^+,R)\right)\cap\G(\Phi,R,I)$, and by Levi decomposition $u_2\in\U(\Sigma_s^+,I)$, $g'\in\G(\Delta_s,R,I)$.
 \end{proof}
@@
 \end{lemma}
-Here $I^{\indexbox{2}}$ stands for the ideal generated by squares $a^2$, where $a\in I$.
+Here $I^{\indexbox{2}}$ denotes the ideal generated by squares $a^2$, where $a\in I$.
 Recall also that $I^2$ is generated by products $ab$ for all $a,b\in I$.

### 2015-08-15 stability-conditions.tex
Small fixes in lemma:asrUnip

@@
 Let $v\in V=R^{2\ell}$ be a vector of the natural representation of $\G(\rD_\ell, R)$.
-Denote by $v_+$ and $v_-$ the upper and the lower halves of $v$ i.e. $v_+=(v_1,\ldots, v_\ell)^t$, $v_-=(v_{-\ell},\ldots, v_{-1})^t$.
+Denote by $v_+$ and $v_-$ the upper and the lower halves of $v$, i.e. $v_+=(v_1,\ldots, v_\ell)^t$, $v_-=(v_{-\ell},\ldots, v_{-1})^t$.
 \begin{lemma}\label{lemma:asrUnip}
- Let $\Phi=\rD_\ell$ and assume that $\asr(I)\leq \ell -1$. 
+ Let $\Phi=\rD_\ell$ and assume that $\asr(I)\leqslant \ell -1$. 
  Then for any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$
- there exist $g\in\U(\Sigma^+_\ell, I)$ such that $(g \cdot v)_+ \in \Ums(\ell, I)$.
+ there exists $g\in\U(\Sigma^+_\ell, I)$ such that $(g \cdot v)_+ \in \Ums(\ell, I)$.
 \end{lemma}
-\begin{proof} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \leq I$.
-By Proposition~\ref{prop:sr_properties} $\sr(I/J) \leq \ell-1$ therefore
+\begin{proof} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \subseteq I$.
+By Proposition~\ref{prop:sr_properties} $\sr(I/J) \leqslant \ell-1$, therefore
 the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
-This implies existence of $h\in \E(\Delta_\ell, R, I)$ such that for $v' = h \cdot v$ and $i=1,\ldots, \ell$ one has $v'_i \equiv \delta_{i1} \mod J$.
+This implies the existence of an element $h\in \E(\Delta_\ell, R, I)$ such that the vector $v' = h \cdot v$ satisfies $v'_i \equiv \delta_{i1} \pmod J$ for $i=1,\ldots, \ell$.
 
 Clearly, $(v'_1,v'_{-\ell},\ldots, v'_{-1})$ is $I$-unimodular.
-Applying statement~\ref{asr-bak-like} of Lemma~\ref{lemma:relative-asr-unimod} we find $c_2,\ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}t_{-i, -1}(c_i)\cdot v'$ one has
+Applying statement~\ref{asr-bak-like} of Lemma~\ref{lemma:relative-asr-unimod} we find $c_2,\ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}x_{-i, -1}(c_i)\cdot v'$ one has
 $(v''_1, v''_{-\ell},\ldots, v''_{-2})\in\Ums(\ell+1, I)$.
@@
 %$(v''_1, v''_{-\ell},\ldots, v''_{-2})$ is $I$-unimodular. 
-Now, applying condition $\sr(I) \leq \ell-1$ once again we find
+Now, applying the condition $\sr(I) \leqslant \ell-1$ once again we find
 $d_1,d_3,\ldots, d_{\ell}\in I$ such that the entries $(v'''_1, v'''_{-\ell},\ldots, v'''_{-3})$
-of $v'''=t_{-2,1}(d_1) \cdot \prod_{i=3}^{\ell} t_{-2,-i}(d_i) \cdot v''$ form a $I$-unimodular column.
+of $v'''=x_{-2,1}(d_1) \cdot \prod_{i=3}^{\ell} x_{-2,-i}(d_i) \cdot v''$ form an $I$-unimodular column.
 
 We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v'''_1+\sum_{i=3}^\ell f_i v'''_{-i} = 1$.
-Set $\xi = v'''_1-v'''_2-1 \in I$, $v^4=t_{1,2}(\xi f_1) \cdot \prod_{i=3}^\ell t_{-i,2}(\xi f_i) \cdot v'''$.
-Clearly $v^4_2 = v^4_1-1$, therefore $v^4_+$ is $I$-unimodular.
-Summarizing the above, we have found $g\in \EP_\ell(R, I)$ such that $v^4=g \cdot v$
-and assertion of the lemma immediately follows from Levi decomposition. \end{proof}
+Set $\xi = v'''_1-v'''_2-1 \in I$, $v^{(4)}=x_{1,2}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-i,2}(\xi f_i) \cdot v'''$.
+Clearly $v^{(4)}_2 = v^{(4)}_1-1$, therefore $v^{(4)}_+$ is $I$-unimodular.
+Summarizing the above, we have found $g\in \EP_\ell(R, I)$ such that $v^{(4)}=g \cdot v$
+and the assertion of the lemma immediately follows from Levi decomposition. \end{proof}
 

### 2015-08-15 bass-kolster.tex
BK proofreading almost finished

@@
 \begin{thm}\label{thm:BassKolster}
-Let $\Phi$ be a classical root system of rank $\ell\geqslant2$, let $R$ be arbitary commutative ring and $I$ be an ideal, satisfying one of the following assumptions:
-\newline \indent \begin{tabular}{l l l}      
-\textbullet & $\Phi = \rA_\ell$, $\ell\geq 2$, & $\sr(I) \leqslant \ell$; \\     
-\textbullet & $\Phi = \rC_\ell$, $\ell\geq 2$, & $\sr(I) \leqslant 2\ell-1$; \\ 
-\textbullet & $\Phi = \rB_\ell$, $\rD_\ell$ $\ell\geq 3$,  & $\asr(I) \leqslant \ell-1$. \end{tabular}
-
-\noindent Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
-\[\G(\Phi,R,I)=  \U(\Phi^+,I) \cdot \U(\Phi^-,I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I)\]
-where $\Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\mid r\in I \right\}$.
+Let $\Phi$ be a classical root system of rank $\ell\geqslant2$, let $R$ be an arbitrary commutative ring and $I$ be an ideal, satisfying one of the following assumptions:
+\[\begin{array}{l@{\quad}l@{\quad}l@{\quad}c}
+\Phi = \rA_\ell,\ \ell\geqslant 2, & \sr(I) \leqslant \ell; \\
+\Phi = \rC_\ell,\ \ell\geqslant 2, & \sr(I) \leqslant 2\ell-1; \\
+\Phi = \rB_\ell, \rD_\ell,\ \ell\geqslant 3, & \asr(I) \leqslant \ell-1.
+\end{array}\]
+Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
+\[ \G(\Phi,R,I)=  \U(\Phi^+,I) \cdot \U(\Phi^-,I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I), \]
+where $\Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\ \middle|\ r\in I \right\}$.
 \end{thm}
@@
 Let $g$ be an element of $\G(\Phi, R, I)$. Set $v=g \cdot v^+\in\Ums(n, I)$. 
-Notice that in each of the cases it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that 
+Notice that in each case it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that 
 \begin{equation} \label{eq1} (g'\cdot v^+)_{1} = 1 + s \text{ and } (g'\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}} = s\ \text{for some}\ s\in I. \end{equation}
@@
 
-\textsc{Case $\Phi=\rA_\ell$, $n=\ell + 1$:}
+\textsc{Case $\Phi=\rA_\ell$, $n=\ell + 1$.}
 %Set $v=(1+v_1,v_2,\ldots,v_\ell,v_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
@@
 
-\textsc{Case $\Phi=\rC_\ell$, $n=2\ell$:}
+\textsc{Case $\Phi=\rC_\ell$, $n=2\ell$.}
 Notice that column $(v_1,\ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
 Applying condition $\sr(I)\leq 2\ell-1$ we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
-By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for $h_1 = t_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} t_{i,-1}(c_i) \in \U(\Sigma_1^-, I)$.
+By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for
+\[ h_1 = x_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} x_{i,-1}(c_i) \in \U(\Sigma_1^-, I). \]
 
@@
 %TODO: Determine exact sign
-Set $\xi = v''_1-v''_{-1}-1 \in I$, $h_2 = t_{-1,1}(\xi f_1 \pm \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}) \cdot \prod_{i=2}^{-2} t_{-1,i}(\xi f_i) \in \U(\Sigma_1, I)$.
+Set $\xi = v''_1-v''_{-1}-1 \in I$,
+\[ h_2 = x_{-1,1}\biggl(\xi f_1 \pm \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1,i}(\xi f_i) \in \U(\Sigma_1, I). \]
 Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\ref{eq1}.
@@
 Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
-$v''=h_2 \cdot t_{1,2}(c_1) \cdot v'$, $h_2=\prod_{i=3}^\ell t_{i,2}(c_i)$.
+\[ v''=h_2 \cdot x_{1,2}(c_1) \cdot v', \quad h_2=\prod_{i=3}^\ell x_{i,2}(c_i). \]
 
 We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v''_1+\sum_{i=3}^\ell f_i v''_{i} = 1$.
-As before, set $\xi = v''_1-v''_{-2}-1 \in I$, $h_3 = t_{1,-2}(\xi f_1) \cdot \prod_{i=3}^\ell t_{i,-2}(\xi f_i)$, $v'''=h_3 \cdot v''$.
+As before, set
+\[ \xi = v''_1-v''_{-2}-1 \in I, \quad h_3 = x_{-2,1}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-2,i}(\xi f_i), \quad v'''=h_3 \cdot v''. \]
 %Clearly, $v'''_{-2}=v'''_1-1$, therefore for $v_4 = z_{-\alpha_{max}}(-v'''_{-2}, 1) \cdot v'''$ one has $v^4_1 = 1$, as required.
-Clearly, $t_{1,2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, while $ h_3 \cdot h_2 \in \U(\Phi^-, I)$.
+Clearly, $t_{1,2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, $ h_3 \cdot h_2 \in \U(\Phi^-, I)$ and $v'''$ satisfies \ref{eq1}.
 
-\textsc{Case $\Phi=\rB_\ell$, $n=2\ell+1$:} Subdivide $v\in \Ums(2\ell+1, I)$ as $v=(v_+, v_0, v_-)\in R^\ell\times R\times R^\ell$.
+\textsc{Case $\Phi=\rB_\ell$, $n=2\ell+1$.} Subdivide $v\in \Ums(2\ell+1, I)$ as $v=(v_+, v_0, v_-)\in R^\ell\times R\times R^\ell$.
 Denote by $J\leq I$ the ideal spanned by components of $v_-$.
-Since $\sr(I/J)\leq \ell$ we can find $c_1,\dots,c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell t_{i, 0}(c_i) \in \U(\Phi^+, I)$
+Since $\sr(I/J)\leq \ell$ we can find $c_1,\dots,c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell x_{i,0}(c_i) \in \U(\Phi^+, I)$
 one has $\bar{v'}_+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, I)$.
@@
 In the assumptions and notation of Theorem~\ref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
-can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $n(\Phi)$ elementary root unipotents $t_{\alpha}(s)$ of level $I$, where
+can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $n(\Phi)$ elementary root unipotents $x_\alpha(s)$ of level $I$, where
 $n(\rA_\ell)= 4 \ell - 1$, $n(\rB_\ell)= 8 \ell - 5$, $n(\rC_\ell)= 8 \ell - 5$, $n(\rD_\ell)= 8 \ell - 9$. \end{cor}
@@
 We can present an element $g$ of $\U(\Sigma_\ell, I)$ as a product of $g_1 \in \U(\Sigma_{\{1,2\}} \cap \Sigma_\ell)$ and $g_2\in \U(\Delta_{\{1,2\}}\cap \Sigma_\ell)$.
-An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one) and therefore can be moved to the right-hand side of the formula.
+An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one) and therefore can be moved to the right until it is consumed by $\G(\Delta_1)$.
 On the other hand, $g_1$ is a product of at most $2\ell-3$ elementary unipotents, while the width of $\U(\Sigma_1^\pm, I)$ and $\U(\Sigma_2^-\cap\Delta_1)$ in elementary unipotents does not exceed $2\ell-2$ and $2\ell-4$, respectively.

### 2015-08-19 congrsubgr-boundgen.tex
Various fixes
Gauss for sr(I)=1

@@
 We now give an application of parabolic factorizations to the problem of bounded generation.
-\begin{dfn} 
-Let $G$ be an abstract group with a generating set $X \subset G$. %(for simplicity we assume $X=X^{-1}$ and $1\in X$),
-One defines {\it the width of $G$ with respect to $X$} as the smallest natural number $N$ such that 
- every element of $G$ is a product of at most $N$ elements of $X$, i.\,e. $G=X^N$. \end{dfn}
 
 \begin{lemma}\label{lemma:srRI1}
-Let $I$ be an ideal of $R$ such that $\sr(I)=1$. The following statements are true.
-\begin{enumerate}
- \item The width of $\SL(2, R, I)$ with respect to generators $z_\alpha(s, \xi)$ of Theorem~\ref{theorem:Tits-Vaserstein} does not exceed $4$.
- \item The width of $\SL(2, R, I)$ with respect to $1$-parameter subgroups of the form $X_\alpha(I)$ and $X_\alpha(I)^{x_{-\alpha}(1)} = \left\{z_\alpha(s,1)\mid s\in I\right\}$ does not exceed $5$.
-\end{enumerate}
+Let $\Phi$ be a root system, $I$ be an ideal of $R$ such that $\sr(I)=1$. Then the relative elementary Chevalley group admits Gauss decomposition
+\[ \E(\Phi,R,I) = \Hh(\Phi,R,I) \U(\Phi,I)\U^-(\Phi,I)\U(\Phi,I). \]
+As a corollary, the width of $\E(\Phi,R,I)$ with respect to generators $z_\alpha(s,\xi)$ of Theorem~\ref{theorem:Tits-Vaserstein} does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
 \end{lemma}
@@
 \end{equation}
-where $\varepsilon\in 1+I$ and $y\in I$. Direct calculation shows that
-\begin{multline*}
-\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix} =
-\begin{pmatrix} 1 & -1 \\ 0 & 1 \end{pmatrix}
-\begin{pmatrix} 1 & 0 \\ 1-\varepsilon & 1 \end{pmatrix}
-\begin{pmatrix} 1 & 1/\varepsilon \\ 0 & 1 \end{pmatrix}
-\begin{pmatrix} 1 & 0 \\ \varepsilon^2-\varepsilon & 1 \end{pmatrix} =\\=
-\begin{pmatrix} 1 & -1 \\ 0 & 1 \end{pmatrix}
-\begin{pmatrix} 1 & 0 \\ 1-\varepsilon & 1 \end{pmatrix}
-\begin{pmatrix} 1 & 1+z \\ 0 & 1 \end{pmatrix}
-\begin{pmatrix} 1 & 1/\varepsilon-1-z \\ 0 & 1 \end{pmatrix}
-\begin{pmatrix} 1 & 0 \\ \varepsilon^2-\varepsilon & 1 \end{pmatrix},
-\end{multline*}
-therefore
-\[ A=z_{21}(1-\varepsilon,-1-z)\cdot x_{12}(1/\varepsilon-1-z)\cdot x_{21}(\varepsilon^2-\varepsilon+y)\cdot x_{12}(b'/a'), \]
-which simultaneously implies both statements of the lemma.
+where $\varepsilon\in 1+I$ and $y\in I$. Theorem~\ref{thm:Gauss} implies that the Gauss decomposition of length $3$ hold for every relative elementary Chevalley group.
+
+To obtain the width estimates fix an element $g\in\E(\Phi,R,I)$ and decompose it into $g=u_1 h v_2 u_3$, where $h\in\Hh(\Phi,R,I)$, $u_1,u_3\in\U(\Phi,I)$, $v_2\in\U^-(\Phi,I)$.
+Write $h=\prod_{i=1}^\ell h_{\alpha_i}(\varepsilon_i)$, $\varepsilon\in1+I$.
+Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $\X_\alpha(I)$ (see formula~\ref{rel:R6}), we have a decomposition
+\[ g\in\U(\Phi,I)\cdot\prod_{\i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
+and the estimate follows.
+%
+%
+%Direct calculation shows that
+%\begin{multline*}
+%\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix} =
+%\begin{pmatrix} 1 & -1 \\ 0 & 1 \end{pmatrix}
+%\begin{pmatrix} 1 & 0 \\ 1-\varepsilon & 1 \end{pmatrix}
+%\begin{pmatrix} 1 & 1/\varepsilon \\ 0 & 1 \end{pmatrix}
+%\begin{pmatrix} 1 & 0 \\ \varepsilon^2-\varepsilon & 1 \end{pmatrix} =\\=
+%\begin{pmatrix} 1 & -1 \\ 0 & 1 \end{pmatrix}
+%\begin{pmatrix} 1 & 0 \\ 1-\varepsilon & 1 \end{pmatrix}
+%\begin{pmatrix} 1 & 1+z \\ 0 & 1 \end{pmatrix}
+%\begin{pmatrix} 1 & 1/\varepsilon-1-z \\ 0 & 1 \end{pmatrix}
+%\begin{pmatrix} 1 & 0 \\ \varepsilon^2-\varepsilon & 1 \end{pmatrix},
+%\end{multline*}
+%therefore
+%\[ A=z_{21}(1-\varepsilon,-1-z)\cdot x_{12}(1/\varepsilon-1-z)\cdot x_{21}(\varepsilon^2-\varepsilon+y)\cdot x_{12}(b'/a'), \]
+%which simultaneously implies both statements of the lemma.
 \end{proof}
@@
 \begin{pmatrix} p^\beta q & mp^{\beta+u} \\ * & * \end{pmatrix}. \]
-Since $g_2\equiv 1\pmod m$, we can write $p^\beta q=1+cm$ for some $c$.
+Since $g_2\equiv 1\pmod m$, we can write $p^\beta q=1+cm$ for some $c$. Now let
 \begin{align*}

### 2015-08-20 congrsubgr-boundgen.tex
Added more items to bibliography; added some text to introduction

@@
 By Lemma~\ref{lemma:Stepanov-ideal} the group $\E\left(\Phi,\mathcal{O}_S,I^2\right)$ is contained in $\E(\Phi,I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
-Notice that under the assumptions of the lemma it is known that $\E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$, see~\cite[Theorem~3.3]{TavgenThesis}.
+Notice that under the assumptions of the lemma it is known that $\E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$, see~\cite{Tavgen93} or \cite[Theorem~3.3]{TavgenThesis}.
 

### 2015-08-20 paper.tex
Gauss for sr(I)=1
Added more items to bibliography; added some text to introduction

@@
 \DeclareMathOperator{\SL}{SL}
+\DeclareMathOperator{\Sp}{Sp}
 \DeclareMathOperator{\St}{St}
@@
 \section{Introduction}\label{sec:intro}
-Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system.
-Denote by $G=\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over $R$ and let $\E(\Phi, R)$ denote its elementary subgroup, 
- i.\,e. the group generated by root unipotents $t_\alpha(\xi)$, $ $ see~\cite{VP, St78, S}.
-For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the relative Chevalley group (or the principal congruence subgroup) of level $I$, 
-i.\,e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection.
+Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system with a fixed basis of simple roots $\Pi$.
+Denote by $G=\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over $R$ and by $\E(\Phi, R)$ its {\it elementary subgroup}, 
+ i.\,e. the subgroup generated by root unipotents $t_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
+For an ideal $I \trianglelefteq R$ denote by $\G(\Phi, R, I)$ the {\it relative Chevalley group} (also called {\it principal congruence subgroup}) of level $I$, 
+i.\,e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection $R\rightarrow R/I$.
 
@@
 \begin{itemize}
-\item Gauss decomposition i.\,e. decomposition of the form $\E(\Phi,R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup,
+\item {\it Gauss decomposition} i.\,e. decomposition of the form $\E(\Phi,R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup,
       and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
-\item Bass---Kolster decomposition $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
-      $\Par_i$ is the maximal parabolic subgroup of $\G$ corresponding to $i$-th vertex of the Dynkin diagram of $\Phi$ and 
-      $\U_i$, $\U_i^-$ are the unipotent radicals associated with it;
-\item Dennis---Vaserstein decomposition $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$.
+\item {\it Bass---Kolster} decomposition $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
+      $\Par_i$, $\Par_i^-$ are the opposite maximal parabolic subgroups of $\G$ corresponding to $i$-th simple root of $\Phi$ and $\U_i$, $\U_i^-$ are their unipotent radicals;
+\item {\it Dennis---Vaserstein} decomposition $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$,
+      where $\EP_i$ denotes the subgroup generated by root unipotents $t_\alpha(\xi)$ contained in $\Par_i$.
 \end{itemize}
@@
 
+%TODO: Illustrate each statement of the text below with a reference:
 There are two main reasons to study parabolic factorizations.
-Recall that a number of various factorizations of $\G$ are known over rings having small dimension.
-For example, Bruhat decomposition is the key instrument in the study of linear groups over fields, 
- while Gauss decomposition and unitriangular factorizations are useful tools in the study of groups over local rings.
+Recall that a number of various factorizations of $\G$ are known over small-dimensional rings.
+For example, Bruhat decomposition is the key instrument in the study of linear groups over fields, whereas Gauss decomposition and unitriangular factorizations are useful tools in the study of groups over local rings.
 Moreover, for each particular analytic or arithmetic setting there is a special decomposition theorem (Iwasawa, Cartan and Iwahori decompositions, to mention a few).
 Unfortunately, neither of these decompositions can be carried over to rings of higher dimension.
-The advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of milder ring-theoretic assumptions such as the stable range condition.
+The main advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of milder ring-theoretic assumptions formulated in terms of the {\it stable rank} of the ground ring.
+Their another advantage is that they prove useful in the study of asymptotical properties of Chevalley groups. We are going to discuss this theme in more detail below.
 
-Another advantage of parabolic factorizations is that they prove useful in the study of asymptotical properties of Chevalley groups.
-The following theorem is the first such application.
+Let $G$ be an abstract group with a generating set $X \subset G$. 
+We denote by $W(G, X)$ the {\it width of $G$ with respect to $X$} i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
+The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $t_\alpha(\xi)$ has been extensively studied in a number of works (see e.\,g.
+\cite{CK83, Ka82, Tavgen91, Mo07, VseUnitrZ1p, VavSmSuUnitrEng}).
+Summarizing results of these works, one can hope that such width is finite only for rather narrow classes of rings of number-theoretic nature, e.\,g.
+localizations of Dedeking rings of arithmetic type.
+For example, W.~van der Kallen has shown that the width of $\SL_3(R)$ is infinite already for a euclidean ring $R=\mathbb{C}[t]$.
 
-Let $G$ be an abstract group with a generating set $X \subset G$. %(for simplicity we assume $X=X^{-1}$ and $1\in X$),
-One defines {\it the width of $G$ with respect to $X$} as the smallest natural number $N=w(G,X)$ such that every element of $G$ is a product of at most $N$ elements of $X$.
-
-The relative elementary group $\E(\Phi,R,I)$ is generated by certain elements $z_\alpha(s,\xi)$, see Theorem~\ref{theorem:Tits-Vaserstein}.
-The width $w(\E(\Phi,R),\mathcal{X})$, where $\mathcal{X}$ is the set of all elementary generators $x_\alpha(\xi)$, has been studied extensively \cite{?}.
-Denote by $\mathcal{Z}$ the set of all $z_\alpha(s,\xi)$.
+On the other hand, much less is known about the width of relative groups $\G(\Phi, R, I)$. 
+It is a classical result of J.~Tits and L.~Vaserstein that the relative elementary group $\E(\Phi, R, I)$ is generated by elements $z_\alpha(s,\xi)=t_{\alpha}(s)^{t_{-\alpha}(\xi)}$, see Theorem~\ref{theorem:Tits-Vaserstein} below.
+Denote by $\mathcal{Z}$ the set of all $z_\alpha(s, \xi)$, $s\in I$, $\xi \in R$. 
+Our first application of parabolic factorizations is the following estimate of the width of $\G(\Phi, R, I)$ in terms of $\mathcal{Z}$.
 
@@
 \begin{enumerate}
-\item If $\sr(I) = 1$, then $w(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+3\rk\Phi$;
+\item If $\sr(I) = 1$, then $w(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+2\rk\Phi-1$;
 \item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$, and $\Phi$ is classical, then under the assumption of the Generalized Riemann Hypothesis $w(\E(\Phi,R,I),\mathcal{Z})\leqslant ???$;
@@
 \begin{proof}
-content...
+%In the proof of the above theorem we use Bass---Kolster decomposition to reduce to the case $\Phi=\rA_1$ which then can be settled directly.
+%Notice that the particular case $I=R$ of the above theorem was demonstrated in~\cite{VavSmSuUnitrEng} (see also \cite{VseUnitrZ1p}).
+...
 \end{proof}
-\noindent In the proof of the above theorem we use Bass---Kolster decomposition to reduce to the case $\Phi=\rA_1$ which then can be settled directly.
-Notice that the particular case $I=R$ of the above theorem was demonstrated in~\cite{VavSmSuUnitrEng} (see also \cite{VseUnitrZ1p}).
+The particular case $\Phi = \rA_l$, $R = \mathbb{Z}$ of the above theorem was considered by U.~Hadad in~\cite[Theorem~1.6]{Ha12}.
 
@@
 We also define $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w(-1)$. Then
-\[ h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R. \]
+\begin{equation}\label{rel:R6}
+h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R.
+\end{equation}
 
@@
 \[ \Hh(\Phi,R,I) = \Hh(\Phi,R)\cap\G(\Phi,R,I)=\langle h_\alpha(\varepsilon),\ \alpha\in\Phi,\ \varepsilon\in R^*\cap(1+I)\rangle. \]
-\begin{lemma}
+\begin{lemma}\label{lemma:rel-tor-elementary}
 $\Hh(\Phi,R,I)\leqslant\E(\Phi,R,I)$.

### 2015-08-20 paper.tex
Small typography and grammar/punctuation fixes

@@
 Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system with a fixed basis of simple roots $\Pi$.
-Denote by $G=\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over $R$ and by $\E(\Phi, R)$ its {\it elementary subgroup}, 
- i.\,e. the subgroup generated by root unipotents $t_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
-For an ideal $I \trianglelefteq R$ denote by $\G(\Phi, R, I)$ the {\it relative Chevalley group} (also called {\it principal congruence subgroup}) of level $I$, 
+Denote by $G=\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over $R$ and by $\E(\Phi, R)$ its \emph{elementary subgroup}, 
+i.\,e. the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
+For an ideal $I \trianglelefteq R$ denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (also called \emph{principal congruence subgroup}) of level $I$, 
 i.\,e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection $R\rightarrow R/I$.
@@
 \begin{itemize}
-\item {\it Gauss decomposition} i.\,e. decomposition of the form $\E(\Phi,R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup,
+\item \emph{Gauss decomposition,} i.\,e. a decomposition of the form $\E(\Phi,R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup,
       and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
-\item {\it Bass---Kolster} decomposition $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
+\item \emph{Bass---Kolster} decomposition $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
       $\Par_i$, $\Par_i^-$ are the opposite maximal parabolic subgroups of $\G$ corresponding to $i$-th simple root of $\Phi$ and $\U_i$, $\U_i^-$ are their unipotent radicals;
-\item {\it Dennis---Vaserstein} decomposition $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$,
+\item \emph{Dennis---Vaserstein} decomposition $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$,
       where $\EP_i$ denotes the subgroup generated by root unipotents $t_\alpha(\xi)$ contained in $\Par_i$.
@@
 Unfortunately, neither of these decompositions can be carried over to rings of higher dimension.
-The main advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of milder ring-theoretic assumptions formulated in terms of the {\it stable rank} of the ground ring.
+The main advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of milder ring-theoretic assumptions formulated in terms of the \emph{stable rank} of the ground ring.
 Their another advantage is that they prove useful in the study of asymptotical properties of Chevalley groups. We are going to discuss this theme in more detail below.
@@
 Let $G$ be an abstract group with a generating set $X \subset G$. 
-We denote by $W(G, X)$ the {\it width of $G$ with respect to $X$} i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
-The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $t_\alpha(\xi)$ has been extensively studied in a number of works (see e.\,g.
+We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
+The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $x_\alpha(\xi)$ has been extensively studied in a number of works (see e.\,g.
 \cite{CK83, Ka82, Tavgen91, Mo07, VseUnitrZ1p, VavSmSuUnitrEng}).
@@
 localizations of Dedeking rings of arithmetic type.
-For example, W.~van der Kallen has shown that the width of $\SL_3(R)$ is infinite already for a euclidean ring $R=\mathbb{C}[t]$.
+For example, W.~van der Kallen has shown that the width of $\SL_3(R)$ is infinite already for a Euclidean ring $R=\mathbb{C}[t]$.
 
@@
 \begin{enumerate}
-\item If $\sr(I) = 1$, then $w(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+2\rk\Phi-1$;
-\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$, and $\Phi$ is classical, then under the assumption of the Generalized Riemann Hypothesis $w(\E(\Phi,R,I),\mathcal{Z})\leqslant ???$;
-\item If $\mathcal{O}_S$ is a Dedekind ring of arithmetic type in some global field $k$ having a real embedding and $\rk\Phi\geqslant2$, then $w(\G(\Phi,\mathcal{O}_S,I),\mathcal{Z})$ is finite.
+\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+2\rk\Phi-1$;
+\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$, and $\Phi$ is classical, then under the assumption of the Generalized Riemann Hypothesis $W(\E(\Phi,R,I),\mathcal{Z})\leqslant ???$;
+\item If $\mathcal{O}_S$ is a Dedekind ring of arithmetic type in some global field $k$ having a real embedding and $\rk\Phi\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I),\mathcal{Z})$ is finite.
 \end{enumerate}
@@
 \end{proof}
-The particular case $\Phi = \rA_l$, $R = \mathbb{Z}$ of the above theorem was considered by U.~Hadad in~\cite[Theorem~1.6]{Ha12}.
+The particular case $\Phi = \rA_\ell$, $R = \mathbb{Z}$ of the above theorem was considered by U.~Hadad in~\cite[Theorem~1.6]{Ha12}.
 
 The second application concerns subsystem factorizations of Chevalley groups formulated in terms of submaximal subgroups of type $\rA_\ell$.
-The case when $R=I$ is a field this question was studied by N.~Nikolov in \cite{NikProdDecomp}. 
+In case when $R=I$ is a field this question was studied by N.~Nikolov in \cite{NikProdDecomp}. 
 \begin{thm*} Let $G$ be a classical Chevalley group (of normal or twisted type) of rank $n$ over a finite field.
@@
 
-It is also classically known that over arbitrary field $F$ the group $\SL(n+1, F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
+It is also classically known that over an arbitrary field $F$ the group $\SL(n+1, F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
 On the other hand, from the classical Dennis---Vaserstein theorem (see~\cite{Va69} and \cite[Lemma~2.1]{ST76})
-it follows that $\SL_{n+1}(R, I)$ is a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leq n-1$.
+it follows that $\SL_{n+1}(R, I)$ is a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
 Using another Dennis---Vaserstein type factorization we obtain the following result.

### 2015-08-23 paper.tex
Minor changes

@@
       and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
-\item \emph{Bass---Kolster} decomposition $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
+\item \emph{Bass---Kolster decomposition} $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
       $\Par_i$, $\Par_i^-$ are the opposite maximal parabolic subgroups of $\G$ corresponding to $i$-th simple root of $\Phi$ and $\U_i$, $\U_i^-$ are their unipotent radicals;
-\item \emph{Dennis---Vaserstein} decomposition $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$,
-      where $\EP_i$ denotes the subgroup generated by root unipotents $t_\alpha(\xi)$ contained in $\Par_i$.
+\item \emph{Dennis---Vaserstein decomposition} $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$,
+      where $\EP_i$ denotes the subgroup generated by root unipotents $x_\alpha(\xi)$ contained in $\Par_i$.
 \end{itemize}
@@
 On the other hand, much less is known about the width of relative groups $\G(\Phi, R, I)$. 
-It is a classical result of J.~Tits and L.~Vaserstein that the relative elementary group $\E(\Phi, R, I)$ is generated by elements $z_\alpha(s,\xi)=t_{\alpha}(s)^{t_{-\alpha}(\xi)}$, see Theorem~\ref{theorem:Tits-Vaserstein} below.
+It is a classical result of J.~Tits and L.~Vaserstein that the relative elementary group $\E(\Phi, R, I)$ is generated by elements $z_\alpha(s,\xi)=x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, see Theorem~\ref{theorem:Tits-Vaserstein} below.
 Denote by $\mathcal{Z}$ the set of all $z_\alpha(s, \xi)$, $s\in I$, $\xi \in R$. 
@@
 
-The second application concerns subsystem factorizations of Chevalley groups formulated in terms of submaximal subgroups of type $\rA_\ell$.
+Another application of parabolic factorizations developed in this paper are subsystem factorizations in terms of subgroups of type $\rA_1$.
+The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
+More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
+In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
+In fact, Gauss decomposition (see~\cite{Sm12}) implies a similar factorization for the elementary subgroup $\E(\Phi, R)$ with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.
+
+\begin{thm} Let $I$ be an ideal of a commutative ring $R$ such that $\sr(I)\leq N$. Assume that one of the following is true:
+\begin{itemize} 
+\item $\Phi=\rA_\ell$, $\ell\geq 2$, $\sr(I)\leq 2$;
+\item $\Phi=\rC_\ell$, $\ell\geq 2$, $\sr(I)\leq 3$; \end{itemize}
+Then $\G(\Phi, R, I)$ equals the product of at most $3|\Phi^+| + A\rk(\Phi) + B$ copies of subgroups of type $\G(\rA_1, R, I)$. \end{thm}
+
+Yet another application of parabolic factorizations concerns subsystem factorizations of Chevalley groups formulated in terms of submaximal subgroups of type $\rA_\ell$.
 In case when $R=I$ is a field this question was studied by N.~Nikolov in \cite{NikProdDecomp}. 
@@
 \begin{thm} Assume that $\sr(I) = 2$ then the group $\Spin_{2\ell}(R, I)=\G_{sc}(\rD_\ell, R, I)$ is a product of at most $C$ copies of subgroups of type $\rA_{\ell-1}$. \end{thm}
-
-Another applications of parabolic factorizations developed in this paper are subsystem factorizations in terms of subgroups of type $\rA_1$.
-The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
-More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
-In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
-In fact, Gauss decomposition (see~\cite{Sm12}) implies a similar factorization for the elementary subgroup $\E(\Phi, R)$ with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.
-
-\begin{thm} Let $I$ be an ideal of a commutative ring $R$ such that $\sr(R)\leq n$, where
-\begin{itemize}
- \item $n=1$ and $\Phi$ is either classical or of type $\rE_\ell$;
- \item $n=2, 3$ and $\Phi$ is simply laced.
-\end{itemize}
-Then $\G(\Phi, R, I)$ is a product of at most $q_{n}(\Phi)$ copies of $\SL_{n+1}(R, I)$, where each $q_{n}(\Phi)$, $n=1,2,3$ is a quadratic function of $\rk(\Phi)$ given in Table~XXX.
-\end{thm}
 
@@
 \input{congrsubgr-boundgen}
-\subsection{Subsystem factorizations}\label{sec:subsysfact}
-\input{subsystem-factorizations}
+%\subsection{Subsystem factorizations}\label{sec:subsysfact}
+%\input{subsystem-factorizations}
 

### 2015-08-24 bass-kolster.tex
Written proof for Theorem 2

@@
 \[ \G(\Phi,R,I)=  \U(\Phi^+,I) \cdot \U(\Phi^-,I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I), \]
-where $\Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\ \middle|\ r\in I \right\}$.
+where $Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\ \middle|\ r\in I \right\}$.
 \end{thm}
@@
 The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{thm:SL2width}]
+Consider the case $\Phi=\rA_\ell$, $\sr(I)\leq 2$. First of all, notice that we can improve the estimate of the number of factors involved in Bass---Kolster decomposition.
+Indeed, when performing the first step of the proof of Theorem~\ref{thm:BassKolster} it suffices to make only $2$ additions of $v_{\ell+1}$ (e.\,g.
+to $v_{1}$ and $v_2$) to make the first $\ell$ entries of $v'$ form a unimodular column.
+In particular, $\G(\Phi, R, I)$ can be presented as a product of one element of $\G(\Delta_1, R, I)$, one element of $Z$ and $3\ell+1$ root unipotents $x_\alpha(s)$, $s\in I$.
+The latter elements are contained in a product of $3\ell + 1$ copies of $\SL_2(R, I)$. Now the statement of the theorem follows by induction on $\ell$.
+
+The proof in the case $\Phi=\rC_\ell$ is similar (notice that we use the exceptional isomorphism $\SL_2\cong \Sp_2$).
+\end{proof}

### 2015-08-24 paper.tex
Written proof for Theorem 2

@@
 Another application of parabolic factorizations developed in this paper are subsystem factorizations in terms of subgroups of type $\rA_1$.
-The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
+The case of a finite field $R=F$ was exhaustively studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
 More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
 In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
-In fact, Gauss decomposition (see~\cite{Sm12}) implies a similar factorization for the elementary subgroup $\E(\Phi, R)$ with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.
+In fact, Gauss decomposition (see~\cite{Sm12}) implies a similar factorization for the elementary subgroup $\E(\Phi, R)$ 
+with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.
 
-\begin{thm} Let $I$ be an ideal of a commutative ring $R$ such that $\sr(I)\leq N$. Assume that one of the following is true:
+In the linear and symplectic case the above results can be extended to even larger class of rings (which includes all Dedekind rings, for example).
+\begin{thm}\label{thm:SL2width}
+Assume that one of the following is true:
 \begin{itemize} 
-\item $\Phi=\rA_\ell$, $\ell\geq 2$, $\sr(I)\leq 2$;
-\item $\Phi=\rC_\ell$, $\ell\geq 2$, $\sr(I)\leq 3$; \end{itemize}
-Then $\G(\Phi, R, I)$ equals the product of at most $3|\Phi^+| + A\rk(\Phi) + B$ copies of subgroups of type $\G(\rA_1, R, I)$. \end{thm}
+\item $I$ is an ideal of a (not neccessarily commutative) ring $R$ such that $\sr(I)\leq 2$, $\Phi=\rA_\ell$, $l\geq 2$, $N=3|\Phi^+|+\rk(\Phi) - 3$.
+\item $I$ is an ideal of a commutative ring $R$ such that $\sr(I)\leq 3$, $\Phi=\rC_\ell$, $l\geq 2$, $N=3|\Phi^+|+2\rk(\Phi) - 4$
+\end{itemize}
+Then $\G(\Phi, R, I)$ can be presented as a product of at most $N$ copies of its subgroups isomorphic to $\G(\rA_1, R, I)$. \end{thm}
 

### 2015-08-24 paper.tex
Slightly reorganized exposition

@@
 \DeclareMathOperator{\asr}{asr}
-%TODO: Deprecate Um -- Use Ums/Umd whenever possible
-\DeclareMathOperator{\Um}{Um}
 \DeclareMathOperator{\Ums}{Ums}
@@
 
-\title{Relative parabolic factorizations of Chevalley groups}
+\title [Parabolic factorizations of congruence subgroups ] {Parabolic factorizations and width of congruence subgroups in Chevalley groups}
 \keywords {Chevalley groups, relative subgroups, stability for $\K_1$. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
@@
 On the other hand, much less is known about the width of relative groups $\G(\Phi, R, I)$. 
-It is a classical result of J.~Tits and L.~Vaserstein that the relative elementary group $\E(\Phi, R, I)$ is generated by elements $z_\alpha(s,\xi)=x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, see Theorem~\ref{theorem:Tits-Vaserstein} below.
-Denote by $\mathcal{Z}$ the set of all $z_\alpha(s, \xi)$, $s\in I$, $\xi \in R$. 
-Our first application of parabolic factorizations is the following estimate of the width of $\G(\Phi, R, I)$ in terms of $\mathcal{Z}$.
+Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
+It is a classical result of J.~Tits and L.~Vaserstein (see e.\,g. Theorem~\cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
+the set of elements $\mathcal{Z} = \{ z_\alpha(s,\xi) \mid \alpha \in \Phi,\ s\in I,\ \xi \in R \}.$
+Recently, A.~Stepanov has shown that, in fact, a more economical set of generators can be chosen for $\E(\Phi, R, I)$ (see~\cite[Theorem~3.4]{S}).
+\begin{thm}
+Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S$ be any parabolic subset of roots of $\Phi$ with the special part $\Sigma_S$ (see section~\ref{sec:rootsys}).
+Denote by $\mathcal{Z}(\Sigma_S)$ the subset of $\mathcal{Z}$ consisting of the following two families of elements:
+\begin{itemize}
+\item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
+\item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
+\end{itemize}
+Then $\E(\Phi, R, I)$ is generated (as an abstract group) by $\mathcal{Z}(\Sigma_S)$.
+\end{thm}
 
+Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\G(\Phi, R, I)$ in terms $\mathcal{Z}$.
 \begin{thm} Let $\Phi$ be a root system, and let $I$ be an ideal of a commutative ring $R$.
@@
 \item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+2\rk\Phi-1$;
-\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$, and $\Phi$ is classical, then under the assumption of the Generalized Riemann Hypothesis $W(\E(\Phi,R,I),\mathcal{Z})\leqslant ???$;
-\item If $\mathcal{O}_S$ is a Dedekind ring of arithmetic type in some global field $k$ having a real embedding and $\rk\Phi\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I),\mathcal{Z})$ is finite.
+\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$, and $\Phi$ is classical, then under the assumption of the Generalized Riemann Hypothesis $W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell))\leqslant ???$;
+\item If $\mathcal{O}_S$ is a Dedekind ring of arithmetic type in some global field $k$ having a real embedding and $\rk\Phi\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell))$ is finite.
 \end{enumerate}
@@
 \begin{proof}
+
 %In the proof of the above theorem we use Bass---Kolster decomposition to reduce to the case $\Phi=\rA_1$ which then can be settled directly.
@@
 \end{proof}
-The particular case $\Phi = \rA_\ell$, $R = \mathbb{Z}$ of the above theorem was considered by U.~Hadad in~\cite[Theorem~1.6]{Ha12}.
+The particular case $\Phi = \rA_\ell$, $R = I = \mathbb{Z}$ of the above theorem is similar to a recent theorem of U.~Hadad (see ~\cite[Theorem~1.6]{Ha12}).
 
@@
 
-\subsection{Root systems}
+\subsection{Root systems}\label{sec:rootsys}
 Let $\Pi=\{\alpha_1, \ldots, \alpha_l\}$ be a basis of $\Phi$. Denote by $\Phi^+$ and $\Phi^-$ subsets of positive and negative roots with respect to $\Pi$.
@@
 Denote by $z_\alpha(s, \xi)$ the element $x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$.
-The following result of L.~Vaserstein and J.~Tits describes a set of generators of $\E(\Phi, R, I)$ (see e.\,g.~\cite[Theorem~2]{Va86}).
 
-\begin{thm}\label{theorem:Tits-Vaserstein} Let $\Phi$ be an irreducible root system of rank $\geq 2$, then the relative elementary subgroup $\E(\Phi, R, I)$
-is generated by the elements $z_\alpha(s, \xi)$, $\alpha\in \Phi$, $s\in I$, $\xi\in R$.
-\end{thm}
+%The following result of L.~Vaserstein and J.~Tits describes a set of generators of $\E(\Phi, R, I)$ (see e.\,g.~\cite[Theorem~2]{Va86}).
+%\begin{thm}\label{theorem:Tits-Vaserstein} Let $\Phi$ be an irreducible root system of rank $\geq 2$, then the relative elementary subgroup $\E(\Phi, R, I)$
+%is generated by the elements $z_\alpha(s, \xi)$, $\alpha\in \Phi$, $s\in I$, $\xi\in R$. \end{thm}
 
-In fact, one can choose a more economical set of generators for $\E(\Phi, R, I)$ (see~\cite[Theorem~3.4]{S}).
-\begin{thm}\label{theorem:Stepanov}
-Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S$ be any parabolic subset of roots of $\Phi$ with the special part $\Sigma_S$.
-Then $\E(\Phi, R, I)$ is generated by the union of the following two families of elements:
-\begin{itemize}
-\item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
-\item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
-\end{itemize}
-\end{thm}
+%In fact, one can choose a more economical set of generators for $\E(\Phi, R, I)$ (see~\cite[Theorem~3.4]{S}).
+%\begin{thm}\label{theorem:Stepanov}
+%Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S$ be any parabolic subset of roots of $\Phi$ with the special part $\Sigma_S$.
+%Then $\E(\Phi, R, I)$ is generated by the union of the following two families of elements:
+%\begin{itemize}
+%\item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
+%\item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
+%\end{itemize}
+%\end{thm}
 
@@
 
-\section{Applications}\label{sec:applications}
-\subsection{Bounded generation}\label{sec:boundgen}
+%\section{Applications} %\label{sec:applications}
+\section{Bounded generation}\label{sec:boundgen}
 \input{congrsubgr-boundgen}

### 2015-08-26 congrsubgr-boundgen.tex
Added exceptional isomorphisms

@@
 \[ \E(\Phi,R,I) = \Hh(\Phi,R,I) \U(\Phi,I)\U^-(\Phi,I)\U(\Phi,I). \]
-As a corollary, the width of $\E(\Phi,R,I)$ with respect to generators $z_\alpha(s,\xi)$ of Theorem~\ref{theorem:Tits-Vaserstein} does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
+As a corollary, the width of $\E(\Phi,R,I)$ with respect to the generating set $\mathcal{Z}$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
 \end{lemma}
@@
 \begin{lemma}\label{lemma:Z1p}
-Let $R=\mathbb{Z}[\sfrac{1}{p}]$ and let $I$ be an ideal of $R$.
-Under the assumption of GRH the width of $\SL(2,R,I)$ with respect to generators $z_\alpha(s, \xi)$ of Theorem~\ref{theorem:Tits-Vaserstein} does not exceed $6$.
+Set $R=\mathbb{Z}[\sfrac{1}{p}]$ and let $I$ be an ideal of $R$.
+Under the assumption of GRH the width of $\SL(2,R,I)$ with respect to the generating set $$\mathcal{Z}(\Sigma_1)=X_{12}(I)\cup X_{21}(I) \cup \{z_{21}(s, \xi) \mid s\in I,\ \xi\in R\}$$ does not exceed $6$.
 \end{lemma}
@@
 \begin{proof}
-Clearly, $I$ is a principal ideal generated by some $m\in\mathbb{Z}$ not divisible by $p$.
+Clearly, $I$ is a principal ideal generated by some integer $m\in\mathbb{Z}$ not divisible by $p$.
 Let $g$ be an element of $\SL(2,R,I)$. Write
@@
 %Now it is easy to derive bounded generation property for $\G(\Phi,\mathcal{O}_S,I)$ from the above statements.
-\begin{lemma}
-Let $\Phi$ be a classical root system of rank $\geqslant 2$.
-If $k$ has a real embedding, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to generators $z_\alpha(s, \xi)$ of Theorem~\ref{theorem:Tits-Vaserstein}.
+\begin{lemma}\ref{lemma:width-dedekind}
+Let $\Phi$ be an irreducible classical root system of rank $\ell \geqslant 2$.
+If $k$ has a real embedding, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to the generating set $\mathcal{Z}(\Sigma_\ell)$.
 \end{lemma}
@@
 First of all, notice that $\asr(I) \leq \asr(\mathcal{O}_S) \leq 2$. 
-By Theorem~\ref{thm:BassKolster} we can present any element of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators $z_\alpha(s, \xi)$ and one element of $G_0=\G(\rA_1, \mathcal{O}_S, I)=\SL(2,\mathcal{O}_S,I)$.
+Inductively applying Theorem~\ref{thm:BassKolster} and using exceptional isomorphisms for small-rank groups we can present any element of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators from $\mathcal{Z}(\Sigma_\ell}$ and one element of $\G(\{\alpha_\ell, -\alpha_\ell\} \mathcal{O}_S, I)\cong\SL(2,\mathcal{O}_S,I)$.
 Consequently, to prove the statement of the lemma it suffices to express every element $g = \begin{psmallmatrix}1+a & b \\ c & 1+d \end{psmallmatrix} \in G_0$ as a product of a finite number of generators contained in some rank $2$ subgroup of $G$ containing $G_0$.

### 2015-08-26 paper.tex
Added exceptional isomorphisms

@@
 
-\title [Parabolic factorizations of congruence subgroups ] {Parabolic factorizations and width of congruence subgroups in Chevalley groups}
+\title [Parabolic factorizations of congruence subgroups] {Parabolic factorizations and width of congruence subgroups in Chevalley groups}
 \keywords {Chevalley groups, relative subgroups, stability for $\K_1$. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
@@
 Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\G(\Phi, R, I)$ in terms $\mathcal{Z}$.
-\begin{thm} Let $\Phi$ be a root system, and let $I$ be an ideal of a commutative ring $R$.
+\begin{thm} Let $\Phi$ be an irreducible root system, and let $I$ be an ideal of a commutative ring $R$.
 \begin{enumerate}
-\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+2\rk\Phi-1$;
-\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime $p$, and $\Phi$ is classical, then under the assumption of the Generalized Riemann Hypothesis $W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell))\leqslant ???$;
-\item If $\mathcal{O}_S$ is a Dedekind ring of arithmetic type in some global field $k$ having a real embedding and $\rk\Phi\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell))$ is finite.
+\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
+\item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume that $\Phi$ is classical, then under the assumption of the Generalized Riemann Hypothesis one has $W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 6$;
+\item If $\mathcal{O}_S$ is a Dedekind ring of arithmetic type in some global field $k$ having a real embedding and $\rk(\Phi)\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell))$ is finite.
 \end{enumerate}
@@
 
-In the linear and symplectic case the above results can be extended to even larger class of rings (which includes all Dedekind rings, for example).
+In the linear and symplectic case the above results can be extended to even larger class of rings (which e.\,g. includes all Dedekind rings).
 \begin{thm}\label{thm:SL2width}
@@
 \subsection{Chevalley groups}
-Our exposition of Chevalley groups is standard and follows (...).
-\textbf{TODO: Write more about Chevalley groups}
+Our exposition of Chevalley groups is standard and follows~\cite{Ta, S, St78, VP, Va86}.
+We denote by $\G(\Phi, R)$ the simply-connected split Chevalley group of type $\Phi$ over arbitrary commutative ring $R$.
+For example, for each of the four classical series $\Phi=\rA_\ell, \rB_\ell, \rC_\ell, \rD_\ell$ the group $\G(\Phi, R)$ equals $\SL(\ell+1, R)$, $\Spin(2\ell+1, R)$, $\Sp(2\ell, R)$, $\Spin(2\ell, R)$, respectively.
+Notice that from the uniqueness theorem of M.~Demazure (see~\cite[Corollaire~5.2]{SGA3}) it follows that the exceptional isomorphisms of small-rank groups (which are well-known in the theory of groups over fields) remain valid for Chevalley groups over arbitrary commutative rings $R$.
+In particular there are isomorphisms of groups $\Spin(5, R)\cong \Sp(4, R)$, $\Spin(6, R)\cong\SL(4, R)$ $\SL(2, R)\cong \Sp(2, R)$.
 
-In this paper we work with the irreducible representations of Chevalley groups corresponding to the highest weight
-$\varpi_1$ (in the case of a classical $\Phi_\ell$) or $\varpi_\ell$ (in the case $\Phi_\ell=\rE_\ell$). 
-The former are the natural vector representations of the classical groups acting on the free modules $V=R^n$ of dimension 
-$n=\ell+1, 2\ell+1, 2\ell,2\ell$ for $\Phi=\rA_\ell,\rB_\ell,\rC_\ell,\rD_\ell$ respectively.
+In this paper we work with the irreducible representations of Chevalley groups with the highest weight
+$\varpi_1$ (in the case of a classical $\Phi$) or $\varpi_\ell$ (in the case $\Phi=\rE_\ell$, $\ell=6,7$).
+The former are the natural vector representations of classical groups acting on free modules $V=R^n$ of dimension $n=\ell+1, 2\ell+1, 2\ell,2\ell$ for $\Phi=\rA_\ell,\rB_\ell,\rC_\ell,\rD_\ell$ respectively.
 The latter are the microweight representations of dimension $n=27, 56$ for $\ell=6,7$.
@@
 
-It will be convenient to use the standard numbering for the weights of the natural representations of the classical groups (cp.~\cite[§1B]{St78}):
+It will be convenient to use the standard numbering for the weights of the natural representations of classical groups (cp.~\cite[§1B]{St78}):
 \[\begin{array}{cll}

### 2015-08-26 congrsubgr-boundgen.tex
Minor fixes

@@
 First of all, notice that $\asr(I) \leq \asr(\mathcal{O}_S) \leq 2$. 
-Inductively applying Theorem~\ref{thm:BassKolster} and using exceptional isomorphisms for small-rank groups we can present any element of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators from $\mathcal{Z}(\Sigma_\ell}$ and one element of $\G(\{\alpha_\ell, -\alpha_\ell\} \mathcal{O}_S, I)\cong\SL(2,\mathcal{O}_S,I)$.
+Inductively applying Theorem~\ref{thm:BassKolster} and using exceptional isomorphisms for small-rank groups we can present any element of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators from $\mathcal{Z}(\Sigma_\ell)$ and one element of $\G(\{\alpha_\ell, -\alpha_\ell\} \mathcal{O}_S, I)\cong\SL(2,\mathcal{O}_S,I)$.
 Consequently, to prove the statement of the lemma it suffices to express every element $g = \begin{psmallmatrix}1+a & b \\ c & 1+d \end{psmallmatrix} \in G_0$ as a product of a finite number of generators contained in some rank $2$ subgroup of $G$ containing $G_0$.

### 2015-08-26 paper.tex
Minor fixes

@@
 
-Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\G(\Phi, R, I)$ in terms $\mathcal{Z}$.
+Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\G(\Phi, R, I)$ in terms of $\mathcal{Z}$.
 \begin{thm} Let $\Phi$ be an irreducible root system, and let $I$ be an ideal of a commutative ring $R$.
@@
 \item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
-\item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume that $\Phi$ is classical, then under the assumption of the Generalized Riemann Hypothesis one has $W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 6$;
-\item If $\mathcal{O}_S$ is a Dedekind ring of arithmetic type in some global field $k$ having a real embedding and $\rk(\Phi)\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell))$ is finite.
+\item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume $\Phi$ is classical.
+Then under the assumption of the Generalized Riemann Hypothesis there is an estimaete  $W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1$;
+\item Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type embedded into some global field $k$ having a real embedding.
+Assume that $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell))$ is finite.
 \end{enumerate}
@@
 \end{proof}
-The particular case $\Phi = \rA_\ell$, $R = I = \mathbb{Z}$ of the above theorem is similar to a recent theorem of U.~Hadad (see ~\cite[Theorem~1.6]{Ha12}).
+The particular case $\Phi = \rA_\ell$, $R = I = \mathbb{Z}$ of the above theorem is similar in spirit to a recent theorem of U.~Hadad (see ~\cite[Theorem~1.6]{Ha12}).
 
@@
 On the other hand, from the classical Dennis---Vaserstein theorem (see~\cite{Va69} and \cite[Lemma~2.1]{ST76})
-it follows that $\SL_{n+1}(R, I)$ is a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
+it follows that $\SL(n+1, R, I)$ is a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
 Using another Dennis---Vaserstein type factorization we obtain the following result.

### 2015-08-26 bass-kolster.tex
Slight changes in the notation; further reorganization

@@
 one has $\bar{v'}_+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, I)$.
-Now the proof can be finished by repeating the argument for the case $\Phi=\rD_l$ (applied to the subset of long roots of $\rB_\ell$).
+Now the proof can be finished by repeating the argument for the case $\Phi=\rD_\ell$ (applied to the subset of long roots of $\rB_\ell$).
 %(clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ under the natural embedding $\rD_\ell\subseteq\rB_\ell$). 
@@
 In the assumptions and notation of Theorem~\ref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
-can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $n(\Phi)$ elementary root unipotents $x_\alpha(s)$ of level $I$, where
-$n(\rA_\ell)= 4 \ell - 1$, $n(\rB_\ell)= 8 \ell - 5$, $n(\rC_\ell)= 8 \ell - 5$, $n(\rD_\ell)= 8 \ell - 9$. \end{cor}
+can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4(|\Phi^+| - |\Delta_1^+|)-1$ elementary root unipotents $x_\alpha(s)$ of level $I$. \end{cor}
 \begin{proof}
@@
 Summing up these upper bounds we obtain
-$$n(\rD_\ell) = (2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9.$$
+$$(2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9 = 4(|\rD_\ell| - |\rD_{\ell-1}|) - 1.$$
 
@@
 In particular, $\G(\Phi, R, I)$ can be presented as a product of one element of $\G(\Delta_1, R, I)$, one element of $Z$ and $3\ell+1$ root unipotents $x_\alpha(s)$, $s\in I$.
-The latter elements are contained in a product of $3\ell + 1$ copies of $\SL_2(R, I)$. Now the statement of the theorem follows by induction on $\ell$.
+The latter elements are contained in a product of $3\ell + 1$ copies of $\SL(2, R, I)$. Now the statement of the theorem follows by induction on $\ell$.
 
-The proof in the case $\Phi=\rC_\ell$ is similar (notice that we use the exceptional isomorphism $\SL_2\cong \Sp_2$).
+The proof in the case $\Phi=\rC_\ell$ is similar (notice that we use the exceptional isomorphism $\SL(2, R)\cong \Sp(2, R)$).
 \end{proof}

### 2015-08-26 congrsubgr-boundgen.tex
Slight changes in the notation; further reorganization

@@
 
-\begin{lemma}\label{lemma:srRI1}
-Let $\Phi$ be a root system, $I$ be an ideal of $R$ such that $\sr(I)=1$. Then the relative elementary Chevalley group admits Gauss decomposition
-\[ \E(\Phi,R,I) = \Hh(\Phi,R,I) \U(\Phi,I)\U^-(\Phi,I)\U(\Phi,I). \]
-As a corollary, the width of $\E(\Phi,R,I)$ with respect to the generating set $\mathcal{Z}$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
+\begin{lemma}\label{lemma:srRI1_width} In the assumptions of Lemma~\ref{lemma:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
 \end{lemma}
 \begin{proof}
-Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}\in\SL(2,R,I)$ be an element of $\SL(2, R, I)$.
-The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
-Multiplying $A$ on the left by $x_{12}(z)$ we get matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible top-left corner element $a'$.
-After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
-Thus we obtain relative Gauss decomposition of $A$
-\begin{equation}\nonumber
-A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
-\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
-\cdot x_{12}(b'/a')=x_{12}(-z)\cdot
-\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
-\cdot x_{21}(y) \cdot x_{12}(b'/a'),
-\end{equation}
-where $\varepsilon\in 1+I$ and $y\in I$. Theorem~\ref{thm:Gauss} implies that the Gauss decomposition of length $3$ hold for every relative elementary Chevalley group.
-
-To obtain the width estimates fix an element $g\in\E(\Phi,R,I)$ and decompose it into $g=u_1 h v_2 u_3$, where $h\in\Hh(\Phi,R,I)$, $u_1,u_3\in\U(\Phi,I)$, $v_2\in\U^-(\Phi,I)$.
+Take an element $g\in\E(\Phi,R,I)$ and decompose it into $g=u_1 h v_2 u_3$, where $h\in\Hh(\Phi,R,I)$, $u_1,u_3\in\U(\Phi,I)$, $v_2\in\U(\Phi^-,I)$. 
 Write $h=\prod_{i=1}^\ell h_{\alpha_i}(\varepsilon_i)$, $\varepsilon\in1+I$. 
-Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $\X_\alpha(I)$ (see formula~\ref{rel:R6}), we have a decomposition
+Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
+ (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $\X_\alpha(I)$ (see formula~\ref{rel:R6}), we have a decomposition
 \[ g\in\U(\Phi,I)\cdot\prod_{\i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
-and the estimate follows.
-%
-%
-%Direct calculation shows that
-%\begin{multline*}
-%\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix} =
-%\begin{pmatrix} 1 & -1 \\ 0 & 1 \end{pmatrix}
-%\begin{pmatrix} 1 & 0 \\ 1-\varepsilon & 1 \end{pmatrix}
-%\begin{pmatrix} 1 & 1/\varepsilon \\ 0 & 1 \end{pmatrix}
-%\begin{pmatrix} 1 & 0 \\ \varepsilon^2-\varepsilon & 1 \end{pmatrix} =\\=
-%\begin{pmatrix} 1 & -1 \\ 0 & 1 \end{pmatrix}
-%\begin{pmatrix} 1 & 0 \\ 1-\varepsilon & 1 \end{pmatrix}
-%\begin{pmatrix} 1 & 1+z \\ 0 & 1 \end{pmatrix}
-%\begin{pmatrix} 1 & 1/\varepsilon-1-z \\ 0 & 1 \end{pmatrix}
-%\begin{pmatrix} 1 & 0 \\ \varepsilon^2-\varepsilon & 1 \end{pmatrix},
-%\end{multline*}
-%therefore
-%\[ A=z_{21}(1-\varepsilon,-1-z)\cdot x_{12}(1/\varepsilon-1-z)\cdot x_{21}(\varepsilon^2-\varepsilon+y)\cdot x_{12}(b'/a'), \]
-%which simultaneously implies both statements of the lemma.
-\end{proof}
+and the estimate follows. \end{proof}
 
@@
 %Now it is easy to derive bounded generation property for $\G(\Phi,\mathcal{O}_S,I)$ from the above statements.
-\begin{lemma}\ref{lemma:width-dedekind}
+\begin{lemma}\label{lemma:width-dedekind}
 Let $\Phi$ be an irreducible classical root system of rank $\ell \geqslant 2$.
@@
 First of all, notice that $\asr(I) \leq \asr(\mathcal{O}_S) \leq 2$. 
-Inductively applying Theorem~\ref{thm:BassKolster} and using exceptional isomorphisms for small-rank groups we can present any element of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators from $\mathcal{Z}(\Sigma_\ell)$ and one element of $\G(\{\alpha_\ell, -\alpha_\ell\} \mathcal{O}_S, I)\cong\SL(2,\mathcal{O}_S,I)$.
-Consequently, to prove the statement of the lemma it suffices to express every element $g = \begin{psmallmatrix}1+a & b \\ c & 1+d \end{psmallmatrix} \in G_0$ as a product of a finite number of generators contained in some rank $2$ subgroup of $G$ containing $G_0$.
+Inductively applying Theorem~\ref{thm:BassKolster} and using exceptional isomorphisms for small-rank groups we can present any element 
+of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators from $\mathcal{Z}(\Sigma_\ell)$ and one element of 
+$\G(\{\alpha_\ell, -\alpha_\ell\}, \mathcal{O}_S, I)\cong\SL(2,\mathcal{O}_S,I)$.
+Consequently, to prove the statement of the lemma it suffices to express every element 
+$g = \begin{psmallmatrix}1+a & b \\ c & 1+d \end{psmallmatrix} \in G_0$
+as a product of a finite number of generators contained in some rank $2$ subgroup of $G$ containing $G_0$.
 
@@
 \end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{thm:width}] The first statement of the theorem is contained in Lemma~\ref{lemma:srRI1_width}.
+The second and third statement follow from Lemmas~\ref{lemma:Z1p}--\ref{lemma:width-dedekind}. \end{proof}

### 2015-08-26 gauss.tex
Slight changes in the notation; further reorganization

@@
-\begin{thm}\label{thm:Gauss}
+The proof of Gauss decomposition presented below is similar to the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
+
+\begin{prop}\label{thm:Gauss}
 Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1, \Delta_\ell$ be
@@
 \[ \E(\Phi, R, I) = \Hh(\Phi,R,I) \cdot \U(\Phi^+,I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm,I). \]
-\end{thm}
+\end{prop}
 \begin{proof}
@@
 \end{proof}
+
+\begin{lemma}\label{lemma:srRI1}
+Let $\Phi$ be a root system, let $I$ be an ideal of arbitrary commutative ring $R$ such that $\sr(I)=1$.
+Then the relative elementary Chevalley group admits Gauss decomposition
+\[ \E(\Phi,R,I) = \Hh(\Phi,R,I) \cdot \U(\Phi,I) \cdot \U(\Phi^-,I) \cdot \U(\Phi,I). \]
+\end{lemma}
+\begin{proof}
+In view of the above proposition it suffices to prove that Gauss decomposition of length $3$ holds for $\Phi=\rA_1$.
+
+Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}\in\SL(2,R,I)$ be an element of $\SL(2, R, I)$.
+The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
+Multiplying $A$ on the left by $x_{12}(z)$ we get matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible top-left corner element $a'$.
+After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
+Thus we obtain relative Gauss decomposition of $A$
+\begin{equation}\nonumber
+A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
+\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
+\cdot x_{12}(b'/a')=x_{12}(-z)\cdot
+\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
+\cdot x_{21}(y) \cdot x_{12}(b'/a'),
+\end{equation}
+where $\varepsilon\in 1+I$ and $y\in I$. \end{proof}

### 2015-08-26 paper.tex
Slight changes in the notation; further reorganization

@@
 localizations of Dedeking rings of arithmetic type.
-For example, W.~van der Kallen has shown that the width of $\SL_3(R)$ is infinite already for a Euclidean ring $R=\mathbb{C}[t]$.
+For example, W.~van der Kallen has shown that the width of $\SL(3,R)$ is infinite already for a Euclidean ring $R=\mathbb{C}[t]$.
 
-On the other hand, much less is known about the width of relative groups $\G(\Phi, R, I)$. 
+On the other hand, much less is known about the width of the relative group $\G(\Phi, R, I)$. 
 Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
-It is a classical result of J.~Tits and L.~Vaserstein (see e.\,g. Theorem~\cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
+It is a classical result of J.~Tits and L.~Vaserstein (see e.\,g.~\cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
 the set of elements $\mathcal{Z} = \{ z_\alpha(s,\xi) \mid \alpha \in \Phi,\ s\in I,\ \xi \in R \}.$
-Recently, A.~Stepanov has shown that, in fact, a more economical set of generators can be chosen for $\E(\Phi, R, I)$ (see~\cite[Theorem~3.4]{S}).
-\begin{thm}
-Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S$ be any parabolic subset of roots of $\Phi$ with the special part $\Sigma_S$ (see section~\ref{sec:rootsys}).
-Denote by $\mathcal{Z}(\Sigma_S)$ the subset of $\mathcal{Z}$ consisting of the following two families of elements:
-\begin{itemize}
-\item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
-\item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
-\end{itemize}
-Then $\E(\Phi, R, I)$ is generated (as an abstract group) by $\mathcal{Z}(\Sigma_S)$.
-\end{thm}
 
-Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\G(\Phi, R, I)$ in terms of $\mathcal{Z}$.
-\begin{thm} Let $\Phi$ be an irreducible root system, and let $I$ be an ideal of a commutative ring $R$.
+In fact, one can choose a smaller set of generators for $\E(\Phi, R, I)$. 
+Let $\Sigma$ be any special subset of $\Phi$, (e.\,g. the set of simple roots $\Pi$ or the special part of $\Sigma_S$ of some parabolic subset of roots $S$, see section~\ref{sec:rootsys}).
+Set $$\mathcal{X} = \{ x_\alpha(s) \mid \alpha\in \Phi,\ s\in I\};\ \ \mathcal{Z}(\Sigma) = \{ z_\alpha(s, \xi) \mid s \in I,\ \xi \in R, \alpha\in \Sigma \} \cup \mathcal{X}.$$
+
+Now we are ready to state a recent theorem of A.~Stepanov (see~\cite[Theorem~3.4]{S}).  
+\begin{thm}\label{thm:Stepanov} Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S \subset \Phi$ be any parabolic subset of roots.
+Then $\E(\Phi, R, I)$ is generated as an abstract group by $\mathcal{Z}(\Sigma_S)$. \end{thm}
+
+Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\G(\Phi, R, I)$ in terms of certain subsets of $\mathcal{Z}$.
+\begin{thm}\label{thm:width} Let $\Phi$ be an irreducible root system, and let $I$ be an ideal of a commutative ring $R$.
 \begin{enumerate}
-\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z})\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
-\item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume $\Phi$ is classical.
-Then under the assumption of the Generalized Riemann Hypothesis there is an estimaete  $W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1$;
+\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
+\item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume $\Phi$ is classical. Then under the assumption of the Generalized Riemann Hypothesis one has
+ $$W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1;$$
 \item Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type embedded into some global field $k$ having a real embedding. 
-Assume that $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell))$ is finite.
+Assume $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell))$ is finite.
 \end{enumerate}
 \end{thm}
-\begin{proof}
-
-%In the proof of the above theorem we use Bass---Kolster decomposition to reduce to the case $\Phi=\rA_1$ which then can be settled directly.
-%Notice that the particular case $I=R$ of the above theorem was demonstrated in~\cite{VavSmSuUnitrEng} (see also \cite{VseUnitrZ1p}).
-...
-\end{proof}
 The particular case $\Phi = \rA_\ell$, $R = I = \mathbb{Z}$ of the above theorem is similar in spirit to a recent theorem of U.~Hadad (see ~\cite[Theorem~1.6]{Ha12}).
@@
 \begin{itemize} 
-\item $I$ is an ideal of a (not neccessarily commutative) ring $R$ such that $\sr(I)\leq 2$, $\Phi=\rA_\ell$, $l\geq 2$, $N=3|\Phi^+|+\rk(\Phi) - 3$.
-\item $I$ is an ideal of a commutative ring $R$ such that $\sr(I)\leq 3$, $\Phi=\rC_\ell$, $l\geq 2$, $N=3|\Phi^+|+2\rk(\Phi) - 4$
+\item $I$ is an ideal such that $\sr(I)\leq 2$, $\Phi=\rA_\ell$, $l\geq 2$, $N=3|\Phi^+|+\rk(\Phi) - 3$.
+\item $I$ is an ideal such that $\sr(I)\leq 3$, $\Phi=\rC_\ell$, $l\geq 2$, $N=3|\Phi^+|+2\rk(\Phi) - 4$
 \end{itemize}
@@
 
-We also define $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w(-1)$. Then
+Define semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$. Then
 \begin{equation}\label{rel:R6}

### 2015-08-26 paper.tex
Minor changes

@@
 \item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume $\Phi$ is classical. Then under the assumption of the Generalized Riemann Hypothesis one has
+%TODO: I'm not sure whether in the orthogonal case we have the estimate 3|\Phi^+| and not 4|\Phi^+|; doublecheck this
  $$W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1;$$
@@
 We denote by $\G(\Phi, R)$ the simply-connected split Chevalley group of type $\Phi$ over arbitrary commutative ring $R$.
-For example, for each of the four classical series $\Phi=\rA_\ell, \rB_\ell, \rC_\ell, \rD_\ell$ the group $\G(\Phi, R)$ equals $\SL(\ell+1, R)$, $\Spin(2\ell+1, R)$, $\Sp(2\ell, R)$, $\Spin(2\ell, R)$, respectively.
-Notice that from the uniqueness theorem of M.~Demazure (see~\cite[Corollaire~5.2]{SGA3}) it follows that the exceptional isomorphisms of small-rank groups (which are well-known in the theory of groups over fields) remain valid for Chevalley groups over arbitrary commutative rings $R$.
-In particular there are isomorphisms of groups $\Spin(5, R)\cong \Sp(4, R)$, $\Spin(6, R)\cong\SL(4, R)$ $\SL(2, R)\cong \Sp(2, R)$.
+For example, for each of the four classical series $\Phi=\rA_\ell, \rB_\ell, \rC_\ell, \rD_\ell$
+the group $\G(\Phi, R)$ equals $\SL(\ell+1, R)$, $\Spin(2\ell+1, R)$, $\Sp(2\ell, R)$, $\Spin(2\ell, R)$, respectively.
+Notice that from the uniqueness theorem of M.~Demazure (see~\cite[Corollaire~5.2]{SGA3})
+it follows that the exceptional isomorphisms of small-rank groups (which are well-known in the theory of groups over fields) remain valid for Chevalley groups over arbitrary commutative rings.
+In particular, there are isomorphisms of groups $\Spin(5, R)\cong \Sp(4, R)$, $\Spin(6, R)\cong\SL(4, R)$, $\SL(2, R)\cong \Sp(2, R)$.
 

### 2015-08-27 bass-kolster.tex
Fixes from 27.08 meeting

@@
 In the assumptions and notation of Theorem~\ref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
-can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4(|\Phi^+| - |\Delta_1^+|)-1$ elementary root unipotents $x_\alpha(s)$ of level $I$. \end{cor}
+can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elementary root unipotents $x_\alpha(s)$ of level $I$. \end{cor}
 \begin{proof}

### 2015-08-27 congrsubgr-boundgen.tex
Fixes from 27.08 meeting

@@
 Set $R=\mathbb{Z}[\sfrac{1}{p}]$ and let $I$ be an ideal of $R$.
-Under the assumption of GRH the width of $\SL(2,R,I)$ with respect to the generating set $$\mathcal{Z}(\Sigma_1)=X_{12}(I)\cup X_{21}(I) \cup \{z_{21}(s, \xi) \mid s\in I,\ \xi\in R\}$$ does not exceed $6$.
+Under the assumption of GRH the width of $\SL(2,R,I)$ with respect to the generating set $$\mathcal{Z}(\{-\alpha_1\})=X_{12}(I)\cup X_{21}(I) \cup \{z_{21}(s, \xi) \mid s\in I,\ \xi\in R\}$$ does not exceed $6$.
 \end{lemma}

### 2015-08-27 paper.tex
Fixes from 27.08 meeting

@@
 Now we are ready to state a recent theorem of A.~Stepanov (see~\cite[Theorem~3.4]{S}).  
-\begin{thm}\label{thm:Stepanov} Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S \subset \Phi$ be any parabolic subset of roots.
-Then $\E(\Phi, R, I)$ is generated as an abstract group by $\mathcal{Z}(\Sigma_S)$. \end{thm}
+\begin{thm*}\label{thm:Stepanov}
+Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S \subset \Phi$ be any parabolic subset of roots.
+Then $\E(\Phi, R, I)$ is generated as an abstract group by $\mathcal{Z}(\Sigma_S)$.
+\end{thm*}
 
@@
 \begin{enumerate}
-\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
+\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z}(-\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
 \item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume $\Phi$ is classical. Then under the assumption of the Generalized Riemann Hypothesis one has
 %TODO: I'm not sure whether in the orthogonal case we have the estimate 3|\Phi^+| and not 4|\Phi^+|; doublecheck this
- $$W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1;$$
+ $$W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1;$$
 \item Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type embedded into some global field $k$ having a real embedding. 
-Assume $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell))$ is finite.
+Assume $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
 \end{enumerate}
@@
 it follows that the exceptional isomorphisms of small-rank groups (which are well-known in the theory of groups over fields) remain valid for Chevalley groups over arbitrary commutative rings.
-In particular, there are isomorphisms of groups $\Spin(5, R)\cong \Sp(4, R)$, $\Spin(6, R)\cong\SL(4, R)$, $\SL(2, R)\cong \Sp(2, R)$.
+In particular, there are isomorphisms of groups $\Spin(3,R)\cong\SL(2,R)$, $\Spin(5, R)\cong \Sp(4, R)$, $\Spin(6, R)\cong\SL(4, R)$, $\SL(2, R)\cong \Sp(2, R)$.
 

### 2015-08-28 stability-conditions.tex
Stable rank

@@
 \begin{enumerate}
-\item For any ideal $J\subseteq I$ one has $\sr(J)\leqslant\sr(I)$, $\sr(I/J)\leqslant\sr(I)$.
-\item One has $\sr\left(\prod\limits_{i=1}^n R_i\right)=\max\limits_{i=1}^n\left(\sr(R_i)\right).$
-\item Let $J$ denote the Jacobson radical of $R$, then one has $\sr(R)=\sr(R/J)$.
+\item For any ideal $J\subseteq I$ one has $\sr(J)\leqslant\sr(I)$, $\sr(I/J)\leqslant\sr(I)$;
+\item One has $\sr\left(\prod\limits_{i=1}^n R_i\right)=\max\limits_{i=1}^n\left(\sr(R_i)\right)$;
+\item Let $J$ denote the Jacobson radical of $R$, then one has $\sr(R)=\sr(R/J)$;
+\item If $I\subseteq J$, then $\sr(I)=1$;
+\item Let $I^1$ denote the ring obtained by formally adjoining $1$ to $I$. Then $\sr(I^1)=\max(2,\sr(I))$.
 \end{enumerate}
@@
 Other examples of rings of stable rank $1$ are provided by boolean rings, the ring of algebraic integers, the ring of entire functions, the disk-algebra, etc.
+For this and many other examples see~\cite{VasSR1}.
+
+Formally adjoining a unit to a non-unital ring of stable rank $1$ produces a non-trivial example of an ideal having the stable rank strictly lower that the ambient ring.
 \end{example}
@@
 \[\sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
+\cite{MKV} gives the examples of rings of stable rank $1$ but of absolute stable rank $\geqslant2$. Theorem~1.3 therein shows that for principal ideal rings $\sr(R)=\asr(R)$.
 

### 2015-08-29 paper.tex
K_1 triviality

@@
 \DeclareMathOperator{\K}{K}
+\DeclareMathOperator{\SK}{SK}
 \DeclareMathOperator{\G}{G}
@@
 
+Since elementary subgroup $\E(\Phi,R,I)$ is normal in $\G(\Phi,R,I)$, one can define the $\K_1$-functor by $\K_1(\Phi,R,I)=\G(\Phi,R,I)/\E(\Phi,R,I)$.
+When $I=R$, we write $\K_1(\Phi,R)$ for $\K_1(\Phi,R,R)$.
+In some cases it is known that $\K_1(\Phi,R,I)$ is trivial.
+For example, $\SK_1(\ell+1,R)=\K(\rA_\ell,R)=1$ for any ring of stable rank $1$ (see Section~\ref{sec:stability-conditions}), and for other root systems some stronger assumption is required such as $\asr(R)=1$ or being semilocal.
+For a Euclidean ring $\K_1$ is trivial for every root system.
+
+Let $k$ be a global field, $S$ be a set of places of $k$, $\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and $I$ be an ideal of $\mathcal{O}_S$.
+\begin{thm*}[{\cite[Theorem~3.6]{BassMilnorSerre} and \cite[Corollary~4.5]{Ma69}}]
+Assume that the field $k$ has a real embedding. Then $\K_1(\Phi,\mathcal{O}_S,I)=1$.
+\end{thm*}
+
 %The following result of L.~Vaserstein and J.~Tits describes a set of generators of $\E(\Phi, R, I)$ (see e.\,g.~\cite[Theorem~2]{Va86}).

### 2015-08-29 congrsubgr-boundgen.tex
K_1 triviality
Transpose lemma:Z1p

@@
  (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $\X_\alpha(I)$ (see formula~\ref{rel:R6}), we have a decomposition
-\[ g\in\U(\Phi,I)\cdot\prod_{\i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
+\[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
 and the estimate follows. \end{proof}
@@
 Let $g$ be an element of $\SL(2,R,I)$. Write
-\[ g=\begin{pmatrix}x & y \\ z & w\end{pmatrix},\ \text{for}\ x=p^\alpha a,\ y=p^\beta bm,\ \text{where}\ a,b,\alpha,\beta\in\mathbb{Z},\ p\nmid a,b. \]
+\[ g=\begin{pmatrix}x & y \\ z & w\end{pmatrix},\ \text{for}\ x=p^\alpha a,\ z=p^\beta bm,\ \text{where}\ a,b,\alpha,\beta\in\mathbb{Z},\ p\nmid a,b. \]
 
@@
 Write
-\[ g_1=g\cdot x_{21}(mk) =
-\begin{pmatrix} p^\beta q & p^\beta bm \\ * & * \end{pmatrix}.\]
+\[ g_1=x_{12}(mk)\cdot g =
+\begin{pmatrix} p^\beta q & * \\ p^\beta bm & * \end{pmatrix}.\]
 There exists $u\geqslant 1$ such that $p^u\equiv b\pmod q$, say $p^u=b+lq$. Then
-\[ g_2 = g_1\cdot x_{12}(ml) =
-\begin{pmatrix} p^\beta q & mp^{\beta+u} \\ * & * \end{pmatrix}. \]
+\[ g_2 =  x_{21}(ml)\cdot g_1 =
+\begin{pmatrix} p^\beta q & * \\ mp^{\beta+u} & * \end{pmatrix}. \]
 Since $g_2\equiv 1\pmod m$, we can write $p^\beta q=1+cm$ for some $c$. Now let
 \begin{align*}
-g_3 = & g_2\cdot x_{21}\left(\dfrac{-c}{p^{\beta+u}}\right) =
-\begin{pmatrix} 1 & mp^{\beta+u} \\ * & * \end{pmatrix}, \\
-g_4 = & g_3\cdot x_{12}\left(-mp^{\beta+u}\right) =
-\begin{pmatrix} 1 & 0 \\ * & * \end{pmatrix}, \\
-g_5 = & g_4\cdot x_{21}\left(\dfrac{c}{p^{\beta+u}}\right) =
-\begin{pmatrix} 1 & 0 \\ * & * \end{pmatrix}.
+g_3 = & x_{12}\left(\dfrac{-c}{p^{\beta+u}}\right)\cdot g_2 =
+\begin{pmatrix} 1 & * \\ mp^{\beta+u} & * \end{pmatrix}, \\
+g_4 = & x_{21}\left(-mp^{\beta+u}\right)\cdot g_3 =
+\begin{pmatrix} 1 & * \\ 0 & * \end{pmatrix}, \\
+g_5 = & x_{12}\left(\dfrac{c}{p^{\beta+u}}\right)\cdot g_4 =
+\begin{pmatrix} 1 & * \\ 0 & * \end{pmatrix}.
 \end{align*}
-Notice that $g_5=g_2\cdot z_{12}\left(-mp^{\beta+u},c/p^{\beta+u}\right)$ hence $g=x_{21} \cdot z_{12} \cdot x_{12} \cdot x_{21}$
+Notice that $g_5=z_{21}\left(-mp^{\beta+u},c/p^{\beta+u}\right)\cdot g_2$ hence $g=x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$
 and the length of $g$ does not exceed $4$.
@@
 Then $k+\alpha>-k+\beta$ and
-\[ g\cdot h_{12}\left(p^k\right) =
-\begin{pmatrix} p^\alpha a & p^\beta bm \\ * & * \end{pmatrix}
-\begin{pmatrix} p^k & 0 \\ 0 & p^{-k} \end{pmatrix}=
-\begin{pmatrix} p^{k+\alpha} a & p^{-k+\beta} bm \\ * & * \end{pmatrix}. \]
-We find ourselves in the situation of Case 1, therefore we can write $g=x_{21} \cdot z_{12} \cdot x_{12} \cdot x_{21} \cdot h_{12}$.
-Finally, using the same token as in Lemma~\ref{lemma:srRI1} we get that $g=x_{21} \cdot z_{12} \cdot x_{12} \cdot z_{12} \cdot x_{21} \cdot x_{12}$.
+\[ h_{12}\left(p^k\right)\cdot g =
+\begin{pmatrix} p^k & 0 \\ 0 & p^{-k} \end{pmatrix}
+\begin{pmatrix} p^\alpha a & * \\ p^\beta bm & * \end{pmatrix}=
+\begin{pmatrix} p^{k+\alpha} a & * \\ p^{-k+\beta} bm & * \end{pmatrix}. \]
+We find ourselves in the situation of Case 1, therefore we can write $g=h_{12}\cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
+Finally, expressing $h=x_{21}\cdot z_{21}\cdot x_{12}$ as in Lemma~\ref{lemma:rel-tor-elementary}, we get that $g=x_{21} \cdot z_{21} \cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
 \end{proof}
@@
 For any matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)$ lies in $\SL\left(2,\mathcal{O}_S,I^2\right)$.
-Recall that if $k$ has a real embedding then $\G(\Phi, \mathcal{O}_S,I) = \E(\Phi, \mathcal{O}_S, I)$ for any ideal $I$ by virtue of \cite[Corollary~4.5]{Ma69} and \cite[Theorem~3.6]{BassMilnorSerre}.
 

### 2015-08-30 bass-kolster.tex
Some detainl on A_l, C_l of BK (and the signs checked)

@@
 %Set $v=(1+v_1,v_2,\ldots,v_\ell,v_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
-Thanks to the relative stable rank condition one can add suitable multiples of the last component $v_{\ell+1}$ to the first $\ell$ components of $v$ so that the upper
-$\ell$ coefficients of the resulting vector $v'$ form an $I$-unimodular column of length $\ell$.
-Now multiplying $v'$ by a suitable $y\in \U(\Sigma_\ell^-, I)$ we obtain equalities~\ref{eq1}.
+Since $\sr(I)\leqslant\ell$, one can find $a_1,\ldots,a_\ell\in I$ such that $(v_1+a_1v_{\ell+1},\ldots,v_\ell+a_\ell v_{\ell+1})^t=(v'_1,\ldots,v'_\ell)^t$ is $I$-unimodular.
+Then there are $b_1,\ldots,b_\ell\in I$ such that $b_1v'_1+\ldots b_\ell v'_\ell=v'-1\in I$.
+So the vector
+\[ v'' = \prod_{i=1}^\ell x_{\ell+1,i}(b_i) \cdot \prod_{i=1}^\ell x_{i,\ell+1}(a_i) \cdot v \]
+satisfies the equalities~\ref{eq1}.
 
 \textsc{Case $\Phi=\rC_\ell$, $n=2\ell$.}
-Notice that column $(v_1,\ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
+Notice that the column $(v_1,\ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
 Applying condition $\sr(I)\leq 2\ell-1$ we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
@@
 Set $\xi = v''_1-v''_{-1}-1 \in I$,
-\[ h_2 = x_{-1,1}\biggl(\xi f_1 \pm \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1,i}(\xi f_i) \in \U(\Sigma_1, I). \]
+\[ h_2 = x_{-1,1}\biggl(\xi f_1 \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1,i}(\xi f_i) \in \U(\Sigma_1, I). \]
 Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\ref{eq1}.

### 2015-08-30 bass-kolster.tex
Oups! Tiny fix.
Iterated Bass---Kolster in a separate statement

@@
 Set $\xi = v''_1-v''_{-1}-1 \in I$,
-\[ h_2 = x_{-1,1}\biggl(\xi f_1 \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1,i}(\xi f_i) \in \U(\Sigma_1, I). \]
+\[ h_2 = x_{-1,1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1,i}(\xi f_i) \in \U(\Sigma_1, I). \]
 Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\ref{eq1}.
@@
 It is easy to see that the proof of the above theorem is effective and gives an estimate of the total number of elementary root unipotents involved in the decomposition.
-\begin{cor}
+\begin{cor}\label{cor:bass-kolster-count}
 In the assumptions and notation of Theorem~\ref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
-can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elementary root unipotents $x_\alpha(s)$ of level $I$. \end{cor}
+can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elementary root unipotents $x_\alpha(s)$ of level $I$.
+\end{cor}
 \begin{proof}
@@
 The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}
-
+The Bass---Kolster decomposition can be iterated if the stability assumption allows, with a slight improvement of Corollary~\ref{cor:bass-kolster-count}.
+\begin{cor}\label{cor:bass-kolster-iterated}
+Assume $\sr(R)\leqslant2$ in case $\Phi=\rA_\ell,\rC_\ell$ and $\asr(R)\leqslant2$ in case $\Phi=\rB_\ell,\rD_\ell$.
+Then every element of $\G(\Phi,R,I)$ is a product of an element of $\G(\langle\pm\alpha_\ell\rangle,R,I)$, at most $\ell$ elements of the form $z_{-\alpha}(*,*)$, $\alpha$ the maximal root of a terminal subsystem containing $\alpha_\ell$, and at most $N$ elementary root unipotents $x_\alpha(s)$, $s\in I$, where $N$ is $3\left|\Phi^+\right|+\ell$ in case $\Phi=\rA_\ell,\rC_\ell$ and $N=4\left|\Phi^+\right|-\ell$ in case $\Phi=\rB_\ell,\rD_\ell$.
+\end{cor}
+\begin{proof}
+The improved estimate for $\Phi=\rA_\ell,\rC_\ell$ is obtained by using the fact that it suffices to make only two additions to make the shorter column unimodular in the first step of the Bass---Kolster decomposition.
+\end{proof}
 \begin{proof}[Proof of Theorem~\ref{thm:SL2width}]

### 2015-08-30 congrsubgr-boundgen.tex
Iterated Bass---Kolster in a separate statement

@@
 First of all, notice that $\asr(I) \leq \asr(\mathcal{O}_S) \leq 2$. 
-Inductively applying Theorem~\ref{thm:BassKolster} and using exceptional isomorphisms for small-rank groups we can present any element 
-of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators from $\mathcal{Z}(\Sigma_\ell)$ and one element of 
+By Corollary~\ref{cor:bass-kolster-iterated} we can present any element 
+of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators $\mathcal{Z}(\Sigma_\ell)$ and one element of 
 $\G(\{\alpha_\ell, -\alpha_\ell\}, \mathcal{O}_S, I)\cong\SL(2,\mathcal{O}_S,I)$.

### 2015-08-31 bass-kolster.tex
Stability map diagram
Theorem 2

@@
 \begin{cor}\label{cor:bass-kolster-iterated}
-Assume $\sr(R)\leqslant2$ in case $\Phi=\rA_\ell,\rC_\ell$ and $\asr(R)\leqslant2$ in case $\Phi=\rB_\ell,\rD_\ell$.
-Then every element of $\G(\Phi,R,I)$ is a product of an element of $\G(\langle\pm\alpha_\ell\rangle,R,I)$, at most $\ell$ elements of the form $z_{-\alpha}(*,*)$, $\alpha$ the maximal root of a terminal subsystem containing $\alpha_\ell$, and at most $N$ elementary root unipotents $x_\alpha(s)$, $s\in I$, where $N$ is $3\left|\Phi^+\right|+\ell$ in case $\Phi=\rA_\ell,\rC_\ell$ and $N=4\left|\Phi^+\right|-\ell$ in case $\Phi=\rB_\ell,\rD_\ell$.
+Assume $\sr(I)\leqslant2$ in case $\Phi=\rA_\ell$, $\sr(I)\leqslant3$ in case $\rC_\ell$ and $\asr(I)\leqslant2$ in case $\Phi=\rB_\ell,\rD_\ell$.
+Then every element of $\G(\Phi,R,I)$ is a product of an element of $\G(\langle\pm\alpha_\ell\rangle,R,I)$, at most $\ell-1$ elements of the form $z_{-\alpha}(*,*)$, $\alpha$ the maximal root of some terminal subsystem containing $\alpha_\ell$, and at most $N$ elementary root unipotents $x_\alpha(s)$, $s\in I$, where $N$ is $3\left|\Phi^+\right|+\ell$ in case $\Phi=\rA_\ell$, $N=3\left|\Phi^+\right|+2\ell$ in case $\Phi=\rC_\ell$ and $N=4\left|\Phi^+\right|-\ell$ in case $\Phi=\rB_\ell,\rD_\ell$.
 \end{cor}
 \begin{proof}
-The improved estimate for $\Phi=\rA_\ell,\rC_\ell$ is obtained by using the fact that it suffices to make only two additions to make the shorter column unimodular in the first step of the Bass---Kolster decomposition.
+The improved estimate for $\Phi=\rA_\ell$ or $\rC_\ell$ is obtained by using the fact that it suffices to make only two or three additions respectively to make the shorter column unimodular in the first step of the Bass---Kolster decomposition.
 \end{proof}
+\[
+\begin{tikzcd}[row sep=tiny]
+\rD_4 \arrow[out=0,in=120]{rd}{\asr\leqslant3} & & & \\
+\rA_4 \arrow{r}{\sr\leqslant4} & \rA_3 \arrow{r}{\sr\leqslant3} & \rA_2 \arrow{r}{\sr\leqslant2} & \rA_1 \\
+\rC_4 \arrow{r}{\sr\leqslant7} & \rC_3 \arrow{r}{\sr\leqslant5} & \rC_2 \arrow[out=0,in=-120,swap]{ru}{\sr\leqslant3} \\
+\rB_4 \arrow{r}{\asr\leqslant3} & \rB_3 \arrow[out=0,in=-120,swap]{ru}{\asr\leqslant2} & &
+\end{tikzcd}
+\]
 \begin{proof}[Proof of Theorem~\ref{thm:SL2width}]
-Consider the case $\Phi=\rA_\ell$, $\sr(I)\leq 2$. First of all, notice that we can improve the estimate of the number of factors involved in Bass---Kolster decomposition.
-Indeed, when performing the first step of the proof of Theorem~\ref{thm:BassKolster} it suffices to make only $2$ additions of $v_{\ell+1}$ (e.\,g.
-to $v_{1}$ and $v_2$) to make the first $\ell$ entries of $v'$ form a unimodular column.
-In particular, $\G(\Phi, R, I)$ can be presented as a product of one element of $\G(\Delta_1, R, I)$, one element of $Z$ and $3\ell+1$ root unipotents $x_\alpha(s)$, $s\in I$.
-The latter elements are contained in a product of $3\ell + 1$ copies of $\SL(2, R, I)$. Now the statement of the theorem follows by induction on $\ell$.
-
-The proof in the case $\Phi=\rC_\ell$ is similar (notice that we use the exceptional isomorphism $\SL(2, R)\cong \Sp(2, R)$).
+A direct application of Corollary~\ref{cor:bass-kolster-iterated}.
 \end{proof}

### 2015-08-31 paper.tex
Theorem 1 for Z[1/p] split in two cases
Stability map diagram
Many improvements in the bibliography
Theorem 2

@@
 \usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
-\usepackage[all]{xy}
+%\usepackage[all]{xy}
 \usepackage[activate={true,nocompatibility}]{microtype}
+\usepackage{tikz-cd}
 
@@
 \DeclareFieldFormat[inproceedings]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+\DeclareFieldFormat[inbook]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
 \DeclareFieldFormat[thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
@@
 \item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume $\Phi$ is classical. Then under the assumption of the Generalized Riemann Hypothesis one has
-%TODO: I'm not sure whether in the orthogonal case we have the estimate 3|\Phi^+| and not 4|\Phi^+|; doublecheck this
- $$W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1;$$
+%TODO: Now check the coefficients of \rk(\Phi) in the expression below
+\begin{alignat*}{2}
+& W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1 & \text{ if } \Phi=\rA_\ell,\rC_\ell, \\
+& W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell,\rD_\ell;
+\end{alignat*}
 \item Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type embedded into some global field $k$ having a real embedding. 
@@
 Another application of parabolic factorizations developed in this paper are subsystem factorizations in terms of subgroups of type $\rA_1$.
-The case of a finite field $R=F$ was exhaustively studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{NikProdDecomp}.
+The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{LiebNikShaSL2}.
 More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
@@
 \begin{thm}\label{thm:SL2width}
-Assume that one of the following is true:
-\begin{itemize} 
-\item $I$ is an ideal such that $\sr(I)\leq 2$, $\Phi=\rA_\ell$, $l\geq 2$, $N=3|\Phi^+|+\rk(\Phi) - 3$.
-\item $I$ is an ideal such that $\sr(I)\leq 3$, $\Phi=\rC_\ell$, $l\geq 2$, $N=3|\Phi^+|+2\rk(\Phi) - 4$
-\end{itemize}
-Then $\G(\Phi, R, I)$ can be presented as a product of at most $N$ copies of its subgroups isomorphic to $\G(\rA_1, R, I)$. \end{thm}
+Let $I\trianglelefteq R$ be an ideal, $\Phi$ be a classical root system.
+Then under a suitable stability assumption the prncipal congruence subgroup $\G(\Phi,R,I)$ can be presented as a product of at most $N$ copies of its subgroups isomorphic to $\G(\rA_1,R,I)$, where the stability assumption and the corresponding value of $N$ is as follows:
+%TODO: Constants for A and C - where do they come from?
+\[\begin{array}{l@{\quad}l@{\quad}l}
+\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right|+\rk(\Phi) - 3; \\
+\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right|+2\rk(\Phi) - 4; \\
+\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right|.
+\end{array}\]
+\end{thm}
 

### 2015-08-31 congrsubgr-boundgen.tex
Partially rewritten DV section

@@
 Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
- (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $\X_\alpha(I)$ (see formula~\ref{rel:R6}), we have a decomposition
+ (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\ref{rel:R6}), we have a decomposition
 \[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]

### 2015-08-31 dennis-vaserstein.tex
Slight changes in the notation; further reorganization
Tiny typography fix in DV statement
Partially rewritten DV section

@@
 Let $\Phi$ be an irreducible root system of rank $\ell$.
-Let $r$, $s$ be two distinct indices $1\leq r,s \leq \ell$.
-From Levi decomposition it follows that
+For an integer $1 \leq s \leq \ell$ consider the following two subgroups of $\E(\Phi, R)$:
+$$\EP_s(R) = \E(\Delta_s, R) \cdot \U(\Sigma_s, R),\ \EP_s(R, I) = \E(\Delta_s, R, I) \cdot \U(\Sigma_s, I).$$
+
+Let $1\leq r,s \leq \ell$ be two distinct integers.
+From Levi decomposition it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
 \begin{multline*}
@@
 \end{multline*}
-Denote by $A_{rs}$ any of the equal subsets from the previous formula.
+\begin{dfn}
+ Denote by $A_{rs}$ any of the above equal subsets.
+ We call the decomposition of the form $\E(\Phi, R, I) = A_{rs}$ the {\it relative Dennis---Vaserstein} decomposition.
+\end{dfn}
 
-The main result of this subsection is the following theorem which is a relative analogue of Dennis---Vaserstein decomposition~\cite[Theorem~2.5]{St78}.
-
+The main result of this subsection is the following theorem which is a relative version of \cite[Lemma~2.1]{ST76} and \cite[Theorem~2.5]{St78}).
 \begin{thm}\label{thm:DennisVaserstein}
-The relative elementary subgroup $\E(\Phi, R, I)$ coincides with the subset $A_{rs}$ under the following assumptions on $I$:
-\[\begin{array}{l@{\quad}l@{\quad}l@{\quad}c}
-\Phi = \rA_\ell, \rB_\ell,\ \ell\geqslant 2, & (s, r)=(1, \ell), & \sr(I) \leqslant \ell-1; \\     
-\Phi = \rD_\ell,\ \ell\geqslant 4,           & (s, r)=(1, \ell), & \sr(I) \leqslant \ell-2; \\ 
-\Phi = \rE_\ell,\ \ell=6,7,             & (s, r)=(\ell, 2), & \sr(I) \leqslant \ell-3; \\ 
-\Phi = \rE_\ell,\ \ell=6,7,             & (s, r)=(\ell, 1), & \asr(I)\leqslant \ell-2.
+The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition under the following assumptions on $I$.
+\[\begin{array}{|c|l|c|l|}
+\hline \Phi & s & r & \text{ring condition} \\ \hline
+\rA_\ell, \rB_\ell,\ \ell\geqslant 2 & 1 & \ell & \sr(I) \leqslant \ell-1 \\     
+\rC_\ell,\ \ell \geqslant 2          & 1 & \ell & \sr(I) \leqslant \ell-1 \\
+\rD_\ell,\ \ell\geqslant 4           & 1 & \ell & \sr(I) \leqslant \ell-2 \\ 
+\rD_\ell,\ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2 \\
+\rE_\ell,\ \ell=6,7             & \ell & 2 & \sr(I) \leqslant \ell-3 \\ 
+\rE_\ell,\ \ell=6,7             & \ell & 1 & \asr(I)\leqslant \ell-2 \\ \hline
 \end{array}\]
 \end{thm}
-The proof of Theorem~\ref{thm:DennisVaserstein} occupies the rest of this section.
-Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
-This action induces an action of $\E(\Phi, R)$ on the set $\mathfrak{S}$ of all subsets of $\E(\Phi, R, I)$.
-On the other hand, $\E(\Phi, R, I)$ acts on $\mathfrak{S}$ by left multiplication.
-Denote by $N_{rs}$ and $L_{rs}$ stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
-\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} = A_{rs} \right\},\quad L_{rs}= \left\{ g\in \E(\Phi, R, I)\ \middle|\ g \cdot A_{rs} = A_{rs} \right\}. \]
+%Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
+%This action induces an action of $\E(\Phi, R)$ on the set $\mathfrak{S}$ of all subsets of $\E(\Phi, R, I)$.
+%On the other hand, $\E(\Phi, R, I)$ acts on $\mathfrak{S}$ by left multiplication.
+%Denote by $N_{rs}$ and $L_{rs}$ stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
+Consider the following two subsets of $\E(\Phi, R)$:
+\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} = A_{rs} \right\}, \quad
+   L_{rs}=  \left\{ g\in \E(\Phi, R, I)\ \middle|\ g \cdot A_{rs} \subseteq A_{rs} \right\}. \]
 
-It is easy to see that $N_{rs}$ normalizes $L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
-$$h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq A_{rs}^g \subseteq A_{rs}.$$
+It is easy to see that $N_{rs}$ normalizes $L_{rs}$, i.e. ${L_{rs}}^{N_{rs}} \subseteq L_{rs}$. 
+Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+$$h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} = g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g = A_{rs}.$$
 
-\begin{lemma}\label{lemma:dv_unipotent}
-For any $1\leq i\leq n$ the following statements hold (together with their analogues for $\Phi^-$).
+\begin{lemma}\label{lemma:dv_unipotent} For any $1\leq i\leq n$ the following statements hold. 
+\begin{thmlist} \item \label{item-dvu1} $\U(\Phi^+, I) = X_{\alpha\ssub{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I) = \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I)\cdot X_{\alpha\ssub{i}}(I)$.
+\item \label{item-dvu2} For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha\ssub{i}}(\xi)} \subseteq \U(\Phi^+, I)$.
+\item \label{item-dvu3} $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{i}}(I) \cdot X_{-\alpha\ssub{i}}(I)$.
+\end{thmlist} \end{lemma}
+\begin{proof} The first two statements easily follow from Chevalley commutator formula~\ref{rel:CCF} while the third one is a formal consequence of the first two. \end{proof}
+
+%The following lemma is a relative version of the main reduction used by M.~Stein in~\cite{St78}
+%for the proof of the absolute Dennis--Vaserstein decomposition.
+
+\begin{lemma}\label{lemma:Stein_reduction}
+Assume that there exists a subset $B \subseteq \E(\Delta_r, R, I)$ satisfying the following assumptions:
 \begin{enumerate}
-\item $\U(\Phi^+, I) = \X_{\alpha\ssub{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I) = \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I)\cdot \X_{\alpha\ssub{i}}(I)$.
-\item For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha\ssub{i}}(\xi)} \subseteq \U(\Phi^+, I)$.
-\item $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot \X_{\alpha\ssub{i}}(I) \cdot \X_{-\alpha\ssub{i}}(I)$.
+ \item\label{stein_cond1} One has $\U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B.$
+ \item\label{stein_cond2} One has $X_{-\alpha\ssub{r}}(I)^B \subseteq \EP_s(R, I).$
 \end{enumerate}
+Then $X_{-\alpha_r}(I) \subseteq L_{rs}$ and $\EP_s(R) \subseteq N_{rs}.$
 \end{lemma}
-\begin{proof}
- The first two statements easily follow from Chevalley commutator formula while the third one is a formal consequence of the first two.
-\end{proof}
+\begin{proof} Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
+From the first assumption of the lemma it follows that $A_{rs}=A$.
+On the other hand, by the second assumption we have
+\begin{multline*} X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
+ X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
+ \subseteq B \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I) \subseteq 
+ B \cdot \EP_s(R, I). \end{multline*}
+Together with the third statement of~\cref{lemma:dv_unipotent} this implies that
+\begin{equation} \label{rel:sred} A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I). \end{equation}
+Consequently, from the second statement of~\cref{lemma:dv_unipotent} it follows that
+\begin{equation} \label{rel:linv} X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I) = A. \end{equation}
+Since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we also get that:
+\begin{equation} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A. \end{equation}
 
-The following lemma is a relative version of the main reduction used by M.~Stein in~\cite{St78} for the proof of the absolute Dennis--Vaserstein decomposition.
-\begin{lemma}\label{lemma:Stein_reduction}
-Assume that there exists a subset $\widetilde{L_r} \subseteq \E(\Delta_r, R, I)$ with the following properties:
-\begin{enumerate}[label=(\alph*)] 
- \item\label{stein_cond1} One has $\U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r}.$
- \item\label{stein_cond2} One has $\X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \EP_s(R, I).$
-\end{enumerate}
-Then $\X_{-\alpha_r}(I) \subseteq L_{rs}$ and $\EP_s \subseteq N_{rs}.$
-\end{lemma}
-\begin{proof} Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(\Phi, R, I).$
-From assumption~\ref{stein_cond1} of the lemma it follows that $A_{rs}=A$.
-Observe first that Lemma~\ref{lemma:dv_unipotent} and condition~\ref{stein_cond2} together imply
-\begin{multline*}
-A \subseteq \U(\Phi^+\setminus \{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \X_{\alpha\ssub{r}}(I) \cdot \X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\ 
-\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \X_{\alpha\ssub{r}}(I) \cdot \X_{-\alpha\ssub{r}}(I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) \subseteq \\
-\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I)  \cdot \EP_s(R, I) \subseteq \\
-\subseteq \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I).
-\end{multline*}
-Now applying Lemma~\ref{lemma:dv_unipotent} we get the following inclusions:
-\begin{align*}
-& A^{\X_{-\alpha\ssub{r}}} \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} ^{\X_{-\alpha\ssub{r}}} \cdot \EP_s(R, I) \subseteq A; \\
-& \X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot \X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot \widetilde{L_r} \cdot \EP_s(R, I) = A.
-\end{align*}
-To prove the second part of the statement observe first that $\EP_s$ is generated by $\X_{\alpha\ssub{i}}$ for $1\leqslant i\leqslant n$ and $\X_{-\alpha\ssub{i}}$ for $i\neq s$.
+To prove the second part of the statement observe first that $\EP_s(R)$ is generated by $X_{\alpha\ssub{i}}(R)$ for $1\leqslant i\leqslant n$ and $X_{-\alpha\ssub{i}}(R)$ for $i\neq s$.
 %TODO: Find proper reference for this fact
-We have just shown that $\X_{-\alpha_r}\subseteq N_{rs}$.
-On the other hand, inclusions $\X_{\alpha\ssub{k}} \subseteq N_{rs}$ for $\ 1\leqslant k\leqslant \ell$ and $\X_{-\alpha\ssub{k}} \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
+From \ref{rel:ninv} it follows that $X_{-\alpha_r}(R)\subseteq N_{rs}$.
+On the other hand, inclusions $X_{\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $\ 1\leqslant k\leqslant \ell$ and $X_{-\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
 \end{proof}
@@
 %TODO: PICK AS L_r!!!
-Let $\widetilde{L_r}$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma_0$.
+Let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma_0$.
 In any of  the specified cases the assumption on $I$ allows us to apply Lemma~\ref{lemma:uraction} to the subsystem $\Delta_r$ and find
-$x\in\U(\Delta_r\cap\Phi^+, I)$, $y\in \U(\Delta_r\cap\Phi^-, I)$ such that $yx\cdot g \in \widetilde{L_r}$.
+$x\in\U(\Delta_r\cap\Phi^+, I)$, $y\in \U(\Delta_r\cap\Phi^-, I)$ such that $yx\cdot g \in B$.
 This proves the first condition of Lemma~\ref{lemma:Stein_reduction}, indeed:
-\[ \U(\Sigma^+_r, I) \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \U(\Phi^-, I) \widetilde{L_r}. \]
-To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in\widetilde{L_r}$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
-\[ \X_{-\alpha\ssub{r}}(I)^{\widetilde{L_r}} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \E(\Delta_s, R, I) \subseteq \EP_s(R, I). \]
+\[ \U(\Sigma^+_r, I) \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \U(\Phi^-, I) B. \]
+To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
+\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \E(\Delta_s, R, I) \subseteq \EP_s(R, I). \]
 
 From now on we can assume that the conclusion of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
-Notice that in view of Theorem~\ref{theorem:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:
+Notice that in view of Theorem~\ref{thm:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:
 \begin{itemize} \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
@@
 Notice that the Weyl group $W(\Delta_s)$ acts transitively on $\Delta_s$, therefore in view of relation~\ref{rel:R3} the subgroup
-$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leqslant \EP_s$ acts transitively on the set of root subgroups $\X_\alpha(I)$, $\alpha\in \Delta_s$
+$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leqslant \EP_s$ acts transitively on the set of root subgroups $X_\alpha(I)$, $\alpha\in \Delta_s$
 and we get that that $\U(\Delta_s \cap \Phi^-, I)\subseteq L_{rs}$.
@@
 %By the same argument as above we get that $W(\Delta_s)$.
-Since $\X_{\alpha\ssub{s}} \subseteq L_{rs}$ by the same argument as above, we get $\U({\Sigma^-_s}^>, I)\subseteq L_{rs}$.
+Since $X_{\alpha\ssub{s}} \subseteq L_{rs}$ by the same argument as above, we get $\U({\Sigma^-_s}^>, I)\subseteq L_{rs}$.
 This completes the proof of the theorem for $\Phi\neq \rB_\ell$.
 
-In the case $\Phi=\rB_\ell$ we have to show additionally that $\X_{-\alpha^<_{\mathrm{max}}}(I) \leqslant L_{rs}$, where $\alpha^<_{\mathrm{max}}$
+In the case $\Phi=\rB_\ell$ we have to show additionally that $X_{-\alpha^<_{\mathrm{max}}}(I) \leqslant L_{rs}$, where $\alpha^<_{\mathrm{max}}$
 denotes the maximal short root of $\rB_\ell$.
@@
 \[ x_{-{\alpha^<_{\mathrm{max}}}}(s) = x_{-1,0}(s) = x_{1,-2}(s) \cdot x_{-1,-2}(-s)^{x_{-2, 0}(-1)} \cdot x_{-1, 2}(\xi),\ s\in I. \]
-On the other hand, $x_{-2,0}(1) \in \EP_s$, and we have already shown $\X_{-1,-2}(I), \X_{-1, 2}(I) \subseteq L_{rs}$.
+On the other hand, $x_{-2,0}(1) \in \EP_s$, and we have already shown $X_{-1,-2}(I), X_{-1, 2}(I) \subseteq L_{rs}$.
 This concludes the proof of the theorem.

### 2015-08-31 paper.tex
Explicit formulas for the roots unipotents in vector representations
Partially rewritten DV section

@@
 \documentclass[12pt]{amsart}
-\usepackage{amscd, amsmath, verbatim, enumitem, graphicx, amssymb, mathtools, xfrac, amsthm, amsfonts, amstext, hyperref}
+\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, graphicx, mathtools, xfrac, hyperref, tikz-cd, nameref, thmtools}
 \usepackage[utf8]{inputenc}
 \usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
-%\usepackage[all]{xy}
 \usepackage[activate={true,nocompatibility}]{microtype}
-\usepackage{tikz-cd}
+\usepackage[capitalize]{cleveref}
 
+%Bibliography
 \renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
@@
 \DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
-\DeclareFieldFormat[article]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
-\DeclareFieldFormat[inproceedings]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
-\DeclareFieldFormat[inbook]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
-\DeclareFieldFormat[thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+\DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
 \addbibresource{paper.bib}
 
-\textwidth 16cm 
-\textheight 22cm 
-\headheight 0.5cm 
-\evensidemargin 0.3cm 
-\oddsidemargin 0.2cm
+%Theorem counters
+\newlist{thmlist}{enumerate}{1}
+\setlist[thmlist]{label=(\roman{thmlisti}), ref=\thethm.(\roman{thmlisti}),noitemsep}
+
+\declaretheorem[name=Theorem, Refname={Theorem,Theorems}]{thm}
+\declaretheorem[name=Corollary, Refname={Corollary, Corollaries}, sibling=thm]{cor}
+
+\declaretheorem[name=Lemma, Refname={Lemma,Lemmas}]{lemma}
+\declaretheorem[name=Proposition, Refname={Proposition,Propositions}, sibling=lemma]{prop}
+
+\Crefname{thm}{Theorem}{Theorems}
+\Crefname{lemma}{Lemma}{Lemmas}
+
+\Crefname{cor}{Corollary}{Corollaries}
+\Crefname{prop}{Proposition}{Propositions}
 
 \numberwithin{equation}{section}
-\newcounter{thmcounter} \newcounter{lemmacounter}
-\newtheorem{thm}[thmcounter]{Theorem}
-\newtheorem{prop}[thmcounter]{Proposition}
-\newtheorem{cor}[thmcounter]{Corollary}
-\newtheorem{lemma}[lemmacounter]{Lemma}
 \theoremstyle{definition}
@@
 
+%Page layout
+\textwidth 16cm 
+\textheight 22cm 
+\headheight 0.5cm 
+\evensidemargin 0.3cm 
+\oddsidemargin 0.2cm
+
+%Math operators
 \DeclareMathOperator{\K}{K}
@@
 \DeclareMathOperator{\U}{U}
-\DeclareMathOperator{\X}{X}
 \DeclareMathOperator{\Z}{Z}

### 2015-08-31 dennis-vaserstein.tex
Reordered lemmata in section 2

@@
-Let $\Phi$ be an irreducible root system of rank $\ell$.
-For an integer $1 \leq s \leq \ell$ consider the following two subgroups of $\E(\Phi, R)$:
-$$\EP_s(R) = \E(\Delta_s, R) \cdot \U(\Sigma_s, R),\ \EP_s(R, I) = \E(\Delta_s, R, I) \cdot \U(\Sigma_s, I).$$
-
-Let $1\leq r,s \leq \ell$ be two distinct integers.
-From Levi decomposition it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
+Let $\Phi$ be an irreducible root system of rank $\ell$ and let $1\leq r,s \leq \ell$ be two distinct integers.
+From Levi decomposition~\ref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
 \begin{multline*}
@@
 \end{multline*}
+
+\begin{lemma}\label{lemma:dv-normal} The set $A_{rs}$ is normalized by the subgroup $\EP_{\{r,s\}}(R) \leq \E(\Phi, R)$. \end{lemma}
+
 \begin{dfn}

### 2015-08-31 paper.tex
Reordered lemmata in section 2

@@
 \DeclareMathOperator{\Sp}{Sp}
+\DeclareMathOperator{\SO}{SO}
 \DeclareMathOperator{\St}{St}
@@
 
-We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\alpha, \alpha)$.
+We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\beta, \beta)$.
 Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all reflections $\sigma_\alpha$ where $\sigma_\alpha(\beta)=\beta-\langle\alpha,\beta \rangle\cdot \alpha$.
@@
 
-\begin{rem} Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
+\begin{rem}
+Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
 In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
-For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$. \end{rem}
+For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
+\end{rem}
+For other classical root systems the elementary root unipotents are as follows.
 
+In case $\Phi=\rC_\ell$ the long and short root unipotenrs are
+\begin{align*}
+& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
+& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
+\end{align*}
+
+Here $\varepsilon_i$ is the sign of $i$.
+
+In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
+\begin{align*}
+& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
+& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
+\end{align*}
+
+\subsection{Relative Chevalley groups}\label{sec:relative-elementary}
 Let $I\leq R$ be an ideal. Denote by $\E(\Phi, I)$ the subgroup of $\G_{sc}(\Phi, R)$ generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$.
 In the special case $I=R$ the subgroup $\E(\Phi, R)$ is called the {\it elementary subgroup} of the Chevalley group $\G_{sc}(\Phi, R)$.
-Taddei's theorem asserts that $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$.
 
 We denote by $\E(\Phi, R, I)$ the normal closure of $\E(\Phi, I)$ in $\E(\Phi, R)$, in other words $\E(\Phi, R, I) = \E(\Phi, I)^{\E(\Phi, R)}$.
-Denote by $z_\alpha(s, \xi)$ the element $x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$.
+Recall from the introduction that the elements $z_\alpha(s, \xi) = x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$ generate $\E(\Phi, R, I)$ as an abstract group.
 
-Since elementary subgroup $\E(\Phi,R,I)$ is normal in $\G(\Phi,R,I)$, one can define the $\K_1$-functor by $\K_1(\Phi,R,I)=\G(\Phi,R,I)/\E(\Phi,R,I)$.
-When $I=R$, we write $\K_1(\Phi,R)$ for $\K_1(\Phi,R,R)$.
-In some cases it is known that $\K_1(\Phi,R,I)$ is trivial.
-For example, $\SK_1(\ell+1,R)=\K(\rA_\ell,R)=1$ for any ring of stable rank $1$ (see Section~\ref{sec:stability-conditions}), and for other root systems some stronger assumption is required such as $\asr(R)=1$ or being semilocal.
-For a Euclidean ring $\K_1$ is trivial for every root system.
-
-Let $k$ be a global field, $S$ be a set of places of $k$, $\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and $I$ be an ideal of $\mathcal{O}_S$.
-\begin{thm*}[{\cite[Theorem~3.6]{BassMilnorSerre} and \cite[Corollary~4.5]{Ma69}}]
-Assume that the field $k$ has a real embedding. Then $\K_1(\Phi,\mathcal{O}_S,I)=1$.
-\end{thm*}
-
-%The following result of L.~Vaserstein and J.~Tits describes a set of generators of $\E(\Phi, R, I)$ (see e.\,g.~\cite[Theorem~2]{Va86}).
-%\begin{thm}\label{theorem:Tits-Vaserstein} Let $\Phi$ be an irreducible root system of rank $\geq 2$, then the relative elementary subgroup $\E(\Phi, R, I)$
-%is generated by the elements $z_\alpha(s, \xi)$, $\alpha\in \Phi$, $s\in I$, $\xi\in R$. \end{thm}
-
-%In fact, one can choose a more economical set of generators for $\E(\Phi, R, I)$ (see~\cite[Theorem~3.4]{S}).
-%\begin{thm}\label{theorem:Stepanov}
-%Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S$ be any parabolic subset of roots of $\Phi$ with the special part $\Sigma_S$.
-%Then $\E(\Phi, R, I)$ is generated by the union of the following two families of elements:
-%\begin{itemize}
-%\item $x_{\alpha}(s)$, where $s\in I$, $\alpha\in\Phi$;
-%\item $z_\alpha(s,\xi)$, where $s\in I$, $\xi\in R$, $\alpha\in\Sigma_S$.
-%\end{itemize}
-%\end{thm}
+\begin{lemma}[{\cite[Corollary~3.3]{S}}]\label{lemma:Stepanov-ideal}
+Let $\Phi$ be a root system of rank $\geqslant2$, let $R$ be a commutative ring and $I\trianglelefteq R$ be its ideal.
+If $\Phi\neq\rC_\ell$ then $\E\left(\Phi,R,I^2\right)\leqslant\E(\Phi,I)$, otherwise $\E\left(\Phi,R,II^{\indexbox{2}}\right)\leqslant\E(\Phi,I)$.
+\end{lemma}
+Here $I^{\indexbox{2}}$ denotes the ideal generated by squares $a^2$, where $a\in I$.
+Recall also that $I^2$ is generated by products $ab$ for all $a,b\in I$.
+Clearly, $II^{\indexbox{2}}$ is generated by elements of the form $a^2b$ for $a,b\in I$.
 
@@
 The following two equalities will be referred to in the sequel as {\it Levi decomposition}: 
-\[ \EP_J(R, I) = \U(\Sigma_J, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I). \]
+\begin{equation} \label{rel:Levi-decomp} \EP_J(R, I) = \U(\Sigma_J, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I). \end{equation}
+When $J = \{ \alpha_s \}$ for some $1 \leq s\leq \ell$ we use shorthand $\EP_s(R, I)$ for $\EP_{\{s\}}(R, I)$.
+When $I=R$ we also write $\EP_J(R)$ instead of $\EP_J(R, R)$.
+
+Denote by $\Hh(\Phi,R)$ the subgroup generated by all $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$. Then set
+\[ \Hh(\Phi,R,I) = \Hh(\Phi,R)\cap\G(\Phi,R,I)=\langle h_\alpha(\varepsilon),\ \alpha\in\Phi,\ \varepsilon\in R^*\cap(1+I)\rangle. \]
+\begin{lemma}\label{lemma:rel-tor-elementary} $\Hh(\Phi,R,I)\leqslant\E(\Phi,R,I)$. \end{lemma}
+\begin{proof}
+Set $\varepsilon=1+s$, $s\in I$ and write
+\begin{multline*}
+h_\alpha(1+s) = x_\alpha\left(-1\middle)\, x_{-\alpha}\middle(-s\middle)\, x_\alpha\middle((1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right) = \\
+= x_\alpha\left((1+s)^{-1}-1\middle)\, z_{-\alpha}\middle(-s,(1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right).
+\end{multline*}
+It remains to note that $(1+s)^{-1}\in 1+I$ and so all the factors lie in $\E(\Phi,R,I)$.
+\end{proof}
 
@@
 
-Denote by $\Hh(\Phi,R)$ the subgroup generated by all $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$. Then set
-\[ \Hh(\Phi,R,I) = \Hh(\Phi,R)\cap\G(\Phi,R,I)=\langle h_\alpha(\varepsilon),\ \alpha\in\Phi,\ \varepsilon\in R^*\cap(1+I)\rangle. \]
-\begin{lemma}\label{lemma:rel-tor-elementary}
-$\Hh(\Phi,R,I)\leqslant\E(\Phi,R,I)$.
-\end{lemma}
-\begin{proof}
-Set $\varepsilon=1+s$, $s\in I$ and write
-\begin{multline*}
-h_\alpha(1+s) = x_\alpha\left(-1\middle)\, x_{-\alpha}\middle(-s\middle)\, x_\alpha\middle((1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right) = \\
-= x_\alpha\left((1+s)^{-1}-1\middle)\, z_{-\alpha}\middle(-s,(1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right).
-\end{multline*}
-It remains to note that $(1+s)^{-1}\in 1+I$ and so all the factors lie in $\E(\Phi,R,I)$.
-\end{proof}
+\subsection{$\K_1$-functor modeled on Chevalley groups}
 
-\begin{lemma}[{\cite[Corollary~3.3]{S}}]\label{lemma:Stepanov-ideal}
-Let $\Phi$ be a root system of rank $\geqslant2$, let $R$ be a commutative ring and $I\trianglelefteq R$ be its ideal.
-If $\Phi\neq\rC_\ell$ then $\E\left(\Phi,R,I^2\right)\leqslant\E(\Phi,I)$, otherwise $\E\left(\Phi,R,II^{\indexbox{2}}\right)\leqslant\E(\Phi,I)$.
-\end{lemma}
-Here $I^{\indexbox{2}}$ denotes the ideal generated by squares $a^2$, where $a\in I$.
-Recall also that $I^2$ is generated by products $ab$ for all $a,b\in I$.
-Clearly, $II^{\indexbox{2}}$ is generated by elements of the form $a^2b$ for $a,b\in I$.
+Recall that by Taddei's theorem $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).
+
+Using standard relativization argument it is not hard to deduce from Taddei's result that $\E(\Phi,R,I)$ is normal in $\G(\Phi,R,I)$ under the same assumptions on $\Phi$.
+This allows us to define the relative $\K_1$-group as $\K_1(\Phi,R,I)=\G(\Phi,R,I)/\E(\Phi,R,I).$
+When $I=R$, we write $\K_1(\Phi, R)$ for $\K_1(\Phi, R, R)$.
+
+In some cases it is known that $\K_1(\Phi, R, I)$ is trivial.
+For example, $\SK_1(\ell+1,R)=\K(\rA_\ell,R)=1$ for any ring of stable rank $1$ (see Section~\ref{sec:stability-conditions}), 
+and for other root systems some stronger assumption is required such as $\asr(R)=1$ or being semilocal. 
+For any Euclidean ring $\K_1(\Phi, R, I)$ is trivial for every root system $\Phi$.
+
+Let $k$ be a global field, $S$ be a set of places of $k$, 
+$\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and $I$ be an ideal of $\mathcal{O}_S$.
+\begin{prop} \label{prop:K1triv} Assume that the field $k$ has a real embedding. Then $\K_1(\Phi,\mathcal{O}_S,I)=1$. \end{prop}
+\begin{proof} Follows from \cite[Theorem~3.6]{BassMilnorSerre} and \cite[Corollary~4.5]{Ma69}. \end{proof}
 

### 2015-09-01 congrsubgr-boundgen.tex
Added one more auxiliary lemma to the introduction

@@
 Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
- (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\ref{rel:R6}), we have a decomposition
+ (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\ref{rel:h-w}), we have a decomposition
 \[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]

### 2015-09-01 paper.tex
Added one more auxiliary lemma to the introduction

@@
 
-Now we are ready to state a recent theorem of A.~Stepanov (see~\cite[Theorem~3.4]{S}).  
-\begin{thm*}\label{thm:Stepanov}
+Now we are ready to state a recent result of A.~Stepanov.  
+\begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
 Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S \subset \Phi$ be any parabolic subset of roots.
 Then $\E(\Phi, R, I)$ is generated as an abstract group by $\mathcal{Z}(\Sigma_S)$.
-\end{thm*}
+\end{prop}
 
@@
 Let $J\subseteq \Pi$ be a subset of simple roots. 
-For a root $\beta = \sum d_i\alpha_i \in \Phi$ set $\shape(J, \beta):=\sum\limits_{i\in J}d_i \alpha_i$.
+For a root $\beta = \sum m_i(\beta)\alpha_i \in \Phi$ set $\shape(J, \beta):=\sum\limits_{i\in J} m_i(\beta) \alpha_i$.
 Set $$\Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\},\quad \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha)\in\Phi^\pm \}.$$
@@
 The integers $N_{\alpha\beta ij}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.
+We refer the reader to~\cite[\S14]{VP} for basic properties of structure constants.
 
@@
 \end{equation}
-where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S13]{VP} for more details on $\eta_{\alpha, \beta}$).
+where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed through structure constants (cf.~\cite[\S13]{VP}).
+For a subset $\Psi \subseteq \Phi$ denote by $\widetilde{W}(\Psi)$ the subgroup of $\E(\Phi, R)$ generated by all $w_{\alpha}(1)$, $\alpha \in \Psi$.
+\begin{lemma} \begin{thmlist} \item For every roots $\alpha, \beta \in \Phi$ having the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
+ \item The elementary group $\E(\Phi, R)$ (resp. $\EP_r(R)$, $1\leq r\leq \ell$) is generated as an abstract group by root subgroups $X_{\alpha}(R)$, $\alpha \in S$,
+       where $S = \Pi \cup -\Pi$ (resp. $S = \Pi \cup -\Pi \setminus \{ -\alpha_r \}$).
+ \item Assume that for a simple root $\alpha_s\in \Pi$ one has $m_s(\alpha_\mathrm{max}) = 1$.
+       Then for $\alpha, \beta \in \Sigma^\pm_s$ having the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$. \end{thmlist} \end{lemma}
+\begin{proof}
+ The first statement of the lemma follows from identity~\ref{rel:R3} and the well-known fact that the Weyl group $W(\Phi)$ acts transitively on the set of roots of the same length.
 
-Define semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$. Then
-\begin{equation}\label{rel:R6}
-h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R.
-\end{equation}
+ The prove the second statement observe that the subgroup $\langle X_\alpha(R) \mid \alpha \in S \rangle$ contains $\widetilde{W}(\Phi)$ (resp. $\widetilde{W}(\Delta_s)$).
+ %TODO: FINISH PROOF
+\end{proof}
+
+Define semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
+The elements $h_\alpha(\varepsilon)$ satisfy the following relations:
+\begin{align}
+ [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] & = 1, & \alpha, \beta \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^*  \label{rel:h-comm} \\
+ h_\alpha(\varepsilon_1 \varepsilon_2) & = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2) & \alpha \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^* \label{rel:h-mult} \\
+ h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} & = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right) & \alpha, \beta \in \Phi,\ \varepsilon \in R^*, \xi \in R \label{rel:h-w}
+\end{align}
 
@@
 
-In case $\Phi=\rC_\ell$ the long and short root unipotenrs are
+In case $\Phi=\rC_\ell$ the long and short root unipotents are
 \begin{align*}
@@
 \subsection{$\K_1$-functor modeled on Chevalley groups}
-
 Recall that by Taddei's theorem $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).

### 2015-09-01 paper.tex
Several tabular and alignment issues

@@
 \begin{align}
-& \phantom{\left[{}\vphantom{x_\beta(t)}\right.}
+& \phantom{[}
 x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \label{rel:add}\\
-& \left[x_\alpha(s),  x_\beta(t)\right] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
+& [x_\alpha(s),  x_\beta(t)] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
 \end{align} 
@@
 For a subset $\Psi \subseteq \Phi$ denote by $\widetilde{W}(\Psi)$ the subgroup of $\E(\Phi, R)$ generated by all $w_{\alpha}(1)$, $\alpha \in \Psi$.
-\begin{lemma} \begin{thmlist} \item For every roots $\alpha, \beta \in \Phi$ having the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
+\begin{lemma}
+\begin{thmlist}
+\item For every roots $\alpha, \beta \in \Phi$ having the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
 \item The elementary group $\E(\Phi, R)$ (resp. $\EP_r(R)$, $1\leq r\leq \ell$) is generated as an abstract group by root subgroups $X_{\alpha}(R)$, $\alpha \in S$,
@@
 \item Assume that for a simple root $\alpha_s\in \Pi$ one has $m_s(\alpha_\mathrm{max}) = 1$.
-       Then for $\alpha, \beta \in \Sigma^\pm_s$ having the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$. \end{thmlist} \end{lemma}
+       Then for $\alpha, \beta \in \Sigma^\pm_s$ having the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$.
+\end{thmlist}
+\end{lemma}
 \begin{proof}
@@
 The elements $h_\alpha(\varepsilon)$ satisfy the following relations:
-\begin{align}
- [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] & = 1, & \alpha, \beta \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^*  \label{rel:h-comm} \\
- h_\alpha(\varepsilon_1 \varepsilon_2) & = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2) & \alpha \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^* \label{rel:h-mult} \\
- h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} & = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right) & \alpha, \beta \in \Phi,\ \varepsilon \in R^*, \xi \in R \label{rel:h-w}
-\end{align}
+\begin{alignat}{2}
+& [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] = 1, &\quad& \alpha, \beta \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-comm} \\
+& \phantom{[} h_\alpha(\varepsilon_1 \varepsilon_2) = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2), && \alpha \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-mult} \\
+& \phantom{[} h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right), && \alpha, \beta \in \Phi,\ \varepsilon \in R^*, \xi \in R.
+\label{rel:h-w}
+\end{alignat}
 

### 2015-09-01 paper.tex
Proved lemma 3

@@
 For a subset $\Psi \subseteq \Phi$ denote by $\widetilde{W}(\Psi)$ the subgroup of $\E(\Phi, R)$ generated by all $w_{\alpha}(1)$, $\alpha \in \Psi$.
-\begin{lemma}
+\begin{lemma} \label{lemma:weylfacts} Let $\Phi$ be an irreducible root system and let $I$ be an ideal of $R$.
+Assume also that $\alpha_s\in \Pi$ is a simple root of $\Phi$ such that $m_s(\alpha_\mathrm{max}) = 1$.
 \begin{thmlist}
-\item For every roots $\alpha, \beta \in \Phi$ having the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
-\item The elementary group $\E(\Phi, R)$ (resp. $\EP_r(R)$, $1\leq r\leq \ell$) is generated as an abstract group by root subgroups $X_{\alpha}(R)$, $\alpha \in S$,
-       where $S = \Pi \cup -\Pi$ (resp. $S = \Pi \cup -\Pi \setminus \{ -\alpha_r \}$).
-\item Assume that for a simple root $\alpha_s\in \Pi$ one has $m_s(\alpha_\mathrm{max}) = 1$.
-       Then for $\alpha, \beta \in \Sigma^\pm_s$ having the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$.
+\item \label{item-trans1} For every roots $\alpha, \beta \in \Phi$ of the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
+\item \label{item-trans2} For $\alpha, \beta \in \Sigma^\pm_s$ of the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$.
+\item \label{item-egen} The elementary group $\E(\Phi, R)$  is generated as an abstract group by root subgroups $X_{\alpha}(R)$, $\alpha \in \Pi \cup -\Pi$.
 \end{thmlist}
@@
 
- The prove the second statement observe that the subgroup $\langle X_\alpha(R) \mid \alpha \in S \rangle$ contains $\widetilde{W}(\Phi)$ (resp. $\widetilde{W}(\Delta_s)$).
- %TODO: FINISH PROOF
+The same argument combined with~\cref{lemma:abs} also proves the second statement. Indeed, by our assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.
+
+To prove the third assertion notice that the subgroup $\langle X_\alpha(R) \mid \alpha \in \Pi \cup -\Pi \rangle$ contains $\widetilde{W}(\Phi)$ and therefore contains all other root subgroups $X_\alpha(R)$, $\alpha\in \Phi$.
 \end{proof}
@@
 When $I=R$ we also write $\EP_J(R)$ instead of $\EP_J(R, R)$.
+
+\begin{rem}
+Notice that by the same token as in the proof of~\cref{lemma:weylfacts} one can show that $\EP_s(R)$ is generated as an abstract group by root subgroups $X_\alpha(R)$, $\alpha\in \Pi \cup (-\Pi\setminus \{ -\alpha_ s\})$, $1\leq s\leq \ell$.
+\end{rem}
 

### 2015-09-01 dennis-vaserstein.tex
Added one more auxiliary lemma to the introduction
Several tabular and alignment issues
Purged some unneccessary facts

@@
 
-\begin{lemma}\label{lemma:dv-normal} The set $A_{rs}$ is normalized by the subgroup $\EP_{\{r,s\}}(R) \leq \E(\Phi, R)$. \end{lemma}
+%\begin{lemma}\label{lemma:dv-normal} The set $A_{rs}$ is normalized by the subgroup $\EP_{\{r,s\}}(R) \leq \E(\Phi, R)$. \end{lemma}
 
@@
 The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition under the following assumptions on $I$.
-\[\begin{array}{|c|l|c|l|}
-\hline \Phi & s & r & \text{ring condition} \\ \hline
+\[\begin{array}{l@{\qquad}c@{\quad}c@{\qquad}l}
+\Phi & s & r & \text{ring condition} \\ \hline\vphantom{\Bigl(}
 \rA_\ell, \rB_\ell,\ \ell\geqslant 2 & 1 & \ell & \sr(I) \leqslant \ell-1 \\     
@@
 \rE_\ell,\ \ell=6,7             & \ell & 2 & \sr(I) \leqslant \ell-3 \\ 
-\rE_\ell,\ \ell=6,7             & \ell & 1 & \asr(I)\leqslant \ell-2 \\ \hline
+\rE_\ell,\ \ell=6,7             & \ell & 1 & \asr(I)\leqslant \ell-2
 \end{array}\]
@@
 \end{enumerate}
-Then $X_{-\alpha_r}(I) \subseteq L_{rs}$ and $\EP_s(R) \subseteq N_{rs}.$
+Then $X_{-\alpha_r}(I) \subseteq L_{rs}$ and $X_{-\alpha_r}(R) \subseteq N_{rs}.$
 \end{lemma}
@@
 \begin{equation} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A. \end{equation}
+Clearly, the assertion of the lemma follows from~\ref{rel:linv}--\ref{rel:ninv}
+\end{proof}
 
-To prove the second part of the statement observe first that $\EP_s(R)$ is generated by $X_{\alpha\ssub{i}}(R)$ for $1\leqslant i\leqslant n$ and $X_{-\alpha\ssub{i}}(R)$ for $i\neq s$.
-%TODO: Find proper reference for this fact
-From \ref{rel:ninv} it follows that $X_{-\alpha_r}(R)\subseteq N_{rs}$.
-On the other hand, inclusions $X_{\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $\ 1\leqslant k\leqslant \ell$ and $X_{-\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
-\end{proof}
+%To prove the second part of the statement observe first that $\EP_s(R)$ is generated by $X_{\alpha\ssub{i}}(R)$ for $1\leqslant i\leqslant n$ and $X_{-\alpha\ssub{i}}(R)$ for $i\neq s$.
+%From \ref{rel:ninv} it follows that $X_{-\alpha_r}(R)\subseteq N_{rs}$.
+%On the other hand, inclusions $X_{\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $\ 1\leqslant k\leqslant \ell$ and $X_{-\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
 
@@
 From now on we can assume that the conclusion of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
-Notice that in view of Theorem~\ref{thm:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:
+Notice that in view of~\cref{prop:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:
 \begin{itemize} \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;

### 2015-09-02 paper.tex
Purged some unneccessary facts
Partly rewritten proof of Dennis---Vaserstein

@@
 \Crefname{prop}{Proposition}{Propositions}
+
+\Crefname{thmlisti}{Lemma}{Lemmas}
 
@@
 For a root $\beta = \sum m_i(\beta)\alpha_i \in \Phi$ set $\shape(J, \beta):=\sum\limits_{i\in J} m_i(\beta) \alpha_i$.
-Set $$\Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\},\quad \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha)\in\Phi^\pm \}.$$
-Clearly, $\Delta_J$ is a reductive subset of roots while $\Sigma^\pm_J$ are special subsets.
+Set $$\Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\},\quad \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha)\in\Phi^\pm \}, \quad S_J^\pm := \Delta_J \sqcup \Sigma_J^\pm.$$
+Clearly, $\Delta_J$ is a reductive subset, while $S^\pm_J$ and $\Sigma^\pm_J$ are reductive and special subsets, respectively.
 For two disjoint subsets $I, J\subseteq \Pi$ one has $\Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J$ while $\Delta_{I\cup J} = \Delta_I \cap \Delta_J$.
@@
 \begin{lemma} \label{lemma:weylfacts} Let $\Phi$ be an irreducible root system and let $I$ be an ideal of $R$. 
-Assume also that $\alpha_s\in \Pi$ is a simple root of $\Phi$ such that $m_s(\alpha_\mathrm{max}) = 1$.
 \begin{thmlist}
 \item \label{item-trans1} For every roots $\alpha, \beta \in \Phi$ of the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
-\item \label{item-trans2} For $\alpha, \beta \in \Sigma^\pm_s$ of the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$.
 \item \label{item-egen} The elementary group $\E(\Phi, R)$  is generated as an abstract group by root subgroups $X_{\alpha}(R)$, $\alpha \in \Pi \cup -\Pi$.
+\item \label{item-trans2} Assume that $\alpha_s\in \Pi$ is a simple root of $\Phi$ such that $m_s(\alpha_\mathrm{max}) = 1$. 
+Then for $\alpha, \beta \in \Sigma^\pm_s$ of the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$.
+
 \end{thmlist}
@@
 
-The same argument combined with~\cref{lemma:abs} also proves the second statement. Indeed, by our assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.
+The same argument combined with~\cref{lemma:abs} also proves the third statement. Indeed, by our assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.
 
-To prove the third assertion notice that the subgroup $\langle X_\alpha(R) \mid \alpha \in \Pi \cup -\Pi \rangle$ contains $\widetilde{W}(\Phi)$ and therefore contains all other root subgroups $X_\alpha(R)$, $\alpha\in \Phi$.
+To prove the second assertion notice that the subgroup $\langle X_\alpha(R) \mid \alpha \in \Pi \cup -\Pi \rangle$ contains $\widetilde{W}(\Phi)$ and therefore contains all other root subgroups $X_\alpha(R)$, $\alpha\in \Phi$.
 \end{proof}
@@
 When $I=R$ we also write $\EP_J(R)$ instead of $\EP_J(R, R)$.
-
-\begin{rem}
-Notice that by the same token as in the proof of~\cref{lemma:weylfacts} one can show that $\EP_s(R)$ is generated as an abstract group by root subgroups $X_\alpha(R)$, $\alpha\in \Pi \cup (-\Pi\setminus \{ -\alpha_ s\})$, $1\leq s\leq \ell$.
-\end{rem}
 

### 2015-09-02 dennis-vaserstein.tex
Minor change

@@
-Let $\Phi$ be an irreducible root system of rank $\ell$ and let $1\leq r,s \leq \ell$ be two distinct integers.
+Let $\Phi$ be an irreducible root system of rank $\ell$.
+In what follows, $r$ and $s$ are two distinct integers such that $1 \leq r, s \leq \ell$.
 From Levi decomposition~\ref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
@@
 \hspace{5em} = \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s, I) = \\
-= \EP_r(R, I) \cdot \U(\Sigma^-_r\cap \Sigma^-_s, I) \cdot \EP_s(R, I).
+= \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).
 \end{multline*}
-
-%\begin{lemma}\label{lemma:dv-normal} The set $A_{rs}$ is normalized by the subgroup $\EP_{\{r,s\}}(R) \leq \E(\Phi, R)$. \end{lemma}
 
@@
 %Denote by $N_{rs}$ and $L_{rs}$ stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
-Consider the following two subsets of $\E(\Phi, R)$:
-\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} = A_{rs} \right\}, \quad
+Consider the following two submonoids of $\E(\Phi, R)$:
+\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \right\}, \quad
    L_{rs}=  \left\{ g\in \E(\Phi, R, I)\ \middle|\ g \cdot A_{rs} \subseteq A_{rs} \right\}. \]
@@
 Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
-$$h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} = g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g = A_{rs}.$$
+\begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
+It is also clear that $L_{rs}$ contains $\EP_r(R, I)$.
+
+\begin{lemma}\label{lemma:dv-normal} 
+For every $\alpha \in \Delta_{\{r,s\}} \cup (\Phi^+ \setminus (\Sigma^+_r \cap \Sigma^+_s))$ one has $X_\alpha(R) \subseteq N_{rs}$. \end{lemma}
+\begin{proof}
+Notice that for every $i$ the factor $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence a fortiori it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
+Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r,s\}}, R)$ we obtain the assertion of the lemma for $\alpha \in \Delta_{\{r, s\}}$.
+
+Now if $\alpha$ lies in $\Phi^+ \setminus \Sigma_r \cap \Sigma_s$ it is contained either in $\Delta_r$ or in $\Delta_s$.
+Assume, for example, the latter. It remains to notice that $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}.$
+\end{proof}
 
@@
 Together with the third statement of~\cref{lemma:dv_unipotent} this implies that
-\begin{equation} \label{rel:sred} A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I). \end{equation}
+\begin{equation*} \label{rel:sred} A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I). \end{equation*}
 Consequently, from the second statement of~\cref{lemma:dv_unipotent} it follows that
@@
 \begin{equation} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A. \end{equation}
-Clearly, the assertion of the lemma follows from~\ref{rel:linv}--\ref{rel:ninv}
-\end{proof}
+Clearly, the assertion of the lemma follows from~\ref{rel:linv}--\ref{rel:ninv}. \end{proof}
 
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:DennisVaserstein}]
 We first show that the assumed stability conditions on $I$ imply the assumptions of Lemma~\ref{lemma:Stein_reduction}.
@@
 
-From now on we can assume that the conclusion of Lemma~\ref{lemma:Stein_reduction} holds and $\EP_s$ normalizes $A_{rs}$.
-Notice that in view of~\cref{prop:Stepanov} it suffices to show that the following two families of elements are contained in $L_{rs}$:
-\begin{itemize} \item $z_{\alpha}(s, \xi)$, $s\in I$, $\xi \in R$, $\alpha\in\Sigma^-_s$;
-\item $x_{\beta}(s)$, $s \in I$, $\beta \in \Phi$. \end{itemize}
-Since $\EP_s \subseteq N_{rs}$, the inclusions for the first family of elements follow from those for the second one.
-We already know that $\U(\Phi^+, I) \subseteq L_{rs}$, hence it only suffices to show $\U(\Phi^-, I) \subseteq L_{rs}$.
+\begin{proof}[Proof of Theorem~\ref{thm:DennisVaserstein}]
+We may assume that the assertion of~\cref{lemma:Stein_reduction} holds.
+Set $\Pi' = \Pi \setminus \{\alpha_s\}$.
+From~\cref{lemma:dv-normal} and \cref{lemma:Stein_reduction} it follows that $X_\alpha(R) \subseteq N_{rs}$ for $\alpha \in \Pi' \cup -\Pi'$.
+Since $\Delta_s$ is irreducible in all the cases under consideration we get from~\cref{item-egen} that $\E(\Delta_s, R) \subseteq N_{rs}$.
 
-Notice that the Weyl group $W(\Delta_s)$ acts transitively on $\Delta_s$, therefore in view of relation~\ref{rel:R3} the subgroup
-$W_s := \langle w_\alpha(1) \mid \alpha\in\Delta_s\rangle \leqslant \EP_s$ acts transitively on the set of root subgroups $X_\alpha(I)$, $\alpha\in \Delta_s$
-and we get that that $\U(\Delta_s \cap \Phi^-, I)\subseteq L_{rs}$.
+Our next step is to show that $\U(\Sigma_s, R) \subseteq N_{rs}$.
+First of all, notice that by~\cref{lemma:dv-normal} we have that $X_{\alpha_s}(R) \subseteq N_{rs}$.
+In the case $\Phi\neq \rB_\ell, \rC_\ell$ all roots of $\Sigma^+_s$ have the same $s$-shape and length therefore the needed statement follows from~\cref{item-trans2}.
+In the case $\Phi=\rB_\ell$ (resp. $\Phi=\rC_\ell$) the above argument only shows that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ (resp. $\U(\Sigma_s^{+<}, R) \subseteq N_{rs}$)
+and a separate argument is needed for the root subgroup corresponding to the sole short (resp. long) root of $\Sigma_s^+$.
 
-%Now denote by $\widetilde{\alpha}$ the maximal root of $\Phi$.
-By our assumptions on $\Phi$ we have $m_s(\alpha\ssub{\mathrm{max}})=1$, hence every two roots $\alpha, \beta \in \Sigma^-_s$ of the same length
-have the same $s$-shape and
-%(i.\,e. $\shape(\{s\}, \alpha = \shape(\{s\}, \beta)$).
-hence by Lemma~\ref{lemma:abs} are interchanged by the action of $W(\Delta_s)$. % $\alpha$ and $\beta$ if their length is equal.
-%By the same argument as above we get that $W(\Delta_s)$.
-Since $X_{\alpha\ssub{s}} \subseteq L_{rs}$ by the same argument as above, we get $\U({\Sigma^-_s}^>, I)\subseteq L_{rs}$.
-This completes the proof of the theorem for $\Phi\neq \rB_\ell$.
+Specializing commutator formula~\ref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
+\begin{equation} \label{rel:CCF-specBC} t_{1,0}(ab) = [t_{1, 2}(a), t_{2, 0}(b)] \cdot t_{1,-2}(-a b^2), \quad t_{1,-1}(-ab^2) = t_{-2,1}(ab) \cdot [t_{-2, 2}(a), t_{2, -1}(b)]. \end{equation}
+Clearly, the root subgroup $X_{2, 0}(R)$ (resp.
+$X_{-2,2}(R)$) is contained in $\E(\Delta_s, R) \subseteq N_{rs}$ while we already know by the above argument that the subgroups $X_{2, 0}(R)$, $X_{1,-2}(R)$
+(resp. $X_{-2,1}(R)$, $X_{2,-1}(R)$) are contained in $N_{rs}$.
 
-In the case $\Phi=\rB_\ell$ we have to show additionally that $X_{-\alpha^<_{\mathrm{max}}}(I) \leqslant L_{rs}$, where $\alpha^<_{\mathrm{max}}$
-denotes the maximal short root of $\rB_\ell$.
-By Chevalley commutator formula we have
-\[ x_{-{\alpha^<_{\mathrm{max}}}}(s) = x_{-1,0}(s) = x_{1,-2}(s) \cdot x_{-1,-2}(-s)^{x_{-2, 0}(-1)} \cdot x_{-1, 2}(\xi),\ s\in I. \]
-On the other hand, $x_{-2,0}(1) \in \EP_s$, and we have already shown $X_{-1,-2}(I), X_{-1, 2}(I) \subseteq L_{rs}$.
-This concludes the proof of the theorem.
+Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. By~\cref{prop:Stepanov} it is enough to prove the inclusion $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
+In turn, in view of identity \ref{rel:NnormL} and the previous part of the proof it suffices to show that $\mathcal{X} \subseteq L_{rs}$.
+
+%TODO: finish proof of the theorem
 \end{proof}

### 2015-09-03 dennis-vaserstein.tex
Finished rewriting Dennis--Vaserstein combinatorial part

@@
 \begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
-It is also clear that $L_{rs}$ contains $\EP_r(R, I)$.
 
@@
 
-Specializing commutator formula~\ref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
+Specializing identity~\ref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
 \begin{equation} \label{rel:CCF-specBC} t_{1,0}(ab) = [t_{1, 2}(a), t_{2, 0}(b)] \cdot t_{1,-2}(-a b^2), \quad t_{1,-1}(-ab^2) = t_{-2,1}(ab) \cdot [t_{-2, 2}(a), t_{2, -1}(b)]. \end{equation}
@@
 
-Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. By~\cref{prop:Stepanov} it is enough to prove the inclusion $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
-In turn, in view of identity \ref{rel:NnormL} and the previous part of the proof it suffices to show that $\mathcal{X} \subseteq L_{rs}$.
+Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. 
+By~\cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
+In fact, in view of identity \ref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
+It is obvious that $\EP_r(R, I) \subseteq L_{rs}$.
+From $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$.
+Thus, we are left to prove the inclusion $\U(\Sigma^-_r \cap \Sigma^-_s, I) \subseteq L_{rs}$.
+
+Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
+The proof in the case $\Phi=\rB_\ell$ is also similar to the one presented above.
+Indeed, from the identity $t_{0, 1}(-a) = [t_{2,1}(-a); t_{0, 2}(-1)] t_{-2,1}(a)$ we conclude that
+$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{t_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}.$$
 

### 2015-09-03 subsystem-factorizations.tex
Added some introduction and stated some theorems

@@
-One of the reasons to study parabolic factorizations is that they provide an easy way to obtain subsystem factorizations, that is a decomposition of a given Chevalley group into a product of some of its subsystem subgroups.
-Among such decompositions one is of particular interest, namely the $\rA_n$-factorization.
-Those, in turn, come in two denominations:
-\begin{itemize}
-\item $\SL_2$-factorizations, see~\cite{LiebNikShaSL2,VavKovSL2};
-\item $\SL_n$-factorizations for $n$ submaximal, see~\cite{NikProdDecomp}.
-\end{itemize}
 The main result of \cite{NikProdDecomp} is the following
 \begin{thm*}
-Let $G$ be a classical Chevalley group of rank $n+1$ over a finite field. Then $G$ equals the product of at most $200$ conjugates of an $\SL_{n+1}$ subgroup.
+Let $G$ be a classical (possibly twisted) Chevalley group of rank $n$ over a finite field. Then $G$ equals the product of at most $200$ conjugates of an $\SL_n$ subgroup.
 \end{thm*}
-The above theorem holds for the twisted classical groups as well.
+As indicated in the introduction, the Dennis---Vaserstein decomposition gives the following result.
+\begin{lemma}
+Assume $\sr(I)\leqslant n-1$. Then $\SL(n+1,R,I)$ is a product of at most $5$ subgroups isomorphic to $\SL(n,R,I)$.
+\end{lemma}
+\begin{proof}
+By the Dennis---Vaserstein decomposition one can present $\SL(n+1,R,I)$ as a product
+\[ \SL(n+1,R,I) =  \Par_1\cdot X_{n1}\cdot\Par_n=S_1\U_1\cdot X_{n1}\cdot\U_n S_n, \]
+where $S_1$ and $S_n$ are two obvious embeddings of $\SL(n,R,I)$ in $\SL(n+1,R,I)$, avoiding respectively the first and the last row and column.
+Now $\U_1=(\U_1\cap S_n)\cdot X_{1n}$ and $U_n= X_{1n}\cdot(U_n\cap S_1)$, while $X_{1n}X_{n1}X_{1n}\in S_1^{w_{12}(1)}$.
+\end{proof}
+We will now elaborate on the case $\Phi=\rD_\ell$ to show that the Dennis---Vaserstein decomposition is suitable for handling other Chevalley groups, albeit with a stronger assumption on the base ring.
+The following lemma is an analogue of Proposition~1 of~\cite{NikProdDecomp}.
+\begin{lemma}
+Let $\Phi=\rD_\ell$. There exist an element $y\in\G(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell)\subset[\U(\Delta_\ell^-),y]\cdot{}^w\U(\Delta_\ell^+)$.
+\end{lemma}
+\begin{proof}
+Set $\beta_i = \alpha_{2i-1} + 2\alpha_{2i}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell$, for $i=1,\ldots,\lfloor\ell/2\rfloor$, i.\,e.
+$\beta_i$ form a maximal set of pairwise orthogonal maximal roots in some subsystems of type $\rD_{k}$.
+Denote $B=\{\beta_i\}$, then decompose $\U(\Sigma_\ell)=\U(\Sigma_\ell\setminus B)\cdot\U(B)$.
 
-\cite{NikProdDecomp} also contains a proof that over a field $\SL(n+1,F)$ is a product of four copies of $\SL(n,F)$. In fact, this is true for any Hermitian ring (for example, any PID qualifies).
+Set $y=\prod_{\beta\in B}x_\beta(1)$. We will now show that $\U(\Sigma_\ell\setminus B)\subset[\U(\Delta_\ell^-),y]\cdot\U(B)$.
 
-The following lemma is a reformulation of Proposition~1 from \cite{NikProdDecomp}:
-\begin{lemma}
-Let $\Phi$ be a root system of rank $\ell$, $\Delta<\Phi$ an $\rA_{\ell-1}$-subsystem, $\Sigma\subset\Phi^+$ a closed set of positive roots and $\Psi_1,\ldots,\Psi_K\subset\Phi$ be sets of roots such that:
-\begin{enumerate}
-\item For any $\alpha\in\Delta^+$ and for any $i=1,\ldots,K$, the elementary root unipotent $x_\alpha$ does not commute with at most one of $x_\beta$, $\beta\in\Psi_i$;
-\item $\Sigma\subset\Delta^++\bigcup_{i=1}^K\Psi_i$.
-\end{enumerate} 
-Then $\U(\Sigma)\subset\prod_{i=1}^{K}\left[\U(\Delta^+),a_i\right]$, where $a_i=\prod_{\beta\in\Psi_i}x_\beta(1)$.
-\end{lemma}
-Of course, each of the commutators in the statement of the Lemma can be written in the reversed order.
-
-Now starting from a unitriangular factorization, one can express $\U(\Phi^\pm)=\U(\Delta^\pm)\U(\Sigma^\pm)$ for $\Sigma^\pm=\Phi^\pm\setminus\Delta$, then cover each of $\U(\Sigma^\pm)$ with a product of conjugates of $\U(\Delta^\pm)$, and put all the factors together.
-
-However, one can start from a parabolic decomposition, which might already have a large $\rA_n$-factor, namely the Levi subgroup of a given parabolic.
-
-Over a ring $R$ of stable rank $1$ one has a decomposition $\G(\Phi,R)=P_\alpha\U_\alpha^-P_\alpha$, where $\U_\alpha^-=\U(\Sigma_\alpha^-)$ is the unipotent radical of the parabolic subgroup $P_\alpha^-$.
-This follows immediately from the Gauss decomposition.
-Choosing $\alpha\in\Pi$ so that $\Delta=\Delta_\alpha$ is of type $\rA$, we find suitable $\Psi_1,\ldots,\Psi_K$ and see that $\G(\Phi,R)=\G(\Delta_\alpha)\U(\Sigma_\alpha)\U(\Sigma_\alpha^-)\U(\Sigma_\alpha)$ is a product of $1+3\cdot\lfloor K/2\rfloor+(K\bmod2)$ conjugated of $\G(\Delta_\alpha)$.
+We first note that
+\[ \bigl[\U(\Delta_2^-),x_{\beta_1}(1)\bigr]=1,\quad \Bigl[\U(\Sigma_2^-\cap\Delta_\ell),\prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
+This implies
+\[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell)\cdot\U(\Delta_{2,\ell}^-), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell\cap\Delta_2).
+\]
+Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell)$ and decompose it as $u=vw$, $v\in\U(\Sigma_{1,2}^-\cap\Delta_\ell)$, $w\in\U(\Sigma_2^-\cap\Delta_{1,\ell})$, then, using the identity $[ab,c]={}^a[b,c]\cdot[a,c]$, rewrite
+\[ [vw,x_{\beta_1}(1)] = {}^v[w,x_{\beta_1}(1)]\cdot[v,x_{\beta_1}(1)].  \]
+Since $\U(\Sigma_{1,2}^-\cap\Delta_\ell)$ and $\U(\Sigma_2^-\cap\Delta_{1,\ell})$ are abelian, it is easy to see that
+\[ [v,x_{\beta_1}(1)]\in\U(\Sigma_{2,\ell}\cap\Delta_1), \quad [w,x_{\beta_1}(1)]\in\U(\Sigma_{1,\ell}\setminus\{\beta_1\}), \]
+and varying $v$ and $w$ one can obtain any element of $\U(\Sigma_{2,\ell}\cap\Delta_1)$ and $\U(\Sigma_{1,\ell}\setminus\{\beta_1\})$ respectively. By the Levi decomposition
+\[ {}^v\U(\Sigma_{1,\ell}\setminus\{\beta_1\}) \equiv \U(\Sigma_{1,\ell}\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2). \]
+Thus we have shown that
+\[ [\U(\Sigma_2^-)\cdot\U(\Delta_{2,\ell}),y] \equiv \U(\Sigma_{1,\ell}\cup\Sigma_{2,\ell}\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2), \]
+and this reduces the problem to the $\rD_{\ell-2}$-subsystem $\Delta_{1,2}$.
+So we can carry the induction on the rank of the subsystem, and construct for any given $a\in\U(\Sigma_\ell\setminus B)$ an element $b\in\U(\Delta_\ell^-)$ such that $a\in[b,y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-),y]\cdot\U(B)$.
+\end{proof}

### 2015-09-03 paper.tex
Nikolov lemma for D_l and some intro on subsystem factorizations
The end of Nikolov-type lemma and the A_n-decomposition for Spin_2n

@@
 Using another Dennis---Vaserstein type factorization we obtain the following result.
-\begin{thm} Assume that $\sr(I) = 2$ then the group $\Spin_{2\ell}(R, I)=\G_{sc}(\rD_\ell, R, I)$ is a product of at most $C$ copies of subgroups of type $\rA_{\ell-1}$. \end{thm}
+\begin{thm}\label{thm:spin-sln-prod}
+Assume that $\sr(I) = 2$ then the group $\Spin_{2\ell}(R, I)=\G_{sc}(\rD_\ell, R, I)$ is a product of at most $9$ copies of subgroups of type $\rA_{\ell-1}$.
+\end{thm}
 
@@
 \input{congrsubgr-boundgen}
-%\subsection{Subsystem factorizations}\label{sec:subsysfact}
-%\input{subsystem-factorizations}
+\section{Subsystem factorizations}\label{sec:subsysfact}
+\input{subsystem-factorizations}
 

### 2015-09-03 subsystem-factorizations.tex
The end of Nikolov-type lemma and the A_n-decomposition for Spin_2n

@@
 The following lemma is an analogue of Proposition~1 of~\cite{NikProdDecomp}.
-\begin{lemma}
-Let $\Phi=\rD_\ell$. There exist an element $y\in\G(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell)\subset[\U(\Delta_\ell^-),y]\cdot{}^w\U(\Delta_\ell^+)$.
+\begin{lemma}\label{lemma:nikolov-type-dl}
+Let $\Phi=\rD_\ell$. There exist an element $y\in\G(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell)\subset[\U(\Delta_\ell^-),y]\cdot{}^w\!\U(\Delta_\ell^+)$.
 \end{lemma}
@@
 and varying $v$ and $w$ one can obtain any element of $\U(\Sigma_{2,\ell}\cap\Delta_1)$ and $\U(\Sigma_{1,\ell}\setminus\{\beta_1\})$ respectively. By the Levi decomposition
-\[ {}^v\U(\Sigma_{1,\ell}\setminus\{\beta_1\}) \equiv \U(\Sigma_{1,\ell}\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2). \]
+\[ {}^v\!\U(\Sigma_{1,\ell}\setminus\{\beta_1\}) \equiv \U(\Sigma_{1,\ell}\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2). \]
 Thus we have shown that
@@
 So we can carry the induction on the rank of the subsystem, and construct for any given $a\in\U(\Sigma_\ell\setminus B)$ an element $b\in\U(\Delta_\ell^-)$ such that $a\in[b,y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-),y]\cdot\U(B)$.
+
+It remains to note that the roots $\pm\beta_i$ lie inside a maximal root subsystem of type $\rA_1+\ldots+\rA_1+\rD_3$.
+All such subsystemrs are conjugate under the action of the Weyl group, so there exist an element $w\in W(\Phi)$ such that $w(\beta_1)=\alpha_1$, $w(\beta_2)=\alpha_3$, $w(\beta_3)=\alpha_5$ and so on, so that all of $w(\beta_i)$ lie in $\Delta_\ell^+$.
 \end{proof}
+\begin{proof}[Proof of Theorem~\ref{thm:spin-sln-prod}]
+By Theorem~\ref{thm:DennisVaserstein} one has a decomposition
+\[ \Spin(2\ell,R,I) = \Par_{\ell-1}\cdot\U_{\ell-1,\ell}^-\cdot\Par_{\ell} = \G(\Delta_{\ell-1})\cdot\U(\Sigma_{\ell-1})\cdot\U(\Sigma_{\ell-1,\ell}^-)\cdot\U(\Sigma_{\ell})\cdot\G(\Delta_\ell). \]
+By Lemma~\ref{lemma:nikolov-type-dl} there exist elements $y_1,y_2,y_3\in\G(\rD_\ell,R)$ and $w_1,w_2,w_3\in\widetilde{W}(\rD_\ell)$ such that
+\begin{align*}
+& \U(\Sigma_{\ell-1}) \subset \U(\Delta_{\ell-1}^-) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+), \\
+& \U(\Sigma_\ell) \subset {}^{w_2}\!\U(\Delta_\ell^+) \cdot {}^{y_2}\!\U(\Delta_\ell^-) \cdot \U(\Delta_\ell^-), \\
+& \U(\Sigma_{\ell-1,\ell}^-) \subset \U(\Delta_\ell^+) \cdot {}^{y_3}\!\U(\Delta_\ell^+) \cdot {}^{w_3}\!\U(\Delta_\ell^-).
+\end{align*}
+Thus $\G(\rD_\ell,R,I)$ is a product of $9$ subgroups isomorphic to $\G(\rA_{\ell-1},R,I)\cong\SL(\ell,R,I)$ (and conjugated inside $\G(\rD_\ell,R)$).
+\end{proof}

### 2015-09-03 dennis-vaserstein.tex
Finished rewriting Dennis---Vaserstein decomposition

@@
 The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition under the following assumptions on $I$.
-\[\begin{array}{l@{\qquad}c@{\quad}c@{\qquad}l}
-\Phi & s & r & \text{ring condition} \\ \hline\vphantom{\Bigl(}
-\rA_\ell, \rB_\ell,\ \ell\geqslant 2 & 1 & \ell & \sr(I) \leqslant \ell-1 \\     
-\rC_\ell,\ \ell \geqslant 2          & 1 & \ell & \sr(I) \leqslant \ell-1 \\
-\rD_\ell,\ \ell\geqslant 4           & 1 & \ell & \sr(I) \leqslant \ell-2 \\ 
-\rD_\ell,\ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2 \\
-\rE_\ell,\ \ell=6,7             & \ell & 2 & \sr(I) \leqslant \ell-3 \\ 
-\rE_\ell,\ \ell=6,7             & \ell & 1 & \asr(I)\leqslant \ell-2
-\end{array}\]
+\[\begin{array}{l@{\qquad}l@{\qquad}c@{\quad}c@{\qquad}l}
+   & \Phi                                 & s    & r      & \text{ring condition} \\ \hline\vphantom{\Bigl(}
+1. & \rA_\ell,\ \ell\geqslant 2            & 1    & \ell   & \sr(I) \leqslant \ell-1                         \\    
+2. & \rB_\ell,\ \ell\geqslant 2            & 1    & \ell   & \sr(I) \leqslant \ell-1                         \\
+3. & \rC_\ell,\ \ell \geqslant 2          & 1    & \ell   & \sr(I) \leqslant \ell-1,\ 2I+I^{\indexbox{2}}=I \\
+4. & \rD_\ell,\ \ell\geqslant 4           & 1    & \ell   & \sr(I) \leqslant \ell-2                         \\ 
+5. & \rD_\ell,\ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2                              \\
+6. & \rE_\ell,\ \ell=6,7                  & \ell & 2      & \sr(I) \leqslant \ell-3                         \\ 
+7. & \rE_\ell,\ \ell=6,7                  & \ell & 1      & \asr(I)\leqslant \ell-2                         \end{array}\]
 \end{thm}
-%Consider the usual conjugation action of $\E(\Phi, R)$ on $\E(\Phi, R, I)$. 
-%This action induces an action of $\E(\Phi, R)$ on the set $\mathfrak{S}$ of all subsets of $\E(\Phi, R, I)$.
-%On the other hand, $\E(\Phi, R, I)$ acts on $\mathfrak{S}$ by left multiplication.
-%Denote by $N_{rs}$ and $L_{rs}$ stabilizers of $A_{rs} \in \mathfrak{S}$ with respect to these actions.
 Consider the following two submonoids of $\E(\Phi, R)$:
@@
 \end{enumerate}
-Then $X_{-\alpha_r}(I) \subseteq L_{rs}$ and $X_{-\alpha_r}(R) \subseteq N_{rs}.$
+Then $X_{-\alpha_r}(R) \subseteq N_{rs}.$
 \end{lemma}
@@
 \begin{equation*} \label{rel:sred} A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I). \end{equation*}
-Consequently, from the second statement of~\cref{lemma:dv_unipotent} it follows that
-\begin{equation} \label{rel:linv} X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I) = A. \end{equation}
-Since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we also get that:
-\begin{equation} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A. \end{equation}
-Clearly, the assertion of the lemma follows from~\ref{rel:linv}--\ref{rel:ninv}. \end{proof}
+%Consequently, from the second statement of~\cref{lemma:dv_unipotent} it follows that
+%\begin{equation*} \label{rel:linv} X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I) = A. \end{equation*}
+Consequently, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we get that:
+\begin{equation*} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A, \end{equation*}
+which implies the assertion of the lemma.
+%Clearly, the assertion of the lemma follows from~\ref{rel:linv}--\ref{rel:ninv}.
+\end{proof}
 
-%To prove the second part of the statement observe first that $\EP_s(R)$ is generated by $X_{\alpha\ssub{i}}(R)$ for $1\leqslant i\leqslant n$ and $X_{-\alpha\ssub{i}}(R)$ for $i\neq s$.
-%From \ref{rel:ninv} it follows that $X_{-\alpha_r}(R)\subseteq N_{rs}$.
-%On the other hand, inclusions $X_{\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $\ 1\leqslant k\leqslant \ell$ and $X_{-\alpha\ssub{k}}(R) \subseteq N_{rs}$ for $k\neq r,s$ are obvious.
+First of all we show that the assumptions on $I$ formulated in \cref{thm:DennisVaserstein} imply the conditions of Lemma~\ref{lemma:Stein_reduction}.
+Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
+The type of $\pi$ and the total number of weights in $\Lambda(\pi)$ are listed in Figure~\ref{fig:table}.
 
-We first show that the assumed stability conditions on $I$ imply the assumptions of Lemma~\ref{lemma:Stein_reduction}.
-Consider the following two subsets of $\Lambda(\pi)$:
-$$\Gamma = \varpi_s- (\Sigma_s^+\cap \Delta_r),\quad \Gamma_0 = \{\lambda \in \Gamma \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$$
-With the choice of $s$ as in the assumption, $\Gamma$ is the set of weights of an irreducible representation of $\G(\Delta_r, R)$ corresponding to the same highest weight $\varpi_s$.
-The subsystem $\Delta_r$ has type $\rA_{\ell-1}$ in all cases except the last one.
-It is also clear that $|\Gamma_0|=1$ for $\Phi=\rA_\ell, \rB_\ell$, $|\Gamma_0|=2$ for $\Phi=\rD_\ell$, and $|\Gamma_0|=3$ in case $\Phi=\rE_\ell$ and $r=2$.
-If $\Phi=\rE_\ell$, $r=1$, the subsystem $\Delta_r$ has type $\rD_{\ell-1}$ and $|\Gamma_0|=\ell-1$.
+Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=G(\Delta_r, R)$ it becomes reducible.
+Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
 
-%TODO: PICK AS L_r!!!
-Let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma_0$.
-In any of  the specified cases the assumption on $I$ allows us to apply Lemma~\ref{lemma:uraction} to the subsystem $\Delta_r$ and find
+Consider the following subset of $\Lambda(\pi')$:
+$$ \Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$$
+
+The type of $\pi'$ and the number of elements in $\Lambda(\pi')$, $\Gamma$ are listed in Figure~\ref{fig:table}.
+
+\begin{rem}
+The sets $\Lambda(\pi')$, $\Gamma$ can be visualized using the technique of {\it weight diagrams} developed in~\cite{PSV98}.
+In the simplest case of a microweight representation (i.\,e. a representation without zero weights)
+the weight diagram of $(V, \pi)$ is just a graph whose vertices are in one-to-one correspondence with the set of weights $\Lambda(\pi)$.
+Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ iff $\lambda-\mu = \alpha_i$.
+
+Now let $G$ be the weight diagram of $\pi$.
+The authors of~\cite{PSV98} locate the vertex corresponding to the highest weight of $\pi$ to the upper-left corner of the picture.
+Therefore the subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the upper-left connected component of the graph obtained from $G$ by removing all bonds marked $r$.
+On the other hand, the set $\Gamma$ corresponds to vertices of $\Lambda(\pi')$ which are incident with the removed bonds.
+\end{rem}
+
+\begin{figure}
+\[\begin{array}{l @{\qquad} l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} l @{\qquad} l}
+   & \Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\pi'$}        & (|\Gamma|, |\Gamma_0|)  \\ \hline\vphantom{\Bigl(}
+1. & \rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & (\rA_{l-1}, \varpi_1)        & (\ell,1)  \\     
+2. & \rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & (\rA_{l-1}, \varpi_1)        & (\ell,1) \\     
+3. & \rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & (\rA_{l-1}, \varpi_1)        & (\ell,1)  \\
+4. & \rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & (\rA_{l-1}, \varpi_1)        & (\ell,2)  \\ 
+5. & \rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & (\rA_{l-1}, \varpi_{\ell-1}) & (\ell,\ell-2)  \\
+6. & \rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & (\rA_{l-1}, \varpi_1)        & (\ell,3)  \\ 
+7. & \rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & (\rD_{l-1}, \varpi_1)        & (2\ell-2,\ell-1)  \end{array}\]
+ \caption[Table]{List of representation involved in the proof of~\cref{thm:DennisVaserstein}.} \label{fig:table}
+\end{figure}
+
+Now let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma$.
+Applying~\cref{lemma:uraction} to the subsystem $\Delta_r$ we find
 $x\in\U(\Delta_r\cap\Phi^+, I)$, $y\in \U(\Delta_r\cap\Phi^-, I)$ such that $yx\cdot g \in B$.
-This proves the first condition of Lemma~\ref{lemma:Stein_reduction}, indeed:
-\[ \U(\Sigma^+_r, I) \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \U(\Phi^-, I) B. \]
-To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma_0$ for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
-\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \E(\Delta_s, R, I) \subseteq \EP_s(R, I). \]
+This proves the first assumption of Lemma~\ref{lemma:Stein_reduction}, indeed:
+\[ \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B. \]
+To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma$ and~\cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
+\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s \cap \Phi^-, I) \subseteq \EP_s(R, I). \]
 
 \begin{proof}[Proof of Theorem~\ref{thm:DennisVaserstein}]
-We may assume that the assertion of~\cref{lemma:Stein_reduction} holds.
+By the above discussion we may assume that the assertion of~\cref{lemma:Stein_reduction} holds.
 Set $\Pi' = \Pi \setminus \{\alpha_s\}$.

### 2015-09-04 paper.tex
Finished rewriting Dennis---Vaserstein decomposition
Added Matsumoto lemma

@@
 
-%TODO: Rewrite this using better terminology.
 For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $V_\lambda$ the weight subspace corresponding to $\lambda\in\Lambda$.
+
+\textbf{TODO: Give definitions of $\Lambda^*$, $V^0$, the notion of ``basic representation''. }
+
 For any of the representations described above (with the sole exception of $(\rE_8, \varpi_8)$) all weight subspaces $V_\lambda$ are one-dimensional. 
@@
 \end{align*}
+
+The following result of H.~Matsumoto describes the action of elementary root unipotents in a basic representation of $\G(\Phi, R)$.
+\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
+ Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
+ One can choose a basis $v_\lambda$, $\lambda\in\Lambda(\pi)$ of $V$ such that the action of elementary root unipotents $t_\alpha(\xi)$ on it is described by the following formulae:
+ \begin{thmlist}
+  \item $t_{\alpha}(\xi) v_\lambda = v_\lambda$ for $\lambda\in\Lambda^*(\pi), \lambda+\alpha\not\in\Lambda(\pi)$;
+  \item $t_\alpha(\xi)v_\lambda=v_\lambda\pm\xi v_{\lambda+\alpha}$ for $\lambda,\lambda+\alpha\in\Lambda^*(\pi)$;
+  \item $t_\alpha(\xi)v_0 = v_0$ for every $v_0\in V^0$, $\alpha\not\in\Lambda^*(\pi)$;
+  \item $t_\alpha(\xi)v_{-\alpha}=v_{-\alpha}\pm\xi v_0(\alpha)\pm\xi^2 v_{\alpha},$ $t_\alpha(\xi)v_0 = v_0\pm\xi\alpha_*(v_0)v_\alpha$ for $\alpha\in\Lambda^*(\pi)$.
+ \end{thmlist}
+\end{lemma}
 

### 2015-09-04 congrsubgr-boundgen.tex
Several tabular and alignment issues
Edits from 04.09.15 meeting

@@
 
-\begin{lemma}\label{lemma:srRI1_width} In the assumptions of Lemma~\ref{lemma:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
+\begin{lemma}\label{lemma:srRI1_width}
+In the assumptions of Lemma~\ref{thm:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
 \end{lemma}
@@
 \[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
-and the estimate follows. \end{proof}
+and the estimate follows.
+\end{proof}
 
@@
 Write
-\[ g_1=x_{12}(mk)\cdot g =
-\begin{pmatrix} p^\beta q & * \\ p^\beta bm & * \end{pmatrix}.\]
+\begin{align*}
+g_1 & = x_{12}(mk)\cdot g =
+\begin{pmatrix} p^\beta q & * \\ p^\beta bm & * \end{pmatrix}. \\
+\intertext{
 There exists $u\geqslant 1$ such that $p^u\equiv b\pmod q$, say $p^u=b+lq$. Then
-\[ g_2 =  x_{21}(ml)\cdot g_1 =
-\begin{pmatrix} p^\beta q & * \\ mp^{\beta+u} & * \end{pmatrix}. \]
+}
+g_2 & = x_{21}(ml)\cdot g_1 =
+\begin{pmatrix} p^\beta q & * \\ mp^{\beta+u} & * \end{pmatrix}. \\
+\intertext{
 Since $g_2\equiv 1\pmod m$, we can write $p^\beta q=1+cm$ for some $c$. Now let
-\begin{align*}
-g_3 = & x_{12}\left(\dfrac{-c}{p^{\beta+u}}\right)\cdot g_2 =
+}
+g_3 & = x_{12}\left(\dfrac{-c}{p^{\beta+u}}\right)\cdot g_2 =
 \begin{pmatrix} 1 & * \\ mp^{\beta+u} & * \end{pmatrix}, \\
-g_4 = & x_{21}\left(-mp^{\beta+u}\right)\cdot g_3 =
+g_4 & = x_{21}\left(-mp^{\beta+u}\right)\cdot g_3 =
 \begin{pmatrix} 1 & * \\ 0 & * \end{pmatrix}, \\
-g_5 = & x_{12}\left(\dfrac{c}{p^{\beta+u}}\right)\cdot g_4 =
+g_5 & = x_{12}\left(\dfrac{c}{p^{\beta+u}}\right)\cdot g_4 =
 \begin{pmatrix} 1 & * \\ 0 & * \end{pmatrix}.
@@
 By Lemma~\ref{lemma:Stepanov-ideal} the group $\E\left(\Phi,\mathcal{O}_S,I^2\right)$ is contained in $\E(\Phi,I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
-Notice that under the assumptions of the lemma it is known that $\E(\Phi,I)$ has finite width with respect to $\{x_\alpha(s)\mid\alpha\in\Phi,\ s\in I\}$, see~\cite{Tavgen93} or \cite[Theorem~3.3]{TavgenThesis}.
+Notice that under the assumptions of the lemma it is known that $\E(\Phi,I)$ has finite width with respect to $\mathcal{X}$, see~\cite{Tavgen93} or \cite[Theorem~3.3]{TavgenThesis}.
 

### 2015-09-04 dennis-vaserstein.tex
Edits from 04.09.15 meeting

@@
 \end{lemma}
-\begin{proof} Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
+\begin{proof}
+Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
 From the first assumption of the lemma it follows that $A_{rs}=A$.
 On the other hand, by the second assumption we have
-\begin{multline*} X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
+\begin{multline*}
+X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
 X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
- \subseteq B \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I) \subseteq 
- B \cdot \EP_s(R, I). \end{multline*}
+\subseteq B \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I) =
+B \cdot \EP_s(R, I).
+\end{multline*}
 Together with the third statement of~\cref{lemma:dv_unipotent} this implies that
-\begin{equation*} \label{rel:sred} A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I). \end{equation*}
+\begin{equation*} \label{rel:sred}
+A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).
+\end{equation*}
 %Consequently, from the second statement of~\cref{lemma:dv_unipotent} it follows that
@@
 
-First of all we show that the assumptions on $I$ formulated in \cref{thm:DennisVaserstein} imply the conditions of Lemma~\ref{lemma:Stein_reduction}.
+Let us construct a set $B$ satisfying the assumptions of \cref{lemma:Stein_reduction} explicitly.
+
 Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
@@
 
-Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=G(\Delta_r, R)$ it becomes reducible.
+Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=\G(\Delta_r, R)$ it becomes reducible.
 Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
@@
 In the simplest case of a microweight representation (i.\,e. a representation without zero weights)
-the weight diagram of $(V, \pi)$ is just a graph whose vertices are in one-to-one correspondence with the set of weights $\Lambda(\pi)$.
+the weight diagram of $(V, \pi)$ is just a graph whose vertices are in one-to-one correspondence with the elements of $\Lambda(\pi)$.
 Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ iff $\lambda-\mu = \alpha_i$.
 
-Now let $G$ be the weight diagram of $\pi$.
-The authors of~\cite{PSV98} locate the vertex corresponding to the highest weight of $\pi$ to the upper-left corner of the picture.
-Therefore the subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the upper-left connected component of the graph obtained from $G$ by removing all bonds marked $r$.
-On the other hand, the set $\Gamma$ corresponds to vertices of $\Lambda(\pi')$ which are incident with the removed bonds.
+The authors of~\cite{PSV98} put the vertex corresponding to the highest weight $\varpi_s$ of $\pi$ in the upper-left corner of the weight diagram.
+Therefore the subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the upper-left connected component of the graph obtained by removing all bonds marked $r$.
+In turn, the set $\Gamma$ corresponds to the vertices of $\Lambda(\pi')$ incident to the removed bonds.
 \end{rem}
@@
 \[\begin{array}{l @{\qquad} l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} l @{\qquad} l}
-   & \Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\pi'$}        & (|\Gamma|, |\Gamma_0|)  \\ \hline\vphantom{\Bigl(}
+   & \Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\pi'$}        & (|\Lambda(\pi')|, |\Gamma|)  \\ \hline\vphantom{\Bigl(}
 1. & \rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & (\rA_{l-1}, \varpi_1)        & (\ell,1)  \\     
@@
 
-Now let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for $\lambda\in\Gamma$.
+Now let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
 Applying~\cref{lemma:uraction} to the subsystem $\Delta_r$ we find
-$x\in\U(\Delta_r\cap\Phi^+, I)$, $y\in \U(\Delta_r\cap\Phi^-, I)$ such that $yx\cdot g \in B$.
+$x\in\U(\Delta_r^+, I)$, $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
 This proves the first assumption of Lemma~\ref{lemma:Stein_reduction}, indeed:
@@
 To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma$ and~\cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
-\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s \cap \Phi^-, I) \subseteq \EP_s(R, I). \]
+\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I). \]
 
@@
 
-Specializing identity~\ref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
+Specializing identity~\eqref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
 \begin{equation} \label{rel:CCF-specBC} t_{1,0}(ab) = [t_{1, 2}(a), t_{2, 0}(b)] \cdot t_{1,-2}(-a b^2), \quad t_{1,-1}(-ab^2) = t_{-2,1}(ab) \cdot [t_{-2, 2}(a), t_{2, -1}(b)]. \end{equation}
@@
 By~\cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
-In fact, in view of identity \ref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
+In fact, in view of formula~\eqref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
 It is obvious that $\EP_r(R, I) \subseteq L_{rs}$.
-From $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$.
+From $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$. Indeed, for $g\in\EP_s(R,I)$
+\[ gA_{rs} \subseteq g {A_{rs}}^g = A_rs g = A_rs. \]
 Thus, we are left to prove the inclusion $\U(\Sigma^-_r \cap \Sigma^-_s, I) \subseteq L_{rs}$.

### 2015-09-04 gauss.tex
Partially rewritten DV section
Edits from 04.09.15 meeting

@@
 Since $\E(\Phi,R)$ contains the normalizer of the torus, the set $X^{\E(\Phi,R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi),\  \alpha\in\Phi,\ \xi\in I \rangle$.
-Finally, the inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi,R,I)$ normalizes every root subgroup $\X_\alpha(I)$.
+Finally, the inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi,R,I)$ normalizes every root subgroup $X_\alpha(I)$.
 \end{proof}
 
-\begin{lemma}\label{lemma:srRI1}
+\begin{thm}\label{thm:srRI1}
 Let $\Phi$ be a root system, let $I$ be an ideal of arbitrary commutative ring $R$ such that $\sr(I)=1$.
@@
 \[ \E(\Phi,R,I) = \Hh(\Phi,R,I) \cdot \U(\Phi,I) \cdot \U(\Phi^-,I) \cdot \U(\Phi,I). \]
-\end{lemma}
+\end{thm}
 \begin{proof}
@@
 
-Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}\in\SL(2,R,I)$ be an element of $\SL(2, R, I)$.
+Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}$ be an element of $\SL(2, R, I)$.
 The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.

### 2015-09-04 paper.tex
Reordered subsections of section 4
Edits from 04.09.15 meeting

@@
 \DeclareMathOperator{\Spin}{Spin}
+\DeclareMathOperator{\Epin}{Epin}
 \DeclareMathOperator{\Stab}{Stab}
@@
 \begin{thm}\label{thm:spin-sln-prod}
-Assume that $\sr(I) = 2$ then the group $\Spin_{2\ell}(R, I)=\G_{sc}(\rD_\ell, R, I)$ is a product of at most $9$ copies of subgroups of type $\rA_{\ell-1}$.
+Assume that $\sr(I) \leqslant 2$ then the group $\Epin_{2\ell}(R, I)=\E_{sc}(\rD_\ell, R, I)$ is a product of at most $9$ copies of subgroups of type $\rA_{\ell-1}$.
 \end{thm}
@@
 Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all reflections $\sigma_\alpha$ where $\sigma_\alpha(\beta)=\beta-\langle\alpha,\beta \rangle\cdot \alpha$.
-For $S\subseteq \Phi$ denote by $W(S)$ the subgroup of $W(\Phi)$ generated by $\sigma_\alpha$ for $\alpha\in S$.
+For a reductive subset $\Delta\subseteq \Phi$ denote by $W(\Delta)$ the subgroup of $W(\Phi)$ generated by $\sigma_\alpha$ for $\alpha\in\Delta$.
 
@@
 For a root $\beta = \sum m_i(\beta)\alpha_i \in \Phi$ set $\shape(J, \beta):=\sum\limits_{i\in J} m_i(\beta) \alpha_i$.
-Set $$\Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\},\quad \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha)\in\Phi^\pm \}, \quad S_J^\pm := \Delta_J \sqcup \Sigma_J^\pm.$$
-Clearly, $\Delta_J$ is a reductive subset, while $S^\pm_J$ and $\Sigma^\pm_J$ are reductive and special subsets, respectively.
-For two disjoint subsets $I, J\subseteq \Pi$ one has $\Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J$ while $\Delta_{I\cup J} = \Delta_I \cap \Delta_J$.
+Set $$\Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\},\quad \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha)\in\mathbb{Z}_{\geqslant0}\Phi^\pm \}, \quad S_J^\pm := \Delta_J \sqcup \Sigma_J^\pm.$$
+Clearly, $\Delta_J$ is a reductive subset, while $S^\pm_J$ and $\Sigma^\pm_J$ are parabolic and special subsets, respectively.
+For two disjoint subsets $I, J\subseteq \Pi$ one has 
+\[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
 
@@
 
+For an additive subset $I\subseteq R$ we denote by $X_\alpha(I)$ the corresponding \emph{root subgroup} of level $I$, i.\,e.
+the subgroup consisting of all elementary root unipotents $x_\alpha(\xi)$, $\xi\in I$.
+
+The subgroup $\E(\Phi, R)$, generated by all $X_\alpha(R)$, $\alpha\in\Phi$ is called the {\it elementary subgroup} of the Chevalley group $\G_{sc}(\Phi, R)$.
+
 For $\varepsilon\in R^*$ set $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_{\alpha}(\varepsilon).$
@@
 where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed through structure constants (cf.~\cite[\S13]{VP}).
-For a subset $\Psi \subseteq \Phi$ denote by $\widetilde{W}(\Psi)$ the subgroup of $\E(\Phi, R)$ generated by all $w_{\alpha}(1)$, $\alpha \in \Psi$.
+For a reductive subset $\Delta \subseteq \Phi$ denote by $\widetilde{W}(\Delta)$ the \emph{extended Weyl group}, i.\,e.
+the subgroup of $\E(\Phi, R)$ generated by all $w_{\alpha}(1)$, $\alpha \in \Delta$.
 \begin{lemma} \label{lemma:weylfacts} Let $\Phi$ be an irreducible root system and let $I$ be an ideal of $R$. 
@@
 Let $I\leq R$ be an ideal. Denote by $\E(\Phi, I)$ the subgroup of $\G_{sc}(\Phi, R)$ generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$.
-In the special case $I=R$ the subgroup $\E(\Phi, R)$ is called the {\it elementary subgroup} of the Chevalley group $\G_{sc}(\Phi, R)$.
 
@@
 
-For a special subset of roots $S\subseteq \Phi$ we denote by $\U(S, I)$ the subgroup spanned by all $x_{\alpha}(s)$ for $s\in I$, $\alpha\in S$.
-The subgroup $\U(\Sigma_J, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I)$ is a subgroup. 
+For a special subset of roots $\Sigma\subseteq \Phi$ we denote by $\U(\Sigma, I)$ the subgroup spanned by all $x_{\alpha}(I)$ for $\alpha\in \Sigma$. Let $J\subset\Pi$.
+The subgroup $\U(\Sigma_J, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I)$ is a subgroup called a \emph{standard parabolic subgroup}.
 The following two equalities will be referred to in the sequel as {\it Levi decomposition}: 
@@
 
-Denote by $\Hh(\Phi,R)$ the subgroup generated by all $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$. Then set
+Denote by $\Hh(\Phi,R)$ the subgroup generated by all $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$, and set
 \[ \Hh(\Phi,R,I) = \Hh(\Phi,R)\cap\G(\Phi,R,I)=\langle h_\alpha(\varepsilon),\ \alpha\in\Phi,\ \varepsilon\in R^*\cap(1+I)\rangle. \]
-\begin{lemma}\label{lemma:rel-tor-elementary} $\Hh(\Phi,R,I)\leqslant\E(\Phi,R,I)$. \end{lemma}
+\begin{lemma}\label{lemma:rel-tor-elementary}
+$\Hh(\Phi,R,I)$ is contained in $\E(\Phi,R,I)$.
+\end{lemma}
 \begin{proof}
@@
 $\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and $I$ be an ideal of $\mathcal{O}_S$.
-\begin{prop} \label{prop:K1triv} Assume that the field $k$ has a real embedding. Then $\K_1(\Phi,\mathcal{O}_S,I)=1$. \end{prop}
+\begin{prop} \label{prop:K1triv}
+Let $\Phi$ be a root system of rank $\geqslant2$. Assume that the field $k$ has a real embedding. Then $\K_1(\Phi,\mathcal{O}_S,I)=1$.
+\end{prop}
 \begin{proof} Follows from \cite[Theorem~3.6]{BassMilnorSerre} and \cite[Corollary~4.5]{Ma69}. \end{proof}
@@
 
+\subsection{Relative Gauss decomposition}\label{sec:gauss}
+\input{gauss}
 \subsection{Relative Bass---Kolster decompositions}\label{sec:bass-kolster}
@@
 \input{dennis-vaserstein}
-\subsection{Relative Gauss decomposition}\label{sec:gauss}
-\input{gauss}
 

### 2015-09-04 stability-conditions.tex
Edits from 04.09.15 meeting

--- 2015-08-15 stability-conditions.tex
@@
 
-It is not hard to show that for a $I$-unimodular row $a$ there exists an $I$-unimodular column $b$ such that $ab=1$ (see~\cite[\S~2]{Va69}).
+It is not hard to show that for an $I$-unimodular row $a$ there exists an $I$-unimodular column $b$ such that $ab=1$ (see~\cite[\S~2]{Va69}).
 
@@
 \begin{enumerate}
-\item For any ideal $J\subseteq I$ one has $\sr(J)\leqslant\sr(I)$, $\sr(I/J)\leqslant\sr(I)$.
-\item One has $\sr\left(\prod\limits_{i=1}^n R_i\right)=\max\limits_{i=1}^n\left(\sr(R_i)\right).$
-\item Let $J$ denote the Jacobson radical of $R$, then one has $\sr(R)=\sr(R/J)$.
+\item For any ideal $J\subseteq I$ one has $\sr(J)\leqslant\sr(I)$, $\sr(I/J)\leqslant\sr(I)$;
+\item One has $\sr\Bigl(\prod\limits_{i=1}^n R_i\Bigr)=\max\limits_{i=1}^n\bigl(\sr(R_i)\bigr)$;
+\item Let $J$ denote the Jacobson radical of $R$, then one has $\sr(R)=\sr(R/J)$;
+\item If $I\subseteq J$, then $\sr(I)=1$;
+\item Let $I\rtimes\mathbb{Z}$ denote the ring obtained by formally adjoining $1$ to $I$. Then $\sr(I\rtimes\mathbb{Z})=\max(2,\sr(I))$.
 \end{enumerate}
@@
 Other examples of rings of stable rank $1$ are provided by boolean rings, the ring of algebraic integers, the ring of entire functions, the disk-algebra, etc.
+For this and many other examples see~\cite{VasSR1}.
+
+%Formally adjoining a unit to a non-unital ring of stable rank $1$ produces a non-trivial example of an ideal having the stable rank strictly lower that the ambient ring.
 \end{example}
@@
 Obviously, the second statement of Lemma~\ref{lemma:relative-asr-unimod} does not depend on $R$, hence, as suggested by the notation, $\asr(I)$ is independent of $R$.
-As another corollary of Lemma~\ref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$ (cf.~\cite[\S~1]{Pl98}).
-\begin{cor}[A.~Bak] For a commutative ring $R$ the following statements are equivalent:
+As another corollary of Lemma~\ref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$.
+\begin{cor}[A.~Bak, {cf.~\cite[\S~1]{Pl98}}] For a commutative ring $R$ the following statements are equivalent:
 \begin{enumerate}
@@
 
-Let $R$ be a commutative ring. We denote by $\Max(R)$ its \emph{maximum spectrum} i.e. the set of maximal ideals of $R$ equipped with Zariski topology.
+Let $R$ be a commutative ring.
+We denote by $\Max(R)$ its \emph{maximum spectrum} i.e.
+the set of maximal ideals of $R$ equipped with Zariski topology.
+For a topological space $X$ denote by $\dim(X)$ its usual topological dimension.
 The following result gives an upper estimate for the absolute stable rank (see~\cite[Theorem~2.3]{EO}, \cite[Theorem~3.7]{MKV}).
-\begin{thm}
+\begin{prop}
 Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets 
-$X_1\ldots, X_m$ such that the topological dimension of every subset $X_i$ does not exceed some number $d$. 
-Then $\asr(A)\leqslant d+1$.
-\end{thm}
+$X_1\ldots, X_m$ such that $\dim(X_i)\leqslant d$ for every $i$. Then $\asr(A)\leqslant d+1$.
+\end{prop}
 %TODO: Add more comments?
-Clearly one has
-\[\sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
+From the definition of $\asr(I)$ and the previous proposition it follows that
+\[ \sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
+\begin{rem}
+There exist examples of rings for which the first inequality in the above formula is strict.
+Namely, there are rings of stable rank $1$ but of absolute stable rank $\geqslant2$, see~\cite{MKV}.
+However, \cite[Theorem~1.3]{MKV} shows that $\sr(R)=\asr(R)$ for any principal ideal ring $R$.
+\end{rem}
 

### 2015-09-05 bass-kolster.tex
Edits from 04.09.15 meeting
Iterated BK: the statement formatted into a table

@@
 \begin{cor}\label{cor:bass-kolster-iterated}
-Assume $\sr(I)\leqslant2$ in case $\Phi=\rA_\ell$, $\sr(I)\leqslant3$ in case $\rC_\ell$ and $\asr(I)\leqslant2$ in case $\Phi=\rB_\ell,\rD_\ell$.
-Then every element of $\G(\Phi,R,I)$ is a product of an element of $\G(\langle\pm\alpha_\ell\rangle,R,I)$, at most $\ell-1$ elements of the form $z_{-\alpha}(*,*)$, $\alpha$ the maximal root of some terminal subsystem containing $\alpha_\ell$, and at most $N$ elementary root unipotents $x_\alpha(s)$, $s\in I$, where $N$ is $3\left|\Phi^+\right|+\ell$ in case $\Phi=\rA_\ell$, $N=3\left|\Phi^+\right|+2\ell$ in case $\Phi=\rC_\ell$ and $N=4\left|\Phi^+\right|-\ell$ in case $\Phi=\rB_\ell,\rD_\ell$.
+Let $\Phi$ be a root system, $R$ a commutative ring and $I$ its ideal.
+Then under a suitable stability assumption every element of $\G(\Phi,R,I)$ is a product of an element of $\G(\langle\pm\alpha_\ell\rangle,R,I)\cong\SL(2,R,I)$, at most $\ell-1$ elements of the form $z_{-\alpha}(*,*)$, $\alpha$ the maximal root of some terminal subsystem containing $\alpha_\ell$, and at most $N$ elementary root unipotents $x_\alpha(s)$, $s\in I$.
+The stability assumption and the number $N$ are as follows:
+\[\begin{array}{l@{\quad}l@{\quad}l}
+\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right|+\ell; \\
+\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right|+2\ell; \\
+\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right|-\ell.
+\end{array}\]
 \end{cor}
@@
 \end{proof}
+\begin{figure}[htb]\label{fig:bass-kolster}
 \[
@@
 \]
+\caption{Reductions provided by the Bass---Kolster decomposition}
+\end{figure}
+
 \begin{proof}[Proof of Theorem~\ref{thm:SL2width}]

### 2015-09-05 paper.tex
Minor fixes in the introduction

@@
 \declaretheorem[name=Theorem, Refname={Theorem,Theorems}]{thm}
-\declaretheorem[name=Corollary, Refname={Corollary, Corollaries}, sibling=thm]{cor}
-
-\declaretheorem[name=Lemma, Refname={Lemma,Lemmas}]{lemma}
-\declaretheorem[name=Proposition, Refname={Proposition,Propositions}, sibling=lemma]{prop}
+\declaretheorem[name=Proposition, Refname={Proposition,Propositions}, sibling=thm]{prop}
+\declaretheorem[name=Corollary, Refname={Corollary, Corollaries}, numberwithin=section]{cor}
+\declaretheorem[name=Lemma, Refname={Lemma,Lemmas}, numberwithin=section]{lemma}
 
@@
 \begin{enumerate}
-\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z}(-\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
+\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
 \item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume $\Phi$ is classical. Then under the assumption of the Generalized Riemann Hypothesis one has
@@
 
-It is also classically known that over an arbitrary field $F$ the group $\SL(n+1, F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
+It is also classically known that over an arbitrary field $F$ the group $\SL_{n+1}(F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
 On the other hand, from the classical Dennis---Vaserstein theorem (see~\cite{Va69} and \cite[Lemma~2.1]{ST76})
-it follows that $\SL(n+1, R, I)$ is a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
+it follows that $\SL_{n+1}(R, I)$ is a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
 Using another Dennis---Vaserstein type factorization we obtain the following result.
 \begin{thm}\label{thm:spin-sln-prod}
-Assume that $\sr(I) \leqslant 2$ then the group $\Epin_{2\ell}(R, I)=\E_{sc}(\rD_\ell, R, I)$ is a product of at most $9$ copies of subgroups of type $\rA_{\ell-1}$.
+Assume that $\sr(I) \leqslant 2$ then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ copies of its subgroups of type $\rA_{\ell-1}$.
 \end{thm}

### 2015-09-05 stability-conditions.tex
Some references on large stable ranks

@@
 The following result gives an upper estimate for the absolute stable rank (see~\cite[Theorem~2.3]{EO}, \cite[Theorem~3.7]{MKV}).
-\begin{prop}
+\begin{prop}\label{prop:asr-dimmax}
 Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets 
@@
 \end{rem}
+\cref{prop:asr-dimmax} shows in particular, that every Dedekind domain $R$ satisfies $\asr(R)\leqslant2$, and that $\sr(A)[x]\leqslant3$ for every locally principal ring $A$.
+It is shown in \cite{GruMenVasSL2ZxSL2kxy} that $\sr(\mathbb{Z}[x])=3$.
+Note that $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ if $n>1$ \cite[Example after Theorem~18.2]{VasSusSerreProblem}.
 

### 2015-09-06 paper.tex
Reordering and fixes in sec:elementary

@@
 
+The following result of H.~Matsumoto describes the action of elementary root unipotents in a basic representation of $\G(\Phi, R)$.
+\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
+Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
+One can choose a basis $v^\lambda$, $\lambda\in\Lambda(\pi)$ of $V$ such that the action of the elementary root unipotents $x_\alpha(\xi)$ on it is described by the following formulae:
+
+\begin{tabular}{ll}
+If $\lambda\in\Lambda^*,\ \lambda+\alpha\notin\Lambda$, then & $x_\alpha(\xi)v^\lambda=v^\lambda$; \\
+If $\lambda,\lambda+\alpha\in\Lambda^*$, then & $x_\alpha(\xi)v^\lambda=v^\lambda\pm\xi v^{\lambda+\alpha}$; \\
+If $\alpha\notin\Lambda^*$, then & $x_\alpha(\xi)v^0=v^0$ for any $v^0\in V^0$; \\
+If $\alpha\in\Lambda^*$, then & $x_\alpha(\xi)v^{-\alpha}=v^{-\alpha}\pm\xi v^0(\alpha)\pm\xi^2 v^\alpha$ and \\
+& $x_\alpha(\xi)v^0=v^0\pm\xi\alpha_*(v^0)v^\alpha$.
+\end{tabular}
+% \begin{thmlist}
+%  \item $x_{\alpha}(\xi) v_\lambda = v_\lambda$ for $\lambda\in\Lambda^*(\pi), \lambda+\alpha\not\in\Lambda(\pi)$;
+%  \item $x_\alpha(\xi)v_\lambda=v_\lambda\pm\xi v_{\lambda+\alpha}$ for $\lambda,\lambda+\alpha\in\Lambda^*(\pi)$;
+%  \item $x_\alpha(\xi)v_0 = v_0$ for every $v_0\in V^0$, $\alpha\not\in\Lambda^*(\pi)$;
+%  \item $x_\alpha(\xi)v_{-\alpha}=v_{-\alpha}\pm\xi v_0(\alpha)\pm\xi^2 v_{\alpha}$,\\
+%   $x_\alpha(\xi)v_0 = v_0\pm\xi\alpha_*(v_0)v_\alpha$ for $\alpha\in\Lambda^*(\pi)$.
+% \end{thmlist}
+\end{lemma}
+
+\begin{rem}
+Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
+In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ (for some choice of $\lambda_1,\lambda_2$) instead of $x_{\lambda_1-\lambda_2}(\xi)$.
+For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$. This is done in order to fix the signs in \cref{lemma:Matsumoto}.
+\end{rem}
+For classigal groups there is a standard way to fix the signs.
+In case $\Phi=\rC_\ell$ the long and short root unipotents are
+\begin{align*}
+& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
+& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
+\end{align*}
+Here $\varepsilon_i$ is the sign of $i$.
+In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
+\begin{align*}
+& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
+& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
+\end{align*}
+
 For $\varepsilon\in R^*$ set $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_{\alpha}(\varepsilon).$
@@
 \end{alignat}
-
-\begin{rem}
-Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
-In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
-For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
-\end{rem}
-For other classical root systems the elementary root unipotents are as follows.
-
-In case $\Phi=\rC_\ell$ the long and short root unipotents are
-\begin{align*}
-& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
-& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
-\end{align*}
-
-Here $\varepsilon_i$ is the sign of $i$.
-
-In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
-\begin{align*}
-& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
-& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
-\end{align*}
-
-The following result of H.~Matsumoto describes the action of elementary root unipotents in a basic representation of $\G(\Phi, R)$.
-\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
- Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
- One can choose a basis $v_\lambda$, $\lambda\in\Lambda(\pi)$ of $V$ such that the action of elementary root unipotents $t_\alpha(\xi)$ on it is described by the following formulae:
- \begin{thmlist}
-  \item $t_{\alpha}(\xi) v_\lambda = v_\lambda$ for $\lambda\in\Lambda^*(\pi), \lambda+\alpha\not\in\Lambda(\pi)$;
-  \item $t_\alpha(\xi)v_\lambda=v_\lambda\pm\xi v_{\lambda+\alpha}$ for $\lambda,\lambda+\alpha\in\Lambda^*(\pi)$;
-  \item $t_\alpha(\xi)v_0 = v_0$ for every $v_0\in V^0$, $\alpha\not\in\Lambda^*(\pi)$;
-  \item $t_\alpha(\xi)v_{-\alpha}=v_{-\alpha}\pm\xi v_0(\alpha)\pm\xi^2 v_{\alpha},$ $t_\alpha(\xi)v_0 = v_0\pm\xi\alpha_*(v_0)v_\alpha$ for $\alpha\in\Lambda^*(\pi)$.
- \end{thmlist}
-\end{lemma}
 

### 2015-09-06 stability-conditions.tex
A reference to Krusenmayer and the exactness of stable rank estimates for the polynomial rings

@@
 \end{rem}
-\cref{prop:asr-dimmax} shows in particular, that every Dedekind domain $R$ satisfies $\asr(R)\leqslant2$, and that $\sr(A)[x]\leqslant3$ for every locally principal ring $A$.
+\cref{prop:asr-dimmax} shows in particular, that every Dedekind domain $R$ satisfies $\asr(R)\leqslant2$, and that $\sr(A[x])\leqslant3$ for every locally principal ring $A$.
 It is shown in \cite{GruMenVasSL2ZxSL2kxy} that $\sr(\mathbb{Z}[x])=3$.
 Note that $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ if $n>1$ \cite[Example after Theorem~18.2]{VasSusSerreProblem}.
+
+Another corollary of \cref{prop:asr-dimmax} is an estimate for the stable rank of the polynomial rings over a field.
+Namely, $\sr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$.
+The estimate is known to be not always exact, for example, if $F$ is algebraic over a finite field, then $\sr(F[x_1,\ldots,x_n])\leqslant n$ \cite[Corollary~17.4]{VasSusSerreProblem}.
+However, $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ \cite{KrusenmeyerThesis} and $\sr(F[x_1,\ldots,x_n])=n+1$ if $f\leqslant\mathbb{R}$ \cite{Va71}.
 

### 2015-09-06 dennis-vaserstein.tex
t_\alpha -> x_\alpha

@@
 Specializing identity~\eqref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
-\begin{equation} \label{rel:CCF-specBC} t_{1,0}(ab) = [t_{1, 2}(a), t_{2, 0}(b)] \cdot t_{1,-2}(-a b^2), \quad t_{1,-1}(-ab^2) = t_{-2,1}(ab) \cdot [t_{-2, 2}(a), t_{2, -1}(b)]. \end{equation}
+\begin{align*} \label{rel:CCF-specBC}
+& x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2), \\
+& x_{1,-1}(-ab^2) = x_{-2,1}(ab) \cdot [x_{-2, 2}(a), x_{2, -1}(b)].
+\end{align*}
 Clearly, the root subgroup $X_{2, 0}(R)$ (resp.
@@
 The proof in the case $\Phi=\rB_\ell$ is also similar to the one presented above.
-Indeed, from the identity $t_{0, 1}(-a) = [t_{2,1}(-a); t_{0, 2}(-1)] t_{-2,1}(a)$ we conclude that
+Indeed, from the identity $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
 $$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{t_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}.$$

### 2015-09-06 paper.tex
sigma delta s j

@@
 For a root $\beta = \sum m_i(\beta)\alpha_i \in \Phi$ set $\shape(J, \beta):=\sum\limits_{i\in J} m_i(\beta) \alpha_i$.
-Set $$\Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\},\quad \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha)\in\mathbb{Z}_{\geqslant0}\Phi^\pm \}, \quad S_J^\pm := \Delta_J \sqcup \Sigma_J^\pm.$$
+Set
+\begin{align*}
+& \Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\},\\
+& \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha) \in \mathbb{Z}_{\geqslant0} \Phi^\pm \},\\
+& S_J^\pm := \Delta_J \sqcup \Sigma_J^\pm.
+\end{align*}
 Clearly, $\Delta_J$ is a reductive subset, while $S^\pm_J$ and $\Sigma^\pm_J$ are parabolic and special subsets, respectively.
@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
+We often omit the curly braces in the notations above, so, for example, $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i,j}=\Sigma_{\{i,j\}}$.
 

### 2015-09-06 dennis-vaserstein.tex
Some typography fixes

@@
 \[ \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B. \]
-To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma$ and~\cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
+To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma$ and by~\cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
 \[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I). \]

### 2015-09-06 paper.tex
Some typography fixes

@@
 \documentclass[12pt]{amsart}
-\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, graphicx, mathtools, xfrac, hyperref, tikz-cd, nameref, thmtools}
+\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, nameref, thmtools, hyperref}
 \usepackage[utf8]{inputenc}
@@
 \end{alignat*}
-\item Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type embedded into some global field $k$ having a real embedding. 
-Assume $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
+\item Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type in some global field $k$ having a real embedding. 
+Assume that $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
 \end{enumerate}

### 2015-09-06 subsystem-factorizations.tex
Deleted a false claim in the proof thm:spin-sln-prod
More details on lemma:nikolov-type-dl

@@
 \begin{proof}
-Set $\beta_i = \alpha_{2i-1} + 2\alpha_{2i}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell$, for $i=1,\ldots,\lfloor\ell/2\rfloor$, i.\,e.
-$\beta_i$ form a maximal set of pairwise orthogonal maximal roots in some subsystems of type $\rD_{k}$.
+Set $\beta_i = \alpha_{2i-1} + 2\alpha_{2i}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell$, for $i=1,\ldots,\lfloor\ell/2\rfloor-1$.
+Set $\beta_{\lfloor\ell/2\rfloor}=\alpha_{\ell-2}+\alpha_{\ell-1}+\alpha_\ell$ if $\ell$ is odd, and $\beta_{\lfloor\ell/2\rfloor}=\alpha_\ell$ if $\ell$ is even.
 Denote $B=\{\beta_i\}$, then decompose $\U(\Sigma_\ell)=\U(\Sigma_\ell\setminus B)\cdot\U(B)$.
+In fact, $\U(\Sigma_\ell)$ is abelian.
 
@@
 
-We first note that
+Note that \eqref{rel:CCF} implies
 \[ \bigl[\U(\Delta_2^-),x_{\beta_1}(1)\bigr]=1,\quad \Bigl[\U(\Sigma_2^-\cap\Delta_\ell),\prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
-This implies
+The first follows from the fact that the only root $\alpha$ with $m_2(\alpha)=2$ is $\beta_1$.
+The second holds since a root $\alpha\in(\Sigma_2^-\cap\Delta_\ell)+(B\setminus\{\beta_1\})$ must simultaneously satisfy $m_2(\alpha)=-1$ and $m_\ell(\alpha)=1$, which is impossible.
+
+Since $B\setminus\{\beta_1\}\subset\Sigma_\ell\cap\Delta_2$, this implies
 \[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell)\cdot\U(\Delta_{2,\ell}^-), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell\cap\Delta_2).
 \]
-Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell)$ and decompose it as $u=vw$, $v\in\U(\Sigma_{1,2}^-\cap\Delta_\ell)$, $w\in\U(\Sigma_2^-\cap\Delta_{1,\ell})$, then, using the identity $[ab,c]={}^a[b,c]\cdot[a,c]$, rewrite
+Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell)$ and decompose it as $u=vw$, $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell)$, $w\in\U(\Sigma_2^-\cap\Delta_{1,\ell})$, then, using the identity
+\begin{equation}\label{eq:comm-ab-c}
+[ab,c]={}^a[b,c]\cdot[a,c],
+\end{equation}
+rewrite
 \[ [vw,x_{\beta_1}(1)] = {}^v[w,x_{\beta_1}(1)]\cdot[v,x_{\beta_1}(1)].  \]
-Since $\U(\Sigma_{1,2}^-\cap\Delta_\ell)$ and $\U(\Sigma_2^-\cap\Delta_{1,\ell})$ are abelian, it is easy to see that
-\[ [v,x_{\beta_1}(1)]\in\U(\Sigma_{2,\ell}\cap\Delta_1), \quad [w,x_{\beta_1}(1)]\in\U(\Sigma_{1,\ell}\setminus\{\beta_1\}), \]
-and varying $v$ and $w$ one can obtain any element of $\U(\Sigma_{2,\ell}\cap\Delta_1)$ and $\U(\Sigma_{1,\ell}\setminus\{\beta_1\})$ respectively. By the Levi decomposition
-\[ {}^v\!\U(\Sigma_{1,\ell}\setminus\{\beta_1\}) \equiv \U(\Sigma_{1,\ell}\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2). \]
+Since $\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell)$ and $\U(\Sigma_2^-\cap\Delta_{1,\ell})$ are abelian, it is easy to see that
+\[ [v,x_{\beta_1}(1)]\in\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1), \quad [w,x_{\beta_1}(1)]\in\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}). \]
+Varying $v$ and $w$ one can obtain any element of $\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1)$ and $\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\})$ respectively.
+This is easy to see by using \eqref{eq:comm-ab-c} repeatedly and the fact that $\U(\Sigma_2^-\cap\Delta_\ell)$ commutes with $\U(\Sigma_\ell)$.
+Now by the Levi decomposition
+\[ {}^v\!\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}) \equiv \U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2). \]
 Thus we have shown that
-\[ [\U(\Sigma_2^-)\cdot\U(\Delta_{2,\ell}),y] \equiv \U(\Sigma_{1,\ell}\cup\Sigma_{2,\ell}\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2), \]
+\[ [\U(\Sigma_2^-)\cdot\U(\Delta_{2,\ell}),y] \equiv \U((\Sigma_{1,2}\cap\Sigma_\ell)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2), \]
 and this reduces the problem to the $\rD_{\ell-2}$-subsystem $\Delta_{1,2}$.
@@
 It remains to note that the roots $\pm\beta_i$ lie inside a maximal root subsystem of type $\rA_1+\ldots+\rA_1+\rD_3$.
-All such subsystemrs are conjugate under the action of the Weyl group, so there exist an element $w\in W(\Phi)$ such that $w(\beta_1)=\alpha_1$, $w(\beta_2)=\alpha_3$, $w(\beta_3)=\alpha_5$ and so on, so that all of $w(\beta_i)$ lie in $\Delta_\ell^+$.
+All such subsystems are conjugate under the action of the Weyl group, so there exist an element $w\in W(\Phi)$ such that $w(\beta_1)=\alpha_1$, $w(\beta_2)=\alpha_3$, $w(\beta_3)=\alpha_5$ and so on, so that all of $w(\beta_i)$ lie in $\Delta_\ell^+$.
 \end{proof}
@@
 \end{align*}
-Thus $\G(\rD_\ell,R,I)$ is a product of $9$ subgroups isomorphic to $\G(\rA_{\ell-1},R,I)\cong\SL(\ell,R,I)$ (and conjugated inside $\G(\rD_\ell,R)$).
+Thus $\G(\rD_\ell,R,I)$ is a product of $9$ subgroups isomorphic to $\G(\rA_{\ell-1},R,I)\cong\SL(\ell,R,I)$.
 \end{proof}

### 2015-09-07 dennis-vaserstein.tex
Minor fix

@@
 \end{align*}
-Clearly, the root subgroup $X_{2, 0}(R)$ (resp.
-$X_{-2,2}(R)$) is contained in $\E(\Delta_s, R) \subseteq N_{rs}$ while we already know by the above argument that the subgroups $X_{2, 0}(R)$, $X_{1,-2}(R)$
-(resp. $X_{-2,1}(R)$, $X_{2,-1}(R)$) are contained in $N_{rs}$.
+The root subgroup $X_{2, 0}(R)$ (resp. $X_{-2,2}(R)$) is contained in $\E(\Delta_s, R) \subseteq N_{rs}$.
+On the other hand, by the above argument we know that the subgroup $X_{1,-2}(R)$ (resp. subgroups $X_{-2,1}(R)$, $X_{2,-1}(R)$) are contained in $N_{rs}$.
+Therefore $X_{1,0}(R) \subseteq N_{rs}$ (resp. $X_{1,-1}(R) \subseteq N_{rs}$).
+Thus in all the cases we have $\U(\Sigma_s, R) \subseteq N_{rs}$.
 
@@
 It is obvious that $\EP_r(R, I) \subseteq L_{rs}$.
-From $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$. Indeed, for $g\in\EP_s(R,I)$
+From $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$. Indeed, for $g\in\EP_s(R,I)$ one has
 \[ gA_{rs} \subseteq g {A_{rs}}^g = A_rs g = A_rs. \]
@@
 Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
-The proof in the case $\Phi=\rB_\ell$ is also similar to the one presented above.
-Indeed, from the identity $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
+In the case $\Phi=\rB_\ell$ from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
 $$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{t_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}.$$
+In the case $\Phi=\rC_\ell$ from $x_{}$
+$$X_{-1,1}(I) = X_{-1,1}(I^\indexbox{2}) \cdot X_{-1,1}(2I) \subseteq \cdot $$
 

### 2015-09-07 dennis-vaserstein.tex
Moved symplectic case into a separate lemma

--- 2015-09-06 dennis-vaserstein.tex
@@
 In the case $\Phi\neq \rB_\ell, \rC_\ell$ all roots of $\Sigma^+_s$ have the same $s$-shape and length therefore the needed statement follows from~\cref{item-trans2}.
-In the case $\Phi=\rB_\ell$ (resp. $\Phi=\rC_\ell$) the above argument only shows that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ (resp. $\U(\Sigma_s^{+<}, R) \subseteq N_{rs}$)
-and a separate argument is needed for the root subgroup corresponding to the sole short (resp. long) root of $\Sigma_s^+$.
-
-Specializing identity~\eqref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
-\begin{align*} \label{rel:CCF-specBC}
-& x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2), \\
-& x_{1,-1}(-ab^2) = x_{-2,1}(ab) \cdot [x_{-2, 2}(a), x_{2, -1}(b)].
-\end{align*}
-Clearly, the root subgroup $X_{2, 0}(R)$ (resp.
-$X_{-2,2}(R)$) is contained in $\E(\Delta_s, R) \subseteq N_{rs}$ while we already know by the above argument that the subgroups $X_{2, 0}(R)$, $X_{1,-2}(R)$
-(resp. $X_{-2,1}(R)$, $X_{2,-1}(R)$) are contained in $N_{rs}$.
+In the case $\Phi=\rB_\ell$ the above argument only shows that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ and a separate argument is needed for the root subgroup corresponding to the sole short root of $\Sigma_s^+$.
+Specializing identity~\eqref{rel:CCF} we get:
+\begin{equation*} \label{rel:CCF-specBC} x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2) \end{equation*}
+The root subgroup $X_{2, 0}(R)$ is contained in $\E(\Delta_s, R) \subseteq N_{rs}$.
+On the other hand, by the above argument we know that $X_{1,-2}(R) \subseteq N_{rs}$, therefore $X_{1,0}(R) \subseteq N_{rs}$ and $\U(\Sigma_s, R) \subseteq N_{rs}$.
+The case $\Phi=\rC_\ell$ will be analyzed separately below (see~\cref{lemma:DVcaseCl}).
 
@@
 Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
-The proof in the case $\Phi=\rB_\ell$ is also similar to the one presented above.
-Indeed, from the identity $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
-$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{t_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}.$$
+In the case $\Phi=\rB_\ell$ from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
+$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs},$$
+whence the statement of the theorem follows. \end{proof}
 
-%TODO: finish proof of the theorem
-\end{proof}
+\begin{lemma} \label{lemma:DVcaseCl}
+
+\end{lemma}

### 2015-09-08 dennis-vaserstein.tex
Sketched the proof in the symplectic case

@@
 \begin{lemma} \label{lemma:DVcaseCl}
+Let $\Phi=\rC_\ell$ and let $I$ be any ideal satisfying $\sr(I) \leq \ell-1$. Then $X_{-\alpha_1}(R) \subseteq N_{\ell, 1}$.
+\end{lemma}
+\begin{proof}
+Consider the subset $C \subseteq \EP_1(R, I)$ consisting of matrices such that matrix components $v=(g_{i,2})$, $i=2,\ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
+We are going to show that $C$ satisfies the following properties.
+ \begin{enumerate}
+  \item \label{item-dvc1} For every $g \in \EP_1(R, I)$ there exists $x \in \U(\Sigma_\ell \cap \Delta_1, I)$ such that $xg \in C$.  
+  \item \label{item-dvc2} For every $g \in C$ one can choose $y \in \U(\Sigma_1 \cap \Delta_\ell, I)$ such that $(y g)_{1,2} = 0$.
+ \end{enumerate}
+%TODO: Write proof of these 2 facts.
 
-\end{lemma}
+Now set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot C$.
+Notice that from the first property of $C$ we immediately obtain that $A_{\ell, 1} = A'$.
+Indeed for $g\in \EP_1(R, I)$ we have
+\begin{equation} \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq 
+ \EP_\ell(R, I)x^{-1}  \cdot \U(\Sigma_1^-, I) \cdot xg \subseteq A'. \end{equation}
+
+On the other hand, from the second property of $C$ we obtain for every $g\in C$ that
+\begin{multline*}
+ \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq \EP_\ell(R, I) y^{-1} \cdot \U(\Sigma_\ell^-\cap \Sigma_1^-, I)^{y^{-1}} \cdot y g \subseteq \\
+  \subseteq \EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot y g
+\end{multline*}
+It is clear that $(yg)^{x_{2,1}(\xi)} \in \EP_1(R, I)$ hence
+\begin{equation*} A'^{X_{2,1}(R)} \subseteq (\EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot ?) ^ {X_{2,1}(R)} \subseteq \EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell,1}.
+\end{equation*}
+\end{proof}

### 2015-09-08 stability-conditions.tex
Added symplectic lemma

@@
 \begin{lemma}\label{lemma:asrUnip}
- Let $\Phi=\rD_\ell$ and assume that $\asr(I)\leqslant \ell -1$. 
- Then for any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$
- there exists $g\in\U(\Sigma^+_\ell, I)$ such that $(g \cdot v)_+ \in \Ums(\ell, I)$.
+Then for any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$ there exists $g\in\U(\Sigma^+_\ell, I) \leq \G(\Phi, R, I)$ such that $(g \cdot v)_+ \in \Ums(\ell, I)$ under the following assumptions on $\Phi$ and $I$.
+\begin{thmlist}
+\item \label{item:asrUnipC} $\Phi=\rC_\ell$ and $\sr(I) \leqslant \ell$;
+\item \label{item:asrUnipD} $\Phi=\rD_\ell$ and $\asr(I)\leqslant \ell -1$.
+\end{thmlist}
 \end{lemma}
-\begin{proof} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \subseteq I$.
+\begin{proof} 
+\textsc{Case $\Phi=\rC_\ell$.}
+Set $d =\mathrm{diag}(v_{-\ell},\ldots,v_{-1}).$
+It is easy to see that the column $$v'=(v_1,\ldots,v_\ell, v_{-\ell}^2,\ldots,v_{-1}^2)^t$$ is also $I$-unimodular.
+By the definition of the relative stable rank we can find a matrix $b\in \M(\ell,I)$
+such that the upper half $v''_+$ of the vector $v''= g \cdot v'$, $g=\left(\begin{smallmatrix} e_\ell & b \\ 0 & e_{\ell} \end{smallmatrix}\right)$ is $I$-unimodular.
+It is clear that $v''_+ = v'_+ + b v'_- = v_+ + bd v_-$. Define matrix $a \in M(\ell, I)$ by 
+$$a_{ij} = b_{ij} v_{-j} + b_{ji} v_{-i},\ a_{ii} = b_{ii} v_{-i} - \sum\limits_{j\neq i} b_{ji} v_{-j}. $$
+Direct calculation shows that $v_+ + (bd)v_- = v_+ + av_-$.
+
+%Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are located on the skew-diagonal, i.\,e. $p_{ij}=(\delta_{i, \ell-j+1})$.
+%Notice that if we could choose $b$ to be persymmetric (i.\,e. such that $(pb)^t=pb$) the assertion of the lemma would follow. Indeed, in such a case $g$ would lie in $\U(\Sigma_\ell, I)$.
+%Choose a diagonal matrix $d' \in \M(\ell, R)$ such that $du^- = -(bd)^tu^-$ and set $a = bd + (bd)^t - d'.$
+%Then obviously, $u^++pa\cdot u^-=u^++p(bd)\cdot u^-$, $a=a^t\in \M(n,I)$.
+%Остаётся воспользоваться замечанием~\ref{UnitarySpecialCases} и леммой~\ref{unipAction}.
+
+\textsc{Case $\Phi=\rD_\ell$.} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \subseteq I$.
 By Proposition~\ref{prop:sr_properties} $\sr(I/J) \leqslant \ell-1$, therefore
@@
 $(v''_1, v''_{-\ell},\ldots, v''_{-2})\in\Ums(\ell+1, I)$.
-%$\mathfrak{J}(v''_{-\ell},\ldots, v''_{-2}) = \mathfrak{J}(v'^-)$. Clearly, $v''_1$ is still congruent to $1$ modulo $J$, therefore 
-%$(v''_1, v''_{-\ell},\ldots, v''_{-2})$ is $I$-unimodular. 
 Now, applying the condition $\sr(I) \leqslant \ell-1$ once again we find
@@
 \textsc{Case $\Phi=\rA_\ell$.} From the definition of the relative stable rank it follows that we can find 
-$x= \left(\begin{smallmatrix} e_k & a \\ * & e_{n-k} \end{smallmatrix}\right) \in \U(\Sigma_k^+, I)$ such that 
+$x= \left(\begin{smallmatrix} e_k & a \\ 0 & e_{n-k} \end{smallmatrix}\right) \in \U(\Sigma_k^+, I)$ such that 
 the upper $k$ components of $v'= x \cdot v$ form an $I$-unimodular column. 

### 2015-09-09 congrsubgr-boundgen.tex
Finished symplectic case

@@
 \begin{lemma}\label{lemma:srRI1_width}
-In the assumptions of Lemma~\ref{thm:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
+In the assumptions of~\cref{thm:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
 \end{lemma}
@@
 Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
- (see Lemma~\ref{lemma:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\ref{rel:h-w}), we have a decomposition
+ (see~\cref{lemma:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we have a decomposition
 \[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
@@
 We find ourselves in the situation of Case 1, therefore we can write $g=h_{12}\cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
-Finally, expressing $h=x_{21}\cdot z_{21}\cdot x_{12}$ as in Lemma~\ref{lemma:rel-tor-elementary}, we get that $g=x_{21} \cdot z_{21} \cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
+Finally, expressing $h=x_{21}\cdot z_{21}\cdot x_{12}$ as in~\cref{lemma:rel-tor-elementary}, we get that $g=x_{21} \cdot z_{21} \cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
 \end{proof}
@@
 First of all, notice that $\asr(I) \leq \asr(\mathcal{O}_S) \leq 2$. 
-By Corollary~\ref{cor:bass-kolster-iterated} we can present any element 
+By~\cref{cor:bass-kolster-iterated} we can present any element 
 of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators $\mathcal{Z}(\Sigma_\ell)$ and one element of 
@@
 
-By Lemma~\ref{lemma:Stepanov-ideal} the group $\E\left(\Phi,\mathcal{O}_S,I^2\right)$ is contained in $\E(\Phi,I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
+By~\cref{lemma:Stepanov-ideal} the group $\E\left(\Phi,\mathcal{O}_S,I^2\right)$ is contained in $\E(\Phi,I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
 Notice that under the assumptions of the lemma it is known that $\E(\Phi,I)$ has finite width with respect to $\mathcal{X}$, see~\cite{Tavgen93} or \cite[Theorem~3.3]{TavgenThesis}.
@@
 \end{align*}
-Thus $g_4\cdot x_{21}(*)\in\SL\left(2,\mathcal{O}_S,II^{\indexbox{2}}\right)$ is contained in $\E(\rC_\ell,I)$ by Lemma~\ref{lemma:Stepanov-ideal} and therefore can be expressed as a bounded product of $x_\alpha$.
+Thus $g_4\cdot x_{21}(*)\in\SL\left(2,\mathcal{O}_S,II^{\indexbox{2}}\right)$ is contained in $\E(\rC_\ell,I)$ by~\cref{lemma:Stepanov-ideal} and therefore can be expressed as a bounded product of $x_\alpha$.
 \end{proof}
 
-\begin{proof}[Proof of Theorem~\ref{thm:width}] The first statement of the theorem is contained in Lemma~\ref{lemma:srRI1_width}.
-The second and third statement follow from Lemmas~\ref{lemma:Z1p}--\ref{lemma:width-dedekind}. \end{proof}
+\begin{proof}[Proof of Theorem~\ref{thm:width}] The first statement of the theorem is contained in~\cref{lemma:srRI1_width}.
+The second and third statement follow from~\cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}

### 2015-09-09 dennis-vaserstein.tex
Added symplectic lemma
Finished symplectic case

--- 2015-09-07 dennis-vaserstein.tex
@@
 2. & \rB_\ell,\ \ell\geqslant 2            & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
-3. & \rC_\ell,\ \ell \geqslant 2          & 1    & \ell   & \sr(I) \leqslant \ell-1,\ 2I+I^{\indexbox{2}}=I \\
+3. & \rC_\ell,\ \ell \geqslant 2          & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
 4. & \rD_\ell,\ \ell\geqslant 4           & 1    & \ell   & \sr(I) \leqslant \ell-2 \\ 
@@
 \end{equation*}
-%Consequently, from the second statement of~\cref{lemma:dv_unipotent} it follows that
-%\begin{equation*} \label{rel:linv} X_{-\alpha\ssub{r}}(I) \cdot A \subseteq \U(\Phi^+, I) \cdot X_{-\alpha\ssub{r}}(I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I) = A. \end{equation*}
 Consequently, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we get that:
 \begin{equation*} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A, \end{equation*}
-which implies the assertion of the lemma.
-%Clearly, the assertion of the lemma follows from~\ref{rel:linv}--\ref{rel:ninv}.
-\end{proof}
+which implies the assertion of the lemma. \end{proof}
 
@@
 First of all, notice that by~\cref{lemma:dv-normal} we have that $X_{\alpha_s}(R) \subseteq N_{rs}$.
-In the case $\Phi\neq \rB_\ell, \rC_\ell$ all roots of $\Sigma^+_s$ have the same $s$-shape and length therefore the needed statement follows from~\cref{item-trans2}.
-In the case $\Phi=\rB_\ell$ the above argument only shows that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ and a separate argument is needed for the root subgroup corresponding to the sole short root of $\Sigma_s^+$.
+In cases $\Phi\neq \rB_\ell, \rC_\ell$ all roots of $\Sigma^+_s$ have the same $s$-shape and length therefore the needed statement follows from~\cref{item-trans2}.
+We defer the proof in the case $\Phi=\rC_\ell$ until we prove a separate lemma (see~\cref{lemma:DVcaseCl} below).
+
+In the case $\Phi=\rB_\ell$ the above reasoning only shows that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ and a separate argument is needed for the root subgroup corresponding to the sole short root of $\Sigma_s^+$.
 Specializing identity~\eqref{rel:CCF} we get:
@@
 On the other hand, by the above argument we know that $X_{1,-2}(R) \subseteq N_{rs}$, therefore $X_{1,0}(R) \subseteq N_{rs}$ and $\U(\Sigma_s, R) \subseteq N_{rs}$.
-The case $\Phi=\rC_\ell$ will be analyzed separately below (see~\cref{lemma:DVcaseCl}).
 
@@
 It is obvious that $\EP_r(R, I) \subseteq L_{rs}$.
-From $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$. Indeed, for $g\in\EP_s(R,I)$ one has
-\[ gA_{rs} \subseteq g {A_{rs}}^g = A_rs g = A_rs. \]
+Since $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$.
+Indeed, for $g \in s\EP_s(R,I)$ one has
+\[ g \cdot A_{rs} \subseteq g \cdot {A_{rs}}^g = A_{rs} \cdot g = A_{rs}. \]
 Thus, we are left to prove the inclusion $\U(\Sigma^-_r \cap \Sigma^-_s, I) \subseteq L_{rs}$.
@@
 \begin{lemma} \label{lemma:DVcaseCl}
+For $\Phi=\rC_\ell$ and any ideal $I$ satisfying $\sr(I) \leq \ell-1$ one has $X_{-\alpha_1}(R) \subseteq N_{\ell, 1}$.
+\end{lemma}
+\begin{proof}
+Consider the subset $C \subseteq \EP_1(R, I)$ consisting of matrices such that matrix components $v=(g_{i,2})$, $i=2,\ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
+Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot C$.
 
-\end{lemma}
+By~\cref{item:asrUnipC} (applied to the subgroup $\G(\Delta_1, R, I)$) we find for every $g \in \EP_1(R, I)$ a matrix $x \in \U(\Sigma_\ell \cap \Delta_1, I)$ such that $xg \in C$.  
+Notice that one immediately gets the equality $A_{\ell, 1} = A'$ from this.
+Indeed for $g\in \EP_1(R, I)$ one has
+\begin{equation*} \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq 
+ \EP_\ell(R, I)x^{-1}  \cdot \U(\Sigma_1^-, I) \cdot xg \subseteq A'. \end{equation*}
+
+By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_1 \cap \Delta_\ell, I)$ such that $(y \cdot g)_{1,2} = 0$.
+Consequently, for every $g\in C$ one has
+\begin{multline*}
+ \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq \EP_\ell(R, I) y^{-1} \cdot \U(\Sigma_\ell^-\cap \Sigma_1^-, I)^{y^{-1}} \cdot y g \subseteq \\
+  \subseteq \EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot y g
+\end{multline*}
+Direct calculation using~\cref{lemma:Chevalley-Matsumoto} shows that $(yg)^{x_{2,1}(\xi)} = u h$ for $\xi \in R$, $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$ hence
+\begin{multline*} {A_{\ell,1}}^{X_{-\alpha_1}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_\ell(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\
+ \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell,1} \end{multline*}
+ as claimed.
+\end{proof}
+
+\begin{proof}[End of proof of Theorem~\ref{thm:DennisVaserstein}]
+In the remaining case $\Phi=\rC_\ell$ we conclude from~\cref{lemma:dv-normal,lemma:Stein_reduction,lemma:DVcaseCl} that $X_{\pm \alpha_i}(R) \subseteq N_{\ell,1}$, $1\leq i\leq \ell$.
+Therefore, by~\cref{lemma:weylfacts} we get that $\widetilde{W}(\Phi) \subseteq N_{\ell,1}$ and hence $\mathcal{X} \subseteq L_{\ell,1}$ as required.
+\end{proof}

### 2015-09-09 paper.tex
Finished symplectic case

@@
 %Theorem counters
-\newlist{thmlist}{enumerate}{1}
-\setlist[thmlist]{label=(\roman{thmlisti}), ref=\thethm.(\roman{thmlisti}),noitemsep}
+\newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label=(\roman{thmlisti}), ref=\thethm.(\roman{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
+\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelemma.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
 
-\declaretheorem[name=Theorem, Refname={Theorem,Theorems}]{thm}
-\declaretheorem[name=Proposition, Refname={Proposition,Propositions}, sibling=thm]{prop}
-\declaretheorem[name=Corollary, Refname={Corollary, Corollaries}, numberwithin=section]{cor}
-\declaretheorem[name=Lemma, Refname={Lemma,Lemmas}, numberwithin=section]{lemma}
+\theoremstyle{plain} \declaretheorem[name=Theorem, Refname={Theorem,Theorems}]{thm} \Crefname{thm}{Theorem}{Theorems}
+\numberwithin{equation}{section}
 
-\Crefname{thm}{Theorem}{Theorems}
-\Crefname{lemma}{Lemma}{Lemmas}
-
-\Crefname{cor}{Corollary}{Corollaries}
-\Crefname{prop}{Proposition}{Propositions}
-
-\Crefname{thmlisti}{Lemma}{Lemmas}
-
-\numberwithin{equation}{section}
-\theoremstyle{definition}
-\newtheorem{rem}[equation]{Remark}
-\newtheorem{example}[equation]{Example}
-\newtheorem{dfn}[equation]{Definition}
-\newtheorem{notation}[equation]{Notation}
+\newtheorem{lemma}{Lemma} \numberwithin{lemma}{section} \Crefname{lemma}{Lemma}{Lemmas}
+\newtheorem{cor}[lemma]{Corollary} \Crefname{cor}{Corollary}{Corollaries}
+\newtheorem{prop}[lemma]{Proposition} \Crefname{prop}{Proposition}{Propositions}
+\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
+\theoremstyle{definition} \newtheorem{dfn}[lemma]{Definition} \Crefname{dfn}{Definition}{Definitions}
+\theoremstyle{remark} \newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}
 
@@
 & \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha) \in \mathbb{Z}_{\geqslant0} \Phi^\pm \},\\
-& S_J^\pm := \Delta_J \sqcup \Sigma_J^\pm.
+& S_J^\pm = \Delta_J \sqcup \Sigma_J^\pm.
 \end{align*}
@@
 \begin{lemma} \label{lemma:weylfacts} Let $\Phi$ be an irreducible root system and let $I$ be an ideal of $R$. 
-\begin{thmlist}
+\begin{lemlist}
 \item \label{item-trans1} For every roots $\alpha, \beta \in \Phi$ of the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
@@
 \item \label{item-trans2} Assume that $\alpha_s\in \Pi$ is a simple root of $\Phi$ such that $m_s(\alpha_\mathrm{max}) = 1$. 
-Then for $\alpha, \beta \in \Sigma^\pm_s$ of the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$.
-
-\end{thmlist}
+                          Then for $\alpha, \beta \in \Sigma^\pm_s$ of the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$. \end{lemlist}
 \end{lemma}

### 2015-09-09 stability-conditions.tex
Finished symplectic case

@@
 Then for any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$ there exists $g\in\U(\Sigma^+_\ell, I) \leq \G(\Phi, R, I)$ such that $(g \cdot v)_+ \in \Ums(\ell, I)$ under the following assumptions on $\Phi$ and $I$.
-\begin{thmlist}
+\begin{lemlist}
 \item \label{item:asrUnipC} $\Phi=\rC_\ell$ and $\sr(I) \leqslant \ell$;
 \item \label{item:asrUnipD} $\Phi=\rD_\ell$ and $\asr(I)\leqslant \ell -1$.
-\end{thmlist}
+\end{lemlist}
 \end{lemma}
@@
 \textsc{Case $\Phi=\rC_\ell$.}
+Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are located on the skew-diagonal, i.\,e. $p_{ij}=(\delta_{i, \ell-j+1})$. 
 Set $d =\mathrm{diag}(v_{-\ell},\ldots,v_{-1}).$
-It is easy to see that the column $$v'=(v_1,\ldots,v_\ell, v_{-\ell}^2,\ldots,v_{-1}^2)^t$$ is also $I$-unimodular.
+Notice that the column $$v'=(v_1,\ldots,v_\ell, v_{-\ell}^2,\ldots,v_{-1}^2)^t$$ is also $I$-unimodular.
 By the definition of the relative stable rank we can find a matrix $b\in \M(\ell,I)$
-such that the upper half $v''_+$ of the vector $v''= g \cdot v'$, $g=\left(\begin{smallmatrix} e_\ell & b \\ 0 & e_{\ell} \end{smallmatrix}\right)$ is $I$-unimodular.
-It is clear that $v''_+ = v'_+ + b v'_- = v_+ + bd v_-$. Define matrix $a \in M(\ell, I)$ by 
-$$a_{ij} = b_{ij} v_{-j} + b_{ji} v_{-i},\ a_{ii} = b_{ii} v_{-i} - \sum\limits_{j\neq i} b_{ji} v_{-j}. $$
-Direct calculation shows that $v_+ + (bd)v_- = v_+ + av_-$.
-
-%Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are located on the skew-diagonal, i.\,e. $p_{ij}=(\delta_{i, \ell-j+1})$.
-%Notice that if we could choose $b$ to be persymmetric (i.\,e. such that $(pb)^t=pb$) the assertion of the lemma would follow. Indeed, in such a case $g$ would lie in $\U(\Sigma_\ell, I)$.
-%Choose a diagonal matrix $d' \in \M(\ell, R)$ such that $du^- = -(bd)^tu^-$ and set $a = bd + (bd)^t - d'.$
-%Then obviously, $u^++pa\cdot u^-=u^++p(bd)\cdot u^-$, $a=a^t\in \M(n,I)$.
-%Остаётся воспользоваться замечанием~\ref{UnitarySpecialCases} и леммой~\ref{unipAction}.
+such that the upper half $v''_+$ of the vector $v''= g(b) \cdot v'$, where 
+$g(b)=\left(\begin{smallmatrix} e_\ell & p \cdot b \\ 0 & e_{\ell} \end{smallmatrix}\right)$, is $I$-unimodular.
+It is clear that $v''_+ = v'_+ + pb v'_- = v_+ + pbd v_-$. 
+Define matrix $a \in M(\ell, I)$ by 
+\begin{align*}
+ & a_{ij} = b_{ij} v_{-j} + b_{ji} v_{-i},\ j\neq i,\\
+ & a_{ii} = b_{ii} v_{-i} - \sum\limits_{j=1, j\neq i}^\ell b_{ji} v_{-j}.
+\end{align*}
+It is clear that the matrix $pa$ is persymmetric and that $g(a) \in \U(\Sigma_\ell, I)$. 
+On the other hand, direct calculation shows that $(g(a)\cdot v)_+=v_+ + pav_- = v_+ + pbdv_- = v''_+ \in \Ums(\ell, I)$.
+%$$(av_-)_k = \sum\limits_{i=1,\ i\neq k}^\ell \left( b_{ki} v_{-i} + b_{ik} v_{-k} \right)v_{-i}  +
+%\left(b_{kk}v_{-k} - \sum\limits_{i=1,\ i\neq k}^\ell b_{ik} v_{-i}\right)v_{-k} = \sum\limits_{i=1}^\ell b_{ki} v_{-i}^2 = (bdv_-)_k$$
 

### 2015-09-09 bass-kolster.tex
\ref{} ---> \cref{}

@@
 Indeed, set $g'' = z_{-\alpha\ssub{max}}(-s, 1) \cdot g'$.
-Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}=0$ and the conclusion of the theorem follows from Lemma~\ref{lemma:Chevalley-Matsumoto}.
+Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}=0$ and the conclusion of the theorem follows from~\cref{lemma:Chevalley-Matsumoto}.
 
@@
 \[ v'' = \prod_{i=1}^\ell x_{\ell+1,i}(b_i) \cdot \prod_{i=1}^\ell x_{i,\ell+1}(a_i) \cdot v \]
-satisfies the equalities~\ref{eq1}.
+satisfies the equalities~\eqref{eq1}.
 
@@
 \[ h_2 = x_{-1,1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1,i}(\xi f_i) \in \U(\Sigma_1, I). \]
-Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\ref{eq1}.
-
-%Now we can assume that the first $2\ell-1$ entries of $v$ are unimodular and find $c_1,\ldots,c_{-2}\in I$ such that $c_1v_1+\ldots+c_{-2}v_{-2}=(v_1-1)-v_{-1}$.
-Add $c_{-i}v_i$ to $v_{-1}$, $i=2,\ldots,\ell$:
-%\[ (v_1,v_2\ldots,v_\ell,v_{-\ell},\ldots,v_{-2},v_{-1})^t\longmapsto (v_1,v'_2\ldots,v'_\ell,v_{-\ell},\ldots,v_{-2},v'_{-1})^t. \]
-%Then add $c_iv_i'=c_i(v_1+c_{-i}v_{-i})$, $i=2,\ldots,\ell$ to the last entry:
-%\[ v_1\longmapsto v_1,\quad v'_{-1}\longmapsto v_{-1}+\sum_{i=2}^\ell c_{-i}v_{-i}+\sum_{i=2}^\ell c_i(v_i+c_{-i}v_1)=v''_{-1}. \]
-%Next add $\left(c_1-\sum_{i=2}^\ell c_ic_{-i}\right)v_1$ to $v''_{-1}$ to get $v_1-1$ in position $-1$.
-%Again, as in case of $\rA_n$, apply $z_\gamma(1-v_1,1)$ with $\gamma=-\alpha_\mathrm{max}$, to get $1$ as the first entry and $0$ as the last.
+Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\eqref{eq1}.
 
 \textsc{Case $\Phi=\rD_\ell$, $n= 2\ell$.} 
-By Lemma~\ref{lemma:asrUnip} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of $v'=h_1 \cdot v$ is $I$-unimodular.
+By~\cref{item:asrUnipD} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of $v'=h_1 \cdot v$ is $I$-unimodular.
 Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
@@
 \[ \xi = v''_1-v''_{-2}-1 \in I, \quad h_3 = x_{-2,1}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-2,i}(\xi f_i), \quad v'''=h_3 \cdot v''. \]
-%Clearly, $v'''_{-2}=v'''_1-1$, therefore for $v_4 = z_{-\alpha_{max}}(-v'''_{-2}, 1) \cdot v'''$ one has $v^4_1 = 1$, as required.
-Clearly, $t_{1,2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, $ h_3 \cdot h_2 \in \U(\Phi^-, I)$ and $v'''$ satisfies \ref{eq1}.
+Clearly, $t_{1,2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, $ h_3 \cdot h_2 \in \U(\Phi^-, I)$ and $v'''$ satisfies~\eqref{eq1}.
 
@@
 Now the proof can be finished by repeating the argument for the case $\Phi=\rD_\ell$ (applied to the subset of long roots of $\rB_\ell$).
-%(clearly, the maximal root of $\rD_\ell$ maps to the maximal root of $\rB_\ell$ under the natural embedding $\rD_\ell\subseteq\rB_\ell$). 
 \end{proof}
@@
 \begin{cor}\label{cor:bass-kolster-count}
-In the assumptions and notation of Theorem~\ref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
+In the assumptions and notation of~\cref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
 can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elementary root unipotents $x_\alpha(s)$ of level $I$.
@@
 Cases $\Phi=\rA_\ell, \rC_\ell$ are immediate.
-In the case $\Phi=\rD_\ell$ the proof of Theorem~\ref{thm:BassKolster} implies that
+In the case $\Phi=\rD_\ell$ the proof of~\cref{thm:BassKolster} implies that
 \begin{multline}\nonumber
@@
 The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}
-The Bass---Kolster decomposition can be iterated if the stability assumption allows, with a slight improvement of Corollary~\ref{cor:bass-kolster-count}.
+The Bass---Kolster decomposition can be iterated if the stability assumption allows, with a slight improvement of~\cref{cor:bass-kolster-count}.
 \begin{cor}\label{cor:bass-kolster-iterated}
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:SL2width}]
-A direct application of Corollary~\ref{cor:bass-kolster-iterated}.
+\begin{proof}[Proof of~\cref{thm:SL2width}]
+A direct application of~\cref{cor:bass-kolster-iterated}.
 \end{proof}

### 2015-09-09 dennis-vaserstein.tex
\ref{} ---> \cref{}

@@
 In what follows, $r$ and $s$ are two distinct integers such that $1 \leq r, s \leq \ell$.
-From Levi decomposition~\ref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
+From Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
 \begin{multline*}
@@
 \end{thmlist} \end{lemma}
-\begin{proof} The first two statements easily follow from Chevalley commutator formula~\ref{rel:CCF} while the third one is a formal consequence of the first two. \end{proof}
+\begin{proof} The first two statements easily follow from Chevalley commutator formula~\eqref{rel:CCF} while the third one is a formal consequence of the first two. \end{proof}
 
@@
 The authors of~\cite{PSV98} put the vertex corresponding to the highest weight $\varpi_s$ of $\pi$ in the upper-left corner of the weight diagram.
-Therefore the subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the upper-left connected component of the graph obtained by removing all bonds marked $r$.
+Thus the subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the upper-left connected component of the graph obtained by removing all bonds marked $r$.
 In turn, the set $\Gamma$ corresponds to the vertices of $\Lambda(\pi')$ incident to the removed bonds.
+
+The action of elementary root unipotents $x_\alpha(\xi)$ on $V$ also can be visualized using weight diagrams.
+
 \end{rem}
@@
 $x\in\U(\Delta_r^+, I)$, $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
-This proves the first assumption of Lemma~\ref{lemma:Stein_reduction}, indeed:
+This proves the first assumption of~\cref{lemma:Stein_reduction}, indeed:
 \[ \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B. \]
-To prove the second assumption of Lemma~\ref{lemma:Stein_reduction} notice that by the definition of $\Gamma$ and by~\cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
+To prove the second assumption of~\cref{lemma:Stein_reduction} notice that by the definition of $\Gamma$ and by~\cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
 \[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I). \]
 
-\begin{proof}[Proof of Theorem~\ref{thm:DennisVaserstein}]
+\begin{proof}[Proof of~\cref{thm:DennisVaserstein}]
 By the above discussion we may assume that the assertion of~\cref{lemma:Stein_reduction} holds.
@@
 
-\begin{proof}[End of proof of Theorem~\ref{thm:DennisVaserstein}]
+\begin{proof}[End of the proof of~\cref{thm:DennisVaserstein}]
 In the remaining case $\Phi=\rC_\ell$ we conclude from~\cref{lemma:dv-normal,lemma:Stein_reduction,lemma:DVcaseCl} that $X_{\pm \alpha_i}(R) \subseteq N_{\ell,1}$, $1\leq i\leq \ell$.

### 2015-09-09 paper.tex
\ref{} ---> \cref{}

@@
 For $\varepsilon\in R^*$ set $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_{\alpha}(\varepsilon).$
-If $\rk(\Phi)\geqslant 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
+If $\rk(\Phi)\geqslant 2$ the following relation is a consequence of \eqref{rel:add}--\eqref{rel:CCF}:
 \begin{equation}\label{rel:R3}
@@
 \begin{proof}
-The first statement of the lemma follows from identity~\ref{rel:R3} and the well-known fact that the Weyl group $W(\Phi)$ acts transitively on the set of roots of the same length.
+The first statement of the lemma follows from identity~\eqref{rel:R3} and the well-known fact that the Weyl group $W(\Phi)$ acts transitively on the set of roots of the same length.
 
@@
 In some cases it is known that $\K_1(\Phi, R, I)$ is trivial.
-For example, $\SK_1(\ell+1,R)=\K(\rA_\ell,R)=1$ for any ring of stable rank $1$ (see Section~\ref{sec:stability-conditions}), 
+For example, $\SK_1(\ell+1,R)=\K(\rA_\ell,R)=1$ for any ring of stable rank $1$ (see section~\ref{sec:stability-conditions}), 
 and for other root systems some stronger assumption is required such as $\asr(R)=1$ or being semilocal. 

### 2015-09-09 stability-conditions.tex
\ref{} ---> \cref{}

@@
 For a commutative ring $R$ and an ideal $I \leq R$ the following statements are equivalent:
-\begin{enumerate} \item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable;
+\begin{lemlist} 
+\item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable;
 \item\label{asr-bak-like} For any $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Umd(n+2,I)$ there exist $c_1,\ldots,c_n\in I$ 
  such that $(b+b',a_1+c_1d,\ldots,a_n+c_nd)$ is $I$-unimodular for any $b'\in J$, where $J=I \cdot a_1 + \ldots + I \cdot a_n + I \cdot d\leq I$.
-\end{enumerate} 
+\end{lemlist} 
 \end{lemma}
@@
 
-Obviously, the second statement of Lemma~\ref{lemma:relative-asr-unimod} does not depend on $R$, hence, as suggested by the notation, $\asr(I)$ is independent of $R$.
-As another corollary of Lemma~\ref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$.
+Obviously, the second statement of~\cref{lemma:relative-asr-unimod} does not depend on $R$, hence, as suggested by the notation, $\asr(I)$ is independent of $R$.
+As another corollary of~\cref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$.
 \begin{cor}[A.~Bak, {cf.~\cite[\S~1]{Pl98}}] For a commutative ring $R$ the following statements are equivalent:
@@
 It is clear that $v''_+ = v'_+ + pb v'_- = v_+ + pbd v_-$. 
-Define matrix $a \in M(\ell, I)$ by 
+Consider the matrix $a \in M(\ell, I)$ defined by 
 \begin{align*}
@@
 \textsc{Case $\Phi=\rD_\ell$.} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \subseteq I$.
-By Proposition~\ref{prop:sr_properties} $\sr(I/J) \leqslant \ell-1$, therefore
+By~\cref{prop:sr_properties} $\sr(I/J) \leqslant \ell-1$, therefore
 the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
@@
 Clearly, $(v'_1,v'_{-\ell},\ldots, v'_{-1})$ is $I$-unimodular.
-Applying statement~\ref{asr-bak-like} of Lemma~\ref{lemma:relative-asr-unimod} we find $c_2,\ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}x_{-i, -1}(c_i)\cdot v'$ one has
+Applying~\cref{asr-bak-like} we find $c_2,\ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}x_{-i, -1}(c_i)\cdot v'$ one has
 $(v''_1, v''_{-\ell},\ldots, v''_{-2})\in\Ums(\ell+1, I)$.
@@
 Assume that one of the following conditions holds:
-\begin{itemize}
- \item $\Phi=\rA_\ell$, $\Gamma=\{ k+1, \ldots, \ell+1\} \subset \Lambda(\pi)$ and $\sr(I)\leq k\leq \ell$;
- \item $\Phi=\rD_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(I)\leq \ell-1$. 
-\end{itemize}
+\begin{lemlist}
+ \item \label{item:uractionA} $\Phi=\rA_\ell$, $\Gamma=\{ k+1, \ldots, \ell+1\} \subset \Lambda(\pi)$ and $\sr(I)\leq k\leq \ell$;
+ \item \label{item:uractionD} $\Phi=\rD_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(I)\leq \ell-1$. 
+\end{lemlist}
 Then for $g\in \G(\Phi, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yxg \cdot v^+)_\lambda = 0$ for $\lambda\in \Gamma$.
@@
 
-\textsc{Case $\Phi=\rD_\ell$.} From the proof of Lemma~\ref{lemma:asrUnip} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.
-Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$ hence by Chevalley---Matsumoto lemma there exists $h_2 \in \U(\Phi^-, I)$ such that the element
+\textsc{Case $\Phi=\rD_\ell$.} From the proof of~\cref{item:asrUnipD} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.
+Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$ hence by~\cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
 $g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fixes $v^+$. 

### 2015-09-09 subsystem-factorizations.tex
\ref{} ---> \cref{}

@@
 \end{proof}
-\begin{proof}[Proof of Theorem~\ref{thm:spin-sln-prod}]
-By Theorem~\ref{thm:DennisVaserstein} one has a decomposition
+\begin{proof}[Proof of~\cref{thm:spin-sln-prod}]
+By~\cref{thm:DennisVaserstein} one has a decomposition
 \[ \Spin(2\ell,R,I) = \Par_{\ell-1}\cdot\U_{\ell-1,\ell}^-\cdot\Par_{\ell} = \G(\Delta_{\ell-1})\cdot\U(\Sigma_{\ell-1})\cdot\U(\Sigma_{\ell-1,\ell}^-)\cdot\U(\Sigma_{\ell})\cdot\G(\Delta_\ell). \]
-By Lemma~\ref{lemma:nikolov-type-dl} there exist elements $y_1,y_2,y_3\in\G(\rD_\ell,R)$ and $w_1,w_2,w_3\in\widetilde{W}(\rD_\ell)$ such that
+By~\cref{lemma:nikolov-type-dl} there exist elements $y_1,y_2,y_3\in\G(\rD_\ell,R)$ and $w_1,w_2,w_3\in\widetilde{W}(\rD_\ell)$ such that
 \begin{align*}

### 2015-09-09 dennis-vaserstein.tex
Slightly improved the exposition

@@
 \end{multline*}
-
-\begin{dfn}
 Denote by $A_{rs}$ any of the above equal subsets.
- We call the decomposition of the form $\E(\Phi, R, I) = A_{rs}$ the {\it relative Dennis---Vaserstein} decomposition.
-\end{dfn}
 
@@
 \begin{thm}\label{thm:DennisVaserstein}
-The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition under the following assumptions on $I$.
+The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\,e.
+a decompostion of the form $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
 \[\begin{array}{l@{\qquad}l@{\qquad}c@{\quad}c@{\qquad}l}
@@
 
-Let us construct a set $B$ satisfying the assumptions of \cref{lemma:Stein_reduction} explicitly.
-
-Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
-The type of $\pi$ and the total number of weights in $\Lambda(\pi)$ are listed in Figure~\ref{fig:table}.
-
-Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=\G(\Delta_r, R)$ it becomes reducible.
-Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
-
-Consider the following subset of $\Lambda(\pi')$:
-$$ \Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$$
-
-The type of $\pi'$ and the number of elements in $\Lambda(\pi')$, $\Gamma$ are listed in Figure~\ref{fig:table}.
-
-\begin{rem}
-The sets $\Lambda(\pi')$, $\Gamma$ can be visualized using the technique of {\it weight diagrams} developed in~\cite{PSV98}.
+The next step of the proof is to construct explicitly the set $B$ satisfying the assumptions of \cref{lemma:Stein_reduction}.
+For this purpose we are going to use the technique of {\it weight diagrams} developed in~\cite{PSV98}.
 In the simplest case of a microweight representation (i.\,e. a representation without zero weights)
@@
 
-The authors of~\cite{PSV98} put the vertex corresponding to the highest weight $\varpi_s$ of $\pi$ in the upper-left corner of the weight diagram.
-Thus the subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the upper-left connected component of the graph obtained by removing all bonds marked $r$.
-In turn, the set $\Gamma$ corresponds to the vertices of $\Lambda(\pi')$ incident to the removed bonds.
+Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
+Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=\G(\Delta_r, R)$ it becomes reducible.
+Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
+Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
 
-The action of elementary root unipotents $x_\alpha(\xi)$ on $V$ also can be visualized using weight diagrams.
+Using the language of weight diagrams subsets $\Lambda(\pi')$, $\Gamma$ can be visualized as follows.
+After removing all bonds marked $r$ the diagram of $\pi$ splits into several connected components.
+The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component containg the vertex $\varpi_s$.
+In turn, the set $\Gamma$ corresponds to vertices of $\Lambda(\pi')$ incident to any of the removed bonds.
+%Calculating with weight diagrams we get the number of weights in $\Lambda(\pi')$ and $\Gamma$ (see~Figure~\ref{fig:table}).
 
-\end{rem}
+Notice that $\Delta_s$ has type either $\rD_\ell$ (in the case $\Phi=\rE_\ell$, $(r,s)=(2,\ell)$) or $\rA_\ell$ (otherwise).
+The number of elements in $\Lambda(\pi')$, $\Gamma$ are listed in Figure~\ref{fig:table}.
+Clearly, in all cases $\pi'$ is the natural representation of $\G(\Delta_s, R)$.
+
+Another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in~\cref{lemma:Matsumoto}.
+Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
+for every bond of the diagram joining vertices $\lambda$ and $\lambda + \alpha$ the element $x_{\alpha}(\xi)$ adds $\pm \xi \cdot v_\lambda$ to $v_{\lambda+\alpha}$.
+See~\cite[Section~3.4]{PSV98} for more detailed description.
 
@@
 \[\begin{array}{l @{\qquad} l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} l @{\qquad} l}
-   & \Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\pi'$}        & (|\Lambda(\pi')|, |\Gamma|)  \\ \hline\vphantom{\Bigl(}
-1. & \rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & (\rA_{l-1}, \varpi_1)        & (\ell,1)  \\     
-2. & \rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & (\rA_{l-1}, \varpi_1)        & (\ell,1) \\     
-3. & \rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & (\rA_{l-1}, \varpi_1)        & (\ell,1)  \\
-4. & \rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & (\rA_{l-1}, \varpi_1)        & (\ell,2)  \\ 
-5. & \rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & (\rA_{l-1}, \varpi_{\ell-1}) & (\ell,\ell-2)  \\
-6. & \rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & (\rA_{l-1}, \varpi_1)        & (\ell,3)  \\ 
-7. & \rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & (\rD_{l-1}, \varpi_1)        & (2\ell-2,\ell-1)  \end{array}\]
+   & \Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
+1. & \rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \ell           & 1  \\     
+2. & \rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \ell           & 1  \\     
+3. & \rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 1  \\
+4. & \rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 2  \\ 
+5. & \rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \ell           & \ell-2  \\
+6. & \rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \ell           & 3       \\ 
+7. & \rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & 2(\ell-1)      & \ell-1  \end{array}\]
  \caption[Table]{List of representation involved in the proof of~\cref{thm:DennisVaserstein}.} \label{fig:table}
@@
 First of all, notice that by~\cref{lemma:dv-normal} we have that $X_{\alpha_s}(R) \subseteq N_{rs}$.
-In cases $\Phi\neq \rB_\ell, \rC_\ell$ all roots of $\Sigma^+_s$ have the same $s$-shape and length therefore the needed statement follows from~\cref{item-trans2}.
-We defer the proof in the case $\Phi=\rC_\ell$ until we prove a separate lemma (see~\cref{lemma:DVcaseCl} below).
+For $\Phi\neq \rB_\ell, \rC_\ell$ all roots of $\Sigma^+_s$ have the same $s$-shape and length hence the assertion follows from~\cref{item-trans2}.
 
@@
 On the other hand, by the above argument we know that $X_{1,-2}(R) \subseteq N_{rs}$, therefore $X_{1,0}(R) \subseteq N_{rs}$ and $\U(\Sigma_s, R) \subseteq N_{rs}$.
+
+We defer the proof in the case $\Phi=\rC_\ell$ until we prove~\cref{lemma:DVcaseCl} below.
 

### 2015-09-09 paper.tex
Slightly improved the exposition

@@
 \section{Introduction}\label{sec:intro}
-Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system with a fixed basis of simple roots $\Pi$.
+Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots $\Pi=\{\alpha_1,\ldots, \alpha_\ell\}$ numbered as in Bourbaki's book~\cite{Bou}.
 Denote by $G=\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over $R$ and by $\E(\Phi, R)$ its \emph{elementary subgroup}, 
@@
 By a parabolic factorization we mean a decomposition of $G$ into a product of several parabolic and unipotent subgroups.
-To be more specific, we study relative versions of the following three kinds of decompositions:
+To be more specific, we study relative analogues of the following three kinds of decompositions:
 \begin{itemize}
@@
 \end{tabular}
-% \begin{thmlist}
-%  \item $x_{\alpha}(\xi) v_\lambda = v_\lambda$ for $\lambda\in\Lambda^*(\pi), \lambda+\alpha\not\in\Lambda(\pi)$;
-%  \item $x_\alpha(\xi)v_\lambda=v_\lambda\pm\xi v_{\lambda+\alpha}$ for $\lambda,\lambda+\alpha\in\Lambda^*(\pi)$;
-%  \item $x_\alpha(\xi)v_0 = v_0$ for every $v_0\in V^0$, $\alpha\not\in\Lambda^*(\pi)$;
-%  \item $x_\alpha(\xi)v_{-\alpha}=v_{-\alpha}\pm\xi v_0(\alpha)\pm\xi^2 v_{\alpha}$,\\
-%   $x_\alpha(\xi)v_0 = v_0\pm\xi\alpha_*(v_0)v_\alpha$ for $\alpha\in\Lambda^*(\pi)$.
-% \end{thmlist}
 \end{lemma}

### 2015-09-09 dennis-vaserstein.tex
Yet another improvement in the exposition

@@
 a decompostion of the form $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
-\[\begin{array}{l@{\qquad}l@{\qquad}c@{\quad}c@{\qquad}l}
-   & \Phi                                 & s    & r      & \text{ring condition} \\ \hline\vphantom{\Bigl(}
-1. & \rA_\ell,\ \ell\geqslant 2            & 1    & \ell   & \sr(I) \leqslant \ell-1 \\    
-2. & \rB_\ell,\ \ell\geqslant 2            & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
-3. & \rC_\ell,\ \ell \geqslant 2          & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
-4. & \rD_\ell,\ \ell\geqslant 4           & 1    & \ell   & \sr(I) \leqslant \ell-2 \\ 
-5. & \rD_\ell,\ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2      \\
-6. & \rE_\ell,\ \ell=6,7                  & \ell & 2      & \sr(I) \leqslant \ell-3 \\ 
-7. & \rE_\ell,\ \ell=6,7                  & \ell & 1      & \asr(I)\leqslant \ell-2 \end{array}\]
+\[\begin{array}{l@{\qquad}c@{\quad}c@{\qquad}l}
+\Phi                                 & s    & r      & \text{ring condition} \\ \hline\vphantom{\Bigl(}
+\rA_\ell,\ \ell\geqslant 2            & 1    & \ell   & \sr(I) \leqslant \ell-1 \\    
+\rB_\ell,\ \ell\geqslant 2            & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
+\rC_\ell,\ \ell \geqslant 2          & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
+\rD_\ell,\ \ell\geqslant 4           & 1    & \ell   & \sr(I) \leqslant \ell-2 \\ 
+\rD_\ell,\ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2      \\
+\rE_\ell,\ \ell=6,7                  & \ell & 2      & \sr(I) \leqslant \ell-3 \\ 
+\rE_\ell,\ \ell=6,7                  & \ell & 1      & \asr(I)\leqslant \ell-2 \end{array}\]
 \end{thm}
@@
 In turn, the set $\Gamma$ corresponds to vertices of $\Lambda(\pi')$ incident to any of the removed bonds.
-%Calculating with weight diagrams we get the number of weights in $\Lambda(\pi')$ and $\Gamma$ (see~Figure~\ref{fig:table}).
 
 Notice that $\Delta_s$ has type either $\rD_\ell$ (in the case $\Phi=\rE_\ell$, $(r,s)=(2,\ell)$) or $\rA_\ell$ (otherwise).
-The number of elements in $\Lambda(\pi')$, $\Gamma$ are listed in Figure~\ref{fig:table}.
-Clearly, in all cases $\pi'$ is the natural representation of $\G(\Delta_s, R)$.
+From a consideration of weight diagrams we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Figure~\ref{fig:table}).
+It is clear that in all cases $\pi'$ is the natural representation of $\G(\Delta_s, R)$.
 
-Another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in~\cref{lemma:Matsumoto}.
+Yet another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in~\cref{lemma:Matsumoto}.
 Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
@@
 \begin{figure}
-\[\begin{array}{l @{\qquad} l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} l @{\qquad} l}
-   & \Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
-1. & \rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \ell           & 1  \\     
-2. & \rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \ell           & 1  \\     
-3. & \rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 1  \\
-4. & \rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 2  \\ 
-5. & \rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \ell           & \ell-2  \\
-6. & \rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \ell           & 3       \\ 
-7. & \rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & 2(\ell-1)      & \ell-1  \end{array}\]
+\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} l @{\qquad} l}
+\Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
+\rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \ell           & 1  \\     
+\rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \ell           & 1  \\     
+\rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 1  \\
+\rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 2  \\ 
+\rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \ell           & \ell-2  \\
+\rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \ell           & 3       \\ 
+\rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & 2(\ell-1)      & \ell-1  \end{array}\]
  \caption[Table]{List of representation involved in the proof of~\cref{thm:DennisVaserstein}.} \label{fig:table}
@@
 From~\cref{lemma:dv-normal} and \cref{lemma:Stein_reduction} it follows that $X_\alpha(R) \subseteq N_{rs}$ for $\alpha \in \Pi' \cup -\Pi'$.
-Since $\Delta_s$ is irreducible in all the cases under consideration we get from~\cref{item-egen} that $\E(\Delta_s, R) \subseteq N_{rs}$.
+Since $\Delta_s$ is irreducible we get from~\cref{item-egen} that $\E(\Delta_s, R) \subseteq N_{rs}$.
 
 Our next step is to show that $\U(\Sigma_s, R) \subseteq N_{rs}$.
-First of all, notice that by~\cref{lemma:dv-normal} we have that $X_{\alpha_s}(R) \subseteq N_{rs}$.
-For $\Phi\neq \rB_\ell, \rC_\ell$ all roots of $\Sigma^+_s$ have the same $s$-shape and length hence the assertion follows from~\cref{item-trans2}.
+First of all, notice that by~\cref{lemma:dv-normal} we have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
+In all cases under consideration except $\Phi=\rC_\ell$ we have $m_s(\alpha_{\mathrm{max}})=1$.
+Therefore, for $\Phi\neq \rB_\ell, \rC_\ell$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from~\cref{item-trans2}.
 
-In the case $\Phi=\rB_\ell$ the above reasoning only shows that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ and a separate argument is needed for the root subgroup corresponding to the sole short root of $\Sigma_s^+$.
+In the case $\Phi=\rB_\ell$ the above argument only proves that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ and a separate treatment is needed for the sole root subgroup $X_{1,0}(R)$ corresponding to the short root of $\Sigma_s^+$.
 Specializing identity~\eqref{rel:CCF} we get:
 \begin{equation*} \label{rel:CCF-specBC} x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2) \end{equation*}
-The root subgroup $X_{2, 0}(R)$ is contained in $\E(\Delta_s, R) \subseteq N_{rs}$.
-On the other hand, by the above argument we know that $X_{1,-2}(R) \subseteq N_{rs}$, therefore $X_{1,0}(R) \subseteq N_{rs}$ and $\U(\Sigma_s, R) \subseteq N_{rs}$.
+We already know that $X_{2, 0}(R)$ and $X_{1,-2}(R)$ are contained in $\E(\Delta_s, R) \subseteq N_{rs}$ hence $X_{1,0}(R) \subseteq N_{rs}$, as claimed.
 
@@
 By~\cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
-In fact, in view of formula~\eqref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
-It is obvious that $\EP_r(R, I) \subseteq L_{rs}$.
-Since $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$.
-Indeed, for $g \in s\EP_s(R,I)$ one has
+In view of formula~\eqref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
+It is clear that $\EP_r(R, I) \subseteq L_{rs}$.
+Since $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$, indeed, for $g \in \EP_s(R,I)$ one has
 \[ g \cdot A_{rs} \subseteq g \cdot {A_{rs}}^g = A_{rs} \cdot g = A_{rs}. \]

### 2015-09-09 dennis-vaserstein.tex
Minor

@@
 \[ \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B. \]
-To prove the second assumption of~\cref{lemma:Stein_reduction} notice that by the definition of $\Gamma$ and by~\cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
+To prove the second assumption of~\cref{lemma:Stein_reduction} notice that by~\cref{lemma:Matsumoto} and the definition of $\Gamma$ for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
 \[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I). \]

### 2015-09-10 bass-kolster.tex
Minor changes

@@
 Indeed, set $g'' = z_{-\alpha\ssub{max}}(-s, 1) \cdot g'$.
-Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}=0$ and the conclusion of the theorem follows from~\cref{lemma:Chevalley-Matsumoto}.
+Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}=0$ and the conclusion of the theorem follows from \cref{lemma:Chevalley-Matsumoto}.
 
@@
 \textsc{Case $\Phi=\rD_\ell$, $n= 2\ell$.} 
-By~\cref{item:asrUnipD} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of $v'=h_1 \cdot v$ is $I$-unimodular.
+By \cref{item:asrUnipD} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of $v'=h_1 \cdot v$ is $I$-unimodular.
 Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
@@
 \begin{cor}\label{cor:bass-kolster-count}
-In the assumptions and notation of~\cref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
+In the assumptions and notation of \cref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
 can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elementary root unipotents $x_\alpha(s)$ of level $I$.
@@
 Cases $\Phi=\rA_\ell, \rC_\ell$ are immediate.
-In the case $\Phi=\rD_\ell$ the proof of~\cref{thm:BassKolster} implies that
+In the case $\Phi=\rD_\ell$ the proof of \cref{thm:BassKolster} implies that
 \begin{multline}\nonumber
@@
 The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}
-The Bass---Kolster decomposition can be iterated if the stability assumption allows, with a slight improvement of~\cref{cor:bass-kolster-count}.
+The Bass---Kolster decomposition can be iterated if the stability assumption allows, with a slight improvement of \cref{cor:bass-kolster-count}.
 \begin{cor}\label{cor:bass-kolster-iterated}
@@
 
-\begin{proof}[Proof of~\cref{thm:SL2width}]
-A direct application of~\cref{cor:bass-kolster-iterated}.
+\begin{proof}[Proof of \cref{thm:SL2width}]
+A direct application of \cref{cor:bass-kolster-iterated}.
 \end{proof}

### 2015-09-10 congrsubgr-boundgen.tex
\ref{} ---> \cref{}
Minor changes

@@
 \begin{lemma}\label{lemma:srRI1_width}
-In the assumptions of~\cref{thm:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
+In the assumptions of \cref{thm:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
 \end{lemma}
@@
 Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
- (see~\cref{lemma:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we have a decomposition
+ (see \cref{lemma:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we have a decomposition
 \[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
@@
 We find ourselves in the situation of Case 1, therefore we can write $g=h_{12}\cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
-Finally, expressing $h=x_{21}\cdot z_{21}\cdot x_{12}$ as in~\cref{lemma:rel-tor-elementary}, we get that $g=x_{21} \cdot z_{21} \cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
+Finally, expressing $h=x_{21}\cdot z_{21}\cdot x_{12}$ as in \cref{lemma:rel-tor-elementary}, we get that $g=x_{21} \cdot z_{21} \cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
 \end{proof}
@@
 First of all, notice that $\asr(I) \leq \asr(\mathcal{O}_S) \leq 2$. 
-By~\cref{cor:bass-kolster-iterated} we can present any element 
+By \cref{cor:bass-kolster-iterated} we can present any element 
 of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators $\mathcal{Z}(\Sigma_\ell)$ and one element of 
@@
 
-By~\cref{lemma:Stepanov-ideal} the group $\E\left(\Phi,\mathcal{O}_S,I^2\right)$ is contained in $\E(\Phi,I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
+By \cref{lemma:Stepanov-ideal} the group $\E\left(\Phi,\mathcal{O}_S,I^2\right)$ is contained in $\E(\Phi,I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
 Notice that under the assumptions of the lemma it is known that $\E(\Phi,I)$ has finite width with respect to $\mathcal{X}$, see~\cite{Tavgen93} or \cite[Theorem~3.3]{TavgenThesis}.
@@
 \end{align*}
-Thus $g_4\cdot x_{21}(*)\in\SL\left(2,\mathcal{O}_S,II^{\indexbox{2}}\right)$ is contained in $\E(\rC_\ell,I)$ by~\cref{lemma:Stepanov-ideal} and therefore can be expressed as a bounded product of $x_\alpha$.
+Thus $g_4\cdot x_{21}(*)\in\SL\left(2,\mathcal{O}_S,II^{\indexbox{2}}\right)$ is contained in $\E(\rC_\ell,I)$ by \cref{lemma:Stepanov-ideal} and therefore can be expressed as a bounded product of $x_\alpha$.
 \end{proof}
 
-\begin{proof}[Proof of Theorem~\ref{thm:width}] The first statement of the theorem is contained in~\cref{lemma:srRI1_width}.
-The second and third statement follow from~\cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}
+\begin{proof}[Proof of \cref{thm:width}] The first statement of the theorem is contained in \cref{lemma:srRI1_width}.
+The second and third statement follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}

### 2015-09-10 dennis-vaserstein.tex
Minor changes

@@
 \end{multline*}
-Together with the third statement of~\cref{lemma:dv_unipotent} this implies that
+Together with the third statement of \cref{lemma:dv_unipotent} this implies that
 \begin{equation*} \label{rel:sred}
@@
 
-Yet another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in~\cref{lemma:Matsumoto}.
+Yet another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in \cref{lemma:Matsumoto}.
 Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
@@
 \rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & 2(\ell-1)      & \ell-1  \end{array}\]
- \caption[Table]{List of representation involved in the proof of~\cref{thm:DennisVaserstein}.} \label{fig:table}
+ \caption[Table]{List of representation involved in the proof of \cref{thm:DennisVaserstein}.} \label{fig:table}
 \end{figure}
@@
 Now let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
-Applying~\cref{lemma:uraction} to the subsystem $\Delta_r$ we find
+Applying \cref{lemma:uraction} to the subsystem $\Delta_r$ we find
 $x\in\U(\Delta_r^+, I)$, $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
-This proves the first assumption of~\cref{lemma:Stein_reduction}, indeed:
+This proves the first assumption of \cref{lemma:Stein_reduction}, indeed:
 \[ \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B. \]
-To prove the second assumption of~\cref{lemma:Stein_reduction} notice that by~\cref{lemma:Matsumoto} and the definition of $\Gamma$ for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
+To prove the second assumption of \cref{lemma:Stein_reduction} notice that by \cref{lemma:Matsumoto} and the definition of $\Gamma$ for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
 \[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I). \]
 
-\begin{proof}[Proof of~\cref{thm:DennisVaserstein}]
-By the above discussion we may assume that the assertion of~\cref{lemma:Stein_reduction} holds.
+\begin{proof}[Proof of \cref{thm:DennisVaserstein}]
+By the above discussion we may assume that the assertion of \cref{lemma:Stein_reduction} holds.
 Set $\Pi' = \Pi \setminus \{\alpha_s\}$.
-From~\cref{lemma:dv-normal} and \cref{lemma:Stein_reduction} it follows that $X_\alpha(R) \subseteq N_{rs}$ for $\alpha \in \Pi' \cup -\Pi'$.
-Since $\Delta_s$ is irreducible we get from~\cref{item-egen} that $\E(\Delta_s, R) \subseteq N_{rs}$.
+From \cref{lemma:dv-normal} and \cref{lemma:Stein_reduction} it follows that $X_\alpha(R) \subseteq N_{rs}$ for $\alpha \in \Pi' \cup -\Pi'$.
+Since $\Delta_s$ is irreducible we get from \cref{item-egen} that $\E(\Delta_s, R) \subseteq N_{rs}$.
 
 Our next step is to show that $\U(\Sigma_s, R) \subseteq N_{rs}$.
-First of all, notice that by~\cref{lemma:dv-normal} we have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
+First of all, notice that by \cref{lemma:dv-normal} we have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
 In all cases under consideration except $\Phi=\rC_\ell$ we have $m_s(\alpha_{\mathrm{max}})=1$.
-Therefore, for $\Phi\neq \rB_\ell, \rC_\ell$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from~\cref{item-trans2}.
+Therefore, for $\Phi\neq \rB_\ell, \rC_\ell$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from \cref{item-trans2}.
 
@@
 
-We defer the proof in the case $\Phi=\rC_\ell$ until we prove~\cref{lemma:DVcaseCl} below.
+We defer the proof in the case $\Phi=\rC_\ell$ until we prove \cref{lemma:DVcaseCl} below.
 
 Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. 
-By~\cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
+By \cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
 In view of formula~\eqref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
@@
 
-Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
+Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from \cref{item-trans2}.
 In the case $\Phi=\rB_\ell$ from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
@@
 
-By~\cref{item:asrUnipC} (applied to the subgroup $\G(\Delta_1, R, I)$) we find for every $g \in \EP_1(R, I)$ a matrix $x \in \U(\Sigma_\ell \cap \Delta_1, I)$ such that $xg \in C$.  
+By \cref{item:asrUnipC} (applied to the subgroup $\G(\Delta_1, R, I)$) we find for every $g \in \EP_1(R, I)$ a matrix $x \in \U(\Sigma_\ell \cap \Delta_1, I)$ such that $xg \in C$.  
 Notice that one immediately gets the equality $A_{\ell, 1} = A'$ from this.
@@
 \end{multline*}
-Direct calculation using~\cref{lemma:Chevalley-Matsumoto} shows that $(yg)^{x_{2,1}(\xi)} = u h$ for $\xi \in R$, $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$ hence
+Direct calculation using \cref{lemma:Chevalley-Matsumoto} shows that $(yg)^{x_{2,1}(\xi)} = u h$ for $\xi \in R$, $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$ hence
 \begin{multline*} {A_{\ell,1}}^{X_{-\alpha_1}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_\ell(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\
@@
 
-\begin{proof}[End of the proof of~\cref{thm:DennisVaserstein}]
-In the remaining case $\Phi=\rC_\ell$ we conclude from~\cref{lemma:dv-normal,lemma:Stein_reduction,lemma:DVcaseCl} that $X_{\pm \alpha_i}(R) \subseteq N_{\ell,1}$, $1\leq i\leq \ell$.
-Therefore, by~\cref{lemma:weylfacts} we get that $\widetilde{W}(\Phi) \subseteq N_{\ell,1}$ and hence $\mathcal{X} \subseteq L_{\ell,1}$ as required.
+\begin{proof}[End of the proof of \cref{thm:DennisVaserstein}]
+In the remaining case $\Phi=\rC_\ell$ we conclude from \cref{lemma:dv-normal,lemma:Stein_reduction,lemma:DVcaseCl} that $X_{\pm \alpha_i}(R) \subseteq N_{\ell,1}$, $1\leq i\leq \ell$.
+Therefore, by \cref{lemma:weylfacts} we get that $\widetilde{W}(\Phi) \subseteq N_{\ell,1}$ and hence $\mathcal{X} \subseteq L_{\ell,1}$ as required.
 \end{proof}

### 2015-09-10 paper.tex
Minor
Examples styled as remarks
Minor changes

@@
 
-%Theorem counters
 \newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label=(\roman{thmlisti}), ref=\thethm.(\roman{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
@@
 \newtheorem{prop}[lemma]{Proposition} \Crefname{prop}{Proposition}{Propositions}
-\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
-\theoremstyle{definition} \newtheorem{dfn}[lemma]{Definition} \Crefname{dfn}{Definition}{Definitions}
-\theoremstyle{remark} \newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}
-
 \newtheorem*{thm*}{Theorem}
 \newtheorem*{lemma*}{Lemma}
+\theoremstyle{definition} \newtheorem{dfn}[lemma]{Definition} \Crefname{dfn}{Definition}{Definitions}
+\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
+\theoremstyle{remark} \newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}
 
@@
 
-On the other hand, much less is known about the width of the relative group $\G(\Phi, R, I)$. 
+On the other hand, much less is known about the width of the relative group $\G(\Phi, R, I)$ and the relative elementary group $\E(\Phi, R, I)$.
+Recall that the \emph{relative elementary group} $\E(\Phi, R, I)$ is defined as the normal closure of $\E(\Phi, I)$ in $\E(\Phi, R)$, where
+$\E(\Phi, I)$ denotes the subgroup of $\G_{sc}(\Phi, R)$ generated by all elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$, i.\,e. $\E(\Phi, R, I) = \E(\Phi, I)^{\E(\Phi, R)}$.
+
 Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
@@
 
-The same argument combined with~\cref{lemma:abs} also proves the third statement. Indeed, by our assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.
+The same argument combined with \cref{lemma:abs} also proves the third statement. Indeed, by our assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.
 
@@
 \subsection{Relative Chevalley groups}\label{sec:relative-elementary}
-Let $I\leq R$ be an ideal. Denote by $\E(\Phi, I)$ the subgroup of $\G_{sc}(\Phi, R)$ generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$.
-
-We denote by $\E(\Phi, R, I)$ the normal closure of $\E(\Phi, I)$ in $\E(\Phi, R)$, in other words $\E(\Phi, R, I) = \E(\Phi, I)^{\E(\Phi, R)}$.
 Recall from the introduction that the elements $z_\alpha(s, \xi) = x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$ generate $\E(\Phi, R, I)$ as an abstract group.

### 2015-09-10 stability-conditions.tex
Minor changes

@@
 
-Obviously, the second statement of~\cref{lemma:relative-asr-unimod} does not depend on $R$, hence, as suggested by the notation, $\asr(I)$ is independent of $R$.
-As another corollary of~\cref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$.
+Obviously, the second statement of \cref{lemma:relative-asr-unimod} does not depend on $R$, hence, as suggested by the notation, $\asr(I)$ is independent of $R$.
+As another corollary of \cref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$.
 \begin{cor}[A.~Bak, {cf.~\cite[\S~1]{Pl98}}] For a commutative ring $R$ the following statements are equivalent:
@@
 Namely, $\sr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$.
-The estimate is known to be not always exact, for example, if $F$ is algebraic over a finite field, then $\sr(F[x_1,\ldots,x_n])\leqslant n$ \cite[Corollary~17.4]{VasSusSerreProblem}.
-However, $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ \cite{KrusenmeyerThesis} and $\sr(F[x_1,\ldots,x_n])=n+1$ if $f\leqslant\mathbb{R}$ \cite{Va71}.
+For certain classes of fields this upper estimate can be further improved.
+For example, if $F$ is algebraic over a finite field then $\sr(F[x_1,\ldots,x_n])\leqslant n$ by~\cite[Corollary~17.4]{VasSusSerreProblem}.
+On the other hand, it is known that $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ \cite{KrusenmeyerThesis} and $\sr(F[x_1,\ldots,x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
 
@@
 \textsc{Case $\Phi=\rD_\ell$.} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \subseteq I$.
-By~\cref{prop:sr_properties} $\sr(I/J) \leqslant \ell-1$, therefore
+By \cref{prop:sr_properties} $\sr(I/J) \leqslant \ell-1$, therefore
 the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
@@
 Clearly, $(v'_1,v'_{-\ell},\ldots, v'_{-1})$ is $I$-unimodular.
-Applying~\cref{asr-bak-like} we find $c_2,\ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}x_{-i, -1}(c_i)\cdot v'$ one has
+Applying \cref{asr-bak-like} we find $c_2,\ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}x_{-i, -1}(c_i)\cdot v'$ one has
 $(v''_1, v''_{-\ell},\ldots, v''_{-2})\in\Ums(\ell+1, I)$.
@@
 
-\textsc{Case $\Phi=\rD_\ell$.} From the proof of~\cref{item:asrUnipD} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.
-Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$ hence by~\cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
+\textsc{Case $\Phi=\rD_\ell$.} From the proof of \cref{item:asrUnipD} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.
+Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$ hence by \cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
 $g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fixes $v^+$. 

### 2015-09-10 subsystem-factorizations.tex
Minor changes

@@
 \end{proof}
-\begin{proof}[Proof of~\cref{thm:spin-sln-prod}]
-By~\cref{thm:DennisVaserstein} one has a decomposition
+\begin{proof}[Proof of \cref{thm:spin-sln-prod}]
+By \cref{thm:DennisVaserstein} one has a decomposition
 \[ \Spin(2\ell,R,I) = \Par_{\ell-1}\cdot\U_{\ell-1,\ell}^-\cdot\Par_{\ell} = \G(\Delta_{\ell-1})\cdot\U(\Sigma_{\ell-1})\cdot\U(\Sigma_{\ell-1,\ell}^-)\cdot\U(\Sigma_{\ell})\cdot\G(\Delta_\ell). \]
-By~\cref{lemma:nikolov-type-dl} there exist elements $y_1,y_2,y_3\in\G(\rD_\ell,R)$ and $w_1,w_2,w_3\in\widetilde{W}(\rD_\ell)$ such that
+By \cref{lemma:nikolov-type-dl} there exist elements $y_1,y_2,y_3\in\G(\rD_\ell,R)$ and $w_1,w_2,w_3\in\widetilde{W}(\rD_\ell)$ such that
 \begin{align*}

### 2015-09-18 dennis-vaserstein.tex
Minor fixes

@@
 \end{multline*}
-Direct calculation using \cref{lemma:Chevalley-Matsumoto} shows that $(yg)^{x_{2,1}(\xi)} = u h$ for $\xi \in R$, $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$ hence
+Notice that the matrix entry $(yg)_{1,1}$ is invertible.
+From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1:=(yg)^{x_{2,1}(\xi)}$
+satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$.
+Consequently, one has
 \begin{multline*} {A_{\ell,1}}^{X_{-\alpha_1}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_\ell(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\

### 2015-09-18 stability-conditions.tex
Minor fixes

@@
  & a_{ij} = b_{ij} v_{-j} + b_{ji} v_{-i},\ j\neq i,\\
- & a_{ii} = b_{ii} v_{-i} - \sum\limits_{j=1, j\neq i}^\ell b_{ji} v_{-j}.
+ & a_{ii} = b_{ii} v_{-i} - \sum\limits_{\mathclap{\substack{j=1 \\ j\neq i}}}^\ell b_{ji} v_{-j}.
 \end{align*}

### 2015-09-21 dennis-vaserstein.tex
Added abstract; abridged introduction; introduced notation for the maximal root; minor fixes; rewritten proof of Nikolov lemma; added citation of Dynkin paper

@@
 \begin{figure}
-\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} l @{\qquad} l}
+\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} c @{\qquad} c}
 \Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
@@
 First of all, notice that by \cref{lemma:dv-normal} we have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
-In all cases under consideration except $\Phi=\rC_\ell$ we have $m_s(\alpha_{\mathrm{max}})=1$.
-Therefore, for $\Phi\neq \rB_\ell, \rC_\ell$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from \cref{item-trans2}.
+In all the cases except $\Phi=\rC_\ell$ we have $m_s(\alpha_{\mathrm{max}})=1$,
+therefore for $\Phi\neq \rB_\ell, \rC_\ell$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from \cref{item-trans2}.
 

### 2015-09-21 paper.tex
Added abstract; abridged introduction; introduced notation for the maximal root; minor fixes; rewritten proof of Nikolov lemma; added citation of Dynkin paper

@@
 
-\title [Parabolic factorizations of congruence subgroups] {Parabolic factorizations and width of congruence subgroups in Chevalley groups}
+\title [Parabolic factorizations of congruence subgroups] {Parabolic factorizations of principal congruence subgroups in Chevalley groups and their applications}
 \keywords {Chevalley groups, relative subgroups, stability for $\K_1$. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
@@
 
-%\begin{abstract} \end{abstract}
+\begin{abstract} We formulate and prove relative analogues (i.\,e. analogues for principal congruence subgroups) of Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
+As an application we obtain upper estimates for the width of congruence subgroups with respect to elementary generators and subgroups of type $\SL_2$.
+We also study submaximal factorizations of Chevalley groups of type $\rA_\ell$ and $\rD_\ell$.
+\end{abstract}
 
@@
 \section{Introduction}\label{sec:intro}
-Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots $\Pi=\{\alpha_1,\ldots, \alpha_\ell\}$ numbered as in Bourbaki's book~\cite{Bou}.
+Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots.
 Denote by $G=\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over $R$ and by $\E(\Phi, R)$ its \emph{elementary subgroup}, 
@@
 %TODO: Illustrate each statement of the text below with a reference:
-There are two main reasons to study parabolic factorizations.
-Recall that a number of various factorizations of $\G$ are known over small-dimensional rings.
-For example, Bruhat decomposition is the key instrument in the study of linear groups over fields, whereas Gauss decomposition and unitriangular factorizations are useful tools in the study of groups over local rings.
-Moreover, for each particular analytic or arithmetic setting there is a special decomposition theorem (Iwasawa, Cartan and Iwahori decompositions, to mention a few).
-Unfortunately, neither of these decompositions can be carried over to rings of higher dimension.
-The main advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of milder ring-theoretic assumptions formulated in terms of the \emph{stable rank} of the ground ring.
-Their another advantage is that they prove useful in the study of asymptotical properties of Chevalley groups. We are going to discuss this theme in more detail below.
+%There are two main reasons to study parabolic factorizations.
+%Recall that a number of various factorizations of $\G$ are known over small-dimensional rings.
+%For example, Bruhat decomposition is the key instrument in the study of linear groups over fields, whereas Gauss decomposition and unitriangular factorizations are useful tools in the study of groups over local rings.
+%Moreover, for each particular analytic or arithmetic setting there is a special decomposition theorem (Iwasawa, Cartan and Iwahori decompositions, to mention a few).
+%Unfortunately, neither of these decompositions can be carried over to rings of higher dimension.
+%The main advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of milder ring-theoretic assumptions formulated in terms of the \emph{stable rank} of the ground ring.
+%Their another advantage is that they prove useful in the study of asymptotical properties of Chevalley groups. We are going to discuss this theme in more detail below.
 
@@
 \subsection{Root systems}\label{sec:rootsys}
-Let $\Pi=\{\alpha_1, \ldots, \alpha_l\}$ be a basis of $\Phi$. Denote by $\Phi^+$ and $\Phi^-$ subsets of positive and negative roots with respect to $\Pi$.
-Denote by $m_i(\alpha)$ the coefficient of $\beta$ in the expansion of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
+Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
+We use conventional numbering of basis vectors of $\Pi$ following Bourbaki's book~\cite{Bou}.
+Denote by $\Phi^+$ and $\Phi^-$ the subsets of positive and negative roots with respect to $\Pi$.
+Let $\alpha_\mathrm{max}$ denote the maximal root of $\Phi$.
+For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th component of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
 

### 2015-09-21 subsystem-factorizations.tex
Added abstract; abridged introduction; introduced notation for the maximal root; minor fixes; rewritten proof of Nikolov lemma; added citation of Dynkin paper

@@
-The main result of \cite{NikProdDecomp} is the following
-\begin{thm*}
-Let $G$ be a classical (possibly twisted) Chevalley group of rank $n$ over a finite field. Then $G$ equals the product of at most $200$ conjugates of an $\SL_n$ subgroup.
-\end{thm*}
+%The main result of \cite{NikProdDecomp} is the following
+%\begin{thm*}
+%Let $G$ be a classical (possibly twisted) Chevalley group of rank $n$ over a finite field. Then $G$ equals the product of at most $200$ conjugates of an $\SL_n$ subgroup.
+%\end{thm*}
 As indicated in the introduction, the Dennis---Vaserstein decomposition gives the following result.
@@
 We will now elaborate on the case $\Phi=\rD_\ell$ to show that the Dennis---Vaserstein decomposition is suitable for handling other Chevalley groups, albeit with a stronger assumption on the base ring.
+
+Consider the decreasing chain $\Phi_k$, $k=1,\ldots, \lfloor \ell/2 \rfloor$ of root subsystems of $\Phi=\rD_\ell$ defined as follows.
+If $2k \neq \ell$ let $\Phi_k$ be the subsystem of $\Phi$ spanned by simple roots $\alpha_{2k-1}, \ldots, \alpha_\ell$.
+Clearly, such $\Phi_k$ has type $\rD_{(\ell-2k+2)}$. 
+In the remaining case $2k = \ell$ set $\Phi_k = \langle \alpha_\ell \rangle \cong \rA_1$.
+Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\,e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1,\ldots, \lfloor \ell/2 \rfloor$.
+Denote by $B$ the set of all $\beta_k$. From the definition it is clear that elements of $B$ are mutually perpendicular to each other.
+The roots $\beta_k$ can also be defined by explicit formulae:
+\begin{align*}
+ \beta_k =  \alpha_{2k-1} + 2\alpha_{2k}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell, & \text{ for } i=1,\ldots,\lfloor\ell/2\rfloor-1, \\
+ \beta_{\lfloor\ell/2\rfloor} = \alpha_{\ell-2}+\alpha_{\ell-1}+\alpha_\ell, & \text{ if $\ell$ is odd,} \\
+ \beta_{\lfloor\ell/2\rfloor} = \alpha_\ell, & \text{ if $\ell$ is even.}
+\end{align*}
+
+\begin{lemma}\label{lemma:nikolov-weyl} There exists an element $w\in W(\rD_\ell)$ such that $w(B) \subseteq \Delta_\ell^+$. \end{lemma}
+\begin{proof}
+\textsc{Case $\ell=4$.} \textbf{TODO: Write proof}
+
+\textsc{Case $\ell \geq 5$.}
+Recall from \cite[Table~9]{Dy72} that for odd (resp. even) $\ell$ all maximal subsystems of type $\rA_1+\ldots+\rA_1+\rD_3$
+(resp. $\rA_1+\ldots+\rA_1+\rD_4$) are conjugate under the action of $W(\Phi)$. Consequently, we can find $w\in W(\Phi)$
+such that $w(\beta_k) = \alpha_{2k-1}$ for $k < \lfloor\ell/2\rfloor$ (resp. $k < \lfloor\ell/2\rfloor-1$). It remains to
+notice that we can move the remaining root $\beta_{\lfloor\ell/2\rfloor}$ 
+(resp. the remaining $2$ roots $\beta_{\lfloor\ell/2\rfloor-1}$, $\beta_{\lfloor\ell/2\rfloor}$) to
+$\alpha_{\ell-1}$ (resp. to $\alpha_{\ell-3}$, $\alpha_{\ell-1}$) using the fact that the Weyl group $W(\rD_3)$ acts
+transitively on roots (resp. using the first part of the proof of the lemma). \end{proof}
+
 The following lemma is an analogue of Proposition~1 of~\cite{NikProdDecomp}.
 \begin{lemma}\label{lemma:nikolov-type-dl}
-Let $\Phi=\rD_\ell$. There exist an element $y\in\G(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell)\subset[\U(\Delta_\ell^-),y]\cdot{}^w\!\U(\Delta_\ell^+)$.
+Let $\Phi=\rD_\ell$, $\ell\geq 4$.
+There exist an element $y\in\E(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell, I)\subset[\U(\Delta_\ell^-, I),y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
 \end{lemma}
 \begin{proof}
-Set $\beta_i = \alpha_{2i-1} + 2\alpha_{2i}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell$, for $i=1,\ldots,\lfloor\ell/2\rfloor-1$.
-Set $\beta_{\lfloor\ell/2\rfloor}=\alpha_{\ell-2}+\alpha_{\ell-1}+\alpha_\ell$ if $\ell$ is odd, and $\beta_{\lfloor\ell/2\rfloor}=\alpha_\ell$ if $\ell$ is even.
-Denote $B=\{\beta_i\}$, then decompose $\U(\Sigma_\ell)=\U(\Sigma_\ell\setminus B)\cdot\U(B)$.
-In fact, $\U(\Sigma_\ell)$ is abelian.
+Since $\U(\Sigma_\ell, I)$ is abelian we can decompose it as $\U(\Sigma_\ell, I)=\U(\Sigma_\ell\setminus B, I) \cdot \U(B, I)$. 
+Set $y=\prod_{\beta\in B}x_\beta(1)$. We will now show that $\U(\Sigma_\ell\setminus B, I)\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I)$.
 
-Set $y=\prod_{\beta\in B}x_\beta(1)$. We will now show that $\U(\Sigma_\ell\setminus B)\subset[\U(\Delta_\ell^-),y]\cdot\U(B)$.
-
-Note that \eqref{rel:CCF} implies
-\[ \bigl[\U(\Delta_2^-),x_{\beta_1}(1)\bigr]=1,\quad \Bigl[\U(\Sigma_2^-\cap\Delta_\ell),\prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
-The first follows from the fact that the only root $\alpha$ with $m_2(\alpha)=2$ is $\beta_1$.
-The second holds since a root $\alpha\in(\Sigma_2^-\cap\Delta_\ell)+(B\setminus\{\beta_1\})$ must simultaneously satisfy $m_2(\alpha)=-1$ and $m_\ell(\alpha)=1$, which is impossible.
-
-Since $B\setminus\{\beta_1\}\subset\Sigma_\ell\cap\Delta_2$, this implies
-\[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell)\cdot\U(\Delta_{2,\ell}^-), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell\cap\Delta_2).
+Notice that $\beta_1$ is the only root of $\Phi$ satisfying $m_2(\beta_1)=2$ therefore the commutator formula~\eqref{rel:CCF} implies
+\[ \bigl[\U(\Delta_2^-, I),x_{\beta_1}(1)\bigr]=1. \]
+Since the set $A=(\Sigma_2^-\cap\Delta_\ell)+(B\setminus\{\beta_1\})$ is disjoint from $\Phi$ 
+(for $\alpha\in A$ one has $m_2(\alpha)=-1$ and $m_\ell(\alpha)=1$)
+we also get from~~\eqref{rel:CCF} that
+\[\Bigl[\U(\Sigma_2^-\cap\Delta_\ell, I),\prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
+Since $B\setminus\{\beta_1\}\subset\Sigma_\ell\cap\Delta_2$, the above identities imply
+\[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2,\ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell\cap\Delta_2, I).
 \]
-Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell)$ and decompose it as $u=vw$, $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell)$, $w\in\U(\Sigma_2^-\cap\Delta_{1,\ell})$, then, using the identity
+Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$, $w\in\U(\Sigma_2^-\cap\Delta_{1,\ell}, I)$.
+Using the identity
 \begin{equation}\label{eq:comm-ab-c}
@@
 \end{equation}
-rewrite
+we can rewrite
 \[ [vw,x_{\beta_1}(1)] = {}^v[w,x_{\beta_1}(1)]\cdot[v,x_{\beta_1}(1)].  \]
-Since $\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell)$ and $\U(\Sigma_2^-\cap\Delta_{1,\ell})$ are abelian, it is easy to see that
-\[ [v,x_{\beta_1}(1)]\in\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1), \quad [w,x_{\beta_1}(1)]\in\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}). \]
+Since $\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $\U(\Sigma_2^-\cap\Delta_{1,\ell}, I)$ are abelian, it is easy to see that
+\[ [v,x_{\beta_1}(1)]\in\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1, I), \quad [w,x_{\beta_1}(1)]\in\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}, I). \]
+%TODO: <add text from thesis>
 Varying $v$ and $w$ one can obtain any element of $\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1)$ and $\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\})$ respectively.
@@
 So we can carry the induction on the rank of the subsystem, and construct for any given $a\in\U(\Sigma_\ell\setminus B)$ an element $b\in\U(\Delta_\ell^-)$ such that $a\in[b,y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-),y]\cdot\U(B)$.
+%TODO: </add text from thesis>
 
-It remains to note that the roots $\pm\beta_i$ lie inside a maximal root subsystem of type $\rA_1+\ldots+\rA_1+\rD_3$.
-All such subsystems are conjugate under the action of the Weyl group, so there exist an element $w\in W(\Phi)$ such that $w(\beta_1)=\alpha_1$, $w(\beta_2)=\alpha_3$, $w(\beta_3)=\alpha_5$ and so on, so that all of $w(\beta_i)$ lie in $\Delta_\ell^+$.
+It remains to notice that the assertion of the lemma follows from~\cref{lemma:nikolov-weyl}.
+%It remains to note that the roots $\pm\beta_i$ lie inside a maximal root subsystem of type $\rA_1+\ldots+\rA_1+\rD_3$.
+%All such subsystems are conjugate under the action of the Weyl group, so there exist an element $w\in W(\Phi)$ such that
+%$w(\beta_1)=\alpha_1$, $w(\beta_2)=\alpha_3$, $w(\beta_3)=\alpha_5$ and so on, so that all of 
+%$w(\beta_i)$ lie in $\Delta_\ell^+$.
 \end{proof}

### 2015-09-21 subsystem-factorizations.tex
Finished combinatorial part of Nikolov lemma for D_l

@@
 \begin{align*}
- \beta_k =  \alpha_{2k-1} + 2\alpha_{2k}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell, & \text{ for } i=1,\ldots,\lfloor\ell/2\rfloor-1, \\
+ \beta_k =  \alpha_{2k-1} + 2\alpha_{2k}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell, & \text{ for } k=1,\ldots,\lfloor\ell/2\rfloor-1, \\
  \beta_{\lfloor\ell/2\rfloor} = \alpha_{\ell-2}+\alpha_{\ell-1}+\alpha_\ell, & \text{ if $\ell$ is odd,} \\
@@
 \begin{proof}
-\textsc{Case $\ell=4$.} \textbf{TODO: Write proof}
+\textsc{Case $\ell=4$.} Set $w = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}} \circ \sigma_{\alpha\ssub{2} + \alpha\ssub{4}}$.
+Straightforward computation shows that 
+$$w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3,\quad w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1 $$
+which implies the assertion of the lemma.
 
@@
 (resp. $\rA_1+\ldots+\rA_1+\rD_4$) are conjugate under the action of $W(\Phi)$. Consequently, we can find $w\in W(\Phi)$
-such that $w(\beta_k) = \alpha_{2k-1}$ for $k < \lfloor\ell/2\rfloor$ (resp. $k < \lfloor\ell/2\rfloor-1$). It remains to
-notice that we can move the remaining root $\beta_{\lfloor\ell/2\rfloor}$ 
+such that $w(\beta_k) = \alpha_{2k-1}$ for $k < \lfloor\ell/2\rfloor$ (resp. $k < \lfloor\ell/2\rfloor-1$). 
+Now using transitivity of the action of $W(\rD_3)$ on roots (resp. by the same argument as in the case $\ell=4$) we can move the remaining root $\beta_{\lfloor\ell/2\rfloor}$ 
 (resp. the remaining $2$ roots $\beta_{\lfloor\ell/2\rfloor-1}$, $\beta_{\lfloor\ell/2\rfloor}$) to
-$\alpha_{\ell-1}$ (resp. to $\alpha_{\ell-3}$, $\alpha_{\ell-1}$) using the fact that the Weyl group $W(\rD_3)$ acts
-transitively on roots (resp. using the first part of the proof of the lemma). \end{proof}
+$\alpha_{\ell-1}$ (resp. to $\alpha_{\ell-3}$, $\alpha_{\ell-1}$) while fixing all the other $\beta_k$. \end{proof}
 

### 2015-09-21 dennis-vaserstein.tex
Preparation for writing down case F_4

@@
 \rE_\ell,\ \ell=6,7                  & \ell & 2      & \sr(I) \leqslant \ell-3 \\ 
-\rE_\ell,\ \ell=6,7                  & \ell & 1      & \asr(I)\leqslant \ell-2 \end{array}\]
+\rE_\ell,\ \ell=6,7                  & \ell & 1      & \asr(I)\leqslant \ell-2 \\ 
+\rF_4                                & 4    & 1      & \asr(I)\leqslant 3 \end{array}\]
 \end{thm}
@@
 \begin{figure}
-\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} c @{\qquad} c}
-\Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
-\rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \ell           & 1  \\     
-\rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \ell           & 1  \\     
-\rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 1  \\
-\rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \ell           & 2  \\ 
-\rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \ell           & \ell-2  \\
-\rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \ell           & 3       \\ 
-\rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & 2(\ell-1)      & \ell-1  \end{array}\]
+\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} c @{\qquad} c @{\qquad} c}
+\Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\Delta_r$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
+\rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\
+\rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 2  \\ 
+\rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
+\rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
+\rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \\
+\rF_4                                & (4, 1)        & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
  \caption[Table]{List of representation involved in the proof of \cref{thm:DennisVaserstein}.} \label{fig:table}
@@
 \begin{lemma} \label{lemma:DVcaseCl}
-For $\Phi=\rC_\ell$ and any ideal $I$ satisfying $\sr(I) \leq \ell-1$ one has $X_{-\alpha_1}(R) \subseteq N_{\ell, 1}$.
+For $\Phi=\rC_\ell$ and any ideal $I$ satisfying $\sr(I) \leq \ell-1$ one has $X_{-\alpha_s}(R) \subseteq N_{rs}$.
 \end{lemma}
 \begin{proof}
-Consider the subset $C \subseteq \EP_1(R, I)$ consisting of matrices such that matrix components $v=(g_{i,2})$, $i=2,\ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
-Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot C$.
+Consider the subset $C \subseteq \EP_s(R, I)$ consisting of matrices such that matrix components $v=(g_{i,2})$, $i=2,\ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
+Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot C$.
 
-By \cref{item:asrUnipC} (applied to the subgroup $\G(\Delta_1, R, I)$) we find for every $g \in \EP_1(R, I)$ a matrix $x \in \U(\Sigma_\ell \cap \Delta_1, I)$ such that $xg \in C$.  
-Notice that one immediately gets the equality $A_{\ell, 1} = A'$ from this.
-Indeed for $g\in \EP_1(R, I)$ one has
-\begin{equation*} \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq 
- \EP_\ell(R, I)x^{-1}  \cdot \U(\Sigma_1^-, I) \cdot xg \subseteq A'. \end{equation*}
+By \cref{item:asrUnipC} (applied to the subgroup $\G(\Delta_s, R, I)$) we find for every $g \in \EP_s(R, I)$ a matrix $x \in \U(\Sigma_r \cap \Delta_s, I)$ such that $xg \in C$.  
+Notice that one immediately gets the equality $A_{rs} = A'$ from this.
+Indeed for $g\in \EP_s(R, I)$ one has
+\begin{equation*} \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq 
+ \EP_r(R, I)x^{-1}  \cdot \U(\Sigma_s^-, I) \cdot xg \subseteq A'. \end{equation*}
 
-By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_1 \cap \Delta_\ell, I)$ such that $(y \cdot g)_{1,2} = 0$.
+By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s \cap \Delta_r, I)$ such that $(y \cdot g)_{1,2} = 0$.
 Consequently, for every $g\in C$ one has
 \begin{multline*}
- \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq \EP_\ell(R, I) y^{-1} \cdot \U(\Sigma_\ell^-\cap \Sigma_1^-, I)^{y^{-1}} \cdot y g \subseteq \\
-  \subseteq \EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot y g
+ \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq \EP_r(R, I) y^{-1} \cdot \U(\Sigma_r^-\cap \Sigma_s^-, I)^{y^{-1}} \cdot y g \subseteq \\
+  \subseteq \EP_r(R, I) \cdot \U(\Sigma_r^-, I) \cdot y g
 \end{multline*}
@@
 From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1:=(yg)^{x_{2,1}(\xi)}$
-satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$.
+satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_s^-, I)$, $h \in \EP_1(R, I)$.
 Consequently, one has
-\begin{multline*} {A_{\ell,1}}^{X_{-\alpha_1}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_\ell(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\
- \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell,1} \end{multline*}
+\begin{multline*} {A_{rs}}^{X_{-\alpha_s}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_r(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_r^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_s^-, I) \cdot \EP_s(R, I) \subseteq \\
+ \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_s(R, I) \subseteq A_{rs} \end{multline*}
  as claimed.
@@
 \begin{proof}[End of the proof of \cref{thm:DennisVaserstein}]
-In the remaining case $\Phi=\rC_\ell$ we conclude from \cref{lemma:dv-normal,lemma:Stein_reduction,lemma:DVcaseCl} that $X_{\pm \alpha_i}(R) \subseteq N_{\ell,1}$, $1\leq i\leq \ell$.
-Therefore, by \cref{lemma:weylfacts} we get that $\widetilde{W}(\Phi) \subseteq N_{\ell,1}$ and hence $\mathcal{X} \subseteq L_{\ell,1}$ as required.
+In the remaining case $\Phi=\rC_\ell$ we conclude from \cref{lemma:dv-normal,lemma:Stein_reduction,lemma:DVcaseCl} that $X_{\pm \alpha_i}(R) \subseteq N_{rs}$, $1\leq i\leq \ell$.
+Therefore, by \cref{lemma:weylfacts} we get that $\widetilde{W}(\Phi) \subseteq N_{rs}$ and hence $\mathcal{X} \subseteq L_{rs}$ as required.
 \end{proof}

### 2015-09-22 stability-conditions.tex
Added one more lemma on the action of unipotent radicals

--- 2015-09-10 stability-conditions.tex
@@
 \subsection{Action of unipotent radicals}\label{sec:ur-action}
+\begin{lemma}\label{lemma:PSV-symplectic-trick}
+ Let $v=(v_1,\ldots, v_n)^t$ be a column. Denote by $v'$ the vector composed of squares of the components of $v$, i.\,e. $v'=(v_1^2, \ldots, v_n^2)^t$.
+ Then for any matrix $b \in M(n, I)$ one can find a symmetric matrix $a \in M(n, I)$, $a=a^t$ such that $b \cdot v' = a \cdot v$. \end{lemma}
+\begin{proof}
+Straightforward computation shows that the assertion of lemma holds for the matrix $a$ defined by
+\begin{equation*}
+a_{ij} = b_{ij} v_{j} + b_{ji} v_{i},\ j\neq i,\quad a_{ii} = b_{ii} v_{i} - \sum\limits_{\mathclap{\substack{j=1 \\ j\neq i}}}^\ell b_{ji} v_{j}. \qedhere
+\end{equation*}
+%$$(av)_k = \sum\limits_{i=1,\ i\neq k}^\ell \left( b_{ki} v_{i} + b_{ik} v_{k} \right)v_{i}  +
+%\left(b_{kk}v_{k} - \sum\limits_{i=1,\ i\neq k}^\ell b_{ik} v_{i}\right)v_{k} = \sum\limits_{i=1}^\ell b_{ki} v_{i}^2 = (bv')_k$$
+\end{proof}
+
 Let $v\in V=R^{2\ell}$ be a vector of the natural representation of $\G(\rD_\ell, R)$.
@@
 \begin{lemma}\label{lemma:asrUnip}
-Then for any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$ there exists $g\in\U(\Sigma^+_\ell, I) \leq \G(\Phi, R, I)$ such that $(g \cdot v)_+ \in \Ums(\ell, I)$ under the following assumptions on $\Phi$ and $I$.
+For any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$ there exists $g\in\U(\Sigma^+_\ell, I) \leq \E(\Phi, R, I)$ 
+such that $(g \cdot v)_+ \in \Ums(\ell, I)$ under the following assumptions on $\Phi$ and $I$.
 \begin{lemlist}
@@
 \textsc{Case $\Phi=\rC_\ell$.}
-Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are located on the skew-diagonal, i.\,e. $p_{ij}=(\delta_{i, \ell-j+1})$. 
-Set $d =\mathrm{diag}(v_{-\ell},\ldots,v_{-1}).$
-Notice that the column $$v'=(v_1,\ldots,v_\ell, v_{-\ell}^2,\ldots,v_{-1}^2)^t$$ is also $I$-unimodular.
-By the definition of the relative stable rank we can find a matrix $b\in \M(\ell,I)$
-such that the upper half $v''_+$ of the vector $v''= g(b) \cdot v'$, where 
-$g(b)=\left(\begin{smallmatrix} e_\ell & p \cdot b \\ 0 & e_{\ell} \end{smallmatrix}\right)$, is $I$-unimodular.
-It is clear that $v''_+ = v'_+ + pb v'_- = v_+ + pbd v_-$. 
-Consider the matrix $a \in M(\ell, I)$ defined by 
-\begin{align*}
- & a_{ij} = b_{ij} v_{-j} + b_{ji} v_{-i},\ j\neq i,\\
- & a_{ii} = b_{ii} v_{-i} - \sum\limits_{j=1, j\neq i}^\ell b_{ji} v_{-j}.
-\end{align*}
-It is clear that the matrix $pa$ is persymmetric and that $g(a) \in \U(\Sigma_\ell, I)$. 
-On the other hand, direct calculation shows that $(g(a)\cdot v)_+=v_+ + pav_- = v_+ + pbdv_- = v''_+ \in \Ums(\ell, I)$.
-%$$(av_-)_k = \sum\limits_{i=1,\ i\neq k}^\ell \left( b_{ki} v_{-i} + b_{ik} v_{-k} \right)v_{-i}  +
-%\left(b_{kk}v_{-k} - \sum\limits_{i=1,\ i\neq k}^\ell b_{ik} v_{-i}\right)v_{-k} = \sum\limits_{i=1}^\ell b_{ki} v_{-i}^2 = (bdv_-)_k$$
+Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are on the skew-diagonal, i.\,e. $p_{ij}=(\delta_{i, \ell-j+1})$. 
+For $b \in M(\ell, I)$ set $g(b)=\left(\begin{smallmatrix} e_\ell & p \cdot b \\ 0 & e_{\ell} \end{smallmatrix}\right)$.
+Clearly, if $b$ is symmetric then $g(b)$ lies in $\U(\Sigma_\ell, I)\leq \E(\rC_\ell, R, I)$.
+
+Notice that the column $v'=(v_1,\ldots,v_\ell, v_{-\ell}^2,\ldots,v_{-1}^2)^t$ is $I$-unimodular.
+By the definition of the relative stable rank we can find a matrix $b\in \M(\ell,I)$ such that the upper half $v''_+$ of the vector $v''= g(b) \cdot v'$ is $I$-unimodular.
+It is clear that $v''_+ = v_+ + pb v'_-$. 
+Finally, applying \cref{lemma:PSV-symplectic-trick} we find a symmetric matrix $a$ such that
+$$(g(a)\cdot v)_+=v_+ + pav_- = v_+ + pbv'_- = v''_+ \in \Ums(\ell, I).$$
 
@@
 \begin{lemma} \label{lemma:uraction} 
-Let $\Phi=\rA_\ell, \rD_\ell$. Denote by $\pi$ the natural representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1,2\ell$.
+Let $\Phi=\rA_\ell, \rC_\ell, \rD_\ell$. Denote by $\pi$ the natural representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1,2\ell$.
 Assume that one of the following conditions holds:
@@
  \item \label{item:uractionA} $\Phi=\rA_\ell$, $\Gamma=\{ k+1, \ldots, \ell+1\} \subset \Lambda(\pi)$ and $\sr(I)\leq k\leq \ell$;
+ \item \label{item:uractionC} $\Phi=\rC_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\sr(I)\leq \ell$. 
  \item \label{item:uractionD} $\Phi=\rD_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(I)\leq \ell-1$. 
@@
 
+\textsc{Case $\Phi=\rC_\ell$.} 
+Applying \cref{item:asrUnipC} we find $x \in \U(\Sigma_\ell, I)$ such that the upper half $v'_+$ of $v' = x \cdot v$ is unimodular.
+Set $g(a) = \left(\begin{smallmatrix} e_\ell & 0 \\ p \cdot a & e_{\ell} \end{smallmatrix}\right)$.
+Clearly, if $a$ is symmetric then $g(a) \in \U(\Sigma_\ell^-, I)$.
+Since the column $v''_+ = ({v'_1}^2, \ldots, {v'_\ell}^2)^t$ is $I$-unimodular there exists a matrix $b \in M(\ell, I)$ such that $v'_- + p b v''_+ = 0$.
+Finally, using \cref{lemma:PSV-symplectic-trick} we find a symmetric matrix $a$ such that $(g(a) \cdot v')_- = p a v'_+ + v'_- = p b v''_+ + v'_- = 0$.
+
 \textsc{Case $\Phi=\rD_\ell$.} From the proof of \cref{item:asrUnipD} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.

### 2015-09-22 dennis-vaserstein.tex
Added proof in the case F4

@@
 First of all, notice that by \cref{lemma:dv-normal} we have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
-In all the cases except $\Phi=\rC_\ell$ we have $m_s(\alpha_{\mathrm{max}})=1$,
-therefore for $\Phi\neq \rB_\ell, \rC_\ell$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from \cref{item-trans2}.
+In all the cases except $\Phi=\rC_\ell, \rF_4$ we have $m_s(\alpha_{\mathrm{max}})=1$,
+therefore for $\Phi\neq \rB_\ell, \rC_\ell, \rF_4$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from \cref{item-trans2}.
 
@@
 
-We defer the proof in the case $\Phi=\rC_\ell$ until we prove \cref{lemma:DVcaseCl} below.
+We defer the proof in the cases $\Phi=\rC_\ell, \rF_4$ until we prove \cref{lemma:DVcaseCl} below.
 
@@
 
-Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from \cref{item-trans2}.
+Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell, \rF_4$ follow from \cref{item-trans2}.
 In the case $\Phi=\rB_\ell$ from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
 $$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs},$$
-whence the statement of the theorem follows. \end{proof}
+and the statement of the theorem follows. \end{proof}
 
-\begin{lemma} \label{lemma:DVcaseCl}
-For $\Phi=\rC_\ell$ and any ideal $I$ satisfying $\sr(I) \leq \ell-1$ one has $X_{-\alpha_s}(R) \subseteq N_{rs}$.
+\begin{lemma}\label{lemma:DVST}
+Assume that one of the following holds:
+\begin{lemlist}
+ \item \label{lemma:DVcaseCl} $\Phi=\rC_\ell$ and $\sr(I) \leq \ell-1$;
+ \item \label{lemma:DVcaseF4} $\Phi=\rF_4$ and $\asr(I) \leq 3$.
+\end{lemlist}
+Then one has $X_{-\alpha_s}(R) \subseteq N_{rs}$.
 \end{lemma}
@@
 
-By \cref{item:asrUnipC} (applied to the subgroup $\G(\Delta_s, R, I)$) we find for every $g \in \EP_s(R, I)$ a matrix $x \in \U(\Sigma_r \cap \Delta_s, I)$ such that $xg \in C$.  
+By \cref{item:asrUnipC} and \cref{cor:embeddingBD} (applied to the subgroup $\G(\Delta_s, R, I)$) we find for every $g \in \EP_s(R, I)$ a matrix $x \in \U(\Sigma_r \cap \Delta_s, I)$ such that $xg \in C$.
 Notice that one immediately gets the equality $A_{rs} = A'$ from this.
@@
 
-By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s \cap \Delta_r, I)$ such that $(y \cdot g)_{1,2} = 0$.
+By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s \cap \Delta_r, I)$ such that $(y \cdot g)_{\varpi_s,\varpi_s - \alpha_s} = 0$.
 Consequently, for every $g\in C$ one has
@@
 \end{multline*}
-Notice that the matrix entry $(yg)_{1,1}$ is invertible.
-From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1:=(yg)^{x_{2,1}(\xi)}$
+Notice that the matrix entry $(yg)_{\varpi_s,\varpi_s}$ is invertible.
+From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1:=(yg)^{x_{-\alpha_s}(\xi)}$
 satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_s^-, I)$, $h \in \EP_1(R, I)$.
 Consequently, one has
-\begin{multline*} {A_{rs}}^{X_{-\alpha_s}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_r(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_r^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_s^-, I) \cdot \EP_s(R, I) \subseteq \\
+\begin{multline*} {A_{rs}}^{X_{-\alpha_{s}}(R)} \subseteq \EP_r(R, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_r^-, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_s^-, I) \cdot \EP_s(R, I) \subseteq \\
  \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_s(R, I) \subseteq A_{rs} \end{multline*}

### 2015-09-22 stability-conditions.tex
Added proof in the case F4

@@
 
+\begin{cor} \label{cor:embeddingBD}
+ Denote by $i$ the standard embedding $\B_3 \hookrightarrow \rD_4$. 
+ If $\asr(I)\leq 3$ then for every $I$-unimodular column $v \in \Ums(8, I)$ there exists $g \in \U(\Sigma_3, I) \leq \E(\rB_3, R, I)$ such that
+ the upper half of the vector $i(g) \cdot v$ forms an $I$-unimodular column of height $4$.
+\end{cor}
+\begin{proof}
+ The assertion follows from the fact that for every $g \in \U(\Sigma_4, I) \leq \E(\rD_4, R, I)$ one can find $g' \in \G(\Delta_4, R, I)$ such that
+ $gg'$ lies in the image of $i\colon \G(\rB_3, R, I) \hookrightarrow \G(\rD_4, R, I)$.
+\end{proof}
+
 \begin{lemma} \label{lemma:uraction} 

### 2015-09-22 dennis-vaserstein.tex
Rewriting preliminaries; moved discussion of weight diagrams to the introduction

@@
 
-The next step of the proof is to construct explicitly the set $B$ satisfying the assumptions of \cref{lemma:Stein_reduction}.
-For this purpose we are going to use the technique of {\it weight diagrams} developed in~\cite{PSV98}.
-In the simplest case of a microweight representation (i.\,e. a representation without zero weights)
-the weight diagram of $(V, \pi)$ is just a graph whose vertices are in one-to-one correspondence with the elements of $\Lambda(\pi)$.
-Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ iff $\lambda-\mu = \alpha_i$.
+%The next step of the proof is to construct explicitly the set $B$ satisfying the assumptions of \cref{lemma:Stein_reduction}.
+%For this purpose we are going to use the technique of {\it weight diagrams} developed in~\cite{PSV98}.
+%In the simplest case of a microweight representation (i.\,e. a representation without zero weights)
+%the weight diagram of $(V, \pi)$ is just a graph whose vertices are in one-to-one correspondence with the elements of $\Lambda(\pi)$.
+%Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ iff $\lambda-\mu = \alpha_i$.
 
-Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
-Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=\G(\Delta_r, R)$ it becomes reducible.
-Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
-Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
+%Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
+%Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=\G(\Delta_r, R)$ it becomes reducible.
+%Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
+%Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
 
-Using the language of weight diagrams subsets $\Lambda(\pi')$, $\Gamma$ can be visualized as follows.
-After removing all bonds marked $r$ the diagram of $\pi$ splits into several connected components.
-The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component containg the vertex $\varpi_s$.
-In turn, the set $\Gamma$ corresponds to vertices of $\Lambda(\pi')$ incident to any of the removed bonds.
+%Using the language of weight diagrams subsets $\Lambda(\pi')$, $\Gamma$ can be visualized as follows.
+%After removing all bonds marked $r$ the diagram of $\pi$ splits into several connected components.
+%The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component containg the vertex $\varpi_s$.
+%In turn, the set $\Gamma$ corresponds to vertices of $\Lambda(\pi')$ incident to any of the removed bonds.
 
-Notice that $\Delta_s$ has type either $\rD_\ell$ (in the case $\Phi=\rE_\ell$, $(r,s)=(2,\ell)$) or $\rA_\ell$ (otherwise).
-From a consideration of weight diagrams we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Figure~\ref{fig:table}).
-It is clear that in all cases $\pi'$ is the natural representation of $\G(\Delta_s, R)$.
+%Notice that $\Delta_s$ has type either $\rD_\ell$ (in the case $\Phi=\rE_\ell$, $(r,s)=(2,\ell)$) or $\rA_\ell$ (otherwise).
+%From a consideration of weight diagrams we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Figure~\ref{fig:table}).
+%It is clear that in all cases $\pi'$ is the natural representation of $\G(\Delta_s, R)$.
 
-Yet another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in \cref{lemma:Matsumoto}.
-Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
-for every bond of the diagram joining vertices $\lambda$ and $\lambda + \alpha$ the element $x_{\alpha}(\xi)$ adds $\pm \xi \cdot v_\lambda$ to $v_{\lambda+\alpha}$.
-See~\cite[Section~3.4]{PSV98} for more detailed description.
+%Yet another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in \cref{lemma:Matsumoto}.
+%Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
+%for every bond of the diagram joining vertices $\lambda$ and $\lambda + \alpha$ the element $x_{\alpha}(\xi)$ adds $\pm \xi \cdot v_\lambda$ to $v_{\lambda+\alpha}$.
+%See~\cite[Section~3.4]{PSV98} for more detailed description.
 

### 2015-09-22 paper.tex
Preparation for writing down case F_4
Rewriting preliminaries; moved discussion of weight diagrams to the introduction

@@
 \newcommand{\rE}{\mathsf{E}}
+\newcommand{\rF}{\mathsf{F}}
+\newcommand{\rG}{\mathsf{G}}
 
@@
 Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
-We use conventional numbering of basis vectors of $\Pi$ following Bourbaki's book~\cite{Bou}.
+We use conventional numbering of basis vectors of $\Pi$ which follows Bourbaki (cf.~\cite[Table~1]{PSV98}).
 Denote by $\Phi^+$ and $\Phi^-$ the subsets of positive and negative roots with respect to $\Pi$.
@@
 
-\subsection{Chevalley groups}
+\subsection{Chevalley groups and their elementary subgroups} \label{sec:elementary}
 Our exposition of Chevalley groups is standard and follows~\cite{Ta, S, St78, VP, Va86}.
@@
 the group $\G(\Phi, R)$ equals $\SL(\ell+1, R)$, $\Spin(2\ell+1, R)$, $\Sp(2\ell, R)$, $\Spin(2\ell, R)$, respectively.
+
 Notice that from the uniqueness theorem of M.~Demazure (see~\cite[Corollaire~5.2]{SGA3}) 
@@
 
-In this paper we work with the irreducible representations of Chevalley groups with the highest weight
-$\varpi_1$ (in the case of a classical $\Phi$) or $\varpi_\ell$ (in the case $\Phi=\rE_\ell$, $\ell=6,7$).
-The former are the natural vector representations of classical groups acting on free modules $V=R^n$ of dimension $n=\ell+1, 2\ell+1, 2\ell,2\ell$ for $\Phi=\rA_\ell,\rB_\ell,\rC_\ell,\rD_\ell$ respectively.
-The latter are the microweight representations of dimension $n=27, 56$ for $\ell=6,7$.
-
-For a representation $\pi$ of $\G(\Phi, R)$ on $V$ we denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $V_\lambda$ the weight subspace corresponding to $\lambda\in\Lambda$.
-
-\textbf{TODO: Give definitions of $\Lambda^*$, $V^0$, the notion of ``basic representation''. }
-
-For any of the representations described above (with the sole exception of $(\rE_8, \varpi_8)$) all weight subspaces $V_\lambda$ are one-dimensional. 
-This allows us to choose a basis $E_\pi=\{e_\lambda\}_{\lambda\in\Lambda}$.
-
-It will be convenient to use the standard numbering for the weights of the natural representations of classical groups (cp.~\cite[§1B]{St78}):
-\[\begin{array}{cll}
-  1,2,\ldots, \ell+1 & \text{in the case} & \Phi =\rA_\ell, \\
-  1,2,\ldots \ell, 0, -\ell,\ldots, -2, -1 & \text{in the case} & \Phi =\rB_\ell, \\
-  1,2,\ldots \ell, -\ell,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
-\end{array}\]
-For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ etc.
-
-For a weight $\lambda\in \Lambda$ we denote by $(-)_\lambda\colon V\to R$ the coordinate function corresponding to $\lambda$.
-In other words,  $v_\lambda$ is the coefficient of the basis vector $e_\lambda$ in the expansion of $v$ in $E_\pi$, i.e. $v=\sum_{\lambda\in \Lambda} v_\lambda e_\lambda$.
-We denote by $v^+$ the basis vector corresponding to the highest weight.
-For classical $\Phi$ we have $v^+=e_1$.
-
-\subsection{Elementary subgroup}\label{sec:elementary}
 Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
@@
 The subgroup $\E(\Phi, R)$, generated by all $X_\alpha(R)$, $\alpha\in\Phi$ is called the {\it elementary subgroup} of the Chevalley group $\G_{sc}(\Phi, R)$.
-
-The following result of H.~Matsumoto describes the action of elementary root unipotents in a basic representation of $\G(\Phi, R)$.
-\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
-Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
-One can choose a basis $v^\lambda$, $\lambda\in\Lambda(\pi)$ of $V$ such that the action of the elementary root unipotents $x_\alpha(\xi)$ on it is described by the following formulae:
-
-\begin{tabular}{ll}
-If $\lambda\in\Lambda^*,\ \lambda+\alpha\notin\Lambda$, then & $x_\alpha(\xi)v^\lambda=v^\lambda$; \\
-If $\lambda,\lambda+\alpha\in\Lambda^*$, then & $x_\alpha(\xi)v^\lambda=v^\lambda\pm\xi v^{\lambda+\alpha}$; \\
-If $\alpha\notin\Lambda^*$, then & $x_\alpha(\xi)v^0=v^0$ for any $v^0\in V^0$; \\
-If $\alpha\in\Lambda^*$, then & $x_\alpha(\xi)v^{-\alpha}=v^{-\alpha}\pm\xi v^0(\alpha)\pm\xi^2 v^\alpha$ and \\
-& $x_\alpha(\xi)v^0=v^0\pm\xi\alpha_*(v^0)v^\alpha$.
-\end{tabular}
-\end{lemma}
-
-\begin{rem}
-Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
-In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ (for some choice of $\lambda_1,\lambda_2$) instead of $x_{\lambda_1-\lambda_2}(\xi)$.
-For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$. This is done in order to fix the signs in \cref{lemma:Matsumoto}.
-\end{rem}
-For classigal groups there is a standard way to fix the signs.
-In case $\Phi=\rC_\ell$ the long and short root unipotents are
-\begin{align*}
-& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
-& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
-\end{align*}
-Here $\varepsilon_i$ is the sign of $i$.
-In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
-\begin{align*}
-& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
-& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
-\end{align*}
 
@@
 \end{alignat}
+
+\subsection{Representations of Chevalley groups}
+In our approach to representations of Chevalley groups we follow \cite[\S~1.4]{PSV98} and \cite[\S~I.2]{Ma69})
+Let $\pi$ be an irreducible representation of $\G(\Phi, R)$ acting on a free $R$-module $V$.
+We denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $\Lambda(\pi)^*$ the subset of non-zero weights.
+Denote by $V_\lambda \leq V$ the \emph{weight subspace} corresponding to $\lambda\in\Lambda(\pi)$ and denote by $m_\lambda$ the dimension of $V_\lambda$.
+
+A representation $\pi$ is called \emph{basic} if for every pair of non-zero weights $\lambda, \mu \in \Lambda^*(\pi)$ such that $\lambda - \mu \in \Pi$ one has $\sigma_\alpha(\lambda) = \mu$.
+In the sequel we work with the irreducible basic representations of Chevalley groups listed in~\cite[Table~2]{PSV98}.
+
+All nonzero weights of a basic representation have multiplicty $1$ and $m_0 = |\Delta(\pi)|$, where $\Delta(\pi)= \Lambda(\pi)^* \cap \Pi$ (see~\cite[Lemma~2.1]{Ma69}).
+Consequently, one can choose a basis $E_\pi = \{ e_\lambda \}_{\lambda \in \Lambda(\pi)} \cup \{ e_0^{\beta}\}_{\beta\in \Delta(\pi)}$ of $V$ in which the action of elementary root unipotents $x_\alpha(\xi)$ has particularly simple description.
+
+\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
+Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
+One can choose a basis $v^\lambda$, $\lambda\in\Lambda(\pi)$ of $V$ such that the action of the elementary root unipotents $x_\alpha(\xi)$ on $V$ is described by the following formulae:
+\newline \begin{tabular}{ll}
+If $\lambda\in\Lambda(\pi)^*,\ \lambda+\alpha\notin\Lambda(\pi)$, then & $x_\alpha(\xi)e_\lambda=e_\lambda$; \\
+If $\lambda,\lambda+\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_\lambda=e_\lambda\pm\xi e_{\lambda+\alpha}$; \\
+If $\alpha\notin\Lambda(\pi)^*$, then & $x_\alpha(\xi)v_0=v_0$ for any $v_0\in V_0$; \\
+If $\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_{-\alpha}=e_{-\alpha}\pm\xi e_0(\alpha)\pm\xi^2 e_\alpha$ and \\
+& $x_\alpha(\xi)v_0=v_0\pm\xi\alpha_*(v_0)e_\alpha$ for $v_0 \in V_0$.
+\end{tabular} \end{lemma}
+
+For a weight $\lambda\in \Lambda$ we denote by $(-)_\lambda\colon V\to R$ the coordinate function corresponding to $\lambda$.
+In other words,  $v_\lambda$ is the coefficient of the basis vector $e_\lambda$ in the expansion of $v$ in $E_\pi$, i.e. $v=\sum_{\lambda\in \Lambda} v_\lambda e_\lambda$.
+We denote by $v^+$ the basis vector corresponding to the highest weight.
+
+It will be convenient to use the standard numbering for the weights of the natural representations of classical groups (cp.~\cite[\S~1B]{St78}):
+\[\begin{array}{cll}
+  1,2,\ldots, \ell+1 & \text{in the case} & \Phi =\rA_\ell, \\
+  1,2,\ldots \ell, 0, -\ell,\ldots, -2, -1 & \text{in the case} & \Phi =\rB_\ell, \\
+  1,2,\ldots \ell, -\ell,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
+\end{array}\]
+For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ etc.
+
+%For classical $\Phi$ we have $v^+=e_1$.
+
+Throughout this article we use the technique of {\it weight diagrams} described in detail in~\cite{PSV98}.
+In the simplest case of a microweight representation (i.\,e. a representation without zero weights)
+the weight diagram of $(V, \pi)$ is just a graph whose vertices are in one-to-one correspondence with the elements of $\Lambda(\pi)$.
+Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ iff $\lambda-\mu = \alpha_i$.
+
+Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
+Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=\G(\Delta_r, R)$ it becomes reducible.
+Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
+Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
+
+%Yet another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in \cref{lemma:Matsumoto}.
+%Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
+%for every bond of the diagram joining vertices $\lambda$ and $\lambda + \alpha$ the element $x_{\alpha}(\xi)$ adds $\pm \xi \cdot v_\lambda$ to $v_{\lambda+\alpha}$.
+%See~\cite[Section~3.4]{PSV98} for more detailed description.
+
+\begin{rem}
+Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
+In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ (for some choice of $\lambda_1,\lambda_2$) instead of $x_{\lambda_1-\lambda_2}(\xi)$.
+For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$. This is done in order to fix the signs in \cref{lemma:Matsumoto}.
+\end{rem}
+For classigal groups there is a standard way to fix the signs.
+In case $\Phi=\rC_\ell$ the long and short root unipotents are
+\begin{align*}
+& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
+& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
+\end{align*}
+Here $\varepsilon_i$ is the sign of $i$.
+In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
+\begin{align*}
+& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
+& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
+\end{align*}
+
+Using the language of weight diagrams subsets $\Lambda(\pi')$, $\Gamma$ can be visualized as follows.
+After removing all bonds marked $r$ the diagram of $\pi$ splits into several connected components.
+The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component containg the vertex $\varpi_s$.
+In turn, the set $\Gamma$ corresponds to vertices of $\Lambda(\pi')$ incident to any of the removed bonds.
+
+%Notice that $\Delta_s$ has type either $\rD_\ell$ (in the case $\Phi=\rE_\ell$, $(r,s)=(2,\ell)$) or $\rA_\ell$ (otherwise).
+%From a consideration of weight diagrams we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Figure~\ref{fig:table}).
+%It is clear that in all cases $\pi'$ is the natural representation of $\G(\Delta_s, R)$.
+
+Yet another benefit of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in \cref{lemma:Matsumoto}.
+Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
+for every bond of the diagram joining vertices $\lambda$ and $\lambda + \alpha$ the element $x_{\alpha}(\xi)$ adds $\pm \xi \cdot v_\lambda$ to $v_{\lambda+\alpha}$.
+See~\cite[Section~3.4]{PSV98} for more detailed description.
 

### 2015-09-23 dennis-vaserstein.tex
Rewriting preliminaries

--- 2015-09-22 dennis-vaserstein.tex
@@
 The next step of the proof is to construct explicitly the set $B$ satisfying the assumptions of \cref{lemma:Stein_reduction}.
-For this purpose we are going to use the technique of {\it weight diagrams} developed in~\cite{PSV98}.
-In the simplest case of a microweight representation (i.\,e. a representation without zero weights)
-the weight diagram of $(V, \pi)$ is just a graph whose vertices are in one-to-one correspondence with the elements of $\Lambda(\pi)$.
-Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ iff $\lambda-\mu = \alpha_i$.
 
-Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
-Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=\G(\Delta_r, R)$ it becomes reducible.
-Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
-Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
+%Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
+%Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=\G(\Delta_r, R)$ it becomes reducible.
+%Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
+%Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
 
@@
 It is clear that in all cases $\pi'$ is the natural representation of $\G(\Delta_s, R)$.
-
-Yet another advantage of weight diagrams is that they allow one to visualize the action of elementary root unipotents $x_\alpha(\xi)$ on $v = \sum_{\lambda \in \Lambda(\pi)} v_\lambda e_\lambda \in V$ described in \cref{lemma:Matsumoto}.
-Such description for microweight $\pi$ and $\alpha = \pm\alpha_i\in \pm\Pi$ is particularly simple: 
-for every bond of the diagram joining vertices $\lambda$ and $\lambda + \alpha$ the element $x_{\alpha}(\xi)$ adds $\pm \xi \cdot v_\lambda$ to $v_{\lambda+\alpha}$.
-See~\cite[Section~3.4]{PSV98} for more detailed description.
 

### 2015-09-23 paper.tex
Rewriting preliminaries

--- 2015-09-21 paper.tex
@@
 \DeclareMathOperator{\Par}{P}
+\DeclareMathOperator{\Hom}{Hom}
 \DeclareMathOperator{\B}{B}
@@
 We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\beta, \beta)$.
+Let $\varpi_1, \ldots, \varpi_\ell$ be the \emph{fundamental weights }of $\Phi$, i.\,e. vectors
+defined by $\langle\varpi_i,\alpha_j^\vee\rangle=\delta_{i,j},$ where $\alpha^\vee = \frac{\alpha}{2(\alpha,\alpha)}$.
+
 Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all reflections $\sigma_\alpha$ where $\sigma_\alpha(\beta)=\beta-\langle\alpha,\beta \rangle\cdot \alpha$.
@@
 Let $J\subseteq \Pi$ be a subset of simple roots. 
-For a root $\beta = \sum m_i(\beta)\alpha_i \in \Phi$ set $\shape(J, \beta):=\sum\limits_{i\in J} m_i(\beta) \alpha_i$.
+For a root $\beta = \sum m_i(\beta)\alpha_i \in \Phi$ define \emph{$J$-shape} of $\beta$ (denoted $\shape(J, \beta)$) as $\sum_{i\in J} m_i(\beta) \alpha_i$.
 Set
@@
 \end{alignat}
+
+\subsection{Representations of Chevalley groups}
+Our notation and terminology pertaining to representations of Chevalley groups follows \cite[\S~1.4]{PSV98} and \cite[\S~I.2]{Ma69})
+Let $\pi$ be an irreducible representation of $\G(\Phi, R)$ acting on a free $R$-module $V$.
+We denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $\Lambda(\pi)^*$ the subset of non-zero weights.
+Denote by $V_\lambda \leq V$ the \emph{weight subspace} corresponding to $\lambda\in\Lambda(\pi)$ and denote by $m_\lambda$ the dimension of $V_\lambda$.
+Clearly, $V = V_0 \oplus V'$, where $V'$ denotes the sum of all weight subspaces $V_\lambda$, $\lambda \in \Lambda(\pi)^*$.
+
+A representation $\pi$ is called \emph{basic} if for every pair of non-zero weights $\lambda, \mu \in \Lambda^*(\pi)$ such that $\lambda - \mu \in \Pi$ one has $\sigma_\alpha(\lambda) = \mu$.
+Obviously, this is equivalent to saying that $W(\Phi)$ acts transitively on $\Lambda(\pi)^*$.
+
+The irreducible representations of Chevalley groups used in these paper form a sublist of~\cite[Table~2]{PSV98}.
+More specifically, all of them are \emph{fundamental} (i.\,e. their highest weight is fundamental) and basic.
+We widely employ the technique of \emph{weight diagrams} (see~\cite[\S~2]{PSV98}) to help visualize their structure.
+In the simplest case of a \emph{microweight} representation $\pi$ (i.\,e. $\pi$ such that $V_0 = 0$)
+the weight diagram of $(V, \pi)$ is just an undirected graph whose vertices are in one-to-one correspondence with the elements of $\Lambda(\pi)$.
+Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ iff $\lambda-\mu = \alpha_i$.
+
+An immediate application of weight diagrams is that allow one to quickly read off the branching of a given basic representation with respect to a subsystem subgroup.
+If $J$ is a subset of $\Pi$ and $\Delta$ is the subsystem of $\Phi$ spanned by $J$ then the weight diagram of $\pi$ restricted to $G(\Delta, R)$ can be obtained
+from the weight diagram of $\pi$ by simply removing all the bonds whose label $i$ is such that $\alpha_i\not\in J$ (cf.~\cite[\S~2.7]{PSV98}).
+
+Recall that all nonzero weights of a basic representation have multiplicty one and the multiplicity $m_0$ of the zero weight subspace equals $|\Delta(\pi)|$, where $\Delta(\pi)= \Lambda(\pi)^* \cap \Pi$ (see~\cite[Lemma~2.1]{Ma69}).
+Consequently, one can pick a basis $E_\pi = \{ e_\lambda \}_{\lambda \in \Lambda^*(\pi)}$ of $V'$,
+choose elements $e_0(\alpha) \in V_0$, $\alpha \in \Phi$ (of which $e_0(\alpha)$, $\alpha \in \Delta(\pi)$ form a basis of $V_0$)
+and functionals $\alpha_* \in V_0^* = \Hom_R(V_0, R)$, $\alpha \in \Phi$ in such a way that the action of elementary root unipotents $x_\alpha(\xi)$ has particularly simple description.
+
+\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
+Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
+Then the action of $x_\alpha(\xi)$ is described by the following formulae.
+\newline \begin{tabular}{ll}
+If $\lambda\in\Lambda(\pi)^*,\ \lambda+\alpha\notin\Lambda(\pi)$, then & $x_\alpha(\xi)e_\lambda=e_\lambda$; \\
+If $\lambda,\lambda+\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_\lambda=e_\lambda\pm\xi e_{\lambda+\alpha}$; \\
+If $\alpha\notin\Lambda(\pi)^*$, then & $x_\alpha(\xi)v_0=v_0$ for any $v_0\in V_0$; \\
+If $\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_{-\alpha} = e_{-\alpha}\pm\xi e_0(\alpha)\pm\xi^2 e_\alpha$ and \\
+                                   & $x_\alpha(\xi)v_0         = v_0\pm\xi\alpha_*(v_0)e_\alpha$ for $v_0 \in V_0$.
+\end{tabular} \end{lemma}
+
+The action of $x_\alpha(\xi)$ can be visualized on a weight diagram of $\pi$ as follows. Blah-blah-blah
+\textbf{TODO: Write a passage about this} %TODO:
+
+Notice that the highest weight of natural representations of classical groups is $\varpi_1$.
+It will be convenient for us to number the weights of these representations as in~\cite[\S~1B]{St78}:
+\[\begin{array}{cll}
+  1,2,\ldots, \ell+1 & \text{in the case} & \Phi =\rA_\ell, \\
+  1,2,\ldots \ell, 0, -\ell,\ldots, -2, -1 & \text{in the case} & \Phi =\rB_\ell, \\
+  1,2,\ldots \ell, -\ell,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
+\end{array}\]
+For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ etc.
+
+Although it is possible to fix signs of the action constants in the statement of \cref{lemma:Matsumoto} in the general situation (see~\cite{V08}),
+for our purposes it suffices to do that only for classical groups in their natural representations.
+
+\begin{rem}
+Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
+In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ (for some choice of $\lambda_1,\lambda_2$) instead of $x_{\lambda_1-\lambda_2}(\xi)$.
+For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$. \end{rem}
+For classical groups there is a standard way to fix the signs.
+In case $\Phi=\rC_\ell$ the long and short root unipotents are
+\begin{align*}
+& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
+& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
+\end{align*}
+Here $\varepsilon_i$ is the sign of $i$.
+In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
+\begin{align*}
+& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
+& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
+\end{align*}
 

### 2015-09-23 dennis-vaserstein.tex
Rewritten proof of Dennis---Vaserstein

@@
 \begin{multline*}
-\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
+A_{rs} := \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
 = \U(\Sigma_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \hspace{5em} \\
@@
 \end{multline*}
-Denote by $A_{rs}$ any of the above equal subsets.
 
-The main result of this subsection is the following theorem which is a relative version of \cite[Lemma~2.1]{ST76} and \cite[Theorem~2.5]{St78}).
+The main result of this subsection is the following theorem which is a relative version of Dennis---Vaserstein theorem (compare with \cite[Lemma~2.1]{ST76} and \cite[Theorem~2.5]{St78}).
+Notice that M.~Stein uses the first of the above $4$ equivalent ways of writing down the decomposition while A.~Suslin and M.~Tulenbaev use the fourth.
 \begin{thm}\label{thm:DennisVaserstein}
-The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\,e.
-a decompostion of the form $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
+The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\,e. $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
 \[\begin{array}{l@{\qquad}c@{\quad}c@{\qquad}l}
@@
 \end{thm}
-Consider the following two submonoids of $\E(\Phi, R)$:
-\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \right\}, \quad
-   L_{rs}=  \left\{ g\in \E(\Phi, R, I)\ \middle|\ g \cdot A_{rs} \subseteq A_{rs} \right\}. \]
-
-It is easy to see that $N_{rs}$ normalizes $L_{rs}$, i.e. ${L_{rs}}^{N_{rs}} \subseteq L_{rs}$. 
-Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
-\begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
+Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$ consisting of elements which normalize the subset $A_{rs}$, i.\,e.
+\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \right\}. \]
 
@@
 Assume, for example, the latter. It remains to notice that $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}.$
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:DennisVaserstein}]
+Denote by $L_{rs}$ the set consisting of all the elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
+It is easy to see that $N_{rs}$ normalizes $L_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+\begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
+
+The first step of the proof is show that $N_{rs}$ contains sufficiently many elements. 
+This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke the stability conditions for the first time.
+We show that $N_{rs}$ contains the root subgroup $X_{-\alpha\ssub{s}}(R)$, which together with \cref{lemma:dv-normal} and \cref{item-egen} immediately implies that $N_{rs}$ contains the Levi subgroup $\E(\Delta_s, R)$ and hence the extended Weyl group $\widetilde{W}(\Delta_s)$.
+
+The next goal is to demonstrate the inclusion $\U(\Sigma_s, R) \subseteq N_{rs}$ (which implies $\EP_s(R) \subseteq N_{rs}$).
+All the possibilities for $(\Phi, r, s)$ mentioned in the statement of the theorem fall into one of the following three categories:
+\begin{enumerate}
+ \item \textit{Case $m_s(\alpha_{\mathrm{max}})=1$ and $\Phi$ is simply laced.}
+  In this case all the roots of $\Sigma^+_s$ have the same $s$-shape and length, hence the assertion follows from \cref{item-trans2}, \eqref{rel:NnormL} and the fact that we already have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
+ \item \textit{Case $\Phi = \rB_\ell$.} Using the argument as in the first case we get $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$.
+  It remains to prove the inclusion $X_{1,0}(R) \subset N_{rs}$.
+  Specializing identity~\eqref{rel:CCF} we get \begin{equation*} \label{rel:CCF-specBC} x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2) \end{equation*}
+  We already know that $X_{2, 0}(R)$ and $X_{1,-2}(R)$ are contained in $\E(\Delta_s, R) \subseteq N_{rs}$ hence we obtain $X_{1,0}(R) \subseteq N_{rs}$, as claimed.
+ \item \textit{Case $\Phi = \rC_\ell, \rF_4, \rE_8$.}
+ We settle these remaining cases in \cref{lemma:DVST} where we invoke the stability conditions one more time. 
+ In fact, we prove a stronger result, namely that $N_{rs}$ contains $X_{-\alpha\ssub{r}}(R)$ and, consequently, $N_{rs} = \E(\Phi, R)$.
+\end{enumerate}
+
+In view of \cref{prop:Stepanov} to prove the theorem it suffices to show that $L_{rs}$ contains the generating set $\mathcal{Z}(\Sigma_s^-) \cup \mathcal{X}$ of $\E(\Phi, R, I)$.
+From $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)}$ and \eqref{rel:NnormL} it follows that we only have to show $\mathcal{X} \subseteq L_{rs}$.
+
+Finally, the last inclusion follows from the same transitivity argument as above and the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
+For $\Phi=\rB_\ell$ one has to use additionally the fact that
+%from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
+$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere$$ 
 \end{proof}
@@
 
-\begin{proof}[Proof of \cref{thm:DennisVaserstein}]
-By the above discussion we may assume that the assertion of \cref{lemma:Stein_reduction} holds.
-Set $\Pi' = \Pi \setminus \{\alpha_s\}$.
-From \cref{lemma:dv-normal} and \cref{lemma:Stein_reduction} it follows that $X_\alpha(R) \subseteq N_{rs}$ for $\alpha \in \Pi' \cup -\Pi'$.
-Since $\Delta_s$ is irreducible we get from \cref{item-egen} that $\E(\Delta_s, R) \subseteq N_{rs}$.
-
-Our next step is to show that $\U(\Sigma_s, R) \subseteq N_{rs}$.
-First of all, notice that by \cref{lemma:dv-normal} we have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
-In all the cases except $\Phi=\rC_\ell, \rF_4$ we have $m_s(\alpha_{\mathrm{max}})=1$,
-therefore for $\Phi\neq \rB_\ell, \rC_\ell, \rF_4$ all the roots of $\Sigma^+_s$ have the same $s$-shape and length and the assertion follows from \cref{item-trans2}.
-
-In the case $\Phi=\rB_\ell$ the above argument only proves that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$ and a separate treatment is needed for the sole root subgroup $X_{1,0}(R)$ corresponding to the short root of $\Sigma_s^+$.
-Specializing identity~\eqref{rel:CCF} we get:
-\begin{equation*} \label{rel:CCF-specBC} x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2) \end{equation*}
-We already know that $X_{2, 0}(R)$ and $X_{1,-2}(R)$ are contained in $\E(\Delta_s, R) \subseteq N_{rs}$ hence $X_{1,0}(R) \subseteq N_{rs}$, as claimed.
-
-We defer the proof in the cases $\Phi=\rC_\ell, \rF_4$ until we prove \cref{lemma:DVcaseCl} below.
-
-Our ultimate goal is to show the inclusion $\E(\Phi, R, I) \subseteq L_{rs}$. 
-By \cref{prop:Stepanov} it is enough to prove that $\mathcal{Z}(\Sigma^-_s) \subseteq L_{rs}$.
-In view of formula~\eqref{rel:NnormL} and the previous part of the proof it suffices to show only that $\mathcal{X} \subseteq L_{rs}$.
-It is clear that $\EP_r(R, I) \subseteq L_{rs}$.
-Since $\EP_s(R, I) \subseteq \EP_s(R) \subseteq N_{rs}$ we also conclude that $\EP_s(R, I) \subseteq L_{rs}$, indeed, for $g \in \EP_s(R,I)$ one has
-\[ g \cdot A_{rs} \subseteq g \cdot {A_{rs}}^g = A_{rs} \cdot g = A_{rs}. \]
-Thus, we are left to prove the inclusion $\U(\Sigma^-_r \cap \Sigma^-_s, I) \subseteq L_{rs}$.
-
-Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell, \rF_4$ follow from \cref{item-trans2}.
-In the case $\Phi=\rB_\ell$ from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
-$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs},$$
-and the statement of the theorem follows. \end{proof}
-
 \begin{lemma}\label{lemma:DVST}

### 2015-09-24 dennis-vaserstein.tex
Finished rewriting Dennis---Vaserstein decomposition

@@
 This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke the stability conditions for the first time.
-We show that $N_{rs}$ contains the root subgroup $X_{-\alpha\ssub{s}}(R)$, which together with \cref{lemma:dv-normal} and \cref{item-egen} immediately implies that $N_{rs}$ contains the Levi subgroup $\E(\Delta_s, R)$ and hence the extended Weyl group $\widetilde{W}(\Delta_s)$.
+We show that $N_{rs}$ contains the root subgroup $X_{-\alpha\ssub{r}}(R)$, which together with \cref{lemma:dv-normal} and \cref{item-egen} immediately implies that $N_{rs}$ contains the Levi subgroup $\E(\Delta_s, R)$ and hence the extended Weyl group $\widetilde{W}(\Delta_s)$.
 
@@
   Specializing identity~\eqref{rel:CCF} we get \begin{equation*} \label{rel:CCF-specBC} x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2) \end{equation*}
-  We already know that $X_{2, 0}(R)$ and $X_{1,-2}(R)$ are contained in $\E(\Delta_s, R) \subseteq N_{rs}$ hence we obtain $X_{1,0}(R) \subseteq N_{rs}$, as claimed.
- \item \textit{Case $\Phi = \rC_\ell, \rF_4, \rE_8$.}
+  We already know that $X_{2, 0}(R)$ and $X_{1,-2}(R)$ are contained in $N_{rs}$ hence we obtain $X_{1,0}(R) \subseteq N_{rs}$, as claimed.
+ \item \textit{Case $\Phi = \rC_\ell, \rF_4$.}
  We settle these remaining cases in \cref{lemma:DVST} where we invoke the stability conditions one more time. 
- In fact, we prove a stronger result, namely that $N_{rs}$ contains $X_{-\alpha\ssub{r}}(R)$ and, consequently, $N_{rs} = \E(\Phi, R)$.
+ In fact, we prove a stronger result, namely that $N_{rs}$ contains $X_{-\alpha\ssub{s}}(R)$ and, consequently, $N_{rs} = \E(\Phi, R)$.
 \end{enumerate}
@@
 Finally, the last inclusion follows from the same transitivity argument as above and the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
-For $\Phi=\rB_\ell$ one has to use additionally the fact that
+For $\Phi=\rB_\ell$ one has to additionally use the fact that
 %from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
@@
 \begin{lemma}\label{lemma:Stein_reduction}
-Assume that there exists a subset $B \subseteq \E(\Delta_r, R, I)$ satisfying the following assumptions:
-\begin{enumerate}
- \item\label{stein_cond1} One has $\U(\Sigma^+_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \subseteq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B.$
- \item\label{stein_cond2} One has $X_{-\alpha\ssub{r}}(I)^B \subseteq \EP_s(R, I).$
-\end{enumerate}
-Then $X_{-\alpha_r}(R) \subseteq N_{rs}.$
+Under the assumptions of \cref{thm:DennisVaserstein} one has $X_{-\alpha_r}(R) \subseteq N_{rs}.$
 \end{lemma}
 \begin{proof}
-Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
-From the first assumption of the lemma it follows that $A_{rs}=A$.
-On the other hand, by the second assumption we have
-\begin{multline*}
-X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
-X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
-\subseteq B \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I) =
-B \cdot \EP_s(R, I).
-\end{multline*}
-Together with the third statement of \cref{lemma:dv_unipotent} this implies that
-\begin{equation*} \label{rel:sred}
-A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).
-\end{equation*}
-Consequently, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we get that:
-\begin{equation*} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A, \end{equation*}
-which implies the assertion of the lemma. \end{proof}
+Let $(\pi, V)$ be the irreducible representation of $\G(\Phi, R)$ with the highest weight $\varpi_s$.
+Notice that $\Delta_r$ is an irreducible classical root system of type $\rA_\ell$, $\rC_\ell$ or $\rD_\ell$.
+Denote by $(\pi', V')$ the irreducible component of the restriction of $\pi$ to $\G(\Delta_r, R)$ containing the highest weight vector $v^+$ of $\pi$.
+In all the cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta, R)$.
+Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
 
-The next step of the proof is to construct explicitly the set $B$ satisfying the assumptions of \cref{lemma:Stein_reduction}.
+The set $\Gamma$ can be visualized using weight diagrams in the following manner.
+After removing all bonds marked $r$ the weight diagram of $\pi$ splits into several connected components.
+The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram containg the vertex marked $\varpi_s$.
+Clearly, $\Gamma$ consists of weights from $\Lambda(\pi')$ incident to the removed bonds.
 
-%Denote by $\pi$ the irreducible representation of $G=\G(\Phi, R)$ on a free module $V$ with the highest weight $\varpi_s$.
-%Clearly, after restricting the representation $(V, \pi)$ to the subgroup $G'=\G(\Delta_r, R)$ it becomes reducible.
-%Denote by $(V', \pi')$ the irreducible component corresponding to the same highest weight $\varpi_s \in \Lambda(\pi)$.
-%Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
-
-Using the language of weight diagrams subsets $\Lambda(\pi')$, $\Gamma$ can be visualized as follows.
-After removing all bonds marked $r$ the diagram of $\pi$ splits into several connected components.
-The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component containg the vertex $\varpi_s$.
-In turn, the set $\Gamma$ corresponds to vertices of $\Lambda(\pi')$ incident to any of the removed bonds.
-
-Notice that $\Delta_s$ has type either $\rD_\ell$ (in the case $\Phi=\rE_\ell$, $(r,s)=(2,\ell)$) or $\rA_\ell$ (otherwise).
-From a consideration of weight diagrams we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Figure~\ref{fig:table}).
-It is clear that in all cases $\pi'$ is the natural representation of $\G(\Delta_s, R)$.
-
+From a consideration of weight diagrams (see~\cite{PSV98}) we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (cf.~Figure~\ref{fig:table}).
 \begin{figure}
@@
 \end{figure}
+Consider the subset $B \in \E(\Delta_r, R, I)$ consisting of elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
+Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
 
-Now let $B$ be the set of all elements $g$ of $\E(\Delta_r,R, I)$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
 Applying \cref{lemma:uraction} to the subsystem $\Delta_r$ we find
 $x\in\U(\Delta_r^+, I)$, $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
-This proves the first assumption of \cref{lemma:Stein_reduction}, indeed:
-\[ \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B. \]
-To prove the second assumption of \cref{lemma:Stein_reduction} notice that by \cref{lemma:Matsumoto} and the definition of $\Gamma$ for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$ hence
-\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I). \]
+Consequenty, this shows that $A = A_{rs}$, indeed:
+\begin{equation*} \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B.
+\end{equation*}
+
+Notice that by the definition of $\Gamma$ and \cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$.
+Consequently, one has
+\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I), \]
+which implies the following inclusion
+\begin{multline*}
+X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
+X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
+\subseteq B \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I) =
+B \cdot \EP_s(R, I).
+\end{multline*}
+Together with the third statement of \cref{lemma:dv_unipotent} this shows that
+\begin{equation*} \label{rel:sred}
+A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).
+\end{equation*}
+Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we obtain the assertion of the lemma, indeed
+\begin{equation*} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A. \qedhere \end{equation*}
+\end{proof}
 
@@
 \end{proof}
-
-\begin{proof}[End of the proof of \cref{thm:DennisVaserstein}]
-In the remaining case $\Phi=\rC_\ell$ we conclude from \cref{lemma:dv-normal,lemma:Stein_reduction,lemma:DVcaseCl} that $X_{\pm \alpha_i}(R) \subseteq N_{rs}$, $1\leq i\leq \ell$.
-Therefore, by \cref{lemma:weylfacts} we get that $\widetilde{W}(\Phi) \subseteq N_{rs}$ and hence $\mathcal{X} \subseteq L_{rs}$ as required.
-\end{proof}

### 2015-09-24 paper.tex
Finished rewriting Dennis---Vaserstein decomposition

@@
    {_{\!\lower1.5pt\hbox{$\scriptscriptstyle #1$}}}}
+
+\newcommand\restr[2]{\ensuremath{\left.#1\right|_{#2}}}
 
@@
 
-\subsection{Representations of Chevalley groups}
+\subsection{Representations of Chevalley groups} \label{sec:repr}
 Our notation and terminology pertaining to representations of Chevalley groups follows \cite[\S~1.4]{PSV98} and \cite[\S~I.2]{Ma69})
@@
 
-An immediate application of weight diagrams is that allow one to quickly read off the branching of a given basic representation with respect to a subsystem subgroup.
+An immediate application of weight diagrams is that they allow one to quickly read off the branching of a given basic representation with respect to a subsystem subgroup.
 If $J$ is a subset of $\Pi$ and $\Delta$ is the subsystem of $\Phi$ spanned by $J$ then the weight diagram of $\pi$ restricted to $G(\Delta, R)$ can be obtained

### 2015-09-24 dennis-vaserstein.tex
Added invariant-looking statement of D-V theorem

@@
 
-The main result of this subsection is the following theorem which is a relative version of Dennis---Vaserstein theorem (compare with \cite[Lemma~2.1]{ST76} and \cite[Theorem~2.5]{St78}).
-Notice that M.~Stein uses the first of the above $4$ equivalent ways of writing down the decomposition while A.~Suslin and M.~Tulenbaev use the fourth.
+The main result of this subsection is the following theorem which is a relative version of Dennis---Vaserstein theorem (cf. \cite[Lemma~2.1]{ST76} and \cite[Theorem~2.5]{St78}).
+Notice that M.~Stein uses the first of the above $4$ equivalent ways of writing down the decomposition while A.~Suslin and M.~Tulenbaev use the 4th.
 \begin{thm}\label{thm:DennisVaserstein}
-The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\,e. $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
-\[\begin{array}{l@{\qquad}c@{\quad}c@{\qquad}l}
-\Phi                                 & s    & r      & \text{ring condition} \\ \hline\vphantom{\Bigl(}
-\rA_\ell,\ \ell\geqslant 2           & 1    & \ell   & \sr(I) \leqslant \ell-1 \\    
-\rB_\ell,\ \ell\geqslant 2           & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
-\rC_\ell,\ \ell \geqslant 2          & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
-\rD_\ell,\ \ell\geqslant 4           & 1    & \ell   & \sr(I) \leqslant \ell-2 \\ 
-\rD_\ell,\ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2      \\
-\rE_\ell,\ \ell=6,7                  & \ell & 2      & \sr(I) \leqslant \ell-3 \\ 
-\rE_\ell,\ \ell=6,7                  & \ell & 1      & \asr(I)\leqslant \ell-2 \\ 
-\rF_4                                & 4    & 1      & \asr(I)\leqslant 3 \end{array}\]
+Let $\Phi$ be a reduced irreducible root system not equal to $\rE_8$ and let $\{ r, s \}$ denote the labels of some pair of distinct endnodes of the Dynkin diagram of $\Phi$
+such that $\{ r, s\} \neq \{ 1,2 \}$ for $\Phi=\rE_\ell$. Denote by $d$ the distance between $r$ and $s$ on the Dynkin diagram.
+Then the relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\,e. $\E(\Phi, R, I) = A_{rs}$ 
+under the following assumption on $I$:
+\begin{enumerate}
+ \item $\asr(I) \leq d$ for $\Phi=\rF_4$ or $\Phi=\rE_\ell$, $\{r, s\} = \{1, \ell \}$,
+ \item $\sr(I) \leq d$, otherwise.
+\end{enumerate}
+
+%The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\,e. $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
+%\[\begin{array}{l@{\qquad}c@{\quad}c@{\qquad}l}
+%\Phi                                 & s    & r      & \text{ring condition} \\ \hline\vphantom{\Bigl(}
+%\rA_\ell,\ \ell\geqslant 2           & 1    & \ell   & \sr(I) \leqslant \ell-1 \\    
+%\rB_\ell,\ \ell\geqslant 2           & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
+%\rC_\ell,\ \ell \geqslant 2          & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
+%\rD_\ell,\ \ell\geqslant 4           & 1    & \ell   & \sr(I) \leqslant \ell-2 \\ 
+%\rD_\ell,\ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2      \\
+%\rE_\ell,\ \ell=6,7                  & \ell & 2      & \sr(I) \leqslant \ell-3 \\ 
+%\rE_\ell,\ \ell=6,7                  & \ell & 1      & \asr(I)\leqslant \ell-2 \\ 
+%\rF_4                                & 4    & 1      & \asr(I)\leqslant 3 \end{array}\]
 \end{thm}
+Using identities~\ref{rel:h-comm}--\ref{rel:h-w} it is easy to show that Dennis---Vaserstein decomposition is a consequence of Gauss decomposition (see \cref{thm:srRI1}).
+In particular, for rings of stable rank $1$ and groups of rank $2$ (e.\,g. $\Phi=\rG_2$) it is preferable to use Gauss decomposition since it is more accurate.
+
 Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$ consisting of elements which normalize the subset $A_{rs}$, i.\,e.
@@
 Denote by $L_{rs}$ the set consisting of all the elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
-It is easy to see that $N_{rs}$ normalizes $L_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and that $N_{rs}$ normalizes $L_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
 \begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
@@
   In this case all the roots of $\Sigma^+_s$ have the same $s$-shape and length, hence the assertion follows from \cref{item-trans2}, \eqref{rel:NnormL} and the fact that we already have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
- \item \textit{Case $\Phi = \rB_\ell$.} Using the argument as in the first case we get $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$.
+ \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case we get that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$.
   It remains to prove the inclusion $X_{1,0}(R) \subset N_{rs}$.
   Specializing identity~\eqref{rel:CCF} we get \begin{equation*} \label{rel:CCF-specBC} x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2) \end{equation*}
-  We already know that $X_{2, 0}(R)$ and $X_{1,-2}(R)$ are contained in $N_{rs}$ hence we obtain $X_{1,0}(R) \subseteq N_{rs}$, as claimed.
+  Since $X_{2, 0}(R)$ and $X_{1,-2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1,0}(R) \subseteq N_{rs}$ follows.
  \item \textit{Case $\Phi = \rC_\ell, \rF_4$.}
@@
 For $\Phi=\rB_\ell$ one has to additionally use the fact that
-%from $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
 $$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere$$ 
@@
 \begin{proof} The first two statements easily follow from Chevalley commutator formula~\eqref{rel:CCF} while the third one is a formal consequence of the first two. \end{proof}
-
-%The following lemma is a relative version of the main reduction used by M.~Stein in~\cite{St78}
-%for the proof of the absolute Dennis--Vaserstein decomposition.
 
@@
 After removing all bonds marked $r$ the weight diagram of $\pi$ splits into several connected components.
-The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram containg the vertex marked $\varpi_s$.
+The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram containing the vertex marked $\varpi_s$.
 Clearly, $\Gamma$ consists of weights from $\Lambda(\pi')$ incident to the removed bonds.
@@
 \rF_4                                & (4, 1)        & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
- \caption[Table]{List of representation involved in the proof of \cref{thm:DennisVaserstein}.} \label{fig:table}
+ \caption[Table]{List of representations involved in the proof of \cref{thm:DennisVaserstein}.} \label{fig:table}
 \end{figure}

### 2015-09-24 paper.tex
Added invariant-looking statement of D-V theorem

@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
-We often omit the curly braces in the notations above, so, for example, $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i,j}=\Sigma_{\{i,j\}}$.
+We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i,j}=\Sigma_{\{i,j\}}$ etc.
 
@@
 Denote by $V_\lambda \leq V$ the \emph{weight subspace} corresponding to $\lambda\in\Lambda(\pi)$ and denote by $m_\lambda$ the dimension of $V_\lambda$.
-Clearly, $V = V_0 \oplus V'$, where $V'$ denotes the sum of all weight subspaces $V_\lambda$, $\lambda \in \Lambda(\pi)^*$.
 
@@
 More specifically, all of them are \emph{fundamental} (i.\,e. their highest weight is fundamental) and basic.
-We widely employ the technique of \emph{weight diagrams} (see~\cite[\S~2]{PSV98}) to help visualize their structure.
+We widely employ the technique of \emph{weight diagrams} (see~\cite[\S~2]{PSV98}) to help visualize the structure of these representations.
 In the simplest case of a \emph{microweight} representation $\pi$ (i.\,e. $\pi$ such that $V_0 = 0$)
@@
 Recall that all nonzero weights of a basic representation have multiplicty one and the multiplicity $m_0$ of the zero weight subspace equals $|\Delta(\pi)|$, where $\Delta(\pi)= \Lambda(\pi)^* \cap \Pi$ (see~\cite[Lemma~2.1]{Ma69}).
-Consequently, one can pick a basis $E_\pi = \{ e_\lambda \}_{\lambda \in \Lambda^*(\pi)}$ of $V'$,
-choose elements $e_0(\alpha) \in V_0$, $\alpha \in \Phi$ (of which $e_0(\alpha)$, $\alpha \in \Delta(\pi)$ form a basis of $V_0$)
-and functionals $\alpha_* \in V_0^* = \Hom_R(V_0, R)$, $\alpha \in \Phi$ in such a way that the action of elementary root unipotents $x_\alpha(\xi)$ has particularly simple description.
+For $\alpha \in \Phi$ one can define certain elements $e_0(\alpha) \in V_0$ and $\alpha_* \in V_0^* = \Hom_R(V_0, R)$
+and choose some set of vectors $E^* = \{ e_\lambda \}_{\lambda \in \Lambda^*(\pi)}$ in such a way that 
+$E_\pi = E^* \cup \{ e_0(\alpha) \}_{\alpha \in \Delta(\pi)}$ forms a basis of $V$ in which the action of elementary root unipotents $x_\alpha(\xi)$ has particularly simple description.
 

### 2015-10-05 dennis-vaserstein.tex
Fixes from 05.10.15 meeting

@@
   In this case all the roots of $\Sigma^+_s$ have the same $s$-shape and length, hence the assertion follows from \cref{item-trans2}, \eqref{rel:NnormL} and the fact that we already have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
- \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case we get that $\U(\Sigma_s^{+>}, R) \subseteq N_{rs}$.
+ \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case we get that $N_{rs}$ contains the subgroup generated by the root subgroups $X_\alpha(R)$, where $\alpha$ varies over long roots of $\Sigma_s^+$.
   It remains to prove the inclusion $X_{1,0}(R) \subset N_{rs}$.

### 2015-10-05 paper.tex
Fixes from 05.10.15 meeting

@@
 \end{thm}
-The particular case $\Phi = \rA_\ell$, $R = I = \mathbb{Z}$ of the above theorem is similar in spirit to a recent theorem of U.~Hadad (see ~\cite[Theorem~1.6]{Ha12}).
+Notice that a recent result of U.~Hadad and D.~W.~Morris \cite[Theorem~1.6]{Ha12} implies the finiteness of $W(\E(\Phi, R, I), \mathcal{Z}(\Phi^+))$
+for $R=\mathbb{Z}$ and $\Phi=\rA_\ell$.
 

### 2015-10-05 stability-conditions.tex
Fixes from 05.10.15 meeting

--- 2015-09-22 stability-conditions.tex
@@
 
+\begin{cor} \label{cor:embeddingBD}
+ Denote by $i$ the standard embedding $\G(\rB_{\ell-1}, R, I) \hookrightarrow \G(\rD_\ell, R, I)$. 
+ If $\asr(I) \leqslant \ell-1$ then for every $I$-unimodular column $v \in \Ums(8, I)$ there exists $g \in \U(\Sigma_3, I) \leq \E(\rB_3, R, I)$ such that
+ the upper half of the vector $i(g) \cdot v$ forms an $I$-unimodular column of height $4$.
+\end{cor}
+\begin{proof}
+ The assertion follows from the fact that for every $u \in \U(\Sigma_\ell, I) \leq \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that
+ $uu'$ lies in the image of $i$. Namely, denote by $\sigma$ the symmetry of the Dynkin diagram of $\rD_\ell$,
+ and decompose $u$ into the product $u_1 \cdot u_2$, $u_1 \in \U(\Sigma_\ell\cap\Delta_{\ell-1}, I)$, $u_2 \in \Sigma(\Sigma_\ell \cap \Sigma_{\ell-1}, I)$.
+ Then one takes $u' = \sigma(u_1)$.
+
+ Now by \cref{item:asrUnipD} one finds a suitable $u \in \U(\Sigma_\ell, I) \leqslant \E(\rD_\ell, R, I)$ which makes the upper half unimodular,
+ and since $u'$ lies in $\G(\Delta_\ell, R, I)$, the upper half remains unimodular.
+\end{proof}
+
 \begin{lemma} \label{lemma:uraction} 

### 2015-10-06 bass-kolster.tex
Shortened statement of Corollary 4.3, title and abstract

@@
 The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}
-The Bass---Kolster decomposition can be iterated if the stability assumption allows, with a slight improvement of \cref{cor:bass-kolster-count}.
+By iterating Bass---Kolster decomposition one obtains the following result.
 \begin{cor}\label{cor:bass-kolster-iterated}
-Let $\Phi$ be a root system, $R$ a commutative ring and $I$ its ideal.
-Then under a suitable stability assumption every element of $\G(\Phi,R,I)$ is a product of an element of $\G(\langle\pm\alpha_\ell\rangle,R,I)\cong\SL(2,R,I)$, at most $\ell-1$ elements of the form $z_{-\alpha}(*,*)$, $\alpha$ the maximal root of some terminal subsystem containing $\alpha_\ell$, and at most $N$ elementary root unipotents $x_\alpha(s)$, $s\in I$.
-The stability assumption and the number $N$ are as follows:
+Under the assumptions stated below every element of $\G(\Phi,R,I)$ can be factored as a product of one element of 
+$\G(\langle\pm\alpha_\ell\rangle,R,I)\cong\SL(2,R,I)$ and at most $N$ elements of $\mathcal{Z}(\Sigma_\ell)$, where
 \[\begin{array}{l@{\quad}l@{\quad}l}
-\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right|+\ell; \\
-\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right|+2\ell; \\
-\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right|-\ell.
+\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right|+2\ell - 1; \\
+\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right|+3\ell - 1; \\
+\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right|-1.
 \end{array}\]
@@
 \begin{proof}
-The improved estimate for $\Phi=\rA_\ell$ or $\rC_\ell$ is obtained by using the fact that it suffices to make only two or three additions respectively to make the shorter column unimodular in the first step of the Bass---Kolster decomposition.
+A direct consequence of~\cref{cor:bass-kolster-count}.
+The improved estimate for $\Phi=\rA_\ell$ (resp. $\rC_\ell$) follows from the fact that it takes only two (resp. three) additions to shorten 
+the unimodular column in the first step of the proof of~\cref{thm:BassKolster}.
 \end{proof}

### 2015-10-06 paper.tex
Shortened statement of Corollary 4.3, title and abstract

--- 2015-09-24 paper.tex
@@
 
-\title [Parabolic factorizations of congruence subgroups] {Parabolic factorizations of principal congruence subgroups in Chevalley groups and their applications}
-\keywords {Chevalley groups, relative subgroups, stability for $\K_1$. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
+\title {Decompositions of relative Chevalley groups}
+\keywords {Chevalley groups, principal congruence subgroups, stability for $\K_1$, bounded generation, subsystem factorizations, $\SL_2$-factorizations.
+{\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
 \author {Sergey Sinchuk, Andrei Smolensky}
@@
 
-\begin{abstract} We formulate and prove relative analogues (i.\,e. analogues for principal congruence subgroups) of Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
-As an application we obtain upper estimates for the width of congruence subgroups with respect to elementary generators and subgroups of type $\SL_2$.
-We also study submaximal factorizations of Chevalley groups of type $\rA_\ell$ and $\rD_\ell$.
+\begin{abstract} 
+We formulate and prove relative analogues (i.\,e. analogues for principal congruence subgroups) of Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
+As an application we obtain upper estimates for the width of principal congruence subgroups with respect to several families of generators.
+%elementary generators and subgroups of type $\SL_2$ we also study submaximal factorizations of Chevalley groups of type $\rA_\ell$ and $\rD_\ell$.
 \end{abstract}
@@
 \end{thm}
-The particular case $\Phi = \rA_\ell$, $R = I = \mathbb{Z}$ of the above theorem is similar in spirit to a recent theorem of U.~Hadad (see ~\cite[Theorem~1.6]{Ha12}).
+Notice that a recent result of U.~Hadad and D.~W.~Morris \cite[Theorem~1.6]{Ha12} implies finiteness of $W(\E(\Phi, R, I), \mathcal{Z}(\Phi^+))$
+for $R=\mathbb{Z}$ and $\Phi=\rA_\ell$.
 

### 2015-10-07 bass-kolster.tex
Improved 4.2

@@
 \[ \G(\Phi,R,I)=  \U(\Phi^+,I) \cdot \U(\Phi^-,I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I), \]
-where $Z=\left\{ z_{-\alpha_\mathrm{max}}(r,1)\ \middle|\ r\in I \right\}$.
+where $Z = Z_{\alpha_\mathrm{max}}(I)=\left\{z_{-\alpha_\mathrm{max}}(r,1)\ \middle|\ r\in I \right\}$.
 \end{thm}
@@
 \textsc{Case $\Phi=\rA_\ell$, $n=\ell + 1$.}
-%Set $v=(1+v_1,v_2,\ldots,v_\ell,v_{\ell+1})^t\in\Ums(\ell+1,R,I)$.
 Since $\sr(I)\leqslant\ell$, one can find $a_1,\ldots,a_\ell\in I$ such that $(v_1+a_1v_{\ell+1},\ldots,v_\ell+a_\ell v_{\ell+1})^t=(v'_1,\ldots,v'_\ell)^t$ is $I$-unimodular.
 Then there are $b_1,\ldots,b_\ell\in I$ such that $b_1v'_1+\ldots b_\ell v'_\ell=v'-1\in I$. 
-So the vector
-\[ v'' = \prod_{i=1}^\ell x_{\ell+1,i}(b_i) \cdot \prod_{i=1}^\ell x_{i,\ell+1}(a_i) \cdot v \]
+Thus the vector \[ v'' = \prod_{i=1}^\ell x_{\ell+1,i}(b_i) \cdot \prod_{i=1}^\ell x_{i,\ell+1}(a_i) \cdot v \]
 satisfies the equalities~\eqref{eq1}.
@@
 \[ v''=h_2 \cdot x_{1,2}(c_1) \cdot v', \quad h_2=\prod_{i=3}^\ell x_{i,2}(c_i). \]
-
 We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v''_1+\sum_{i=3}^\ell f_i v''_{i} = 1$.
@@
 In the assumptions and notation of \cref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
-can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elementary root unipotents $x_\alpha(s)$ of level $I$.
+can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elements of $\mathcal{X}$.
 \end{cor}
 \begin{proof}
-The above estimates can be obtained by a careful analysis of the proof of the previous theorem.
+The assertion can be obtained by a careful analysis of the proof of the previous theorem.
 Cases $\Phi=\rA_\ell, \rC_\ell$ are immediate.
-In the case $\Phi=\rD_\ell$ the proof of \cref{thm:BassKolster} implies that
-\begin{multline}\nonumber
-\G(\Phi,R,I) =  \U(\Sigma_\ell,I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1,I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z  \cdot \\ \cdot \U(\Sigma_1^-,I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I).
-\end{multline}
+In the case $\Phi=\rD_\ell$ from the proof of \cref{thm:BassKolster} one obtains that
+\begin{equation*} \G(\Phi,R,I) =  \U(\Sigma_\ell,I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1,I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z \cdot \U(\Sigma_1^-,I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I).
+\end{equation*}
 We can present an element $g$ of $\U(\Sigma_\ell, I)$ as a product of $g_1 \in \U(\Sigma_{\{1,2\}} \cap \Sigma_\ell)$ and $g_2\in \U(\Delta_{\{1,2\}}\cap \Sigma_\ell)$.
-An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one) and therefore can be moved to the right until it is consumed by $\G(\Delta_1)$.
+An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one)
+and therefore can be moved to the right until it is consumed by $\G(\Delta_1, R, I)$.
 On the other hand, $g_1$ is a product of at most $2\ell-3$ elementary unipotents, while the width of $\U(\Sigma_1^\pm, I)$ and $\U(\Sigma_2^-\cap\Delta_1)$ in elementary unipotents does not exceed $2\ell-2$ and $2\ell-4$, respectively.
 Summing up these upper bounds we obtain
-$$(2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9 = 4(|\rD_\ell| - |\rD_{\ell-1}|) - 1.$$
+$$(2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9 = 4|\Sigma_1| - 1.$$
 
 The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}
-By iterating Bass---Kolster decomposition one obtains the following result.
 \begin{cor}\label{cor:bass-kolster-iterated}
-Under the assumptions stated below every element of $\G(\Phi,R,I)$ can be factored as a product of one element of 
-$\G(\langle\pm\alpha_\ell\rangle,R,I)\cong\SL(2,R,I)$ and at most $N$ elements of $\mathcal{Z}(\Sigma_\ell)$, where
+Under the assumptions on $\Phi$, $I$ and $N'$ stated below every element of $\G(\Phi,R,I)$ can be factored into a product of 
+one element of $\G(\langle\pm\alpha_\ell\rangle,R,I)\cong\SL(2,R,I)$ and at most $N'$ elements of $\mathcal{Z}(\Sigma_\ell)$:
 \[\begin{array}{l@{\quad}l@{\quad}l}
-\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right|+2\ell - 1; \\
-\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right|+3\ell - 1; \\
-\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right|-1.
+\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N'=3\left|\Phi^+\right|+2\ell - 5; \\
+\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N'=3\left|\Phi^+\right|+3\ell - 6; \\
+\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N'=4\left|\Phi^+\right| - 4.
 \end{array}\]
@@
 \begin{proof}
-A direct consequence of~\cref{cor:bass-kolster-count}.
-The improved estimate for $\Phi=\rA_\ell$ (resp. $\rC_\ell$) follows from the fact that it takes only two (resp. three) additions to shorten 
-the unimodular column in the first step of the proof of~\cref{thm:BassKolster}.
-\end{proof}
 \begin{figure}[htb]\label{fig:bass-kolster}
-\[
-\begin{tikzcd}[row sep=tiny]
+\[\begin{tikzcd}[row sep=tiny]
 \rD_4 \arrow[out=0,in=120]{rd}{\asr\leqslant3} & & & \\
@@
 \rB_4 \arrow{r}{\asr\leqslant3} & \rB_3 \arrow[out=0,in=-120,swap]{ru}{\asr\leqslant2} & &
-\end{tikzcd}
-\]
-\caption{Reductions provided by the Bass---Kolster decomposition}
-\end{figure}
-
+\end{tikzcd}\] \caption{Reductions used in the proof of \cref{cor:bass-kolster-iterated} and \cref{thm:SL2width}} \end{figure}
+The assertion can be obtained by iteratively applying (for a total of $\ell-1$ times) the decomposition of \cref{thm:BassKolster}.
+The improved estimate for $\Phi=\rA_\ell$ (resp.
+$\rC_\ell$) follows from the fact that it suffices to make only two (resp.
+three) additions to shorten the unimodular column in the first step of the proof of \cref{thm:BassKolster}.
+\end{proof}
 \begin{proof}[Proof of \cref{thm:SL2width}]
-A direct application of \cref{cor:bass-kolster-iterated}.
+ As in the proof of the above corollary one has to iteratively apply \cref{thm:BassKolster}.
+ To reduce the number of $\SL_2$-factors involved in the decompositoin one has to group into a single $\SL_2$-factor a pair of opposite root subgroups $X_{\alpha}(I)$, $X_{-\alpha}(I)$ (or $Z_{\pm\alpha}(I)$) appearing on each
+ of the $3$ junctions between the positive and negative unipotent subgroups in the Bass---Kolster decomposition.
+ Since a total of $\ell-1$ reductions are used, we get the estimate $N \leq N' - 3(\ell - 1) + 1$ and the assertion of \cref{thm:SL2width} follows.
 \end{proof}

### 2015-10-07 paper.tex
Improved 4.2

@@
 \begin{abstract} 
-We formulate and prove relative analogues (i.\,e. analogues for principal congruence subgroups) of Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
-As an application we obtain upper estimates for the width of principal congruence subgroups with respect to several families of generators.
-%elementary generators and subgroups of type $\SL_2$ we also study submaximal factorizations of Chevalley groups of type $\rA_\ell$ and $\rD_\ell$.
+We formulate and prove relative versions of Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
+As an application we obtain upper estimates for the width of principal congruence subgroups in terms of several families of generators.
 \end{abstract}
@@
 \begin{thm}\label{thm:SL2width}
-Let $I\trianglelefteq R$ be an ideal, $\Phi$ be a classical root system.
-Then under a suitable stability assumption the prncipal congruence subgroup $\G(\Phi,R,I)$ can be presented as a product of at most $N$ copies of its subgroups isomorphic to $\G(\rA_1,R,I)$, where the stability assumption and the corresponding value of $N$ is as follows:
-%TODO: Constants for A and C - where do they come from?
+Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system satisfying the following assumptions.
 \[\begin{array}{l@{\quad}l@{\quad}l}
-\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right|+\rk(\Phi) - 3; \\
-\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right|+2\rk(\Phi) - 4; \\
-\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right|.
+\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right| - \rk(\Phi) - 1; \\
+\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right| - 2; \\
+\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right| - 3\rk(\Phi).
 \end{array}\]
+Then the principal congruence subgroup $\G(\Phi,R,I)$ can be presented as a product of at most $N$ copies of its (regularly embedded) subgroups isomorphic to $\SL_2(R, I)$.
 \end{thm}
@@
 
-%\section{Applications} %\label{sec:applications}
-\section{Bounded generation}\label{sec:boundgen}
+\section{Applications} %\label{sec:applications}
+\subsection{Bounded generation}\label{sec:boundgen}
 \input{congrsubgr-boundgen}
-\section{Subsystem factorizations}\label{sec:subsysfact}
+\subsection{Subsystem factorizations}\label{sec:subsysfact}
 \input{subsystem-factorizations}

### 2015-10-07 stability-conditions.tex
Improved 4.2

@@
  Denote by $i$ the standard embedding $\G(\rB_{\ell-1}, R, I) \hookrightarrow \G(\rD_\ell, R, I)$. 
- If $\asr(I) \leqslant \ell-1$ then for every $I$-unimodular column $v \in \Ums(8, I)$ there exists $g \in \U(\Sigma_3, I) \leq \E(\rB_3, R, I)$ such that
- the upper half of the vector $i(g) \cdot v$ forms an $I$-unimodular column of height $4$.
+ If $\asr(I) \leqslant \ell-1$ then for every $I$-unimodular column $v \in \Ums(2\ell, I)$ there exists $g \in \U(\Sigma_{\ell-1}, I) \leq \E(\rB_{\ell-1}, R, I)$ such that
+ the upper half of the vector $i(g) \cdot v$ forms an $I$-unimodular column of height $\ell$.
 \end{cor}
 \begin{proof}
- The assertion follows from the fact that for every $u \in \U(\Sigma_\ell, I) \leq \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that
- $uu'$ lies in the image of $i$. Namely, denote by $\sigma$ the symmetry of the Dynkin diagram of $\rD_\ell$,
- and decompose $u$ into the product $u_1 \cdot u_2$, $u_1 \in \U(\Sigma_\ell\cap\Delta_{\ell-1}, I)$, $u_2 \in \Sigma(\Sigma_\ell \cap \Sigma_{\ell-1}, I)$.
+ The assertion follows from the fact that for every $u \in \U(\Sigma_\ell, I) \leq \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that $uu'$ lies in the image of $i$. 
+ Indeed, denote by $\sigma$ the symmetry of the Dynkin diagram of $\rD_\ell$,
+ and decompose $u$ into the product $u_1 \cdot u_2$, $u_1 \in \U(\Sigma_\ell\cap\Delta_{\ell-1}, I)$, $u_2 \in \U(\Sigma_\ell \cap \Sigma_{\ell-1}, I)$.
  Then one takes $u' = \sigma(u_1)$.

### 2015-10-07 dennis-vaserstein.tex
Improved 4.2
Moved Gauss and DV theorems to the introduction

@@
 \end{multline*}
-
-The main result of this subsection is the following theorem which is a relative version of Dennis---Vaserstein theorem (cf. \cite[Lemma~2.1]{ST76} and \cite[Theorem~2.5]{St78}).
-Notice that M.~Stein uses the first of the above $4$ equivalent ways of writing down the decomposition while A.~Suslin and M.~Tulenbaev use the 4th.
-\begin{thm}\label{thm:DennisVaserstein}
-Let $\Phi$ be a reduced irreducible root system not equal to $\rE_8$ and let $\{ r, s \}$ denote the labels of some pair of distinct endnodes of the Dynkin diagram of $\Phi$
-such that $\{ r, s\} \neq \{ 1,2 \}$ for $\Phi=\rE_\ell$. Denote by $d$ the distance between $r$ and $s$ on the Dynkin diagram.
-Then the relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\,e. $\E(\Phi, R, I) = A_{rs}$ 
-under the following assumption on $I$:
-\begin{enumerate}
- \item $\asr(I) \leq d$ for $\Phi=\rF_4$ or $\Phi=\rE_\ell$, $\{r, s\} = \{1, \ell \}$,
- \item $\sr(I) \leq d$, otherwise.
-\end{enumerate}
 
@@
 %\rF_4                                & 4    & 1      & \asr(I)\leqslant 3 \end{array}\]
-\end{thm}
+
 Using identities~\ref{rel:h-comm}--\ref{rel:h-w} it is easy to show that Dennis---Vaserstein decomposition is a consequence of Gauss decomposition (see \cref{thm:srRI1}).

### 2015-10-07 gauss.tex
Added reference on Abe '69
Fixed references to Abe
Fixes from 05.10.15 meeting
Moved Gauss and DV theorems to the introduction

@@
-The proof of Gauss decomposition presented below is similar to the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
-
+The proof of Gauss decomposition presented below is similar to the absolute case (cf. with the proof of~\cite[Theorem~5.1]{Sm12}).
 \begin{prop}\label{thm:Gauss}
@@
 \begin{multline*}
-Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi,R,I) \cdot x_\alpha(-\xi) X_{\alpha}(I) \cdot \E(\Delta_i,R,I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) =\\
+Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi,R,I) \cdot x_\alpha(-\xi) \cdot X_{\alpha}(I) \cdot \E(\Delta_i,R,I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) =\\
 = \Hh(\Phi, R, I) \cdot \E(\Delta_i,R,I) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) = Y.
@@
 
-\begin{thm}\label{thm:srRI1}
-Let $\Phi$ be a root system, let $I$ be an ideal of arbitrary commutative ring $R$ such that $\sr(I)=1$.
-Then the relative elementary Chevalley group admits Gauss decomposition
-\[ \E(\Phi,R,I) = \Hh(\Phi,R,I) \cdot \U(\Phi,I) \cdot \U(\Phi^-,I) \cdot \U(\Phi,I). \]
-\end{thm}
-\begin{proof}
+\begin{proof}[Proof of \cref{thm:srRI1}]
 In view of the above proposition it suffices to prove that Gauss decomposition of length $3$ holds for $\Phi=\rA_1$.

### 2015-10-07 paper.tex
Moved Gauss and DV theorems to the introduction

@@
 \begin{abstract} 
-We formulate and prove relative versions of Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
+We formulate and prove relative versions of several classical decompositions known in the theory of Chevalley groups over commutative rings.
+% Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
 As an application we obtain upper estimates for the width of principal congruence subgroups in terms of several families of generators.
@@
 \section{Introduction}\label{sec:intro}
-Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots.
-Denote by $G=\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over $R$ and by $\E(\Phi, R)$ its \emph{elementary subgroup}, 
-i.\,e. the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
-For an ideal $I \trianglelefteq R$ denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (also called \emph{principal congruence subgroup}) of level $I$, 
+%Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots.
+Let $\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over arbitarary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup} (see e.\,g.~\cite{St78, VP, S}).
+%i.\,e. the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
+For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (aka \emph{principal congruence subgroup}) of level $I$, 
 i.\,e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection $R\rightarrow R/I$.
 
-The main goal of the present paper is to study parabolic factorizations of Chevalley groups and their analogues for principal congruence subgroups $\G(\Phi, R, I)$.
-By a parabolic factorization we mean a decomposition of $G$ into a product of several parabolic and unipotent subgroups.
-To be more specific, we study relative analogues of the following three kinds of decompositions:
-\begin{itemize}
-\item \emph{Gauss decomposition,} i.\,e. a decomposition of the form $\E(\Phi,R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup,
-      and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
-\item \emph{Bass---Kolster decomposition} $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
-      $\Par_i$, $\Par_i^-$ are the opposite maximal parabolic subgroups of $\G$ corresponding to $i$-th simple root of $\Phi$ and $\U_i$, $\U_i^-$ are their unipotent radicals;
-\item \emph{Dennis---Vaserstein decomposition} $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$,
-      where $\EP_i$ denotes the subgroup generated by root unipotents $x_\alpha(\xi)$ contained in $\Par_i$.
-\end{itemize}
+The main goal of the present paper is to obtain relative analogues of several classical parabolic factorizations of Chevalley groups (i.\,e.
+factorizations into a product of several parabolic and unipotent subgroups)
+%To be more specific, we study relative analogues of the following three kinds of decompositions:
+%\begin{itemize}
+%\item \emph{Gauss decomposition,} i.\,e. a decomposition of the form $\E(\Phi,R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup,
+%      and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
+%\item \emph{Bass---Kolster decomposition} $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
+%      $\Par_i$, $\Par_i^-$ are the opposite maximal parabolic subgroups of $\G$ corresponding to $i$-th simple root of $\Phi$ and $\U_i$, $\U_i^-$ are their unipotent radicals;
+%\item \emph{Dennis---Vaserstein decomposition} $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$,
+%      where $\EP_i$ denotes the subgroup generated by root unipotents $x_\alpha(\xi)$ contained in $\Par_i$.
+%\end{itemize}
 %TODO: Insert some links to VIP's papers :)
@@
 %Their another advantage is that they prove useful in the study of asymptotical properties of Chevalley groups. We are going to discuss this theme in more detail below.
+
+Our first result is a relative version Gauss decomposition.
+All the notation for the subgroups appearing in this theorem and the other theorems stated below is explained in~\ref{sec:prelim}.
+\begin{thm}\label{thm:srRI1}
+Let $\Phi$ be a root system, let $I$ be an ideal of arbitrary commutative ring $R$ such that $\sr(I)=1$.
+Then the relative elementary Chevalley $\E(\Phi, R, I)$ group admits the following decomposition
+\[ \E(\Phi,R,I) = \Hh(\Phi,R,I) \cdot \U(\Phi,I) \cdot \U(\Phi^-,I) \cdot \U(\Phi,I). \]
+\end{thm}
+The special case $I=R$ of the \cref{thm:srRI1} was obtained by the second named author in~\cite{Sm12}.
+We also note that in special case of a semilocal ring $R$ the above theorem was proved by E.~Abe and K.~Suzuki, see~\cite[Proposition~2.3]{AbeSuzNormalSubgroups}.
+
+Our next main result is a relative Dennis---Vaserstein decomposition which holds for a broader class of groups of rings as compared to \cref{thm:srRI1}.
+\begin{thm}\label{thm:DennisVaserstein}
+Let $\Phi \neq \rE_8$ be a reduced irreducible root system and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$ the distance between which equals $d$.
+Assume that $\Phi$ and $I$ satisfy either of the following assumptions:
+\begin{enumerate}
+ \item $\asr(I) \leq d$ for $\Phi=\rF_4$ or $\Phi=\rE_\ell$, $\{r, s\} = \{1, \ell \}$,
+ \item $\sr(I) \leq d$, otherwise.
+\end{enumerate}
+Then $\E(\Phi, R, I)$ factors as $\EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s) \cdot \EP_s(R, I).$ \end{thm}
+Even in the special case $I=R$ the above theorem contains several new cases as compared to M.~Stein's Theorems~2.5, 4.1, see~\cite{St78}.
+The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev (cf.~\cite[Lemma~2.1]{ST76}).
+
+The condition $\asr(I)$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable range} of D.~Estes and J.~Ohm which does not depend on the ambient ring $R$ (see section~\ref{sec:rel-asr}).
 
@@
 \begin{thm}\label{thm:spin-sln-prod}
-Assume that $\sr(I) \leqslant 2$ then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ copies of its subgroups of type $\rA_{\ell-1}$.
+Assume that $\sr(I) \leqslant 2$ then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ copies of its (regularly embedded) subgroups of type $\rA_{\ell-1}$.
 \end{thm}

### 2015-10-07 paper.tex
Rewriting introduction

@@
 As an application we obtain upper estimates for the width of principal congruence subgroups in terms of several families of generators.
+Some of our results are new even in the absolute case and were previously studied only for groups over finite fields.
 \end{abstract}
@@
 %Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots.
-Let $\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over arbitarary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup} (see e.\,g.~\cite{St78, VP, S}).
-%i.\,e. the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
+Let $\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over arbitarary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup}
+i.\,e. the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
 For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (aka \emph{principal congruence subgroup}) of level $I$, 
@@
 
-The main goal of the present paper is to obtain relative analogues of several classical parabolic factorizations of Chevalley groups (i.\,e.
-factorizations into a product of several parabolic and unipotent subgroups)
+In our theorems we also use the notion of the \emph{relative elementary Chevalley group} $\E(\Phi, R, I)$.
+Recall that $\E(\Phi, R, I)$ is defined as the normal closure of the subgroup generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi,\ \xi \in I \}$.
+
+Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
+It is a classical result of J.~Tits and L.~Vaserstein (see e.\,g.~\cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
+the set of elements $\mathcal{Z} = \{ z_\alpha(s,\xi) \mid \alpha \in \Phi,\ s\in I,\ \xi \in R \}.$
+
+The following recent result of A.~Stepanov served as a starting point for the present paper.
+All the notation and definitions used below are explained properly in section~\ref{sec:prelim}.
+\begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
+Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be any parabolic subset of roots.
+Let $\Sigma_S$ be the special part of $S$, then $\E(\Phi, R, I)$ is generated as an abstract group by the following set of generators
+$$\mathcal{Z}(\Sigma) = \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s \in I,\ \xi \in R, \alpha\in \Sigma \}.$$ \end{prop}
+
+The first goal of the present paper is to obtain relative analogues of several classical parabolic factorizations of Chevalley groups 
+(i.\,e. factorizations into a product of several parabolic and unipotent subgroups)
 %To be more specific, we study relative analogues of the following three kinds of decompositions:
@@
 
-Our first result is a relative version Gauss decomposition.
-All the notation for the subgroups appearing in this theorem and the other theorems stated below is explained in~\ref{sec:prelim}.
+Our first result is a relative version of Gauss decomposition formulated in terms of the \emph{stable rank} of the ideal $I$ (see section~\ref{sec:stability-conditions} for the definition)
 \begin{thm}\label{thm:srRI1}
@@
 \end{thm}
-The special case $I=R$ of the \cref{thm:srRI1} was obtained by the second named author in~\cite{Sm12}.
-We also note that in special case of a semilocal ring $R$ the above theorem was proved by E.~Abe and K.~Suzuki, see~\cite[Proposition~2.3]{AbeSuzNormalSubgroups}.
+In the special case when $I$ is contained in the Jacobson radical of $R$ the above theorem boils down to~\cite[Proposition~2.3]{AbeSuzNormalSubgroups}. 
+Notice that the special case $I=R$ was treated by the second named author in~\cite{Sm12}.
 
@@
 \end{enumerate}
-Then $\E(\Phi, R, I)$ factors as $\EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s) \cdot \EP_s(R, I).$ \end{thm}
-Even in the special case $I=R$ the above theorem contains several new cases as compared to M.~Stein's Theorems~2.5, 4.1, see~\cite{St78}.
+Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s) \cdot \EP_s(R, I).$ \end{thm}
+Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5, 4.1]{St78}.
 The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev (cf.~\cite[Lemma~2.1]{ST76}).
 
-The condition $\asr(I)$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable range} of D.~Estes and J.~Ohm which does not depend on the ambient ring $R$ (see section~\ref{sec:rel-asr}).
+The condition $\asr(I)$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable rank} of D.~Estes and J.~Ohm which does not depend on the ambient ring $R$ (see section~\ref{sec:rel-asr}).
 
@@
 On the other hand, much less is known about the width of the relative group $\G(\Phi, R, I)$ and the relative elementary group $\E(\Phi, R, I)$.
-Recall that the \emph{relative elementary group} $\E(\Phi, R, I)$ is defined as the normal closure of $\E(\Phi, I)$ in $\E(\Phi, R)$, where
-$\E(\Phi, I)$ denotes the subgroup of $\G_{sc}(\Phi, R)$ generated by all elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in I$, i.\,e. $\E(\Phi, R, I) = \E(\Phi, I)^{\E(\Phi, R)}$.
-
-Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
-It is a classical result of J.~Tits and L.~Vaserstein (see e.\,g.~\cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
-the set of elements $\mathcal{Z} = \{ z_\alpha(s,\xi) \mid \alpha \in \Phi,\ s\in I,\ \xi \in R \}.$
-
-In fact, one can choose a smaller set of generators for $\E(\Phi, R, I)$. 
-Let $\Sigma$ be any special subset of $\Phi$, (e.\,g. the set of simple roots $\Pi$ or the special part of $\Sigma_S$ of some parabolic subset of roots $S$, see section~\ref{sec:rootsys}).
-Set $$\mathcal{X} = \{ x_\alpha(s) \mid \alpha\in \Phi,\ s\in I\};\ \ \mathcal{Z}(\Sigma) = \{ z_\alpha(s, \xi) \mid s \in I,\ \xi \in R, \alpha\in \Sigma \} \cup \mathcal{X}.$$
-
-Now we are ready to state a recent result of A.~Stepanov.  
-\begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
-Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$ and let $S \subset \Phi$ be any parabolic subset of roots.
-Then $\E(\Phi, R, I)$ is generated as an abstract group by $\mathcal{Z}(\Sigma_S)$.
-\end{prop}
 

### 2015-10-07 paper.tex
Rewriting introduction

@@
 
-In our theorems we also use the notion of the \emph{relative elementary Chevalley group} $\E(\Phi, R, I)$.
-Recall that $\E(\Phi, R, I)$ is defined as the normal closure of the subgroup generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi,\ \xi \in I \}$.
+In our theorems we also use the notion of the \emph{relative elementary Chevalley group} $\E(\Phi, R, I) \leq \G(\Phi, R, I)$.
+Recall that $\E(\Phi, R, I)$ is defined as the normal closure in $\E(\Phi, R)$ of the subgroup generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi,\ \xi \in I \}$.
 
 Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
-It is a classical result of J.~Tits and L.~Vaserstein (see e.\,g.~\cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
+It is a classical result of J.~Tits and L.~Vaserstein (see~\cite{Tits76}, \cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
 the set of elements $\mathcal{Z} = \{ z_\alpha(s,\xi) \mid \alpha \in \Phi,\ s\in I,\ \xi \in R \}.$
@@
 The following recent result of A.~Stepanov served as a starting point for the present paper.
-All the notation and definitions used below are explained properly in section~\ref{sec:prelim}.
+The notation for the subgroups involved in the statements of our results below is introduced properly in section~\ref{sec:prelim}.
 \begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
 Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be any parabolic subset of roots.
-Let $\Sigma_S$ be the special part of $S$, then $\E(\Phi, R, I)$ is generated as an abstract group by the following set of generators
-$$\mathcal{Z}(\Sigma) = \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s \in I,\ \xi \in R, \alpha\in \Sigma \}.$$ \end{prop}
+Let $\Sigma_S$ be the special part of $S$, then $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$, where
+$$\mathcal{Z}(\Sigma) = \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s \in I,\ \xi \in R,\ \alpha\in \Sigma \}.$$ \end{prop}
 
-The first goal of the present paper is to obtain relative analogues of several classical parabolic factorizations of Chevalley groups 
-(i.\,e. factorizations into a product of several parabolic and unipotent subgroups)
+The purpose of this paper is two-fold. 
+First, we obtain relative analogues of several classical parabolic factorizations of Chevalley groups such as Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
+Secondly, we apply these factorizations to the study of various bounded generation properties of Chevalley groups over rings.
 %To be more specific, we study relative analogues of the following three kinds of decompositions:
@@
 \end{enumerate}
-Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s) \cdot \EP_s(R, I).$ \end{thm}
+Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$ \end{thm}
 Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5, 4.1]{St78}.
@@
 We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
-The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $x_\alpha(\xi)$ has been extensively studied in a number of works (see e.\,g.
+%The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $x_\alpha(\xi)$ has been extensively studied in a number of works (see e.\,g.
 \cite{CK83, Ka82, Tavgen91, Mo07, VseUnitrZ1p, VavSmSuUnitrEng}).
-Summarizing results of these works, one can hope that such width is finite only for rather narrow classes of rings of number-theoretic nature, e.\,g.
+%Summarizing results of these works, one can hope that such width is finite only for rather narrow classes of rings of number-theoretic nature, e.\,g.
 localizations of Dedeking rings of arithmetic type.
-For example, W.~van der Kallen has shown that the width of $\SL(3,R)$ is infinite already for a Euclidean ring $R=\mathbb{C}[t]$.
+%For example, W.~van der Kallen has shown that the width of $\SL(3,R)$ is infinite already for a Euclidean ring $R=\mathbb{C}[t]$.
 
-On the other hand, much less is known about the width of the relative group $\G(\Phi, R, I)$ and the relative elementary group $\E(\Phi, R, I)$.
+%On the other hand, much less is known about the width of the relative group $\G(\Phi, R, I)$ and the relative elementary group $\E(\Phi, R, I)$.
 
-Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\G(\Phi, R, I)$ in terms of certain subsets of $\mathcal{Z}$.
+Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of relative Chevalley groups in terms of Tits generators.
 \begin{thm}\label{thm:width} Let $\Phi$ be an irreducible root system, and let $I$ be an ideal of a commutative ring $R$.
@@
 \begin{thm}\label{thm:spin-sln-prod}
-Assume that $\sr(I) \leqslant 2$ then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ copies of its (regularly embedded) subgroups of type $\rA_{\ell-1}$.
+Assume that $\sr(I) \leqslant 2$ then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of (regularly embedded) subgroups of type $\rA_{\ell-1}$.
 \end{thm}

### 2015-10-08 paper.tex
Finished rewriting introduction

@@
 \title {Decompositions of relative Chevalley groups}
-\keywords {Chevalley groups, principal congruence subgroups, stability for $\K_1$, bounded generation, subsystem factorizations, $\SL_2$-factorizations.
-{\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
+\keywords {Chevalley groups, principal congruence subgroups, stability for $\K_1$, bounded generation, $\SL_2$-factorizations. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
 \author {Sergey Sinchuk, Andrei Smolensky}
@@
 
-The condition $\asr(I)$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable rank} of D.~Estes and J.~Ohm which does not depend on the ambient ring $R$ (see section~\ref{sec:rel-asr}).
+The condition $\asr(I) \leq d$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
 
@@
 
-Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of relative Chevalley groups in terms of Tits generators.
+Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\E(\Phi, R)$ in terms of Tits generators and is, thus, a quantitative analogue of \cref{prop:Stepanov}
+and a relative analogue of the results of~\cite{CK83, Tavgen91, Mo07, VseUnitrZ1p, VavSmSuUnitrEng}.
 \begin{thm}\label{thm:width} Let $\Phi$ be an irreducible root system, and let $I$ be an ideal of a commutative ring $R$.
 \begin{enumerate}
+\item Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type in some global field $k$ having a real embedding. 
+Assume that $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
 \item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
@@
 \end{alignat*}
-\item Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type in some global field $k$ having a real embedding. 
-Assume that $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
 \end{enumerate}
 \end{thm}
-Notice that a recent result of U.~Hadad and D.~W.~Morris \cite[Theorem~1.6]{Ha12} implies finiteness of $W(\E(\Phi, R, I), \mathcal{Z}(\Phi^+))$
-for $R=\mathbb{Z}$ and $\Phi=\rA_\ell$.
+The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{Tavgen93, TavgenThesis}),
+while for the second and the third assertion we give a direct proof.
+Compare \cref{thm:width} also with a recent result of U.~Hadad and D.~W.~Morris \cite[Theorem~1.6]{Ha12} which asserts that 
+$W(\SL(n, \mathbb{Z}, I), \mathcal{Z}(\Pi))$ is finite for any ideal $I \leq \mathbb{Z}$ and $n \geq 3$.
 
@@
 More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
+
 In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
-In fact, Gauss decomposition (see~\cite{Sm12}) implies a similar factorization for the elementary subgroup $\E(\Phi, R)$ 
-with $3|\Phi^+|$ factors for arbitrary commutative ring of stable rank $1$.
-
-In the linear and symplectic case the above results can be extended to even larger class of rings (which e.\,g. includes all Dedekind rings).
+In fact, in the context of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
+Our next result further extends this to even larger class of rings (which e.\,g. includes ideals of all Dedekind rings).
 \begin{thm}\label{thm:SL2width}
@@
 
-Yet another application of parabolic factorizations concerns subsystem factorizations of Chevalley groups formulated in terms of submaximal subgroups of type $\rA_\ell$.
-In case when $R=I$ is a field this question was studied by N.~Nikolov in \cite{NikProdDecomp}. 
+Our yet another application of parabolic factorizations concerns product decompositions of Chevalley groups formulated in terms of subgroups of type $\rA_\ell$ of submaximal rank.
+Recall that in \cite{NikProdDecomp} N.~Nikolov proves the following result. 
 \begin{thm*} Let $G$ be a classical Chevalley group (of normal or twisted type) of rank $n$ over a finite field.
@@
 
-It is also classically known that over an arbitrary field $F$ the group $\SL_{n+1}(F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
-On the other hand, from the classical Dennis---Vaserstein theorem (see~\cite{Va69} and \cite[Lemma~2.1]{ST76})
-it follows that $\SL_{n+1}(R, I)$ is a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
-Using another Dennis---Vaserstein type factorization we obtain the following result.
+It is classically known that over an arbitrary field $F$ the group $\SL_{n+1}(F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
+On the other hand, one immediately obtains from \cref{thm:DennisVaserstein} that $\SL_{n+1}(R, I)$ factors into a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
+
+Applying \cref{thm:DennisVaserstein} and generalizing (in the special case $\Phi=\rD_\ell$) Nikolov's \cite[Proposition~1]{NikProdDecomp} to arbitrary rings we obtain the following result.
 \begin{thm}\label{thm:spin-sln-prod}

### 2015-10-08 dennis-vaserstein.tex
DV and intro fixes

@@
 Now if $\alpha$ lies in $\Phi^+ \setminus \Sigma_r \cap \Sigma_s$ it is contained either in $\Delta_r$ or in $\Delta_s$.
-Assume, for example, the latter. It remains to notice that $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}.$
+Assume, for example, the latter. By Levi decomopsition $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}.$
 \end{proof}
@@
 Denote by $L_{rs}$ the set consisting of all the elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
-It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and that $N_{rs}$ normalizes $L_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+Obviously, $L_{rs}$ contains $\EP_r(R, I)$, and it is easy to see that $N_{rs}$ normalizes $L_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
 \begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
@@
 
-Finally, the last inclusion follows from the same transitivity argument as above and the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
-For $\Phi=\rB_\ell$ one has to additionally use the fact that
+The last inclusion follows from the same transitivity argument as above and the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
+For $\Phi=\rB_\ell$ one has to additionally use the Chevalley commutator formula~\eqref{rel:CCF-specBC}:
 $$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere$$ 
@@
 
-From a consideration of weight diagrams (see~\cite{PSV98}) we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (cf.~Figure~\ref{fig:table}).
-\begin{figure}
+From a consideration of the weight diagrams (see~\cite{PSV98}) we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
+\begin{table}[htb]
 \[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} c @{\qquad} c @{\qquad} c}
@@
 \rF_4                                & (4, 1)        & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
- \caption[Table]{List of representations involved in the proof of \cref{thm:DennisVaserstein}.} \label{fig:table}
-\end{figure}
-Consider the subset $B \in \E(\Delta_r, R, I)$ consisting of elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
+ \caption{List of representations involved in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
+\end{table}
+
+Consider the subset $B \subset \E(\Delta_r, R, I)$ consisting of elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
 Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$

### 2015-10-08 paper.tex
DV and intro fixes

--- 2015-10-07 paper.tex
@@
 \begin{thm}\label{thm:spin-sln-prod}
-Assume that $\sr(I) \leqslant 2$ then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of (regularly embedded) subgroups of type $\rA_{\ell-1}$.
+Assume that $\sr(I) \leqslant 2$. Then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of (regularly embedded) subgroups of type $\rA_{\ell-1}$.
 \end{thm}

### 2015-10-08 congrsubgr-boundgen.tex

@@
 
-\begin{proof}[Proof of \cref{thm:width}] The first statement of the theorem is contained in \cref{lemma:srRI1_width}.
-The second and third statement follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}
+\begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.
+The the first and the third assertions follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}

### 2015-10-08 dennis-vaserstein.tex
Fixed Smolensky comments

@@
 %\rF_4                                & 4    & 1      & \asr(I)\leqslant 3 \end{array}\]
-
-Using identities~\ref{rel:h-comm}--\ref{rel:h-w} it is easy to show that Dennis---Vaserstein decomposition is a consequence of Gauss decomposition (see \cref{thm:srRI1}).
-In particular, for rings of stable rank $1$ and groups of rank $2$ (e.\,g. $\Phi=\rG_2$) it is preferable to use Gauss decomposition since it is more accurate.
-
 Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$ consisting of elements which normalize the subset $A_{rs}$, i.\,e.
@@
 \begin{proof}
-Notice that for every $i$ the factor $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence a fortiori it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
+Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence a fortiori it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
 Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r,s\}}, R)$ we obtain the assertion of the lemma for $\alpha \in \Delta_{\{r, s\}}$.
@@
 Now if $\alpha$ lies in $\Phi^+ \setminus \Sigma_r \cap \Sigma_s$ it is contained either in $\Delta_r$ or in $\Delta_s$.
-Assume, for example, the latter. By Levi decomopsition $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}.$
+Assume, for example, the latter. By Levi decomposition we have $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$
+which again implies the assertion of the lemma.
 \end{proof}
@@
 \begin{proof}[Proof of \cref{thm:DennisVaserstein}]
+First of all, notice that in the special case $\Phi=\rG_2$ \cref{thm:DennisVaserstein} formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
+Since $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, 
+it suffices to consider only the choices for $\Phi$, $r$ and $s$ listed in the table below.
+\begin{table}[htb]
+\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} c @{\qquad} c @{\qquad} c}
+\Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\Delta_r$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
+\rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\
+\rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 2  \\ 
+\rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
+\rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
+\rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \\
+\rF_4                                & (4, 1)        & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
+ \caption{List of representations involved in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
+\end{table}
+
 Denote by $L_{rs}$ the set consisting of all the elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
@@
 
-The first step of the proof is show that $N_{rs}$ contains sufficiently many elements. 
-This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke the stability conditions for the first time.
+The first step of the proof is to show that $N_{rs}$ contains sufficiently many elements. 
+This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke stability conditions for the first time.
 We show that $N_{rs}$ contains the root subgroup $X_{-\alpha\ssub{r}}(R)$, which together with \cref{lemma:dv-normal} and \cref{item-egen} immediately implies that $N_{rs}$ contains the Levi subgroup $\E(\Delta_s, R)$ and hence the extended Weyl group $\widetilde{W}(\Delta_s)$.
@@
 The next goal is to demonstrate the inclusion $\U(\Sigma_s, R) \subseteq N_{rs}$ (which implies $\EP_s(R) \subseteq N_{rs}$).
-All the possibilities for $(\Phi, r, s)$ mentioned in the statement of the theorem fall into one of the following three categories:
+All the possibilities for $\Phi$, $r$ and $s$ appearing in the statement of the theorem fall into one of the following three cases:
 \begin{enumerate}
@@
 The last inclusion follows from the same transitivity argument as above and the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
-For $\Phi=\rB_\ell$ one has to additionally use the Chevalley commutator formula~\eqref{rel:CCF-specBC}:
+For $\Phi=\rB_\ell$ one has to once again apply Chevalley commutator formula~\eqref{rel:CCF}:
 $$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere$$ 
@@
 \begin{proof}
-Let $(\pi, V)$ be the irreducible representation of $\G(\Phi, R)$ with the highest weight $\varpi_s$.
+Let $\pi$ be the irreducible representation of $\G(\Phi, R)$ with the highest weight $\varpi_s$ (see Table~\ref{table:dv-reps}).
 Notice that $\Delta_r$ is an irreducible classical root system of type $\rA_\ell$, $\rC_\ell$ or $\rD_\ell$.
@@
 From a consideration of the weight diagrams (see~\cite{PSV98}) we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
-\begin{table}[htb]
-\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} c @{\qquad} c @{\qquad} c}
-\Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\Delta_r$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
-\rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
-\rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
-\rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\
-\rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 2  \\ 
-\rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
-\rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
-\rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \\
-\rF_4                                & (4, 1)        & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
- \caption{List of representations involved in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
-\end{table}
 

### 2015-10-08 dennis-vaserstein.tex
Some fixes in the introduction

@@
 \begin{proof}[Proof of \cref{thm:DennisVaserstein}]
-First of all, notice that in the special case $\Phi=\rG_2$ \cref{thm:DennisVaserstein} formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
+First of all, notice that in the case $\Phi=\rG_2$ \cref{thm:DennisVaserstein} formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
 Since $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, 
-it suffices to consider only the choices for $\Phi$, $r$ and $s$ listed in the table below.
+it suffices to consider only the following choices for $\Phi$, $r$ and $s$.
 \begin{table}[htb]

### 2015-10-08 paper.tex
Some fixes in the introduction

@@
 
-\title {Decompositions of relative Chevalley groups}
+\title {Decompositions of congruence subgroups of Chevalley groups}
 \keywords {Chevalley groups, principal congruence subgroups, stability for $\K_1$, bounded generation, $\SL_2$-factorizations. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
@@
 It is a classical result of J.~Tits and L.~Vaserstein (see~\cite{Tits76}, \cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
-the set of elements $\mathcal{Z} = \{ z_\alpha(s,\xi) \mid \alpha \in \Phi,\ s\in I,\ \xi \in R \}.$
+the set of elements $\mathcal{Z}(\Phi) = \{ z_\alpha(s,\xi) \mid s\in I,\ \xi \in R,\ \alpha \in \Phi\}.$
 
@@
 In the special case when $I$ is contained in the Jacobson radical of $R$ the above theorem boils down to~\cite[Proposition~2.3]{AbeSuzNormalSubgroups}. 
-Notice that the special case $I=R$ was treated by the second named author in~\cite{Sm12}.
+The special case $I=R$ was treated by the second named author in~\cite{Sm12}.
 
-Our next main result is a relative Dennis---Vaserstein decomposition which holds for a broader class of groups of rings as compared to \cref{thm:srRI1}.
+The next main result is a relative Dennis---Vaserstein decomposition which holds for a broader class of groups of rings as compared to \cref{thm:srRI1}.
 \begin{thm}\label{thm:DennisVaserstein}
@@
 and a relative analogue of the results of~\cite{CK83, Tavgen91, Mo07, VseUnitrZ1p, VavSmSuUnitrEng}.
-\begin{thm}\label{thm:width} Let $\Phi$ be an irreducible root system, and let $I$ be an ideal of a commutative ring $R$.
+\begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.
 \begin{enumerate}
-\item Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type in some global field $k$ having a real embedding. 
-Assume that $\Phi$ is classical of rank $\geqslant2$, then $W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
-\item If $\sr(I) = 1$, then $W(\E(\Phi,R,I),\mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1$;
-\item Let $p$ be a prime integer, set $R = \mathbb{Z}[\sfrac{1}{p}]$ and assume $\Phi$ is classical. Then under the assumption of the Generalized Riemann Hypothesis one has
-%TODO: Now check the coefficients of \rk(\Phi) in the expression below
+\item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
+$W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
+\item If $\sr(I) = 1$ and $\Phi$ is arbitrary irreducible root system then 
+\[W(\E(\Phi,R,I),\mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1;\]
+\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime number $p$, then under the assumption of the Generalized Riemann Hypothesis one has
 \begin{alignat*}{2}
@@
 while for the second and the third assertion we give a direct proof.
-Compare \cref{thm:width} also with a recent result of U.~Hadad and D.~W.~Morris \cite[Theorem~1.6]{Ha12} which asserts that 
+Compare \cref{thm:width} with a recent result of U.~Hadad and D.~W.~Morris \cite[Theorem~1.6]{Ha12} which asserts that 
 $W(\SL(n, \mathbb{Z}, I), \mathcal{Z}(\Pi))$ is finite for any ideal $I \leq \mathbb{Z}$ and $n \geq 3$.
@@
 
-Applying \cref{thm:DennisVaserstein} and generalizing (in the special case $\Phi=\rD_\ell$) Nikolov's \cite[Proposition~1]{NikProdDecomp} to arbitrary rings we obtain the following result.
+Applying \cref{thm:DennisVaserstein} and generalizing Nikolov's \cite[Proposition~1]{NikProdDecomp} in the special case $\Phi=\rD_\ell$ to arbitrary rings we obtain the following result.
 \begin{thm}\label{thm:spin-sln-prod}
-Assume that $\sr(I) \leqslant 2$. Then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of (regularly embedded) subgroups of type $\rA_{\ell-1}$.
+Assume that $\sr(I) \leqslant 2$. Then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of its (regularly embedded) subgroups of type $\rA_{\ell-1}$.
 \end{thm}
+
+The rest of the article is organized as follows.
+In sections \ref{sec:prelim}--\ref{sec:stability-conditions} we introduce principal notation pertaining to Chevalley groups and stability conditions.
+In section \ref{sec:factorizations} we prove our parabolic factorizations and thus obtain Theorems~\ref{thm:srRI1}, \ref{thm:DennisVaserstein} and \ref{thm:SL2width}.
+Finally, we treat bounded generation and product decompositions separately in section~\ref{sec:applications} where Theorems~\ref{thm:width} and \ref{thm:spin-sln-prod} are proved.
 
@@
 
-A root subset $S\subseteq \Phi$ is called {\it parabolic} (resp. {\it reductive}, resp. {\it special}) if $\Phi=S \cup -S$ (resp. $S = -S$, resp. $S \cap -S=\varnothing$).
-Any parabolic subset $S \subseteq \Phi$ can be decomposed into the disjoint union of its reductive and special part, i.e. 
+A proper closed subset of roots $S\subseteq \Phi$ is called {\it parabolic} (resp. {\it reductive}, resp. {\it special}) if $\Phi=S \cup -S$ (resp. $S = -S$, resp. $S \cap -S=\varnothing$).
+Any parabolic subset $S \subseteq \Phi$ can be decomposed into the disjoint union of its \emph{reductive} and \emph{special} parts, i.e. 
 $S = \Sigma_S \sqcup \Delta_S$, where $\Sigma_S \cap (-\Sigma_S) = \varnothing$, $\Delta_S = -\Delta_S$.
@@
 
-\section{Applications} %\label{sec:applications}
+\section{Applications} \label{sec:applications}
 \subsection{Bounded generation}\label{sec:boundgen}

### 2015-10-08 dennis-vaserstein.tex
Fixed case F_4 in DV

@@
 \begin{proof}[Proof of \cref{thm:DennisVaserstein}]
-First of all, notice that in the case $\Phi=\rG_2$ \cref{thm:DennisVaserstein} formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
-Since $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, 
-it suffices to consider only the following choices for $\Phi$, $r$ and $s$.
+First of all, notice that in the case $\Phi=\rG_2$ the assertion of the theorem formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
+Since $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$.
 \begin{table}[htb]
-\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\qquad} c @{\qquad} c @{\qquad} c}
-\Phi                                 & (s,r)         & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\Delta_r$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
-\rA_\ell,\ \ell\geqslant 2           & (1,\ell)      & \ell+1         & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
-\rB_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell+1        & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
-\rC_\ell,\ \ell\geqslant 2           & (1,\ell)      & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\
-\rD_\ell,\ \ell\geqslant 4           & (1,\ell)      & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 2  \\ 
-\rD_\ell,\ \ell\geqslant 4           & (\ell,\ell-1) & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
-\rE_\ell,\ \ell=6,7                  & (\ell,2)      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
-\rE_\ell,\ \ell=6,7                  & (\ell,1)      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \\
-\rF_4                                & (4, 1)        & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
- \caption{List of representations involved in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
+\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\quad} c @{\qquad} c @{\qquad} c @{\qquad} c}
+\Phi                                 & s    &r      & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\Delta_r$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
+\rA_\ell,\ \ell\geqslant 2           & 1    &\ell   & \ell+1         & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rB_\ell,\ \ell\geqslant 2           & 1    &\ell   & 2\ell+1        & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rC_\ell,\ \ell\geqslant 2           & 1    &\ell   & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\
+\rD_\ell,\ \ell\geqslant 4           & 1    &\ell   & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 2  \\ 
+\rD_\ell,\ \ell\geqslant 4           & \ell &\ell-1 & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
+\rE_\ell,\ \ell=6,7                  & \ell &2      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
+\rE_\ell,\ \ell=6,7                  & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \\
+\rF_4                                & 4    &1     & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
+ \caption{List of the cases considered in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
 \end{table}
@@
 Denote by $L_{rs}$ the set consisting of all the elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
-Obviously, $L_{rs}$ contains $\EP_r(R, I)$, and it is easy to see that $N_{rs}$ normalizes $L_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
 \begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
@@
 The next goal is to demonstrate the inclusion $\U(\Sigma_s, R) \subseteq N_{rs}$ (which implies $\EP_s(R) \subseteq N_{rs}$).
-All the possibilities for $\Phi$, $r$ and $s$ appearing in the statement of the theorem fall into one of the following three cases:
+All the possibilities for $\Phi$, $s$ and $r$ fall into one of the following three cases:
 \begin{enumerate}
@@
 
-In view of \cref{prop:Stepanov} to prove the theorem it suffices to show that $L_{rs}$ contains the generating set $\mathcal{Z}(\Sigma_s^-) \cup \mathcal{X}$ of $\E(\Phi, R, I)$.
+In view of \cref{prop:Stepanov} to prove the theorem it suffices to show that $L_{rs}$ contains the generating set $\mathcal{Z}(\Sigma_s^-)$ of $\E(\Phi, R, I)$.
 From $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)}$ and \eqref{rel:NnormL} it follows that we only have to show $\mathcal{X} \subseteq L_{rs}$.
@@
 The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram containing the vertex marked $\varpi_s$.
-Clearly, $\Gamma$ consists of weights from $\Lambda(\pi')$ incident to the removed bonds.
+Clearly, $\Gamma$ consists of the weights of $\Lambda(\pi')$ incident to the removed bonds.
 
@@
 \begin{proof}
-Consider the subset $C \subseteq \EP_s(R, I)$ consisting of matrices such that matrix components $v=(g_{i,2})$, $i=2,\ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
+Consider the subset $C \subseteq \EP_s(R, I)$ consisting of elements satisfying the following condition:
+\begin{itemize}
+ \item \textsc{Case $\Phi=\rC_\ell$.} Matrix entries $(g_{i,2})$, $i=2,\ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
+ \item \textsc{Case $\Phi=\rF_4$.} Matrix entries $(g_{\lambda, \lambda}, \ldots, g_{\lambda, \lambda - \alpha_3 - \alpha_2 - \alpha_1})$, where $\lambda = \varpi_4 - \alpha_4$ (see~\cite[Fig.~26]{PSV98}),
+                                     form an $I$-unimodular column of height $4$. \end{itemize}
+
 Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot C$.
-
-By \cref{item:asrUnipC} and \cref{cor:embeddingBD} (applied to the subgroup $\G(\Delta_s, R, I)$) we find for every $g \in \EP_s(R, I)$ a matrix $x \in \U(\Sigma_r \cap \Delta_s, I)$ such that $xg \in C$.
+By \cref{item:asrUnipC} (in the case $\Phi=\rC_\ell$) or \cref{cor:embeddingBD} (in the case $\Phi=\rF_4$) applied to the subgroup $\G(\Delta_s, R, I)$ 
+we find for every $g \in \EP_s(R, I)$ an element $x \in \U(\Sigma_r \cap \Delta_s, I)$ such that $xg \in C$.  
 Notice that one immediately gets the equality $A_{rs} = A'$ from this.

### 2015-10-08 paper.tex
Fixed case F_4 in DV

@@
 \item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
-$W(\G(\Phi,\mathcal{O}_S,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
+$W(\G(\Phi,R,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
 \item If $\sr(I) = 1$ and $\Phi$ is arbitrary irreducible root system then 
@@
 Recall that in \cite{NikProdDecomp} N.~Nikolov proves the following result. 
-\begin{thm*} Let $G$ be a classical Chevalley group (of normal or twisted type) of rank $n$ over a finite field.
-Then $G$ equals the product of at most $200$ conjugates of $\SL_n$. \end{thm*}
+\begin{thm*} Let $G$ be a classical Chevalley group (of normal or twisted type) of rank $\ell$ over a finite field $F$.
+Then $G$ can be presented as a product of at most $200$ conjugates of its subgroups of type $\rA_{\ell-1}$. \end{thm*}
 
@@
 The rest of the article is organized as follows.
-In sections \ref{sec:prelim}--\ref{sec:stability-conditions} we introduce principal notation pertaining to Chevalley groups and stability conditions.
+In sections \ref{sec:prelim}--\ref{sec:stability-conditions} we introduce principal notation and prove basic facts pertaining to Chevalley groups over rings and stability conditions.
 In section \ref{sec:factorizations} we prove our parabolic factorizations and thus obtain Theorems~\ref{thm:srRI1}, \ref{thm:DennisVaserstein} and \ref{thm:SL2width}.

### 2015-10-09 stability-conditions.tex
Removed unneccessary corollary and replaced reference

@@
 
-\subsection{Relative absolute stable rank}\label{sec:rel-asr}
+\subsection{Relativization of the absolute stable rank}\label{sec:rel-asr}
 For a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ denote by $\mathfrak{J}(a)$ the intersection of all maximal ideals of $R$ containing $a_1,\ldots,a_n$.
@@
 
-A priori our definition of condition $\ASR_n(I)$ depends on $R$.
+A priori our definition of $\ASR_n(I)$ depends on $R$.
 Below we will see that, in fact, there is no such dependence.
+The following lemma is a relativization of~\cite[Lemma~8.2]{MKV}. 
 \begin{lemma}\label{lemma:relative-asr-unimod}
@@
 Obviously, the second statement of \cref{lemma:relative-asr-unimod} does not depend on $R$, hence, as suggested by the notation, $\asr(I)$ is independent of $R$.
-As another corollary of \cref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$.
-\begin{cor}[A.~Bak, {cf.~\cite[\S~1]{Pl98}}] For a commutative ring $R$ the following statements are equivalent:
-\begin{enumerate}
- \item\label{asr_Stein} $R$ satisfies $\ASR_n(R)$;
- \item\label{asr_Bak} For any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Umd(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for all $t\in R$.
-\end{enumerate}
-\end{cor}
+%As another corollary of \cref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$.
+%\begin{cor}[A.~Bak, {cf.~\cite[\S~1]{Pl98}}] For a commutative ring $R$ the following statements are equivalent:
+%\begin{enumerate}
+% \item\label{asr_Stein} $R$ satisfies $\ASR_n(R)$;
+% \item\label{asr_Bak} For any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Umd(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for all $t\in R$.
+%\end{enumerate}
+%\end{cor}
 

### 2015-10-09 paper.tex
Tiny fixes

@@
 
-Applying \cref{thm:DennisVaserstein} and generalizing Nikolov's \cite[Proposition~1]{NikProdDecomp} in the special case $\Phi=\rD_\ell$ to arbitrary rings we obtain the following result.
+Applying \cref{thm:DennisVaserstein} and proving a more accurate version of \cite[Proposition~1]{NikProdDecomp} in the special case $\Phi=\rD_\ell$ we obtain the following result.
 \begin{thm}\label{thm:spin-sln-prod}

### 2015-10-09 paper.tex
Finished proofreading 5.2

--- 2015-10-08 paper.tex
@@
 It is classically known that over an arbitrary field $F$ the group $\SL_{n+1}(F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
-On the other hand, one immediately obtains from \cref{thm:DennisVaserstein} that $\SL_{n+1}(R, I)$ factors into a product of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
+On the other hand, one immediately obtains from \cref{thm:DennisVaserstein} and surjective stability for linear $\K_1$ that $\SL_{n+1}(R, I)$ factors into a product
+of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
 

### 2015-10-09 subsystem-factorizations.tex
"Varying v and w..." part
Finished proofreading 5.2

@@
 %\end{thm*}
-As indicated in the introduction, the Dennis---Vaserstein decomposition gives the following result.
-\begin{lemma}
-Assume $\sr(I)\leqslant n-1$. Then $\SL(n+1,R,I)$ is a product of at most $5$ subgroups isomorphic to $\SL(n,R,I)$.
-\end{lemma}
-\begin{proof}
-By the Dennis---Vaserstein decomposition one can present $\SL(n+1,R,I)$ as a product
-\[ \SL(n+1,R,I) =  \Par_1\cdot X_{n1}\cdot\Par_n=S_1\U_1\cdot X_{n1}\cdot\U_n S_n, \]
-where $S_1$ and $S_n$ are two obvious embeddings of $\SL(n,R,I)$ in $\SL(n+1,R,I)$, avoiding respectively the first and the last row and column.
+%As indicated in the introduction, the Dennis---Vaserstein decomposition gives the following result.
+%\begin{lemma}
+%Assume $\sr(I)\leqslant n-1$. Then $\SL(n+1,R,I)$ is a product of at most $5$ subgroups isomorphic to $\SL(n,R,I)$.
+%\end{lemma}
+%\begin{proof}
+%By the Dennis---Vaserstein decomposition one can present $\SL(n+1,R,I)$ as a product
+%\[ \SL(n+1,R,I) =  \Par_1\cdot X_{n1}\cdot\Par_n=S_1\U_1\cdot X_{n1}\cdot\U_n S_n, \]
+%where $S_1$ and $S_n$ are two obvious embeddings of $\SL(n,R,I)$ in $\SL(n+1,R,I)$, avoiding respectively the first and the last row and column.
 Now $\U_1=(\U_1\cap S_n)\cdot X_{1n}$ and $U_n= X_{1n}\cdot(U_n\cap S_1)$, while $X_{1n}X_{n1}X_{1n}\in S_1^{w_{12}(1)}$.
-\end{proof}
-We will now elaborate on the case $\Phi=\rD_\ell$ to show that the Dennis---Vaserstein decomposition is suitable for handling other Chevalley groups, albeit with a stronger assumption on the base ring.
+%\end{proof}
+%We will now elaborate on the case $\Phi=\rD_\ell$ to show that the Dennis---Vaserstein decomposition is suitable for handling other Chevalley groups, albeit with a stronger assumption on the base ring.
 
@@
 \begin{lemma}\label{lemma:nikolov-type-dl}
-Let $\Phi=\rD_\ell$, $\ell\geq 4$.
+Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $R$ be arbitrary ring.
 There exist an element $y\in\E(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell, I)\subset[\U(\Delta_\ell^-, I),y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
@@
 Since $\U(\Sigma_\ell, I)$ is abelian we can decompose it as $\U(\Sigma_\ell, I)=\U(\Sigma_\ell\setminus B, I) \cdot \U(B, I)$. 
-Set $y=\prod_{\beta\in B}x_\beta(1)$. We will now show that $\U(\Sigma_\ell\setminus B, I)\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I)$.
+Set $y=\prod_{\beta\in B}x_\beta(1)$. 
+We will now show by induction on $\ell$ that 
+\begin{equation}\label{eq:ind-stat} \U(\Sigma_\ell\setminus B, I)\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I). \end{equation}
+The induction base in the cases $\ell=2,3$ is trivial.
 
@@
 \[ [v,x_{\beta_1}(1)]\in\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1, I), \quad [w,x_{\beta_1}(1)]\in\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}, I). \]
-%TODO: <add text from thesis>
-Varying $v$ and $w$ one can obtain any element of $\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1)$ and $\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\})$ respectively.
-This is easy to see by using \eqref{eq:comm-ab-c} repeatedly and the fact that $\U(\Sigma_2^-\cap\Delta_\ell)$ commutes with $\U(\Sigma_\ell)$.
-Now by the Levi decomposition
-\[ {}^v\!\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}) \equiv \U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2). \]
-Thus we have shown that
-\[ [\U(\Sigma_2^-)\cdot\U(\Delta_{2,\ell}),y] \equiv \U((\Sigma_{1,2}\cap\Sigma_\ell)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2), \]
-and this reduces the problem to the $\rD_{\ell-2}$-subsystem $\Delta_{1,2}$.
-So we can carry the induction on the rank of the subsystem, and construct for any given $a\in\U(\Sigma_\ell\setminus B)$ an element $b\in\U(\Delta_\ell^-)$ such that $a\in[b,y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-),y]\cdot\U(B)$.
-%TODO: </add text from thesis>
+Every element of $\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1, I)$ (resp. $\U(\Sigma_1\cap\Sigma_\ell\setminus\{\beta_1\}, I)$) can be obtained as above for a suitable choice of $v$ (resp. $w$).
+Indeed, set $v=x_\gamma(\xi_\gamma)\cdot v'$, $\gamma=-\alpha_1-\alpha_2$, $v' \in \U(\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell \setminus \{\gamma\})$.
+Using relation \eqref{eq:comm-ab-c} and the fact that $\U(\Sigma_2^-\cap\Delta_\ell)$ commutes with $\U(\Sigma_\ell)$ we get that:
+\begin{multline*} [v, x_{\beta_1}(1)] = [x_\gamma(\xi_\gamma)\cdot v', x_{\beta_1}(1)] = {}^{x_\gamma(\xi_\alpha)}[v', x_{\beta_1}(1)] \cdot [x_\gamma(\xi_\gamma), x_{\beta_1}(1)] = \\
+ = [v', x_{\beta_1}(1)]\cdot x_{\beta_1-\alpha_1-\alpha_2}(\xi_\gamma) = \ldots = \prod_{\mathclap{\alpha\in\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell}} x_{\beta_1+\alpha}(\xi_\alpha).
+\end{multline*}
+It remains to note that $\Sigma_2 \cap \Sigma_\ell \cap \Delta_1 = \beta_1 + \Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell$. The same argument works for $[w, x_{\beta_1}(1)]$.
+Direct calculation using the commutator formula shows that
+\[ {}^v\!\U(\Sigma_1\cap\Sigma_\ell\setminus\{\beta_1\}, I) \equiv \U(\Sigma_1\cap\Sigma_\ell\setminus\{\beta_1\}, I) \bmod \U(\Sigma_\ell\cap\Delta_2, I). \]
+Summing up the above arguments, we get that
+\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2,\ell}^-, I),y] \equiv \U((\Sigma_{1,2}\cap\Sigma_\ell)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2, I). \]
+hence \eqref{eq:ind-stat} follows from the induction hypothesis (applied to $\Delta_{1,2} \cong \rD_{\ell-2}$).
 
-It remains to notice that the assertion of the lemma follows from~\cref{lemma:nikolov-weyl}.
-%It remains to note that the roots $\pm\beta_i$ lie inside a maximal root subsystem of type $\rA_1+\ldots+\rA_1+\rD_3$.
-%All such subsystems are conjugate under the action of the Weyl group, so there exist an element $w\in W(\Phi)$ such that
-%$w(\beta_1)=\alpha_1$, $w(\beta_2)=\alpha_3$, $w(\beta_3)=\alpha_5$ and so on, so that all of 
-%$w(\beta_i)$ lie in $\Delta_\ell^+$.
+Finally, we have found $a\in\U(\Sigma_\ell\setminus B, I)$ and $b\in\U(\Delta_\ell^-, I)$
+such that $$a\in[b,y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I).$$
+Now the assertion of the lemma follows from~\cref{lemma:nikolov-weyl}.
 \end{proof}
+
 \begin{proof}[Proof of \cref{thm:spin-sln-prod}]
-By \cref{thm:DennisVaserstein} one has a decomposition
-\[ \Spin(2\ell,R,I) = \Par_{\ell-1}\cdot\U_{\ell-1,\ell}^-\cdot\Par_{\ell} = \G(\Delta_{\ell-1})\cdot\U(\Sigma_{\ell-1})\cdot\U(\Sigma_{\ell-1,\ell}^-)\cdot\U(\Sigma_{\ell})\cdot\G(\Delta_\ell). \]
-By \cref{lemma:nikolov-type-dl} there exist elements $y_1,y_2,y_3\in\G(\rD_\ell,R)$ and $w_1,w_2,w_3\in\widetilde{W}(\rD_\ell)$ such that
-\begin{align*}
-& \U(\Sigma_{\ell-1}) \subset \U(\Delta_{\ell-1}^-) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+), \\
-& \U(\Sigma_\ell) \subset {}^{w_2}\!\U(\Delta_\ell^+) \cdot {}^{y_2}\!\U(\Delta_\ell^-) \cdot \U(\Delta_\ell^-), \\
-& \U(\Sigma_{\ell-1,\ell}^-) \subset \U(\Delta_\ell^+) \cdot {}^{y_3}\!\U(\Delta_\ell^+) \cdot {}^{w_3}\!\U(\Delta_\ell^-).
-\end{align*}
-Thus $\G(\rD_\ell,R,I)$ is a product of $9$ subgroups isomorphic to $\G(\rA_{\ell-1},R,I)\cong\SL(\ell,R,I)$.
-\end{proof}
+Set $L = \E(\Delta_\ell, R, I) \leq \E(\rD_\ell, R, I)$ and denote by $\sigma$ the automorphism of $\G(\rD_\ell, R)$ induced by the sole diagram automorphism of the Dynkin diagram of $\rD_\ell$.
+By \cref{thm:DennisVaserstein} one has
+\begin{multline*}
+\E(\rD_\ell,R,I) = \EP_{\ell}(R, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot\EP_{\ell-1}(R, I) = \\
+= L \cdot\U(\Sigma_{\ell}, I)\cdot\U(\Sigma_{\ell-1} \cap \Sigma_{\ell}^-, I)\cdot \left(L \cdot \U(\Sigma_{\ell}, I) \right)^\sigma.
+\end{multline*}  
+Now using \cref{lemma:nikolov-type-dl} one can find $y_1,y_2\in\G(\rD_\ell,R)$ and $w_1,w_2\in\widetilde{W}(\rD_\ell)$ such that
+\begin{align*} & L \cdot \U(\Sigma_{\ell}, I) \subset L \cdot \U(\Delta_{\ell-1}^-, I) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-, I) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+, I), \\
+& \U(\Sigma_{\ell-1,\ell}^-, I) \subset \U(\Delta_\ell^+, I) \cdot {}^{y_2}\!\U(\Delta_\ell^+, I) \cdot {}^{w_2}\!\U(\Delta_\ell^-, I). \end{align*} 
+Thus $\E(\rD_\ell,R,I)$ is a product of at most $9$ conjugates of $L \cong \E(\rA_{\ell-1}, R, I)$. \end{proof}

### 2015-10-09 dennis-vaserstein.tex

@@
 For $\Phi=\rB_\ell$ one has to once again apply Chevalley commutator formula~\eqref{rel:CCF}:
-$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere$$ 
+\[ X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
 \end{proof}

### 2015-10-09 bass-kolster.tex
Minor fix

@@
 \begin{cor}\label{cor:bass-kolster-iterated}
-Under the assumptions on $\Phi$, $I$ and $N'$ stated below every element of $\G(\Phi,R,I)$ can be factored into a product of 
-one element of $\G(\langle\pm\alpha_\ell\rangle,R,I)\cong\SL(2,R,I)$ and at most $N'$ elements of $\mathcal{Z}(\Sigma_\ell)$:
+Assume that $\Phi$ and $I$ satisfy one of the following assumptions
 \[\begin{array}{l@{\quad}l@{\quad}l}
@@
 \end{array}\]
+Then every element of $\G(\Phi,R,I)$ can be factored into a product of one element of $\G(\langle\pm\alpha_\ell\rangle,R,I)\cong\SL(2,R,I)$ and at most $N'$ elements of $\mathcal{Z}(\Sigma_\ell)$:
 \end{cor}

### 2015-10-09 paper.tex
Scrapper explicit formulae for root unipotents

@@
 The action of $x_\alpha(\xi)$ can be visualized on a weight diagram of $\pi$ as follows. Blah-blah-blah
-\textbf{TODO: Write a passage about this} %TODO:
+%\textbf{TODO: Write a passage about this}
 
@@
 
-Although it is possible to fix signs of the action constants in the statement of \cref{lemma:Matsumoto} in the general situation (see~\cite{V08}),
-for our purposes it suffices to do that only for classical groups in their natural representations.
+Although it is possible to fix signs of the action constants in the statement of \cref{lemma:Matsumoto} (see~\cite{V08}), we make no attempt to do this in this article.
 
-\begin{rem}
-Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
-In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ (for some choice of $\lambda_1,\lambda_2$) instead of $x_{\lambda_1-\lambda_2}(\xi)$.
-For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$. \end{rem}
-For classical groups there is a standard way to fix the signs.
-In case $\Phi=\rC_\ell$ the long and short root unipotents are
-\begin{align*}
-& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
-& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
-\end{align*}
-Here $\varepsilon_i$ is the sign of $i$.
-In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
-\begin{align*}
-& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
-& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
-\end{align*}
+Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ such that $\lambda_1-\lambda_2\in \Phi$.
+It will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
+For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
+
+%\begin{rem}
+%For classical groups there is a standard way to fix the signs.
+%In case $\Phi=\rC_\ell$ the long and short root unipotents are
+%\begin{align*}
+%& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
+%& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
+%\end{align*}
+%Here $\varepsilon_i$ is the sign of $i$.
+%In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
+%\begin{align*}
+%& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
+%& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
+%\end{align*}
 

### 2015-10-09 subsystem-factorizations.tex
Subsystem factorizations exposition fixes

@@
 Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\,e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1,\ldots, \lfloor \ell/2 \rfloor$.
-Denote by $B$ the set of all $\beta_k$. From the definition it is clear that elements of $B$ are mutually perpendicular to each other.
+Denote by $B$ the set of all $\beta_k$. From the definition it is clear that elements of $B$ are mutually orthogonal to each other.
 The roots $\beta_k$ can also be defined by explicit formulae:
@@
 \begin{lemma}\label{lemma:nikolov-type-dl}
-Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $R$ be arbitrary ring.
+Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $R$ be a commutative ring.
 There exist an element $y\in\E(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell, I)\subset[\U(\Delta_\ell^-, I),y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
@@
 \begin{equation}\label{eq:ind-stat} \U(\Sigma_\ell\setminus B, I)\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I). \end{equation}
-The induction base in the cases $\ell=2,3$ is trivial.
+The induction base in the cases $\ell=2, 3$ is trivial.
 
-Notice that $\beta_1$ is the only root of $\Phi$ satisfying $m_2(\beta_1)=2$ therefore the commutator formula~\eqref{rel:CCF} implies
+Notice that $\beta_1$ is the only root of $\Phi$ satisfying $m_2(\beta_1)=2$, therefore the commutator formula~\eqref{rel:CCF} implies
 \[ \bigl[\U(\Delta_2^-, I),x_{\beta_1}(1)\bigr]=1. \]
-Since the set $A=(\Sigma_2^-\cap\Delta_\ell)+(B\setminus\{\beta_1\})$ is disjoint from $\Phi$ 
-(for $\alpha\in A$ one has $m_2(\alpha)=-1$ and $m_\ell(\alpha)=1$)
-we also get from~~\eqref{rel:CCF} that
+There is no root of the form $\gamma=\alpha+\beta$ with $\alpha\in\Sigma_2^-\cap\Delta_\ell$ and $\beta\in B\setminus\{\beta_1\}$, because such a root $\gamma$ must satisfy $m_2(\gamma)=-1$ and $m_\ell(\gamma)=1$.
+Thus~\eqref{rel:CCF} gives
 \[\Bigl[\U(\Sigma_2^-\cap\Delta_\ell, I),\prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
-Since $B\setminus\{\beta_1\}\subset\Sigma_\ell\cap\Delta_2$, the above identities imply
+Since $B\setminus\{\beta_1\}\subset\Sigma_\ell\cap\Delta_2$, the above two identities imply
 \[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2,\ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell\cap\Delta_2, I).
@@
 \[ [v,x_{\beta_1}(1)]\in\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1, I), \quad [w,x_{\beta_1}(1)]\in\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}, I). \]
-Every element of $\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1, I)$ (resp. $\U(\Sigma_1\cap\Sigma_\ell\setminus\{\beta_1\}, I)$) can be obtained as above for a suitable choice of $v$ (resp. $w$).
+Every element of $\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1, I)$ (resp.
+$\U(\Sigma_1\cap\Sigma_\ell\setminus\{\beta_1\}, I)$) can be expressed as such a commutator for a suitable choice of $v$ (resp.
+$w$).
 Indeed, set $v=x_\gamma(\xi_\gamma)\cdot v'$, $\gamma=-\alpha_1-\alpha_2$, $v' \in \U(\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell \setminus \{\gamma\})$.
 Using relation \eqref{eq:comm-ab-c} and the fact that $\U(\Sigma_2^-\cap\Delta_\ell)$ commutes with $\U(\Sigma_\ell)$ we get that:
-\begin{multline*} [v, x_{\beta_1}(1)] = [x_\gamma(\xi_\gamma)\cdot v', x_{\beta_1}(1)] = {}^{x_\gamma(\xi_\alpha)}[v', x_{\beta_1}(1)] \cdot [x_\gamma(\xi_\gamma), x_{\beta_1}(1)] = \\
+\begin{multline*}
+[v, x_{\beta_1}(1)] = [x_\gamma(\xi_\gamma)\cdot v', x_{\beta_1}(1)] = {}^{x_\gamma(\xi_\alpha)}[v', x_{\beta_1}(1)] \cdot [x_\gamma(\xi_\gamma), x_{\beta_1}(1)] = \\
 = [v', x_{\beta_1}(1)]\cdot x_{\beta_1-\alpha_1-\alpha_2}(\xi_\gamma) = \ldots = \prod_{\mathclap{\alpha\in\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell}} x_{\beta_1+\alpha}(\xi_\alpha).
@@
 Summing up the above arguments, we get that
-\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2,\ell}^-, I),y] \equiv \U((\Sigma_{1,2}\cap\Sigma_\ell)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2, I). \]
-hence \eqref{eq:ind-stat} follows from the induction hypothesis (applied to $\Delta_{1,2} \cong \rD_{\ell-2}$).
+\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2,\ell}^-, I),y] \equiv \U((\Sigma_{1,2}\cap\Sigma_\ell)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2, I), \]
+hence the inclusion~\eqref{eq:ind-stat} follows from the induction hypothesis (applied to $\Delta_{1,2} \cong \rD_{\ell-2}$).
 

### 2015-10-09 bass-kolster.tex
Ref to VBRA for the weight diagrams

@@
 \begin{proof}
-\begin{figure}[htb]\label{fig:bass-kolster}
+The assertion can be obtained by iteratively applying (for a total of $\ell-1$ times) the decomposition of \cref{thm:BassKolster}.
+The improved estimate for $\Phi=\rA_\ell$ (resp.
+$\rC_\ell$) follows from the fact that it suffices to make only two (resp.
+three) additions to shorten the unimodular column in the first step of the proof of \cref{thm:BassKolster}.
+\end{proof}
+\begin{figure}[hb]\label{fig:bass-kolster}
 \[\begin{tikzcd}[row sep=tiny]
@@
 \end{tikzcd}\] \caption{Reductions used in the proof of \cref{cor:bass-kolster-iterated} and \cref{thm:SL2width}} \end{figure}
-The assertion can be obtained by iteratively applying (for a total of $\ell-1$ times) the decomposition of \cref{thm:BassKolster}.
-The improved estimate for $\Phi=\rA_\ell$ (resp.
-$\rC_\ell$) follows from the fact that it suffices to make only two (resp.
-three) additions to shorten the unimodular column in the first step of the proof of \cref{thm:BassKolster}.
-\end{proof}
 \begin{proof}[Proof of \cref{thm:SL2width}]

### 2015-10-09 bass-kolster.tex
\Sigma^\pm

@@
 By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for
-\[ h_1 = x_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} x_{i,-1}(c_i) \in \U(\Sigma_1^-, I). \]
+\[ h_1 = x_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} x_{i,-1}(c_i) \in \U(\Sigma_1^+, I). \]
 
 We can find $f_1, f_2,\ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
-%TODO: Determine exact sign
 Set $\xi = v''_1-v''_{-1}-1 \in I$,
-\[ h_2 = x_{-1,1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1,i}(\xi f_i) \in \U(\Sigma_1, I). \]
+\[ h_2 = x_{-1,1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1,i}(\xi f_i) \in \U(\Sigma_1^-, I). \]
 Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\eqref{eq1}.
@@
 In the case $\Phi=\rD_\ell$ from the proof of \cref{thm:BassKolster} one obtains that
-\begin{equation*} \G(\Phi,R,I) =  \U(\Sigma_\ell,I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1,I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z \cdot \U(\Sigma_1^-,I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I).
+\begin{equation*} \G(\Phi,R,I) =  \U(\Sigma_\ell^+,I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1,I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z \cdot \U(\Sigma_1^-,I) \cdot \U(\Sigma_1^+,I) \cdot \G(\Delta_1,R,I).
 \end{equation*}
-We can present an element $g$ of $\U(\Sigma_\ell, I)$ as a product of $g_1 \in \U(\Sigma_{\{1,2\}} \cap \Sigma_\ell)$ and $g_2\in \U(\Delta_{\{1,2\}}\cap \Sigma_\ell)$.
+We can present an element $g$ of $\U(\Sigma_\ell^+, I)$ as a product of $g_1 \in \U(\Sigma_{\{1,2\}^+} \cap \Sigma_\ell^+)$ and $g_2\in \U(\Delta_{\{1,2\}}\cap \Sigma_\ell^+)$.
 An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one)

### 2015-10-09 dennis-vaserstein.tex
Minor fix
\Sigma^\pm

@@
 A_{rs} := \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
-= \U(\Sigma_r, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \hspace{5em} \\
-\hspace{5em} = \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s, I) = \\
+= \U(\Sigma_r^+, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \hspace{5em} \\
+\hspace{5em} = \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s^+, I) = \\
 = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).
@@
 
-Now if $\alpha$ lies in $\Phi^+ \setminus \Sigma_r \cap \Sigma_s$ it is contained either in $\Delta_r$ or in $\Delta_s$.
+Now if $\alpha$ lies in $\Phi^+ \setminus \Sigma_r^+ \cap \Sigma_s^+$ it is contained either in $\Delta_r$ or in $\Delta_s$.
 Assume, for example, the latter. By Levi decomposition we have $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$
@@
 
-The next goal is to demonstrate the inclusion $\U(\Sigma_s, R) \subseteq N_{rs}$ (which implies $\EP_s(R) \subseteq N_{rs}$).
+The next goal is to demonstrate the inclusion $\U(\Sigma_s^+, R) \subseteq N_{rs}$ (which implies $\EP_s(R) \subseteq N_{rs}$).
 All the possibilities for $\Phi$, $s$ and $r$ fall into one of the following three cases:
@@
 
-Applying \cref{lemma:uraction} to the subsystem $\Delta_r$ we find
+Let $g$ be an element of $\E(\Delta_r, R, I)$. Applying \cref{lemma:uraction} to the subsystem $\Delta_r$ we find
 $x\in\U(\Delta_r^+, I)$, $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
@@
 X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
-\subseteq B \cdot \U(\Sigma_r, I) \cdot \EP_s(R, I) =
+\subseteq B \cdot \U(\Sigma_r^+, I) \cdot \EP_s(R, I) =
 B \cdot \EP_s(R, I).
@@
 By \cref{item:asrUnipC} (in the case $\Phi=\rC_\ell$) or \cref{cor:embeddingBD} (in the case $\Phi=\rF_4$) applied to the subgroup $\G(\Delta_s, R, I)$ 
-we find for every $g \in \EP_s(R, I)$ an element $x \in \U(\Sigma_r \cap \Delta_s, I)$ such that $xg \in C$.  
+we find for every $g \in \EP_s(R, I)$ an element $x \in \U(\Sigma_r^+ \cap \Delta_s, I)$ such that $xg \in C$.  
 Notice that one immediately gets the equality $A_{rs} = A'$ from this.
@@
 
-By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s \cap \Delta_r, I)$ such that $(y \cdot g)_{\varpi_s,\varpi_s - \alpha_s} = 0$.
+By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s^+ \cap \Delta_r, I)$ such that $(y \cdot g)_{\varpi_s,\varpi_s - \alpha_s} = 0$.
 Consequently, for every $g\in C$ one has

### 2015-10-09 paper.tex
Ref to VBRA for the weight diagrams
\Sigma^\pm

@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
-We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i,j}=\Sigma_{\{i,j\}}$ etc.
+We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i,j}^\pm=\Sigma_{\{i,j\}}^\pm$, etc.
 
@@
 
-The action of $x_\alpha(\xi)$ can be visualized on a weight diagram of $\pi$ as follows. Blah-blah-blah
-%\textbf{TODO: Write a passage about this}
+The action of $x_\alpha(\xi)$ can be visualized on a weight diagram of $\pi$, see~\cite{PSV98}.
 
@@
 For a special subset of roots $\Sigma\subseteq \Phi$ we denote by $\U(\Sigma, I)$ the subgroup spanned by all $x_{\alpha}(I)$ for $\alpha\in \Sigma$. Let $J\subset\Pi$.
-The subgroup $\U(\Sigma_J, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I)$ is a subgroup called a \emph{standard parabolic subgroup}.
+The subgroup $\U(\Sigma_J^+, I)$ are normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I)$ is a subgroup called a \emph{standard parabolic subgroup}.
 The following two equalities will be referred to in the sequel as {\it Levi decomposition}: 
-\begin{equation} \label{rel:Levi-decomp} \EP_J(R, I) = \U(\Sigma_J, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I). \end{equation}
+\begin{equation} \label{rel:Levi-decomp} \EP_J(R, I) = \U(\Sigma_J^+, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I). \end{equation}
 When $J = \{ \alpha_s \}$ for some $1 \leq s\leq \ell$ we use shorthand $\EP_s(R, I)$ for $\EP_{\{s\}}(R, I)$.

### 2015-10-09 stability-conditions.tex
\Sigma^\pm

@@
 For $b \in M(\ell, I)$ set $g(b)=\left(\begin{smallmatrix} e_\ell & p \cdot b \\ 0 & e_{\ell} \end{smallmatrix}\right)$.
-Clearly, if $b$ is symmetric then $g(b)$ lies in $\U(\Sigma_\ell, I)\leq \E(\rC_\ell, R, I)$.
+Clearly, if $b$ is symmetric then $g(b)$ lies in $\U(\Sigma_\ell^+, I)\leq \E(\rC_\ell, R, I)$.
 
@@
  Denote by $i$ the standard embedding $\G(\rB_{\ell-1}, R, I) \hookrightarrow \G(\rD_\ell, R, I)$. 
- If $\asr(I) \leqslant \ell-1$ then for every $I$-unimodular column $v \in \Ums(2\ell, I)$ there exists $g \in \U(\Sigma_{\ell-1}, I) \leq \E(\rB_{\ell-1}, R, I)$ such that
+ If $\asr(I) \leqslant \ell-1$ then for every $I$-unimodular column $v \in \Ums(2\ell, I)$ there exists $g \in \U(\Sigma_{\ell-1}^+, I) \leq \E(\rB_{\ell-1}, R, I)$ such that
  the upper half of the vector $i(g) \cdot v$ forms an $I$-unimodular column of height $\ell$.
@@
 \begin{proof}
- The assertion follows from the fact that for every $u \in \U(\Sigma_\ell, I) \leq \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that $uu'$ lies in the image of $i$. 
+ The assertion follows from the fact that for every $u \in \U(\Sigma_\ell^+, I) \leq \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that $uu'$ lies in the image of $i$. 
  Indeed, denote by $\sigma$ the symmetry of the Dynkin diagram of $\rD_\ell$,
- and decompose $u$ into the product $u_1 \cdot u_2$, $u_1 \in \U(\Sigma_\ell\cap\Delta_{\ell-1}, I)$, $u_2 \in \U(\Sigma_\ell \cap \Sigma_{\ell-1}, I)$.
+ and decompose $u$ into the product $u_1 \cdot u_2$, $u_1 \in \U(\Sigma_\ell^+\cap\Delta_{\ell-1}, I)$, $u_2 \in \U(\Sigma_\ell^+ \cap \Sigma_{\ell-1}^+, I)$.
  Then one takes $u' = \sigma(u_1)$.
 
- Now by \cref{item:asrUnipD} one finds a suitable $u \in \U(\Sigma_\ell, I) \leqslant \E(\rD_\ell, R, I)$ which makes the upper half unimodular,
+ Now by \cref{item:asrUnipD} one finds a suitable $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ which makes the upper half unimodular,
  and since $u'$ lies in $\G(\Delta_\ell, R, I)$, the upper half remains unimodular.
@@
 \textsc{Case $\Phi=\rC_\ell$.} 
-Applying \cref{item:asrUnipC} we find $x \in \U(\Sigma_\ell, I)$ such that the upper half $v'_+$ of $v' = x \cdot v$ is unimodular.
+Applying \cref{item:asrUnipC} we find $x \in \U(\Sigma_\ell^+, I)$ such that the upper half $v'_+$ of $v' = x \cdot v$ is unimodular.
 Set $g(a) = \left(\begin{smallmatrix} e_\ell & 0 \\ p \cdot a & e_{\ell} \end{smallmatrix}\right)$.

### 2015-10-09 subsystem-factorizations.tex
\Sigma^\pm

@@
 Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $R$ be a commutative ring.
-There exist an element $y\in\E(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell, I)\subset[\U(\Delta_\ell^-, I),y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
+There exist an element $y\in\E(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell^+, I)\subset[\U(\Delta_\ell^-, I),y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
 \end{lemma}
 \begin{proof}
-Since $\U(\Sigma_\ell, I)$ is abelian we can decompose it as $\U(\Sigma_\ell, I)=\U(\Sigma_\ell\setminus B, I) \cdot \U(B, I)$. 
+Since $\U(\Sigma_\ell^+, I)$ is abelian we can decompose it as $\U(\Sigma_\ell^+, I)=\U(\Sigma_\ell^+\setminus B, I) \cdot \U(B, I)$. 
 Set $y=\prod_{\beta\in B}x_\beta(1)$. 
 We will now show by induction on $\ell$ that 
-\begin{equation}\label{eq:ind-stat} \U(\Sigma_\ell\setminus B, I)\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I). \end{equation}
+\begin{equation}\label{eq:ind-stat} \U(\Sigma_\ell^+\setminus B, I)\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I). \end{equation}
 The induction base in the cases $\ell=2, 3$ is trivial.
@@
 \[\Bigl[\U(\Sigma_2^-\cap\Delta_\ell, I),\prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
-Since $B\setminus\{\beta_1\}\subset\Sigma_\ell\cap\Delta_2$, the above two identities imply
-\[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2,\ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell\cap\Delta_2, I).
+Since $B\setminus\{\beta_1\}\subset\Sigma_\ell^+\cap\Delta_2$, the above two identities imply
+\[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2,\ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell^+\cap\Delta_2, I).
 \]
@@
 Since $\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $\U(\Sigma_2^-\cap\Delta_{1,\ell}, I)$ are abelian, it is easy to see that
-\[ [v,x_{\beta_1}(1)]\in\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1, I), \quad [w,x_{\beta_1}(1)]\in\U((\Sigma_1\cap\Sigma_\ell)\setminus\{\beta_1\}, I). \]
-Every element of $\U(\Sigma_2\cap\Sigma_\ell\cap\Delta_1, I)$ (resp.
-$\U(\Sigma_1\cap\Sigma_\ell\setminus\{\beta_1\}, I)$) can be expressed as such a commutator for a suitable choice of $v$ (resp.
+\[ [v,x_{\beta_1}(1)]\in\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I), \quad [w,x_{\beta_1}(1)]\in\U((\Sigma_1^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}, I). \]
+Every element of $\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I)$ (resp.
+$\U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I)$) can be expressed as such a commutator for a suitable choice of $v$ (resp.
 $w$).
 Indeed, set $v=x_\gamma(\xi_\gamma)\cdot v'$, $\gamma=-\alpha_1-\alpha_2$, $v' \in \U(\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell \setminus \{\gamma\})$.
-Using relation \eqref{eq:comm-ab-c} and the fact that $\U(\Sigma_2^-\cap\Delta_\ell)$ commutes with $\U(\Sigma_\ell)$ we get that:
+Using relation \eqref{eq:comm-ab-c} and the fact that $\U(\Sigma_2^-\cap\Delta_\ell)$ commutes with $\U(\Sigma_\ell^+)$ we get that:
 \begin{multline*}
@@
  \end{multline*}
-It remains to note that $\Sigma_2 \cap \Sigma_\ell \cap \Delta_1 = \beta_1 + \Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell$. The same argument works for $[w, x_{\beta_1}(1)]$.
+It remains to note that $\Sigma_2^+ \cap \Sigma_\ell^+ \cap \Delta_1 = \beta_1 + \Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell$. The same argument works for $[w, x_{\beta_1}(1)]$.
 Direct calculation using the commutator formula shows that
-\[ {}^v\!\U(\Sigma_1\cap\Sigma_\ell\setminus\{\beta_1\}, I) \equiv \U(\Sigma_1\cap\Sigma_\ell\setminus\{\beta_1\}, I) \bmod \U(\Sigma_\ell\cap\Delta_2, I). \]
+\[ {}^v\!\U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I) \equiv \U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I). \]
 Summing up the above arguments, we get that
-\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2,\ell}^-, I),y] \equiv \U((\Sigma_{1,2}\cap\Sigma_\ell)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell\cap\Delta_2, I), \]
+\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2,\ell}^-, I),y] \equiv \U((\Sigma_{1,2}^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I), \]
 hence the inclusion~\eqref{eq:ind-stat} follows from the induction hypothesis (applied to $\Delta_{1,2} \cong \rD_{\ell-2}$).
 
-Finally, we have found $a\in\U(\Sigma_\ell\setminus B, I)$ and $b\in\U(\Delta_\ell^-, I)$
+Finally, we have found $a\in\U(\Sigma_\ell^+\setminus B, I)$ and $b\in\U(\Delta_\ell^-, I)$
 such that $$a\in[b,y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I).$$
@@
 \E(\rD_\ell,R,I) = \EP_{\ell}(R, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot\EP_{\ell-1}(R, I) = \\
-= L \cdot\U(\Sigma_{\ell}, I)\cdot\U(\Sigma_{\ell-1} \cap \Sigma_{\ell}^-, I)\cdot \left(L \cdot \U(\Sigma_{\ell}, I) \right)^\sigma.
+= L \cdot\U(\Sigma_\ell^+, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot \big(L \cdot \U(\Sigma_\ell^+, I) \big)^\sigma.
 \end{multline*}  
 Now using \cref{lemma:nikolov-type-dl} one can find $y_1,y_2\in\G(\rD_\ell,R)$ and $w_1,w_2\in\widetilde{W}(\rD_\ell)$ such that
-\begin{align*} & L \cdot \U(\Sigma_{\ell}, I) \subset L \cdot \U(\Delta_{\ell-1}^-, I) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-, I) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+, I), \\
-& \U(\Sigma_{\ell-1,\ell}^-, I) \subset \U(\Delta_\ell^+, I) \cdot {}^{y_2}\!\U(\Delta_\ell^+, I) \cdot {}^{w_2}\!\U(\Delta_\ell^-, I). \end{align*} 
+\begin{align*} & L \cdot \U(\Sigma_\ell^+, I) \subset L \cdot \U(\Delta_{\ell-1}^-, I) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-, I) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+, I), \\
+& \U(\Sigma_{\ell-1}^-\cap\Sigma_\ell^-, I) \subset \U(\Delta_\ell^+, I) \cdot {}^{y_2}\!\U(\Delta_\ell^+, I) \cdot {}^{w_2}\!\U(\Delta_\ell^-, I). \end{align*} 
 Thus $\E(\rD_\ell,R,I)$ is a product of at most $9$ conjugates of $L \cong \E(\rA_{\ell-1}, R, I)$. \end{proof}

### 2015-10-09 paper.tex
A few technicalities in the preamble

@@
 \documentclass[12pt]{amsart}
-\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, nameref, thmtools, hyperref}
+\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, geometry, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, nameref, thmtools, hyperref}
 \usepackage[utf8]{inputenc}
+
 \usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
@@
 \usepackage[capitalize]{cleveref}
+
+\geometry{left=2.5cm, right=2.5cm, top=3cm, bottom=3cm}
 
@@
 
-\theoremstyle{plain} \declaretheorem[name=Theorem, Refname={Theorem,Theorems}]{thm} \Crefname{thm}{Theorem}{Theorems}
+\theoremstyle{plain}
+
+\newtheorem{thm}{Theorem}
+\Crefname{thm}{Theorem}{Theorems}
 \numberwithin{equation}{section}
 
-\newtheorem{lemma}{Lemma} \numberwithin{lemma}{section} \Crefname{lemma}{Lemma}{Lemmas}
-\newtheorem{cor}[lemma]{Corollary} \Crefname{cor}{Corollary}{Corollaries}
-\newtheorem{prop}[lemma]{Proposition} \Crefname{prop}{Proposition}{Propositions}
+\newtheorem{lemma}{Lemma}
+\numberwithin{lemma}{section}
+\Crefname{lemma}{Lemma}{Lemmas}
+
+\newtheorem{cor}[lemma]{Corollary}
+\Crefname{cor}{Corollary}{Corollaries}
+
+\newtheorem{prop}[lemma]{Proposition}
+\Crefname{prop}{Proposition}{Propositions}
+
 \newtheorem*{thm*}{Theorem}
 \newtheorem*{lemma*}{Lemma}
-\theoremstyle{definition} \newtheorem{dfn}[lemma]{Definition} \Crefname{dfn}{Definition}{Definitions}
-\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
-\theoremstyle{remark} \newtheorem{rem}[lemma]{Remark} \Crefname{rem}{Remark}{Remarks}
 
-%Page layout
-\textwidth 16cm 
-\textheight 22cm 
-\headheight 0.5cm 
-\evensidemargin 0.3cm 
-\oddsidemargin 0.2cm
+\theoremstyle{definition}
+
+\newtheorem{dfn}[lemma]{Definition}
+\Crefname{dfn}{Definition}{Definitions}
+\newtheorem{example}[lemma]{Example}
+\Crefname{example}{Example}{Examples}
+
+\theoremstyle{remark}
+
+\newtheorem{rem}[lemma]{Remark}
+\Crefname{rem}{Remark}{Remarks}
 

### 2015-10-09 stability-conditions.tex
SR estimates and examples

@@
 For a topological space $X$ denote by $\dim(X)$ its usual topological dimension.
-The following result gives an upper estimate for the absolute stable rank (see~\cite[Theorem~2.3]{EO}, \cite[Theorem~3.7]{MKV}).
-\begin{prop}\label{prop:asr-dimmax}
-Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets 
-$X_1\ldots, X_m$ such that $\dim(X_i)\leqslant d$ for every $i$. Then $\asr(A)\leqslant d+1$.
-\end{prop}
-%TODO: Add more comments?
-From the definition of $\asr(I)$ and the previous proposition it follows that
-\[ \sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
+The following result gives an upper estimate for the absolute stable rank (see~).
+%\begin{prop}\label{prop:asr-dimmax}
+%Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets 
+%$X_1\ldots, X_m$ such that $\dim(X_i)\leqslant d$ for every $i$. Then $\asr(A)\leqslant d+1$.
+%\end{prop}
+From the definition of $\asr(I)$ and \cite[Theorem~2.3]{EO} (or~\cite[Theorem~3.7]{MKV}) it follows that
+\begin{equation} \label{sr-estimates}
+\sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1.
+\end{equation}
 \begin{rem}
@@
 \end{rem}
-\cref{prop:asr-dimmax} shows in particular, that every Dedekind domain $R$ satisfies $\asr(R)\leqslant2$, and that $\sr(A[x])\leqslant3$ for every locally principal ring $A$.
+\begin{example}
+\eqref{sr-estimates} shows in particular, that every Dedekind domain $R$ satisfies $\asr(R)\leqslant2$, and that $\sr(A[x])\leqslant3$ for every locally principal ring $A$.
 It is shown in \cite{GruMenVasSL2ZxSL2kxy} that $\sr(\mathbb{Z}[x])=3$.
@@
 
-Another corollary of \cref{prop:asr-dimmax} is an estimate for the stable rank of the polynomial rings over a field.
+Another corollary of \eqref{sr-estimates} is an estimate for the stable rank of the polynomial rings over a field.
 Namely, $\sr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$.
@@
 On the other hand, it is known that $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ \cite{KrusenmeyerThesis} and $\sr(F[x_1,\ldots,x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
+\end{example}
 

### 2015-10-09 paper.tex
Some fixes

@@
 and choose some set of vectors $E^* = \{ e_\lambda \}_{\lambda \in \Lambda^*(\pi)}$ in such a way that 
-$E_\pi = E^* \cup \{ e_0(\alpha) \}_{\alpha \in \Delta(\pi)}$ forms a basis of $V$ in which the action of elementary root unipotents $x_\alpha(\xi)$ has particularly simple description.
+$E_\pi = E^* \cup \{ e_0(\alpha) \}_{\alpha \in \Delta(\pi)}$ forms a basis of $V$ in which the action of elementary root unipotents
+$x_\alpha(\xi)$ has particularly simple description.
 
@@
 \end{tabular} \end{lemma}
-
-The action of $x_\alpha(\xi)$ can be visualized on a weight diagram of $\pi$, see~\cite{PSV98}.
+The statement of the above lemma can be visualized using weight diagrams, see~\cite[\S~3.4]{PSV98}.
+Although it is possible to fix signs in the statement of the above lemma, we make no attempt to do this in this article and refer the reader to~\cite{V08}.
 
@@
 For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ etc.
-
-Although it is possible to fix signs of the action constants in the statement of \cref{lemma:Matsumoto} (see~\cite{V08}), we make no attempt to do this in this article.
 

### 2015-10-09 stability-conditions.tex
Some fixes

@@
 \begin{dfn}\label{dfn:j-stable}
-We say that a row $a=(a_1,\ldots,a_{n+1})\in{}^{n+1}\!I$ is {\it $\mathfrak{J}$-stable}, if there exist $c_1,\ldots,c_n\in I$ such that
+We say that a row $a=(a_1,\ldots,a_{n+1})\in{}^{n+1}\!I$ can be {\it $I$-shortened}, if there exist $c_1,\ldots,c_n\in I$ such that
 $\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1},\ldots,a_n+c_na_{n+1}).$
@@
 \begin{dfn}\label{dfn:asr}
-We say that an ideal $I$ satisfies condition $\ASR_n(I)$ if it satisfies $\SR_n(I)$ and, moreover, any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable.
+We say that an ideal $I$ satisfies condition $\ASR_n(I)$ if it satisfies $\SR_n(I)$ and, moreover, any row $a\in{}^{n+1}\!I$ can be $I$-shortened.
 \end{dfn}
@@
 It is easy to see that $\ASR_m(I)$ implies $\ASR_n(I)$ for any $n\geqslant m$. 
-By definition, the \emph{absolute relative stable rank} $\asr(I)$ is the smallest natural $n$ such that $\ASR_n(I)$ holds. 
-Similarly to the case of usual stable rank, we set $\asr(I)=\infty$ if no such $n$ exists.
+By definition, the \emph{absolute relative stable rank} $\asr(I)$ is the smallest natural $n$ such that $\ASR_n(I)$ holds (again we set $\asr(I)=\infty$ if no such $n$ exists).
 
@@
 Below we will see that, in fact, there is no such dependence.
-The following lemma is a relativization of~\cite[Lemma~8.2]{MKV}. 
+The following lemma is a relative version of~\cite[Lemma~8.2]{MKV}. 
 \begin{lemma}\label{lemma:relative-asr-unimod}
@@
 \begin{lemlist} 
-\item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable;
+\item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ can be $I$-shortened;
 \item\label{asr-bak-like} For any $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Umd(n+2,I)$ there exist $c_1,\ldots,c_n\in I$ 
@@
 \begin{proof}
-Assume first that any row $a\in{}^{n+1}\!I$ is $\mathfrak{J}$-stable. 
+Assume first that any row $a\in{}^{n+1}\!I$ can be $I$-shortened. 
 In particular for a given $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Umd(n+2,I)$ there exist $c_1,\ldots,c_n$ such that
@@
 By hypothesis, there exist $c_1,\ldots,c_n$ such that \[ v=(1+b',a'_1,\ldots,a'_n)=(1+b',a_1+c_1d,\ldots,a_n+c_nd) \] is unimodular for any $b'\in J$.
-Assume that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that all $a'_1,\ldots,a'_n$ are contained in $\mathfrak{m}$
- but at least one of the elements $d$, $a_i$ is not.
+Assume that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that all $a'_1,\ldots,a'_n$ are contained in $\mathfrak{m}$ but at least one of the elements $d$, $a_i$ is not.
 Clearly then $d\notin\mathfrak{m}$ and $I\not\subseteq \mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$ contrary to the assumption).
@@
 For a topological space $X$ denote by $\dim(X)$ its usual topological dimension.
-The following result gives an upper estimate for the absolute stable rank (see~).
+%The following result gives an upper estimate for the absolute stable rank (see~).
 %\begin{prop}\label{prop:asr-dimmax}
@@
 From the definition of $\asr(I)$ and \cite[Theorem~2.3]{EO} (or~\cite[Theorem~3.7]{MKV}) it follows that
-\begin{equation} \label{sr-estimates}
-\sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1.
-\end{equation}
-\begin{rem}
+\begin{equation} \label{sr-estimates} \sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \end{equation}
 There exist examples of rings for which the first inequality in the above formula is strict.
-Namely, there are rings of stable rank $1$ but of absolute stable rank $\geqslant2$, see~\cite{MKV}.
-However, \cite[Theorem~1.3]{MKV} shows that $\sr(R)=\asr(R)$ for any principal ideal ring $R$.
-\end{rem}
+More precisely, there are rings of stable rank $1$ but of absolute stable rank $\geqslant2$, see~\cite{MKV}.
+On the other hand, \cite[Theorem~1.3]{MKV} shows that $\sr(R)=\asr(R)$ for any principal ideal ring $R$.
 \begin{example}

### 2015-10-09 stability-conditions.tex
Rewritten example 3.6

@@
 \begin{example}
-\eqref{sr-estimates} shows in particular, that every Dedekind domain $R$ satisfies $\asr(R)\leqslant2$, and that $\sr(A[x])\leqslant3$ for every locally principal ring $A$.
-It is shown in \cite{GruMenVasSL2ZxSL2kxy} that $\sr(\mathbb{Z}[x])=3$.
-Note that $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ if $n>1$ \cite[Example after Theorem~18.2]{VasSusSerreProblem}.
+From inequality~\eqref{sr-estimates} one concludes, in particular, that 
+\begin{itemize}
+ \item $\asr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$;
+ \item $\asr(A[x])\leqslant3$ for every locally principal ring $A$;
+ \item $\asr(R)\leqslant2$ for every Dedekind domain $R$.
+\end{itemize}
+Notice also that $\sr(\mathbb{Z}[x])=3$ (see \cite{GruMenVasSL2ZxSL2kxy}) and $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ for $n>1$ (see example after~\cite[Theorem~18.2]{VasSusSerreProblem}).
 
-Another corollary of \eqref{sr-estimates} is an estimate for the stable rank of the polynomial rings over a field.
-Namely, $\sr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$.
-For certain classes of fields this upper estimate can be further improved.
-For example, if $F$ is algebraic over a finite field then $\sr(F[x_1,\ldots,x_n])\leqslant n$ by~\cite[Corollary~17.4]{VasSusSerreProblem}.
-On the other hand, it is known that $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ \cite{KrusenmeyerThesis} and $\sr(F[x_1,\ldots,x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
+For certain classes of fields the estimate for the stable rank of $R = F[x_1,\ldots, x_n]$ can be further improved.
+For example, if $F$ is algebraic over a finite field then $\sr(R)\leqslant n$ by~\cite[Corollary~17.4]{VasSusSerreProblem}.
+On the other hand, it is known that $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ (see~\cite{KrusenmeyerThesis}) and $\sr(R)=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
 \end{example}

### 2015-10-10 paper.tex
Scrapped proof of relative Chevalley---Matsumoto; some other slight improvements

@@
 \DeclareMathOperator{\sr}{sr}
+\DeclareMathOperator{\asr}{asr}
 \DeclareMathOperator{\shape}{shape}
@@
 \DeclareMathOperator{\ASR}{ASR}
-\DeclareMathOperator{\asr}{asr}
 \DeclareMathOperator{\Ums}{Ums}
@@
 \end{thm}
-In the special case when $I$ is contained in the Jacobson radical of $R$ the above theorem boils down to~\cite[Proposition~2.3]{AbeSuzNormalSubgroups}. 
-The special case $I=R$ was treated by the second named author in~\cite{Sm12}.
+In the special case when $I$ is contained in the Jacobson radical of $R$ \cref{thm:srRI1} boils down to~\cite[Proposition~2.3]{AbeSuzNormalSubgroups}. 
+We also note that the absolute case (i.\,e. $I=R$) of the theorem was treated by the second named author in~\cite{Sm12}.
 
@@
 The following lemma is a relative version of the classical result sometimes called Chevalley---Matsumoto decomposition.
+It can be deduced easily from the absolute statement (see~\cite[Theorem~1.3]{St78}).
 \begin{lemma}\label{lemma:Chevalley-Matsumoto}
-Let $\pi$ be the fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
+Let $\pi$ be a basic fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
 Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then 
@@
 \end{lemma}
-\begin{proof}
-In the absolute case ($I=R$) the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}. 
-Thus we can write $g=u_1\cdot g'\cdot u_2$, where $u_1\in\U(\Sigma_s^-,R)$, $u_2\in\U(\Sigma_s^+,R)$ and $g'\in\G(\Delta_s,R)$.
-Since $g$ lies in $\G(\Phi,R,I)$, the vector $gv^+$ is $I$-unimodular. 
-On the other hand, $g'u_2v^+=v^+$, so $u_1\in\G(\Phi,R,I)\cap\U(\Sigma_s^-,R)=\U(\Sigma_s^-,I)$.
-The matrix $g'u_2$ is an element of $\left(\G(\Delta_s,R)\U(\Sigma_s^+,R)\right)\cap\G(\Phi,R,I)$, and by Levi decomposition $u_2\in\U(\Sigma_s^+,I)$, $g'\in\G(\Delta_s,R,I)$.
-\end{proof}
+%\begin{proof}
+%In the absolute case ($I=R$) the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}. 
+%Thus we can write $g=u_1\cdot g'\cdot u_2$, where $u_1\in\U(\Sigma_s^-,R)$, $u_2\in\U(\Sigma_s^+,R)$ and $g'\in\G(\Delta_s,R)$.
+%Since $g$ lies in $\G(\Phi,R,I)$, the vector $gv^+$ is $I$-unimodular. 
+%On the other hand, $g'u_2v^+=v^+$, so $u_1\in\G(\Phi,R,I)\cap\U(\Sigma_s^-,R)=\U(\Sigma_s^-,I)$.
+%The matrix $g'u_2$ is an element of $\left(\G(\Delta_s,R)\U(\Sigma_s^+,R)\right)\cap\G(\Phi,R,I)$, and by Levi decomposition $u_2\in\U(\Sigma_s^+,I)$, $g'\in\G(\Delta_s,R,I)$.
+%\end{proof}
 

### 2015-10-10 stability-conditions.tex
Scrapped proof of relative Chevalley---Matsumoto; some other slight improvements

@@
 \begin{itemize}
- \item $\asr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$;
+\item $\asr(R) = 1$ for every semilocal ring $R$;
+\item $\asr(R)\leqslant2$ for every Dedekind domain $R$;
 \item $\asr(A[x])\leqslant3$ for every locally principal ring $A$;
- \item $\asr(R)\leqslant2$ for every Dedekind domain $R$.
+\item $\asr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$.
 \end{itemize}
+
+The last estimate further improves to $\sr(F[x_1, \ldots, x_n])\leqslant n$ for $F$ algebraic over a finite field (see~\cite[Corollary~17.4]{VasSusSerreProblem}).
+For certain classes of fields there is also a lower estimate for $\sr(F[x_1, \ldots, x_n])$ which allows to compute precisely the value of both $\sr(R)$ and $\asr(R)$.
+For example, $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ (see~\cite{KrusenmeyerThesis}) and $\sr(F[x_1, \ldots, x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
 Notice also that $\sr(\mathbb{Z}[x])=3$ (see \cite{GruMenVasSL2ZxSL2kxy}) and $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ for $n>1$ (see example after~\cite[Theorem~18.2]{VasSusSerreProblem}).
-
-For certain classes of fields the estimate for the stable rank of $R = F[x_1,\ldots, x_n]$ can be further improved.
-For example, if $F$ is algebraic over a finite field then $\sr(R)\leqslant n$ by~\cite[Corollary~17.4]{VasSusSerreProblem}.
-On the other hand, it is known that $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ (see~\cite{KrusenmeyerThesis}) and $\sr(R)=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
 \end{example}

### 2015-10-11 congrsubgr-boundgen.tex
Removed unneccessary corollary and replaced reference
lemma:rel-tor-elementary turned into a single formula and an inline remark

@@
 Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
- (see \cref{lemma:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we have a decomposition
+(see \eqref{eq:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we have a decomposition
 \[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
@@
 \begin{pmatrix} p^{k+\alpha} a & * \\ p^{-k+\beta} bm & * \end{pmatrix}. \]
-We find ourselves in the situation of Case 1, therefore we can write $g=h_{12}\cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
-Finally, expressing $h=x_{21}\cdot z_{21}\cdot x_{12}$ as in \cref{lemma:rel-tor-elementary}, we get that $g=x_{21} \cdot z_{21} \cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
+We find ourselves in the situation of the previous case, therefore, we can write $g=h_{12}\cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
+Finally, expressing $h=x_{21}\cdot z_{21}\cdot x_{12}$ as in \eqref{eq:rel-tor-elementary}, we get that $g=x_{21} \cdot z_{21} \cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
 \end{proof}

### 2015-10-11 paper.tex
lemma:rel-tor-elementary turned into a single formula and an inline remark

@@
 \[ \Hh(\Phi,R,I) = \Hh(\Phi,R)\cap\G(\Phi,R,I)=\langle h_\alpha(\varepsilon),\ \alpha\in\Phi,\ \varepsilon\in R^*\cap(1+I)\rangle. \]
-\begin{lemma}\label{lemma:rel-tor-elementary}
-$\Hh(\Phi,R,I)$ is contained in $\E(\Phi,R,I)$.
-\end{lemma}
-\begin{proof}
-Set $\varepsilon=1+s$, $s\in I$ and write
-\begin{multline*}
+Consider an element $\varepsilon\in R^*\cap(1+I)$, and rewrite it as $\varepsilon=1+s$, $s\in I$. The element $h_\alpha(\varepsilon)$ can be expressed as
+\begin{multline} \label{eq:rel-tor-elementary}
 h_\alpha(1+s) = x_\alpha\left(-1\middle)\, x_{-\alpha}\middle(-s\middle)\, x_\alpha\middle((1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right) = \\
 = x_\alpha\left((1+s)^{-1}-1\middle)\, z_{-\alpha}\middle(-s,(1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right).
-\end{multline*}
-It remains to note that $(1+s)^{-1}\in 1+I$ and so all the factors lie in $\E(\Phi,R,I)$.
-\end{proof}
+\end{multline}
+Note that $(1+s)^{-1}\in 1+I$ and so all the factors lie in $\E(\Phi,R,I)$. This shows, in particular, that $\Hh(\Phi, R, I) \leqslant \E(\Phi, R, I)$.
 

### 2015-10-11 bass-kolster.tex
BK typographic fixes

@@
 \[\begin{array}{l@{\quad}l@{\quad}l@{\quad}c}
-\Phi = \rA_\ell,\ \ell\geqslant 2, & \sr(I) \leqslant \ell; \\
-\Phi = \rC_\ell,\ \ell\geqslant 2, & \sr(I) \leqslant 2\ell-1; \\
-\Phi = \rB_\ell, \rD_\ell,\ \ell\geqslant 3, & \asr(I) \leqslant \ell-1.
+\Phi = \rA_\ell, \ \ell\geqslant 2, & \sr(I) \leqslant \ell; \\
+\Phi = \rC_\ell, \ \ell\geqslant 2, & \sr(I) \leqslant 2\ell-1; \\
+\Phi = \rB_\ell, \rD_\ell, \ \ell\geqslant 3, & \asr(I) \leqslant \ell-1.
 \end{array}\]
-Then the principal congruence subgroup $\G(\Phi,R,I)$ admits the following relative version of Bass---Kolster decomposition:
-\[ \G(\Phi,R,I)=  \U(\Phi^+,I) \cdot \U(\Phi^-,I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\},I) \cdot \U(\Sigma_1,I) \cdot \G(\Delta_1,R,I), \]
-where $Z = Z_{\alpha_\mathrm{max}}(I)=\left\{z_{-\alpha_\mathrm{max}}(r,1)\ \middle|\ r\in I \right\}$.
+Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of Bass---Kolster decomposition:
+\[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]
+where $Z = Z_{\alpha_\mathrm{max}}(I)=\left\{z_{-\alpha_\mathrm{max}}(r, 1)\ \middle|\ r\in I \right\}$.
 \end{thm}
@@
 \textsc{Case $\Phi=\rA_\ell$, $n=\ell + 1$.}
-Since $\sr(I)\leqslant\ell$, one can find $a_1,\ldots,a_\ell\in I$ such that $(v_1+a_1v_{\ell+1},\ldots,v_\ell+a_\ell v_{\ell+1})^t=(v'_1,\ldots,v'_\ell)^t$ is $I$-unimodular.
-Then there are $b_1,\ldots,b_\ell\in I$ such that $b_1v'_1+\ldots b_\ell v'_\ell=v'-1\in I$. 
-Thus the vector \[ v'' = \prod_{i=1}^\ell x_{\ell+1,i}(b_i) \cdot \prod_{i=1}^\ell x_{i,\ell+1}(a_i) \cdot v \]
+Since $\sr(I)\leqslant\ell$, one can find $a_1, \ldots, a_\ell\in I$ such that $(v_1+a_1v_{\ell+1}, \ldots, v_\ell+a_\ell v_{\ell+1})^t=(v'_1, \ldots, v'_\ell)^t$ is $I$-unimodular.
+Then there are $b_1, \ldots, b_\ell\in I$ such that $b_1v'_1+\ldots b_\ell v'_\ell=v'-1\in I$. 
+Thus the vector \[ v'' = \prod_{i=1}^\ell x_{\ell+1, i}(b_i) \cdot \prod_{i=1}^\ell x_{i, \ell+1}(a_i) \cdot v \]
 satisfies the equalities~\eqref{eq1}.
@@
 \textsc{Case $\Phi=\rC_\ell$, $n=2\ell$.}
-Notice that the column $(v_1,\ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
+Notice that the column $(v_1, \ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
 Applying condition $\sr(I)\leq 2\ell-1$ we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
 By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for
-\[ h_1 = x_{1,-1}(c_1 + d) \cdot \prod_{i=2}^{-2} x_{i,-1}(c_i) \in \U(\Sigma_1^+, I). \]
+\[ h_1 = x_{1, -1}(c_1 + d) \cdot \prod_{i=2}^{-2} x_{i, -1}(c_i) \in \U(\Sigma_1^+, I). \]
 
-We can find $f_1, f_2,\ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
+We can find $f_1, f_2, \ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
 Set $\xi = v''_1-v''_{-1}-1 \in I$, 
-\[ h_2 = x_{-1,1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1,i}(\xi f_i) \in \U(\Sigma_1^-, I). \]
+\[ h_2 = x_{-1, 1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1, i}(\xi f_i) \in \U(\Sigma_1^-, I). \]
 Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\eqref{eq1}.
@@
 Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
-\[ v''=h_2 \cdot x_{1,2}(c_1) \cdot v', \quad h_2=\prod_{i=3}^\ell x_{i,2}(c_i). \]
-We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v''_1+\sum_{i=3}^\ell f_i v''_{i} = 1$.
+\[ v''=h_2 \cdot x_{1, 2}(c_1) \cdot v', \quad h_2=\prod_{i=3}^\ell x_{i, 2}(c_i). \]
+We can find $f_1, f_3, \ldots, f_\ell \in R$ such that $f_1v''_1+\sum_{i=3}^\ell f_i v''_{i} = 1$.
 As before, set
-\[ \xi = v''_1-v''_{-2}-1 \in I, \quad h_3 = x_{-2,1}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-2,i}(\xi f_i), \quad v'''=h_3 \cdot v''. \]
-Clearly, $t_{1,2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, $ h_3 \cdot h_2 \in \U(\Phi^-, I)$ and $v'''$ satisfies~\eqref{eq1}.
+\[ \xi = v''_1-v''_{-2}-1 \in I, \quad h_3 = x_{-2, 1}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-2, i}(\xi f_i), \quad v'''=h_3 \cdot v''. \]
+Clearly, $t_{1, 2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, $ h_3 \cdot h_2 \in \U(\Phi^-, I)$ and $v'''$ satisfies~\eqref{eq1}.
 
@@
 Denote by $J\leq I$ the ideal spanned by components of $v_-$.
-Since $\sr(I/J)\leq \ell$ we can find $c_1,\dots,c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell x_{i,0}(c_i) \in \U(\Phi^+, I)$
-one has $\bar{v'}_+=(\bar{v'_1},\ldots, \bar{v'_\ell}) \in \Ums(\ell, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, I)$.
+Since $\sr(I/J)\leq \ell$ we can find $c_1, \dots, c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell x_{i, 0}(c_i) \in \U(\Phi^+, I)$
+one has $\bar{v'}_+=(\bar{v'_1}, \ldots, \bar{v'_\ell}) \in \Ums(\ell, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, I)$.
 Now the proof can be finished by repeating the argument for the case $\Phi=\rD_\ell$ (applied to the subset of long roots of $\rB_\ell$).
@@
 \begin{cor}\label{cor:bass-kolster-count}
-In the assumptions and notation of \cref{thm:BassKolster} every element of $\G(\Phi,R,I)$ 
-can be factored into a product of one element of $\G(\Delta_1,R,I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elements of $\mathcal{X}$.
+In the assumptions and notation of \cref{thm:BassKolster} every element of $\G(\Phi, R, I)$ 
+can be factored into a product of one element of $\G(\Delta_1, R, I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elements of $\mathcal{X}$.
 \end{cor}
@@
 In the case $\Phi=\rD_\ell$ from the proof of \cref{thm:BassKolster} one obtains that
-\begin{equation*} \G(\Phi,R,I) =  \U(\Sigma_\ell^+,I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1,I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z \cdot \U(\Sigma_1^-,I) \cdot \U(\Sigma_1^+,I) \cdot \G(\Delta_1,R,I).
+\begin{equation*} \G(\Phi, R, I) =  \U(\Sigma_\ell^+, I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1, I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z \cdot \U(\Sigma_1^-, I) \cdot \U(\Sigma_1^+, I) \cdot \G(\Delta_1, R, I).
 \end{equation*}
-We can present an element $g$ of $\U(\Sigma_\ell^+, I)$ as a product of $g_1 \in \U(\Sigma_{\{1,2\}^+} \cap \Sigma_\ell^+)$ and $g_2\in \U(\Delta_{\{1,2\}}\cap \Sigma_\ell^+)$.
+We can present an element $g$ of $\U(\Sigma_\ell^+, I)$ as a product of $g_1 \in \U(\Sigma_{\{1, 2\}^+} \cap \Sigma_\ell^+)$ and $g_2\in \U(\Delta_{\{1, 2\}}\cap \Sigma_\ell^+)$.
 An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one)
@@
 \Phi=\rC_\ell, & \sr(I)\leqslant 3, & N'=3\left|\Phi^+\right|+3\ell - 6; \\
-\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N'=4\left|\Phi^+\right| - 4.
+\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N'=4\left|\Phi^+\right| - 4.
 \end{array}\]
-Then every element of $\G(\Phi,R,I)$ can be factored into a product of one element of $\G(\langle\pm\alpha_\ell\rangle,R,I)\cong\SL(2,R,I)$ and at most $N'$ elements of $\mathcal{Z}(\Sigma_\ell)$:
+Then every element of $\G(\Phi, R, I)$ can be decomposed into a product of one element of $\G(\langle\pm\alpha_\ell\rangle, R, I) \cong \SL(2, R, I)$ and at most $N'$ elements of $\mathcal{Z}(\Sigma_\ell)$:
 \end{cor}
@@
 \[\begin{tikzcd}[row sep=tiny]
-\rD_4 \arrow[out=0,in=120]{rd}{\asr\leqslant3} & & & \\
+\rD_4 \arrow[out=0, in=120]{rd}{\asr\leqslant3} & & & \\
 \rA_4 \arrow{r}{\sr\leqslant4} & \rA_3 \arrow{r}{\sr\leqslant3} & \rA_2 \arrow{r}{\sr\leqslant2} & \rA_1 \\
-\rC_4 \arrow{r}{\sr\leqslant7} & \rC_3 \arrow{r}{\sr\leqslant5} & \rC_2 \arrow[out=0,in=-120,swap]{ru}{\sr\leqslant3} \\
-\rB_4 \arrow{r}{\asr\leqslant3} & \rB_3 \arrow[out=0,in=-120,swap]{ru}{\asr\leqslant2} & &
+\rC_4 \arrow{r}{\sr\leqslant7} & \rC_3 \arrow{r}{\sr\leqslant5} & \rC_2 \arrow[out=0, in=-120, swap]{ru}{\sr\leqslant3} \\
+\rB_4 \arrow{r}{\asr\leqslant3} & \rB_3 \arrow[out=0, in=-120, swap]{ru}{\asr\leqslant2} & &
 \end{tikzcd}\] \caption{Reductions used in the proof of \cref{cor:bass-kolster-iterated} and \cref{thm:SL2width}} \end{figure}

### 2015-10-11 bass-kolster.tex
Paper.tex typography fixes (+1 in BK)

@@
 \end{array}\]
+
 Then every element of $\G(\Phi, R, I)$ can be decomposed into a product of one element of $\G(\langle\pm\alpha_\ell\rangle, R, I) \cong \SL(2, R, I)$ and at most $N'$ elements of $\mathcal{Z}(\Sigma_\ell)$:

### 2015-10-11 paper.tex
Paper.tex typography fixes (+1 in BK)

@@
 \author {Sergey Sinchuk, Andrei Smolensky}
-\email {sinchukss {\it at} yandex.ru,\ andrei.smolensky {\it at} gmail.com}
+\email {sinchukss {\it at} yandex.ru, \ andrei.smolensky {\it at} gmail.com}
 \date {\today}
@@
 Let $\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over arbitarary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup}
-i.\,e. the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
+i.\, e. the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
 For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (aka \emph{principal congruence subgroup}) of level $I$, 
-i.\,e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection $R\rightarrow R/I$.
+i.\, e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection $R\rightarrow R/I$.
 
-In our theorems we also use the notion of the \emph{relative elementary Chevalley group} $\E(\Phi, R, I) \leq \G(\Phi, R, I)$.
-Recall that $\E(\Phi, R, I)$ is defined as the normal closure in $\E(\Phi, R)$ of the subgroup generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi,\ \xi \in I \}$.
+We will also use the notion of the \emph{relative elementary Chevalley group} $\E(\Phi, R, I) \leqslant \G(\Phi, R, I)$.
+Recall that $\E(\Phi, R, I)$ is defined as the normal closure in $\E(\Phi, R)$ of the subgroup generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi, \ \xi \in I \}$.
 
@@
 It is a classical result of J.~Tits and L.~Vaserstein (see~\cite{Tits76}, \cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
-the set of elements $\mathcal{Z}(\Phi) = \{ z_\alpha(s,\xi) \mid s\in I,\ \xi \in R,\ \alpha \in \Phi\}.$
+the set of elements $\mathcal{Z}(\Phi) = \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in \Phi\}.$
 
@@
 Let $\Sigma_S$ be the special part of $S$, then $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$, where
-$$\mathcal{Z}(\Sigma) = \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s \in I,\ \xi \in R,\ \alpha\in \Sigma \}.$$ \end{prop}
+$$\mathcal{Z}(\Sigma) = \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s \in I, \ \xi \in R, \ \alpha\in \Sigma \}.$$ \end{prop}
 
@@
 %\begin{itemize}
-%\item \emph{Gauss decomposition,} i.\,e. a decomposition of the form $\E(\Phi,R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup,
+%\item \emph{Gauss decomposition, } i.\, e. a decomposition of the form $\E(\Phi, R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup, 
 %      and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
@@
 Then the relative elementary Chevalley $\E(\Phi, R, I)$ group admits the following decomposition
-\[ \E(\Phi,R,I) = \Hh(\Phi,R,I) \cdot \U(\Phi,I) \cdot \U(\Phi^-,I) \cdot \U(\Phi,I). \]
+\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi, I). \]
 \end{thm}
 In the special case when $I$ is contained in the Jacobson radical of $R$ \cref{thm:srRI1} boils down to~\cite[Proposition~2.3]{AbeSuzNormalSubgroups}. 
-We also note that the absolute case (i.\,e. $I=R$) of the theorem was treated by the second named author in~\cite{Sm12}.
+We also note that the absolute case (i.\, e. $I=R$) of the theorem was treated by the second named author in~\cite{Sm12}.
 
@@
 Let $G$ be an abstract group with a generating set $X \subset G$. 
-We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
-%The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $x_\alpha(\xi)$ has been extensively studied in a number of works (see e.\,g.
+We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\, e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
+%The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $x_\alpha(\xi)$ has been extensively studied in a number of works (see e.\, g.
 \cite{CK83, Ka82, Tavgen91, Mo07, VseUnitrZ1p, VavSmSuUnitrEng}).
-%Summarizing results of these works, one can hope that such width is finite only for rather narrow classes of rings of number-theoretic nature, e.\,g.
+%Summarizing results of these works, one can hope that such width is finite only for rather narrow classes of rings of number-theoretic nature, e.\, g.
 localizations of Dedeking rings of arithmetic type.
-%For example, W.~van der Kallen has shown that the width of $\SL(3,R)$ is infinite already for a Euclidean ring $R=\mathbb{C}[t]$.
+%For example, W.~van der Kallen has shown that the width of $\SL(3, R)$ is infinite already for a Euclidean ring $R=\mathbb{C}[t]$.
 
@@
 \item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
-$W(\G(\Phi,R,I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
+$W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
 \item If $\sr(I) = 1$ and $\Phi$ is arbitrary irreducible root system then 
-\[W(\E(\Phi,R,I),\mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1;\]
+\[W(\E(\Phi, R, I), \mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1;\]
 \item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime number $p$, then under the assumption of the Generalized Riemann Hypothesis one has
 \begin{alignat*}{2}
-& W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1 & \text{ if } \Phi=\rA_\ell,\rC_\ell, \\
-& W(\E(\Phi,R,I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell,\rD_\ell;
+& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1 & \text{ if } \Phi=\rA_\ell, \rC_\ell, \\
+& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell;
 \end{alignat*}
@@
 In fact, in the context of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
-Our next result further extends this to even larger class of rings (which e.\,g. includes ideals of all Dedekind rings).
+Our next result further extends this to even larger class of rings (which e.\, g. includes ideals of all Dedekind rings).
 \begin{thm}\label{thm:SL2width}
@@
 \Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right| - 2; \\
-\Phi=\rB_\ell,\rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right| - 3\rk(\Phi).
+\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right| - 3\rk(\Phi).
 \end{array}\]
-Then the principal congruence subgroup $\G(\Phi,R,I)$ can be presented as a product of at most $N$ copies of its (regularly embedded) subgroups isomorphic to $\SL_2(R, I)$.
+Then the principal congruence subgroup $\G(\Phi, R, I)$ can be presented as a product of at most $N$ copies of its (regularly embedded) subgroups isomorphic to $\SL_2(R, I)$.
 \end{thm}
@@
 \section{Preliminaries}\label{sec:prelim}
-For any collection of subsets $H_1,\ldots, H_n$ of a group $G$ we denote by $H_1\ldots H_n$ their Minkowski set-product,
-i.\,e. the set consisting of arbitrary products $h_1\ldots h_n$ of elements $h_i\in H_i$. In particular, the equality
+For any collection of subsets $H_1, \ldots, H_n$ of a group $G$ we denote by $H_1\ldots H_n$ their Minkowski set-product, 
+i.\, e. the set consisting of arbitrary products $h_1\ldots h_n$ of elements $h_i\in H_i$. In particular, the equality
 $G = H_1\cdot\ldots\cdot H_n$ means that every element $g\in G$ can be presented as a product $h_1\ldots h_n$ for $h_i\in H_i$.
@@
 Let $\alpha_\mathrm{max}$ denote the maximal root of $\Phi$.
-For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th component of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
+For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th component of $\alpha$ in $\Pi$, i.\, e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
 
@@
 We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\beta, \beta)$.
-Let $\varpi_1, \ldots, \varpi_\ell$ be the \emph{fundamental weights }of $\Phi$, i.\,e. vectors
-defined by $\langle\varpi_i,\alpha_j^\vee\rangle=\delta_{i,j},$ where $\alpha^\vee = \frac{\alpha}{2(\alpha,\alpha)}$.
+Let $\varpi_1, \ldots, \varpi_\ell$ be the \emph{fundamental weights }of $\Phi$, i.\, e. vectors
+defined by $\langle\varpi_i, \alpha_j^\vee\rangle=\delta_{i, j}, $ where $\alpha^\vee = \frac{\alpha}{2(\alpha, \alpha)}$.
 
-Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all reflections $\sigma_\alpha$ where $\sigma_\alpha(\beta)=\beta-\langle\alpha,\beta \rangle\cdot \alpha$.
+Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all reflections $\sigma_\alpha$ where $\sigma_\alpha(\beta)=\beta-\langle\alpha, \beta \rangle\cdot \alpha$.
 For a reductive subset $\Delta\subseteq \Phi$ denote by $W(\Delta)$ the subgroup of $W(\Phi)$ generated by $\sigma_\alpha$ for $\alpha\in\Delta$.
@@
 \begin{align*}
-& \Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\},\\
-& \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha) \in \mathbb{Z}_{\geqslant0} \Phi^\pm \},\\
+& \Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\}, \\
+& \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha) \in \mathbb{Z}_{\geqslant0} \Phi^\pm \}, \\
 & S_J^\pm = \Delta_J \sqcup \Sigma_J^\pm.
@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
-We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i,j}^\pm=\Sigma_{\{i,j\}}^\pm$, etc.
+We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\, g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
 
 \begin{lemma}[{\cite[Lemma~1]{ABS}}]\label{lemma:abs}
-Let $\alpha, \beta \in \Sigma^\pm_J$ be two roots having the same length such that $\shape(J,\alpha)=\shape(J,\beta)\neq 0$.
+Let $\alpha, \beta \in \Sigma^\pm_J$ be two roots having the same length such that $\shape(J, \alpha)=\shape(J, \beta)\neq 0$.
 Then $\alpha$ and $\beta$ are conjugate under the action of $W(\Delta_J)$.
@@
 it follows that the exceptional isomorphisms of small-rank groups (which are well-known in the theory of groups over fields) remain valid for Chevalley groups over arbitrary commutative rings.
-In particular, there are isomorphisms of groups $\Spin(3,R)\cong\SL(2,R)$, $\Spin(5, R)\cong \Sp(4, R)$, $\Spin(6, R)\cong\SL(4, R)$, $\SL(2, R)\cong \Sp(2, R)$.
+In particular, there are isomorphisms of groups $\Spin(3, R)\cong\SL(2, R)$, $\Spin(5, R)\cong \Sp(4, R)$, $\Spin(6, R)\cong\SL(4, R)$, $\SL(2, R)\cong \Sp(2, R)$.
 
@@
 x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \label{rel:add}\\
-& [x_\alpha(s),  x_\beta(t)] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
+& [x_\alpha(s), x_\beta(t)] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right), \quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
 \end{align} 
 The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
-The integers $N_{\alpha\beta ij}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.
+The integers $N_{\alpha\beta ij}$ are called {\it structure constants} of the Chevalley group $\G(\Phi, R)$ and depend only on $\Phi$.
 We refer the reader to~\cite[\S14]{VP} for basic properties of structure constants.
 
-For an additive subset $I\subseteq R$ we denote by $X_\alpha(I)$ the corresponding \emph{root subgroup} of level $I$, i.\,e.
+For an additive subset $I\subseteq R$ we denote by $X_\alpha(I)$ the corresponding \emph{root subgroup} of level $I$, i.\, e.
 the subgroup consisting of all elementary root unipotents $x_\alpha(\xi)$, $\xi\in I$.
@@
 w_\alpha(\varepsilon) x_{\beta}(\xi) w_\alpha(\varepsilon)^{-1} =
-x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\cdot\varepsilon^{-\langle\beta,\alpha \rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R.
+x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\cdot\varepsilon^{-\langle\beta, \alpha \rangle}\xi\right), \quad \varepsilon\in R^*, \ \xi\in R.
 \end{equation}
 where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed through structure constants (cf.~\cite[\S13]{VP}).
-For a reductive subset $\Delta \subseteq \Phi$ denote by $\widetilde{W}(\Delta)$ the \emph{extended Weyl group}, i.\,e.
+For a reductive subset $\Delta \subseteq \Phi$ denote by $\widetilde{W}(\Delta)$ the \emph{extended Weyl group}, i.\, e.
 the subgroup of $\E(\Phi, R)$ generated by all $w_{\alpha}(1)$, $\alpha \in \Delta$.
@@
 \begin{alignat}{2} 
-& [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] = 1, &\quad& \alpha, \beta \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-comm} \\
-& \phantom{[} h_\alpha(\varepsilon_1 \varepsilon_2) = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2), && \alpha \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-mult} \\
-& \phantom{[} h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right), && \alpha, \beta \in \Phi,\ \varepsilon \in R^*, \xi \in R.
+& [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] = 1, &\quad& \alpha, \beta \in \Phi, \ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-comm} \\
+& \phantom{[} h_\alpha(\varepsilon_1 \varepsilon_2) = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2), && \alpha \in \Phi, \ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-mult} \\
+& \phantom{[} h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta, \alpha\rangle}\xi\right), && \alpha, \beta \in \Phi, \ \varepsilon \in R^*, \xi \in R.
 \label{rel:h-w}
@@
 The irreducible representations of Chevalley groups used in these paper form a sublist of~\cite[Table~2]{PSV98}.
-More specifically, all of them are \emph{fundamental} (i.\,e. their highest weight is fundamental) and basic.
+More specifically, all of them are \emph{fundamental} (i.\, e. their highest weight is fundamental) and basic.
 We widely employ the technique of \emph{weight diagrams} (see~\cite[\S~2]{PSV98}) to help visualize the structure of these representations.
-In the simplest case of a \emph{microweight} representation $\pi$ (i.\,e. $\pi$ such that $V_0 = 0$)
+In the simplest case of a \emph{microweight} representation $\pi$ (i.\, e. $\pi$ such that $V_0 = 0$)
 the weight diagram of $(V, \pi)$ is just an undirected graph whose vertices are in one-to-one correspondence with the elements of $\Lambda(\pi)$.
@@
 \newline \begin{tabular}{ll}
-If $\lambda\in\Lambda(\pi)^*,\ \lambda+\alpha\notin\Lambda(\pi)$, then & $x_\alpha(\xi)e_\lambda=e_\lambda$; \\
-If $\lambda,\lambda+\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_\lambda=e_\lambda\pm\xi e_{\lambda+\alpha}$; \\
+If $\lambda\in\Lambda(\pi)^*, \ \lambda+\alpha\notin\Lambda(\pi)$, then & $x_\alpha(\xi)e_\lambda=e_\lambda$; \\
+If $\lambda, \lambda+\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_\lambda=e_\lambda\pm\xi e_{\lambda+\alpha}$; \\
 If $\alpha\notin\Lambda(\pi)^*$, then & $x_\alpha(\xi)v_0=v_0$ for any $v_0\in V_0$; \\
@@
 \[\begin{array}{cll}
-  1,2,\ldots, \ell+1 & \text{in the case} & \Phi =\rA_\ell, \\
-  1,2,\ldots \ell, 0, -\ell,\ldots, -2, -1 & \text{in the case} & \Phi =\rB_\ell, \\
-  1,2,\ldots \ell, -\ell,\ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
+  1, 2, \ldots, \ell+1 & \text{in the case} & \Phi =\rA_\ell, \\
+  1, 2, \ldots \ell, 0, -\ell, \ldots, -2, -1 & \text{in the case} & \Phi =\rB_\ell, \\
+  1, 2, \ldots \ell, -\ell, \ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
 \end{array}\]
@@
 Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ such that $\lambda_1-\lambda_2\in \Phi$.
-It will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
-For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
+It will be convenient for us to write $x_{\lambda_1, \lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
+For example, for $\Phi=\rA_\ell$ we have $x_{1, 2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
 
@@
 %\begin{align*}
-%& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
-%& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
+%& x_{i, -i}(\xi)=e+\xi e_{i, -i}, \\ 
+%& x_{i, j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j, -i}, \quad i\neq\pm j.
 %\end{align*}
 %Here $\varepsilon_i$ is the sign of $i$.
-%In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
+%In case $\Phi=\rB_\ell, \rD_\ell$ the long and short root unipotents in $\SO(n, R)$ are
 %\begin{align*}
-%& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
-%& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
+%& x_{i, j}(\xi)=e+\xi e_{ij}-\xi e_{-j, -i}, \quad i\neq\pm j, \ i, j\neq0, \\
+%& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0, i}-\xi^2 e_{i, -i}, \quad i\neq0.
 %\end{align*}
@@
 Let $\Phi$ be a root system of rank $\geqslant2$, let $R$ be a commutative ring and $I\trianglelefteq R$ be its ideal.
-If $\Phi\neq\rC_\ell$ then $\E\left(\Phi,R,I^2\right)\leqslant\E(\Phi,I)$, otherwise $\E\left(\Phi,R,II^{\indexbox{2}}\right)\leqslant\E(\Phi,I)$.
+If $\Phi\neq\rC_\ell$ then $\E\left(\Phi, R, I^2\right)\leqslant\E(\Phi, I)$, otherwise $\E\left(\Phi, R, II^{\indexbox{2}}\right)\leqslant\E(\Phi, I)$.
 \end{lemma}
 Here $I^{\indexbox{2}}$ denotes the ideal generated by squares $a^2$, where $a\in I$.
-Recall also that $I^2$ is generated by products $ab$ for all $a,b\in I$.
-Clearly, $II^{\indexbox{2}}$ is generated by elements of the form $a^2b$ for $a,b\in I$.
+Recall also that $I^2$ is generated by products $ab$ for all $a, b\in I$.
+Clearly, $II^{\indexbox{2}}$ is generated by elements of the form $a^2b$ for $a, b\in I$.
 
@@
 
-Denote by $\Hh(\Phi,R)$ the subgroup generated by all $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$, and set
-\[ \Hh(\Phi,R,I) = \Hh(\Phi,R)\cap\G(\Phi,R,I)=\langle h_\alpha(\varepsilon),\ \alpha\in\Phi,\ \varepsilon\in R^*\cap(1+I)\rangle. \]
+Denote by $\Hh(\Phi, R)$ the subgroup generated by all $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$, and set
+\[ \Hh(\Phi, R, I) = \Hh(\Phi, R)\cap\G(\Phi, R, I)=\langle h_\alpha(\varepsilon), \ \alpha\in\Phi, \ \varepsilon\in R^*\cap(1+I)\rangle. \]
 Consider an element $\varepsilon\in R^*\cap(1+I)$, and rewrite it as $\varepsilon=1+s$, $s\in I$. The element $h_\alpha(\varepsilon)$ can be expressed as
@@
 h_\alpha(1+s) = x_\alpha\left(-1\middle)\, x_{-\alpha}\middle(-s\middle)\, x_\alpha\middle((1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right) = \\
-= x_\alpha\left((1+s)^{-1}-1\middle)\, z_{-\alpha}\middle(-s,(1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right).
+= x_\alpha\left((1+s)^{-1}-1\middle)\, z_{-\alpha}\middle(-s, (1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right).
 \end{multline}
-Note that $(1+s)^{-1}\in 1+I$ and so all the factors lie in $\E(\Phi,R,I)$. This shows, in particular, that $\Hh(\Phi, R, I) \leqslant \E(\Phi, R, I)$.
+Note that $(1+s)^{-1}\in 1+I$ and so all the factors lie in $\E(\Phi, R, I)$. This shows, in particular, that $\Hh(\Phi, R, I) \leqslant \E(\Phi, R, I)$.
 
@@
 %In the absolute case ($I=R$) the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}. 
-%Thus we can write $g=u_1\cdot g'\cdot u_2$, where $u_1\in\U(\Sigma_s^-,R)$, $u_2\in\U(\Sigma_s^+,R)$ and $g'\in\G(\Delta_s,R)$.
-%Since $g$ lies in $\G(\Phi,R,I)$, the vector $gv^+$ is $I$-unimodular. 
-%On the other hand, $g'u_2v^+=v^+$, so $u_1\in\G(\Phi,R,I)\cap\U(\Sigma_s^-,R)=\U(\Sigma_s^-,I)$.
-%The matrix $g'u_2$ is an element of $\left(\G(\Delta_s,R)\U(\Sigma_s^+,R)\right)\cap\G(\Phi,R,I)$, and by Levi decomposition $u_2\in\U(\Sigma_s^+,I)$, $g'\in\G(\Delta_s,R,I)$.
+%Thus we can write $g=u_1\cdot g'\cdot u_2$, where $u_1\in\U(\Sigma_s^-, R)$, $u_2\in\U(\Sigma_s^+, R)$ and $g'\in\G(\Delta_s, R)$.
+%Since $g$ lies in $\G(\Phi, R, I)$, the vector $gv^+$ is $I$-unimodular. 
+%On the other hand, $g'u_2v^+=v^+$, so $u_1\in\G(\Phi, R, I)\cap\U(\Sigma_s^-, R)=\U(\Sigma_s^-, I)$.
+%The matrix $g'u_2$ is an element of $\left(\G(\Delta_s, R)\U(\Sigma_s^+, R)\right)\cap\G(\Phi, R, I)$, and by Levi decomposition $u_2\in\U(\Sigma_s^+, I)$, $g'\in\G(\Delta_s, R, I)$.
 %\end{proof}
@@
 
-Using standard relativization argument it is not hard to deduce from Taddei's result that $\E(\Phi,R,I)$ is normal in $\G(\Phi,R,I)$ under the same assumptions on $\Phi$.
-This allows us to define the relative $\K_1$-group as $\K_1(\Phi,R,I)=\G(\Phi,R,I)/\E(\Phi,R,I).$
+Using standard relativization argument it is not hard to deduce from Taddei's result that $\E(\Phi, R, I)$ is normal in $\G(\Phi, R, I)$ under the same assumptions on $\Phi$.
+This allows us to define the relative $\K_1$-group as $\K_1(\Phi, R, I)=\G(\Phi, R, I)/\E(\Phi, R, I).$
 When $I=R$, we write $\K_1(\Phi, R)$ for $\K_1(\Phi, R, R)$.
@@
 In some cases it is known that $\K_1(\Phi, R, I)$ is trivial.
-For example, $\SK_1(\ell+1,R)=\K(\rA_\ell,R)=1$ for any ring of stable rank $1$ (see section~\ref{sec:stability-conditions}), 
+For example, $\SK_1(\ell+1, R)=\K(\rA_\ell, R)=1$ for any ring of stable rank $1$ (see section~\ref{sec:stability-conditions}), 
 and for other root systems some stronger assumption is required such as $\asr(R)=1$ or being semilocal. 
@@
 \begin{prop} \label{prop:K1triv}
-Let $\Phi$ be a root system of rank $\geqslant2$. Assume that the field $k$ has a real embedding. Then $\K_1(\Phi,\mathcal{O}_S,I)=1$.
+Let $\Phi$ be a root system of rank $\geqslant2$. Assume that the field $k$ has a real embedding. Then $\K_1(\Phi, \mathcal{O}_S, I)=1$.
 \end{prop}

### 2015-10-11 congrsubgr-boundgen.tex
Commas spaces in Gauss, DV, CB and SF

@@
 \end{align*}
-Notice that $g_5=z_{21}\left(-mp^{\beta+u},c/p^{\beta+u}\right)\cdot g_2$ hence $g=x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$
+Notice that $g_5=z_{21}\left(-mp^{\beta+u}, c/p^{\beta+u}\right)\cdot g_2$ hence $g=x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$
 and the length of $g$ does not exceed $4$.
@@
 
-%Now it is easy to derive bounded generation property for $\G(\Phi,\mathcal{O}_S,I)$ from the above statements.
+%Now it is easy to derive bounded generation property for $\G(\Phi, \mathcal{O}_S, I)$ from the above statements.
 \begin{lemma}\label{lemma:width-dedekind}
 Let $\Phi$ be an irreducible classical root system of rank $\ell \geqslant 2$.
-If $k$ has a real embedding, then $\G(\Phi,\mathcal{O}_S,I)$ has finite width with respect to the generating set $\mathcal{Z}(\Sigma_\ell)$.
+If $k$ has a real embedding, then $\G(\Phi, \mathcal{O}_S, I)$ has finite width with respect to the generating set $\mathcal{Z}(\Sigma_\ell)$.
 \end{lemma}
@@
 of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators $\mathcal{Z}(\Sigma_\ell)$ and one element of 
-$\G(\{\alpha_\ell, -\alpha_\ell\}, \mathcal{O}_S, I)\cong\SL(2,\mathcal{O}_S,I)$.
+$\G(\{\alpha_\ell, -\alpha_\ell\}, \mathcal{O}_S, I)\cong\SL(2, \mathcal{O}_S, I)$.
 Consequently, to prove the statement of the lemma it suffices to express every element 
@@
 Recall that Vaserstein's congruence subgroup is defined as
-\[ G(I,I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2,\mathcal{O}_S)\;\middle|\; a,d\in I^2,\ b,c\in I \right\}. \]
-Notice that $g_1=g\cdot z_{21}(a,1)$ is contained in $G(I,I)$, indeed
-\[ \begin{pmatrix} 1+a & b \\ c & 1+d \end{pmatrix} \cdot \begin{pmatrix} 1-a & -a \\ a & 1+a \end{pmatrix} = \begin{pmatrix} 1+ba-a^2 & b-a-ba-a^2 \\ c+a+ad-ac & 1+bc-ac \end{pmatrix} \in G(I,I). \]
-For any matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I,I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)$ lies in $\SL\left(2,\mathcal{O}_S,I^2\right)$.
+\[ G(I, I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2, \mathcal{O}_S)\;\middle|\; a, d\in I^2, \ b, c\in I \right\}. \]
+Notice that $g_1=g\cdot z_{21}(a, 1)$ is contained in $G(I, I)$, indeed
+\[ \begin{pmatrix} 1+a & b \\ c & 1+d \end{pmatrix} \cdot \begin{pmatrix} 1-a & -a \\ a & 1+a \end{pmatrix} = \begin{pmatrix} 1+ba-a^2 & b-a-ba-a^2 \\ c+a+ad-ac & 1+bc-ac \end{pmatrix} \in G(I, I). \]
+For any matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I, I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)$ lies in $\SL\left(2, \mathcal{O}_S, I^2\right)$.
 
-By \cref{lemma:Stepanov-ideal} the group $\E\left(\Phi,\mathcal{O}_S,I^2\right)$ is contained in $\E(\Phi,I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
-Notice that under the assumptions of the lemma it is known that $\E(\Phi,I)$ has finite width with respect to $\mathcal{X}$, see~\cite{Tavgen93} or \cite[Theorem~3.3]{TavgenThesis}.
+By \cref{lemma:Stepanov-ideal} the group $\E\left(\Phi, \mathcal{O}_S, I^2\right)$ is contained in $\E(\Phi, I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
+Notice that under the assumptions of the lemma it is known that $\E(\Phi, I)$ has finite width with respect to $\mathcal{X}$, see~\cite{Tavgen93} or \cite[Theorem~3.3]{TavgenThesis}.
 
@@
 \end{pmatrix}\bmod II^{\indexbox{2}}. \]
-Now for $g_3=g_2\cdot z_{12}\left(a^2-ab,1\right)$ we have that
+Now for $g_3=g_2\cdot z_{12}\left(a^2-ab, 1\right)$ we have that
 \begin{align*}
-& g_3\equiv\begin{pmatrix} 1 & -2ab \\ -abc-a^2+ab-ac+ad & 1 \end{pmatrix}\bmod II^{\indexbox{2}},\\
+& g_3\equiv\begin{pmatrix} 1 & -2ab \\ -abc-a^2+ab-ac+ad & 1 \end{pmatrix}\bmod II^{\indexbox{2}}, \\
 & g_4=x_{12}(2ab)\cdot g_3\equiv x_{21}\left(-abc-a^2+ab-ac+ad\right)\bmod II^{\indexbox{2}}.
 \end{align*}
-Thus $g_4\cdot x_{21}(*)\in\SL\left(2,\mathcal{O}_S,II^{\indexbox{2}}\right)$ is contained in $\E(\rC_\ell,I)$ by \cref{lemma:Stepanov-ideal} and therefore can be expressed as a bounded product of $x_\alpha$.
+Thus $g_4\cdot x_{21}(*)\in\SL\left(2, \mathcal{O}_S, II^{\indexbox{2}}\right)$ is contained in $\E(\rC_\ell, I)$ by \cref{lemma:Stepanov-ideal} and therefore can be expressed as a bounded product of $x_\alpha$.
 \end{proof}
@@
 \begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.
-The the first and the third assertions follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}
+The the first and the third assertions follow from \cref{lemma:Z1p, lemma:width-dedekind}. \end{proof}

### 2015-10-11 dennis-vaserstein.tex
Commas spaces in Gauss, DV, CB and SF

@@
 
-%The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\,e. $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
+%The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\, e. $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
 %\[\begin{array}{l@{\qquad}c@{\quad}c@{\qquad}l}
 %\Phi                                 & s    & r      & \text{ring condition} \\ \hline\vphantom{\Bigl(}
-%\rA_\ell,\ \ell\geqslant 2           & 1    & \ell   & \sr(I) \leqslant \ell-1 \\    
-%\rB_\ell,\ \ell\geqslant 2           & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
-%\rC_\ell,\ \ell \geqslant 2          & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
-%\rD_\ell,\ \ell\geqslant 4           & 1    & \ell   & \sr(I) \leqslant \ell-2 \\ 
-%\rD_\ell,\ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2      \\
-%\rE_\ell,\ \ell=6,7                  & \ell & 2      & \sr(I) \leqslant \ell-3 \\ 
-%\rE_\ell,\ \ell=6,7                  & \ell & 1      & \asr(I)\leqslant \ell-2 \\ 
+%\rA_\ell, \ \ell\geqslant 2           & 1    & \ell   & \sr(I) \leqslant \ell-1 \\    
+%\rB_\ell, \ \ell\geqslant 2           & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
+%\rC_\ell, \ \ell \geqslant 2          & 1    & \ell   & \sr(I) \leqslant \ell-1 \\
+%\rD_\ell, \ \ell\geqslant 4           & 1    & \ell   & \sr(I) \leqslant \ell-2 \\ 
+%\rD_\ell, \ \ell\geqslant 4           & \ell & \ell-1 & \sr(I) \leqslant 2      \\
+%\rE_\ell, \ \ell=6, 7                  & \ell & 2      & \sr(I) \leqslant \ell-3 \\ 
+%\rE_\ell, \ \ell=6, 7                  & \ell & 1      & \asr(I)\leqslant \ell-2 \\ 
 %\rF_4                                & 4    & 1      & \asr(I)\leqslant 3 \end{array}\]
-Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$ consisting of elements which normalize the subset $A_{rs}$, i.\,e.
+Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$ consisting of elements which normalize the subset $A_{rs}$, i.\, e.
 \[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \right\}. \]
@@
 \begin{lemma}\label{lemma:dv-normal} 
-For every $\alpha \in \Delta_{\{r,s\}} \cup (\Phi^+ \setminus (\Sigma^+_r \cap \Sigma^+_s))$ one has $X_\alpha(R) \subseteq N_{rs}$. \end{lemma}
+For every $\alpha \in \Delta_{\{r, s\}} \cup (\Phi^+ \setminus (\Sigma^+_r \cap \Sigma^+_s))$ one has $X_\alpha(R) \subseteq N_{rs}$. \end{lemma}
 \begin{proof}
 Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence a fortiori it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
-Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r,s\}}, R)$ we obtain the assertion of the lemma for $\alpha \in \Delta_{\{r, s\}}$.
+Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r, s\}}, R)$ we obtain the assertion of the lemma for $\alpha \in \Delta_{\{r, s\}}$.
 
@@
 \Phi                                 & s    &r      & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\Delta_r$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
-\rA_\ell,\ \ell\geqslant 2           & 1    &\ell   & \ell+1         & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
-\rB_\ell,\ \ell\geqslant 2           & 1    &\ell   & 2\ell+1        & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
-\rC_\ell,\ \ell\geqslant 2           & 1    &\ell   & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\
-\rD_\ell,\ \ell\geqslant 4           & 1    &\ell   & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 2  \\ 
-\rD_\ell,\ \ell\geqslant 4           & \ell &\ell-1 & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
-\rE_\ell,\ \ell=6,7                  & \ell &2      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
-\rE_\ell,\ \ell=6,7                  & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \\
+\rA_\ell, \ \ell\geqslant 2           & 1    &\ell   & \ell+1         & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rB_\ell, \ \ell\geqslant 2           & 1    &\ell   & 2\ell+1        & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rC_\ell, \ \ell\geqslant 2           & 1    &\ell   & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\
+\rD_\ell, \ \ell\geqslant 4           & 1    &\ell   & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 2  \\ 
+\rD_\ell, \ \ell\geqslant 4           & \ell &\ell-1 & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
+\rE_\ell, \ \ell=6, 7                  & \ell &2      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
+\rE_\ell, \ \ell=6, 7                  & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \\
 \rF_4                                & 4    &1     & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
@@
 Denote by $L_{rs}$ the set consisting of all the elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
-It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\, e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
 \begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
@@
  \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case we get that $N_{rs}$ contains the subgroup generated by the root subgroups $X_\alpha(R)$, where $\alpha$ varies over long roots of $\Sigma_s^+$.
-  It remains to prove the inclusion $X_{1,0}(R) \subset N_{rs}$.
-  Specializing identity~\eqref{rel:CCF} we get \begin{equation*} \label{rel:CCF-specBC} x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2) \end{equation*}
-  Since $X_{2, 0}(R)$ and $X_{1,-2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1,0}(R) \subseteq N_{rs}$ follows.
+  It remains to prove the inclusion $X_{1, 0}(R) \subset N_{rs}$.
+  Specializing identity~\eqref{rel:CCF} we get \begin{equation*} \label{rel:CCF-specBC} x_{1, 0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1, -2}(-a b^2) \end{equation*}
+  Since $X_{2, 0}(R)$ and $X_{1, -2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1, 0}(R) \subseteq N_{rs}$ follows.
  \item \textit{Case $\Phi = \rC_\ell, \rF_4$.}
@@
 For $\Phi=\rB_\ell$ one has to once again apply Chevalley commutator formula~\eqref{rel:CCF}:
-\[ X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{x_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
+\[ X_{0, 1}(I) \subseteq X_{2, 1}(I) \cdot X_{2, 1}(I)^{x_{0, 2}(1)} \cdot X_{-2, 1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
 \end{proof}
@@
 \begin{itemize}
- \item \textsc{Case $\Phi=\rC_\ell$.} Matrix entries $(g_{i,2})$, $i=2,\ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
+ \item \textsc{Case $\Phi=\rC_\ell$.} Matrix entries $(g_{i, 2})$, $i=2, \ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
  \item \textsc{Case $\Phi=\rF_4$.} Matrix entries $(g_{\lambda, \lambda}, \ldots, g_{\lambda, \lambda - \alpha_3 - \alpha_2 - \alpha_1})$, where $\lambda = \varpi_4 - \alpha_4$ (see~\cite[Fig.~26]{PSV98}),
@@
 
-By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s^+ \cap \Delta_r, I)$ such that $(y \cdot g)_{\varpi_s,\varpi_s - \alpha_s} = 0$.
+By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s^+ \cap \Delta_r, I)$ such that $(y \cdot g)_{\varpi_s, \varpi_s - \alpha_s} = 0$.
 Consequently, for every $g\in C$ one has
@@
 \end{multline*}
-Notice that the matrix entry $(yg)_{\varpi_s,\varpi_s}$ is invertible.
+Notice that the matrix entry $(yg)_{\varpi_s, \varpi_s}$ is invertible.
 From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1:=(yg)^{x_{-\alpha_s}(\xi)}$

### 2015-10-11 gauss.tex
Commas spaces in Gauss, DV, CB and SF

@@
 two reductive subsystems of $\Phi$ corresponding to the endnodes of the Dynkin diagram of $\Phi$.
-Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1,\ell$ admit triangular decomposition with $N$ triangular factors:
-\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I),\quad i=1,\ell. \]
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit triangular decomposition with $N$ triangular factors:
+\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I), \quad i=1, \ell. \]
 Then the group $\E(\Phi, R, I)$ admits the decomposition with the same number of factors:
-\[ \E(\Phi, R, I) = \Hh(\Phi,R,I) \cdot \U(\Phi^+,I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm,I). \]
+\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm, I). \]
 \end{prop}
@@
 Denote by $Y$ the product of subgroups in the right-hand side of the above equality.
-To show that $Y=\E(\Phi,R,I)$ it suffices to check that
+To show that $Y=\E(\Phi, R, I)$ it suffices to check that
 \begin{enumerate}
-\item $Y$ is normalized by $\E(\Phi,R)$, i.\,e. $Y^{\E(\Phi,R)}\subseteq Y$;
-\item there exists a set $X$ generating $\E(\Phi,R,I)$ as a \emph{normal} subgroup of $\E(\Phi,R)$ such that $XY\subseteq Y$.
+\item $Y$ is normalized by $\E(\Phi, R)$, i.\, e. $Y^{\E(\Phi, R)}\subseteq Y$;
+\item there exists a set $X$ generating $\E(\Phi, R, I)$ as a \emph{normal} subgroup of $\E(\Phi, R)$ such that $XY\subseteq Y$.
 \end{enumerate}
@@
 Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or $i=\ell$ and we can expand $Y$ as follows:
-\[ Y=\Hh(\Phi,R,I) \cdot \U(\Delta_i^+,I) \cdot \ldots \cdot \U^\pm(\Delta_i,I) \cdot \U(\Sigma_i^+,I) \cdot \ldots \cdot \U(\Sigma_i^\pm,I). \]
+\[ Y=\Hh(\Phi, R, I) \cdot \U(\Delta_i^+, I) \cdot \ldots \cdot \U^\pm(\Delta_i, I) \cdot \U(\Sigma_i^+, I) \cdot \ldots \cdot \U(\Sigma_i^\pm, I). \]
 For every  $h \in \Hh(\Phi, R, I)$ one has for some $s\in I$
-\[ x_\alpha(\xi)\cdot h = h\cdot x_\alpha((1+s)\xi)=h\cdot x_\alpha(\xi)\,x_\alpha(s\xi). \]
+\[ x_\alpha(\xi)\cdot h = h\cdot x_\alpha((1+s)\xi)=h\cdot x_\alpha(\xi)\, x_\alpha(s\xi). \]
 
@@
 \begin{multline*}
-Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi,R,I) \cdot x_\alpha(-\xi) \cdot X_{\alpha}(I) \cdot \E(\Delta_i,R,I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) =\\
-= \Hh(\Phi, R, I) \cdot \E(\Delta_i,R,I) \cdot \U(\Sigma^+_i,I) \cdot \ldots \cdot \U(\Sigma^\pm_i,I) = Y.
+Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi, R, I) \cdot x_\alpha(-\xi) \cdot X_{\alpha}(I) \cdot \E(\Delta_i, R, I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) =\\
+= \Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) = Y.
 \end{multline*}
 
-Now set $X=\left\{x_\alpha(\xi)\ \middle|\ \alpha\in\Pi,\ \xi\in I \right\}$. 
+Now set $X=\left\{x_\alpha(\xi)\ \middle|\ \alpha\in\Pi, \ \xi\in I \right\}$. 
 Every root is a conjugate of some fundamental root under the action of $W(\Phi)$.
-Since $\E(\Phi,R)$ contains the normalizer of the torus, the set $X^{\E(\Phi,R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi),\  \alpha\in\Phi,\ \xi\in I \rangle$.
-Finally, the inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi,R,I)$ normalizes every root subgroup $X_\alpha(I)$.
+Since $\E(\Phi, R)$ contains the normalizer of the torus, the set $X^{\E(\Phi, R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi), \  \alpha\in\Phi, \ \xi\in I \rangle$.
+Finally, the inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi, R, I)$ normalizes every root subgroup $X_\alpha(I)$.
 \end{proof}

### 2015-10-11 subsystem-factorizations.tex
Commas spaces in Gauss, DV, CB and SF

@@
 %\begin{lemma}
-%Assume $\sr(I)\leqslant n-1$. Then $\SL(n+1,R,I)$ is a product of at most $5$ subgroups isomorphic to $\SL(n,R,I)$.
+%Assume $\sr(I)\leqslant n-1$. Then $\SL(n+1, R, I)$ is a product of at most $5$ subgroups isomorphic to $\SL(n, R, I)$.
 %\end{lemma}
 %\begin{proof}
-%By the Dennis---Vaserstein decomposition one can present $\SL(n+1,R,I)$ as a product
-%\[ \SL(n+1,R,I) =  \Par_1\cdot X_{n1}\cdot\Par_n=S_1\U_1\cdot X_{n1}\cdot\U_n S_n, \]
-%where $S_1$ and $S_n$ are two obvious embeddings of $\SL(n,R,I)$ in $\SL(n+1,R,I)$, avoiding respectively the first and the last row and column.
+%By the Dennis---Vaserstein decomposition one can present $\SL(n+1, R, I)$ as a product
+%\[ \SL(n+1, R, I) =  \Par_1\cdot X_{n1}\cdot\Par_n=S_1\U_1\cdot X_{n1}\cdot\U_n S_n, \]
+%where $S_1$ and $S_n$ are two obvious embeddings of $\SL(n, R, I)$ in $\SL(n+1, R, I)$, avoiding respectively the first and the last row and column.
 Now $\U_1=(\U_1\cap S_n)\cdot X_{1n}$ and $U_n= X_{1n}\cdot(U_n\cap S_1)$, while $X_{1n}X_{n1}X_{1n}\in S_1^{w_{12}(1)}$.
@@
 
-Consider the decreasing chain $\Phi_k$, $k=1,\ldots, \lfloor \ell/2 \rfloor$ of root subsystems of $\Phi=\rD_\ell$ defined as follows.
+Consider the decreasing chain $\Phi_k$, $k=1, \ldots, \lfloor \ell/2 \rfloor$ of root subsystems of $\Phi=\rD_\ell$ defined as follows.
 If $2k \neq \ell$ let $\Phi_k$ be the subsystem of $\Phi$ spanned by simple roots $\alpha_{2k-1}, \ldots, \alpha_\ell$.
@@
 In the remaining case $2k = \ell$ set $\Phi_k = \langle \alpha_\ell \rangle \cong \rA_1$.
-Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\,e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1,\ldots, \lfloor \ell/2 \rfloor$.
+Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\, e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1, \ldots, \lfloor \ell/2 \rfloor$.
 Denote by $B$ the set of all $\beta_k$. From the definition it is clear that elements of $B$ are mutually orthogonal to each other.
@@
 \begin{align*}
- \beta_k =  \alpha_{2k-1} + 2\alpha_{2k}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell, & \text{ for } k=1,\ldots,\lfloor\ell/2\rfloor-1, \\
- \beta_{\lfloor\ell/2\rfloor} = \alpha_{\ell-2}+\alpha_{\ell-1}+\alpha_\ell, & \text{ if $\ell$ is odd,} \\
+ \beta_k =  \alpha_{2k-1} + 2\alpha_{2k}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell, & \text{ for } k=1, \ldots, \lfloor\ell/2\rfloor-1, \\
+ \beta_{\lfloor\ell/2\rfloor} = \alpha_{\ell-2}+\alpha_{\ell-1}+\alpha_\ell, & \text{ if $\ell$ is odd, } \\
  \beta_{\lfloor\ell/2\rfloor} = \alpha_\ell, & \text{ if $\ell$ is even.}
@@
 Straightforward computation shows that 
-$$w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3,\quad w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1 $$
+$$w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \quad w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1 $$
 which implies the assertion of the lemma.
@@
 Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $R$ be a commutative ring.
-There exist an element $y\in\E(\Phi,R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell^+, I)\subset[\U(\Delta_\ell^-, I),y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
+There exist an element $y\in\E(\Phi, R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell^+, I)\subset[\U(\Delta_\ell^-, I), y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
 \end{lemma}
@@
 We will now show by induction on $\ell$ that 
-\begin{equation}\label{eq:ind-stat} \U(\Sigma_\ell^+\setminus B, I)\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I). \end{equation}
+\begin{equation}\label{eq:ind-stat} \U(\Sigma_\ell^+\setminus B, I)\subset[\U(\Delta_\ell^-, I), y]\cdot\U(B, I). \end{equation}
 The induction base in the cases $\ell=2, 3$ is trivial.
@@
 Notice that $\beta_1$ is the only root of $\Phi$ satisfying $m_2(\beta_1)=2$, therefore the commutator formula~\eqref{rel:CCF} implies
-\[ \bigl[\U(\Delta_2^-, I),x_{\beta_1}(1)\bigr]=1. \]
+\[ \bigl[\U(\Delta_2^-, I), x_{\beta_1}(1)\bigr]=1. \]
 There is no root of the form $\gamma=\alpha+\beta$ with $\alpha\in\Sigma_2^-\cap\Delta_\ell$ and $\beta\in B\setminus\{\beta_1\}$, because such a root $\gamma$ must satisfy $m_2(\gamma)=-1$ and $m_\ell(\gamma)=1$.
 Thus~\eqref{rel:CCF} gives
-\[\Bigl[\U(\Sigma_2^-\cap\Delta_\ell, I),\prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
+\[\Bigl[\U(\Sigma_2^-\cap\Delta_\ell, I), \prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
 Since $B\setminus\{\beta_1\}\subset\Sigma_\ell^+\cap\Delta_2$, the above two identities imply
-\[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2,\ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell^+\cap\Delta_2, I).
+\[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2, \ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell^+\cap\Delta_2, I).
 \]
-Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$, $w\in\U(\Sigma_2^-\cap\Delta_{1,\ell}, I)$.
+Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$, $w\in\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$.
 Using the identity
 \begin{equation}\label{eq:comm-ab-c}
-[ab,c]={}^a[b,c]\cdot[a,c],
+[ab, c]={}^a[b, c]\cdot[a, c], 
 \end{equation}
 we can rewrite
-\[ [vw,x_{\beta_1}(1)] = {}^v[w,x_{\beta_1}(1)]\cdot[v,x_{\beta_1}(1)].  \]
-Since $\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $\U(\Sigma_2^-\cap\Delta_{1,\ell}, I)$ are abelian, it is easy to see that
-\[ [v,x_{\beta_1}(1)]\in\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I), \quad [w,x_{\beta_1}(1)]\in\U((\Sigma_1^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}, I). \]
+\[ [vw, x_{\beta_1}(1)] = {}^v[w, x_{\beta_1}(1)]\cdot[v, x_{\beta_1}(1)].  \]
+Since $\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$ are abelian, it is easy to see that
+\[ [v, x_{\beta_1}(1)]\in\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I), \quad [w, x_{\beta_1}(1)]\in\U((\Sigma_1^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}, I). \]
 Every element of $\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I)$ (resp.
@@
 Summing up the above arguments, we get that
-\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2,\ell}^-, I),y] \equiv \U((\Sigma_{1,2}^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I), \]
-hence the inclusion~\eqref{eq:ind-stat} follows from the induction hypothesis (applied to $\Delta_{1,2} \cong \rD_{\ell-2}$).
+\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2, \ell}^-, I), y] \equiv \U((\Sigma_{1, 2}^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I), \]
+hence the inclusion~\eqref{eq:ind-stat} follows from the induction hypothesis (applied to $\Delta_{1, 2} \cong \rD_{\ell-2}$).
 
 Finally, we have found $a\in\U(\Sigma_\ell^+\setminus B, I)$ and $b\in\U(\Delta_\ell^-, I)$
-such that $$a\in[b,y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-, I),y]\cdot\U(B, I).$$
+such that $$a\in[b, y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-, I), y]\cdot\U(B, I).$$
 Now the assertion of the lemma follows from~\cref{lemma:nikolov-weyl}.
@@
 \begin{multline*}
-\E(\rD_\ell,R,I) = \EP_{\ell}(R, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot\EP_{\ell-1}(R, I) = \\
+\E(\rD_\ell, R, I) = \EP_{\ell}(R, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot\EP_{\ell-1}(R, I) = \\
 = L \cdot\U(\Sigma_\ell^+, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot \big(L \cdot \U(\Sigma_\ell^+, I) \big)^\sigma.
 \end{multline*}  
-Now using \cref{lemma:nikolov-type-dl} one can find $y_1,y_2\in\G(\rD_\ell,R)$ and $w_1,w_2\in\widetilde{W}(\rD_\ell)$ such that
+Now using \cref{lemma:nikolov-type-dl} one can find $y_1, y_2\in\G(\rD_\ell, R)$ and $w_1, w_2\in\widetilde{W}(\rD_\ell)$ such that
 \begin{align*} & L \cdot \U(\Sigma_\ell^+, I) \subset L \cdot \U(\Delta_{\ell-1}^-, I) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-, I) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+, I), \\
 & \U(\Sigma_{\ell-1}^-\cap\Sigma_\ell^-, I) \subset \U(\Delta_\ell^+, I) \cdot {}^{y_2}\!\U(\Delta_\ell^+, I) \cdot {}^{w_2}\!\U(\Delta_\ell^-, I). \end{align*} 
-Thus $\E(\rD_\ell,R,I)$ is a product of at most $9$ conjugates of $L \cong \E(\rA_{\ell-1}, R, I)$. \end{proof}
+Thus $\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of $L \cong \E(\rA_{\ell-1}, R, I)$. \end{proof}

### 2015-10-12 congrsubgr-boundgen.tex
No spaces alowed in \cref arguments, though
Abridged paper to 24 pages

@@
 By \cref{lemma:Stepanov-ideal} the group $\E\left(\Phi, \mathcal{O}_S, I^2\right)$ is contained in $\E(\Phi, I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
-Notice that under the assumptions of the lemma it is known that $\E(\Phi, I)$ has finite width with respect to $\mathcal{X}$, see~\cite{Tavgen93} or \cite[Theorem~3.3]{TavgenThesis}.
+Notice that under the assumptions of the lemma it is known that $\E(\Phi, I)$ has finite width with respect to $\mathcal{X}$, see~\cite[Theorem~3.3]{TavgenThesis}.
 
@@
 \begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.
-The the first and the third assertions follow from \cref{lemma:Z1p, lemma:width-dedekind}. \end{proof}
+The the first and the third assertions follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}

### 2015-10-12 paper.tex
Abridged paper to 24 pages

@@
 \end{thm}
-The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{Tavgen93, TavgenThesis}), 
+The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{TavgenThesis}), 
 while for the second and the third assertion we give a direct proof.

### 2015-10-12 paper.tex
Removed unused bibliography items

@@
 \end{thm}
-In the special case when $I$ is contained in the Jacobson radical of $R$ \cref{thm:srRI1} boils down to~\cite[Proposition~2.3]{AbeSuzNormalSubgroups}. 
+In the special case when $I$ is contained in the Jacobson radical of $R$ \cref{thm:srRI1} boils down to~\cite[Proposition~2.3]{Abe76}. 
 We also note that the absolute case (i.\, e. $I=R$) of the theorem was treated by the second named author in~\cite{Sm12}.
@@
 Another application of parabolic factorizations developed in this paper are subsystem factorizations in terms of subgroups of type $\rA_1$.
-The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{LiebNikShaSL2}.
+The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{LNS11}.
 More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
 
-In~\cite{VavKovSL2} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
+In~\cite{V13} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
 In fact, in the context of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
@@
 Our yet another application of parabolic factorizations concerns product decompositions of Chevalley groups formulated in terms of subgroups of type $\rA_\ell$ of submaximal rank.
-Recall that in \cite{NikProdDecomp} N.~Nikolov proves the following result. 
+Recall that in \cite{Nik07} N.~Nikolov proves the following result. 
 \begin{thm*} Let $G$ be a classical Chevalley group (of normal or twisted type) of rank $\ell$ over a finite field $F$.
@@
 
-Applying \cref{thm:DennisVaserstein} and proving a more accurate version of \cite[Proposition~1]{NikProdDecomp} in the special case $\Phi=\rD_\ell$ we obtain the following result.
+Applying \cref{thm:DennisVaserstein} and proving a more accurate version of \cite[Proposition~1]{Nik07} in the special case $\Phi=\rD_\ell$ we obtain the following result.
 \begin{thm}\label{thm:spin-sln-prod}
@@
 \end{prop}
-\begin{proof} Follows from \cite[Theorem~3.6]{BassMilnorSerre} and \cite[Corollary~4.5]{Ma69}. \end{proof}
+\begin{proof} Follows from \cite[Theorem~3.6]{BMS} and \cite[Corollary~4.5]{Ma69}. \end{proof}
 

### 2015-10-12 stability-conditions.tex
Abridged paper to 24 pages
Removed unused bibliography items

@@
 \begin{itemize}
-\item $\asr(R) = 1$ for every semilocal ring $R$;
+%\item $\asr(R) = 1$ for every semilocal ring $R$;
 \item $\asr(R)\leqslant2$ for every Dedekind domain $R$;
@@
 
-The last estimate further improves to $\sr(F[x_1, \ldots, x_n])\leqslant n$ for $F$ algebraic over a finite field (see~\cite[Corollary~17.4]{VasSusSerreProblem}).
+The last estimate further improves to $\sr(F[x_1, \ldots, x_n])\leqslant n$ for $F$ algebraic over a finite field (see~\cite[Corollary~17.4]{VS76}).
 For certain classes of fields there is also a lower estimate for $\sr(F[x_1, \ldots, x_n])$ which allows to compute precisely the value of both $\sr(R)$ and $\asr(R)$.
-For example, $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ (see~\cite{KrusenmeyerThesis}) and $\sr(F[x_1, \ldots, x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
-Notice also that $\sr(\mathbb{Z}[x])=3$ (see \cite{GruMenVasSL2ZxSL2kxy}) and $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ for $n>1$ (see example after~\cite[Theorem~18.2]{VasSusSerreProblem}).
+For example, $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ (see~\cite{Kru73}) and $\sr(F[x_1, \ldots, x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
+Notice also that $\sr(\mathbb{Z}[x])=3$ (see \cite{GMV}) and $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ for $n>1$ (see example after~\cite[Theorem~18.2]{VS76}).
 \end{example}

### 2015-10-15 bass-kolster.tex
Luzgarev comments + spacing in latin corrected

@@
 In the assumptions and notation of \cref{thm:BassKolster} every element of $\G(\Phi, R, I)$ 
-can be factored into a product of one element of $\G(\Delta_1, R, I)$ one element of $Z$ and at most $4|\Sigma_1|-1$ elements of $\mathcal{X}$.
+can be factored into a product of one element of $\G(\Delta_1, R, I)$, one element of $Z$ and at most $4|\Sigma_1|-1$ elements of $\mathcal{X}$.
 \end{cor}

### 2015-10-15 dennis-vaserstein.tex
Luzgarev comments + spacing in latin corrected

@@
 
-%The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\, e. $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
+%The relative elementary subgroup $\E(\Phi, R, I)$ admits Dennis---Vaserstein decomposition, i.\,e. $\E(\Phi, R, I) = A_{rs}$ under the following assumptions on $I$ and $\Phi$.
 %\[\begin{array}{l@{\qquad}c@{\quad}c@{\qquad}l}
@@
 %\rF_4                                & 4    & 1      & \asr(I)\leqslant 3 \end{array}\]
-Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$ consisting of elements which normalize the subset $A_{rs}$, i.\, e.
+Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$ consisting of elements which normalize the subset $A_{rs}$, i.\,e.
 \[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \right\}. \]
@@
 Denote by $L_{rs}$ the set consisting of all the elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
-It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\, e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
 \begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}

### 2015-10-15 paper.tex
Luzgarev comments + spacing in latin corrected

@@
 %Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots.
-Let $\G(\Phi, R)$ the split simply-connected Chevalley group of type $\Phi$ over arbitarary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup}
-i.\, e. the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$ see~\cite{VP, St78, S}.
+Let $\G(\Phi, R)$ be the simply-connected Chevalley group of type $\Phi$ over arbitrary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup}
+i.\,e., the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$, see~\cite{VP, St78, S}.
 For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (aka \emph{principal congruence subgroup}) of level $I$, 
-i.\, e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection $R\rightarrow R/I$.
+i.\,e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection $R\rightarrow R/I$.
 
@@
 It is a classical result of J.~Tits and L.~Vaserstein (see~\cite{Tits76}, \cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
-the set of elements $\mathcal{Z}(\Phi) = \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in \Phi\}.$
+the set of elements $\mathcal{Z}(\Phi)$.
+
+Here for a subset of roots $S\subseteq\Phi$ we denote by $\mathcal{Z}(S)$ the set
+\[ \mathcal{Z}(S) = \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in \Phi\}.\]
 
@@
 %\begin{itemize}
-%\item \emph{Gauss decomposition, } i.\, e. a decomposition of the form $\E(\Phi, R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup, 
+%\item \emph{Gauss decomposition, } i.\,e. a decomposition of the form $\E(\Phi, R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup, 
 %      and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
@@
 Let $\Phi$ be a root system, let $I$ be an ideal of arbitrary commutative ring $R$ such that $\sr(I)=1$.
-Then the relative elementary Chevalley $\E(\Phi, R, I)$ group admits the following decomposition
+Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits the following decomposition
 \[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi, I). \]
 \end{thm}
-In the special case when $I$ is contained in the Jacobson radical of $R$ \cref{thm:srRI1} boils down to~\cite[Proposition~2.3]{Abe76}. 
-We also note that the absolute case (i.\, e. $I=R$) of the theorem was treated by the second named author in~\cite{Sm12}.
+In the special case when $I$ is contained in the Jacobson radical of $R$, \cref{thm:srRI1} boils down to~\cite[Proposition~2.3]{Abe76}. 
+We also note that the absolute case (i.\,e. $I=R$) of the theorem was treated by the second named author in~\cite{Sm12}.
 
@@
 Let $G$ be an abstract group with a generating set $X \subset G$. 
-We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\, e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
-%The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $x_\alpha(\xi)$ has been extensively studied in a number of works (see e.\, g.
+We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
+%The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $x_\alpha(\xi)$ has been extensively studied in a number of works (see e.\,g.
 \cite{CK83, Ka82, Tavgen91, Mo07, VseUnitrZ1p, VavSmSuUnitrEng}).
-%Summarizing results of these works, one can hope that such width is finite only for rather narrow classes of rings of number-theoretic nature, e.\, g.
+%Summarizing results of these works, one can hope that such width is finite only for rather narrow classes of rings of number-theoretic nature, e.\,g.
 localizations of Dedeking rings of arithmetic type.
@@
 $W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
-\item If $\sr(I) = 1$ and $\Phi$ is arbitrary irreducible root system then 
+\item If $\sr(I) = 1$ and $\Phi$ is arbitrary irreducible root system, then 
 \[W(\E(\Phi, R, I), \mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1;\]
@@
 In fact, in the context of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
-Our next result further extends this to even larger class of rings (which e.\, g. includes ideals of all Dedekind rings).
+Our next result further extends this to even larger class of rings (which e.\,g. includes ideals of all Dedekind rings).
 \begin{thm}\label{thm:SL2width}
@@
 For any collection of subsets $H_1, \ldots, H_n$ of a group $G$ we denote by $H_1\ldots H_n$ their Minkowski set-product, 
-i.\, e. the set consisting of arbitrary products $h_1\ldots h_n$ of elements $h_i\in H_i$. In particular, the equality
+i.\,e. the set consisting of arbitrary products $h_1\ldots h_n$ of elements $h_i\in H_i$. In particular, the equality
 $G = H_1\cdot\ldots\cdot H_n$ means that every element $g\in G$ can be presented as a product $h_1\ldots h_n$ for $h_i\in H_i$.
@@
 Let $\alpha_\mathrm{max}$ denote the maximal root of $\Phi$.
-For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th component of $\alpha$ in $\Pi$, i.\, e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
+For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th component of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
 
@@
 We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\beta, \beta)$.
-Let $\varpi_1, \ldots, \varpi_\ell$ be the \emph{fundamental weights }of $\Phi$, i.\, e. vectors
+Let $\varpi_1, \ldots, \varpi_\ell$ be the \emph{fundamental weights }of $\Phi$, i.\,e. vectors
 defined by $\langle\varpi_i, \alpha_j^\vee\rangle=\delta_{i, j}, $ where $\alpha^\vee = \frac{\alpha}{2(\alpha, \alpha)}$.
 
-Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all reflections $\sigma_\alpha$ where $\sigma_\alpha(\beta)=\beta-\langle\alpha, \beta \rangle\cdot \alpha$.
+Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all reflections $\sigma_\alpha$ where $\sigma_\alpha(\beta)=\beta-\langle\beta, \alpha \rangle\cdot \alpha$.
 For a reductive subset $\Delta\subseteq \Phi$ denote by $W(\Delta)$ the subgroup of $W(\Phi)$ generated by $\sigma_\alpha$ for $\alpha\in\Delta$.
@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
-We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\, g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
+We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
 
@@
 
-For an additive subset $I\subseteq R$ we denote by $X_\alpha(I)$ the corresponding \emph{root subgroup} of level $I$, i.\, e.
+For an additive subset $I\subseteq R$ we denote by $X_\alpha(I)$ the corresponding \emph{root subgroup} of level $I$, i.\,e.
 the subgroup consisting of all elementary root unipotents $x_\alpha(\xi)$, $\xi\in I$.
@@
 where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed through structure constants (cf.~\cite[\S13]{VP}).
-For a reductive subset $\Delta \subseteq \Phi$ denote by $\widetilde{W}(\Delta)$ the \emph{extended Weyl group}, i.\, e.
+For a reductive subset $\Delta \subseteq \Phi$ denote by $\widetilde{W}(\Delta)$ the \emph{extended Weyl group}, i.\,e.
 the subgroup of $\E(\Phi, R)$ generated by all $w_{\alpha}(1)$, $\alpha \in \Delta$.
@@
 
-A representation $\pi$ is called \emph{basic} if for every pair of non-zero weights $\lambda, \mu \in \Lambda^*(\pi)$ such that $\lambda - \mu \in \Pi$ one has $\sigma_\alpha(\lambda) = \mu$.
+A representation $\pi$ is called \emph{basic} if for every pair of non-zero weights $\lambda, \mu \in \Lambda^*(\pi)$ such that $\lambda - \mu \in \Pi$ one has $\sigma_\alpha(\lambda) = \mu$ for some $\alpha\in\Phi$.
 Obviously, this is equivalent to saying that $W(\Phi)$ acts transitively on $\Lambda(\pi)^*$.
@@
 The irreducible representations of Chevalley groups used in these paper form a sublist of~\cite[Table~2]{PSV98}.
-More specifically, all of them are \emph{fundamental} (i.\, e. their highest weight is fundamental) and basic.
+More specifically, all of them are \emph{fundamental} (i.\,e. their highest weight is fundamental) and basic.
 We widely employ the technique of \emph{weight diagrams} (see~\cite[\S~2]{PSV98}) to help visualize the structure of these representations.
-In the simplest case of a \emph{microweight} representation $\pi$ (i.\, e. $\pi$ such that $V_0 = 0$)
+In the simplest case of a \emph{microweight} representation $\pi$ (i.\,e. $\pi$ is basic and $V_0 = 0$)
 the weight diagram of $(V, \pi)$ is just an undirected graph whose vertices are in one-to-one correspondence with the elements of $\Lambda(\pi)$.

### 2015-10-15 stability-conditions.tex
Luzgarev comments + spacing in latin corrected

@@
 We say that $I$ satisfies stable range condition $\SR_n(I)$ if any $I$-unimodular row of length $n+1$ is stable.
-It is easy to see that $\SR_n(I)$ implies $\SR_m(I)$ for any $m\geqslant n$. 
+Vaserstein noted~\cite[Theorem~1]{Va71} that $\SR_n(I)$ implies $\SR_m(I)$ for any $m\geqslant n$. 
 It is also clear that condition $\SR_n(I)$ does not depend on the choice of the ambient ring $R$.
-By definition, the {\it stable rank} of $I$ (denoted $\sr(I)$) is the smallest natural $n$ such that $\SR_n(I)$ holds (we set $\sr(I)=\infty$ if no such $n$ exists).
+By definition, the {\it stable rank} of $I$ (denoted $\sr(I)$) is the smallest natural number $n$ such that $\SR_n(I)$ holds (we set $\sr(I)=\infty$ if no such $n$ exists).
 

### 2015-10-17 congrsubgr-boundgen.tex
Removed unused bibliography items
More fixes

@@
 
-The following lemma is a corollary of Theorems~5.7 and 5.8 of \cite{LenMorStePrimitiveRoot}.
+The following lemma is a corollary of Theorems~5.7 and 5.8 of~\cite{LSM}.
 \begin{lemma}
@@
 of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators $\mathcal{Z}(\Sigma_\ell)$ and one element of 
-$\G(\{\alpha_\ell, -\alpha_\ell\}, \mathcal{O}_S, I)\cong\SL(2, \mathcal{O}_S, I)$.
+$G_0 = \G(\{\alpha_\ell, -\alpha_\ell\}, \mathcal{O}_S, I)\cong\SL(2, \mathcal{O}_S, I)$.
 Consequently, to prove the statement of the lemma it suffices to express every element 

### 2015-10-17 paper.tex
Tweaks in bibliography
One more minor tweak
More fixes

@@
 %Bibliography
+\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
 \renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
@@
 Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\E(\Phi, R)$ in terms of Tits generators and is, thus, a quantitative analogue of \cref{prop:Stepanov}
-and a relative analogue of the results of~\cite{CK83, Tavgen91, Mo07, VseUnitrZ1p, VavSmSuUnitrEng}.
+and a relative analogue of the results of~\cite{Tavgen91, VseUnitrZ1p, VavSmSuUnitrEng}.
 \begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.
@@
 \end{thm}
-The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{TavgenThesis}), 
+The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{TavgenThesis}, cf. also with \cite{Mo07}), 
 while for the second and the third assertion we give a direct proof.

### 2015-10-17 stability-conditions.tex
More fixes

@@
 \begin{enumerate}
-\item For any ideal $J\subseteq I$ one has $\sr(J)\leqslant\sr(I)$, $\sr(I/J)\leqslant\sr(I)$;
+\item For any ideal $I'\subseteq I$ one has $\sr(I')\leqslant\sr(I)$, $\sr(I/I')\leqslant\sr(I)$;
 \item One has $\sr\Bigl(\prod\limits_{i=1}^n R_i\Bigr)=\max\limits_{i=1}^n\bigl(\sr(R_i)\bigr)$;
-\item Let $J$ denote the Jacobson radical of $R$, then one has $\sr(R)=\sr(R/J)$;
-\item If $I\subseteq J$, then $\sr(I)=1$;
+\item Let $J(R)$ denote the Jacobson radical of $R$, then $\sr(R)=\sr(R/J(R))$ and $\sr(J(R))=1$;
 \item Let $I\rtimes\mathbb{Z}$ denote the ring obtained by formally adjoining $1$ to $I$. Then $\sr(I\rtimes\mathbb{Z})=\max(2,\sr(I))$.
@@
 \end{itemize}
-
-The last estimate further improves to $\sr(F[x_1, \ldots, x_n])\leqslant n$ for $F$ algebraic over a finite field (see~\cite[Corollary~17.4]{VS76}).
+%The last estimate further improves to $\sr(F[x_1, \ldots, x_n])\leqslant n$ for $F$ algebraic over a finite field (see~\cite[Corollary~17.4]{VS76}).
 For certain classes of fields there is also a lower estimate for $\sr(F[x_1, \ldots, x_n])$ which allows to compute precisely the value of both $\sr(R)$ and $\asr(R)$.

### 2015-10-17 paper.tex
Fixed definition of \mathcal{Z}(S)

@@
 Here for a subset of roots $S\subseteq\Phi$ we denote by $\mathcal{Z}(S)$ the set
-\[ \mathcal{Z}(S) = \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in \Phi\}.\]
+\[ \mathcal{Z}(S) =  \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in S\}.\]
 
@@
 Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be any parabolic subset of roots.
-Let $\Sigma_S$ be the special part of $S$, then $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$, where
-$$\mathcal{Z}(\Sigma) = \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s \in I, \ \xi \in R, \ \alpha\in \Sigma \}.$$ \end{prop}
+Let $\Sigma_S$ be the special part of $S$, then $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$. \end{prop}
 

### 2015-10-20 bass-kolster.tex
Final language, punctuation, typography and notation fixes; sending to the seminar mailing list

@@
-The next theorem is a relative version of the so called Bass---Kolster decomposition (cf.~\cite[Theorem~2.1]{St78}).
+The next theorem is a relative version of the so-called Bass---Kolster decomposition (cf.~\cite[Theorem~2.1]{St78}).
 \begin{thm}\label{thm:BassKolster}
@@
 \end{array}\]
-Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of Bass---Kolster decomposition:
+Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of the Bass---Kolster decomposition:
 \[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]
@@
 Notice that the column $(v_1, \ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
-Applying condition $\sr(I)\leq 2\ell-1$ we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
+Applying the assumption $\sr(I)\leqslant 2\ell-1$, we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
 By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for
@@
 \[ h_2 = x_{-1, 1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1, i}(\xi f_i) \in \U(\Sigma_1^-, I). \]
-Direct computation shows that $v'' = h_2 \cdot v'$ satisfies equalities~\eqref{eq1}.
+Direct computation shows that the vector $v'' = h_2 \cdot v'$ satisfies equalities~\eqref{eq1}.
 
@@
 By \cref{item:asrUnipD} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of $v'=h_1 \cdot v$ is $I$-unimodular.
-Since $\sr(I)\leq \ell-1$ we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
+Since $\sr(I)\leqslant \ell-1$, we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
 \[ v''=h_2 \cdot x_{1, 2}(c_1) \cdot v', \quad h_2=\prod_{i=3}^\ell x_{i, 2}(c_i). \]
@@
 \textsc{Case $\Phi=\rB_\ell$, $n=2\ell+1$.} Subdivide $v\in \Ums(2\ell+1, I)$ as $v=(v_+, v_0, v_-)\in R^\ell\times R\times R^\ell$.
-Denote by $J\leq I$ the ideal spanned by components of $v_-$.
-Since $\sr(I/J)\leq \ell$ we can find $c_1, \dots, c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell x_{i, 0}(c_i) \in \U(\Phi^+, I)$
+Denote by $J\leqslant I$ the ideal spanned by the components of $v_-$.
+Since $\sr(I/J)\leqslant \ell$, we can find $c_1, \dots, c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell x_{i, 0}(c_i) \in \U(\Phi^+, I)$
 one has $\bar{v'}_+=(\bar{v'_1}, \ldots, \bar{v'_\ell}) \in \Ums(\ell, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, I)$.
@@
 \end{equation*}
-We can present an element $g$ of $\U(\Sigma_\ell^+, I)$ as a product of $g_1 \in \U(\Sigma_{\{1, 2\}^+} \cap \Sigma_\ell^+)$ and $g_2\in \U(\Delta_{\{1, 2\}}\cap \Sigma_\ell^+)$.
-An examination of the extended Dynkin diagram of $\rD_\ell$ implies that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one)
+We can present an element $g$ of $\U(\Sigma_\ell^+, I)$ as a product of $g_1 \in \U(\Sigma_{1, 2}^+ \cap \Sigma_\ell^+)$ and $g_2\in \U(\Delta_{1, 2}\cap \Sigma_\ell^+)$.
+An examination of the extended Dynkin diagram of $\rD_\ell$ shows that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one)
 and therefore can be moved to the right until it is consumed by $\G(\Delta_1, R, I)$.
-On the other hand, $g_1$ is a product of at most $2\ell-3$ elementary unipotents, while the width of $\U(\Sigma_1^\pm, I)$ and $\U(\Sigma_2^-\cap\Delta_1)$ in elementary unipotents does not exceed $2\ell-2$ and $2\ell-4$, respectively.
-Summing up these upper bounds we obtain
+On the other hand, $g_1$ is a product of at most $2\ell-3$ elementary unipotents, while the width of $\U(\Sigma_1^\pm, I)$ and $\U(\Sigma_2^-\cap\Delta_1)$ with respect to the elementary unipotents does not exceed $2\ell-2$ and $2\ell-4$, respectively.
+Summing up these upper bounds, we obtain
 $$(2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9 = 4|\Sigma_1| - 1.$$
@@
 \end{proof}
+\begin{proof}[Proof of \cref{thm:SL2width}]
+ As in the proof of the above corollary one has to iteratively apply \cref{thm:BassKolster}.
+ To reduce the number of $\SL_2$-factors involved in the decompositoin one has to group into a single $\SL_2$-factor a pair of opposite root subgroups $X_{\alpha}(I)$, $X_{-\alpha}(I)$ (or $Z_{\pm\alpha}(I)$) appearing on each
+ of the $3$ junctions between the positive and negative unipotent subgroups in the Bass---Kolster decomposition.
+ Since a total of $\ell-1$ reductions are used, we get the estimate $N \leq N' - 3(\ell - 1) + 1$ and the assertion of \cref{thm:SL2width} follows.
+\end{proof}
 \begin{figure}[hb]\label{fig:bass-kolster}
@@
 \end{tikzcd}\] \caption{Reductions used in the proof of \cref{cor:bass-kolster-iterated} and \cref{thm:SL2width}} \end{figure}
-\begin{proof}[Proof of \cref{thm:SL2width}]
- As in the proof of the above corollary one has to iteratively apply \cref{thm:BassKolster}.
- To reduce the number of $\SL_2$-factors involved in the decompositoin one has to group into a single $\SL_2$-factor a pair of opposite root subgroups $X_{\alpha}(I)$, $X_{-\alpha}(I)$ (or $Z_{\pm\alpha}(I)$) appearing on each
- of the $3$ junctions between the positive and negative unipotent subgroups in the Bass---Kolster decomposition.
- Since a total of $\ell-1$ reductions are used, we get the estimate $N \leq N' - 3(\ell - 1) + 1$ and the assertion of \cref{thm:SL2width} follows.
-\end{proof}

### 2015-10-20 congrsubgr-boundgen.tex
Final language, punctuation, typography and notation fixes; sending to the seminar mailing list

@@
-We now give an application of parabolic factorizations to the problem of bounded generation.
+We now give an application of the parabolic factorizations to the problem of bounded generation.
 
@@
 Let $p$ be a rational prime, let $c$, $d$ be a pair of coprime integers such that $p \perp d$.
-Then under the assumption of Generalized Riemann Hypothesis there exist infinitely many primes $q\equiv c\pmod{d}$ such that $p$ is a primitive root modulo $q$.
+Then under the assumption of the Generalized Riemann Hypothesis there exist infinitely many primes $q\equiv c\pmod{d}$ such that $p$ is a primitive root modulo $q$.
 \end{lemma}
 
-The following lemma is a relative version of \cite[Lemma~6]{VavSmSuUnitrEng} (cf. also \cite{VseUnitrZ1p}):
+The following lemma is a relative version of \cite[Lemma~6]{VavSmSuUnitrEng} (see also~\cite{VseUnitrZ1p}):
 
@@
 Set $R=\mathbb{Z}[\sfrac{1}{p}]$ and let $I$ be an ideal of $R$.
-Under the assumption of GRH the width of $\SL(2,R,I)$ with respect to the generating set $$\mathcal{Z}(\{-\alpha_1\})=X_{12}(I)\cup X_{21}(I) \cup \{z_{21}(s, \xi) \mid s\in I,\ \xi\in R\}$$ does not exceed $6$.
+Under the assumption of the GRH the width of $\SL(2, R, I)$ with respect to the generating set
+\[ \mathcal{Z}(\{-\alpha_1\})=X_{12}(I)\cup X_{21}(I) \cup \{z_{21}(s, \xi) \mid s\in I,\ \xi\in R\} \]
+does not exceed $6$.
 \end{lemma}
@@
 such that $p$ is a primitive root modulo $q$. 
-Without loss of generality we may assume that $q$ is prime to $b$. 
+We may assume that $q$ is prime to $b$. 
 Write
@@
 \intertext{
-Since $g_2\equiv 1\pmod m$, we can write $p^\beta q=1+cm$ for some $c$. Now let
+Since $g_2\equiv 1\pmod m$, we can write $p^\beta q=1+cm$ for some $c$. Now set
 }
@@
 For the rest of this subsection $k$ denotes a global field. We assume that there is some finite set of places $S$ chosen on $k$. 
-Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type defined by $S$ and let $I$ be any ideal of $\mathcal{O}_S$.
+Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type defined by $S$ and let $I$ be an ideal of $\mathcal{O}_S$.
 
@@
 \begin{proof}
-First of all, notice that $\asr(I) \leq \asr(\mathcal{O}_S) \leq 2$. 
+First of all, notice that $\asr(I) \leqslant \asr(\mathcal{O}_S) \leqslant 2$. 
 By \cref{cor:bass-kolster-iterated} we can present any element 
-of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators $\mathcal{Z}(\Sigma_\ell)$ and one element of 
+of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators from $\mathcal{Z}(\Sigma_\ell)$ and one element of 
 $G_0 = \G(\{\alpha_\ell, -\alpha_\ell\}, \mathcal{O}_S, I)\cong\SL(2, \mathcal{O}_S, I)$.
@@
 From $\det(g)=1$ we conclude that $a+d=bc-ad\in I^2$. 
-Recall that Vaserstein's congruence subgroup is defined as
+Recall that the Vaserstein's congruence subgroup is defined as
 \[ G(I, I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2, \mathcal{O}_S)\;\middle|\; a, d\in I^2, \ b, c\in I \right\}. \]
-Notice that $g_1=g\cdot z_{21}(a, 1)$ is contained in $G(I, I)$, indeed
+Notice that $g_1=g\cdot z_{21}(a, 1)$ is contained in $G(I, I)$, indeed,
 \[ \begin{pmatrix} 1+a & b \\ c & 1+d \end{pmatrix} \cdot \begin{pmatrix} 1-a & -a \\ a & 1+a \end{pmatrix} = \begin{pmatrix} 1+ba-a^2 & b-a-ba-a^2 \\ c+a+ad-ac & 1+bc-ac \end{pmatrix} \in G(I, I). \]
@@
 
-In remains to consider the case $\Phi=\rC_\ell$. First of all, notice that $2abc-abd\in II^{\indexbox{2}}$, indeed
+In remains to consider the case $\Phi=\rC_\ell$. First of all, notice that $2abc-abd\in II^{\indexbox{2}}$, indeed,
 \[ \det(g_1)=a^3d-3a^2bc+a^2bd+ab^2c+a^3+a^2b+a^2d+2abc-abd+1. \]
-Consequently, we have that
+This means that
 \[ g_2=x_{21}(-a-c)\cdot g_1\cdot x_{12}(a-b)\equiv

### 2015-10-20 dennis-vaserstein.tex
Final language, punctuation, typography and notation fixes; sending to the seminar mailing list

@@
 Let $\Phi$ be an irreducible root system of rank $\ell$.
-In what follows, $r$ and $s$ are two distinct integers such that $1 \leq r, s \leq \ell$.
-From Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
+In what follows, $r$ and $s$ are two distinct integers such that $1 \leqslant r, s \leqslant \ell$.
+From the Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
 \begin{multline*}
-A_{rs} := \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
+A_{rs} \coloneqq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
 = \U(\Sigma_r^+, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \hspace{5em} \\
@@
 %\rF_4                                & 4    & 1      & \asr(I)\leqslant 3 \end{array}\]
-Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$ consisting of elements which normalize the subset $A_{rs}$, i.\,e.
+Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$, consisting of the elements which normalize the subset $A_{rs}$, i.\,e.
 \[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \right\}. \]
@@
 \begin{lemma}\label{lemma:dv-normal} 
-For every $\alpha \in \Delta_{\{r, s\}} \cup (\Phi^+ \setminus (\Sigma^+_r \cap \Sigma^+_s))$ one has $X_\alpha(R) \subseteq N_{rs}$. \end{lemma}
+For every $\alpha \in \Delta_{r, s} \cup (\Phi^+ \setminus (\Sigma^+_r \cap \Sigma^+_s))$ one has $X_\alpha(R) \subseteq N_{rs}$. \end{lemma}
 \begin{proof}
 Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence a fortiori it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
-Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r, s\}}, R)$ we obtain the assertion of the lemma for $\alpha \in \Delta_{\{r, s\}}$.
+Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r, s\}}, R)$, we obtain the assertion of the lemma for $\alpha \in \Delta_{r, s}$.
 
-Now if $\alpha$ lies in $\Phi^+ \setminus \Sigma_r^+ \cap \Sigma_s^+$ it is contained either in $\Delta_r$ or in $\Delta_s$.
-Assume, for example, the latter. By Levi decomposition we have $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$
+Now if $\alpha$ lies in $\Phi^+ \setminus (\Sigma_r^+ \cap \Sigma_s^+)$, then it is contained either in $\Delta_r$ or in $\Delta_s$.
+Assume, for example, the latter. By the Levi decomposition we have $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$,
 which again implies the assertion of the lemma.
@@
 First of all, notice that in the case $\Phi=\rG_2$ the assertion of the theorem formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
-Since $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$.
+Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$:
 \begin{table}[htb]
@@
 The first step of the proof is to show that $N_{rs}$ contains sufficiently many elements. 
-This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke stability conditions for the first time.
+This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke the stability conditions for the first time.
 We show that $N_{rs}$ contains the root subgroup $X_{-\alpha\ssub{r}}(R)$, which together with \cref{lemma:dv-normal} and \cref{item-egen} immediately implies that $N_{rs}$ contains the Levi subgroup $\E(\Delta_s, R)$ and hence the extended Weyl group $\widetilde{W}(\Delta_s)$.
@@
   In this case all the roots of $\Sigma^+_s$ have the same $s$-shape and length, hence the assertion follows from \cref{item-trans2}, \eqref{rel:NnormL} and the fact that we already have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
- \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case we get that $N_{rs}$ contains the subgroup generated by the root subgroups $X_\alpha(R)$, where $\alpha$ varies over long roots of $\Sigma_s^+$.
+ \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case, we get that $N_{rs}$ contains the subgroup generated by the root subgroups $X_\alpha(R)$, where $\alpha$ varies over long roots of $\Sigma_s^+$.
   It remains to prove the inclusion $X_{1, 0}(R) \subset N_{rs}$.
-  Specializing identity~\eqref{rel:CCF} we get \begin{equation*} \label{rel:CCF-specBC} x_{1, 0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1, -2}(-a b^2) \end{equation*}
+  Specializing identity~\eqref{rel:CCF}, we get \begin{equation*} \label{rel:CCF-specBC} x_{1, 0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1, -2}(-a b^2) \end{equation*}
   Since $X_{2, 0}(R)$ and $X_{1, -2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1, 0}(R) \subseteq N_{rs}$ follows.
  \item \textit{Case $\Phi = \rC_\ell, \rF_4$.}
- We settle these remaining cases in \cref{lemma:DVST} where we invoke the stability conditions one more time. 
+ We settle these remaining cases in \cref{lemma:DVST}, where we invoke the stability conditions one more time. 
  In fact, we prove a stronger result, namely that $N_{rs}$ contains $X_{-\alpha\ssub{s}}(R)$ and, consequently, $N_{rs} = \E(\Phi, R)$.
@@
 In view of \cref{prop:Stepanov} to prove the theorem it suffices to show that $L_{rs}$ contains the generating set $\mathcal{Z}(\Sigma_s^-)$ of $\E(\Phi, R, I)$.
-From $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)}$ and \eqref{rel:NnormL} it follows that we only have to show $\mathcal{X} \subseteq L_{rs}$.
+From the inclusion $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)}$ and \eqref{rel:NnormL} it follows that we only have to show that $\mathcal{X} \subseteq L_{rs}$.
 
 The last inclusion follows from the same transitivity argument as above and the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
-For $\Phi=\rB_\ell$ one has to once again apply Chevalley commutator formula~\eqref{rel:CCF}:
+For $\Phi=\rB_\ell$ one has to once again apply the Chevalley commutator formula~\eqref{rel:CCF}:
 \[ X_{0, 1}(I) \subseteq X_{2, 1}(I) \cdot X_{2, 1}(I)^{x_{0, 2}(1)} \cdot X_{-2, 1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
@@
 \end{thmlist} \end{lemma}
-\begin{proof} The first two statements easily follow from Chevalley commutator formula~\eqref{rel:CCF} while the third one is a formal consequence of the first two. \end{proof}
+\begin{proof} The first two statements easily follow from the Chevalley commutator formula~\eqref{rel:CCF} while the third one is a formal consequence of the first two. \end{proof}
 
@@
 Notice that $\Delta_r$ is an irreducible classical root system of type $\rA_\ell$, $\rC_\ell$ or $\rD_\ell$.
-Denote by $(\pi', V')$ the irreducible component of the restriction of $\pi$ to $\G(\Delta_r, R)$ containing the highest weight vector $v^+$ of $\pi$.
+Denote by $(\pi', V')$ the irreducible component of the restriction of $\pi$ to $\G(\Delta_r, R)$ that contains the highest weight vector $v^+$ of $\pi$.
 In all the cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta, R)$.
@@
 
-The set $\Gamma$ can be visualized using weight diagrams in the following manner.
-After removing all bonds marked $r$ the weight diagram of $\pi$ splits into several connected components.
-The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram containing the vertex marked $\varpi_s$.
+The set $\Gamma$ can be visualized using the weight diagrams in the following manner.
+After the removal of all bonds marked $r$ the weight diagram of $\pi$ splits into several connected components.
+The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram that contains the vertex marked $\varpi_s$.
 Clearly, $\Gamma$ consists of the weights of $\Lambda(\pi')$ incident to the removed bonds.
 
-From a consideration of the weight diagrams (see~\cite{PSV98}) we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
+By a consideration of the weight diagrams (see~\cite{PSV98}) we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
 
-Consider the subset $B \subset \E(\Delta_r, R, I)$ consisting of elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
-Set $A:=\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
+Consider the subset $B \subset \E(\Delta_r, R, I)$, consisting of all elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
+Set $A\coloneqq\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
 
-Let $g$ be an element of $\E(\Delta_r, R, I)$. Applying \cref{lemma:uraction} to the subsystem $\Delta_r$ we find
-$x\in\U(\Delta_r^+, I)$, $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
+Let $g$ be an element of $\E(\Delta_r, R, I)$. Applying \cref{lemma:uraction} to the subsystem $\Delta_r$, we find
+$x\in\U(\Delta_r^+, I)$ and $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
 Consequenty, this shows that $A = A_{rs}$, indeed:
@@
 \[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I), \]
-which implies the following inclusion
+which implies the following inclusion:
 \begin{multline*}
@@
 \end{equation*}
-Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$ we obtain the assertion of the lemma, indeed
+Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$, we obtain the assertion of the lemma. Indeed,
 \begin{equation*} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A. \qedhere \end{equation*}
@@
 \begin{proof}
-Consider the subset $C \subseteq \EP_s(R, I)$ consisting of elements satisfying the following condition:
+Consider the subset $C \subseteq \EP_s(R, I)$, consisting of the elements satisfying the following condition:
 \begin{itemize}
@@
 Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot C$.
-By \cref{item:asrUnipC} (in the case $\Phi=\rC_\ell$) or \cref{cor:embeddingBD} (in the case $\Phi=\rF_4$) applied to the subgroup $\G(\Delta_s, R, I)$ 
+By \cref{item:asrUnipC} (in the case $\Phi=\rC_\ell$) or \cref{cor:embeddingBD} (in the case $\Phi=\rF_4$), applied to the subgroup $\G(\Delta_s, R, I)$,
 we find for every $g \in \EP_s(R, I)$ an element $x \in \U(\Sigma_r^+ \cap \Delta_s, I)$ such that $xg \in C$.  
 Notice that one immediately gets the equality $A_{rs} = A'$ from this.
-Indeed for $g\in \EP_s(R, I)$ one has
+Indeed, for $g\in \EP_s(R, I)$ one has
 \begin{equation*} \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq 
@@
 Notice that the matrix entry $(yg)_{\varpi_s, \varpi_s}$ is invertible.
-From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1:=(yg)^{x_{-\alpha_s}(\xi)}$
+From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1 \coloneqq (yg)^{x_{-\alpha_s}(\xi)}$
 satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_s^-, I)$, $h \in \EP_1(R, I)$.

### 2015-10-20 gauss.tex
Luzgarev comments + spacing in latin corrected
Final language, punctuation, typography and notation fixes; sending to the seminar mailing list

@@
-The proof of Gauss decomposition presented below is similar to the absolute case (cf. with the proof of~\cite[Theorem~5.1]{Sm12}).
+The proof of the Gauss decomposition presented below is similar to the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
 \begin{prop}\label{thm:Gauss}
-Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1, \Delta_\ell$ be
-two reductive subsystems of $\Phi$ corresponding to the endnodes of the Dynkin diagram of $\Phi$.
-Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit triangular decomposition with $N$ triangular factors:
+Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1$, $\Delta_\ell$ be
+two reductive subsystems of $\Phi$, corresponding to the endnodes of the Dynkin diagram of $\Phi$.
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit the triangular decomposition with $N$ triangular factors:
 \[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I), \quad i=1, \ell. \]
-Then the group $\E(\Phi, R, I)$ admits the decomposition with the same number of factors:
+Then the ambient group $\E(\Phi, R, I)$ admits the decomposition with the same number of factors:
 \[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm, I). \]
@@
 \begin{enumerate}
-\item $Y$ is normalized by $\E(\Phi, R)$, i.\, e. $Y^{\E(\Phi, R)}\subseteq Y$;
-\item there exists a set $X$ generating $\E(\Phi, R, I)$ as a \emph{normal} subgroup of $\E(\Phi, R)$ such that $XY\subseteq Y$.
+\item $Y$ is normalized by $\E(\Phi, R)$, i.\,e. $Y^{\E(\Phi, R)}\subseteq Y$;
+\item there exists a set $X$, generating $\E(\Phi, R, I)$ as a \emph{normal} subgroup of $\E(\Phi, R)$ such that $XY\subseteq Y$.
 \end{enumerate}
 To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for any $\alpha\in \pm \Pi$, $\xi\in R$.
-Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or $i=\ell$ and we can expand $Y$ as follows:
+Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or for $i=\ell$, and we can expand $Y$ as follows:
 \[ Y=\Hh(\Phi, R, I) \cdot \U(\Delta_i^+, I) \cdot \ldots \cdot \U^\pm(\Delta_i, I) \cdot \U(\Sigma_i^+, I) \cdot \ldots \cdot \U(\Sigma_i^\pm, I). \]
@@
 \begin{proof}[Proof of \cref{thm:srRI1}]
-In view of the above proposition it suffices to prove that Gauss decomposition of length $3$ holds for $\Phi=\rA_1$.
+In view of the above proposition it suffices to prove that the Gauss decomposition of length $3$ holds for $\Phi=\rA_1$.
 
@@
 The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
-Multiplying $A$ on the left by $x_{12}(z)$ we get matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible top-left corner element $a'$.
+Multiplying $A$ on the left by $x_{12}(z)$, we get a matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with the invertible  element $a'$ in the top-left corner.
 After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
-Thus we obtain relative Gauss decomposition of $A$
-\begin{equation}\nonumber
+Thus we have obtained the relative Gauss decomposition of $A$
+\begin{equation*}
 A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
@@
 \cdot x_{21}(y) \cdot x_{12}(b'/a'), 
-\end{equation}
+\end{equation*}
 where $\varepsilon\in 1+I$ and $y\in I$. \end{proof}

### 2015-10-20 paper.tex
Final language, punctuation, typography and notation fixes; sending to the seminar mailing list

@@
 \title {Decompositions of congruence subgroups of Chevalley groups}
-\keywords {Chevalley groups, principal congruence subgroups, stability for $\K_1$, bounded generation, $\SL_2$-factorizations. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
+\keywords {parabolic decompositions, stability for $\K_1$, bounded generation, $\SL_2$-factorizations, subsystem factorizations. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
 \author {Sergey Sinchuk, Andrei Smolensky}
@@
 %Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots.
-Let $\G(\Phi, R)$ be the simply-connected Chevalley group of type $\Phi$ over arbitrary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup}
-i.\,e., the subgroup generated by root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$, see~\cite{VP, St78, S}.
-For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (aka \emph{principal congruence subgroup}) of level $I$, 
+Let $\G(\Phi, R)$ be the simply-connected Chevalley group of type $\Phi$ over an arbitrary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup},
+i.\,e. the subgroup generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$, see~\cite{VP, St78, S}.
+For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (alias the \emph{principal congruence subgroup}) of level $I$, 
 i.\,e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection $R\rightarrow R/I$.
 
-We will also use the notion of the \emph{relative elementary Chevalley group} $\E(\Phi, R, I) \leqslant \G(\Phi, R, I)$.
-Recall that $\E(\Phi, R, I)$ is defined as the normal closure in $\E(\Phi, R)$ of the subgroup generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi, \ \xi \in I \}$.
+We will also use the notion of the \emph{relative elementary Chevalley subgroup} $\E(\Phi, R, I) \leqslant \G(\Phi, R, I)$.
+Recall that $\E(\Phi, R, I)$ is defined to be the normal closure in $\E(\Phi, R)$ of the subgroup generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi, \ \xi \in I \}$.
 
 Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
-It is a classical result of J.~Tits and L.~Vaserstein (see~\cite{Tits76}, \cite[Theorem~2]{Va86}) that the relative elementary group $\E(\Phi, R, I)$ is generated by
+It is a classical result of J.~Tits and L.~Vaserstein (see~\cite{Tits76}, \cite[Theorem~2]{Va86}) that the relative elementary subgroup $\E(\Phi, R, I)$ is generated by
 the set of elements $\mathcal{Z}(\Phi)$.
@@
 The following recent result of A.~Stepanov served as a starting point for the present paper.
-The notation for the subgroups involved in the statements of our results below is introduced properly in section~\ref{sec:prelim}.
+The notation for the subgroups involved in the statements of the results below is introduced properly in section~\ref{sec:prelim}.
 \begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
-Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be any parabolic subset of roots.
-Let $\Sigma_S$ be the special part of $S$, then $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$. \end{prop}
+Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be an arbitrary parabolic subset of roots, and $\Sigma_S$ be the special part of $S$.
+The relative elementary subgroup $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$.
+\end{prop}
 
 The purpose of this paper is two-fold. 
-First, we obtain relative analogues of several classical parabolic factorizations of Chevalley groups such as Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
-Secondly, we apply these factorizations to the study of various bounded generation properties of Chevalley groups over rings.
+First, we obtain relative analogues of several classical parabolic factorizations of Chevalley groups such as the Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
+Then we apply these factorizations to the study of various bounded generation properties of Chevalley groups over rings.
 %To be more specific, we study relative analogues of the following three kinds of decompositions:
@@
 
-Our first result is a relative version of Gauss decomposition formulated in terms of the \emph{stable rank} of the ideal $I$ (see section~\ref{sec:stability-conditions} for the definition)
+Our first result is a relative version of the Gauss decomposition formulated in terms of the \emph{stable rank} of the ideal $I$ (see section~\ref{sec:stability-conditions} for the definition)
 \begin{thm}\label{thm:srRI1}
-Let $\Phi$ be a root system, let $I$ be an ideal of arbitrary commutative ring $R$ such that $\sr(I)=1$.
-Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits the following decomposition
+Let $\Phi$ be a root system, let $I$ be an ideal of an arbitrary commutative ring $R$, and assume that $\sr(I)=1$.
+Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits the following decomposition:
 \[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi, I). \]
@@
 
-The next main result is a relative Dennis---Vaserstein decomposition which holds for a broader class of groups of rings as compared to \cref{thm:srRI1}.
+The next main result is the relative Dennis---Vaserstein decomposition, which holds for a broader class of rings as compared to \cref{thm:srRI1}.
 \begin{thm}\label{thm:DennisVaserstein}
-Let $\Phi \neq \rE_8$ be a reduced irreducible root system and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$ the distance between which equals $d$.
-Assume that $\Phi$ and $I$ satisfy either of the following assumptions:
+Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
+Denote the distance between $r$ and $s$ by $d$.
+Assume that $\Phi$, $I$ and $\{r, s\}$ satisfy either of the following assumptions:
 \begin{enumerate}
- \item $\asr(I) \leq d$ for $\Phi=\rF_4$ or $\Phi=\rE_\ell$, $\{r, s\} = \{1, \ell \}$, 
- \item $\sr(I) \leq d$, otherwise.
+ \item $\asr(I) \leqslant d$ for $\Phi=\rF_4, \rE_\ell$ and $\{r, s\} = \{1, \ell \}$, 
+ \item $\sr(I) \leqslant d$, for $\Phi\neq\rF_4, \rE_\ell$.
 \end{enumerate}
 Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$ \end{thm}
-Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5, 4.1]{St78}.
+Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5 and~4.1]{St78}.
 The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev (cf.~\cite[Lemma~2.1]{ST76}).
 
-The condition $\asr(I) \leq d$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
+The condition $\asr(I) \leq d$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm, which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
 
@@
 
-Our first application of parabolic factorizations is the following theorem which gives an estimate of the width of $\E(\Phi, R)$ in terms of Tits generators and is, thus, a quantitative analogue of \cref{prop:Stepanov}
+Our first application of the parabolic factorizations is the following theorem, which gives an upper bound on the width of $\E(\Phi, R)$ in terms of Tits generators.
+Thus it is a quantitative analogue of \cref{prop:Stepanov}
 and a relative analogue of the results of~\cite{Tavgen91, VseUnitrZ1p, VavSmSuUnitrEng}.
@@
 $W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
-\item If $\sr(I) = 1$ and $\Phi$ is arbitrary irreducible root system, then 
+\item If $\sr(I) = 1$ and $\Phi$ is an arbitrary irreducible root system, then 
 \[W(\E(\Phi, R, I), \mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1;\]
@@
 \end{thm}
-The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{TavgenThesis}, cf. also with \cite{Mo07}), 
+The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{TavgenThesis}, cf.~\cite{Mo07}), 
 while for the second and the third assertion we give a direct proof.
@@
 
-Another application of parabolic factorizations developed in this paper are subsystem factorizations in terms of subgroups of type $\rA_1$.
+Another application of the parabolic factorizations developed in the present paper is the subsystem factorization in terms of subgroups of type $\rA_1$.
 The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{LNS11}.
@@
 
-In~\cite{V13} N.~Vavilov and E.~Kovach noted that Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for arbitrary field $F$.
-In fact, in the context of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
-Our next result further extends this to even larger class of rings (which e.\,g. includes ideals of all Dedekind rings).
+In~\cite{V13} N.~Vavilov and E.~Kovach noted that the Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for an arbitrary field $F$.
+In fact, in the assumptions an by means of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
+Our next result further extends this to an even larger class of rings (which, for example, includes the ideals of all Dedekind rings).
 \begin{thm}\label{thm:SL2width}
@@
 
-Our yet another application of parabolic factorizations concerns product decompositions of Chevalley groups formulated in terms of subgroups of type $\rA_\ell$ of submaximal rank.
+Yet another application of the parabolic factorizations concerns the product decompositions of Chevalley groups formulated in terms of subgroups of type $\rA_\ell$ of submaximal rank.
 Recall that in \cite{Nik07} N.~Nikolov proves the following result. 
@@
 It is classically known that over an arbitrary field $F$ the group $\SL_{n+1}(F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
-On the other hand, one immediately obtains from \cref{thm:DennisVaserstein} and surjective stability for linear $\K_1$ that $\SL_{n+1}(R, I)$ factors into a product
+On the other hand, one immediately obtains from \cref{thm:DennisVaserstein} and surjective stability for linear $\K_1$-functor that $\SL_{n+1}(R, I)$ factors into a product
 of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
 
-Applying \cref{thm:DennisVaserstein} and proving a more accurate version of \cite[Proposition~1]{Nik07} in the special case $\Phi=\rD_\ell$ we obtain the following result.
+Applying \cref{thm:DennisVaserstein} and proving a more accurate version of \cite[Proposition~1]{Nik07} in the special case $\Phi=\rD_\ell$, we obtain the following result.
 \begin{thm}\label{thm:spin-sln-prod}
@@
 The rest of the article is organized as follows.
-In sections \ref{sec:prelim}--\ref{sec:stability-conditions} we introduce principal notation and prove basic facts pertaining to Chevalley groups over rings and stability conditions.
-In section \ref{sec:factorizations} we prove our parabolic factorizations and thus obtain Theorems~\ref{thm:srRI1}, \ref{thm:DennisVaserstein} and \ref{thm:SL2width}.
-Finally, we treat bounded generation and product decompositions separately in section~\ref{sec:applications} where Theorems~\ref{thm:width} and \ref{thm:spin-sln-prod} are proved.
+In sections \ref{sec:prelim}--\ref{sec:stability-conditions} we introduce the principal notation and prove some basic facts pertaining to Chevalley groups over rings and the stability conditions.
+In section \ref{sec:factorizations} we construct various parabolic factorizations and thus prove \cref{thm:srRI1,thm:DennisVaserstein,thm:SL2width}.
+Finally, we treat the bounded generation and the product decompositions separately in section~\ref{sec:applications}, where \cref{thm:width,thm:spin-sln-prod} are proved.
 
 \subsection{Acknowledgements}
-Authors of the present paper acknowledge financial support from Russian Science Foundation grant 14-11-00297.
+Authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297.
 
@@
 i.\,e. the set consisting of arbitrary products $h_1\ldots h_n$ of elements $h_i\in H_i$. In particular, the equality
-$G = H_1\cdot\ldots\cdot H_n$ means that every element $g\in G$ can be presented as a product $h_1\ldots h_n$ for $h_i\in H_i$.
+$G = H_1\cdot\ldots\cdot H_n$ means that every element $g\in G$ can be presented as a product $h_1\ldots h_n$, where $h_i\in H_i$ for each $i$.
 
 \subsection{Root systems}\label{sec:rootsys}
-Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
-We use conventional numbering of basis vectors of $\Pi$ which follows Bourbaki (cf.~\cite[Table~1]{PSV98}).
+Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of fundamental roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
+We use the conventional numbering of basis vectors of $\Pi$ which follows Bourbaki (see~\cite[Table~1]{PSV98}).
 Denote by $\Phi^+$ and $\Phi^-$ the subsets of positive and negative roots with respect to $\Pi$.
 Let $\alpha_\mathrm{max}$ denote the maximal root of $\Phi$.
-For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th component of $\alpha$ in $\Pi$, i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
+For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ with respect to $\Pi$, i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
 
 A proper closed subset of roots $S\subseteq \Phi$ is called {\it parabolic} (resp. {\it reductive}, resp. {\it special}) if $\Phi=S \cup -S$ (resp. $S = -S$, resp. $S \cap -S=\varnothing$).
-Any parabolic subset $S \subseteq \Phi$ can be decomposed into the disjoint union of its \emph{reductive} and \emph{special} parts, i.e. 
+Any parabolic subset $S \subseteq \Phi$ can be decomposed into the disjoint union of its \emph{reductive} and \emph{special} parts, i.\,e. 
 $S = \Sigma_S \sqcup \Delta_S$, where $\Sigma_S \cap (-\Sigma_S) = \varnothing$, $\Delta_S = -\Delta_S$.
@@
 
-Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all reflections $\sigma_\alpha$ where $\sigma_\alpha(\beta)=\beta-\langle\beta, \alpha \rangle\cdot \alpha$.
+Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all simple reflections $\sigma_\alpha$, $\alpha\in\Phi$.
+Recall that a simple reflection is defined by $\sigma_\alpha(\beta)=\beta-\langle\beta, \alpha \rangle\cdot \alpha$.
 For a reductive subset $\Delta\subseteq \Phi$ denote by $W(\Delta)$ the subgroup of $W(\Phi)$ generated by $\sigma_\alpha$ for $\alpha\in\Delta$.
 
-Let $J\subseteq \Pi$ be a subset of simple roots. 
+Let $J\subseteq \Pi$ be a subset of fundamental roots. 
 For a root $\beta = \sum m_i(\beta)\alpha_i \in \Phi$ define \emph{$J$-shape} of $\beta$ (denoted $\shape(J, \beta)$) as $\sum_{i\in J} m_i(\beta) \alpha_i$.
@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
-We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
+We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\,g., $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
 
@@
 Our exposition of Chevalley groups is standard and follows~\cite{Ta, S, St78, VP, Va86}.
-We denote by $\G(\Phi, R)$ the simply-connected split Chevalley group of type $\Phi$ over arbitrary commutative ring $R$.
+We denote by $\G(\Phi, R)$ the simply-connected Chevalley group of type $\Phi$ over an arbitrary commutative ring $R$.
 For example, for each of the four classical series $\Phi=\rA_\ell, \rB_\ell, \rC_\ell, \rD_\ell$
@@
 
-Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
+Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$, called the {\it elementary root unipotents}.
 These elements satisfy the well-known Steinberg relations:
@@
 \end{align} 
-The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
-The integers $N_{\alpha\beta ij}$ are called {\it structure constants} of the Chevalley group $\G(\Phi, R)$ and depend only on $\Phi$.
-We refer the reader to~\cite[\S14]{VP} for basic properties of structure constants.
+The indices $i$, $j$ in the above formula range over all positive integers such that $i\alpha + j\beta\in\Phi$.
+The integers $N_{\alpha\beta ij}$ are called the \emph{structure constants} of the Chevalley group $\G(\Phi, R)$ and depend only on $\Phi$.
+We refer the reader to~\cite[\S14]{VP} for basic properties of the structure constants.
 
@@
 \end{equation}
-where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed through structure constants (cf.~\cite[\S13]{VP}).
+where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed through the structure constants (see~\cite[\S13]{VP}).
 For a reductive subset $\Delta \subseteq \Phi$ denote by $\widetilde{W}(\Delta)$ the \emph{extended Weyl group}, i.\,e.
@@
 \begin{lemlist}
-\item \label{item-trans1} For every roots $\alpha, \beta \in \Phi$ of the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
-\item \label{item-egen} The elementary group $\E(\Phi, R)$  is generated as an abstract group by root subgroups $X_{\alpha}(R)$, $\alpha \in \Pi \cup -\Pi$.
-\item \label{item-trans2} Assume that $\alpha_s\in \Pi$ is a simple root of $\Phi$ such that $m_s(\alpha_\mathrm{max}) = 1$. 
+\item \label{item-trans1} For every two roots $\alpha, \beta \in \Phi$ of the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
+\item \label{item-egen} The elementary group $\E(\Phi, R)$  is generated as an abstract group by the root subgroups $X_{\alpha}(R)$, $\alpha \in \Pi \cup -\Pi$.
+\item \label{item-trans2} Assume that $\alpha_s\in \Pi$ is a fundamental root of $\Phi$ such that $m_s(\alpha_\mathrm{max}) = 1$. 
                           Then for $\alpha, \beta \in \Sigma^\pm_s$ of the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$. \end{lemlist}
@@
 
-Define semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
+Define the semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
 The elements $h_\alpha(\varepsilon)$ satisfy the following relations:
@@
 \subsection{Representations of Chevalley groups} \label{sec:repr}
-Our notation and terminology pertaining to representations of Chevalley groups follows \cite[\S~1.4]{PSV98} and \cite[\S~I.2]{Ma69})
+Our notation and terminology pertaining to the representations of Chevalley groups follows \cite[\S~1.4]{PSV98} and \cite[\S~I.2]{Ma69})
 Let $\pi$ be an irreducible representation of $\G(\Phi, R)$ acting on a free $R$-module $V$.
 We denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $\Lambda(\pi)^*$ the subset of non-zero weights.
-Denote by $V_\lambda \leq V$ the \emph{weight subspace} corresponding to $\lambda\in\Lambda(\pi)$ and denote by $m_\lambda$ the dimension of $V_\lambda$.
+Denote by $V_\lambda \leq V$ the \emph{weight subspace}, corresponding to $\lambda\in\Lambda(\pi)$ and denote by $m_\lambda$ the dimension of $V_\lambda$.
 
@@
 
-The irreducible representations of Chevalley groups used in these paper form a sublist of~\cite[Table~2]{PSV98}.
+The irreducible representations of Chevalley groups used in the present paper form a sublist of~\cite[Table~2]{PSV98}.
 More specifically, all of them are \emph{fundamental} (i.\,e. their highest weight is fundamental) and basic.
@@
 In the simplest case of a \emph{microweight} representation $\pi$ (i.\,e. $\pi$ is basic and $V_0 = 0$)
-the weight diagram of $(V, \pi)$ is just an undirected graph whose vertices are in one-to-one correspondence with the elements of $\Lambda(\pi)$.
-Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ iff $\lambda-\mu = \alpha_i$.
+the weight diagram of $(V, \pi)$ is just an undirected graph whose vertices are in the one-to-one correspondence with the elements of $\Lambda(\pi)$.
+Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ if $\lambda-\mu = \alpha_i$.
 
-An immediate application of weight diagrams is that they allow one to quickly read off the branching of a given basic representation with respect to a subsystem subgroup.
+An immediate application of the weight diagrams is that they allow one to quickly read off the branching of a given basic representation with respect to a subsystem subgroup.
 If $J$ is a subset of $\Pi$ and $\Delta$ is the subsystem of $\Phi$ spanned by $J$ then the weight diagram of $\pi$ restricted to $G(\Delta, R)$ can be obtained
@@
 and choose some set of vectors $E^* = \{ e_\lambda \}_{\lambda \in \Lambda^*(\pi)}$ in such a way that 
-$E_\pi = E^* \cup \{ e_0(\alpha) \}_{\alpha \in \Delta(\pi)}$ forms a basis of $V$ in which the action of elementary root unipotents
-$x_\alpha(\xi)$ has particularly simple description.
+$E_\pi = E^* \cup \{ e_0(\alpha) \}_{\alpha \in \Delta(\pi)}$ forms a basis of $V$ in which the action of the elementary root unipotents
+$x_\alpha(\xi)$ has a particularly simple description.
 
@@
 \end{tabular} \end{lemma}
-The statement of the above lemma can be visualized using weight diagrams, see~\cite[\S~3.4]{PSV98}.
-Although it is possible to fix signs in the statement of the above lemma, we make no attempt to do this in this article and refer the reader to~\cite{V08}.
+The statement of the above lemma can be visualized using the weight diagrams, see~\cite[\S~3.4]{PSV98}.
+Although it is possible to fix the signs in the statement of the above lemma, we make no attempt to do this and refer the reader to~\cite{V08}.
 
-Notice that the highest weight of natural representations of classical groups is $\varpi_1$.
+Notice that the highest weight of the natural representations of the classical groups is $\varpi_1$.
 It will be convenient for us to number the weights of these representations as in~\cite[\S~1B]{St78}:
@@
 \end{lemma}
-Here $I^{\indexbox{2}}$ denotes the ideal generated by squares $a^2$, where $a\in I$.
-Recall also that $I^2$ is generated by products $ab$ for all $a, b\in I$.
-Clearly, $II^{\indexbox{2}}$ is generated by elements of the form $a^2b$ for $a, b\in I$.
+Here $I^{\indexbox{2}}$ denotes the ideal generated by the squares $a^2$, where $a\in I$.
+Recall also that $I^2$ is generated by the products $ab$ for all $a, b\in I$.
+Clearly, $II^{\indexbox{2}}$ is generated by the elements of the form $a^2b$ for $a, b\in I$.
 
 For a special subset of roots $\Sigma\subseteq \Phi$ we denote by $\U(\Sigma, I)$ the subgroup spanned by all $x_{\alpha}(I)$ for $\alpha\in \Sigma$. Let $J\subset\Pi$.
-The subgroup $\U(\Sigma_J^+, I)$ are normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I)$ is a subgroup called a \emph{standard parabolic subgroup}.
-The following two equalities will be referred to in the sequel as {\it Levi decomposition}: 
+The subgroup $\U(\Sigma_J^+, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I)$ is a subgroup called a \emph{standard parabolic subgroup}.
+The following two equalities will be referred to in the sequel as the \emph{Levi decomposition}:
 \begin{equation} \label{rel:Levi-decomp} \EP_J(R, I) = \U(\Sigma_J^+, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I). \end{equation}
-When $J = \{ \alpha_s \}$ for some $1 \leq s\leq \ell$ we use shorthand $\EP_s(R, I)$ for $\EP_{\{s\}}(R, I)$.
-When $I=R$ we also write $\EP_J(R)$ instead of $\EP_J(R, R)$.
+When $J = \{ \alpha_s \}$ for some $1 \leq s\leq \ell$, we use the shorthand $\EP_s(R, I)$ for $\EP_{\{s\}}(R, I)$.
+When $I=R$, we also write $\EP_J(R)$ instead of $\EP_J(R, R)$.
 
@@
 
-The following lemma is a relative version of the classical result sometimes called Chevalley---Matsumoto decomposition.
+The following lemma is a relative version of the classical result sometimes called the Chevalley---Matsumoto decomposition.
 It can be deduced easily from the absolute statement (see~\cite[Theorem~1.3]{St78}).
@@
 \subsection{$\K_1$-functor modeled on Chevalley groups}
-Recall that by Taddei's theorem $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).
+Recall that by a theorem of Taddei $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).
 
@@
 %TODO: Add references to works of Dennis, Bass, Vaserstein, Suslin etc.
-In this section we formulate and prove relative versions of decompositions from~\cite{St78} which will be our main technical tools throughout the next section.
+In this section we formulate and prove the relative versions of the decompositions from~\cite{St78}, which will be the main technical tools throughout the next section.
 

### 2015-10-20 stability-conditions.tex
Final language, punctuation, typography and notation fixes; sending to the seminar mailing list

@@
-In this section we define stability conditions used in the statements of our decomposition theorems from section~\ref{sec:factorizations}.
+In this section we define the stability conditions used in the statements of our decomposition theorems in section~\ref{sec:factorizations}.
 First, we recall the notion of the stable rank of an ideal introduced by L.~Vaserstein in~\cite{Va69, Va71}.
-As we will be mainly concerned with applications to Chevalley groups, our exposition of stable ranks is neccessarily limited to commutative rings.
-The main goal of the subsection~\ref{sec:rel-asr} is to define the relative version of the absolute stable rank condition which generalizes the definition of~\cite{EO, MKV}.
-Finally, in the end of this section we state several technical lemmas describing the action of certain unipotent radicals on unimodular columns under stability conditions.
+As we will be mainly concerned with applications to Chevalley groups, our exposition of the stable ranks is neccessarily limited to commutative rings.
+The main goal of subsection~\ref{sec:rel-asr} is to define the relative version of the absolute stable rank condition, which generalizes the definition in~\cite{EO, MKV}.
+Finally, in the end of this section we state several technical lemmas describing the action of certain unipotent radicals on the unimodular columns under the assumption of a suitable stability condition.
 
 \subsection{Relative stable rank}
-Recall that a row $a\in{}^n\!R$ is called \emph{$I$-unimodular} if it is congruent to $e_1$ modulo $I$ and its components $a_1,a_2,\ldots,a_n$ generate $R$ as an ideal.
+Recall that a row $a\in{}^n\!R$ is called \emph{$I$-unimodular} if it is congruent to $(1, 0, \ldots, 0)$ modulo $I$ and its components $a_1, a_2, \ldots, a_n$ generate $R$ as an ideal.
 A column $b \in R^n$ is called $I$-unimodular if its transpose $b^t$ is an $I$-unimodular row.
 We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n, I)$ (resp. $\Ums(n, I)$).
-When $R=I$ we refer to $R$-unimodular rows and columns as simply unimodular.
+When $I=R$, we refer to the $R$-unimodular rows and columns as simply \emph{unimodular}.
 
@@
 
-An $I$-unimodular row $a=(a_1,\ldots a_{n+1})$ is called \emph{stable} if one can choose $b_1,\ldots,b_n\in I$ such that the row $(a_1+a_{n+1}b_1,\ldots,a_n+a_{n+1}b_n)$ is also $I$-unimodular. 
-We say that $I$ satisfies stable range condition $\SR_n(I)$ if any $I$-unimodular row of length $n+1$ is stable.
+An $I$-unimodular row $a=(a_1, \ldots, a_{n+1})$ is called \emph{stable} if one can choose $b_1, \ldots, b_n\in I$ such that the row $(a_1+a_{n+1}b_1, \ldots, a_n+a_{n+1}b_n)$ is also $I$-unimodular. 
+We say that $I$ satisfies the stable range condition $\SR_n(I)$ if any $I$-unimodular row of length $n+1$ is stable.
 Vaserstein noted~\cite[Theorem~1]{Va71} that $\SR_n(I)$ implies $\SR_m(I)$ for any $m\geqslant n$. 
-It is also clear that condition $\SR_n(I)$ does not depend on the choice of the ambient ring $R$.
-By definition, the {\it stable rank} of $I$ (denoted $\sr(I)$) is the smallest natural number $n$ such that $\SR_n(I)$ holds (we set $\sr(I)=\infty$ if no such $n$ exists).
+It is also clear that the condition $\SR_n(I)$ does not depend on the choice of the ambient ring $R$.
+By definition, the \emph{stable rank} of $I$ (denoted $\sr(I)$) is the smallest natural number $n$ such that $\SR_n(I)$ holds (we set $\sr(I)=\infty$ if no such $n$ exists).
 
-The following proposition summarizes basic properties of stable ranks.
+The following proposition summarizes the basic properties of the stable rank.
 \begin{prop} \label{prop:sr_properties}
-Let $R$ be arbitrary commutative unital ring and let $I\trianglelefteq R$ be an ideal.
+Let $R$ be an arbitrary commutative unital ring and let $I\trianglelefteq R$ be an ideal.
 \begin{enumerate}
@@
 Since the stable rank of a field equals $1$, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$.
-Other examples of rings of stable rank $1$ are provided by boolean rings, the ring of algebraic integers, the ring of entire functions, the disk-algebra, etc.
+Other examples of rings of stable rank $1$ are provided by the Boolean rings, the ring of all algebraic integers, the ring of entire functions, the disk-algebra, etc.
 For this and many other examples see~\cite{VasSR1}.
@@
 \subsection{Relativization of the absolute stable rank}\label{sec:rel-asr}
-For a row $a=(a_1,\ldots,a_n)\in{}^n\!R$ denote by $\mathfrak{J}(a)$ the intersection of all maximal ideals of $R$ containing $a_1,\ldots,a_n$.
+For a row $a=(a_1, \ldots, a_n)\in{}^n\!R$ denote by $\mathfrak{J}(a)$ the intersection of all maximal ideals of $R$ containing $a_1, \ldots, a_n$.
 It is easy to see that a row $a\in R^n$ is unimodular if and only if $\mathfrak{J}(a)=R$. 
@@
 \begin{dfn}\label{dfn:j-stable}
-We say that a row $a=(a_1,\ldots,a_{n+1})\in{}^{n+1}\!I$ can be {\it $I$-shortened}, if there exist $c_1,\ldots,c_n\in I$ such that
-$\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1},\ldots,a_n+c_na_{n+1}).$
+We say that a row $a=(a_1, \ldots, a_{n+1})\in{}^{n+1}\!I$ can be \emph{$I$-shortened}, if there exist $c_1, \ldots, c_n\in I$ such that
+$\mathfrak{J}(a_1, \ldots, a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1}, \ldots, a_n+c_na_{n+1}).$
 \end{dfn}
 \begin{dfn}\label{dfn:asr}
-We say that an ideal $I$ satisfies condition $\ASR_n(I)$ if it satisfies $\SR_n(I)$ and, moreover, any row $a\in{}^{n+1}\!I$ can be $I$-shortened.
+We say that an ideal $I$ satisfies the condition $\ASR_n(I)$ if it satisfies $\SR_n(I)$ and, moreover, any row $a\in{}^{n+1}\!I$ can be $I$-shortened.
 \end{dfn}
@@
 A priori our definition of $\ASR_n(I)$ depends on $R$.
-Below we will see that, in fact, there is no such dependence.
+Below we will see that in fact there is no such dependence.
 The following lemma is a relative version of~\cite[Lemma~8.2]{MKV}. 
 \begin{lemma}\label{lemma:relative-asr-unimod}
-For a commutative ring $R$ and an ideal $I \leq R$ the following statements are equivalent:
+For a commutative ring $R$ and an ideal $I \trianglelefteq R$ the following statements are equivalent:
 \begin{lemlist} 
 \item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ can be $I$-shortened;
-\item\label{asr-bak-like} For any $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Umd(n+2,I)$ there exist $c_1,\ldots,c_n\in I$ 
- such that $(b+b',a_1+c_1d,\ldots,a_n+c_nd)$ is $I$-unimodular for any $b'\in J$, where $J=I \cdot a_1 + \ldots + I \cdot a_n + I \cdot d\leq I$.
+\item\label{asr-bak-like} For any $I$-unimodular row $(b, a_1, \ldots, a_n, d)\in\Umd(n+2, I)$ there exist $c_1, \ldots, c_n\in I$ 
+ such that $(b+b', a_1+c_1d, \ldots, a_n+c_nd)$ is $I$-unimodular for any $b'\in J$, where $J=I \cdot a_1 + \ldots + I \cdot a_n + I \cdot d\leqslant I$.
 \end{lemlist} 
@@
 Assume first that any row $a\in{}^{n+1}\!I$ can be $I$-shortened. 
-In particular for a given $I$-unimodular row $(b,a_1,\ldots,a_n,d)\in\Umd(n+2,I)$ there exist $c_1,\ldots,c_n$ such that
-\[\mathfrak{J}(a_1,\ldots,a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1},\ldots,a_n+c_na_{n+1}).\]
+In particular, for a given $I$-unimodular row $(b, a_1, \ldots, a_n, d)\in\Umd(n+2, I)$ there exist $c_1, \ldots, c_n$ such that
+\[\mathfrak{J}(a_1, \ldots, a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1}, \ldots, a_n+c_na_{n+1}).\]
 Therefore $(b,a_1+c_1d,\ldots,a_n+c_nd)$ is also unimodular. Of course, for any $b'\in J$ we could replace $b$ with $b+b'$ from the very start.
 
-To show the converse take arbitrary row $(a_1,\ldots,a_n,d)\in{}^{n+1}\!I$ and consider $I$-unimodular row $(1,a_1,\ldots,a_n,d)\in\Umd(n+2,I).$
-By hypothesis, there exist $c_1,\ldots,c_n$ such that \[ v=(1+b',a'_1,\ldots,a'_n)=(1+b',a_1+c_1d,\ldots,a_n+c_nd) \] is unimodular for any $b'\in J$.
-Assume that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that all $a'_1,\ldots,a'_n$ are contained in $\mathfrak{m}$ but at least one of the elements $d$, $a_i$ is not.
-Clearly then $d\notin\mathfrak{m}$ and $I\not\subseteq \mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$ contrary to the assumption).
+To show the converse take an arbitrary row $(a_1, \ldots, a_n, d)\in{}^{n+1}\!I$ and consider the $I$-unimodular row $(1, a_1, \ldots, a_n, d)\in\Umd(n+2, I).$
+By the hypothesis, there exist $c_1, \ldots, c_n\in I$ such that
+\[ v=(1+b', a'_1, \ldots, a'_n)=(1+b', a_1+c_1d, \ldots, a_n+c_nd) \]
+is unimodular for any $b'\in J$.
+Assume that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that all $a'_1, \ldots, a'_n$ are contained in $\mathfrak{m}$, but at least one of the elements $d$, $a_i$ is not.
+Then clearly $d\notin\mathfrak{m}$ and $I\not\subseteq \mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$, contrary to the assumption).
 Now we can find $t\in I$ such that its image $\bar{t}$ in the residue field $R/\mathfrak{m}$ equals $-\bar{1}/\bar{d}$.
-We get that $1 + b' \in \mathfrak{m}$ for $b'=td\in J$ which contradicts unimodularity of $v$.
-This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a'_1,\ldots,a'_n)=\mathfrak{J}(a_1,\ldots,a_n,d)$.
+This means that $1 + b' \in \mathfrak{m}$ for $b'=td\in J$ which, contradicts the unimodularity of $v$.
+This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a'_1, \ldots, a'_n)=\mathfrak{J}(a_1, \ldots, a_n, d)$.
 \end{proof}
@@
 Let $R$ be a commutative ring.
-We denote by $\Max(R)$ its \emph{maximum spectrum} i.e.
-the set of maximal ideals of $R$ equipped with Zariski topology.
+We denote by $\Max(R)$ its \emph{maximum spectrum}, i.e.
+the set of maximal ideals of $R$, equipped with the Zariski topology.
 For a topological space $X$ denote by $\dim(X)$ its usual topological dimension.
@@
 \begin{lemma}\label{lemma:PSV-symplectic-trick}
- Let $v=(v_1,\ldots, v_n)^t$ be a column. Denote by $v'$ the vector composed of squares of the components of $v$, i.\,e. $v'=(v_1^2, \ldots, v_n^2)^t$.
+ Let $v=(v_1, \ldots, v_n)^t$ be a column. Denote by $v'$ the vector composed of squares of the components of $v$, i.\,e. $v'=(v_1^2, \ldots, v_n^2)^t$.
  Then for any matrix $b \in M(n, I)$ one can find a symmetric matrix $a \in M(n, I)$, $a=a^t$ such that $b \cdot v' = a \cdot v$. \end{lemma}
@@
 Let $v\in V=R^{2\ell}$ be a vector of the natural representation of $\G(\rD_\ell, R)$.
-Denote by $v_+$ and $v_-$ the upper and the lower halves of $v$, i.e. $v_+=(v_1,\ldots, v_\ell)^t$, $v_-=(v_{-\ell},\ldots, v_{-1})^t$.
+Denote by $v_+$ and $v_-$ the upper and the lower halves of $v$, i.\,e. $v_+=(v_1, \ldots, v_\ell)^t$, $v_-=(v_{-\ell}, \ldots, v_{-1})^t$.
 \begin{lemma}\label{lemma:asrUnip}
@@
 \textsc{Case $\Phi=\rC_\ell$.}
-Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are on the skew-diagonal, i.\,e. $p_{ij}=(\delta_{i, \ell-j+1})$. 
+Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are on the skew-diagonal, i.\,e. $p_{ij}=\delta_{i, \ell-j+1}$. 
 For $b \in M(\ell, I)$ set $g(b)=\left(\begin{smallmatrix} e_\ell & p \cdot b \\ 0 & e_{\ell} \end{smallmatrix}\right)$.
@@
 It is clear that $v''_+ = v_+ + pb v'_-$. 
-Finally, applying \cref{lemma:PSV-symplectic-trick} we find a symmetric matrix $a$ such that
-$$(g(a)\cdot v)_+=v_+ + pav_- = v_+ + pbv'_- = v''_+ \in \Ums(\ell, I).$$
+Finally, applying \cref{lemma:PSV-symplectic-trick}, we find a symmetric matrix $a$ such that
+\[ (g(a)\cdot v)_+=v_+ + pav_- = v_+ + pbv'_- = v''_+ \in \Ums(\ell, I). \]
 
@@
 the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
-This implies the existence of an element $h\in \E(\Delta_\ell, R, I)$ such that the vector $v' = h \cdot v$ satisfies $v'_i \equiv \delta_{i1} \pmod J$ for $i=1,\ldots, \ell$.
+This implies the existence of an element $h\in \E(\Delta_\ell, R, I)$ such that the vector $v' = h \cdot v$ satisfies $v'_i \equiv \delta_{i1} \pmod J$ for $i=1, \ldots, \ell$.
 
-Clearly, $(v'_1,v'_{-\ell},\ldots, v'_{-1})$ is $I$-unimodular.
-Applying \cref{asr-bak-like} we find $c_2,\ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}x_{-i, -1}(c_i)\cdot v'$ one has
+Clearly, $(v'_1, v'_{-\ell}, \ldots, v'_{-1})$ is $I$-unimodular.
+Applying \cref{asr-bak-like}, we find $c_2, \ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}x_{-i, -1}(c_i)\cdot v'$ one has
 $(v''_1, v''_{-\ell},\ldots, v''_{-2})\in\Ums(\ell+1, I)$.
-Now, applying the condition $\sr(I) \leqslant \ell-1$ once again we find
-$d_1,d_3,\ldots, d_{\ell}\in I$ such that the entries $(v'''_1, v'''_{-\ell},\ldots, v'''_{-3})$
-of $v'''=x_{-2,1}(d_1) \cdot \prod_{i=3}^{\ell} x_{-2,-i}(d_i) \cdot v''$ form an $I$-unimodular column.
+Now, applying the condition $\sr(I) \leqslant \ell-1$ once again, we find
+$d_1, d_3, \ldots, d_{\ell}\in I$ such that the entries $(v'''_1, v'''_{-\ell}, \ldots, v'''_{-3})$
+of $v'''=x_{-2, 1}(d_1) \cdot \prod_{i=3}^{\ell} x_{-2, -i}(d_i) \cdot v''$ form an $I$-unimodular column.
 
@@
 Summarizing the above, we have found $g\in \EP_\ell(R, I)$ such that $v^{(4)}=g \cdot v$
-and the assertion of the lemma immediately follows from Levi decomposition. \end{proof}
+and the assertion of the lemma immediately follows from the Levi decomposition. \end{proof}
 
@@
  Denote by $i$ the standard embedding $\G(\rB_{\ell-1}, R, I) \hookrightarrow \G(\rD_\ell, R, I)$. 
- If $\asr(I) \leqslant \ell-1$ then for every $I$-unimodular column $v \in \Ums(2\ell, I)$ there exists $g \in \U(\Sigma_{\ell-1}^+, I) \leq \E(\rB_{\ell-1}, R, I)$ such that
+ If $\asr(I) \leqslant \ell-1$, then for every $I$-unimodular column $v \in \Ums(2\ell, I)$ there exists $g \in \U(\Sigma_{\ell-1}^+, I) \leqslant \E(\rB_{\ell-1}, R, I)$ such that
  the upper half of the vector $i(g) \cdot v$ forms an $I$-unimodular column of height $\ell$.
@@
 \begin{proof}
- The assertion follows from the fact that for every $u \in \U(\Sigma_\ell^+, I) \leq \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that $uu'$ lies in the image of $i$. 
+ The assertion follows from the fact that for every $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that $uu'$ lies in the image of $i$. 
  Indeed, denote by $\sigma$ the symmetry of the Dynkin diagram of $\rD_\ell$,
- and decompose $u$ into the product $u_1 \cdot u_2$, $u_1 \in \U(\Sigma_\ell^+\cap\Delta_{\ell-1}, I)$, $u_2 \in \U(\Sigma_\ell^+ \cap \Sigma_{\ell-1}^+, I)$.
+ and decompose $u$ into the product $u_1 \cdot u_2$, where $u_1 \in \U(\Sigma_\ell^+\cap\Delta_{\ell-1}, I)$ and $u_2 \in \U(\Sigma_\ell^+ \cap \Sigma_{\ell-1}^+, I)$.
  Then one takes $u' = \sigma(u_1)$.
@@
 \begin{lemma} \label{lemma:uraction} 
-Let $\Phi=\rA_\ell, \rC_\ell, \rD_\ell$. Denote by $\pi$ the natural representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1,2\ell$.
-Assume that one of the following conditions holds:
+Let $\Phi=\rA_\ell, \rC_\ell, \rD_\ell$. Denote by $\pi$ the natural representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1, 2\ell, 2\ell$ respectively.
+Assume that one of the following assumptions holds:
 \begin{lemlist}
@@
 \end{lemlist}
-Then for $g\in \G(\Phi, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yxg \cdot v^+)_\lambda = 0$ for $\lambda\in \Gamma$.
+Then for any $g\in \G(\Phi, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yxg \cdot v^+)_\lambda = 0$ for all $\lambda\in \Gamma$.
 \end{lemma}
@@
 the upper $k$ components of $v'= x \cdot v$ form an $I$-unimodular column. 
-Now, to obtain zeroes at desired positions it remains to subtract from $v'_{k+1},\ldots, v'_{\ell+1}$ suitable multiples of $v'_1,\ldots v'_k$.
-Clearly, this operation corresponds to the left multiplication by some element $y\in\U(\Sigma_k^-, I)$.
+Now, to obtain zeroes at the desired positions it remains to subtract from $v'_{k+1},\ldots, v'_{\ell+1}$ suitable multiples of $v'_1, \ldots, v'_k$.
+This operation corresponds to the left multiplication by some element $y\in\U(\Sigma_k^-, I)$.
 
 \textsc{Case $\Phi=\rC_\ell$.} 
-Applying \cref{item:asrUnipC} we find $x \in \U(\Sigma_\ell^+, I)$ such that the upper half $v'_+$ of $v' = x \cdot v$ is unimodular.
+Applying \cref{item:asrUnipC}, we find $x \in \U(\Sigma_\ell^+, I)$ such that the upper half $v'_+$ of $v' = x \cdot v$ is unimodular.
 Set $g(a) = \left(\begin{smallmatrix} e_\ell & 0 \\ p \cdot a & e_{\ell} \end{smallmatrix}\right)$.
-Clearly, if $a$ is symmetric then $g(a) \in \U(\Sigma_\ell^-, I)$.
-Since the column $v''_+ = ({v'_1}^2, \ldots, {v'_\ell}^2)^t$ is $I$-unimodular there exists a matrix $b \in M(\ell, I)$ such that $v'_- + p b v''_+ = 0$.
-Finally, using \cref{lemma:PSV-symplectic-trick} we find a symmetric matrix $a$ such that $(g(a) \cdot v')_- = p a v'_+ + v'_- = p b v''_+ + v'_- = 0$.
+Clearly, if $a$ is symmetric, then $g(a) \in \U(\Sigma_\ell^-, I)$.
+Since the column $v''_+ = ({v'_1}^2, \ldots, {v'_\ell}^2)^t$ is $I$-unimodular, there exists a matrix $b \in M(\ell, I)$ such that $v'_- + p b v''_+ = 0$.
+Finally, using \cref{lemma:PSV-symplectic-trick}, we find a symmetric matrix $a$ such that $(g(a) \cdot v')_- = p a v'_+ + v'_- = p b v''_+ + v'_- = 0$.
 
 \textsc{Case $\Phi=\rD_\ell$.} From the proof of \cref{item:asrUnipD} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.
-Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$ hence by \cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
+Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$, hence by \cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
 $g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fixes $v^+$. 
-Using Levi decomposition we can write $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
+Using the Levi decomposition we can write $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
 It is clear that $x$, $y$ are the desired elements.

### 2015-10-20 subsystem-factorizations.tex
Removed unused bibliography items
Luzgarev comments + spacing in latin corrected
Final language, punctuation, typography and notation fixes; sending to the seminar mailing list

@@
 Consider the decreasing chain $\Phi_k$, $k=1, \ldots, \lfloor \ell/2 \rfloor$ of root subsystems of $\Phi=\rD_\ell$ defined as follows.
-If $2k \neq \ell$ let $\Phi_k$ be the subsystem of $\Phi$ spanned by simple roots $\alpha_{2k-1}, \ldots, \alpha_\ell$.
-Clearly, such $\Phi_k$ has type $\rD_{(\ell-2k+2)}$. 
+If $2k \neq \ell$, let $\Phi_k$ be the subsystem of $\Phi$, spanned by the fundamental roots $\alpha_{2k-1}, \ldots, \alpha_\ell$.
+Clearly, such $\Phi_k$ has type $\rD_{\ell-2k+2}$. 
 In the remaining case $2k = \ell$ set $\Phi_k = \langle \alpha_\ell \rangle \cong \rA_1$.
-Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\, e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1, \ldots, \lfloor \ell/2 \rfloor$.
-Denote by $B$ the set of all $\beta_k$. From the definition it is clear that elements of $B$ are mutually orthogonal to each other.
+Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\,e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1, \ldots, \lfloor \ell/2 \rfloor$.
+Denote by $B$ the set of all $\beta_k$. From the definition it is clear that the elements of $B$ are mutually orthogonal to each other.
 The roots $\beta_k$ can also be defined by explicit formulae:
@@
 Straightforward computation shows that 
-$$w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \quad w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1 $$
+\[ w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \quad w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1, \]
 which implies the assertion of the lemma.
@@
 such that $w(\beta_k) = \alpha_{2k-1}$ for $k < \lfloor\ell/2\rfloor$ (resp. $k < \lfloor\ell/2\rfloor-1$). 
-Now using transitivity of the action of $W(\rD_3)$ on roots (resp. by the same argument as in the case $\ell=4$) we can move the remaining root $\beta_{\lfloor\ell/2\rfloor}$ 
+Now using transitivity of the action of $W(\rD_3)$ on the roots (resp. by the same argument as in the case $\ell=4$) we can move the remaining root $\beta_{\lfloor\ell/2\rfloor}$ 
 (resp. the remaining $2$ roots $\beta_{\lfloor\ell/2\rfloor-1}$, $\beta_{\lfloor\ell/2\rfloor}$) to
@@
 
-The following lemma is an analogue of Proposition~1 of~\cite{NikProdDecomp}.
+The following lemma is an analogue of Proposition~1 of~\cite{Nik07}.
 \begin{lemma}\label{lemma:nikolov-type-dl}
-Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $R$ be a commutative ring.
+Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $I$ be an ideal of a  commutative ring $R$.
 There exist an element $y\in\E(\Phi, R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell^+, I)\subset[\U(\Delta_\ell^-, I), y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
@@
 \begin{proof}
-Since $\U(\Sigma_\ell^+, I)$ is abelian we can decompose it as $\U(\Sigma_\ell^+, I)=\U(\Sigma_\ell^+\setminus B, I) \cdot \U(B, I)$. 
+Since $\U(\Sigma_\ell^+, I)$ is abelian, we can decompose it as $\U(\Sigma_\ell^+, I)=\U(\Sigma_\ell^+\setminus B, I) \cdot \U(B, I)$. 
 Set $y=\prod_{\beta\in B}x_\beta(1)$. 
@@
 \]
-Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$, $w\in\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$.
+Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, where $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $w\in\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$.
 Using the identity
@@
 \end{multline*}  
-Now using \cref{lemma:nikolov-type-dl} one can find $y_1, y_2\in\G(\rD_\ell, R)$ and $w_1, w_2\in\widetilde{W}(\rD_\ell)$ such that
+Now using \cref{lemma:nikolov-type-dl}, one can find $y_1, y_2\in\G(\rD_\ell, R)$ and $w_1, w_2\in\widetilde{W}(\rD_\ell)$ such that
 \begin{align*} & L \cdot \U(\Sigma_\ell^+, I) \subset L \cdot \U(\Delta_{\ell-1}^-, I) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-, I) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+, I), \\

### 2015-11-03 paper.tex
Minor tweaks in keywords/references/title/acknowledgements etc

@@
-\documentclass[12pt]{amsart}
+\documentclass[oneside, 12pt]{amsart}
 \usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, geometry, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, nameref, thmtools, hyperref}
@@
 
-\geometry{left=2.5cm, right=2.5cm, top=3cm, bottom=3cm}
+%\geometry{left=2.5cm, right=2.5cm, top=3cm, bottom=3cm}
+\oddsidemargin 5mm
+\marginparwidth 5mm
+\topmargin 0mm
+\textheight 225mm
+\textwidth 165mm
+\headheight 0mm
+\headsep 10mm
+\footskip 5mm
 
@@
 \addbibresource{paper.bib}
+\renewcommand*{\bibfont}{\small}
 
@@
 
-\title {Decompositions of congruence subgroups of Chevalley groups}
-\keywords {parabolic decompositions, stability for $\K_1$, bounded generation, $\SL_2$-factorizations, subsystem factorizations. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
-\author {Sergey Sinchuk, Andrei Smolensky}
-\email {sinchukss {\it at} yandex.ru, \ andrei.smolensky {\it at} gmail.com}
+\title [Decompositions of congruence subgroups of Chevalley groups] {Decompositions of congruence subgroups \\ of Chevalley groups}
+\keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, subsystem factorization. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
+\author{Sergey Sinchuk}
+\author{Andrei Smolensky}
+\email{sinchukss {\it at} yandex.ru; andrei.smolensky {\it at} gmail.com}
+\thanks{Authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297}
+
 \date {\today}
@@
 Finally, we treat the bounded generation and the product decompositions separately in section~\ref{sec:applications}, where \cref{thm:width,thm:spin-sln-prod} are proved.
-
-\subsection{Acknowledgements}
-Authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297.
 

### 2015-11-07 paper.tex
Final fixes

@@
 
-\newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label=(\roman{thmlisti}), ref=\thethm.(\roman{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
-\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label=(\roman{lemlisti}), ref=\thelemma.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
+\newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label={\rm(\arabic{thmlisti})}, ref=\thethm.(\roman{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
+\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label={\rm(\arabic{lemlisti})}, ref=\thelemma.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
 
@@
 Assume that $\Phi$, $I$ and $\{r, s\}$ satisfy either of the following assumptions:
-\begin{enumerate}
+\begin{thmlist}
  \item $\asr(I) \leqslant d$ for $\Phi=\rF_4, \rE_\ell$ and $\{r, s\} = \{1, \ell \}$, 
  \item $\sr(I) \leqslant d$, for $\Phi\neq\rF_4, \rE_\ell$.
-\end{enumerate}
+\end{thmlist}
 Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$ \end{thm}
@@
 \begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.
-\begin{enumerate}
+\begin{thmlist}
 \item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
@@
 \end{alignat*}
-\end{enumerate}
+\end{thmlist}
 \end{thm}

### 2015-11-07 stability-conditions.tex
Final fixes
Removed commented lines

@@
 Let $R$ be an arbitrary commutative unital ring and let $I\trianglelefteq R$ be an ideal.
-\begin{enumerate}
+\begin{lemlist}
 \item For any ideal $I'\subseteq I$ one has $\sr(I')\leqslant\sr(I)$, $\sr(I/I')\leqslant\sr(I)$;
@@
 \item Let $I\rtimes\mathbb{Z}$ denote the ring obtained by formally adjoining $1$ to $I$. Then $\sr(I\rtimes\mathbb{Z})=\max(2,\sr(I))$.
-\end{enumerate}
+\end{lemlist}
 \end{prop}
@@
 Obviously, the second statement of \cref{lemma:relative-asr-unimod} does not depend on $R$, hence, as suggested by the notation, $\asr(I)$ is independent of $R$.
-%As another corollary of \cref{lemma:relative-asr-unimod} we obtain the following reformulation of the absolute stable rank condition $\ASR_n(R)$.
-%\begin{cor}[A.~Bak, {cf.~\cite[\S~1]{Pl98}}] For a commutative ring $R$ the following statements are equivalent:
-%\begin{enumerate}
-% \item\label{asr_Stein} $R$ satisfies $\ASR_n(R)$;
-% \item\label{asr_Bak} For any \emph{unimodular} row $(a_1,\ldots,a_n,b,d)\in\Umd(n+2,R)$ there exist $c_1,\ldots,c_n\in R$ such that $(a_1+c_1d,\ldots,a_n+c_nd,b+td)$ is unimodular for all $t\in R$.
-%\end{enumerate}
-%\end{cor}
 
@@
 For a topological space $X$ denote by $\dim(X)$ its usual topological dimension.
-%The following result gives an upper estimate for the absolute stable rank (see~).
-%\begin{prop}\label{prop:asr-dimmax}
-%Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets 
-%$X_1\ldots, X_m$ such that $\dim(X_i)\leqslant d$ for every $i$. Then $\asr(A)\leqslant d+1$.
-%\end{prop}
 From the definition of $\asr(I)$ and \cite[Theorem~2.3]{EO} (or~\cite[Theorem~3.7]{MKV}) it follows that
@@
 \begin{itemize}
-%\item $\asr(R) = 1$ for every semilocal ring $R$;
+\item $\asr(R) = 1$ for every semilocal ring $R$;
 \item $\asr(R)\leqslant2$ for every Dedekind domain $R$;
@@
 \end{itemize}
-%The last estimate further improves to $\sr(F[x_1, \ldots, x_n])\leqslant n$ for $F$ algebraic over a finite field (see~\cite[Corollary~17.4]{VS76}).
 For certain classes of fields there is also a lower estimate for $\sr(F[x_1, \ldots, x_n])$ which allows to compute precisely the value of both $\sr(R)$ and $\asr(R)$.
@@
 \end{equation*}
-%$$(av)_k = \sum\limits_{i=1,\ i\neq k}^\ell \left( b_{ki} v_{i} + b_{ik} v_{k} \right)v_{i}  +
-%\left(b_{kk}v_{k} - \sum\limits_{i=1,\ i\neq k}^\ell b_{ik} v_{i}\right)v_{k} = \sum\limits_{i=1}^\ell b_{ki} v_{i}^2 = (bv')_k$$
 \end{proof}

### 2015-11-07 paper.tex
Replaced biber with bibtex
Removed commented lines
Merged all sources into a single file

@@
 
-\usepackage[backend=biber, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
+\usepackage[backend=bibtex, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
 \usepackage[activate={true,nocompatibility}]{microtype}
@@
 Then we apply these factorizations to the study of various bounded generation properties of Chevalley groups over rings.
-%To be more specific, we study relative analogues of the following three kinds of decompositions:
-%\begin{itemize}
-%\item \emph{Gauss decomposition, } i.\,e. a decomposition of the form $\E(\Phi, R)=\B \cdot \U^- \cdot \U$, where $\B$ denotes the standard Borel subgroup, 
-%      and $\U$, $\U^-$ are the unipotent radicals of $\B$ and the opposite Borel subgroup $\B^-$;
-%\item \emph{Bass---Kolster decomposition} $G = \Par_i \cdot \U_i^- \cdot \U_i \cdot \U_i^-$, where 
-%      $\Par_i$, $\Par_i^-$ are the opposite maximal parabolic subgroups of $\G$ corresponding to $i$-th simple root of $\Phi$ and $\U_i$, $\U_i^-$ are their unipotent radicals;
-%\item \emph{Dennis---Vaserstein decomposition} $\E(\Phi, R) = \EP_i \cdot (\U_i^- \cap \U_j^-) \cdot \EP_j$, $i\neq j$, 
-%      where $\EP_i$ denotes the subgroup generated by root unipotents $x_\alpha(\xi)$ contained in $\Par_i$.
-%\end{itemize}
-%TODO: Insert some links to VIP's papers :)
-
-%TODO: Illustrate each statement of the text below with a reference:
-%There are two main reasons to study parabolic factorizations.
-%Recall that a number of various factorizations of $\G$ are known over small-dimensional rings.
-%For example, Bruhat decomposition is the key instrument in the study of linear groups over fields, whereas Gauss decomposition and unitriangular factorizations are useful tools in the study of groups over local rings.
-%Moreover, for each particular analytic or arithmetic setting there is a special decomposition theorem (Iwasawa, Cartan and Iwahori decompositions, to mention a few).
-%Unfortunately, neither of these decompositions can be carried over to rings of higher dimension.
-%The main advantage of parabolic factorizations lies in the fact that they remain true for a broader class of rings described in terms of milder ring-theoretic assumptions formulated in terms of the \emph{stable rank} of the ground ring.
-%Their another advantage is that they prove useful in the study of asymptotical properties of Chevalley groups. We are going to discuss this theme in more detail below.
 
@@
 We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
-%The problem of finding an estimate for the width of $\G(\Phi, R)$ in terms of elementary generators $x_\alpha(\xi)$ has been extensively studied in a number of works (see e.\,g.
-\cite{CK83, Ka82, Tavgen91, Mo07, VseUnitrZ1p, VavSmSuUnitrEng}).
-%Summarizing results of these works, one can hope that such width is finite only for rather narrow classes of rings of number-theoretic nature, e.\,g.
-localizations of Dedeking rings of arithmetic type.
-%For example, W.~van der Kallen has shown that the width of $\SL(3, R)$ is infinite already for a Euclidean ring $R=\mathbb{C}[t]$.
-
-%On the other hand, much less is known about the width of the relative group $\G(\Phi, R, I)$ and the relative elementary group $\E(\Phi, R, I)$.
 
@@
 
-%\begin{rem}
-%For classical groups there is a standard way to fix the signs.
-%In case $\Phi=\rC_\ell$ the long and short root unipotents are
-%\begin{align*}
-%& x_{i, -i}(\xi)=e+\xi e_{i, -i}, \\ 
-%& x_{i, j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j, -i}, \quad i\neq\pm j.
-%\end{align*}
-%Here $\varepsilon_i$ is the sign of $i$.
-%In case $\Phi=\rB_\ell, \rD_\ell$ the long and short root unipotents in $\SO(n, R)$ are
-%\begin{align*}
-%& x_{i, j}(\xi)=e+\xi e_{ij}-\xi e_{-j, -i}, \quad i\neq\pm j, \ i, j\neq0, \\
-%& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0, i}-\xi^2 e_{i, -i}, \quad i\neq0.
-%\end{align*}
-
 \subsection{Relative Chevalley groups}\label{sec:relative-elementary}
@@
 \end{lemma}
-%\begin{proof}
-%In the absolute case ($I=R$) the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}. 
-%Thus we can write $g=u_1\cdot g'\cdot u_2$, where $u_1\in\U(\Sigma_s^-, R)$, $u_2\in\U(\Sigma_s^+, R)$ and $g'\in\G(\Delta_s, R)$.
-%Since $g$ lies in $\G(\Phi, R, I)$, the vector $gv^+$ is $I$-unimodular. 
-%On the other hand, $g'u_2v^+=v^+$, so $u_1\in\G(\Phi, R, I)\cap\U(\Sigma_s^-, R)=\U(\Sigma_s^-, I)$.
-%The matrix $g'u_2$ is an element of $\left(\G(\Delta_s, R)\U(\Sigma_s^+, R)\right)\cap\G(\Phi, R, I)$, and by Levi decomposition $u_2\in\U(\Sigma_s^+, I)$, $g'\in\G(\Delta_s, R, I)$.
-%\end{proof}
 
@@
 \section{Stability conditions}\label{sec:stability-conditions}
-\input{stability-conditions}
+In this section we define the stability conditions used in the statements of our decomposition theorems in section~\ref{sec:factorizations}.
+First, we recall the notion of the stable rank of an ideal introduced by L.~Vaserstein in~\cite{Va69, Va71}.
+As we will be mainly concerned with applications to Chevalley groups, our exposition of the stable ranks is neccessarily limited to commutative rings.
+The main goal of subsection~\ref{sec:rel-asr} is to define the relative version of the absolute stable rank condition, which generalizes the definition in~\cite{EO, MKV}.
+Finally, in the end of this section we state several technical lemmas describing the action of certain unipotent radicals on the unimodular columns under the assumption of a suitable stability condition.
+
+\subsection{Relative stable rank}
+Recall that a row $a\in{}^n\!R$ is called \emph{$I$-unimodular} if it is congruent to $(1, 0, \ldots, 0)$ modulo $I$ and its components $a_1, a_2, \ldots, a_n$ generate $R$ as an ideal.
+A column $b \in R^n$ is called $I$-unimodular if its transpose $b^t$ is an $I$-unimodular row.
+We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n, I)$ (resp. $\Ums(n, I)$).
+When $I=R$, we refer to the $R$-unimodular rows and columns as simply \emph{unimodular}.
+
+It is not hard to show that for an $I$-unimodular row $a$ there exists an $I$-unimodular column $b$ such that $ab=1$ (see~\cite[\S~2]{Va69}).
+
+An $I$-unimodular row $a=(a_1, \ldots, a_{n+1})$ is called \emph{stable} if one can choose $b_1, \ldots, b_n\in I$ such that the row $(a_1+a_{n+1}b_1, \ldots, a_n+a_{n+1}b_n)$ is also $I$-unimodular. 
+We say that $I$ satisfies the stable range condition $\SR_n(I)$ if any $I$-unimodular row of length $n+1$ is stable.
+Vaserstein noted~\cite[Theorem~1]{Va71} that $\SR_n(I)$ implies $\SR_m(I)$ for any $m\geqslant n$. 
+It is also clear that the condition $\SR_n(I)$ does not depend on the choice of the ambient ring $R$.
+By definition, the \emph{stable rank} of $I$ (denoted $\sr(I)$) is the smallest natural number $n$ such that $\SR_n(I)$ holds (we set $\sr(I)=\infty$ if no such $n$ exists).
+
+The following proposition summarizes the basic properties of the stable rank.
+\begin{prop} \label{prop:sr_properties}
+Let $R$ be an arbitrary commutative unital ring and let $I\trianglelefteq R$ be an ideal.
+\begin{lemlist}
+\item For any ideal $I'\subseteq I$ one has $\sr(I')\leqslant\sr(I)$, $\sr(I/I')\leqslant\sr(I)$;
+\item One has $\sr\Bigl(\prod\limits_{i=1}^n R_i\Bigr)=\max\limits_{i=1}^n\bigl(\sr(R_i)\bigr)$;
+\item Let $J(R)$ denote the Jacobson radical of $R$, then $\sr(R)=\sr(R/J(R))$ and $\sr(J(R))=1$;
+\item Let $I\rtimes\mathbb{Z}$ denote the ring obtained by formally adjoining $1$ to $I$. Then $\sr(I\rtimes\mathbb{Z})=\max(2,\sr(I))$.
+\end{lemlist}
+\end{prop}
+\begin{proof} See~\cite[Theorem~2.3]{Va69}, \cite{Va71}. 
+\end{proof}
+\begin{example}
+Since the stable rank of a field equals $1$, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$.
+Other examples of rings of stable rank $1$ are provided by the Boolean rings, the ring of all algebraic integers, the ring of entire functions, the disk-algebra, etc.
+For this and many other examples see~\cite{VasSR1}.
+
+%Formally adjoining a unit to a non-unital ring of stable rank $1$ produces a non-trivial example of an ideal having the stable rank strictly lower that the ambient ring.
+\end{example}
+
+\subsection{Relativization of the absolute stable rank}\label{sec:rel-asr}
+For a row $a=(a_1, \ldots, a_n)\in{}^n\!R$ denote by $\mathfrak{J}(a)$ the intersection of all maximal ideals of $R$ containing $a_1, \ldots, a_n$.
+It is easy to see that a row $a\in R^n$ is unimodular if and only if $\mathfrak{J}(a)=R$. 
+Clearly, for any $g\in\GL(n,R)$ one has $\mathfrak{J}(a\cdot g)=\mathfrak{J}(a)$.
+\begin{dfn}\label{dfn:j-stable}
+We say that a row $a=(a_1, \ldots, a_{n+1})\in{}^{n+1}\!I$ can be \emph{$I$-shortened}, if there exist $c_1, \ldots, c_n\in I$ such that
+$\mathfrak{J}(a_1, \ldots, a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1}, \ldots, a_n+c_na_{n+1}).$
+\end{dfn}
+\begin{dfn}\label{dfn:asr}
+We say that an ideal $I$ satisfies the condition $\ASR_n(I)$ if it satisfies $\SR_n(I)$ and, moreover, any row $a\in{}^{n+1}\!I$ can be $I$-shortened.
+\end{dfn}
+
+It is easy to see that $\ASR_m(I)$ implies $\ASR_n(I)$ for any $n\geqslant m$. 
+By definition, the \emph{absolute relative stable rank} $\asr(I)$ is the smallest natural $n$ such that $\ASR_n(I)$ holds (again we set $\asr(I)=\infty$ if no such $n$ exists).
+
+A priori our definition of $\ASR_n(I)$ depends on $R$.
+Below we will see that in fact there is no such dependence.
+The following lemma is a relative version of~\cite[Lemma~8.2]{MKV}. 
+\begin{lemma}\label{lemma:relative-asr-unimod}
+For a commutative ring $R$ and an ideal $I \trianglelefteq R$ the following statements are equivalent:
+\begin{lemlist} 
+\item\label{asr-j-stable} Any row $a\in{}^{n+1}\!I$ can be $I$-shortened;
+\item\label{asr-bak-like} For any $I$-unimodular row $(b, a_1, \ldots, a_n, d)\in\Umd(n+2, I)$ there exist $c_1, \ldots, c_n\in I$ 
+ such that $(b+b', a_1+c_1d, \ldots, a_n+c_nd)$ is $I$-unimodular for any $b'\in J$, where $J=I \cdot a_1 + \ldots + I \cdot a_n + I \cdot d\leqslant I$.
+\end{lemlist} 
+\end{lemma}
+\begin{proof}
+Assume first that any row $a\in{}^{n+1}\!I$ can be $I$-shortened. 
+In particular, for a given $I$-unimodular row $(b, a_1, \ldots, a_n, d)\in\Umd(n+2, I)$ there exist $c_1, \ldots, c_n$ such that
+\[\mathfrak{J}(a_1, \ldots, a_{n+1})=\mathfrak{J}(a_1+c_1a_{n+1}, \ldots, a_n+c_na_{n+1}).\]
+Therefore $(b,a_1+c_1d,\ldots,a_n+c_nd)$ is also unimodular. Of course, for any $b'\in J$ we could replace $b$ with $b+b'$ from the very start.
+
+To show the converse take an arbitrary row $(a_1, \ldots, a_n, d)\in{}^{n+1}\!I$ and consider the $I$-unimodular row $(1, a_1, \ldots, a_n, d)\in\Umd(n+2, I).$
+By the hypothesis, there exist $c_1, \ldots, c_n\in I$ such that
+\[ v=(1+b', a'_1, \ldots, a'_n)=(1+b', a_1+c_1d, \ldots, a_n+c_nd) \]
+is unimodular for any $b'\in J$.
+Assume that there exists a maximal ideal $\mathfrak{m}\trianglelefteq R$ such that all $a'_1, \ldots, a'_n$ are contained in $\mathfrak{m}$, but at least one of the elements $d$, $a_i$ is not.
+Then clearly $d\notin\mathfrak{m}$ and $I\not\subseteq \mathfrak{m}$ (otherwise $a_i=a'_i-c_id\in\mathfrak{m}$, contrary to the assumption).
+Now we can find $t\in I$ such that its image $\bar{t}$ in the residue field $R/\mathfrak{m}$ equals $-\bar{1}/\bar{d}$.
+This means that $1 + b' \in \mathfrak{m}$ for $b'=td\in J$ which, contradicts the unimodularity of $v$.
+This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a'_1, \ldots, a'_n)=\mathfrak{J}(a_1, \ldots, a_n, d)$.
+\end{proof}
+
+Obviously, the second statement of \cref{lemma:relative-asr-unimod} does not depend on $R$, hence, as suggested by the notation, $\asr(I)$ is independent of $R$.
+
+Let $R$ be a commutative ring.
+We denote by $\Max(R)$ its \emph{maximum spectrum}, i.e.
+the set of maximal ideals of $R$, equipped with the Zariski topology.
+For a topological space $X$ denote by $\dim(X)$ its usual topological dimension.
+From the definition of $\asr(I)$ and \cite[Theorem~2.3]{EO} (or~\cite[Theorem~3.7]{MKV}) it follows that
+\begin{equation} \label{sr-estimates} \sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \end{equation}
+There exist examples of rings for which the first inequality in the above formula is strict.
+More precisely, there are rings of stable rank $1$ but of absolute stable rank $\geqslant2$, see~\cite{MKV}.
+On the other hand, \cite[Theorem~1.3]{MKV} shows that $\sr(R)=\asr(R)$ for any principal ideal ring $R$.
+\begin{example}
+From inequality~\eqref{sr-estimates} one concludes, in particular, that 
+\begin{itemize}
+\item $\asr(R) = 1$ for every semilocal ring $R$;
+\item $\asr(R)\leqslant2$ for every Dedekind domain $R$;
+\item $\asr(A[x])\leqslant3$ for every locally principal ring $A$;
+\item $\asr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$.
+\end{itemize}
+For certain classes of fields there is also a lower estimate for $\sr(F[x_1, \ldots, x_n])$ which allows to compute precisely the value of both $\sr(R)$ and $\asr(R)$.
+For example, $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ (see~\cite{Kru73}) and $\sr(F[x_1, \ldots, x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
+Notice also that $\sr(\mathbb{Z}[x])=3$ (see \cite{GMV}) and $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ for $n>1$ (see example after~\cite[Theorem~18.2]{VS76}).
+\end{example}
+
+\subsection{Action of unipotent radicals}\label{sec:ur-action}
+\begin{lemma}\label{lemma:PSV-symplectic-trick}
+ Let $v=(v_1, \ldots, v_n)^t$ be a column. Denote by $v'$ the vector composed of squares of the components of $v$, i.\,e. $v'=(v_1^2, \ldots, v_n^2)^t$.
+ Then for any matrix $b \in M(n, I)$ one can find a symmetric matrix $a \in M(n, I)$, $a=a^t$ such that $b \cdot v' = a \cdot v$. \end{lemma}
+\begin{proof}
+Straightforward computation shows that the assertion of lemma holds for the matrix $a$ defined by
+\begin{equation*}
+a_{ij} = b_{ij} v_{j} + b_{ji} v_{i},\ j\neq i,\quad a_{ii} = b_{ii} v_{i} - \sum\limits_{\mathclap{\substack{j=1 \\ j\neq i}}}^\ell b_{ji} v_{j}. \qedhere
+\end{equation*}
+\end{proof}
+
+Let $v\in V=R^{2\ell}$ be a vector of the natural representation of $\G(\rD_\ell, R)$.
+Denote by $v_+$ and $v_-$ the upper and the lower halves of $v$, i.\,e. $v_+=(v_1, \ldots, v_\ell)^t$, $v_-=(v_{-\ell}, \ldots, v_{-1})^t$.
+\begin{lemma}\label{lemma:asrUnip}
+For any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$ there exists $g\in\U(\Sigma^+_\ell, I) \leq \E(\Phi, R, I)$ 
+such that $(g \cdot v)_+ \in \Ums(\ell, I)$ under the following assumptions on $\Phi$ and $I$.
+\begin{lemlist}
+\item \label{item:asrUnipC} $\Phi=\rC_\ell$ and $\sr(I) \leqslant \ell$;
+\item \label{item:asrUnipD} $\Phi=\rD_\ell$ and $\asr(I)\leqslant \ell -1$.
+\end{lemlist}
+\end{lemma}
+\begin{proof} 
+\textsc{Case $\Phi=\rC_\ell$.}
+Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are on the skew-diagonal, i.\,e. $p_{ij}=\delta_{i, \ell-j+1}$. 
+For $b \in M(\ell, I)$ set $g(b)=\left(\begin{smallmatrix} e_\ell & p \cdot b \\ 0 & e_{\ell} \end{smallmatrix}\right)$.
+Clearly, if $b$ is symmetric then $g(b)$ lies in $\U(\Sigma_\ell^+, I)\leq \E(\rC_\ell, R, I)$.
+
+Notice that the column $v'=(v_1,\ldots,v_\ell, v_{-\ell}^2,\ldots,v_{-1}^2)^t$ is $I$-unimodular.
+By the definition of the relative stable rank we can find a matrix $b\in \M(\ell,I)$ such that the upper half $v''_+$ of the vector $v''= g(b) \cdot v'$ is $I$-unimodular.
+It is clear that $v''_+ = v_+ + pb v'_-$. 
+Finally, applying \cref{lemma:PSV-symplectic-trick}, we find a symmetric matrix $a$ such that
+\[ (g(a)\cdot v)_+=v_+ + pav_- = v_+ + pbv'_- = v''_+ \in \Ums(\ell, I). \]
+
+\textsc{Case $\Phi=\rD_\ell$.} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \subseteq I$.
+By \cref{prop:sr_properties} $\sr(I/J) \leqslant \ell-1$, therefore
+the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
+This implies the existence of an element $h\in \E(\Delta_\ell, R, I)$ such that the vector $v' = h \cdot v$ satisfies $v'_i \equiv \delta_{i1} \pmod J$ for $i=1, \ldots, \ell$.
+
+Clearly, $(v'_1, v'_{-\ell}, \ldots, v'_{-1})$ is $I$-unimodular.
+Applying \cref{asr-bak-like}, we find $c_2, \ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}x_{-i, -1}(c_i)\cdot v'$ one has
+$(v''_1, v''_{-\ell},\ldots, v''_{-2})\in\Ums(\ell+1, I)$.
+Now, applying the condition $\sr(I) \leqslant \ell-1$ once again, we find
+$d_1, d_3, \ldots, d_{\ell}\in I$ such that the entries $(v'''_1, v'''_{-\ell}, \ldots, v'''_{-3})$
+of $v'''=x_{-2, 1}(d_1) \cdot \prod_{i=3}^{\ell} x_{-2, -i}(d_i) \cdot v''$ form an $I$-unimodular column.
+
+We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v'''_1+\sum_{i=3}^\ell f_i v'''_{-i} = 1$.
+Set $\xi = v'''_1-v'''_2-1 \in I$, $v^{(4)}=x_{1,2}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-i,2}(\xi f_i) \cdot v'''$.
+Clearly $v^{(4)}_2 = v^{(4)}_1-1$, therefore $v^{(4)}_+$ is $I$-unimodular.
+Summarizing the above, we have found $g\in \EP_\ell(R, I)$ such that $v^{(4)}=g \cdot v$
+and the assertion of the lemma immediately follows from the Levi decomposition. \end{proof}
+
+\begin{cor} \label{cor:embeddingBD}
+ Denote by $i$ the standard embedding $\G(\rB_{\ell-1}, R, I) \hookrightarrow \G(\rD_\ell, R, I)$. 
+ If $\asr(I) \leqslant \ell-1$, then for every $I$-unimodular column $v \in \Ums(2\ell, I)$ there exists $g \in \U(\Sigma_{\ell-1}^+, I) \leqslant \E(\rB_{\ell-1}, R, I)$ such that
+ the upper half of the vector $i(g) \cdot v$ forms an $I$-unimodular column of height $\ell$.
+\end{cor}
+\begin{proof}
+ The assertion follows from the fact that for every $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that $uu'$ lies in the image of $i$. 
+ Indeed, denote by $\sigma$ the symmetry of the Dynkin diagram of $\rD_\ell$,
+ and decompose $u$ into the product $u_1 \cdot u_2$, where $u_1 \in \U(\Sigma_\ell^+\cap\Delta_{\ell-1}, I)$ and $u_2 \in \U(\Sigma_\ell^+ \cap \Sigma_{\ell-1}^+, I)$.
+ Then one takes $u' = \sigma(u_1)$.
+
+ Now by \cref{item:asrUnipD} one finds a suitable $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ which makes the upper half unimodular,
+ and since $u'$ lies in $\G(\Delta_\ell, R, I)$, the upper half remains unimodular.
+\end{proof}
+
+\begin{lemma} \label{lemma:uraction} 
+Let $\Phi=\rA_\ell, \rC_\ell, \rD_\ell$. Denote by $\pi$ the natural representation of $\G(\Phi, R)$ on $V=R^n$, $n=\ell+1, 2\ell, 2\ell$ respectively.
+Assume that one of the following assumptions holds:
+\begin{lemlist}
+ \item \label{item:uractionA} $\Phi=\rA_\ell$, $\Gamma=\{ k+1, \ldots, \ell+1\} \subset \Lambda(\pi)$ and $\sr(I)\leq k\leq \ell$;
+ \item \label{item:uractionC} $\Phi=\rC_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\sr(I)\leq \ell$. 
+ \item \label{item:uractionD} $\Phi=\rD_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(I)\leq \ell-1$. 
+\end{lemlist}
+Then for any $g\in \G(\Phi, R, I)$ there exist $x\in \U(\Phi^+, I)$, $y\in \U(\Phi^-, I)$ such that $(yxg \cdot v^+)_\lambda = 0$ for all $\lambda\in \Gamma$.
+\end{lemma}
+\begin{proof} Denote by $v$ the image of the highest weight vector $v^+$ under $g$.
+
+\textsc{Case $\Phi=\rA_\ell$.} From the definition of the relative stable rank it follows that we can find 
+$x= \left(\begin{smallmatrix} e_k & a \\ 0 & e_{n-k} \end{smallmatrix}\right) \in \U(\Sigma_k^+, I)$ such that 
+the upper $k$ components of $v'= x \cdot v$ form an $I$-unimodular column. 
+Now, to obtain zeroes at the desired positions it remains to subtract from $v'_{k+1},\ldots, v'_{\ell+1}$ suitable multiples of $v'_1, \ldots, v'_k$.
+This operation corresponds to the left multiplication by some element $y\in\U(\Sigma_k^-, I)$.
+
+\textsc{Case $\Phi=\rC_\ell$.} 
+Applying \cref{item:asrUnipC}, we find $x \in \U(\Sigma_\ell^+, I)$ such that the upper half $v'_+$ of $v' = x \cdot v$ is unimodular.
+Set $g(a) = \left(\begin{smallmatrix} e_\ell & 0 \\ p \cdot a & e_{\ell} \end{smallmatrix}\right)$.
+Clearly, if $a$ is symmetric, then $g(a) \in \U(\Sigma_\ell^-, I)$.
+Since the column $v''_+ = ({v'_1}^2, \ldots, {v'_\ell}^2)^t$ is $I$-unimodular, there exists a matrix $b \in M(\ell, I)$ such that $v'_- + p b v''_+ = 0$.
+Finally, using \cref{lemma:PSV-symplectic-trick}, we find a symmetric matrix $a$ such that $(g(a) \cdot v')_- = p a v'_+ + v'_- = p b v''_+ + v'_- = 0$.
+
+\textsc{Case $\Phi=\rD_\ell$.} From the proof of \cref{item:asrUnipD} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.
+Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$, hence by \cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
+$g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fixes $v^+$. 
+Using the Levi decomposition we can write $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
+It is clear that $x$, $y$ are the desired elements.
+\end{proof}s
 
 \section{Relative parabolic factorizations} \label{sec:factorizations}
-%TODO: Add references to works of Dennis, Bass, Vaserstein, Suslin etc.
 In this section we formulate and prove the relative versions of the decompositions from~\cite{St78}, which will be the main technical tools throughout the next section.
@@
 \subsection{Relative Gauss decomposition}\label{sec:gauss}
-\input{gauss}
+The proof of the Gauss decomposition presented below is similar to the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
+\begin{prop}\label{thm:Gauss}
+Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1$, $\Delta_\ell$ be
+two reductive subsystems of $\Phi$, corresponding to the endnodes of the Dynkin diagram of $\Phi$.
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit the triangular decomposition with $N$ triangular factors:
+\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I), \quad i=1, \ell. \]
+Then the ambient group $\E(\Phi, R, I)$ admits the decomposition with the same number of factors:
+\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm, I). \]
+\end{prop}
+\begin{proof}
+Denote by $Y$ the product of subgroups in the right-hand side of the above equality.
+To show that $Y=\E(\Phi, R, I)$ it suffices to check that
+\begin{enumerate}
+\item $Y$ is normalized by $\E(\Phi, R)$, i.\,e. $Y^{\E(\Phi, R)}\subseteq Y$;
+\item there exists a set $X$, generating $\E(\Phi, R, I)$ as a \emph{normal} subgroup of $\E(\Phi, R)$ such that $XY\subseteq Y$.
+\end{enumerate}
+To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for any $\alpha\in \pm \Pi$, $\xi\in R$.
+Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or for $i=\ell$, and we can expand $Y$ as follows:
+\[ Y=\Hh(\Phi, R, I) \cdot \U(\Delta_i^+, I) \cdot \ldots \cdot \U^\pm(\Delta_i, I) \cdot \U(\Sigma_i^+, I) \cdot \ldots \cdot \U(\Sigma_i^\pm, I). \]
+For every  $h \in \Hh(\Phi, R, I)$ one has for some $s\in I$
+\[ x_\alpha(\xi)\cdot h = h\cdot x_\alpha((1+s)\xi)=h\cdot x_\alpha(\xi)\, x_\alpha(s\xi). \]
+
+Therefore by the assumption of the theorem
+\begin{multline*}
+Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi, R, I) \cdot x_\alpha(-\xi) \cdot X_{\alpha}(I) \cdot \E(\Delta_i, R, I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) =\\
+= \Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) = Y.
+\end{multline*}
+
+Now set $X=\left\{x_\alpha(\xi)\ \middle|\ \alpha\in\Pi, \ \xi\in I \right\}$. 
+Every root is a conjugate of some fundamental root under the action of $W(\Phi)$.
+Since $\E(\Phi, R)$ contains the normalizer of the torus, the set $X^{\E(\Phi, R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi), \  \alpha\in\Phi, \ \xi\in I \rangle$.
+Finally, the inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi, R, I)$ normalizes every root subgroup $X_\alpha(I)$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:srRI1}]
+In view of the above proposition it suffices to prove that the Gauss decomposition of length $3$ holds for $\Phi=\rA_1$.
+
+Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}$ be an element of $\SL(2, R, I)$.
+The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
+Multiplying $A$ on the left by $x_{12}(z)$, we get a matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with the invertible  element $a'$ in the top-left corner.
+After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
+Thus we have obtained the relative Gauss decomposition of $A$
+\begin{equation*}
+A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
+\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
+\cdot x_{12}(b'/a')=x_{12}(-z)\cdot
+\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
+\cdot x_{21}(y) \cdot x_{12}(b'/a'), 
+\end{equation*}
+where $\varepsilon\in 1+I$ and $y\in I$. \end{proof}
+
 \subsection{Relative Bass---Kolster decompositions}\label{sec:bass-kolster}
-\input{bass-kolster}
+The next theorem is a relative version of the so-called Bass---Kolster decomposition (cf.~\cite[Theorem~2.1]{St78}).
+\begin{thm}\label{thm:BassKolster}
+Let $\Phi$ be a classical root system of rank $\ell\geqslant2$, let $R$ be an arbitrary commutative ring and $I$ be an ideal, satisfying one of the following assumptions:
+\[\begin{array}{l@{\quad}l@{\quad}l@{\quad}c}
+\Phi = \rA_\ell, \ \ell\geqslant 2, & \sr(I) \leqslant \ell; \\
+\Phi = \rC_\ell, \ \ell\geqslant 2, & \sr(I) \leqslant 2\ell-1; \\
+\Phi = \rB_\ell, \rD_\ell, \ \ell\geqslant 3, & \asr(I) \leqslant \ell-1.
+\end{array}\]
+Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of the Bass---Kolster decomposition:
+\[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]
+where $Z = Z_{\alpha_\mathrm{max}}(I)=\left\{z_{-\alpha_\mathrm{max}}(r, 1)\ \middle|\ r\in I \right\}$.
+\end{thm}
+\begin{proof}
+
+Let $g$ be an element of $\G(\Phi, R, I)$. Set $v=g \cdot v^+\in\Ums(n, I)$. 
+Notice that in each case it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that 
+\begin{equation} \label{eq1} (g'\cdot v^+)_{1} = 1 + s \text{ and } (g'\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}} = s\ \text{for some}\ s\in I. \end{equation}
+Indeed, set $g'' = z_{-\alpha\ssub{max}}(-s, 1) \cdot g'$.
+Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}=0$ and the conclusion of the theorem follows from \cref{lemma:Chevalley-Matsumoto}.
+
+\textsc{Case $\Phi=\rA_\ell$, $n=\ell + 1$.}
+Since $\sr(I)\leqslant\ell$, one can find $a_1, \ldots, a_\ell\in I$ such that $(v_1+a_1v_{\ell+1}, \ldots, v_\ell+a_\ell v_{\ell+1})^t=(v'_1, \ldots, v'_\ell)^t$ is $I$-unimodular.
+Then there are $b_1, \ldots, b_\ell\in I$ such that $b_1v'_1+\ldots b_\ell v'_\ell=v'-1\in I$. 
+Thus the vector \[ v'' = \prod_{i=1}^\ell x_{\ell+1, i}(b_i) \cdot \prod_{i=1}^\ell x_{i, \ell+1}(a_i) \cdot v \]
+satisfies the equalities~\eqref{eq1}.
+
+\textsc{Case $\Phi=\rC_\ell$, $n=2\ell$.}
+Notice that the column $(v_1, \ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
+Applying the assumption $\sr(I)\leqslant 2\ell-1$, we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
+By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for
+\[ h_1 = x_{1, -1}(c_1 + d) \cdot \prod_{i=2}^{-2} x_{i, -1}(c_i) \in \U(\Sigma_1^+, I). \]
+
+We can find $f_1, f_2, \ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
+Set $\xi = v''_1-v''_{-1}-1 \in I$, 
+\[ h_2 = x_{-1, 1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1, i}(\xi f_i) \in \U(\Sigma_1^-, I). \]
+Direct computation shows that the vector $v'' = h_2 \cdot v'$ satisfies equalities~\eqref{eq1}.
+
+\textsc{Case $\Phi=\rD_\ell$, $n= 2\ell$.} 
+By \cref{item:asrUnipD} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of $v'=h_1 \cdot v$ is $I$-unimodular.
+Since $\sr(I)\leqslant \ell-1$, we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
+\[ v''=h_2 \cdot x_{1, 2}(c_1) \cdot v', \quad h_2=\prod_{i=3}^\ell x_{i, 2}(c_i). \]
+We can find $f_1, f_3, \ldots, f_\ell \in R$ such that $f_1v''_1+\sum_{i=3}^\ell f_i v''_{i} = 1$.
+As before, set
+\[ \xi = v''_1-v''_{-2}-1 \in I, \quad h_3 = x_{-2, 1}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-2, i}(\xi f_i), \quad v'''=h_3 \cdot v''. \]
+Clearly, $t_{1, 2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, $ h_3 \cdot h_2 \in \U(\Phi^-, I)$ and $v'''$ satisfies~\eqref{eq1}.
+
+\textsc{Case $\Phi=\rB_\ell$, $n=2\ell+1$.} Subdivide $v\in \Ums(2\ell+1, I)$ as $v=(v_+, v_0, v_-)\in R^\ell\times R\times R^\ell$.
+Denote by $J\leqslant I$ the ideal spanned by the components of $v_-$.
+Since $\sr(I/J)\leqslant \ell$, we can find $c_1, \dots, c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell x_{i, 0}(c_i) \in \U(\Phi^+, I)$
+one has $\bar{v'}_+=(\bar{v'_1}, \ldots, \bar{v'_\ell}) \in \Ums(\ell, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, I)$.
+Now the proof can be finished by repeating the argument for the case $\Phi=\rD_\ell$ (applied to the subset of long roots of $\rB_\ell$).
+\end{proof}
+
+It is easy to see that the proof of the above theorem is effective and gives an estimate of the total number of elementary root unipotents involved in the decomposition.
+\begin{cor}\label{cor:bass-kolster-count}
+In the assumptions and notation of \cref{thm:BassKolster} every element of $\G(\Phi, R, I)$ 
+can be factored into a product of one element of $\G(\Delta_1, R, I)$, one element of $Z$ and at most $4|\Sigma_1|-1$ elements of $\mathcal{X}$.
+\end{cor}
+\begin{proof}
+The assertion can be obtained by a careful analysis of the proof of the previous theorem.
+Cases $\Phi=\rA_\ell, \rC_\ell$ are immediate.
+In the case $\Phi=\rD_\ell$ from the proof of \cref{thm:BassKolster} one obtains that
+\begin{equation*} \G(\Phi, R, I) =  \U(\Sigma_\ell^+, I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1, I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z \cdot \U(\Sigma_1^-, I) \cdot \U(\Sigma_1^+, I) \cdot \G(\Delta_1, R, I).
+\end{equation*}
+We can present an element $g$ of $\U(\Sigma_\ell^+, I)$ as a product of $g_1 \in \U(\Sigma_{1, 2}^+ \cap \Sigma_\ell^+)$ and $g_2\in \U(\Delta_{1, 2}\cap \Sigma_\ell^+)$.
+An examination of the extended Dynkin diagram of $\rD_\ell$ shows that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one)
+and therefore can be moved to the right until it is consumed by $\G(\Delta_1, R, I)$.
+On the other hand, $g_1$ is a product of at most $2\ell-3$ elementary unipotents, while the width of $\U(\Sigma_1^\pm, I)$ and $\U(\Sigma_2^-\cap\Delta_1)$ with respect to the elementary unipotents does not exceed $2\ell-2$ and $2\ell-4$, respectively.
+Summing up these upper bounds, we obtain
+$$(2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9 = 4|\Sigma_1| - 1.$$
+
+The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}
+\begin{cor}\label{cor:bass-kolster-iterated}
+Assume that $\Phi$ and $I$ satisfy one of the following assumptions
+\[\begin{array}{l@{\quad}l@{\quad}l}
+\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N'=3\left|\Phi^+\right|+2\ell - 5; \\
+\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N'=3\left|\Phi^+\right|+3\ell - 6; \\
+\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N'=4\left|\Phi^+\right| - 4.
+\end{array}\]
+
+Then every element of $\G(\Phi, R, I)$ can be decomposed into a product of one element of $\G(\langle\pm\alpha_\ell\rangle, R, I) \cong \SL(2, R, I)$ and at most $N'$ elements of $\mathcal{Z}(\Sigma_\ell)$:
+\end{cor}
+\begin{proof}
+The assertion can be obtained by iteratively applying (for a total of $\ell-1$ times) the decomposition of \cref{thm:BassKolster}.
+The improved estimate for $\Phi=\rA_\ell$ (resp.
+$\rC_\ell$) follows from the fact that it suffices to make only two (resp.
+three) additions to shorten the unimodular column in the first step of the proof of \cref{thm:BassKolster}.
+\end{proof}
+\begin{proof}[Proof of \cref{thm:SL2width}]
+ As in the proof of the above corollary one has to iteratively apply \cref{thm:BassKolster}.
+ To reduce the number of $\SL_2$-factors involved in the decompositoin one has to group into a single $\SL_2$-factor a pair of opposite root subgroups $X_{\alpha}(I)$, $X_{-\alpha}(I)$ (or $Z_{\pm\alpha}(I)$) appearing on each
+ of the $3$ junctions between the positive and negative unipotent subgroups in the Bass---Kolster decomposition.
+ Since a total of $\ell-1$ reductions are used, we get the estimate $N \leq N' - 3(\ell - 1) + 1$ and the assertion of \cref{thm:SL2width} follows.
+\end{proof}
+\begin{figure}[hb]\label{fig:bass-kolster}
+\[\begin{tikzcd}[row sep=tiny]
+\rD_4 \arrow[out=0, in=120]{rd}{\asr\leqslant3} & & & \\
+\rA_4 \arrow{r}{\sr\leqslant4} & \rA_3 \arrow{r}{\sr\leqslant3} & \rA_2 \arrow{r}{\sr\leqslant2} & \rA_1 \\
+\rC_4 \arrow{r}{\sr\leqslant7} & \rC_3 \arrow{r}{\sr\leqslant5} & \rC_2 \arrow[out=0, in=-120, swap]{ru}{\sr\leqslant3} \\
+\rB_4 \arrow{r}{\asr\leqslant3} & \rB_3 \arrow[out=0, in=-120, swap]{ru}{\asr\leqslant2} & &
+\end{tikzcd}\] \caption{Reductions used in the proof of \cref{cor:bass-kolster-iterated} and \cref{thm:SL2width}} \end{figure}
+
 \subsection{Relative Dennis---Vaserstein decompositions}\label{sec:dennis-vaserstein}
-\input{dennis-vaserstein}
+Let $\Phi$ be an irreducible root system of rank $\ell$.
+In what follows, $r$ and $s$ are two distinct integers such that $1 \leqslant r, s \leqslant \ell$.
+From the Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
+\begin{multline*}
+A_{rs} \coloneqq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
+= \U(\Sigma_r^+, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \hspace{5em} \\
+\hspace{5em} = \EP_r(R, I) \cdot \E(\Delta_s, R, I) \cdot \U(\Sigma_s^-, I)\cdot \U(\Sigma_s^+, I) = \\
+= \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).
+\end{multline*}
+
+Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$, consisting of the elements which normalize the subset $A_{rs}$, i.\,e.
+\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \right\}. \]
+
+\begin{lemma}\label{lemma:dv-normal} 
+For every $\alpha \in \Delta_{r, s} \cup (\Phi^+ \setminus (\Sigma^+_r \cap \Sigma^+_s))$ one has $X_\alpha(R) \subseteq N_{rs}$. \end{lemma}
+\begin{proof}
+Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence a fortiori it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
+Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r, s\}}, R)$, we obtain the assertion of the lemma for $\alpha \in \Delta_{r, s}$.
+
+Now if $\alpha$ lies in $\Phi^+ \setminus (\Sigma_r^+ \cap \Sigma_s^+)$, then it is contained either in $\Delta_r$ or in $\Delta_s$.
+Assume, for example, the latter. By the Levi decomposition we have $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$,
+which again implies the assertion of the lemma.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:DennisVaserstein}]
+First of all, notice that in the case $\Phi=\rG_2$ the assertion of the theorem formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
+Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$:
+\begin{table}[htb]
+\[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\quad} c @{\qquad} c @{\qquad} c @{\qquad} c}
+\Phi                                 & s    &r      & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\Delta_r$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
+\rA_\ell, \ \ell\geqslant 2           & 1    &\ell   & \ell+1         & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rB_\ell, \ \ell\geqslant 2           & 1    &\ell   & 2\ell+1        & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
+\rC_\ell, \ \ell\geqslant 2           & 1    &\ell   & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\
+\rD_\ell, \ \ell\geqslant 4           & 1    &\ell   & 2\ell          & \text{natural}       & \rA_{\ell-1}              & \ell           & 2  \\ 
+\rD_\ell, \ \ell\geqslant 4           & \ell &\ell-1 & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
+\rE_\ell, \ \ell=6, 7                  & \ell &2      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
+\rE_\ell, \ \ell=6, 7                  & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \\
+\rF_4                                & 4    &1     & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
+ \caption{List of the cases considered in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
+\end{table}
+
+Denote by $L_{rs}$ the set consisting of all the elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
+It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+\begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
+
+The first step of the proof is to show that $N_{rs}$ contains sufficiently many elements. 
+This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke the stability conditions for the first time.
+We show that $N_{rs}$ contains the root subgroup $X_{-\alpha\ssub{r}}(R)$, which together with \cref{lemma:dv-normal} and \cref{item-egen} immediately implies that $N_{rs}$ contains the Levi subgroup $\E(\Delta_s, R)$ and hence the extended Weyl group $\widetilde{W}(\Delta_s)$.
+
+The next goal is to demonstrate the inclusion $\U(\Sigma_s^+, R) \subseteq N_{rs}$ (which implies $\EP_s(R) \subseteq N_{rs}$).
+All the possibilities for $\Phi$, $s$ and $r$ fall into one of the following three cases:
+\begin{enumerate}
+ \item \textit{Case $m_s(\alpha_{\mathrm{max}})=1$ and $\Phi$ is simply laced.}
+  In this case all the roots of $\Sigma^+_s$ have the same $s$-shape and length, hence the assertion follows from \cref{item-trans2}, \eqref{rel:NnormL} and the fact that we already have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
+ \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case, we get that $N_{rs}$ contains the subgroup generated by the root subgroups $X_\alpha(R)$, where $\alpha$ varies over long roots of $\Sigma_s^+$.
+  It remains to prove the inclusion $X_{1, 0}(R) \subset N_{rs}$.
+  Specializing identity~\eqref{rel:CCF}, we get \begin{equation*} \label{rel:CCF-specBC} x_{1, 0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1, -2}(-a b^2) \end{equation*}
+  Since $X_{2, 0}(R)$ and $X_{1, -2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1, 0}(R) \subseteq N_{rs}$ follows.
+ \item \textit{Case $\Phi = \rC_\ell, \rF_4$.}
+ We settle these remaining cases in \cref{lemma:DVST}, where we invoke the stability conditions one more time. 
+ In fact, we prove a stronger result, namely that $N_{rs}$ contains $X_{-\alpha\ssub{s}}(R)$ and, consequently, $N_{rs} = \E(\Phi, R)$.
+\end{enumerate}
+
+In view of \cref{prop:Stepanov} to prove the theorem it suffices to show that $L_{rs}$ contains the generating set $\mathcal{Z}(\Sigma_s^-)$ of $\E(\Phi, R, I)$.
+From the inclusion $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)}$ and \eqref{rel:NnormL} it follows that we only have to show that $\mathcal{X} \subseteq L_{rs}$.
+
+The last inclusion follows from the same transitivity argument as above and the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
+For $\Phi=\rB_\ell$ one has to once again apply the Chevalley commutator formula~\eqref{rel:CCF}:
+\[ X_{0, 1}(I) \subseteq X_{2, 1}(I) \cdot X_{2, 1}(I)^{x_{0, 2}(1)} \cdot X_{-2, 1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
+\end{proof}
+
+\begin{lemma}\label{lemma:dv_unipotent} For any $1\leq i\leq n$ the following statements hold. 
+\begin{thmlist} \item \label{item-dvu1} $\U(\Phi^+, I) = X_{\alpha\ssub{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I) = \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I)\cdot X_{\alpha\ssub{i}}(I)$.
+\item \label{item-dvu2} For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha\ssub{i}}(\xi)} \subseteq \U(\Phi^+, I)$.
+\item \label{item-dvu3} $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{i}}(I) \cdot X_{-\alpha\ssub{i}}(I)$.
+\end{thmlist} \end{lemma}
+\begin{proof} The first two statements easily follow from the Chevalley commutator formula~\eqref{rel:CCF} while the third one is a formal consequence of the first two. \end{proof}
+
+\begin{lemma}\label{lemma:Stein_reduction}
+Under the assumptions of \cref{thm:DennisVaserstein} one has $X_{-\alpha_r}(R) \subseteq N_{rs}.$
+\end{lemma}
+\begin{proof}
+Let $\pi$ be the irreducible representation of $\G(\Phi, R)$ with the highest weight $\varpi_s$ (see Table~\ref{table:dv-reps}).
+Notice that $\Delta_r$ is an irreducible classical root system of type $\rA_\ell$, $\rC_\ell$ or $\rD_\ell$.
+Denote by $(\pi', V')$ the irreducible component of the restriction of $\pi$ to $\G(\Delta_r, R)$ that contains the highest weight vector $v^+$ of $\pi$.
+In all the cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta, R)$.
+Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
+
+The set $\Gamma$ can be visualized using the weight diagrams in the following manner.
+After the removal of all bonds marked $r$ the weight diagram of $\pi$ splits into several connected components.
+The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram that contains the vertex marked $\varpi_s$.
+Clearly, $\Gamma$ consists of the weights of $\Lambda(\pi')$ incident to the removed bonds.
+
+By a consideration of the weight diagrams (see~\cite{PSV98}) we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
+
+Consider the subset $B \subset \E(\Delta_r, R, I)$, consisting of all elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
+Set $A\coloneqq\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
+
+Let $g$ be an element of $\E(\Delta_r, R, I)$. Applying \cref{lemma:uraction} to the subsystem $\Delta_r$, we find
+$x\in\U(\Delta_r^+, I)$ and $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
+Consequenty, this shows that $A = A_{rs}$, indeed:
+\begin{equation*} \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B.
+\end{equation*}
+
+Notice that by the definition of $\Gamma$ and \cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$.
+Consequently, one has
+\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I), \]
+which implies the following inclusion:
+\begin{multline*}
+X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
+X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
+\subseteq B \cdot \U(\Sigma_r^+, I) \cdot \EP_s(R, I) =
+B \cdot \EP_s(R, I).
+\end{multline*}
+Together with the third statement of \cref{lemma:dv_unipotent} this shows that
+\begin{equation*} \label{rel:sred}
+A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).
+\end{equation*}
+Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$, we obtain the assertion of the lemma. Indeed,
+\begin{equation*} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A. \qedhere \end{equation*}
+\end{proof}
+
+\begin{lemma}\label{lemma:DVST}
+Assume that one of the following holds:
+\begin{lemlist}
+ \item \label{lemma:DVcaseCl} $\Phi=\rC_\ell$ and $\sr(I) \leq \ell-1$;
+ \item \label{lemma:DVcaseF4} $\Phi=\rF_4$ and $\asr(I) \leq 3$.
+\end{lemlist}
+Then one has $X_{-\alpha_s}(R) \subseteq N_{rs}$.
+\end{lemma}
+\begin{proof}
+Consider the subset $C \subseteq \EP_s(R, I)$, consisting of the elements satisfying the following condition:
+\begin{itemize}
+ \item \textsc{Case $\Phi=\rC_\ell$.} Matrix entries $(g_{i, 2})$, $i=2, \ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
+ \item \textsc{Case $\Phi=\rF_4$.} Matrix entries $(g_{\lambda, \lambda}, \ldots, g_{\lambda, \lambda - \alpha_3 - \alpha_2 - \alpha_1})$, where $\lambda = \varpi_4 - \alpha_4$ (see~\cite[Fig.~26]{PSV98}),
+                                     form an $I$-unimodular column of height $4$. \end{itemize}
+
+Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot C$.
+By \cref{item:asrUnipC} (in the case $\Phi=\rC_\ell$) or \cref{cor:embeddingBD} (in the case $\Phi=\rF_4$), applied to the subgroup $\G(\Delta_s, R, I)$,
+we find for every $g \in \EP_s(R, I)$ an element $x \in \U(\Sigma_r^+ \cap \Delta_s, I)$ such that $xg \in C$.  
+Notice that one immediately gets the equality $A_{rs} = A'$ from this.
+Indeed, for $g\in \EP_s(R, I)$ one has
+\begin{equation*} \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq 
+ \EP_r(R, I)x^{-1}  \cdot \U(\Sigma_s^-, I) \cdot xg \subseteq A'. \end{equation*}
+
+By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s^+ \cap \Delta_r, I)$ such that $(y \cdot g)_{\varpi_s, \varpi_s - \alpha_s} = 0$.
+Consequently, for every $g\in C$ one has
+\begin{multline*}
+ \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq \EP_r(R, I) y^{-1} \cdot \U(\Sigma_r^-\cap \Sigma_s^-, I)^{y^{-1}} \cdot y g \subseteq \\
+  \subseteq \EP_r(R, I) \cdot \U(\Sigma_r^-, I) \cdot y g
+\end{multline*}
+Notice that the matrix entry $(yg)_{\varpi_s, \varpi_s}$ is invertible.
+From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1 \coloneqq (yg)^{x_{-\alpha_s}(\xi)}$
+satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_s^-, I)$, $h \in \EP_1(R, I)$.
+Consequently, one has
+\begin{multline*} {A_{rs}}^{X_{-\alpha_{s}}(R)} \subseteq \EP_r(R, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_r^-, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_s^-, I) \cdot \EP_s(R, I) \subseteq \\
+ \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_s(R, I) \subseteq A_{rs} \end{multline*}
+ as claimed.
+\end{proof}
 
@@
 \subsection{Bounded generation}\label{sec:boundgen}
-\input{congrsubgr-boundgen}
+We now give an application of the parabolic factorizations to the problem of bounded generation.
+
+\begin{lemma}\label{lemma:srRI1_width}
+In the assumptions of \cref{thm:srRI1} the width of $\E(\Phi,R,I)$ with respect to $\mathcal{Z}(\Pi)$ does not exceed $3\left|\Phi^+\right|+2\rk\Phi-1$.
+\end{lemma}
+\begin{proof}
+Take an element $g\in\E(\Phi,R,I)$ and decompose it into $g=u_1 h v_2 u_3$, where $h\in\Hh(\Phi,R,I)$, $u_1,u_3\in\U(\Phi,I)$, $v_2\in\U(\Phi^-,I)$. 
+Write $h=\prod_{i=1}^\ell h_{\alpha_i}(\varepsilon_i)$, $\varepsilon\in1+I$. 
+Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
+(see \eqref{eq:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we have a decomposition
+\[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
+and the estimate follows.
+\end{proof}
+
+The following lemma is a corollary of Theorems~5.7 and 5.8 of~\cite{LSM}.
+\begin{lemma}
+Let $p$ be a rational prime, let $c$, $d$ be a pair of coprime integers such that $p \perp d$.
+Then under the assumption of the Generalized Riemann Hypothesis there exist infinitely many primes $q\equiv c\pmod{d}$ such that $p$ is a primitive root modulo $q$.
+\end{lemma}
+
+The following lemma is a relative version of \cite[Lemma~6]{VavSmSuUnitrEng} (see also~\cite{VseUnitrZ1p}):
+
+\begin{lemma}\label{lemma:Z1p}
+Set $R=\mathbb{Z}[\sfrac{1}{p}]$ and let $I$ be an ideal of $R$.
+Under the assumption of the GRH the width of $\SL(2, R, I)$ with respect to the generating set
+\[ \mathcal{Z}(\{-\alpha_1\})=X_{12}(I)\cup X_{21}(I) \cup \{z_{21}(s, \xi) \mid s\in I,\ \xi\in R\} \]
+does not exceed $6$.
+\end{lemma}
+
+\begin{proof}
+Clearly, $I$ is a principal ideal generated by some integer $m\in\mathbb{Z}$ not divisible by $p$.
+Let $g$ be an element of $\SL(2,R,I)$. Write
+\[ g=\begin{pmatrix}x & y \\ z & w\end{pmatrix},\ \text{for}\ x=p^\alpha a,\ z=p^\beta bm,\ \text{where}\ a,b,\alpha,\beta\in\mathbb{Z},\ p\nmid a,b. \]
+
+\textsc{Case 1:} $\alpha\geqslant\beta$. 
+Since $p^{\alpha-\beta}a\perp bm^2$ and $p\perp bm^2$, there exist infinitely many rational primes $q$ of the form $p^{\alpha-\beta}a+bm^2k$,
+such that $p$ is a primitive root modulo $q$. 
+We may assume that $q$ is prime to $b$. 
+Write
+\begin{align*}
+g_1 & = x_{12}(mk)\cdot g =
+\begin{pmatrix} p^\beta q & * \\ p^\beta bm & * \end{pmatrix}. \\
+\intertext{
+There exists $u\geqslant 1$ such that $p^u\equiv b\pmod q$, say $p^u=b+lq$. Then
+}
+g_2 & = x_{21}(ml)\cdot g_1 =
+\begin{pmatrix} p^\beta q & * \\ mp^{\beta+u} & * \end{pmatrix}. \\
+\intertext{
+Since $g_2\equiv 1\pmod m$, we can write $p^\beta q=1+cm$ for some $c$. Now set
+}
+g_3 & = x_{12}\left(\dfrac{-c}{p^{\beta+u}}\right)\cdot g_2 =
+\begin{pmatrix} 1 & * \\ mp^{\beta+u} & * \end{pmatrix}, \\
+g_4 & = x_{21}\left(-mp^{\beta+u}\right)\cdot g_3 =
+\begin{pmatrix} 1 & * \\ 0 & * \end{pmatrix}, \\
+g_5 & = x_{12}\left(\dfrac{c}{p^{\beta+u}}\right)\cdot g_4 =
+\begin{pmatrix} 1 & * \\ 0 & * \end{pmatrix}.
+\end{align*}
+Notice that $g_5=z_{21}\left(-mp^{\beta+u}, c/p^{\beta+u}\right)\cdot g_2$ hence $g=x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$
+and the length of $g$ does not exceed $4$.
+
+\textsc{Case 2:} $\alpha<\beta$. 
+Since $\mathbb{Z}[\sfrac{1}{p}]/I$ is finite, there exists $k>0$ such that $p^k\equiv 1\pmod I$.
+One can choose $k>\beta-\alpha$.
+Then $k+\alpha>-k+\beta$ and
+\[ h_{12}\left(p^k\right)\cdot g =
+\begin{pmatrix} p^k & 0 \\ 0 & p^{-k} \end{pmatrix}
+\begin{pmatrix} p^\alpha a & * \\ p^\beta bm & * \end{pmatrix}=
+\begin{pmatrix} p^{k+\alpha} a & * \\ p^{-k+\beta} bm & * \end{pmatrix}. \]
+We find ourselves in the situation of the previous case, therefore, we can write $g=h_{12}\cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
+Finally, expressing $h=x_{21}\cdot z_{21}\cdot x_{12}$ as in \eqref{eq:rel-tor-elementary}, we get that $g=x_{21} \cdot z_{21} \cdot x_{12} \cdot x_{21} \cdot z_{21} \cdot x_{12}$.
+\end{proof}
+
+For the rest of this subsection $k$ denotes a global field. We assume that there is some finite set of places $S$ chosen on $k$. 
+Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type defined by $S$ and let $I$ be an ideal of $\mathcal{O}_S$.
+
+\begin{lemma}\label{lemma:width-dedekind}
+Let $\Phi$ be an irreducible classical root system of rank $\ell \geqslant 2$.
+If $k$ has a real embedding, then $\G(\Phi, \mathcal{O}_S, I)$ has finite width with respect to the generating set $\mathcal{Z}(\Sigma_\ell)$.
+\end{lemma}
+\begin{proof}
+First of all, notice that $\asr(I) \leqslant \asr(\mathcal{O}_S) \leqslant 2$. 
+By \cref{cor:bass-kolster-iterated} we can present any element 
+of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators from $\mathcal{Z}(\Sigma_\ell)$ and one element of 
+$G_0 = \G(\{\alpha_\ell, -\alpha_\ell\}, \mathcal{O}_S, I)\cong\SL(2, \mathcal{O}_S, I)$.
+Consequently, to prove the statement of the lemma it suffices to express every element 
+$g = \begin{psmallmatrix}1+a & b \\ c & 1+d \end{psmallmatrix} \in G_0$
+as a product of a finite number of generators contained in some rank $2$ subgroup of $G$ containing $G_0$.
+
+From $\det(g)=1$ we conclude that $a+d=bc-ad\in I^2$. 
+Recall that the Vaserstein's congruence subgroup is defined as
+\[ G(I, I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2, \mathcal{O}_S)\;\middle|\; a, d\in I^2, \ b, c\in I \right\}. \]
+Notice that $g_1=g\cdot z_{21}(a, 1)$ is contained in $G(I, I)$, indeed,
+\[ \begin{pmatrix} 1+a & b \\ c & 1+d \end{pmatrix} \cdot \begin{pmatrix} 1-a & -a \\ a & 1+a \end{pmatrix} = \begin{pmatrix} 1+ba-a^2 & b-a-ba-a^2 \\ c+a+ad-ac & 1+bc-ac \end{pmatrix} \in G(I, I). \]
+For any matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I, I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)$ lies in $\SL\left(2, \mathcal{O}_S, I^2\right)$.
+
+By \cref{lemma:Stepanov-ideal} the group $\E\left(\Phi, \mathcal{O}_S, I^2\right)$ is contained in $\E(\Phi, I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
+Notice that under the assumptions of the lemma it is known that $\E(\Phi, I)$ has finite width with respect to $\mathcal{X}$, see~\cite[Theorem~3.3]{TavgenThesis}.
+
+In remains to consider the case $\Phi=\rC_\ell$. First of all, notice that $2abc-abd\in II^{\indexbox{2}}$, indeed,
+\[ \det(g_1)=a^3d-3a^2bc+a^2bd+ab^2c+a^3+a^2b+a^2d+2abc-abd+1. \]
+This means that
+\[ g_2=x_{21}(-a-c)\cdot g_1\cdot x_{12}(a-b)\equiv
+\begin{pmatrix}
+1+ab-a^2 & -ab-a^2 \\ ad-ac-abc & 1-ab+a^2
+\end{pmatrix}\bmod II^{\indexbox{2}}. \]
+Now for $g_3=g_2\cdot z_{12}\left(a^2-ab, 1\right)$ we have that
+\begin{align*}
+& g_3\equiv\begin{pmatrix} 1 & -2ab \\ -abc-a^2+ab-ac+ad & 1 \end{pmatrix}\bmod II^{\indexbox{2}}, \\
+& g_4=x_{12}(2ab)\cdot g_3\equiv x_{21}\left(-abc-a^2+ab-ac+ad\right)\bmod II^{\indexbox{2}}.
+\end{align*}
+Thus $g_4\cdot x_{21}(*)\in\SL\left(2, \mathcal{O}_S, II^{\indexbox{2}}\right)$ is contained in $\E(\rC_\ell, I)$ by \cref{lemma:Stepanov-ideal} and therefore can be expressed as a bounded product of $x_\alpha$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.
+The the first and the third assertions follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}
+
 \subsection{Subsystem factorizations}\label{sec:subsysfact}
-\input{subsystem-factorizations}
+Consider the decreasing chain $\Phi_k$, $k=1, \ldots, \lfloor \ell/2 \rfloor$ of root subsystems of $\Phi=\rD_\ell$ defined as follows.
+If $2k \neq \ell$, let $\Phi_k$ be the subsystem of $\Phi$, spanned by the fundamental roots $\alpha_{2k-1}, \ldots, \alpha_\ell$.
+Clearly, such $\Phi_k$ has type $\rD_{\ell-2k+2}$. 
+In the remaining case $2k = \ell$ set $\Phi_k = \langle \alpha_\ell \rangle \cong \rA_1$.
+Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\,e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1, \ldots, \lfloor \ell/2 \rfloor$.
+Denote by $B$ the set of all $\beta_k$. From the definition it is clear that the elements of $B$ are mutually orthogonal to each other.
+The roots $\beta_k$ can also be defined by explicit formulae:
+\begin{align*}
+ \beta_k =  \alpha_{2k-1} + 2\alpha_{2k}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell, & \text{ for } k=1, \ldots, \lfloor\ell/2\rfloor-1, \\
+ \beta_{\lfloor\ell/2\rfloor} = \alpha_{\ell-2}+\alpha_{\ell-1}+\alpha_\ell, & \text{ if $\ell$ is odd, } \\
+ \beta_{\lfloor\ell/2\rfloor} = \alpha_\ell, & \text{ if $\ell$ is even.}
+\end{align*}
+
+\begin{lemma}\label{lemma:nikolov-weyl} There exists an element $w\in W(\rD_\ell)$ such that $w(B) \subseteq \Delta_\ell^+$. \end{lemma}
+\begin{proof}
+\textsc{Case $\ell=4$.} Set $w = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}} \circ \sigma_{\alpha\ssub{2} + \alpha\ssub{4}}$.
+Straightforward computation shows that 
+\[ w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \quad w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1, \]
+which implies the assertion of the lemma.
+
+\textsc{Case $\ell \geq 5$.}
+Recall from \cite[Table~9]{Dy72} that for odd (resp. even) $\ell$ all maximal subsystems of type $\rA_1+\ldots+\rA_1+\rD_3$
+(resp. $\rA_1+\ldots+\rA_1+\rD_4$) are conjugate under the action of $W(\Phi)$. Consequently, we can find $w\in W(\Phi)$
+such that $w(\beta_k) = \alpha_{2k-1}$ for $k < \lfloor\ell/2\rfloor$ (resp. $k < \lfloor\ell/2\rfloor-1$). 
+Now using transitivity of the action of $W(\rD_3)$ on the roots (resp. by the same argument as in the case $\ell=4$) we can move the remaining root $\beta_{\lfloor\ell/2\rfloor}$ 
+(resp. the remaining $2$ roots $\beta_{\lfloor\ell/2\rfloor-1}$, $\beta_{\lfloor\ell/2\rfloor}$) to
+$\alpha_{\ell-1}$ (resp. to $\alpha_{\ell-3}$, $\alpha_{\ell-1}$) while fixing all the other $\beta_k$. \end{proof}
+
+The following lemma is an analogue of Proposition~1 of~\cite{Nik07}.
+\begin{lemma}\label{lemma:nikolov-type-dl}
+Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $I$ be an ideal of a  commutative ring $R$.
+There exist an element $y\in\E(\Phi, R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell^+, I)\subset[\U(\Delta_\ell^-, I), y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
+\end{lemma}
+\begin{proof}
+Since $\U(\Sigma_\ell^+, I)$ is abelian, we can decompose it as $\U(\Sigma_\ell^+, I)=\U(\Sigma_\ell^+\setminus B, I) \cdot \U(B, I)$. 
+Set $y=\prod_{\beta\in B}x_\beta(1)$. 
+We will now show by induction on $\ell$ that 
+\begin{equation}\label{eq:ind-stat} \U(\Sigma_\ell^+\setminus B, I)\subset[\U(\Delta_\ell^-, I), y]\cdot\U(B, I). \end{equation}
+The induction base in the cases $\ell=2, 3$ is trivial.
+
+Notice that $\beta_1$ is the only root of $\Phi$ satisfying $m_2(\beta_1)=2$, therefore the commutator formula~\eqref{rel:CCF} implies
+\[ \bigl[\U(\Delta_2^-, I), x_{\beta_1}(1)\bigr]=1. \]
+There is no root of the form $\gamma=\alpha+\beta$ with $\alpha\in\Sigma_2^-\cap\Delta_\ell$ and $\beta\in B\setminus\{\beta_1\}$, because such a root $\gamma$ must satisfy $m_2(\gamma)=-1$ and $m_\ell(\gamma)=1$.
+Thus~\eqref{rel:CCF} gives
+\[\Bigl[\U(\Sigma_2^-\cap\Delta_\ell, I), \prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
+Since $B\setminus\{\beta_1\}\subset\Sigma_\ell^+\cap\Delta_2$, the above two identities imply
+\[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2, \ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell^+\cap\Delta_2, I).
+\]
+Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, where $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $w\in\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$.
+Using the identity
+\begin{equation}\label{eq:comm-ab-c}
+[ab, c]={}^a[b, c]\cdot[a, c], 
+\end{equation}
+we can rewrite
+\[ [vw, x_{\beta_1}(1)] = {}^v[w, x_{\beta_1}(1)]\cdot[v, x_{\beta_1}(1)].  \]
+Since $\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$ are abelian, it is easy to see that
+\[ [v, x_{\beta_1}(1)]\in\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I), \quad [w, x_{\beta_1}(1)]\in\U((\Sigma_1^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}, I). \]
+Every element of $\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I)$ (resp.
+$\U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I)$) can be expressed as such a commutator for a suitable choice of $v$ (resp.
+$w$).
+Indeed, set $v=x_\gamma(\xi_\gamma)\cdot v'$, $\gamma=-\alpha_1-\alpha_2$, $v' \in \U(\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell \setminus \{\gamma\}, I)$.
+Using relation \eqref{eq:comm-ab-c} and the fact that $X_\gamma(I)$ commutes with $\U(\Sigma_2^+\cap\Delta_1, I)$ we get that:
+\begin{multline*}
+[v, x_{\beta_1}(1)] = [x_\gamma(\xi_\gamma)\cdot v', x_{\beta_1}(1)] = {}^{x_\gamma(\xi_\alpha)}[v', x_{\beta_1}(1)] \cdot [x_\gamma(\xi_\gamma), x_{\beta_1}(1)] = \\
+= [v', x_{\beta_1}(1)]\cdot x_{\beta_1-\alpha_1-\alpha_2}(\xi_\gamma) = \ldots = \prod_{\mathclap{\alpha\in\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell}} x_{\beta_1+\alpha}(\xi_\alpha).
+ \end{multline*}
+It remains to note that $\Sigma_2^+ \cap \Sigma_\ell^+ \cap \Delta_1 = \beta_1 + \Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell$. The same argument works for $[w, x_{\beta_1}(1)]$.
+Direct calculation using the commutator formula shows that
+\[ {}^v\!\U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I) \equiv \U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I). \]
+Summing up the above arguments, we get that
+\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2, \ell}^-, I), y] \equiv \U((\Sigma_{1, 2}^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I), \]
+hence the inclusion~\eqref{eq:ind-stat} follows from the induction hypothesis (applied to $\Delta_{1, 2} \cong \rD_{\ell-2}$).
+
+Finally, we have found $a\in\U(\Sigma_\ell^+\setminus B, I)$ and $b\in\U(\Delta_\ell^-, I)$
+such that $$a\in[b, y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-, I), y]\cdot\U(B, I).$$
+Now the assertion of the lemma follows from~\cref{lemma:nikolov-weyl}.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:spin-sln-prod}]
+Set $L = \E(\Delta_\ell, R, I) \leq \E(\rD_\ell, R, I)$ and denote by $\sigma$ the automorphism of $\G(\rD_\ell, R)$ induced by the sole diagram automorphism of the Dynkin diagram of $\rD_\ell$.
+By \cref{thm:DennisVaserstein} one has
+\begin{multline*}
+\E(\rD_\ell, R, I) = \EP_{\ell}(R, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot\EP_{\ell-1}(R, I) = \\
+= L \cdot\U(\Sigma_\ell^+, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot \big(L \cdot \U(\Sigma_\ell^+, I) \big)^\sigma.
+\end{multline*}  
+Now using \cref{lemma:nikolov-type-dl}, one can find $y_1, y_2\in\G(\rD_\ell, R)$ and $w_1, w_2\in\widetilde{W}(\rD_\ell)$ such that
+\begin{align*} & L \cdot \U(\Sigma_\ell^+, I) \subset L \cdot \U(\Delta_{\ell-1}^-, I) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-, I) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+, I), \\
+& \U(\Sigma_{\ell-1}^-\cap\Sigma_\ell^-, I) \subset \U(\Delta_\ell^+, I) \cdot {}^{y_2}\!\U(\Delta_\ell^+, I) \cdot {}^{w_2}\!\U(\Delta_\ell^-, I). \end{align*} 
+Thus $\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of $L \cong \E(\rA_{\ell-1}, R, I)$. \end{proof}
 

### 2015-11-07 paper.tex
Fixed compilation at arxiv

@@
 \documentclass[oneside, 12pt]{amsart}
-\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, geometry, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, nameref, thmtools, hyperref}
-\usepackage[utf8]{inputenc}
-
-\usepackage[backend=bibtex, citestyle=numeric-comp, natbib=true, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
-\usepackage[activate={true,nocompatibility}]{microtype}
-\usepackage[capitalize]{cleveref}
-
-%\geometry{left=2.5cm, right=2.5cm, top=3cm, bottom=3cm}
+\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, geometry, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, microtype, nameref, thmtools, hyperref, cleveref}
+
+\hypersetup{
+  pdfauthor={Sergey Sinchuk, Andrei Smolensky},
+  pdftitle={Decompositions of congruence subgroups of Chevalley groups},  
+  urlcolor=blue}
+
+\usepackage[backend=bibtex, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
+\addbibresource{paper.bib}
+\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
+\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
+\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
+\DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
+\DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
+%\renewcommand*{\bibfont}{\footnotesize}
+
 \oddsidemargin 5mm
@@
 \footskip 5mm
-
-%Bibliography
-\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
-\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
-\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
-\DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
-\DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
-\addbibresource{paper.bib}
-\renewcommand*{\bibfont}{\small}
 
@@
 \section{Introduction}\label{sec:intro}
-%Let $R$ be a commutative unital ring and $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots.
 Let $\G(\Phi, R)$ be the simply-connected Chevalley group of type $\Phi$ over an arbitrary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup},

### 2015-11-07 paper.tex
Fixed problem with line breaks in hyperrefs

@@
 \documentclass[oneside, 12pt]{amsart}
-\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, geometry, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, microtype, nameref, thmtools, hyperref, cleveref}
+\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, geometry, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, microtype, nameref, thmtools}
+\usepackage[breaklinks=true]{hyperref}
+\usepackage[capitalize]{cleveref}
 
@@
   pdftitle={Decompositions of congruence subgroups of Chevalley groups},  
+  colorlinks=true,
   urlcolor=blue}
 
-\usepackage[backend=bibtex, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
+\usepackage[hyperref=true, backend=bibtex, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
 \addbibresource{paper.bib}
@@
 \newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
-\DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
 \DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
-%\renewcommand*{\bibfont}{\footnotesize}
+\renewcommand*{\bibfont}{\footnotesize}
 

### 2015-11-07 paper.tex
Version as submitted to arXiv

@@
 
+\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
+
 \hypersetup{
@@
   colorlinks=true,
-  urlcolor=blue}
+  urlcolor=darkblue}
 
@@
 We formulate and prove relative versions of several classical decompositions known in the theory of Chevalley groups over commutative rings.
-% Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
 As an application we obtain upper estimates for the width of principal congruence subgroups in terms of several families of generators.

### 2015-11-08 paper.tex
Minor fixes

@@
  \item $\asr(I) \leqslant d$ for $\Phi=\rF_4, \rE_\ell$ and $\{r, s\} = \{1, \ell \}$, 
- \item $\sr(I) \leqslant d$, for $\Phi\neq\rF_4, \rE_\ell$.
+ \item $\sr(I) \leqslant d$, in all other cases.
 \end{thmlist}
@@
 Our first application of the parabolic factorizations is the following theorem, which gives an upper bound on the width of $\E(\Phi, R)$ in terms of Tits generators. 
-Thus it is a quantitative analogue of \cref{prop:Stepanov}
+Thus, it is a quantitative analogue of \cref{prop:Stepanov}
 and a relative analogue of the results of~\cite{Tavgen91, VseUnitrZ1p, VavSmSuUnitrEng}.
@@
 In~\cite{V13} N.~Vavilov and E.~Kovach noted that the Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for an arbitrary field $F$.
-In fact, in the assumptions an by means of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
+In fact, in the assumptions of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
 Our next result further extends this to an even larger class of rings (which, for example, includes the ideals of all Dedekind rings).
 \begin{thm}\label{thm:SL2width}
-Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system satisfying the following assumptions.
+Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system satisfying one of the following assumptions.
 \[\begin{array}{l@{\quad}l@{\quad}l}

### 2015-11-08 paper.tex
More fixes

@@
 \title [Decompositions of congruence subgroups of Chevalley groups] {Decompositions of congruence subgroups \\ of Chevalley groups}
-\keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, subsystem factorization. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
+\keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, product decomposition. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
 \author{Sergey Sinchuk}
@@
 \begin{thm}\label{thm:DennisVaserstein}
-Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
+Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geq 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
 Denote the distance between $r$ and $s$ by $d$.
@@
 \begin{thmlist}
- \item $\asr(I) \leqslant d$ for $\Phi=\rF_4, \rE_\ell$ and $\{r, s\} = \{1, \ell \}$, 
- \item $\sr(I) \leqslant d$, in all other cases.
+ \item $\sr(I) \leqslant d$ for classical $\Phi$,
+ \item $\sr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{ 2, \ell \}$.
+ \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
+ \item $\asr(I) \leqslant d$ for $\Phi=\rF_4$.
 \end{thmlist}
@@
 It is clear that $x$, $y$ are the desired elements.
-\end{proof}s
+\end{proof}
 
@@
 \begin{proof}[Proof of \cref{thm:DennisVaserstein}]
-First of all, notice that in the case $\Phi=\rG_2$ the assertion of the theorem formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
+%First of all, notice that in the case $\Phi=\rG_2$ the assertion of the theorem formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
 Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$:

### 2015-11-09 paper.tex
Fixed broken section names in pdfs

@@
 
-\subsection{$\K_1$-functor modeled on Chevalley groups}
+\subsection{\texorpdfstring{$\K_1$}{K1}-functor modeled on Chevalley groups}
 Recall that by a theorem of Taddei $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).

### 2015-11-09 paper.tex
Version as submitted to arxiv

@@
 
-%Math operators
 \DeclareMathOperator{\K}{K}
@@
 
-\newcommand\restr[2]{\ensuremath{\left.#1\right|_{#2}}}
-
 \title [Decompositions of congruence subgroups of Chevalley groups] {Decompositions of congruence subgroups \\ of Chevalley groups}
@@
 \begin{proof}[Proof of \cref{thm:DennisVaserstein}]
-%First of all, notice that in the case $\Phi=\rG_2$ the assertion of the theorem formally follows from \cref{thm:srRI1} and identities~\ref{rel:h-comm}--\ref{rel:h-w}.
 Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$:

### 2015-11-09 paper.tex
Fixed error in the proof of Theorem 5

@@
 \begin{proof}[Proof of \cref{thm:spin-sln-prod}]
-Set $L = \E(\Delta_\ell, R, I) \leq \E(\rD_\ell, R, I)$ and denote by $\sigma$ the automorphism of $\G(\rD_\ell, R)$ induced by the sole diagram automorphism of the Dynkin diagram of $\rD_\ell$.
+Set $L = \E(\Delta_\ell, R, I) \leq \E(\rD_\ell, R, I)$ and denote by $\sigma$ the automorphism of $\G(\rD_\ell, R)$ induced by the 
+diagram automorphism of $\rD_\ell$ swapping $\alpha_\ell$ and $\alpha_{\ell-1}$.
 By \cref{thm:DennisVaserstein} one has

### 2015-11-09 paper.tex
Small fixes

@@
 
-\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
+\definecolor{darkblue}{rgb}{0.0, 0.0, 0.6}
 
@@
   colorlinks=true,
-  urlcolor=darkblue}
+  urlcolor=darkblue,
+  linkcolor=darkblue,
+  citecolor=darkblue}
 
@@
 \title [Decompositions of congruence subgroups of Chevalley groups] {Decompositions of congruence subgroups \\ of Chevalley groups}
-\keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, product decomposition. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
+\keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, subsystem factorization, product decomposition. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
 \author{Sergey Sinchuk}
@@
 \begin{thm}\label{thm:DennisVaserstein}
-Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geq 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
+Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geqslant 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
 Denote the distance between $r$ and $s$ by $d$.

### 2015-11-09 paper.tex
Display formulas and punctuation

@@
  \item $\sr(I) \leqslant d$ for classical $\Phi$,
- \item $\sr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{ 2, \ell \}$.
+ \item $\sr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{ 2, \ell \}$,
  \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
@@
 \item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
-$W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite.
+$W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite;
 \item If $\sr(I) = 1$ and $\Phi$ is an arbitrary irreducible root system, then 
@@
 & W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1 & \text{ if } \Phi=\rA_\ell, \rC_\ell, \\
-& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell;
+& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell.
 \end{alignat*}
@@
  \item \label{item:uractionA} $\Phi=\rA_\ell$, $\Gamma=\{ k+1, \ldots, \ell+1\} \subset \Lambda(\pi)$ and $\sr(I)\leq k\leq \ell$;
- \item \label{item:uractionC} $\Phi=\rC_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\sr(I)\leq \ell$. 
+ \item \label{item:uractionC} $\Phi=\rC_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\sr(I)\leq \ell$;
  \item \label{item:uractionD} $\Phi=\rD_\ell$, $\Gamma=\{-\ell,\ldots, -2, -1\} \subset \Lambda(\pi)$ and $\asr(I)\leq \ell-1$. 
@@
 \[ h_1 = x_{1, -1}(c_1 + d) \cdot \prod_{i=2}^{-2} x_{i, -1}(c_i) \in \U(\Sigma_1^+, I). \]
-
 We can find $f_1, f_2, \ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
@@
 \begin{lemma}\label{lemma:dv_unipotent} For any $1\leq i\leq n$ the following statements hold. 
-\begin{thmlist} \item \label{item-dvu1} $\U(\Phi^+, I) = X_{\alpha\ssub{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I) = \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I)\cdot X_{\alpha\ssub{i}}(I)$.
-\item \label{item-dvu2} For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha\ssub{i}}(\xi)} \subseteq \U(\Phi^+, I)$.
+\begin{thmlist} \item \label{item-dvu1} $\U(\Phi^+, I) = X_{\alpha\ssub{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I) = \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I)\cdot X_{\alpha\ssub{i}}(I)$;
+\item \label{item-dvu2} For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha\ssub{i}}(\xi)} \subseteq \U(\Phi^+, I)$;
 \item \label{item-dvu3} $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{i}}(I) \cdot X_{-\alpha\ssub{i}}(I)$.
@@
  \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq \EP_r(R, I) y^{-1} \cdot \U(\Sigma_r^-\cap \Sigma_s^-, I)^{y^{-1}} \cdot y g \subseteq \\
-  \subseteq \EP_r(R, I) \cdot \U(\Sigma_r^-, I) \cdot y g
+  \subseteq \EP_r(R, I) \cdot \U(\Sigma_r^-, I) \cdot y g.
 \end{multline*}
@@
 \begin{multline*} {A_{rs}}^{X_{-\alpha_{s}}(R)} \subseteq \EP_r(R, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_r^-, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_s^-, I) \cdot \EP_s(R, I) \subseteq \\
- \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_s(R, I) \subseteq A_{rs} \end{multline*}
+\subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_s(R, I) \subseteq A_{rs}, \end{multline*}
 as claimed.
@@
 Straightforward computation shows that 
-\[ w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \quad w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1, \]
+\begin{align*}
+& w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \\
+& w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1,
+\end{align*}
 which implies the assertion of the lemma.
@@
 Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $I$ be an ideal of a  commutative ring $R$.
-There exist an element $y\in\E(\Phi, R)$ and an element $w\in\widetilde{W}(\Phi)$ such that $\U(\Sigma_\ell^+, I)\subset[\U(\Delta_\ell^-, I), y]\cdot{}^w\!\U(\Delta_\ell^+, I)$.
+There exist an element $y\in\E(\Phi, R)$ and an element $w\in\widetilde{W}(\Phi)$ such that
+\[ \U(\Sigma_\ell^+, I)\subset[\U(\Delta_\ell^-, I), y]\cdot{}^w\!\U(\Delta_\ell^+, I). \]
 \end{lemma}
@@
 Since $B\setminus\{\beta_1\}\subset\Sigma_\ell^+\cap\Delta_2$, the above two identities imply
-\[ \Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2, \ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell^+\cap\Delta_2, I).
-\]
+\begin{multline*}
+\Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2, \ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \\
+\equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell^+\cap\Delta_2, I).
+\end{multline*}
 Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, where $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $w\in\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$.

### 2016-09-01 paper.tex
Fixed grant acknowledgement
Remastered

@@
-\documentclass[oneside, 12pt]{amsart}
-\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, geometry, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, microtype, nameref, thmtools}
+\documentclass[11pt]{amsart}
+\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, microtype, nameref, thmtools}
 \usepackage[breaklinks=true]{hyperref}
@@
 
-\oddsidemargin 5mm
-\marginparwidth 5mm
-\topmargin 0mm
-\textheight 225mm
-\textwidth 165mm
-\headheight 0mm
-\headsep 10mm
-\footskip 5mm
+%\oddsidemargin 5mm
+%\marginparwidth 5mm
+%\topmargin 0mm
+%\textheight 225mm
+%\textwidth 165mm
+%\headheight 0mm
+%\headsep 10mm
+%\footskip 5mm
+
+\usepackage[margin=2cm]{geometry}
 
@@
 
-\title [Decompositions of congruence subgroups of Chevalley groups] {Decompositions of congruence subgroups \\ of Chevalley groups}
+\title[Decompositions of congruence subgroups of Chevalley groups]{Decompositions of congruence subgroups \\ of Chevalley groups}
 \keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, subsystem factorization, product decomposition. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
@@
 \email{sinchukss {\it at} yandex.ru; andrei.smolensky {\it at} gmail.com}
-\thanks{Authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297}
+\thanks{The authors of the present paper acknowledge the financial support of the Russian Science Foundation grant 14-11-00297}
 
@@
 We formulate and prove relative versions of several classical decompositions known in the theory of Chevalley groups over commutative rings.
-As an application we obtain upper estimates for the width of principal congruence subgroups in terms of several families of generators.
+We apply them to construct new factorizations in terms of $\SL_2$ and $\SL_n$ subgroups and to obtain upper estimates on the width of principal congruence subgroups in terms of Tits---Vaserstein generators.
 Some of our results are new even in the absolute case and were previously studied only for groups over finite fields.
@@
 \section{Introduction}\label{sec:intro}
-Let $\G(\Phi, R)$ be the simply-connected Chevalley group of type $\Phi$ over an arbitrary commutative ring $R$ and let $\E(\Phi, R)$ be its \emph{elementary subgroup},
-i.\,e. the subgroup generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$, see~\cite{VP, St78, S}.
-For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (alias the \emph{principal congruence subgroup}) of level $I$, 
-i.\,e. the kernel of the map $\G(\Phi, R)\rightarrow\G(\Phi, R/I)$ induced by the canonical projection $R\rightarrow R/I$.
-
-We will also use the notion of the \emph{relative elementary Chevalley subgroup} $\E(\Phi, R, I) \leqslant \G(\Phi, R, I)$.
-Recall that $\E(\Phi, R, I)$ is defined to be the normal closure in $\E(\Phi, R)$ of the subgroup generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi, \ \xi \in I \}$.
-
-Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
-It is a classical result of J.~Tits and L.~Vaserstein (see~\cite{Tits76}, \cite[Theorem~2]{Va86}) that the relative elementary subgroup $\E(\Phi, R, I)$ is generated by
-the set of elements $\mathcal{Z}(\Phi)$.
-
-Here for a subset of roots $S\subseteq\Phi$ we denote by $\mathcal{Z}(S)$ the set
-\[ \mathcal{Z}(S) =  \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in S\}.\]
-
-The following recent result of A.~Stepanov served as a starting point for the present paper.
-The notation for the subgroups involved in the statements of the results below is introduced properly in section~\ref{sec:prelim}.
-\begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
-Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be an arbitrary parabolic subset of roots, and $\Sigma_S$ be the special part of $S$.
-The relative elementary subgroup $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$.
-\end{prop}
-
-The purpose of this paper is two-fold. 
-First, we obtain relative analogues of several classical parabolic factorizations of Chevalley groups such as the Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
-Then we apply these factorizations to the study of various bounded generation properties of Chevalley groups over rings.
-
-Our first result is a relative version of the Gauss decomposition formulated in terms of the \emph{stable rank} of the ideal $I$ (see section~\ref{sec:stability-conditions} for the definition)
-\begin{thm}\label{thm:srRI1}
-Let $\Phi$ be a root system, let $I$ be an ideal of an arbitrary commutative ring $R$, and assume that $\sr(I)=1$.
-Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits the following decomposition:
-\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi, I). \]
-\end{thm}
-In the special case when $I$ is contained in the Jacobson radical of $R$, \cref{thm:srRI1} boils down to~\cite[Proposition~2.3]{Abe76}. 
-We also note that the absolute case (i.\,e. $I=R$) of the theorem was treated by the second named author in~\cite{Sm12}.
-
-The next main result is the relative Dennis---Vaserstein decomposition, which holds for a broader class of rings as compared to \cref{thm:srRI1}.
-\begin{thm}\label{thm:DennisVaserstein}
+The aim of the present paper is to extend various decomposition of Chevalley groups and their elementary subgroups to their principal congruence subgroups and relative elementary subgroups.
+We focus on the so-called ``parabolic decompositions'', i.e.
+decompositions involving parabolic and unipotent factors.
+The main result is the following
+
+\begin{restatable*}[Dennis---Vaserstein decomposition]{thm}{ThmDennisVaserstein}\label{thm:DennisVaserstein}
 Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geqslant 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
@@
 \end{thmlist}
-Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$ \end{thm}
+Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$
+\end{restatable*}
 Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5 and~4.1]{St78}.
-The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev (cf.~\cite[Lemma~2.1]{ST76}).
-
-The condition $\asr(I) \leq d$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm, which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
-
-Let $G$ be an abstract group with a generating set $X \subset G$. 
-We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
-
-Our first application of the parabolic factorizations is the following theorem, which gives an upper bound on the width of $\E(\Phi, R)$ in terms of Tits generators. 
-Thus, it is a quantitative analogue of \cref{prop:Stepanov}
-and a relative analogue of the results of~\cite{Tavgen91, VseUnitrZ1p, VavSmSuUnitrEng}.
-\begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.
-\begin{thmlist}
-\item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
-$W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite;
-\item If $\sr(I) = 1$ and $\Phi$ is an arbitrary irreducible root system, then 
-\[W(\E(\Phi, R, I), \mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1;\]
-\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime number $p$, then under the assumption of the Generalized Riemann Hypothesis one has
-\begin{alignat*}{2}
-& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1 & \text{ if } \Phi=\rA_\ell, \rC_\ell, \\
-& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell.
-\end{alignat*}
-\end{thmlist}
-\end{thm}
-The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{TavgenThesis}, cf.~\cite{Mo07}), 
-while for the second and the third assertion we give a direct proof.
-Compare \cref{thm:width} with a recent result of U.~Hadad and D.~W.~Morris \cite[Theorem~1.6]{Ha12} which asserts that 
-$W(\SL(n, \mathbb{Z}, I), \mathcal{Z}(\Pi))$ is finite for any ideal $I \leq \mathbb{Z}$ and $n \geq 3$.
-
-Another application of the parabolic factorizations developed in the present paper is the subsystem factorization in terms of subgroups of type $\rA_1$.
-The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{LNS11}.
-More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
-
-In~\cite{V13} N.~Vavilov and E.~Kovach noted that the Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for an arbitrary field $F$.
-In fact, in the assumptions of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
-Our next result further extends this to an even larger class of rings (which, for example, includes the ideals of all Dedekind rings).
-\begin{thm}\label{thm:SL2width}
-Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system satisfying one of the following assumptions.
-\[\begin{array}{l@{\quad}l@{\quad}l}
-\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right| - \rk(\Phi) - 1; \\
-\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right| - 2; \\
-\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right| - 3\rk(\Phi).
-\end{array}\]
-Then the principal congruence subgroup $\G(\Phi, R, I)$ can be presented as a product of at most $N$ copies of its (regularly embedded) subgroups isomorphic to $\SL_2(R, I)$.
-\end{thm}
-
-Yet another application of the parabolic factorizations concerns the product decompositions of Chevalley groups formulated in terms of subgroups of type $\rA_\ell$ of submaximal rank.
-Recall that in \cite{Nik07} N.~Nikolov proves the following result. 
-\begin{thm*} Let $G$ be a classical Chevalley group (of normal or twisted type) of rank $\ell$ over a finite field $F$.
-Then $G$ can be presented as a product of at most $200$ conjugates of its subgroups of type $\rA_{\ell-1}$. \end{thm*}
-
-It is classically known that over an arbitrary field $F$ the group $\SL_{n+1}(F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
-On the other hand, one immediately obtains from \cref{thm:DennisVaserstein} and surjective stability for linear $\K_1$-functor that $\SL_{n+1}(R, I)$ factors into a product
-of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
-
-Applying \cref{thm:DennisVaserstein} and proving a more accurate version of \cite[Proposition~1]{Nik07} in the special case $\Phi=\rD_\ell$, we obtain the following result.
-\begin{thm}\label{thm:spin-sln-prod}
-Assume that $\sr(I) \leqslant 2$. Then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of its (regularly embedded) subgroups of type $\rA_{\ell-1}$.
-\end{thm}
-
-The rest of the article is organized as follows.
-In sections \ref{sec:prelim}--\ref{sec:stability-conditions} we introduce the principal notation and prove some basic facts pertaining to Chevalley groups over rings and the stability conditions.
-In section \ref{sec:factorizations} we construct various parabolic factorizations and thus prove \cref{thm:srRI1,thm:DennisVaserstein,thm:SL2width}.
-Finally, we treat the bounded generation and the product decompositions separately in section~\ref{sec:applications}, where \cref{thm:width,thm:spin-sln-prod} are proved.
-
-\section{Preliminaries}\label{sec:prelim}
-For any collection of subsets $H_1, \ldots, H_n$ of a group $G$ we denote by $H_1\ldots H_n$ their Minkowski set-product, 
-i.\,e. the set consisting of arbitrary products $h_1\ldots h_n$ of elements $h_i\in H_i$. In particular, the equality
-$G = H_1\cdot\ldots\cdot H_n$ means that every element $g\in G$ can be presented as a product $h_1\ldots h_n$, where $h_i\in H_i$ for each $i$.
-
-\subsection{Root systems}\label{sec:rootsys}
+The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev \cite[Lemma~2.1]{ST76}.
+The condition $\asr(I) \leq d$ is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm, which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
+
+We also prove the relative analogues of Gauss and Bass---Kolster decompositions (\cref{thm:srRI1,thm:BassKolster}).
+
+We apply these decompositions to several problems.
+First, we investigate the factorizations of Chevalley groups in terms of their subsystem subgroups.
+One of such factorizations if a decomposition into the product of subgroups isomorphic to $\SL(2, R, I)$.
+We show in \cref{thm:SL2width} that for classical groups over rings satisfying assumptions close to the stable rank $\leqslant2$ there exist such factorizations of length having the leading term $3|\Phi^+|$ in case $\Phi=\rA_\ell, \rC_\ell$ and $4|\Phi^+|$ otherwise.
+
+Another is the decomposition in terms of subgroups of type $\rA_\ell$ of submaximal rank.
+We show that Dennis---Vaserstein decomposition can be of great help in this problem.
+Namely, we prove the following
+\begin{restatable*}{thm}{ThmSpinSLnProd}\label{thm:spin-sln-prod}
+Assume that $\sr(I) \leqslant 2$. Then the group $\Epin(2\ell, R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ regularly embedded subgroups of type $\rA_{\ell-1}$.
+\end{restatable*}
+
+Then we obtain the upper bounds on the width of $\E(\Phi, R, I)$ in terms of Vaserstein---Tits generators for various rings (\cref{thm:width}).
+
+Let us now fix the notations used in the paper.
 Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of fundamental roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
 We use the conventional numbering of basis vectors of $\Pi$ which follows Bourbaki (see~\cite[Table~1]{PSV98}).
-Denote by $\Phi^+$ and $\Phi^-$ the subsets of positive and negative roots with respect to $\Pi$.
-Let $\alpha_\mathrm{max}$ denote the maximal root of $\Phi$.
+
 For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ with respect to $\Pi$, i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
@@
 We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\beta, \beta)$.
-Let $\varpi_1, \ldots, \varpi_\ell$ be the \emph{fundamental weights }of $\Phi$, i.\,e. vectors
-defined by $\langle\varpi_i, \alpha_j^\vee\rangle=\delta_{i, j}, $ where $\alpha^\vee = \frac{\alpha}{2(\alpha, \alpha)}$.
+Let $\varpi_1, \ldots, \varpi_\ell$ be the \emph{fundamental weights }of $\Phi$.
 
 Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all simple reflections $\sigma_\alpha$, $\alpha\in\Phi$.
-Recall that a simple reflection is defined by $\sigma_\alpha(\beta)=\beta-\langle\beta, \alpha \rangle\cdot \alpha$.
 For a reductive subset $\Delta\subseteq \Phi$ denote by $W(\Delta)$ the subgroup of $W(\Phi)$ generated by $\sigma_\alpha$ for $\alpha\in\Delta$.
 
-Let $J\subseteq \Pi$ be a subset of fundamental roots. 
-For a root $\beta = \sum m_i(\beta)\alpha_i \in \Phi$ define \emph{$J$-shape} of $\beta$ (denoted $\shape(J, \beta)$) as $\sum_{i\in J} m_i(\beta) \alpha_i$.
-Set
+Let $J\subseteq \Pi$ be a subset of fundamental roots. Define
 \begin{align*}
+& \shape(J, \beta)=\sum\nolimits_{i\in J} m_i(\beta) \alpha_i, \\
 & \Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\}, \\
@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
-We tend to omit curly braces in the above notations in the case when $J$ is a one or two element set, e.\,g., $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
+We tend to omit curly braces in the above notations when $J$ is a one or two element set, e.\,g., $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
 
@@
 
-\subsection{Chevalley groups and their elementary subgroups} \label{sec:elementary}
-Our exposition of Chevalley groups is standard and follows~\cite{Ta, S, St78, VP, Va86}.
-We denote by $\G(\Phi, R)$ the simply-connected Chevalley group of type $\Phi$ over an arbitrary commutative ring $R$.
-For example, for each of the four classical series $\Phi=\rA_\ell, \rB_\ell, \rC_\ell, \rD_\ell$
-the group $\G(\Phi, R)$ equals $\SL(\ell+1, R)$, $\Spin(2\ell+1, R)$, $\Sp(2\ell, R)$, $\Spin(2\ell, R)$, respectively.
-
-Notice that from the uniqueness theorem of M.~Demazure (see~\cite[Corollaire~5.2]{SGA3}) 
-it follows that the exceptional isomorphisms of small-rank groups (which are well-known in the theory of groups over fields) remain valid for Chevalley groups over arbitrary commutative rings.
-In particular, there are isomorphisms of groups $\Spin(3, R)\cong\SL(2, R)$, $\Spin(5, R)\cong \Sp(4, R)$, $\Spin(6, R)\cong\SL(4, R)$, $\SL(2, R)\cong \Sp(2, R)$.
-
-Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$, called the {\it elementary root unipotents}.
-These elements satisfy the well-known Steinberg relations:
-\begin{align}
-& \phantom{[}
-x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \label{rel:add}\\
-& [x_\alpha(s), x_\beta(t)] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right), \quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
-\end{align} 
-The indices $i$, $j$ in the above formula range over all positive integers such that $i\alpha + j\beta\in\Phi$.
-The integers $N_{\alpha\beta ij}$ are called the \emph{structure constants} of the Chevalley group $\G(\Phi, R)$ and depend only on $\Phi$.
-We refer the reader to~\cite[\S14]{VP} for basic properties of the structure constants.
-
-For an additive subset $I\subseteq R$ we denote by $X_\alpha(I)$ the corresponding \emph{root subgroup} of level $I$, i.\,e.
-the subgroup consisting of all elementary root unipotents $x_\alpha(\xi)$, $\xi\in I$.
-
-The subgroup $\E(\Phi, R)$, generated by all $X_\alpha(R)$, $\alpha\in\Phi$ is called the {\it elementary subgroup} of the Chevalley group $\G_{sc}(\Phi, R)$.
+Let $\G(\Phi, R)$ be the simply-connected Chevalley group of type $\Phi$ over an arbitrary commutative ring $R$ and let $\E(\Phi, R)$ be its elementary subgroup, generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$, see~\cite{VP, St78, S}.
+For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (alias the \emph{principal congruence subgroup}) of level $I$.
+
+The \emph{relative elementary Chevalley subgroup} $\E(\Phi, R, I) \leqslant \G(\Phi, R, I)$ is defined as the normal closure in $\E(\Phi, R)$ of the subgroup $\E(\Phi, I)$ generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi, \ \xi \in I \}$.
+
+Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
+It is a classical result of J.~Tits and L.~Vaserstein (see~\cite{Tits76}, \cite[Theorem~2]{Va86}) that the relative elementary subgroup $\E(\Phi, R, I)$ is generated by the set of elements $\mathcal{Z}(\Phi)$.
+Here for a subset of roots $S\subseteq\Phi$ we denote by $\mathcal{Z}(S)$ the set
+\[ \mathcal{Z}(S) =  \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in S\}.\]
+\begin{lemma}[{\cite[Corollary~3.3]{S}}]\label{lemma:Stepanov-ideal}
+Let $\Phi$ be a root system of rank $\geqslant2$, let $R$ be a commutative ring and $I\trianglelefteq R$ be its ideal.
+If $\Phi\neq\rC_\ell$ then $\E\left(\Phi, R, I^2\right)\leqslant\E(\Phi, I)$, otherwise $\E\left(\Phi, R, II^{\indexbox{2}}\right)\leqslant\E(\Phi, I)$.
+\end{lemma}
+Here $I^{\indexbox{2}}$ denotes the ideal generated by the squares $a^2$, where $a\in I$.
+
+%The following recent result of A.~Stepanov served as a starting point for the present paper.
+%The notation for the subgroups involved in the statements of the results below is introduced properly in section~\ref{sec:prelim}.
+%\begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
+%Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be an arbitrary parabolic subset of roots, and $\Sigma_S$ be the special part of $S$.
+The relative elementary subgroup $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$.
+\end{prop}
+
+%The purpose of this paper is two-fold. 
+%First, we obtain relative analogues of several classical parabolic factorizations of Chevalley groups such as the Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
+%Then we apply these factorizations to the study of various bounded generation properties of Chevalley groups over rings.
+%
+%Our first result is a relative version of the Gauss decomposition formulated in terms of the \emph{stable rank} of the ideal $I$ (see section~\ref{sec:stability-conditions} for the definition)
+%\begin{thm}\label{thm:srRI1}
+%Let $\Phi$ be a root system, let $I$ be an ideal of an arbitrary commutative ring $R$, and assume that $\sr(I)=1$.
+%Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits the following decomposition:
+%\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi, I). \]
+%\end{thm}
+%In the special case when $I$ is contained in the Jacobson radical of $R$, \cref{thm:srRI1} boils down to~\cite[Proposition~2.3]{Abe76}. 
+%We also note that the absolute case (i.\,e. $I=R$) of the theorem was treated by the second named author in~\cite{Sm12}.
+%
+%The next main result is the relative Dennis---Vaserstein decomposition, which holds for a broader class of rings as compared to \cref{thm:srRI1}.
+%\begin{thm}\label{thm:DennisVaserstein}
+%Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geqslant 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
+Denote the distance between $r$ and $s$ by $d$.
+%Assume that $\Phi$, $I$ and $\{r, s\}$ satisfy either of the following assumptions:
+%\begin{thmlist}
+% \item $\sr(I) \leqslant d$ for classical $\Phi$,
+% \item $\sr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{ 2, \ell \}$,
+% \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
+% \item $\asr(I) \leqslant d$ for $\Phi=\rF_4$.
+%\end{thmlist}
+%Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$ \end{thm}
+%Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5 and~4.1]{St78}.
+%The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev (cf.~\cite[Lemma~2.1]{ST76}).
+%
+%The condition $\asr(I) \leq d$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm, which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
+%
+%Let $G$ be an abstract group with a generating set $X \subset G$. 
+%We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
+%
+%Our first application of the parabolic factorizations is the following theorem, which gives an upper bound on the width of $\E(\Phi, R)$ in terms of Tits generators. 
+%Thus, it is a quantitative analogue of \cref{prop:Stepanov}
+%and a relative analogue of the results of~\cite{Tavgen91, VseUnitrZ1p, VavSmSuUnitrEng}.
+%\begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.
+%\begin{thmlist}
+%\item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
+%$W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite;
+%\item If $\sr(I) = 1$ and $\Phi$ is an arbitrary irreducible root system, then 
+%\[W(\E(\Phi, R, I), \mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1;\]
+%\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime number $p$, then under the assumption of the Generalized Riemann Hypothesis one has
+%\begin{alignat*}{2}
+%& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1 & \text{ if } \Phi=\rA_\ell, \rC_\ell, \\
+%& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell.
+%\end{alignat*}
+%\end{thmlist}
+%\end{thm}
+%The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{TavgenThesis}, cf.~\cite{Mo07}), 
+%while for the second and the third assertion we give a direct proof.
+%Compare \cref{thm:width} with a recent result of U.~Hadad and D.~W.~Morris \cite[Theorem~1.6]{Ha12} which asserts that 
+%$W(\SL(n, \mathbb{Z}, I), \mathcal{Z}(\Pi))$ is finite for any ideal $I \leq \mathbb{Z}$ and $n \geq 3$.
+%
+%Another application of the parabolic factorizations developed in the present paper is the subsystem factorization in terms of subgroups of type $\rA_1$.
+%The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{LNS11}.
+%More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
+%
+%In~\cite{V13} N.~Vavilov and E.~Kovach noted that the Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for an arbitrary field $F$.
+%In fact, in the assumptions of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
+%Our next result further extends this to an even larger class of rings (which, for example, includes the ideals of all Dedekind rings).
+%\begin{thm}\label{thm:SL2width}
+%Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system satisfying one of the following assumptions.
+%\[\begin{array}{l@{\quad}l@{\quad}l}
+%\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right| - \rk(\Phi) - 1; \\
+%\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right| - 2; \\
+%\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right| - 3\rk(\Phi).
+%\end{array}\]
+%Then the principal congruence subgroup $\G(\Phi, R, I)$ can be presented as a product of at most $N$ copies of its (regularly embedded) subgroups isomorphic to $\SL_2(R, I)$.
+%\end{thm}
+%
+%Yet another application of the parabolic factorizations concerns the product decompositions of Chevalley groups formulated in terms of subgroups of type $\rA_\ell$ of submaximal rank.
+%Recall that in \cite{Nik07} N.~Nikolov proves the following result. 
+%\begin{thm*} Let $G$ be a classical Chevalley group (of normal or twisted type) of rank $\ell$ over a finite field $F$.
+%Then $G$ can be presented as a product of at most $200$ conjugates of its subgroups of type $\rA_{\ell-1}$. \end{thm*}
+%
+%It is classically known that over an arbitrary field $F$ the group $\SL_{n+1}(F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
+%On the other hand, one immediately obtains from \cref{thm:DennisVaserstein} and surjective stability for linear $\K_1$-functor that $\SL_{n+1}(R, I)$ factors into a product
+%of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
+%
+%Applying \cref{thm:DennisVaserstein} and proving a more accurate version of \cite[Proposition~1]{Nik07} in the special case $\Phi=\rD_\ell$, we obtain the following result.
+%\begin{thm}\label{thm:spin-sln-prod}
+%Assume that $\sr(I) \leqslant 2$. Then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of its (regularly embedded) subgroups of type $\rA_{\ell-1}$.
+%\end{thm}
+
+%The rest of the article is organized as follows.
+%In sections \ref{sec:prelim}--\ref{sec:stability-conditions} we introduce the principal notation and prove some basic facts pertaining to Chevalley groups over rings and the stability conditions.
+%In section \ref{sec:factorizations} we construct various parabolic factorizations and thus prove \cref{thm:srRI1,thm:DennisVaserstein,thm:SL2width}.
+%Finally, we treat the bounded generation and the product decompositions separately in section~\ref{sec:applications}, where \cref{thm:width,thm:spin-sln-prod} are proved.
 
 For $\varepsilon\in R^*$ set $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_{\alpha}(\varepsilon).$
-If $\rk(\Phi)\geqslant 2$ the following relation is a consequence of \eqref{rel:add}--\eqref{rel:CCF}:
+If $\rk(\Phi)\geqslant 2$ the following relation holds:
 \begin{equation}\label{rel:R3}
@@
 
-\subsection{Representations of Chevalley groups} \label{sec:repr}
-Our notation and terminology pertaining to the representations of Chevalley groups follows \cite[\S~1.4]{PSV98} and \cite[\S~I.2]{Ma69})
-Let $\pi$ be an irreducible representation of $\G(\Phi, R)$ acting on a free $R$-module $V$.
-We denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $\Lambda(\pi)^*$ the subset of non-zero weights.
-Denote by $V_\lambda \leq V$ the \emph{weight subspace}, corresponding to $\lambda\in\Lambda(\pi)$ and denote by $m_\lambda$ the dimension of $V_\lambda$.
-
-A representation $\pi$ is called \emph{basic} if for every pair of non-zero weights $\lambda, \mu \in \Lambda^*(\pi)$ such that $\lambda - \mu \in \Pi$ one has $\sigma_\alpha(\lambda) = \mu$ for some $\alpha\in\Phi$.
-Obviously, this is equivalent to saying that $W(\Phi)$ acts transitively on $\Lambda(\pi)^*$.
-
-The irreducible representations of Chevalley groups used in the present paper form a sublist of~\cite[Table~2]{PSV98}.
-More specifically, all of them are \emph{fundamental} (i.\,e. their highest weight is fundamental) and basic.
-We widely employ the technique of \emph{weight diagrams} (see~\cite[\S~2]{PSV98}) to help visualize the structure of these representations.
-In the simplest case of a \emph{microweight} representation $\pi$ (i.\,e. $\pi$ is basic and $V_0 = 0$)
-the weight diagram of $(V, \pi)$ is just an undirected graph whose vertices are in the one-to-one correspondence with the elements of $\Lambda(\pi)$.
-Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ if $\lambda-\mu = \alpha_i$.
-
-An immediate application of the weight diagrams is that they allow one to quickly read off the branching of a given basic representation with respect to a subsystem subgroup.
-If $J$ is a subset of $\Pi$ and $\Delta$ is the subsystem of $\Phi$ spanned by $J$ then the weight diagram of $\pi$ restricted to $G(\Delta, R)$ can be obtained
-from the weight diagram of $\pi$ by simply removing all the bonds whose label $i$ is such that $\alpha_i\not\in J$ (cf.~\cite[\S~2.7]{PSV98}).
-
-Recall that all nonzero weights of a basic representation have multiplicty one and the multiplicity $m_0$ of the zero weight subspace equals $|\Delta(\pi)|$, where $\Delta(\pi)= \Lambda(\pi)^* \cap \Pi$ (see~\cite[Lemma~2.1]{Ma69}).
-For $\alpha \in \Phi$ one can define certain elements $e_0(\alpha) \in V_0$ and $\alpha_* \in V_0^* = \Hom_R(V_0, R)$
-and choose some set of vectors $E^* = \{ e_\lambda \}_{\lambda \in \Lambda^*(\pi)}$ in such a way that 
-$E_\pi = E^* \cup \{ e_0(\alpha) \}_{\alpha \in \Delta(\pi)}$ forms a basis of $V$ in which the action of the elementary root unipotents
-$x_\alpha(\xi)$ has a particularly simple description.
-
-\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
-Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
-Then the action of $x_\alpha(\xi)$ is described by the following formulae.
-\newline \begin{tabular}{ll}
-If $\lambda\in\Lambda(\pi)^*, \ \lambda+\alpha\notin\Lambda(\pi)$, then & $x_\alpha(\xi)e_\lambda=e_\lambda$; \\
-If $\lambda, \lambda+\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_\lambda=e_\lambda\pm\xi e_{\lambda+\alpha}$; \\
-If $\alpha\notin\Lambda(\pi)^*$, then & $x_\alpha(\xi)v_0=v_0$ for any $v_0\in V_0$; \\
-If $\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_{-\alpha} = e_{-\alpha}\pm\xi e_0(\alpha)\pm\xi^2 e_\alpha$ and \\
-                                   & $x_\alpha(\xi)v_0         = v_0\pm\xi\alpha_*(v_0)e_\alpha$ for $v_0 \in V_0$.
-\end{tabular} \end{lemma}
-The statement of the above lemma can be visualized using the weight diagrams, see~\cite[\S~3.4]{PSV98}.
-Although it is possible to fix the signs in the statement of the above lemma, we make no attempt to do this and refer the reader to~\cite{V08}.
-
-Notice that the highest weight of the natural representations of the classical groups is $\varpi_1$.
-It will be convenient for us to number the weights of these representations as in~\cite[\S~1B]{St78}:
-\[\begin{array}{cll}
-  1, 2, \ldots, \ell+1 & \text{in the case} & \Phi =\rA_\ell, \\
-  1, 2, \ldots \ell, 0, -\ell, \ldots, -2, -1 & \text{in the case} & \Phi =\rB_\ell, \\
-  1, 2, \ldots \ell, -\ell, \ldots, -2, -1 & \text{in the cases}   & \Phi =\rC_\ell, \rD_\ell. \\
-\end{array}\]
-For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ etc.
-
-Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ such that $\lambda_1-\lambda_2\in \Phi$.
-It will be convenient for us to write $x_{\lambda_1, \lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
-For example, for $\Phi=\rA_\ell$ we have $x_{1, 2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
-
-\subsection{Relative Chevalley groups}\label{sec:relative-elementary}
-Recall from the introduction that the elements $z_\alpha(s, \xi) = x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$ generate $\E(\Phi, R, I)$ as an abstract group.
-
-\begin{lemma}[{\cite[Corollary~3.3]{S}}]\label{lemma:Stepanov-ideal}
-Let $\Phi$ be a root system of rank $\geqslant2$, let $R$ be a commutative ring and $I\trianglelefteq R$ be its ideal.
-If $\Phi\neq\rC_\ell$ then $\E\left(\Phi, R, I^2\right)\leqslant\E(\Phi, I)$, otherwise $\E\left(\Phi, R, II^{\indexbox{2}}\right)\leqslant\E(\Phi, I)$.
-\end{lemma}
-Here $I^{\indexbox{2}}$ denotes the ideal generated by the squares $a^2$, where $a\in I$.
-Recall also that $I^2$ is generated by the products $ab$ for all $a, b\in I$.
-Clearly, $II^{\indexbox{2}}$ is generated by the elements of the form $a^2b$ for $a, b\in I$.
+%Our notation and terminology pertaining to the representations of Chevalley groups follows \cite[\S~1.4]{PSV98} and \cite[\S~I.2]{Ma69})
+%Let $\pi$ be an irreducible representation of $\G(\Phi, R)$ acting on a free $R$-module $V$.
+%We denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $\Lambda(\pi)^*$ the subset of non-zero weights.
+%Denote by $V_\lambda \leq V$ the \emph{weight subspace}, corresponding to $\lambda\in\Lambda(\pi)$ and denote by $m_\lambda$ the dimension of $V_\lambda$.
+%
+%A representation $\pi$ is called \emph{basic} if for every pair of non-zero weights $\lambda, \mu \in \Lambda^*(\pi)$ such that $\lambda - \mu \in \Pi$ one has $\sigma_\alpha(\lambda) = \mu$ for some $\alpha\in\Phi$.
+%Obviously, this is equivalent to saying that $W(\Phi)$ acts transitively on $\Lambda(\pi)^*$.
+
+%The irreducible representations of Chevalley groups used in the present paper form a sublist of~\cite[Table~2]{PSV98}.
+%More specifically, all of them are \emph{fundamental} (i.\,e. their highest weight is fundamental) and basic.
+%We widely employ the technique of \emph{weight diagrams} (see~\cite[\S~2]{PSV98}) to help visualize the structure of these representations.
+%In the simplest case of a \emph{microweight} representation $\pi$ (i.\,e. $\pi$ is basic and $V_0 = 0$)
+%the weight diagram of $(V, \pi)$ is just an undirected graph whose vertices are in the one-to-one correspondence with the elements of $\Lambda(\pi)$.
+%Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ if $\lambda-\mu = \alpha_i$.
+%
+%An immediate application of the weight diagrams is that they allow one to quickly read off the branching of a given basic representation with respect to a subsystem subgroup.
+%If $J$ is a subset of $\Pi$ and $\Delta$ is the subsystem of $\Phi$ spanned by $J$ then the weight diagram of $\pi$ restricted to $G(\Delta, R)$ can be obtained
+%from the weight diagram of $\pi$ by simply removing all the bonds whose label $i$ is such that $\alpha_i\not\in J$ (cf.~\cite[\S~2.7]{PSV98}).
+% 
+%Recall that all nonzero weights of a basic representation have multiplicty one and the multiplicity $m_0$ of the zero weight subspace equals $|\Delta(\pi)|$, where $\Delta(\pi)= \Lambda(\pi)^* \cap \Pi$ (see~\cite[Lemma~2.1]{Ma69}).
+%For $\alpha \in \Phi$ one can define certain elements $e_0(\alpha) \in V_0$ and $\alpha_* \in V_0^* = \Hom_R(V_0, R)$
+%and choose some set of vectors $E^* = \{ e_\lambda \}_{\lambda \in \Lambda^*(\pi)}$ in such a way that 
+%$E_\pi = E^* \cup \{ e_0(\alpha) \}_{\alpha \in \Delta(\pi)}$ forms a basis of $V$ in which the action of the elementary root unipotents
+%$x_\alpha(\xi)$ has a particularly simple description.
+%
+%\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
+%Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
+%Then the action of $x_\alpha(\xi)$ is described by the following formulae.
+%\newline \begin{tabular}{ll}
+%If $\lambda\in\Lambda(\pi)^*, \ \lambda+\alpha\notin\Lambda(\pi)$, then & $x_\alpha(\xi)e_\lambda=e_\lambda$; \\
+%If $\lambda, \lambda+\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_\lambda=e_\lambda\pm\xi e_{\lambda+\alpha}$; \\
+%If $\alpha\notin\Lambda(\pi)^*$, then & $x_\alpha(\xi)v_0=v_0$ for any $v_0\in V_0$; \\
+%If $\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_{-\alpha} = e_{-\alpha}\pm\xi e_0(\alpha)\pm\xi^2 e_\alpha$ and \\
+%                                   & $x_\alpha(\xi)v_0         = v_0\pm\xi\alpha_*(v_0)e_\alpha$ for $v_0 \in V_0$.
+%\end{tabular} \end{lemma}
+
+%\subsection{Relative Chevalley groups}\label{sec:relative-elementary}
+%Recall from the introduction that the elements $z_\alpha(s, \xi) = x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$ generate $\E(\Phi, R, I)$ as an abstract group.
 
@@
 The subgroup $\U(\Sigma_J^+, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I)$ is a subgroup called a \emph{standard parabolic subgroup}.
-The following two equalities will be referred to in the sequel as the \emph{Levi decomposition}:
+The following two equalities will be referred to as the \emph{Levi decomposition}:
 \begin{equation} \label{rel:Levi-decomp} \EP_J(R, I) = \U(\Sigma_J^+, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I). \end{equation}
@@
 Let $\pi$ be a basic fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
-Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then 
-\[ g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I). \]
-\end{lemma}
-
-\subsection{\texorpdfstring{$\K_1$}{K1}-functor modeled on Chevalley groups}
-Recall that by a theorem of Taddei $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).
-
-Using standard relativization argument it is not hard to deduce from Taddei's result that $\E(\Phi, R, I)$ is normal in $\G(\Phi, R, I)$ under the same assumptions on $\Phi$.
-This allows us to define the relative $\K_1$-group as $\K_1(\Phi, R, I)=\G(\Phi, R, I)/\E(\Phi, R, I).$
-When $I=R$, we write $\K_1(\Phi, R)$ for $\K_1(\Phi, R, R)$.
-
-In some cases it is known that $\K_1(\Phi, R, I)$ is trivial.
-For example, $\SK_1(\ell+1, R)=\K(\rA_\ell, R)=1$ for any ring of stable rank $1$ (see section~\ref{sec:stability-conditions}), 
-and for other root systems some stronger assumption is required such as $\asr(R)=1$ or being semilocal. 
-For any Euclidean ring $\K_1(\Phi, R, I)$ is trivial for every root system $\Phi$.
-
-Let $k$ be a global field, $S$ be a set of places of $k$, 
-$\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and $I$ be an ideal of $\mathcal{O}_S$.
-\begin{prop} \label{prop:K1triv}
-Let $\Phi$ be a root system of rank $\geqslant2$. Assume that the field $k$ has a real embedding. Then $\K_1(\Phi, \mathcal{O}_S, I)=1$.
-\end{prop}
-\begin{proof} Follows from \cite[Theorem~3.6]{BMS} and \cite[Corollary~4.5]{Ma69}. \end{proof}
+Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then $g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
+\end{lemma}
+
+%\subsection{\texorpdfstring{$\K_1$}{K1}-functor modeled on Chevalley groups}
+%Recall that by a theorem of Taddei $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).
+%
+%Using standard relativization argument it is not hard to deduce from Taddei's result that $\E(\Phi, R, I)$ is normal in $\G(\Phi, R, I)$ under the same assumptions on $\Phi$.
+%This allows us to define the relative $\K_1$-group as $\K_1(\Phi, R, I)=\G(\Phi, R, I)/\E(\Phi, R, I).$
+%When $I=R$, we write $\K_1(\Phi, R)$ for $\K_1(\Phi, R, R)$.
+%
+%In some cases it is known that $\K_1(\Phi, R, I)$ is trivial.
+%For example, $\SK_1(\ell+1, R)=\K(\rA_\ell, R)=1$ for any ring of stable rank $1$ (see section~\ref{sec:stability-conditions}), 
+%and for other root systems some stronger assumption is required such as $\asr(R)=1$ or being semilocal. 
+%For any Euclidean ring $\K_1(\Phi, R, I)$ is trivial for every root system $\Phi$.
+%
+%Let $k$ be a global field, $S$ be a set of places of $k$, 
+%$\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and $I$ be an ideal of $\mathcal{O}_S$.
+%\begin{prop} \label{prop:K1triv}
+%Let $\Phi$ be a root system of rank $\geqslant2$. Assume that the field $k$ has a real embedding. Then $\K_1(\Phi, \mathcal{O}_S, I)=1$.
+%\end{prop}
+%\begin{proof} Follows from \cite[Theorem~3.6]{BMS} and \cite[Corollary~4.5]{Ma69}. \end{proof}
 
@@
 
-It is not hard to show that for an $I$-unimodular row $a$ there exists an $I$-unimodular column $b$ such that $ab=1$ (see~\cite[\S~2]{Va69}).
+It is not hard to show that for an $I$-unimodular row $a$ there exists an $I$-unimodular column $b$ such that $ab=1$ (see~\cite[\S2]{Va69}).
 
@@
 
-The following proposition summarizes the basic properties of the stable rank.
-\begin{prop} \label{prop:sr_properties}
-Let $R$ be an arbitrary commutative unital ring and let $I\trianglelefteq R$ be an ideal.
-\begin{lemlist}
-\item For any ideal $I'\subseteq I$ one has $\sr(I')\leqslant\sr(I)$, $\sr(I/I')\leqslant\sr(I)$;
-\item One has $\sr\Bigl(\prod\limits_{i=1}^n R_i\Bigr)=\max\limits_{i=1}^n\bigl(\sr(R_i)\bigr)$;
-\item Let $J(R)$ denote the Jacobson radical of $R$, then $\sr(R)=\sr(R/J(R))$ and $\sr(J(R))=1$;
-\item Let $I\rtimes\mathbb{Z}$ denote the ring obtained by formally adjoining $1$ to $I$. Then $\sr(I\rtimes\mathbb{Z})=\max(2,\sr(I))$.
-\end{lemlist}
-\end{prop}
-\begin{proof} See~\cite[Theorem~2.3]{Va69}, \cite{Va71}. 
-\end{proof}
-\begin{example}
-Since the stable rank of a field equals $1$, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$.
-Other examples of rings of stable rank $1$ are provided by the Boolean rings, the ring of all algebraic integers, the ring of entire functions, the disk-algebra, etc.
+%The following proposition summarizes the basic properties of the stable rank.
+%\begin{prop} \label{prop:sr_properties}
+%Let $R$ be an arbitrary commutative unital ring and let $I\trianglelefteq R$ be an ideal.
+%\begin{lemlist}
+%\item For any ideal $I'\subseteq I$ one has $\sr(I')\leqslant\sr(I)$, $\sr(I/I')\leqslant\sr(I)$;
+%\item One has $\sr\Bigl(\prod\limits_{i=1}^n R_i\Bigr)=\max\limits_{i=1}^n\bigl(\sr(R_i)\bigr)$;
+%\item Let $J(R)$ denote the Jacobson radical of $R$, then $\sr(R)=\sr(R/J(R))$ and $\sr(J(R))=1$;
+%\item Let $I\rtimes\mathbb{Z}$ denote the ring obtained by formally adjoining $1$ to $I$. Then $\sr(I\rtimes\mathbb{Z})=\max(2,\sr(I))$.
+%\end{lemlist}
+%\end{prop}
+%\begin{proof} See~\cite[Theorem~2.3]{Va69}, \cite{Va71}. 
+%\end{proof}
+%\begin{example}
+%Since the stable rank of a field equals $1$, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$.
+%Other examples of rings of stable rank $1$ are provided by the Boolean rings, the ring of all algebraic integers, the ring of entire functions, the disk-algebra, etc.
 For this and many other examples see~\cite{VasSR1}.
-
-%Formally adjoining a unit to a non-unital ring of stable rank $1$ produces a non-trivial example of an ideal having the stable rank strictly lower that the ambient ring.
-\end{example}
+%
+%%Formally adjoining a unit to a non-unital ring of stable rank $1$ produces a non-trivial example of an ideal having the stable rank strictly lower that the ambient ring.
+%\end{example}
 
@@
 \begin{equation} \label{sr-estimates} \sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \end{equation}
-There exist examples of rings for which the first inequality in the above formula is strict.
-More precisely, there are rings of stable rank $1$ but of absolute stable rank $\geqslant2$, see~\cite{MKV}.
-On the other hand, \cite[Theorem~1.3]{MKV} shows that $\sr(R)=\asr(R)$ for any principal ideal ring $R$.
-\begin{example}
-From inequality~\eqref{sr-estimates} one concludes, in particular, that 
-\begin{itemize}
-\item $\asr(R) = 1$ for every semilocal ring $R$;
-\item $\asr(R)\leqslant2$ for every Dedekind domain $R$;
-\item $\asr(A[x])\leqslant3$ for every locally principal ring $A$;
-\item $\asr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$.
-\end{itemize}
-For certain classes of fields there is also a lower estimate for $\sr(F[x_1, \ldots, x_n])$ which allows to compute precisely the value of both $\sr(R)$ and $\asr(R)$.
-For example, $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ (see~\cite{Kru73}) and $\sr(F[x_1, \ldots, x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
-Notice also that $\sr(\mathbb{Z}[x])=3$ (see \cite{GMV}) and $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ for $n>1$ (see example after~\cite[Theorem~18.2]{VS76}).
-\end{example}
+%There exist examples of rings for which the first inequality in the above formula is strict.
+%More precisely, there are rings of stable rank $1$ but of absolute stable rank $\geqslant2$, see~\cite{MKV}.
+%On the other hand, \cite[Theorem~1.3]{MKV} shows that $\sr(R)=\asr(R)$ for any principal ideal ring $R$.
+%\begin{example}
+%From inequality~\eqref{sr-estimates} one concludes, in particular, that 
+%\begin{itemize}
+%\item $\asr(R) = 1$ for every semilocal ring $R$;
+%\item $\asr(R)\leqslant2$ for every Dedekind domain $R$;
+%\item $\asr(A[x])\leqslant3$ for every locally principal ring $A$;
+%\item $\asr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$.
+%\end{itemize}
+%For certain classes of fields there is also a lower estimate for $\sr(F[x_1, \ldots, x_n])$ which allows to compute precisely the value of both $\sr(R)$ and $\asr(R)$.
+%For example, $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ (see~\cite{Kru73}) and $\sr(F[x_1, \ldots, x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
+%Notice also that $\sr(\mathbb{Z}[x])=3$ (see \cite{GMV}) and $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ for $n>1$ (see example after~\cite[Theorem~18.2]{VS76}).
+%\end{example}
 
@@
 \begin{equation*}
-a_{ij} = b_{ij} v_{j} + b_{ji} v_{i},\ j\neq i,\quad a_{ii} = b_{ii} v_{i} - \sum\limits_{\mathclap{\substack{j=1 \\ j\neq i}}}^\ell b_{ji} v_{j}. \qedhere
+a_{ij} = b_{ij} v_{j} + b_{ji} v_{i},\ j\neq i,\quad a_{ii} = b_{ii} v_{i} - \sum\limits_{\mathclap{j=1,\ j\neq i}}^\ell b_{ji} v_{j}. \qedhere
 \end{equation*}
@@
 \textsc{Case $\Phi=\rD_\ell$.} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \subseteq I$.
-By \cref{prop:sr_properties} $\sr(I/J) \leqslant \ell-1$, therefore
-the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
+Since $\sr(I/J) \leqslant \ell-1$, the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
 This implies the existence of an element $h\in \E(\Delta_\ell, R, I)$ such that the vector $v' = h \cdot v$ satisfies $v'_i \equiv \delta_{i1} \pmod J$ for $i=1, \ldots, \ell$.
@@
 In this section we formulate and prove the relative versions of the decompositions from~\cite{St78}, which will be the main technical tools throughout the next section.
-
-\subsection{Relative Gauss decomposition}\label{sec:gauss}
-The proof of the Gauss decomposition presented below is similar to the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
-\begin{prop}\label{thm:Gauss}
-Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1$, $\Delta_\ell$ be
-two reductive subsystems of $\Phi$, corresponding to the endnodes of the Dynkin diagram of $\Phi$.
-Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit the triangular decomposition with $N$ triangular factors:
-\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I), \quad i=1, \ell. \]
-Then the ambient group $\E(\Phi, R, I)$ admits the decomposition with the same number of factors:
-\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm, I). \]
-\end{prop}
-\begin{proof}
-Denote by $Y$ the product of subgroups in the right-hand side of the above equality.
-To show that $Y=\E(\Phi, R, I)$ it suffices to check that
-\begin{enumerate}
-\item $Y$ is normalized by $\E(\Phi, R)$, i.\,e. $Y^{\E(\Phi, R)}\subseteq Y$;
-\item there exists a set $X$, generating $\E(\Phi, R, I)$ as a \emph{normal} subgroup of $\E(\Phi, R)$ such that $XY\subseteq Y$.
-\end{enumerate}
-To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for any $\alpha\in \pm \Pi$, $\xi\in R$.
-Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or for $i=\ell$, and we can expand $Y$ as follows:
-\[ Y=\Hh(\Phi, R, I) \cdot \U(\Delta_i^+, I) \cdot \ldots \cdot \U^\pm(\Delta_i, I) \cdot \U(\Sigma_i^+, I) \cdot \ldots \cdot \U(\Sigma_i^\pm, I). \]
-For every  $h \in \Hh(\Phi, R, I)$ one has for some $s\in I$
-\[ x_\alpha(\xi)\cdot h = h\cdot x_\alpha((1+s)\xi)=h\cdot x_\alpha(\xi)\, x_\alpha(s\xi). \]
-
-Therefore by the assumption of the theorem
-\begin{multline*}
-Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi, R, I) \cdot x_\alpha(-\xi) \cdot X_{\alpha}(I) \cdot \E(\Delta_i, R, I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) =\\
-= \Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) = Y.
-\end{multline*}
-
-Now set $X=\left\{x_\alpha(\xi)\ \middle|\ \alpha\in\Pi, \ \xi\in I \right\}$. 
-Every root is a conjugate of some fundamental root under the action of $W(\Phi)$.
-Since $\E(\Phi, R)$ contains the normalizer of the torus, the set $X^{\E(\Phi, R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi), \  \alpha\in\Phi, \ \xi\in I \rangle$.
-Finally, the inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi, R, I)$ normalizes every root subgroup $X_\alpha(I)$.
-\end{proof}
-
-\begin{proof}[Proof of \cref{thm:srRI1}]
-In view of the above proposition it suffices to prove that the Gauss decomposition of length $3$ holds for $\Phi=\rA_1$.
-
-Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}$ be an element of $\SL(2, R, I)$.
-The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
-Multiplying $A$ on the left by $x_{12}(z)$, we get a matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with the invertible  element $a'$ in the top-left corner.
-After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
-Thus we have obtained the relative Gauss decomposition of $A$
-\begin{equation*}
-A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
-\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
-\cdot x_{12}(b'/a')=x_{12}(-z)\cdot
-\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
-\cdot x_{21}(y) \cdot x_{12}(b'/a'), 
-\end{equation*}
-where $\varepsilon\in 1+I$ and $y\in I$. \end{proof}
-
-\subsection{Relative Bass---Kolster decompositions}\label{sec:bass-kolster}
-The next theorem is a relative version of the so-called Bass---Kolster decomposition (cf.~\cite[Theorem~2.1]{St78}).
-\begin{thm}\label{thm:BassKolster}
-Let $\Phi$ be a classical root system of rank $\ell\geqslant2$, let $R$ be an arbitrary commutative ring and $I$ be an ideal, satisfying one of the following assumptions:
-\[\begin{array}{l@{\quad}l@{\quad}l@{\quad}c}
-\Phi = \rA_\ell, \ \ell\geqslant 2, & \sr(I) \leqslant \ell; \\
-\Phi = \rC_\ell, \ \ell\geqslant 2, & \sr(I) \leqslant 2\ell-1; \\
-\Phi = \rB_\ell, \rD_\ell, \ \ell\geqslant 3, & \asr(I) \leqslant \ell-1.
-\end{array}\]
-Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of the Bass---Kolster decomposition:
-\[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]
-where $Z = Z_{\alpha_\mathrm{max}}(I)=\left\{z_{-\alpha_\mathrm{max}}(r, 1)\ \middle|\ r\in I \right\}$.
-\end{thm}
-\begin{proof}
-
-Let $g$ be an element of $\G(\Phi, R, I)$. Set $v=g \cdot v^+\in\Ums(n, I)$. 
-Notice that in each case it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that 
-\begin{equation} \label{eq1} (g'\cdot v^+)_{1} = 1 + s \text{ and } (g'\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}} = s\ \text{for some}\ s\in I. \end{equation}
-Indeed, set $g'' = z_{-\alpha\ssub{max}}(-s, 1) \cdot g'$.
-Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}=0$ and the conclusion of the theorem follows from \cref{lemma:Chevalley-Matsumoto}.
-
-\textsc{Case $\Phi=\rA_\ell$, $n=\ell + 1$.}
-Since $\sr(I)\leqslant\ell$, one can find $a_1, \ldots, a_\ell\in I$ such that $(v_1+a_1v_{\ell+1}, \ldots, v_\ell+a_\ell v_{\ell+1})^t=(v'_1, \ldots, v'_\ell)^t$ is $I$-unimodular.
-Then there are $b_1, \ldots, b_\ell\in I$ such that $b_1v'_1+\ldots b_\ell v'_\ell=v'-1\in I$. 
-Thus the vector \[ v'' = \prod_{i=1}^\ell x_{\ell+1, i}(b_i) \cdot \prod_{i=1}^\ell x_{i, \ell+1}(a_i) \cdot v \]
-satisfies the equalities~\eqref{eq1}.
-
-\textsc{Case $\Phi=\rC_\ell$, $n=2\ell$.}
-Notice that the column $(v_1, \ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
-Applying the assumption $\sr(I)\leqslant 2\ell-1$, we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
-By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for
-\[ h_1 = x_{1, -1}(c_1 + d) \cdot \prod_{i=2}^{-2} x_{i, -1}(c_i) \in \U(\Sigma_1^+, I). \]
-We can find $f_1, f_2, \ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
-Set $\xi = v''_1-v''_{-1}-1 \in I$, 
-\[ h_2 = x_{-1, 1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1, i}(\xi f_i) \in \U(\Sigma_1^-, I). \]
-Direct computation shows that the vector $v'' = h_2 \cdot v'$ satisfies equalities~\eqref{eq1}.
-
-\textsc{Case $\Phi=\rD_\ell$, $n= 2\ell$.} 
-By \cref{item:asrUnipD} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of $v'=h_1 \cdot v$ is $I$-unimodular.
-Since $\sr(I)\leqslant \ell-1$, we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
-\[ v''=h_2 \cdot x_{1, 2}(c_1) \cdot v', \quad h_2=\prod_{i=3}^\ell x_{i, 2}(c_i). \]
-We can find $f_1, f_3, \ldots, f_\ell \in R$ such that $f_1v''_1+\sum_{i=3}^\ell f_i v''_{i} = 1$.
-As before, set
-\[ \xi = v''_1-v''_{-2}-1 \in I, \quad h_3 = x_{-2, 1}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-2, i}(\xi f_i), \quad v'''=h_3 \cdot v''. \]
-Clearly, $t_{1, 2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, $ h_3 \cdot h_2 \in \U(\Phi^-, I)$ and $v'''$ satisfies~\eqref{eq1}.
-
-\textsc{Case $\Phi=\rB_\ell$, $n=2\ell+1$.} Subdivide $v\in \Ums(2\ell+1, I)$ as $v=(v_+, v_0, v_-)\in R^\ell\times R\times R^\ell$.
-Denote by $J\leqslant I$ the ideal spanned by the components of $v_-$.
-Since $\sr(I/J)\leqslant \ell$, we can find $c_1, \dots, c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell x_{i, 0}(c_i) \in \U(\Phi^+, I)$
-one has $\bar{v'}_+=(\bar{v'_1}, \ldots, \bar{v'_\ell}) \in \Ums(\ell, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, I)$.
-Now the proof can be finished by repeating the argument for the case $\Phi=\rD_\ell$ (applied to the subset of long roots of $\rB_\ell$).
-\end{proof}
-
-It is easy to see that the proof of the above theorem is effective and gives an estimate of the total number of elementary root unipotents involved in the decomposition.
-\begin{cor}\label{cor:bass-kolster-count}
-In the assumptions and notation of \cref{thm:BassKolster} every element of $\G(\Phi, R, I)$ 
-can be factored into a product of one element of $\G(\Delta_1, R, I)$, one element of $Z$ and at most $4|\Sigma_1|-1$ elements of $\mathcal{X}$.
-\end{cor}
-\begin{proof}
-The assertion can be obtained by a careful analysis of the proof of the previous theorem.
-Cases $\Phi=\rA_\ell, \rC_\ell$ are immediate.
-In the case $\Phi=\rD_\ell$ from the proof of \cref{thm:BassKolster} one obtains that
-\begin{equation*} \G(\Phi, R, I) =  \U(\Sigma_\ell^+, I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1, I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z \cdot \U(\Sigma_1^-, I) \cdot \U(\Sigma_1^+, I) \cdot \G(\Delta_1, R, I).
-\end{equation*}
-We can present an element $g$ of $\U(\Sigma_\ell^+, I)$ as a product of $g_1 \in \U(\Sigma_{1, 2}^+ \cap \Sigma_\ell^+)$ and $g_2\in \U(\Delta_{1, 2}\cap \Sigma_\ell^+)$.
-An examination of the extended Dynkin diagram of $\rD_\ell$ shows that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one)
-and therefore can be moved to the right until it is consumed by $\G(\Delta_1, R, I)$.
-On the other hand, $g_1$ is a product of at most $2\ell-3$ elementary unipotents, while the width of $\U(\Sigma_1^\pm, I)$ and $\U(\Sigma_2^-\cap\Delta_1)$ with respect to the elementary unipotents does not exceed $2\ell-2$ and $2\ell-4$, respectively.
-Summing up these upper bounds, we obtain
-$$(2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9 = 4|\Sigma_1| - 1.$$
-
-The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}
-\begin{cor}\label{cor:bass-kolster-iterated}
-Assume that $\Phi$ and $I$ satisfy one of the following assumptions
-\[\begin{array}{l@{\quad}l@{\quad}l}
-\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N'=3\left|\Phi^+\right|+2\ell - 5; \\
-\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N'=3\left|\Phi^+\right|+3\ell - 6; \\
-\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N'=4\left|\Phi^+\right| - 4.
-\end{array}\]
-
-Then every element of $\G(\Phi, R, I)$ can be decomposed into a product of one element of $\G(\langle\pm\alpha_\ell\rangle, R, I) \cong \SL(2, R, I)$ and at most $N'$ elements of $\mathcal{Z}(\Sigma_\ell)$:
-\end{cor}
-\begin{proof}
-The assertion can be obtained by iteratively applying (for a total of $\ell-1$ times) the decomposition of \cref{thm:BassKolster}.
-The improved estimate for $\Phi=\rA_\ell$ (resp.
-$\rC_\ell$) follows from the fact that it suffices to make only two (resp.
-three) additions to shorten the unimodular column in the first step of the proof of \cref{thm:BassKolster}.
-\end{proof}
-\begin{proof}[Proof of \cref{thm:SL2width}]
- As in the proof of the above corollary one has to iteratively apply \cref{thm:BassKolster}.
- To reduce the number of $\SL_2$-factors involved in the decompositoin one has to group into a single $\SL_2$-factor a pair of opposite root subgroups $X_{\alpha}(I)$, $X_{-\alpha}(I)$ (or $Z_{\pm\alpha}(I)$) appearing on each
- of the $3$ junctions between the positive and negative unipotent subgroups in the Bass---Kolster decomposition.
- Since a total of $\ell-1$ reductions are used, we get the estimate $N \leq N' - 3(\ell - 1) + 1$ and the assertion of \cref{thm:SL2width} follows.
-\end{proof}
-\begin{figure}[hb]\label{fig:bass-kolster}
-\[\begin{tikzcd}[row sep=tiny]
-\rD_4 \arrow[out=0, in=120]{rd}{\asr\leqslant3} & & & \\
-\rA_4 \arrow{r}{\sr\leqslant4} & \rA_3 \arrow{r}{\sr\leqslant3} & \rA_2 \arrow{r}{\sr\leqslant2} & \rA_1 \\
-\rC_4 \arrow{r}{\sr\leqslant7} & \rC_3 \arrow{r}{\sr\leqslant5} & \rC_2 \arrow[out=0, in=-120, swap]{ru}{\sr\leqslant3} \\
-\rB_4 \arrow{r}{\asr\leqslant3} & \rB_3 \arrow[out=0, in=-120, swap]{ru}{\asr\leqslant2} & &
-\end{tikzcd}\] \caption{Reductions used in the proof of \cref{cor:bass-kolster-iterated} and \cref{thm:SL2width}} \end{figure}
 
@@
 
-\begin{proof}[Proof of \cref{thm:DennisVaserstein}]
+\ThmDennisVaserstein
+\begin{proof} %[Proof of \cref{thm:DennisVaserstein}]
 Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$:
@@
   It remains to prove the inclusion $X_{1, 0}(R) \subset N_{rs}$.
-  Specializing identity~\eqref{rel:CCF}, we get \begin{equation*} \label{rel:CCF-specBC} x_{1, 0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1, -2}(-a b^2) \end{equation*}
+  By Chevalley commutator formula, we get
+\begin{equation*} \label{rel:CCF-specBC}
+x_{1, 0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1, -2}(-a b^2)
+\end{equation*}
   Since $X_{2, 0}(R)$ and $X_{1, -2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1, 0}(R) \subseteq N_{rs}$ follows.
@@
 
-In view of \cref{prop:Stepanov} to prove the theorem it suffices to show that $L_{rs}$ contains the generating set $\mathcal{Z}(\Sigma_s^-)$ of $\E(\Phi, R, I)$.
+In view of \cite[Theorem~3.4]{S} to prove the theorem it suffices to show that $L_{rs}$ contains the generating set $\mathcal{Z}(\Sigma_s^-)$ of $\E(\Phi, R, I)$.
 From the inclusion $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)}$ and \eqref{rel:NnormL} it follows that we only have to show that $\mathcal{X} \subseteq L_{rs}$.
@@
 The last inclusion follows from the same transitivity argument as above and the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
-For $\Phi=\rB_\ell$ one has to once again apply the Chevalley commutator formula~\eqref{rel:CCF}:
+For $\Phi=\rB_\ell$ one has to once again apply the Chevalley commutator formula:
 \[ X_{0, 1}(I) \subseteq X_{2, 1}(I) \cdot X_{2, 1}(I)^{x_{0, 2}(1)} \cdot X_{-2, 1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
@@
 
-Notice that by the definition of $\Gamma$ and \cref{lemma:Matsumoto} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$.
+Notice that by the definition of $\Gamma$ and Matsumoto lemma~\cite[Lemma~2.3]{Ma69} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$.
 Consequently, one has
@@
 Consequently, for every $g\in C$ one has
-\begin{multline*}
- \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq \EP_r(R, I) y^{-1} \cdot \U(\Sigma_r^-\cap \Sigma_s^-, I)^{y^{-1}} \cdot y g \subseteq \\
+\[
+ \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq \EP_r(R, I) y^{-1} \cdot \U(\Sigma_r^-\cap \Sigma_s^-, I)^{y^{-1}} \cdot y g
   \subseteq \EP_r(R, I) \cdot \U(\Sigma_r^-, I) \cdot y g.
-\end{multline*}
+\]
 Notice that the matrix entry $(yg)_{\varpi_s, \varpi_s}$ is invertible.
@@
 
+\subsection{Relative Gauss decomposition}\label{sec:gauss}
+The proof of the Gauss decomposition presented below is similar to the absolute case \cite[Theorem~5.1]{Sm12}.
+\begin{prop}\label{thm:Gauss}
+Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1$, $\Delta_\ell$ be
+two reductive subsystems of $\Phi$, corresponding to the endnodes of the Dynkin diagram of $\Phi$.
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit the triangular decomposition with $N$ triangular factors:
+\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I), \quad i=1, \ell. \]
+Then the ambient group $\E(\Phi, R, I)$ admits the decomposition with the same number of factors:
+\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm, I). \]
+\end{prop}
+\begin{proof}
+Denote by $Y$ the product of subgroups in the right-hand side of the above equality.
+To show that $Y=\E(\Phi, R, I)$ it suffices to check that
+\begin{enumerate}
+\item $Y$ is normalized by $\E(\Phi, R)$, i.\,e. $Y^{\E(\Phi, R)}\subseteq Y$;
+\item there exists a set $X$, generating $\E(\Phi, R, I)$ as a \emph{normal} subgroup of $\E(\Phi, R)$ such that $XY\subseteq Y$.
+\end{enumerate}
+To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for any $\alpha\in \pm \Pi$, $\xi\in R$.
+Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or for $i=\ell$, and we can expand $Y$ as follows:
+\[ Y=\Hh(\Phi, R, I) \cdot \U(\Delta_i^+, I) \cdot \ldots \cdot \U^\pm(\Delta_i, I) \cdot \U(\Sigma_i^+, I) \cdot \ldots \cdot \U(\Sigma_i^\pm, I). \]
+For every  $h \in \Hh(\Phi, R, I)$ one has for some $s\in I$
+\[ x_\alpha(\xi)\cdot h = h\cdot x_\alpha((1+s)\xi)=h\cdot x_\alpha(\xi)\, x_\alpha(s\xi). \]
+
+Therefore by the assumption of the theorem
+\begin{multline*}
+Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi, R, I) \cdot x_\alpha(-\xi) \cdot X_{\alpha}(I) \cdot \E(\Delta_i, R, I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) =\\
+= \Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) = Y.
+\end{multline*}
+
+Now set $X=\left\{x_\alpha(\xi)\ \middle|\ \alpha\in\Pi, \ \xi\in I \right\}$. 
+Every root is a conjugate of some fundamental root under the action of $W(\Phi)$.
+Since $\E(\Phi, R)$ contains the normalizer of the torus, the set $X^{\E(\Phi, R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi), \  \alpha\in\Phi, \ \xi\in I \rangle$.
+Finally, the inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi, R, I)$ normalizes every root subgroup $X_\alpha(I)$.
+\end{proof}
+\begin{thm}\label{thm:srRI1}
+Let $\Phi$ be a root system, let $I$ be an ideal of an arbitrary commutative ring $R$, and assume that $\sr(I)=1$.
+Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits the following decomposition:
+\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi, I). \]
+\end{thm}
+\begin{proof} %[Proof of \cref{thm:srRI1}]
+In view of \cref{thm:Gauss} it suffices to prove that the Gauss decomposition of length $3$ holds for $\Phi=\rA_1$.
+Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}$ be an element of $\SL(2, R, I)$.
+The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
+Multiplying $A$ on the left by $x_{12}(z)$, we get a matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with the invertible  element $a'$ in the top-left corner.
+After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
+Thus we have obtained the relative Gauss decomposition of $A$
+\begin{equation*}
+A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
+\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
+\cdot x_{12}(b'/a')=x_{12}(-z)\cdot
+\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
+\cdot x_{21}(y) \cdot x_{12}(b'/a'), 
+\end{equation*}
+where $\varepsilon\in 1+I$ and $y\in I$. \end{proof}
+
+\subsection{Relative Bass---Kolster decompositions}\label{sec:bass-kolster}
+The next theorem is a relative version of the so-called Bass---Kolster decomposition \cite[Theorem~2.1]{St78}.
+\begin{thm}\label{thm:BassKolster}
+Let $\Phi$ be a classical root system of rank $\ell\geqslant2$, let $R$ be an arbitrary commutative ring and $I$ be its ideal, satisfying one of the following assumptions:
+\[\begin{array}{l@{\quad}l@{\quad}l@{\quad}c}
+\Phi = \rA_\ell, \ \ell\geqslant 2, & \sr(I) \leqslant \ell; \\
+\Phi = \rC_\ell, \ \ell\geqslant 2, & \sr(I) \leqslant 2\ell-1; \\
+\Phi = \rB_\ell, \rD_\ell, \ \ell\geqslant 3, & \asr(I) \leqslant \ell-1.
+\end{array}\]
+Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of the Bass---Kolster decomposition:
+\[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]
+where $Z = Z_{\alpha_\mathrm{max}}(I)=\left\{z_{-\alpha_\mathrm{max}}(r, 1)\ \middle|\ r\in I \right\}$.
+\end{thm}
+\begin{proof}
+
+Let $g$ be an element of $\G(\Phi, R, I)$. Set $v=g \cdot v^+\in\Ums(n, I)$. 
+Notice that in each case it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that 
+\begin{equation} \label{eq1} (g'\cdot v^+)_{1} = 1 + s \text{ and } (g'\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}} = s\ \text{for some}\ s\in I. \end{equation}
+Indeed, set $g'' = z_{-\alpha\ssub{max}}(-s, 1) \cdot g'$.
+Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}=0$ and the conclusion of the theorem follows from \cref{lemma:Chevalley-Matsumoto}.
+
+\textsc{Case $\Phi=\rA_\ell$, $n=\ell + 1$.}
+Since $\sr(I)\leqslant\ell$, one can find $a_1, \ldots, a_\ell\in I$ such that $(v_1+a_1v_{\ell+1}, \ldots, v_\ell+a_\ell v_{\ell+1})^t=(v'_1, \ldots, v'_\ell)^t$ is $I$-unimodular.
+Then there are $b_1, \ldots, b_\ell\in I$ such that $b_1v'_1+\ldots b_\ell v'_\ell=v'-1\in I$. 
+Thus the vector \[ v'' = \prod_{i=1}^\ell x_{\ell+1, i}(b_i) \cdot \prod_{i=1}^\ell x_{i, \ell+1}(a_i) \cdot v \]
+satisfies the equalities~\eqref{eq1}.
+
+\textsc{Case $\Phi=\rC_\ell$, $n=2\ell$.}
+Notice that the column $(v_1, \ldots, v_{-2}, v_{-1}^2)^t$ is also $I$-unimodular.
+Applying the assumption $\sr(I)\leqslant 2\ell-1$, we find $c_1, c_2, \ldots, c_{-2} \in I \cdot v_{-1}$ such that upper $2\ell -1$ components of $v'=(v_1 + c_1 v_{-1}, \ldots, v_{-2} + c_{-2}v_{-1}, v_{-1})^t$ form an $I$-unimodular column.
+By the choice of $c_i$ we can find suitable $d\in I$ such that $h_1 \cdot v = v'$ for
+\[ h_1 = x_{1, -1}(c_1 + d) \cdot \prod_{i=2}^{-2} x_{i, -1}(c_i) \in \U(\Sigma_1^+, I). \]
+We can find $f_1, f_2, \ldots, f_{-2} \in R$ such that $f_1v'_1+\sum_{i=2}^{-2} f_i v'_i = 1$.
+Set $\xi = v''_1-v''_{-1}-1 \in I$, 
+\[ h_2 = x_{-1, 1}\biggl(\xi f_1 + \sum_{i=2}^\ell v_1' \xi^2 f_i f_{-i}\biggr) \cdot \prod_{i=2}^{-2} x_{-1, i}(\xi f_i) \in \U(\Sigma_1^-, I). \]
+Direct computation shows that the vector $v'' = h_2 \cdot v'$ satisfies equalities~\eqref{eq1}.
+
+\textsc{Case $\Phi=\rD_\ell$, $n= 2\ell$.} 
+By \cref{item:asrUnipD} we can find $h_1\in \U(\Sigma^+_\ell, I)$ such that the upper half $v'_+$ of $v'=h_1 \cdot v$ is $I$-unimodular.
+Since $\sr(I)\leqslant \ell-1$, we can find $c_1$, $c_3, \ldots c_\ell \in I$ such that $(v''_1, v''_3, \ldots, v''_\ell) \in \Ums(\ell-1, I)$, where
+\[ v''=h_2 \cdot x_{1, 2}(c_1) \cdot v', \quad h_2=\prod_{i=3}^\ell x_{i, 2}(c_i). \]
+We can find $f_1, f_3, \ldots, f_\ell \in R$ such that $f_1v''_1+\sum_{i=3}^\ell f_i v''_{i} = 1$.
+As before, set
+\[ \xi = v''_1-v''_{-2}-1 \in I, \quad h_3 = x_{-2, 1}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-2, i}(\xi f_i), \quad v'''=h_3 \cdot v''. \]
+Clearly, $t_{1, 2}(c_1) \cdot h_1 \in \U(\Phi^+, I)$, $ h_3 \cdot h_2 \in \U(\Phi^-, I)$ and $v'''$ satisfies~\eqref{eq1}.
+
+\textsc{Case $\Phi=\rB_\ell$, $n=2\ell+1$.} Subdivide $v\in \Ums(2\ell+1, I)$ as $v=(v_+, v_0, v_-)\in R^\ell\times R\times R^\ell$.
+Denote by $J\leqslant I$ the ideal spanned by the components of $v_-$.
+Since $\sr(I/J)\leqslant \ell$, we can find $c_1, \dots, c_\ell\in I$ such that for $v' = h \cdot v$, $h = \prod_{i=1}^\ell x_{i, 0}(c_i) \in \U(\Phi^+, I)$
+one has $\bar{v'}_+=(\bar{v'_1}, \ldots, \bar{v'_\ell}) \in \Ums(\ell, I/J)$ and, therefore, $(v'_+, v'_-) \in \Ums(2\ell, I)$.
+Now the proof can be finished by repeating the argument for the case $\Phi=\rD_\ell$ (applied to the subset of long roots of $\rB_\ell$).
+\end{proof}
+
+It is easy to see that the proof of the above theorem is effective and gives an estimate of the total number of elementary root unipotents involved in the decomposition.
+\begin{cor}\label{cor:bass-kolster-count}
+In the assumptions and notation of \cref{thm:BassKolster} every element of $\G(\Phi, R, I)$ 
+can be factored into a product of one element of $\G(\Delta_1, R, I)$, one element of $Z$ and at most $4|\Sigma_1|-1$ elements of $\mathcal{X}$.
+\end{cor}
+\begin{proof}
+The assertion can be obtained by a careful analysis of the proof of the previous theorem.
+Cases $\Phi=\rA_\ell, \rC_\ell$ are immediate.
+In the case $\Phi=\rD_\ell$ from the proof of \cref{thm:BassKolster} one obtains that
+\begin{equation*} \G(\Phi, R, I) =  \U(\Sigma_\ell^+, I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1, I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z \cdot \U(\Sigma_1^-, I) \cdot \U(\Sigma_1^+, I) \cdot \G(\Delta_1, R, I).
+\end{equation*}
+We can present an element $g$ of $\U(\Sigma_\ell^+, I)$ as a product of $g_1 \in \U(\Sigma_{1, 2}^+ \cap \Sigma_\ell^+)$ and $g_2\in \U(\Delta_{1, 2}\cap \Sigma_\ell^+)$.
+An examination of the extended Dynkin diagram of $\rD_\ell$ shows that $g_2$ either centralizes or normalizes all factors of the above decomposition (except the last one)
+and therefore can be moved to the right until it is consumed by $\G(\Delta_1, R, I)$.
+On the other hand, $g_1$ is a product of at most $2\ell-3$ elementary unipotents, while the width of $\U(\Sigma_1^\pm, I)$ and $\U(\Sigma_2^-\cap\Delta_1)$ with respect to the elementary unipotents does not exceed $2\ell-2$ and $2\ell-4$, respectively.
+Summing up these upper bounds, we obtain
+$$(2\ell-3) + 1 + (2\ell - 4) + 1 + 2\cdot (2\ell - 2) = 8\ell - 9 = 4|\Sigma_1| - 1.$$
+
+The estimate in the case $\Phi=\rB_\ell$ can be obtained in a similar way. \end{proof}
+\begin{cor}\label{cor:bass-kolster-iterated}
+Assume that $\Phi$ and $I$ satisfy one of the following assumptions
+\[\begin{array}{l@{\quad}l@{\quad}l}
+\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N'=3\left|\Phi^+\right|+2\ell - 5; \\
+\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N'=3\left|\Phi^+\right|+3\ell - 6; \\
+\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N'=4\left|\Phi^+\right| - 4.
+\end{array}\]
+
+Then every element of $\G(\Phi, R, I)$ can be decomposed into a product of one element of $\G(\langle\pm\alpha_\ell\rangle, R, I) \cong \SL(2, R, I)$ and at most $N'$ elements of $\mathcal{Z}(\Sigma_\ell)$:
+\end{cor}
+\begin{proof}
+The assertion can be obtained by iteratively applying (for a total of $\ell-1$ times) the decomposition of \cref{thm:BassKolster}.
+The improved estimate for $\Phi=\rA_\ell$ (resp.
+$\rC_\ell$) follows from the fact that it suffices to make only two (resp.
+three) additions to shorten the unimodular column in the first step of the proof of \cref{thm:BassKolster}.
+\end{proof}
+
+\begin{figure}[hb]\label{fig:bass-kolster}
+\[\begin{tikzcd}[row sep=tiny]
+\rD_4 \arrow[out=0, in=120]{rd}{\asr\leqslant3} & & & \\
+\rA_4 \arrow{r}{\sr\leqslant4} & \rA_3 \arrow{r}{\sr\leqslant3} & \rA_2 \arrow{r}{\sr\leqslant2} & \rA_1 \\
+\rC_4 \arrow{r}{\sr\leqslant7} & \rC_3 \arrow{r}{\sr\leqslant5} & \rC_2 \arrow[out=0, in=-120, swap]{ru}{\sr\leqslant3} \\
+\rB_4 \arrow{r}{\asr\leqslant3} & \rB_3 \arrow[out=0, in=-120, swap]{ru}{\asr\leqslant2} & &
+\end{tikzcd}\] \caption{Reductions used in the proof of \cref{cor:bass-kolster-iterated} and \cref{thm:SL2width}} \end{figure}
+
 \section{Applications} \label{sec:applications}
+\subsection{Subsystem factorizations}\label{sec:subsysfact}
+\begin{thm}\label{thm:SL2width}
+Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system satisfying one of the following assumptions.
+\[\begin{array}{l@{\quad}l@{\quad}l}
+\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right| - \rk(\Phi) - 1; \\
+\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right| - 2; \\
+\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right| - 3\rk(\Phi).
+\end{array}\]
+Then the principal congruence subgroup $\G(\Phi, R, I)$ can be presented as a product of at most $N$ copies of its (regularly embedded) subgroups isomorphic to $\SL(2, R, I)$.
+\end{thm}
+\begin{proof} %[Proof of \cref{thm:SL2width}]
+ As in the proof of \cref{cor:bass-kolster-iterated}, one has to iteratively apply \cref{thm:BassKolster}.
+ To reduce the number of $\SL_2$-factors involved in the decompositoin one has to group into a single $\SL_2$-factor a pair of opposite root subgroups $X_{\alpha}(I)$, $X_{-\alpha}(I)$ (or $Z_{\pm\alpha}(I)$) appearing on each
+ of the $3$ junctions between the positive and negative unipotent subgroups in the Bass---Kolster decomposition.
+ Since a total of $\ell-1$ reductions are used, we get the estimate $N \leq N' - 3(\ell - 1) + 1$ and the assertion of \cref{thm:SL2width} follows.
+\end{proof}
+
+Consider the decreasing chain $\Phi_k$, $k=1, \ldots, \lfloor \ell/2 \rfloor$ of root subsystems of $\Phi=\rD_\ell$ defined as follows.
+If $2k \neq \ell$, let $\Phi_k$ be the subsystem of $\Phi$, spanned by the fundamental roots $\alpha_{2k-1}, \ldots, \alpha_\ell$.
+Clearly, such $\Phi_k$ has type $\rD_{\ell-2k+2}$. 
+In the remaining case $2k = \ell$ set $\Phi_k = \langle \alpha_\ell \rangle \cong \rA_1$.
+Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\,e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1, \ldots, \lfloor \ell/2 \rfloor$.
+Denote by $B$ the set of all $\beta_k$. From the definition it is clear that the elements of $B$ are mutually orthogonal to each other.
+The roots $\beta_k$ can also be defined by explicit formulae:
+\begin{align*}
+ \beta_k =  \alpha_{2k-1} + 2\alpha_{2k}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell, & \text{ for } k=1, \ldots, \lfloor\ell/2\rfloor-1, \\
+ \beta_{\lfloor\ell/2\rfloor} = \alpha_{\ell-2}+\alpha_{\ell-1}+\alpha_\ell, & \text{ if $\ell$ is odd, } \\
+ \beta_{\lfloor\ell/2\rfloor} = \alpha_\ell, & \text{ if $\ell$ is even.}
+\end{align*}
+
+\begin{lemma}\label{lemma:nikolov-weyl} There exists an element $w\in W(\rD_\ell)$ such that $w(B) \subseteq \Delta_\ell^+$. \end{lemma}
+\begin{proof}
+\textsc{Case $\ell=4$.} Set $w = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}} \circ \sigma_{\alpha\ssub{2} + \alpha\ssub{4}}$.
+Straightforward computation shows that 
+\begin{align*}
+& w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \\
+& w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1,
+\end{align*}
+which implies the assertion of the lemma.
+
+\textsc{Case $\ell \geq 5$.}
+Recall from \cite[Table~9]{Dy72} that for odd (resp. even) $\ell$ all maximal subsystems of type $\rA_1+\ldots+\rA_1+\rD_3$
+(resp. $\rA_1+\ldots+\rA_1+\rD_4$) are conjugate under the action of $W(\Phi)$. Consequently, we can find $w\in W(\Phi)$
+such that $w(\beta_k) = \alpha_{2k-1}$ for $k < \lfloor\ell/2\rfloor$ (resp. $k < \lfloor\ell/2\rfloor-1$). 
+Now using transitivity of the action of $W(\rD_3)$ on the roots (resp. by the same argument as in the case $\ell=4$) we can move the remaining root $\beta_{\lfloor\ell/2\rfloor}$ 
+(resp. the remaining $2$ roots $\beta_{\lfloor\ell/2\rfloor-1}$, $\beta_{\lfloor\ell/2\rfloor}$) to
+$\alpha_{\ell-1}$ (resp. to $\alpha_{\ell-3}$, $\alpha_{\ell-1}$) while fixing all the other $\beta_k$. \end{proof}
+
+The following lemma is an analogue of Proposition~1 of~\cite{Nik07}.
+\begin{lemma}\label{lemma:nikolov-type-dl}
+Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $I$ be an ideal of a  commutative ring $R$.
+There exist an element $y\in\E(\Phi, R)$ and an element $w\in\widetilde{W}(\Phi)$ such that
+\[ \U(\Sigma_\ell^+, I)\subset[\U(\Delta_\ell^-, I), y]\cdot{}^w\!\U(\Delta_\ell^+, I). \]
+\end{lemma}
+\begin{proof}
+Since $\U(\Sigma_\ell^+, I)$ is abelian, we can decompose it as $\U(\Sigma_\ell^+, I)=\U(\Sigma_\ell^+\setminus B, I) \cdot \U(B, I)$. 
+Set $y=\prod_{\beta\in B}x_\beta(1)$. 
+We will now show by induction on $\ell$ that 
+\begin{equation}\label{eq:ind-stat} \U(\Sigma_\ell^+\setminus B, I)\subset[\U(\Delta_\ell^-, I), y]\cdot\U(B, I). \end{equation}
+The induction base in the cases $\ell=2, 3$ is trivial.
+
+Notice that $\beta_1$ is the only root of $\Phi$ satisfying $m_2(\beta_1)=2$, therefore the commutator formula~\eqref{rel:CCF} implies
+\[ \bigl[\U(\Delta_2^-, I), x_{\beta_1}(1)\bigr]=1. \]
+There is no root of the form $\gamma=\alpha+\beta$ with $\alpha\in\Sigma_2^-\cap\Delta_\ell$ and $\beta\in B\setminus\{\beta_1\}$, because such a root $\gamma$ must satisfy $m_2(\gamma)=-1$ and $m_\ell(\gamma)=1$.
+Thus the commutator formula gives
+\[\Bigl[\U(\Sigma_2^-\cap\Delta_\ell, I), \prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
+Since $B\setminus\{\beta_1\}\subset\Sigma_\ell^+\cap\Delta_2$, the above two identities imply
+\[
+\Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2, \ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr]
+\equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell^+\cap\Delta_2, I).
+\]
+Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, where $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $w\in\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$.
+Using the identity
+\begin{equation}\label{eq:comm-ab-c}
+[ab, c]={}^a[b, c]\cdot[a, c], 
+\end{equation}
+we can rewrite
+\[ [vw, x_{\beta_1}(1)] = {}^v[w, x_{\beta_1}(1)]\cdot[v, x_{\beta_1}(1)].  \]
+Since $\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$ are abelian, it is easy to see that
+\[ [v, x_{\beta_1}(1)]\in\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I), \quad [w, x_{\beta_1}(1)]\in\U((\Sigma_1^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}, I). \]
+Every element of $\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I)$ (resp.
+$\U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I)$) can be expressed as such a commutator for a suitable choice of $v$ (resp.
+$w$).
+Indeed, set $v=x_\gamma(\xi_\gamma)\cdot v'$, $\gamma=-\alpha_1-\alpha_2$, $v' \in \U(\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell \setminus \{\gamma\}, I)$.
+Using relation \eqref{eq:comm-ab-c} and the fact that $X_\gamma(I)$ commutes with $\U(\Sigma_2^+\cap\Delta_1, I)$ we get that:
+\begin{multline*}
+[v, x_{\beta_1}(1)] = [x_\gamma(\xi_\gamma)\cdot v', x_{\beta_1}(1)] = {}^{x_\gamma(\xi_\alpha)}[v', x_{\beta_1}(1)] \cdot [x_\gamma(\xi_\gamma), x_{\beta_1}(1)] = \\
+= [v', x_{\beta_1}(1)]\cdot x_{\beta_1-\alpha_1-\alpha_2}(\xi_\gamma) = \ldots = \prod_{\mathclap{\alpha\in\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell}} x_{\beta_1+\alpha}(\xi_\alpha).
+ \end{multline*}
+It remains to note that $\Sigma_2^+ \cap \Sigma_\ell^+ \cap \Delta_1 = \beta_1 + \Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell$. The same argument works for $[w, x_{\beta_1}(1)]$.
+Direct calculation using the commutator formula shows that
+\[ {}^v\!\U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I) \equiv \U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I). \]
+Summing up the above arguments, we get that
+\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2, \ell}^-, I), y] \equiv \U((\Sigma_{1, 2}^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I), \]
+hence the inclusion~\eqref{eq:ind-stat} follows from the induction hypothesis (applied to $\Delta_{1, 2} \cong \rD_{\ell-2}$).
+
+Finally, we have found $a\in\U(\Sigma_\ell^+\setminus B, I)$ and $b\in\U(\Delta_\ell^-, I)$
+such that $$a\in[b, y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-, I), y]\cdot\U(B, I).$$
+Now the assertion of the lemma follows from~\cref{lemma:nikolov-weyl}.
+\end{proof}
+
+\ThmSpinSLnProd
+\begin{proof} %[Proof of \cref{thm:spin-sln-prod}]
+Set $L = \E(\Delta_\ell, R, I) \leq \E(\rD_\ell, R, I)$ and denote by $\sigma$ the automorphism of $\G(\rD_\ell, R)$ induced by the 
+diagram automorphism of $\rD_\ell$ swapping $\alpha_\ell$ and $\alpha_{\ell-1}$.
+By \cref{thm:DennisVaserstein} one has
+\begin{align*}
+\E(\rD_\ell, R, I) & = \EP_{\ell}(R, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot\EP_{\ell-1}(R, I) = \\
+& = L \cdot\U(\Sigma_\ell^+, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot \big(L \cdot \U(\Sigma_\ell^+, I) \big)^\sigma\!.
+\end{align*}  
+Now using \cref{lemma:nikolov-type-dl}, one can find $y_1, y_2\in\G(\rD_\ell, R)$ and $w_1, w_2\in\widetilde{W}(\rD_\ell)$ such that
+\begin{align*} & L \cdot \U(\Sigma_\ell^+, I) \subset L \cdot \U(\Delta_{\ell-1}^-, I) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-, I) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+, I), \\
+& \U(\Sigma_{\ell-1}^-\cap\Sigma_\ell^-, I) \subset \U(\Delta_\ell^+, I) \cdot {}^{y_2}\!\U(\Delta_\ell^+, I) \cdot {}^{w_2}\!\U(\Delta_\ell^-, I). \end{align*} 
+Thus $\E(\rD_\ell, R, I)$ is a product of at most $9$ subgroups isomorphic to $\E(\rA_{\ell-1}, R, I)$. \end{proof}
+
 \subsection{Bounded generation}\label{sec:boundgen}
@@
 \end{proof}
-
-\begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.
-The the first and the third assertions follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}
-
-\subsection{Subsystem factorizations}\label{sec:subsysfact}
-Consider the decreasing chain $\Phi_k$, $k=1, \ldots, \lfloor \ell/2 \rfloor$ of root subsystems of $\Phi=\rD_\ell$ defined as follows.
-If $2k \neq \ell$, let $\Phi_k$ be the subsystem of $\Phi$, spanned by the fundamental roots $\alpha_{2k-1}, \ldots, \alpha_\ell$.
-Clearly, such $\Phi_k$ has type $\rD_{\ell-2k+2}$. 
-In the remaining case $2k = \ell$ set $\Phi_k = \langle \alpha_\ell \rangle \cong \rA_1$.
-Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\,e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1, \ldots, \lfloor \ell/2 \rfloor$.
-Denote by $B$ the set of all $\beta_k$. From the definition it is clear that the elements of $B$ are mutually orthogonal to each other.
-The roots $\beta_k$ can also be defined by explicit formulae:
-\begin{align*}
- \beta_k =  \alpha_{2k-1} + 2\alpha_{2k}+ \ldots + 2\alpha_{\ell-2} + \alpha_{\ell-1} + \alpha_\ell, & \text{ for } k=1, \ldots, \lfloor\ell/2\rfloor-1, \\
- \beta_{\lfloor\ell/2\rfloor} = \alpha_{\ell-2}+\alpha_{\ell-1}+\alpha_\ell, & \text{ if $\ell$ is odd, } \\
- \beta_{\lfloor\ell/2\rfloor} = \alpha_\ell, & \text{ if $\ell$ is even.}
-\end{align*}
-
-\begin{lemma}\label{lemma:nikolov-weyl} There exists an element $w\in W(\rD_\ell)$ such that $w(B) \subseteq \Delta_\ell^+$. \end{lemma}
-\begin{proof}
-\textsc{Case $\ell=4$.} Set $w = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}} \circ \sigma_{\alpha\ssub{2} + \alpha\ssub{4}}$.
-Straightforward computation shows that 
-\begin{align*}
-& w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \\
-& w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1,
-\end{align*}
-which implies the assertion of the lemma.
-
-\textsc{Case $\ell \geq 5$.}
-Recall from \cite[Table~9]{Dy72} that for odd (resp. even) $\ell$ all maximal subsystems of type $\rA_1+\ldots+\rA_1+\rD_3$
-(resp. $\rA_1+\ldots+\rA_1+\rD_4$) are conjugate under the action of $W(\Phi)$. Consequently, we can find $w\in W(\Phi)$
-such that $w(\beta_k) = \alpha_{2k-1}$ for $k < \lfloor\ell/2\rfloor$ (resp. $k < \lfloor\ell/2\rfloor-1$). 
-Now using transitivity of the action of $W(\rD_3)$ on the roots (resp. by the same argument as in the case $\ell=4$) we can move the remaining root $\beta_{\lfloor\ell/2\rfloor}$ 
-(resp. the remaining $2$ roots $\beta_{\lfloor\ell/2\rfloor-1}$, $\beta_{\lfloor\ell/2\rfloor}$) to
-$\alpha_{\ell-1}$ (resp. to $\alpha_{\ell-3}$, $\alpha_{\ell-1}$) while fixing all the other $\beta_k$. \end{proof}
-
-The following lemma is an analogue of Proposition~1 of~\cite{Nik07}.
-\begin{lemma}\label{lemma:nikolov-type-dl}
-Let $\Phi=\rD_\ell$, $\ell\geq 2$ and let $I$ be an ideal of a  commutative ring $R$.
-There exist an element $y\in\E(\Phi, R)$ and an element $w\in\widetilde{W}(\Phi)$ such that
-\[ \U(\Sigma_\ell^+, I)\subset[\U(\Delta_\ell^-, I), y]\cdot{}^w\!\U(\Delta_\ell^+, I). \]
-\end{lemma}
-\begin{proof}
-Since $\U(\Sigma_\ell^+, I)$ is abelian, we can decompose it as $\U(\Sigma_\ell^+, I)=\U(\Sigma_\ell^+\setminus B, I) \cdot \U(B, I)$. 
-Set $y=\prod_{\beta\in B}x_\beta(1)$. 
-We will now show by induction on $\ell$ that 
-\begin{equation}\label{eq:ind-stat} \U(\Sigma_\ell^+\setminus B, I)\subset[\U(\Delta_\ell^-, I), y]\cdot\U(B, I). \end{equation}
-The induction base in the cases $\ell=2, 3$ is trivial.
-
-Notice that $\beta_1$ is the only root of $\Phi$ satisfying $m_2(\beta_1)=2$, therefore the commutator formula~\eqref{rel:CCF} implies
-\[ \bigl[\U(\Delta_2^-, I), x_{\beta_1}(1)\bigr]=1. \]
-There is no root of the form $\gamma=\alpha+\beta$ with $\alpha\in\Sigma_2^-\cap\Delta_\ell$ and $\beta\in B\setminus\{\beta_1\}$, because such a root $\gamma$ must satisfy $m_2(\gamma)=-1$ and $m_\ell(\gamma)=1$.
-Thus~\eqref{rel:CCF} gives
-\[\Bigl[\U(\Sigma_2^-\cap\Delta_\ell, I), \prod_{i\neq1}x_{\beta_i}(1)\Bigr]=1. \]
-Since $B\setminus\{\beta_1\}\subset\Sigma_\ell^+\cap\Delta_2$, the above two identities imply
-\begin{multline*}
-\Bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I)\cdot\U(\Delta_{2, \ell}^-, I), x_{\beta_1}(1)\cdot\prod_{i\neq1}x_{\beta_i}(1) \Bigr] \equiv \\
-\equiv \bigl[ \U(\Sigma_2^-\cap\Delta_\ell, I), x_{\beta_1}(1) \bigr] \bmod \U(\Sigma_\ell^+\cap\Delta_2, I).
-\end{multline*}
-Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, where $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $w\in\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$.
-Using the identity
-\begin{equation}\label{eq:comm-ab-c}
-[ab, c]={}^a[b, c]\cdot[a, c], 
-\end{equation}
-we can rewrite
-\[ [vw, x_{\beta_1}(1)] = {}^v[w, x_{\beta_1}(1)]\cdot[v, x_{\beta_1}(1)].  \]
-Since $\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$ are abelian, it is easy to see that
-\[ [v, x_{\beta_1}(1)]\in\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I), \quad [w, x_{\beta_1}(1)]\in\U((\Sigma_1^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}, I). \]
-Every element of $\U(\Sigma_2^+\cap\Sigma_\ell^+\cap\Delta_1, I)$ (resp.
-$\U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I)$) can be expressed as such a commutator for a suitable choice of $v$ (resp.
-$w$).
-Indeed, set $v=x_\gamma(\xi_\gamma)\cdot v'$, $\gamma=-\alpha_1-\alpha_2$, $v' \in \U(\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell \setminus \{\gamma\}, I)$.
-Using relation \eqref{eq:comm-ab-c} and the fact that $X_\gamma(I)$ commutes with $\U(\Sigma_2^+\cap\Delta_1, I)$ we get that:
-\begin{multline*}
-[v, x_{\beta_1}(1)] = [x_\gamma(\xi_\gamma)\cdot v', x_{\beta_1}(1)] = {}^{x_\gamma(\xi_\alpha)}[v', x_{\beta_1}(1)] \cdot [x_\gamma(\xi_\gamma), x_{\beta_1}(1)] = \\
-= [v', x_{\beta_1}(1)]\cdot x_{\beta_1-\alpha_1-\alpha_2}(\xi_\gamma) = \ldots = \prod_{\mathclap{\alpha\in\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell}} x_{\beta_1+\alpha}(\xi_\alpha).
- \end{multline*}
-It remains to note that $\Sigma_2^+ \cap \Sigma_\ell^+ \cap \Delta_1 = \beta_1 + \Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell$. The same argument works for $[w, x_{\beta_1}(1)]$.
-Direct calculation using the commutator formula shows that
-\[ {}^v\!\U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I) \equiv \U(\Sigma_1^+\cap\Sigma_\ell^+\setminus\{\beta_1\}, I) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I). \]
-Summing up the above arguments, we get that
-\[ [\U(\Sigma_2^-, I)\cdot\U(\Delta_{2, \ell}^-, I), y] \equiv \U((\Sigma_{1, 2}^+\cap\Sigma_\ell^+)\setminus\{\beta_1\}) \bmod \U(\Sigma_\ell^+\cap\Delta_2, I), \]
-hence the inclusion~\eqref{eq:ind-stat} follows from the induction hypothesis (applied to $\Delta_{1, 2} \cong \rD_{\ell-2}$).
-
-Finally, we have found $a\in\U(\Sigma_\ell^+\setminus B, I)$ and $b\in\U(\Delta_\ell^-, I)$
-such that $$a\in[b, y]\cdot\prod_{\beta\in B}X_\beta\subset[\U(\Delta_\ell^-, I), y]\cdot\U(B, I).$$
-Now the assertion of the lemma follows from~\cref{lemma:nikolov-weyl}.
-\end{proof}
-
-\begin{proof}[Proof of \cref{thm:spin-sln-prod}]
-Set $L = \E(\Delta_\ell, R, I) \leq \E(\rD_\ell, R, I)$ and denote by $\sigma$ the automorphism of $\G(\rD_\ell, R)$ induced by the 
-diagram automorphism of $\rD_\ell$ swapping $\alpha_\ell$ and $\alpha_{\ell-1}$.
-By \cref{thm:DennisVaserstein} one has
-\begin{multline*}
-\E(\rD_\ell, R, I) = \EP_{\ell}(R, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot\EP_{\ell-1}(R, I) = \\
-= L \cdot\U(\Sigma_\ell^+, I)\cdot\U(\Sigma_{\ell-1}^- \cap \Sigma_{\ell}^-, I)\cdot \big(L \cdot \U(\Sigma_\ell^+, I) \big)^\sigma.
-\end{multline*}  
-Now using \cref{lemma:nikolov-type-dl}, one can find $y_1, y_2\in\G(\rD_\ell, R)$ and $w_1, w_2\in\widetilde{W}(\rD_\ell)$ such that
-\begin{align*} & L \cdot \U(\Sigma_\ell^+, I) \subset L \cdot \U(\Delta_{\ell-1}^-, I) \cdot {}^{y_1}\!\U(\Delta_{\ell-1}^-, I) \cdot {}^{w_1}\!\U(\Delta_{\ell-1}^+, I), \\
-& \U(\Sigma_{\ell-1}^-\cap\Sigma_\ell^-, I) \subset \U(\Delta_\ell^+, I) \cdot {}^{y_2}\!\U(\Delta_\ell^+, I) \cdot {}^{w_2}\!\U(\Delta_\ell^-, I). \end{align*} 
-Thus $\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of $L \cong \E(\rA_{\ell-1}, R, I)$. \end{proof}
+The above lemmas together with \cref{cor:bass-kolster-count,thm:Gauss} give the following
+\begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.
+\begin{thmlist}
+\item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
+$W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite;
+\item If $\sr(I) = 1$ and $\Phi$ is an arbitrary irreducible root system, then 
+\[W(\E(\Phi, R, I), \mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1;\]
+\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime number $p$, then under the assumption of the Generalized Riemann Hypothesis one has
+\begin{alignat*}{2}
+& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1 & \text{ if } \Phi=\rA_\ell, \rC_\ell, \\
+& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell.
+\end{alignat*}
+\end{thmlist}
+\end{thm}
+%\begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.
+%The the first and the third assertions follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}
 

### 2016-09-01 paper.tex
Abstract small fix

@@
 \begin{abstract} 
-We formulate and prove relative versions of several classical decompositions known in the theory of Chevalley groups over commutative rings.
+We formulate and prove relative versions of several classical ``parabolic'' decompositions known in the theory of Chevalley groups over commutative rings.
 We apply them to construct new factorizations in terms of $\SL_2$ and $\SL_n$ subgroups and to obtain upper estimates on the width of principal congruence subgroups in terms of Tits---Vaserstein generators.

### 2017-02-07 paper.tex
Minor fixes

@@
 
-Let us now fix the notations used in the paper.
+\section{Preliminaries}\label{sec:preliminaries}
+%Let us now fix the notations used in the paper.
 Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of fundamental roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
@@
 
-For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ with respect to $\Pi$, i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
+For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ in $\Pi$,
+ i.\,e. $\alpha = \sum_{i=1}^n m_i(\alpha) \alpha_i$.
 
@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
-We tend to omit curly braces in the above notations when $J$ is a one or two element set, e.\,g., $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
+We omit curly braces in the above notations when $J$ is a one or two element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
 
 \begin{lemma}[{\cite[Lemma~1]{ABS}}]\label{lemma:abs}
-Let $\alpha, \beta \in \Sigma^\pm_J$ be two roots having the same length such that $\shape(J, \alpha)=\shape(J, \beta)\neq 0$.
+Let $\alpha, \beta \in \Sigma^\pm_J$ be a pair of roots having the same length such that $\shape(J, \alpha)=\shape(J, \beta)\neq 0$.
 Then $\alpha$ and $\beta$ are conjugate under the action of $W(\Delta_J)$.
@@
 
-Let $\G(\Phi, R)$ be the simply-connected Chevalley group of type $\Phi$ over an arbitrary commutative ring $R$ and let $\E(\Phi, R)$ be its elementary subgroup, generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$, see~\cite{VP, St78, S}.
-For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{relative Chevalley group} (alias the \emph{principal congruence subgroup}) of level $I$.
+Let $\G(\Phi, R)$ be the simply-connected Chevalley group of type $\Phi$ over an arbitrary commutative ring $R$ and let $\E(\Phi, R)$ be its elementary subgroup,
+i.\,e. the subgroup generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$, see~\cite{VP, St78, S}.
+For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{principal congruence subgroup} of level $I$.
 
@@
 %\end{thm}
-%In the special case when $I$ is contained in the Jacobson radical of $R$, \cref{thm:srRI1} boils down to~\cite[Proposition~2.3]{Abe76}. 
-%We also note that the absolute case (i.\,e. $I=R$) of the theorem was treated by the second named author in~\cite{Sm12}.
 %
@@
 \end{equation}
-where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed through the structure constants (see~\cite[\S13]{VP}).
+where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed in terms of the structure constants (see~\cite[\S13]{VP}).
 For a reductive subset $\Delta \subseteq \Phi$ denote by $\widetilde{W}(\Delta)$ the \emph{extended Weyl group}, i.\,e.
@@
 \begin{proof}
-The first statement of the lemma follows from identity~\eqref{rel:R3} and the well-known fact that the Weyl group $W(\Phi)$ acts transitively on the set of roots of the same length.
-
-The same argument combined with \cref{lemma:abs} also proves the third statement. Indeed, by our assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.
+The first assertion follows from \eqref{rel:R3} and the well-known fact that $W(\Phi)$ acts transitively on the set of roots of the same length.
+The same argument combined with \cref{lemma:abs} also proves the third assertion. Indeed, by the assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.
 
@@
 Define the semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
-The elements $h_\alpha(\varepsilon)$ satisfy the following relations:
+The elements $h_\alpha(\varepsilon)$ satisfy the following relation:
 \begin{alignat}{2} 
-& [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] = 1, &\quad& \alpha, \beta \in \Phi, \ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-comm} \\
-& \phantom{[} h_\alpha(\varepsilon_1 \varepsilon_2) = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2), && \alpha \in \Phi, \ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-mult} \\
+%& [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] = 1, &\quad& \alpha, \beta \in \Phi, \ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-comm} \\ 
+%& \phantom{[} h_\alpha(\varepsilon_1 \varepsilon_2) = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2), && \alpha \in \Phi, \ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-mult} \\
 & \phantom{[} h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta, \alpha\rangle}\xi\right), && \alpha, \beta \in \Phi, \ \varepsilon \in R^*, \xi \in R.
@@
 
-For a special subset of roots $\Sigma\subseteq \Phi$ we denote by $\U(\Sigma, I)$ the subgroup spanned by all $x_{\alpha}(I)$ for $\alpha\in \Sigma$. Let $J\subset\Pi$.
-The subgroup $\U(\Sigma_J^+, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I)$ is a subgroup called a \emph{standard parabolic subgroup}.
-The following two equalities will be referred to as the \emph{Levi decomposition}:
+For a special subset of roots $\Sigma\subseteq \Phi$ we denote by $\U(\Sigma, I)$ the subgroup spanned by all $x_{\alpha}(I)$ for $\alpha\in \Sigma$. 
+For $J\subset\Pi$ the subgroup $\U(\Sigma_J^+, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I)$ is a subgroup,
+ which we call a \emph{standard parabolic subgroup}.
+The following two equalities will be referred to in the sequel as \emph{Levi decomposition}:
 \begin{equation} \label{rel:Levi-decomp} \EP_J(R, I) = \U(\Sigma_J^+, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I). \end{equation}
 When $J = \{ \alpha_s \}$ for some $1 \leq s\leq \ell$, we use the shorthand $\EP_s(R, I)$ for $\EP_{\{s\}}(R, I)$.
-When $I=R$, we also write $\EP_J(R)$ instead of $\EP_J(R, R)$.
+In the case $I=R$, we also write $\EP_J(R)$ instead of $\EP_J(R, R)$.
 
@@
 \end{multline}
-Note that $(1+s)^{-1}\in 1+I$ and so all the factors lie in $\E(\Phi, R, I)$. This shows, in particular, that $\Hh(\Phi, R, I) \leqslant \E(\Phi, R, I)$.
-
-The following lemma is a relative version of the classical result sometimes called the Chevalley---Matsumoto decomposition.
-It can be deduced easily from the absolute statement (see~\cite[Theorem~1.3]{St78}).
+Notice that $(1+s)^{-1}\in 1+I$ hence all the above factors lie in $\E(\Phi, R, I)$. 
+ This shows, in particular, that $\Hh(\Phi, R, I) \leqslant \E(\Phi, R, I)$.
+
+The following lemma is, in essence, a relative version of the classical Chevalley---Matsumoto decomposition.
+It can be easily deduced from the absolute statement (see e.\,g.~\cite[Theorem~1.3]{St78}).
 \begin{lemma}\label{lemma:Chevalley-Matsumoto}
@@
 In this section we define the stability conditions used in the statements of our decomposition theorems in section~\ref{sec:factorizations}.
-First, we recall the notion of the stable rank of an ideal introduced by L.~Vaserstein in~\cite{Va69, Va71}.
-As we will be mainly concerned with applications to Chevalley groups, our exposition of the stable ranks is neccessarily limited to commutative rings.
-The main goal of subsection~\ref{sec:rel-asr} is to define the relative version of the absolute stable rank condition, which generalizes the definition in~\cite{EO, MKV}.
-Finally, in the end of this section we state several technical lemmas describing the action of certain unipotent radicals on the unimodular columns under the assumption of a suitable stability condition.
+First, we recall the definition of the stable rank of an ideal introduced by L.~Vaserstein in~\cite{Va69, Va71}.
+As we will be mainly concerned with applications to Chevalley groups, our exposition is limited to commutative rings.
+Next, in section~\ref{sec:rel-asr} we define relative version of the absolute stable range condition introduced in~\cite{EO, MKV}.
+Finally, we formulate and prove several technical lemmas describing the action of certain unipotent subgroups on unimodular columns under the assumption of suitable stability conditions.
 
@@
 We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n, I)$ (resp. $\Ums(n, I)$).
-When $I=R$, we refer to the $R$-unimodular rows and columns as simply \emph{unimodular}.
-
+When $I=R$, we refer to $R$-unimodular rows and columns as simply \emph{unimodular}.
 It is not hard to show that for an $I$-unimodular row $a$ there exists an $I$-unimodular column $b$ such that $ab=1$ (see~\cite[\S2]{Va69}).
@@
 We say that $I$ satisfies the stable range condition $\SR_n(I)$ if any $I$-unimodular row of length $n+1$ is stable.
-Vaserstein noted~\cite[Theorem~1]{Va71} that $\SR_n(I)$ implies $\SR_m(I)$ for any $m\geqslant n$. 
+For $m \geqslant n$ the condition $\SR_n(I)$ implies $\SR_m(I)$, see~\cite[Theorem~1]{Va71}.
 It is also clear that the condition $\SR_n(I)$ does not depend on the choice of the ambient ring $R$.
@@
 \subsection{Action of unipotent radicals}\label{sec:ur-action}
+
+In this section we work with standard vector representations of classical groups (i.\,e. representations with highest weight $\varpi_1$).
+It will be convenient for us to number the weights of these representations as in~\cite[\S~1B]{St78}:
+For example, we write $1$ instead of $\varpi_1$, $2$ instead of $\varpi_1-\alpha_1$ etc.
+
+Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ such that $\lambda_1-\lambda_2\in \Phi$.
+It will be convenient for us to write $x_{\lambda_1, \lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
+For example, for $\Phi=\rA_\ell$ we have $x_{1, 2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
+
 \begin{lemma}\label{lemma:PSV-symplectic-trick}
@@
 \rF_4                                & 4    &1     & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
- \caption{List of the cases considered in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
+ \caption{List of representations used in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
 \end{table}
@@
 The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
-Multiplying $A$ on the left by $x_{12}(z)$, we get a matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with the invertible  element $a'$ in the top-left corner.
+Multiplying $A$ on the left by $x_{12}(z)$, we get a matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible element $a'$ in the top-left corner.
 After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 

### 2017-02-07 paper.tex
Minor fixes

@@
 \begin{abstract} 
-We formulate and prove relative versions of several classical ``parabolic'' decompositions known in the theory of Chevalley groups over commutative rings.
+We formulate and prove relative versions of several decompositions known in the theory of Chevalley groups over commutative rings.
 We apply them to construct new factorizations in terms of $\SL_2$ and $\SL_n$ subgroups and to obtain upper estimates on the width of principal congruence subgroups in terms of Tits---Vaserstein generators.
@@
 \section{Introduction}\label{sec:intro}
-The aim of the present paper is to extend various decomposition of Chevalley groups and their elementary subgroups to their principal congruence subgroups and relative elementary subgroups.
-We focus on the so-called ``parabolic decompositions'', i.e.
-decompositions involving parabolic and unipotent factors.
-The main result is the following
-
-\begin{restatable*}[Dennis---Vaserstein decomposition]{thm}{ThmDennisVaserstein}\label{thm:DennisVaserstein}
+The aim of this paper is to generalize several decompositions of Chevalley groups over rings 
+ to their principal congruence subgroups and relative elementary subgroups.
+We focus on the so-called ``parabolic decompositions'', i.e. decompositions involving parabolic and unipotent factors. 
+One of our main results is the following theorem.
+\begin{thm}[Dennis---Vaserstein decomposition]\label{thm:DennisVaserstein}
 Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geqslant 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
@@
 Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$
-\end{restatable*}
+\end{thm}
 Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5 and~4.1]{St78}.
-The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev \cite[Lemma~2.1]{ST76}.
+%The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev \cite[Lemma~2.1]{ST76}.
 The condition $\asr(I) \leq d$ is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm, which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
-
-We also prove the relative analogues of Gauss and Bass---Kolster decompositions (\cref{thm:srRI1,thm:BassKolster}).
-
-We apply these decompositions to several problems.
-First, we investigate the factorizations of Chevalley groups in terms of their subsystem subgroups.
-One of such factorizations if a decomposition into the product of subgroups isomorphic to $\SL(2, R, I)$.
-We show in \cref{thm:SL2width} that for classical groups over rings satisfying assumptions close to the stable rank $\leqslant2$ there exist such factorizations of length having the leading term $3|\Phi^+|$ in case $\Phi=\rA_\ell, \rC_\ell$ and $4|\Phi^+|$ otherwise.
-
-Another is the decomposition in terms of subgroups of type $\rA_\ell$ of submaximal rank.
-We show that Dennis---Vaserstein decomposition can be of great help in this problem.
-Namely, we prove the following
-\begin{restatable*}{thm}{ThmSpinSLnProd}\label{thm:spin-sln-prod}
+Another results of the paper are relative analogues of Gauss and Bass---Kolster decompositions (see~\cref{thm:srRI1,thm:BassKolster}).
+
+We apply our decompositions to several problems.
+First, we obtain upper estimates of the number of factors in the presentation of a Chevalley group as a product of its subsystem subgroups of type $\rA_\ell$.
+For example, in~\cref{thm:SL2width} such estimates are given for relative classical groups and products of subgroups $\SL(2, R, I)$.
+% For classical groups over rings satisfying suitable dimension assumptions we show the existence of 
+% factorizations with $3|\Phi^+|$ in case $\Phi=\rA_\ell, \rC_\ell$ and $4|\Phi^+|$ otherwise, see
+Our another result is the decomposition in terms of subgroups of type $\rA_\ell$ of submaximal rank. 
+Using~\cref{thm:DennisVaserstein} we prove the following theorem inspired by the main result of~\cite{Nik07}.
+\begin{thm}\label{thm:spin-sln-prod}
 Assume that $\sr(I) \leqslant 2$. Then the group $\Epin(2\ell, R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ regularly embedded subgroups of type $\rA_{\ell-1}$.
-\end{restatable*}
-
-Then we obtain the upper bounds on the width of $\E(\Phi, R, I)$ in terms of Vaserstein---Tits generators for various rings (\cref{thm:width}).
+\end{thm}
+
+Finally, we obtain upper bounds on the width of $\E(\Phi, R, I)$ with respect to Vaserstein---Tits generators for several important classes of small-dimensional rings (see~\cref{thm:width}).
 
@@
 
-\ThmDennisVaserstein
-\begin{proof} %[Proof of \cref{thm:DennisVaserstein}]
+\begin{proof} [Proof of \cref{thm:DennisVaserstein}]
 Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$:
@@
 
-\ThmSpinSLnProd
-\begin{proof} %[Proof of \cref{thm:spin-sln-prod}]
+%\ThmSpinSLnProd
+\begin{proof} [Proof of \cref{thm:spin-sln-prod}]
 Set $L = \E(\Delta_\ell, R, I) \leq \E(\rD_\ell, R, I)$ and denote by $\sigma$ the automorphism of $\G(\rD_\ell, R)$ induced by the 
@@
 \end{proof}
-The above lemmas together with \cref{cor:bass-kolster-count,thm:Gauss} give the following
+The above lemmas together with \cref{cor:bass-kolster-count,thm:Gauss} give the following.
 \begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.
@@
 \end{thm}
+Here $W(G, X)$ denotes \emph{the width of $G$ with respect to a generating set $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
 %\begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.

### 2017-02-08 paper.tex
More minor fixes

@@
 We formulate and prove relative versions of several decompositions known in the theory of Chevalley groups over commutative rings.
-We apply them to construct new factorizations in terms of $\SL_2$ and $\SL_n$ subgroups and to obtain upper estimates on the width of principal congruence subgroups in terms of Tits---Vaserstein generators.
+These decompositions are used to obtain factorizations in terms of subsystem subgroups of type $\rA_\ell$ and 
+ upper estimates of the width of principal congruence subgroups in terms of Tits---Vaserstein generators.
 Some of our results are new even in the absolute case and were previously studied only for groups over finite fields.
@@
 \end{thmlist} \end{lemma}
-\begin{proof} The first two statements easily follow from the Chevalley commutator formula~\eqref{rel:CCF} while the third one is a formal consequence of the first two. \end{proof}
+\begin{proof} The first two statements easily follow from the Chevalley commutator formula while the third one is a formal consequence of the first two. \end{proof}
 
@@
 
-Notice that $\beta_1$ is the only root of $\Phi$ satisfying $m_2(\beta_1)=2$, therefore the commutator formula~\eqref{rel:CCF} implies
+Notice that $\beta_1$ is the only root of $\Phi$ satisfying $m_2(\beta_1)=2$, therefore Chevalley commutator formula implies
 \[ \bigl[\U(\Delta_2^-, I), x_{\beta_1}(1)\bigr]=1. \]

### 2018-01-15 paper.tex
Referee`s comments

@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
-We omit curly braces in the above notations when $J$ is a one or two element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
+We omit curly braces in the above notations when $J$ is a one- or two-element set, e.\,g.
+$\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
+We call $\shape(\{s\}, \beta)$ the $s$-shape of $\beta$.
 
@@
 \end{equation}
-where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed in terms of the structure constants (see~\cite[\S13]{VP}).
+where $\eta_{\alpha, \beta}=\pm 1$. The coefficients $\eta_{\alpha, \beta}$ can be expressed in terms of the structure constants of the corresponding Lie algebra (see~\cite[\S13]{VP}).
 For a reductive subset $\Delta \subseteq \Phi$ denote by $\widetilde{W}(\Delta)$ the \emph{extended Weyl group}, i.\,e.
@@
 For a special subset of roots $\Sigma\subseteq \Phi$ we denote by $\U(\Sigma, I)$ the subgroup spanned by all $x_{\alpha}(I)$ for $\alpha\in \Sigma$. 
-For $J\subset\Pi$ the subgroup $\U(\Sigma_J^+, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I)$ is a subgroup,
- which we call a \emph{standard parabolic subgroup}.
+For $J\subset\Pi$ the subgroup $\U(\Sigma_J^+, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I)$ is a subgroup, which we call a \emph{standard elementary parabolic subgroup}.
 The following two equalities will be referred to in the sequel as \emph{Levi decomposition}:
@@
 Now we can find $t\in I$ such that its image $\bar{t}$ in the residue field $R/\mathfrak{m}$ equals $-\bar{1}/\bar{d}$.
-This means that $1 + b' \in \mathfrak{m}$ for $b'=td\in J$ which, contradicts the unimodularity of $v$.
+This means that $1 + b' \in \mathfrak{m}$ for $b'=td\in J$, which contradicts the unimodularity of $v$.
 This shows that no such $\mathfrak{m}$ may exist and, therefore, $\mathfrak{J}(a'_1, \ldots, a'_n)=\mathfrak{J}(a_1, \ldots, a_n, d)$.
@@
  The assertion follows from the fact that for every $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that $uu'$ lies in the image of $i$. 
- Indeed, denote by $\sigma$ the symmetry of the Dynkin diagram of $\rD_\ell$,
- and decompose $u$ into the product $u_1 \cdot u_2$, where $u_1 \in \U(\Sigma_\ell^+\cap\Delta_{\ell-1}, I)$ and $u_2 \in \U(\Sigma_\ell^+ \cap \Sigma_{\ell-1}^+, I)$.
+ Indeed, denote by $\sigma$ the automorphism of $\E(\rD_\ell, R)$ induced by the symmetry of its Dynkin diagram, and decompose $u$ into the product $u_1 \cdot u_2$, where $u_1 \in \U(\Sigma_\ell^+\cap\Delta_{\ell-1}, I)$ and $u_2 \in \U(\Sigma_\ell^+ \cap \Sigma_{\ell-1}^+, I)$.
  Then one takes $u' = \sigma(u_1)$.
@@
 \begin{proof} [Proof of \cref{thm:DennisVaserstein}]
-Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$:
+Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the possibilities for $\Phi$, $s$, $r$ listed in~\cref{table:dv-reps}.
 \begin{table}[htb]
@@
 \begin{equation*} \label{rel:CCF-specBC}
-x_{1, 0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1, -2}(-a b^2)
+x_{1, 0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1, -2}(-a b^2).
 \end{equation*}
@@
 
-The set $\Gamma$ can be visualized using the weight diagrams in the following manner.
+The set $\Gamma$ can be visualized using the weight diagrams (see~\cite{PSV98}) in the following manner.
 After the removal of all bonds marked $r$ the weight diagram of $\pi$ splits into several connected components.
@@
 
-By a consideration of the weight diagrams (see~\cite{PSV98}) we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
+By a consideration of the weight diagrams we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
 
@@
 \end{proof}
+
+We will now turn our our attention to the factorizations in terms of large rank subsystem subgroups in order to prove \cref{thm:spin-sln-prod}.
 
@@
  \end{multline*}
-It remains to note that $\Sigma_2^+ \cap \Sigma_\ell^+ \cap \Delta_1 = \beta_1 + \Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell$. The same argument works for $[w, x_{\beta_1}(1)]$.
+It remains to note that $\Sigma_2^+ \cap \Sigma_\ell^+ \cap \Delta_1 = \beta_1 + (\Sigma_1^- \cap \Sigma_2^- \cap \Delta_\ell)$. The same argument works for $[w, x_{\beta_1}(1)]$.
 Direct calculation using the commutator formula shows that
@@
 Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
-(see \eqref{eq:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we have a decomposition
+(see \eqref{eq:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we can decompose $g$ as follows:
 \[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
@@
 For the rest of this subsection $k$ denotes a global field. We assume that there is some finite set of places $S$ chosen on $k$. 
-Let $\mathcal{O}_S$ be a Dedekind ring of arithmetic type defined by $S$ and let $I$ be an ideal of $\mathcal{O}_S$.
+Let $\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and let $I$ be an ideal of $\mathcal{O}_S$.
 
@@
 \begin{thmlist}
-\item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
+\item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\ell\geqslant2$, then 
 $W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite;
@@
 \begin{alignat*}{2}
-& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1 & \text{ if } \Phi=\rA_\ell, \rC_\ell, \\
-& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell.
+& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\ell + 1 & \text{ if } \Phi=\rA_\ell, \rC_\ell, \\
+& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \ell + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell.
 \end{alignat*}
@@
 \end{thm}
-Here $W(G, X)$ denotes \emph{the width of $G$ with respect to a generating set $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
+Here $W(G, X)$ denotes \emph{the width of $G$ with respect to a generating set $X$}, i.\,e.
+the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$ and their inverses.
 %\begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.

### 2018-01-18 paper.tex
Minor fixes

@@
 
-We will now turn our our attention to the factorizations in terms of large rank subsystem subgroups in order to prove \cref{thm:spin-sln-prod}.
+We now turn our attention to the proof of \cref{thm:spin-sln-prod} and the study of factorizations in terms of subsystem subgroups of large rank.
 
@@
 \subsection{Bounded generation}\label{sec:boundgen}
-We now give an application of the parabolic factorizations to the problem of bounded generation.
+In this section we apply parabolic factorizations to the problem of bounded generation.
+The main result of this section gives an upper bound on the width of $\E(\Phi, R)$ in terms of Tits generators and is, thus,
+ a quantitative analogue of \cite[Theorem~3.4]{S} and a relative analogue of the results of~\cite{VseUnitrZ1p, VavSmSuUnitrEng}.
 
@@
 
-For the rest of this subsection $k$ denotes a global field. We assume that there is some finite set of places $S$ chosen on $k$. 
+For the rest of this subsection $k$ denotes a global field and $S$ some finite set of places on $k$. 
 Let $\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and let $I$ be an ideal of $\mathcal{O}_S$.
@@
 First of all, notice that $\asr(I) \leqslant \asr(\mathcal{O}_S) \leqslant 2$. 
-By \cref{cor:bass-kolster-iterated} we can present any element 
+By \cref{cor:bass-kolster-iterated} we can write any element 
 of $G=\G(\Phi, \mathcal{O}_S, I)$ as a product of a finite number of generators from $\mathcal{Z}(\Sigma_\ell)$ and one element of 
@@
 Here $W(G, X)$ denotes \emph{the width of $G$ with respect to a generating set $X$}, i.\,e.
-the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$ and their inverses.
+the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$ or their inverses.
 %\begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.

### 2018-01-18 paper.tex
Added affiliation
Purged all comments

@@
 \renewcommand*{\bibfont}{\footnotesize}
-
-%\oddsidemargin 5mm
-%\marginparwidth 5mm
-%\topmargin 0mm
-%\textheight 225mm
-%\textwidth 165mm
-%\headheight 0mm
-%\headsep 10mm
-%\footskip 5mm
 
@@
 \author{Sergey Sinchuk}
+\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
+\email{sinchukss {\it at} yandex.ru;}
+
 \author{Andrei Smolensky}
-\email{sinchukss {\it at} yandex.ru; andrei.smolensky {\it at} gmail.com}
+\address{Department of Mathematics and Mechanics, St. Petersburg State University, St. Petersburg, Russia}
+\email{ andrei.smolensky {\it at} gmail.com}
 \thanks{The authors of the present paper acknowledge the financial support of the Russian Science Foundation grant 14-11-00297}
@@
 Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5 and~4.1]{St78}.
-%The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev \cite[Lemma~2.1]{ST76}.
 The condition $\asr(I) \leq d$ is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm, which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
@@
 For example, in~\cref{thm:SL2width} such estimates are given for relative classical groups and products of subgroups $\SL(2, R, I)$.
-% For classical groups over rings satisfying suitable dimension assumptions we show the existence of 
-% factorizations with $3|\Phi^+|$ in case $\Phi=\rA_\ell, \rC_\ell$ and $4|\Phi^+|$ otherwise, see
 Our another result is the decomposition in terms of subgroups of type $\rA_\ell$ of submaximal rank. 
@@
 \section{Preliminaries}\label{sec:preliminaries}
-%Let us now fix the notations used in the paper.
 Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of fundamental roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
@@
 Here $I^{\indexbox{2}}$ denotes the ideal generated by the squares $a^2$, where $a\in I$.
-
-%The following recent result of A.~Stepanov served as a starting point for the present paper.
-%The notation for the subgroups involved in the statements of the results below is introduced properly in section~\ref{sec:prelim}.
-%\begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
-%Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be an arbitrary parabolic subset of roots, and $\Sigma_S$ be the special part of $S$.
-The relative elementary subgroup $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$.
-\end{prop}
-
-%The purpose of this paper is two-fold. 
-%First, we obtain relative analogues of several classical parabolic factorizations of Chevalley groups such as the Gauss, Bass---Kolster and Dennis---Vaserstein decompositions.
-%Then we apply these factorizations to the study of various bounded generation properties of Chevalley groups over rings.
-%
-%Our first result is a relative version of the Gauss decomposition formulated in terms of the \emph{stable rank} of the ideal $I$ (see section~\ref{sec:stability-conditions} for the definition)
-%\begin{thm}\label{thm:srRI1}
-%Let $\Phi$ be a root system, let $I$ be an ideal of an arbitrary commutative ring $R$, and assume that $\sr(I)=1$.
-%Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits the following decomposition:
-%\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi, I). \]
-%\end{thm}
-%
-%The next main result is the relative Dennis---Vaserstein decomposition, which holds for a broader class of rings as compared to \cref{thm:srRI1}.
-%\begin{thm}\label{thm:DennisVaserstein}
-%Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geqslant 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
-Denote the distance between $r$ and $s$ by $d$.
-%Assume that $\Phi$, $I$ and $\{r, s\}$ satisfy either of the following assumptions:
-%\begin{thmlist}
-% \item $\sr(I) \leqslant d$ for classical $\Phi$,
-% \item $\sr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{ 2, \ell \}$,
-% \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
-% \item $\asr(I) \leqslant d$ for $\Phi=\rF_4$.
-%\end{thmlist}
-%Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$ \end{thm}
-%Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5 and~4.1]{St78}.
-%The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev (cf.~\cite[Lemma~2.1]{ST76}).
-%
-%The condition $\asr(I) \leq d$ used in the statement of \cref{thm:DennisVaserstein} is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm, which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
-%
-%Let $G$ be an abstract group with a generating set $X \subset G$. 
-%We denote by $W(G, X)$ the \emph{width of $G$ with respect to $X$}, i.\,e. the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$.
-%
-%Our first application of the parabolic factorizations is the following theorem, which gives an upper bound on the width of $\E(\Phi, R)$ in terms of Tits generators. 
-%Thus, it is a quantitative analogue of \cref{prop:Stepanov}
-%and a relative analogue of the results of~\cite{Tavgen91, VseUnitrZ1p, VavSmSuUnitrEng}.
-%\begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.
-%\begin{thmlist}
-%\item If $R=\mathcal{O}_S$ is a Dedekind ring of arithmetic type posessing a real embedding and $\Phi$ is classical of rank $\geqslant2$, then 
-%$W(\G(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))$ is finite;
-%\item If $\sr(I) = 1$ and $\Phi$ is an arbitrary irreducible root system, then 
-%\[W(\E(\Phi, R, I), \mathcal{Z}(\Pi))\leqslant 3|\Phi^+|+2\rk(\Phi)-1;\]
-%\item If $R = \mathbb{Z}[\sfrac{1}{p}]$ for some prime number $p$, then under the assumption of the Generalized Riemann Hypothesis one has
-%\begin{alignat*}{2}
-%& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\rk(\Phi) + 1 & \text{ if } \Phi=\rA_\ell, \rC_\ell, \\
-%& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \rk(\Phi) + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell.
-%\end{alignat*}
-%\end{thmlist}
-%\end{thm}
-%The first assertion of the above theorem is essentially a reformulation of a previously known result of O.~Tavgen (see \cite{TavgenThesis}, cf.~\cite{Mo07}), 
-%while for the second and the third assertion we give a direct proof.
-%Compare \cref{thm:width} with a recent result of U.~Hadad and D.~W.~Morris \cite[Theorem~1.6]{Ha12} which asserts that 
-%$W(\SL(n, \mathbb{Z}, I), \mathcal{Z}(\Pi))$ is finite for any ideal $I \leq \mathbb{Z}$ and $n \geq 3$.
-%
-%Another application of the parabolic factorizations developed in the present paper is the subsystem factorization in terms of subgroups of type $\rA_1$.
-%The case of a finite field $R=F$ was studied by M.~Liebeck, N.~Nikolov and A.~Shalev in~\cite{LNS11}.
-%More precisely, for an untwisted Chevalley group it has been proved that $\G(\Phi, F)$ is a product of at most $N=5|\Phi^+|$ copies of $\SL(2, F)$.
-%
-%In~\cite{V13} N.~Vavilov and E.~Kovach noted that the Bruhat decomposition immediately implies a bound of $N=3|\Phi^+|$ factors for an arbitrary field $F$.
-%In fact, in the assumptions of \cref{thm:srRI1} one can immediately obtain the decomposition of $\E(\Phi, R, I)$ with $3|\Phi^+|$ factors of type $\rA_1$.
-%Our next result further extends this to an even larger class of rings (which, for example, includes the ideals of all Dedekind rings).
-%\begin{thm}\label{thm:SL2width}
-%Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system satisfying one of the following assumptions.
-%\[\begin{array}{l@{\quad}l@{\quad}l}
-%\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right| - \rk(\Phi) - 1; \\
-%\Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right| - 2; \\
-%\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right| - 3\rk(\Phi).
-%\end{array}\]
-%Then the principal congruence subgroup $\G(\Phi, R, I)$ can be presented as a product of at most $N$ copies of its (regularly embedded) subgroups isomorphic to $\SL_2(R, I)$.
-%\end{thm}
-%
-%Yet another application of the parabolic factorizations concerns the product decompositions of Chevalley groups formulated in terms of subgroups of type $\rA_\ell$ of submaximal rank.
-%Recall that in \cite{Nik07} N.~Nikolov proves the following result. 
-%\begin{thm*} Let $G$ be a classical Chevalley group (of normal or twisted type) of rank $\ell$ over a finite field $F$.
-%Then $G$ can be presented as a product of at most $200$ conjugates of its subgroups of type $\rA_{\ell-1}$. \end{thm*}
-%
-%It is classically known that over an arbitrary field $F$ the group $\SL_{n+1}(F)$, $n\geq 3$ is a product of at most $4$ subgroups of type $\SL(n, F)$.
-%On the other hand, one immediately obtains from \cref{thm:DennisVaserstein} and surjective stability for linear $\K_1$-functor that $\SL_{n+1}(R, I)$ factors into a product
-%of a most $5$ subgroups of type $\SL_n(R, I)$ for any ideal $I$ satisfying $\sr(I)\leqslant n-1$.
-%
-%Applying \cref{thm:DennisVaserstein} and proving a more accurate version of \cite[Proposition~1]{Nik07} in the special case $\Phi=\rD_\ell$, we obtain the following result.
-%\begin{thm}\label{thm:spin-sln-prod}
-%Assume that $\sr(I) \leqslant 2$. Then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of its (regularly embedded) subgroups of type $\rA_{\ell-1}$.
-%\end{thm}
-
-%The rest of the article is organized as follows.
-%In sections \ref{sec:prelim}--\ref{sec:stability-conditions} we introduce the principal notation and prove some basic facts pertaining to Chevalley groups over rings and the stability conditions.
-%In section \ref{sec:factorizations} we construct various parabolic factorizations and thus prove \cref{thm:srRI1,thm:DennisVaserstein,thm:SL2width}.
-%Finally, we treat the bounded generation and the product decompositions separately in section~\ref{sec:applications}, where \cref{thm:width,thm:spin-sln-prod} are proved.
 
@@
 \begin{alignat}{2} 
-%& [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] = 1, &\quad& \alpha, \beta \in \Phi, \ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-comm} \\ 
-%& \phantom{[} h_\alpha(\varepsilon_1 \varepsilon_2) = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2), && \alpha \in \Phi, \ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-mult} \\
 & \phantom{[} h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta, \alpha\rangle}\xi\right), && \alpha, \beta \in \Phi, \ \varepsilon \in R^*, \xi \in R.
@@
 \end{alignat}
-
-%Our notation and terminology pertaining to the representations of Chevalley groups follows \cite[\S~1.4]{PSV98} and \cite[\S~I.2]{Ma69})
-%Let $\pi$ be an irreducible representation of $\G(\Phi, R)$ acting on a free $R$-module $V$.
-%We denote by $\Lambda=\Lambda(\pi)$ the set of weights of $\pi$ and by $\Lambda(\pi)^*$ the subset of non-zero weights.
-%Denote by $V_\lambda \leq V$ the \emph{weight subspace}, corresponding to $\lambda\in\Lambda(\pi)$ and denote by $m_\lambda$ the dimension of $V_\lambda$.
-%
-%A representation $\pi$ is called \emph{basic} if for every pair of non-zero weights $\lambda, \mu \in \Lambda^*(\pi)$ such that $\lambda - \mu \in \Pi$ one has $\sigma_\alpha(\lambda) = \mu$ for some $\alpha\in\Phi$.
-%Obviously, this is equivalent to saying that $W(\Phi)$ acts transitively on $\Lambda(\pi)^*$.
-
-%The irreducible representations of Chevalley groups used in the present paper form a sublist of~\cite[Table~2]{PSV98}.
-%More specifically, all of them are \emph{fundamental} (i.\,e. their highest weight is fundamental) and basic.
-%We widely employ the technique of \emph{weight diagrams} (see~\cite[\S~2]{PSV98}) to help visualize the structure of these representations.
-%In the simplest case of a \emph{microweight} representation $\pi$ (i.\,e. $\pi$ is basic and $V_0 = 0$)
-%the weight diagram of $(V, \pi)$ is just an undirected graph whose vertices are in the one-to-one correspondence with the elements of $\Lambda(\pi)$.
-%Two vertices $\lambda$, $\mu$ of the diagram are joined by a bond marked $i$ if $\lambda-\mu = \alpha_i$.
-%
-%An immediate application of the weight diagrams is that they allow one to quickly read off the branching of a given basic representation with respect to a subsystem subgroup.
-%If $J$ is a subset of $\Pi$ and $\Delta$ is the subsystem of $\Phi$ spanned by $J$ then the weight diagram of $\pi$ restricted to $G(\Delta, R)$ can be obtained
-%from the weight diagram of $\pi$ by simply removing all the bonds whose label $i$ is such that $\alpha_i\not\in J$ (cf.~\cite[\S~2.7]{PSV98}).
-% 
-%Recall that all nonzero weights of a basic representation have multiplicty one and the multiplicity $m_0$ of the zero weight subspace equals $|\Delta(\pi)|$, where $\Delta(\pi)= \Lambda(\pi)^* \cap \Pi$ (see~\cite[Lemma~2.1]{Ma69}).
-%For $\alpha \in \Phi$ one can define certain elements $e_0(\alpha) \in V_0$ and $\alpha_* \in V_0^* = \Hom_R(V_0, R)$
-%and choose some set of vectors $E^* = \{ e_\lambda \}_{\lambda \in \Lambda^*(\pi)}$ in such a way that 
-%$E_\pi = E^* \cup \{ e_0(\alpha) \}_{\alpha \in \Delta(\pi)}$ forms a basis of $V$ in which the action of the elementary root unipotents
-%$x_\alpha(\xi)$ has a particularly simple description.
-%
-%\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
-%Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
-%Then the action of $x_\alpha(\xi)$ is described by the following formulae.
-%\newline \begin{tabular}{ll}
-%If $\lambda\in\Lambda(\pi)^*, \ \lambda+\alpha\notin\Lambda(\pi)$, then & $x_\alpha(\xi)e_\lambda=e_\lambda$; \\
-%If $\lambda, \lambda+\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_\lambda=e_\lambda\pm\xi e_{\lambda+\alpha}$; \\
-%If $\alpha\notin\Lambda(\pi)^*$, then & $x_\alpha(\xi)v_0=v_0$ for any $v_0\in V_0$; \\
-%If $\alpha\in\Lambda(\pi)^*$, then & $x_\alpha(\xi)e_{-\alpha} = e_{-\alpha}\pm\xi e_0(\alpha)\pm\xi^2 e_\alpha$ and \\
-%                                   & $x_\alpha(\xi)v_0         = v_0\pm\xi\alpha_*(v_0)e_\alpha$ for $v_0 \in V_0$.
-%\end{tabular} \end{lemma}
-
-%\subsection{Relative Chevalley groups}\label{sec:relative-elementary}
-%Recall from the introduction that the elements $z_\alpha(s, \xi) = x_\alpha(s)^{x\ssub{-\alpha}(\xi)}$ generate $\E(\Phi, R, I)$ as an abstract group.
 
@@
 
-%\subsection{\texorpdfstring{$\K_1$}{K1}-functor modeled on Chevalley groups}
-%Recall that by a theorem of Taddei $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).
-%
-%Using standard relativization argument it is not hard to deduce from Taddei's result that $\E(\Phi, R, I)$ is normal in $\G(\Phi, R, I)$ under the same assumptions on $\Phi$.
-%This allows us to define the relative $\K_1$-group as $\K_1(\Phi, R, I)=\G(\Phi, R, I)/\E(\Phi, R, I).$
-%When $I=R$, we write $\K_1(\Phi, R)$ for $\K_1(\Phi, R, R)$.
-%
-%In some cases it is known that $\K_1(\Phi, R, I)$ is trivial.
-%For example, $\SK_1(\ell+1, R)=\K(\rA_\ell, R)=1$ for any ring of stable rank $1$ (see section~\ref{sec:stability-conditions}), 
-%and for other root systems some stronger assumption is required such as $\asr(R)=1$ or being semilocal. 
-%For any Euclidean ring $\K_1(\Phi, R, I)$ is trivial for every root system $\Phi$.
-%
-%Let $k$ be a global field, $S$ be a set of places of $k$, 
-%$\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and $I$ be an ideal of $\mathcal{O}_S$.
-%\begin{prop} \label{prop:K1triv}
-%Let $\Phi$ be a root system of rank $\geqslant2$. Assume that the field $k$ has a real embedding. Then $\K_1(\Phi, \mathcal{O}_S, I)=1$.
-%\end{prop}
-%\begin{proof} Follows from \cite[Theorem~3.6]{BMS} and \cite[Corollary~4.5]{Ma69}. \end{proof}
-
 \section{Stability conditions}\label{sec:stability-conditions}
@@
 By definition, the \emph{stable rank} of $I$ (denoted $\sr(I)$) is the smallest natural number $n$ such that $\SR_n(I)$ holds (we set $\sr(I)=\infty$ if no such $n$ exists).
-
-%The following proposition summarizes the basic properties of the stable rank.
-%\begin{prop} \label{prop:sr_properties}
-%Let $R$ be an arbitrary commutative unital ring and let $I\trianglelefteq R$ be an ideal.
-%\begin{lemlist}
-%\item For any ideal $I'\subseteq I$ one has $\sr(I')\leqslant\sr(I)$, $\sr(I/I')\leqslant\sr(I)$;
-%\item One has $\sr\Bigl(\prod\limits_{i=1}^n R_i\Bigr)=\max\limits_{i=1}^n\bigl(\sr(R_i)\bigr)$;
-%\item Let $J(R)$ denote the Jacobson radical of $R$, then $\sr(R)=\sr(R/J(R))$ and $\sr(J(R))=1$;
-%\item Let $I\rtimes\mathbb{Z}$ denote the ring obtained by formally adjoining $1$ to $I$. Then $\sr(I\rtimes\mathbb{Z})=\max(2,\sr(I))$.
-%\end{lemlist}
-%\end{prop}
-%\begin{proof} See~\cite[Theorem~2.3]{Va69}, \cite{Va71}. 
-%\end{proof}
-%\begin{example}
-%Since the stable rank of a field equals $1$, one can conclude from the previous proposition that $\sr(R)=1$ for any semilocal ring $R$.
-%Other examples of rings of stable rank $1$ are provided by the Boolean rings, the ring of all algebraic integers, the ring of entire functions, the disk-algebra, etc.
-For this and many other examples see~\cite{VasSR1}.
-%
-%%Formally adjoining a unit to a non-unital ring of stable rank $1$ produces a non-trivial example of an ideal having the stable rank strictly lower that the ambient ring.
-%\end{example}
 
@@
 \begin{equation} \label{sr-estimates} \sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \end{equation}
-%There exist examples of rings for which the first inequality in the above formula is strict.
-%More precisely, there are rings of stable rank $1$ but of absolute stable rank $\geqslant2$, see~\cite{MKV}.
-%On the other hand, \cite[Theorem~1.3]{MKV} shows that $\sr(R)=\asr(R)$ for any principal ideal ring $R$.
-%\begin{example}
-%From inequality~\eqref{sr-estimates} one concludes, in particular, that 
-%\begin{itemize}
-%\item $\asr(R) = 1$ for every semilocal ring $R$;
-%\item $\asr(R)\leqslant2$ for every Dedekind domain $R$;
-%\item $\asr(A[x])\leqslant3$ for every locally principal ring $A$;
-%\item $\asr(F[x_1,\ldots,x_n])\leqslant n+1$ for any field $F$.
-%\end{itemize}
-%For certain classes of fields there is also a lower estimate for $\sr(F[x_1, \ldots, x_n])$ which allows to compute precisely the value of both $\sr(R)$ and $\asr(R)$.
-%For example, $\sr(F[x,y])=3$ for every $F$ with $\K_2^M(F)\neq0$ (see~\cite{Kru73}) and $\sr(F[x_1, \ldots, x_n])=n+1$ for $F\subseteq\mathbb{R}$, see~\cite[Theorem~8]{Va71}.
-%Notice also that $\sr(\mathbb{Z}[x])=3$ (see \cite{GMV}) and $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ for $n>1$ (see example after~\cite[Theorem~18.2]{VS76}).
-%\end{example}
 
@@
 \end{thm}
-\begin{proof} %[Proof of \cref{thm:srRI1}]
+\begin{proof}
 In view of \cref{thm:Gauss} it suffices to prove that the Gauss decomposition of length $3$ holds for $\Phi=\rA_1$.
@@
 \end{thm}
-\begin{proof} %[Proof of \cref{thm:SL2width}]
+\begin{proof} 
  As in the proof of \cref{cor:bass-kolster-iterated}, one has to iteratively apply \cref{thm:BassKolster}.
@@
 the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$ or their inverses.
-%\begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.
-%The the first and the third assertions follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}
 

### 2018-01-19 paper.tex
Removed unused bibliography; some minor fixes

@@
 These decompositions are used to obtain factorizations in terms of subsystem subgroups of type $\rA_\ell$ and 
- upper estimates of the width of principal congruence subgroups in terms of Tits---Vaserstein generators.
+ upper estimates of the width of principal congruence subgroups in terms of Tits--Vaserstein generators.
 Some of our results are new even in the absolute case and were previously studied only for groups over finite fields.
@@
 One of our main results is the following theorem.
-\begin{thm}[Dennis---Vaserstein decomposition]\label{thm:DennisVaserstein}
-Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geqslant 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$.
+\begin{thm}[Dennis--Vaserstein decomposition]\label{thm:DennisVaserstein}
+Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geqslant 2$ and let $\{ r, s \}$ be a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
 Denote the distance between $r$ and $s$ by $d$.
@@
 The condition $\asr(I) \leq d$ is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm, which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
-Another results of the paper are relative analogues of Gauss and Bass---Kolster decompositions (see~\cref{thm:srRI1,thm:BassKolster}).
+Another results of the paper are relative analogues of Gauss and Bass--Kolster decompositions (see~\cref{thm:srRI1,thm:BassKolster}).
 
@@
 
-Finally, we obtain upper bounds on the width of $\E(\Phi, R, I)$ with respect to Vaserstein---Tits generators for several important classes of small-dimensional rings (see~\cref{thm:width}).
+Finally, we obtain upper bounds on the width of $\E(\Phi, R, I)$ with respect to Tits--Vaserstein generators for several important classes of small-dimensional rings (see~\cref{thm:width}).
 
@@
 
-The following lemma is, in essence, a relative version of the classical Chevalley---Matsumoto decomposition.
+The following lemma is, in essence, a relative version of the classical Chevalley--Matsumoto decomposition.
 It can be easily deduced from the absolute statement (see e.\,g.~\cite[Theorem~1.3]{St78}).
@@
 
-\subsection{Relative Dennis---Vaserstein decompositions}\label{sec:dennis-vaserstein}
+\subsection{Relative Dennis--Vaserstein decompositions}\label{sec:dennis-vaserstein}
 Let $\Phi$ be an irreducible root system of rank $\ell$.
@@
 
-Denote by $L_{rs}$ the set consisting of all the elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
+Denote by $L_{rs}$ the set consisting of all elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
 It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
@@
 Clearly, $\Gamma$ consists of the weights of $\Lambda(\pi')$ incident to the removed bonds.
-
-By a consideration of the weight diagrams we determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
+By a consideration of the weight diagrams it is easy to determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
 
@@
 \subsection{Relative Gauss decomposition}\label{sec:gauss}
-The proof of the Gauss decomposition presented below is similar to the absolute case \cite[Theorem~5.1]{Sm12}.
+The proof of the Gauss decomposition presented below is similar to the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
 \begin{prop}\label{thm:Gauss}
@@
 After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
-Thus we have obtained the relative Gauss decomposition of $A$
+Thus we have obtained a relative Gauss decomposition for $A$:
 \begin{equation*}
@@
 
-\subsection{Relative Bass---Kolster decompositions}\label{sec:bass-kolster}
-The next theorem is a relative version of the so-called Bass---Kolster decomposition \cite[Theorem~2.1]{St78}.
+\subsection{Relative Bass--Kolster decompositions}\label{sec:bass-kolster}
+The next theorem is a relative version of the so-called Bass--Kolster decomposition \cite[Theorem~2.1]{St78}.
 \begin{thm}\label{thm:BassKolster}
@@
 \end{array}\]
-Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of the Bass---Kolster decomposition:
+Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of the Bass--Kolster decomposition:
 \[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]
@@
 \subsection{Subsystem factorizations}\label{sec:subsysfact}
+Recall from~\cite{LNS11, V13} that a Chevalley group over a field $\G(\Phi, F)$ can be presented as a product of at most $3|\Phi^+|$ of its subgroups $\SL(2, F)$.
+As an easy corollary of relative Bass--Kolster decomposition we show that similar decomposition exists in the relative situation and for even larger class of rings.
 \begin{thm}\label{thm:SL2width}
-Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system satisfying one of the following assumptions.
+Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system of rank $\ell$ satisfying one the following 4 conditions:
 \[\begin{array}{l@{\quad}l@{\quad}l}
-\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right| - \rk(\Phi) - 1; \\
+\Phi=\rA_\ell, & \sr(I)\leqslant 2, & N=3\left|\Phi^+\right| - \ell - 1; \\
 \Phi=\rC_\ell, & \sr(I)\leqslant 3, & N=3\left|\Phi^+\right| - 2; \\
-\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right| - 3\rk(\Phi).
+\Phi=\rB_\ell, \rD_\ell, & \asr(I)\leqslant 2, & N=4\left|\Phi^+\right| - 3\ell.
 \end{array}\]
-Then the principal congruence subgroup $\G(\Phi, R, I)$ can be presented as a product of at most $N$ copies of its (regularly embedded) subgroups isomorphic to $\SL(2, R, I)$.
+Then the principal congruence subgroup $\G(\Phi, R, I)$ can be presented as a product of at most $N$ of its subgroups, 
+ where each subgroup is an isomorphic copy of $\SL(2, R, I)$.
 \end{thm}
+
 \begin{proof}
@@
  To reduce the number of $\SL_2$-factors involved in the decompositoin one has to group into a single $\SL_2$-factor a pair of opposite root subgroups $X_{\alpha}(I)$, $X_{-\alpha}(I)$ (or $Z_{\pm\alpha}(I)$) appearing on each
- of the $3$ junctions between the positive and negative unipotent subgroups in the Bass---Kolster decomposition.
+ of the $3$ junctions between the positive and negative unipotent subgroups in the Bass--Kolster decomposition.
  Since a total of $\ell-1$ reductions are used, we get the estimate $N \leq N' - 3(\ell - 1) + 1$ and the assertion of \cref{thm:SL2width} follows.
@@
 
-We now turn our attention to the proof of \cref{thm:spin-sln-prod} and the study of factorizations in terms of subsystem subgroups of large rank.
+We now turn our attention to the proof of \cref{thm:spin-sln-prod}, which will occupy the rest of this subsection.
 
@@
 
-%\ThmSpinSLnProd
 \begin{proof} [Proof of \cref{thm:spin-sln-prod}]
@@
 \subsection{Bounded generation}\label{sec:boundgen}
-In this section we apply parabolic factorizations to the problem of bounded generation.
-The main result of this section gives an upper bound on the width of $\E(\Phi, R)$ in terms of Tits generators and is, thus,
- a quantitative analogue of \cite[Theorem~3.4]{S} and a relative analogue of the results of~\cite{VseUnitrZ1p, VavSmSuUnitrEng}.
+For a group $G$ denote by $W(G, X)$ \emph{the width of $G$ with respect to a generating set $X \subseteq G$}, i.\,e. the smallest natural number $N$ 
+such that every element of $G$ is a product of at most $N$ elements of $X$ or their inverses.
 
@@
 \end{proof}
-The above lemmas together with \cref{cor:bass-kolster-count,thm:Gauss} give the following.
+The above lemmas together with \cref{cor:bass-kolster-count,thm:Gauss} imply the following result
+ which is a quantitative analogue of \cite[Theorem~3.4]{S} and an analogue of the results of~\cite{VseUnitrZ1p, VavSmSuUnitrEng, Tavgen91} for relative groups.
 \begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.
@@
 \end{thm}
-Here $W(G, X)$ denotes \emph{the width of $G$ with respect to a generating set $X$}, i.\,e.
-the smallest natural number $N$ such that every element of $G$ is a product of at most $N$ elements of $X$ or their inverses.
 

### 2018-01-19 paper.tex
Minor language fixes

@@
 \begin{proof}
-Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence a fortiori it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
-Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r, s\}}, R)$, we obtain the assertion of the lemma for $\alpha \in \Delta_{r, s}$.
-
-Now if $\alpha$ lies in $\Phi^+ \setminus (\Sigma_r^+ \cap \Sigma_s^+)$, then it is contained either in $\Delta_r$ or in $\Delta_s$.
+Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
+Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r, s\}}, R)$, we obtain the result for $\alpha \in \Delta_{r, s}$.
+
+Now if $\alpha$ lies in $\Phi^+ \setminus (\Sigma_r^+ \cap \Sigma_s^+)$, it is contained either in $\Delta_r$ or $\Delta_s$.
 Assume, for example, the latter. By the Levi decomposition we have $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$,
@@
 
-Denote by $L_{rs}$ the set consisting of all elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
+Denote by $L_{rs}$ the set consisting of elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
 It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
@@
 
-The next goal is to demonstrate the inclusion $\U(\Sigma_s^+, R) \subseteq N_{rs}$ (which implies $\EP_s(R) \subseteq N_{rs}$).
+Our next goal is to demonstrate the inclusion $\U(\Sigma_s^+, R) \subseteq N_{rs}$ (which would imply $\EP_s(R) \subseteq N_{rs}$).
 All the possibilities for $\Phi$, $s$ and $r$ fall into one of the following three cases:
@@
   In this case all the roots of $\Sigma^+_s$ have the same $s$-shape and length, hence the assertion follows from \cref{item-trans2}, \eqref{rel:NnormL} and the fact that we already have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
- \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case, we get that $N_{rs}$ contains the subgroup generated by the root subgroups $X_\alpha(R)$, where $\alpha$ varies over long roots of $\Sigma_s^+$.
+ \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case, we get that $N_{rs}$ contains the subgroup generated by the root subgroups $X_\alpha(R)$, where $\alpha$ varies over the long roots of $\Sigma_s^+$.
   It remains to prove the inclusion $X_{1, 0}(R) \subset N_{rs}$.
-  By Chevalley commutator formula, we get
+  From Chevalley commutator formula we obtain
 \begin{equation*} \label{rel:CCF-specBC}
@@
 \end{equation*}
-  Since $X_{2, 0}(R)$ and $X_{1, -2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1, 0}(R) \subseteq N_{rs}$ follows.
+  Since $X_{2, 0}(R)$, $X_{1, -2}(R)$ and $X_{1,2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1, 0}(R) \subseteq N_{rs}$ follows.
  \item \textit{Case $\Phi = \rC_\ell, \rF_4$.}
  We settle these remaining cases in \cref{lemma:DVST}, where we invoke the stability conditions one more time. 
- In fact, we prove a stronger result, namely that $N_{rs}$ contains $X_{-\alpha\ssub{s}}(R)$ and, consequently, $N_{rs} = \E(\Phi, R)$.
+ In fact, we prove a stronger assertion, namely that $N_{rs}$ contains $X_{-\alpha\ssub{s}}(R)$ and, consequently, that $N_{rs} = \E(\Phi, R)$.
 \end{enumerate}
@@
 In view of \cite[Theorem~3.4]{S} to prove the theorem it suffices to show that $L_{rs}$ contains the generating set $\mathcal{Z}(\Sigma_s^-)$ of $\E(\Phi, R, I)$.
-From the inclusion $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)}$ and \eqref{rel:NnormL} it follows that we only have to show that $\mathcal{X} \subseteq L_{rs}$.
-
-The last inclusion follows from the same transitivity argument as above and the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
-For $\Phi=\rB_\ell$ one has to once again apply the Chevalley commutator formula:
+From the inclusion $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)}$ and \eqref{rel:NnormL} it follows that we only need to verify that $\mathcal{X} \subseteq L_{rs}$.
+In turn, the last inclusion follows from the same transitivity argument as above if we use the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
+For $\Phi=\rB_\ell$ we need to apply Chevalley commutator formula once again:
 \[ X_{0, 1}(I) \subseteq X_{2, 1}(I) \cdot X_{2, 1}(I)^{x_{0, 2}(1)} \cdot X_{-2, 1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
@@
 Recall from~\cite{LNS11, V13} that a Chevalley group over a field $\G(\Phi, F)$ can be presented as a product of at most $3|\Phi^+|$ of its subgroups $\SL(2, F)$.
-As an easy corollary of relative Bass--Kolster decomposition we show that similar decomposition exists in the relative situation and for even larger class of rings.
+As an easy corollary of the relative Bass--Kolster decomposition we get that a similar factorization exists for relative groups over a rather general class of commutative rings.
 \begin{thm}\label{thm:SL2width}

### 2018-01-21 paper.tex
Fixed misprints

@@
 Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot C$.
-By \cref{item:asrUnipC} (in the case $\Phi=\rC_\ell$) or \cref{cor:embeddingBD} (in the case $\Phi=\rF_4$), applied to the subgroup $\G(\Delta_s, R, I)$,
+Applying \cref{item:asrUnipC} or \cref{cor:embeddingBD} (in the cases $\Phi=\rC_\ell$ or $\Phi=\rF_4$, respectively), %to the subgroup $\G(\Delta_s, R, I)$,
 we find for every $g \in \EP_s(R, I)$ an element $x \in \U(\Sigma_r^+ \cap \Delta_s, I)$ such that $xg \in C$.  
-Notice that one immediately gets the equality $A_{rs} = A'$ from this.
-Indeed, for $g\in \EP_s(R, I)$ one has
+Notice that the equality $A_{rs} = A'$ follows from this, indeed, for $g\in \EP_s(R, I)$ one has
 \begin{equation*} \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq 
@@
 
-By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s^+ \cap \Delta_r, I)$ such that $(y \cdot g)_{\varpi_s, \varpi_s - \alpha_s} = 0$.
+By the definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s^+ \cap \Delta_r, I)$ such that $(y \cdot g)_{\varpi_s, \varpi_s - \alpha_s} = 0$.
 Consequently, for every $g\in C$ one has
@@
 From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1 \coloneqq (yg)^{x_{-\alpha_s}(\xi)}$
-satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_s^-, I)$, $h \in \EP_1(R, I)$.
+satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_s^-, I)$, $h \in \EP_s(R, I)$.
 Consequently, one has
 \begin{multline*} {A_{rs}}^{X_{-\alpha_{s}}(R)} \subseteq \EP_r(R, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_r^-, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_s^-, I) \cdot \EP_s(R, I) \subseteq \\
-\subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_s(R, I) \subseteq A_{rs}, \end{multline*}
+\subseteq \EP_r(R, I) \cdot \U(\Phi^-, I) \cdot \EP_s(R, I) \subseteq A_{rs}, \end{multline*}
 as claimed.

### 2018-01-24 paper.tex
Minor fixes in Corollary 3.6

@@
 \begin{cor} \label{cor:embeddingBD}
- Denote by $i$ the standard embedding $\G(\rB_{\ell-1}, R, I) \hookrightarrow \G(\rD_\ell, R, I)$. 
+ Denote by $i$ the standard embedding $\G(\rB_{\ell-1}, R) \hookrightarrow \G(\rD_\ell, R)$. 
  If $\asr(I) \leqslant \ell-1$, then for every $I$-unimodular column $v \in \Ums(2\ell, I)$ there exists $g \in \U(\Sigma_{\ell-1}^+, I) \leqslant \E(\rB_{\ell-1}, R, I)$ such that
@@
  The assertion follows from the fact that for every $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that $uu'$ lies in the image of $i$. 
- Indeed, denote by $\sigma$ the automorphism of $\E(\rD_\ell, R)$ induced by the symmetry of its Dynkin diagram, and decompose $u$ into the product $u_1 \cdot u_2$, where $u_1 \in \U(\Sigma_\ell^+\cap\Delta_{\ell-1}, I)$ and $u_2 \in \U(\Sigma_\ell^+ \cap \Sigma_{\ell-1}^+, I)$.
- Then one takes $u' = \sigma(u_1)$.
-
- Now by \cref{item:asrUnipD} one finds a suitable $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ which makes the upper half unimodular,
- and since $u'$ lies in $\G(\Delta_\ell, R, I)$, the upper half remains unimodular.
+ Indeed, denote by $\sigma$ the automorphism of $\E(\rD_\ell, R)$ induced by the symmetry of its Dynkin diagram.
+ Write $u$ as a product $u_1 \cdot u_2$, where $u_1 \in \U(\Sigma_\ell^+\cap\Delta_{\ell-1}, I)$ and $u_2 \in \U(\Sigma_\ell^+ \cap \Sigma_{\ell-1}^+, I)$ and set $u' = \sigma(u_1)$.
+
+ Now by \cref{item:asrUnipD} one finds a suitable $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ such that $(u\cdot v)^+$ is unimodular.
+ Since $u'$ lies in $\G(\Delta_\ell, R, I)$ the column $(uu' \cdot v)^+$ is also unimodular, as claimed.
 \end{proof}

### 2018-01-26 paper.tex
Removed incorrect statement

@@
 \begin{thm}[Dennis--Vaserstein decomposition]\label{thm:DennisVaserstein}
-Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geqslant 2$ and let $\{ r, s \}$ be a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
+Let $\Phi$ be a either a classical irreducible root system of rank $\ell\geqslant 2$ or $\Phi=\rE_7, \rE_8$. 
+Let $\{ r, s \}$ be a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
 Denote the distance between $r$ and $s$ by $d$.
@@
  \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
- \item $\asr(I) \leqslant d$ for $\Phi=\rF_4$.
 \end{thmlist}
@@
 
-\begin{cor} \label{cor:embeddingBD}
- Denote by $i$ the standard embedding $\G(\rB_{\ell-1}, R) \hookrightarrow \G(\rD_\ell, R)$. 
- If $\asr(I) \leqslant \ell-1$, then for every $I$-unimodular column $v \in \Ums(2\ell, I)$ there exists $g \in \U(\Sigma_{\ell-1}^+, I) \leqslant \E(\rB_{\ell-1}, R, I)$ such that
- the upper half of the vector $i(g) \cdot v$ forms an $I$-unimodular column of height $\ell$.
-\end{cor}
-\begin{proof}
- The assertion follows from the fact that for every $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ one can find $u' \in \G(\Delta_\ell, R, I)$ such that $uu'$ lies in the image of $i$. 
- Indeed, denote by $\sigma$ the automorphism of $\E(\rD_\ell, R)$ induced by the symmetry of its Dynkin diagram.
- Write $u$ as a product $u_1 \cdot u_2$, where $u_1 \in \U(\Sigma_\ell^+\cap\Delta_{\ell-1}, I)$ and $u_2 \in \U(\Sigma_\ell^+ \cap \Sigma_{\ell-1}^+, I)$ and set $u' = \sigma(u_1)$.
-
- Now by \cref{item:asrUnipD} one finds a suitable $u \in \U(\Sigma_\ell^+, I) \leqslant \E(\rD_\ell, R, I)$ such that $(u\cdot v)^+$ is unimodular.
- Since $u'$ lies in $\G(\Delta_\ell, R, I)$ the column $(uu' \cdot v)^+$ is also unimodular, as claimed.
-\end{proof}
-
 \begin{lemma} \label{lemma:uraction} 
@@
 \rE_\ell, \ \ell=6, 7                  & \ell &2      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
-\rE_\ell, \ \ell=6, 7                  & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \\
-\rF_4                                & 4    &1     & 26             & \text{minimal}       & \rC_3                     & 6              & 3\end{array}\]
+\rE_\ell, \ \ell=6, 7                  & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \end{array}\]
  \caption{List of representations used in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
@@
   Since $X_{2, 0}(R)$, $X_{1, -2}(R)$ and $X_{1,2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1, 0}(R) \subseteq N_{rs}$ follows.
- \item \textit{Case $\Phi = \rC_\ell, \rF_4$.}
- We settle these remaining cases in \cref{lemma:DVST}, where we invoke the stability conditions one more time. 
+ \item \textit{Case $\Phi = \rC_\ell$.}
+ We settle the remaining case in \cref{lemma:DVST}, where we invoke the stability conditions one more time. 
  In fact, we prove a stronger assertion, namely that $N_{rs}$ contains $X_{-\alpha\ssub{s}}(R)$ and, consequently, that $N_{rs} = \E(\Phi, R)$.
@@
 \begin{lemma}\label{lemma:DVST}
-Assume that one of the following holds:
-\begin{lemlist}
- \item \label{lemma:DVcaseCl} $\Phi=\rC_\ell$ and $\sr(I) \leq \ell-1$;
- \item \label{lemma:DVcaseF4} $\Phi=\rF_4$ and $\asr(I) \leq 3$.
-\end{lemlist}
-Then one has $X_{-\alpha_s}(R) \subseteq N_{rs}$.
-\end{lemma}
-\begin{proof}
-Consider the subset $C \subseteq \EP_s(R, I)$, consisting of the elements satisfying the following condition:
-\begin{itemize}
- \item \textsc{Case $\Phi=\rC_\ell$.} Matrix entries $(g_{i, 2})$, $i=2, \ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
- \item \textsc{Case $\Phi=\rF_4$.} Matrix entries $(g_{\lambda, \lambda}, \ldots, g_{\lambda, \lambda - \alpha_3 - \alpha_2 - \alpha_1})$, where $\lambda = \varpi_4 - \alpha_4$ (see~\cite[Fig.~26]{PSV98}),
-                                     form an $I$-unimodular column of height $4$. \end{itemize}
+Assume that $\Phi=\rC_\ell$ and $\sr(I) \leq \ell-1$, then $X_{-\alpha_s}(R) \subseteq N_{rs}$.
+\end{lemma}
+\begin{proof}
+Denoteb by $C$ the set consisting of elements $g \in \EP_s(R, I)$ for which matrix entries $(g_{i, 2})$, $i=2, \ldots, \ell$ form an $I$-unimodular column of height $\ell-1$
 
 Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot C$.
-Applying \cref{item:asrUnipC} or \cref{cor:embeddingBD} (in the cases $\Phi=\rC_\ell$ or $\Phi=\rF_4$, respectively), %to the subgroup $\G(\Delta_s, R, I)$,
-we find for every $g \in \EP_s(R, I)$ an element $x \in \U(\Sigma_r^+ \cap \Delta_s, I)$ such that $xg \in C$.  
+Applying \cref{item:asrUnipC} we find for every $g \in \EP_s(R, I)$ an element $x \in \U(\Sigma_r^+ \cap \Delta_s, I)$ such that $xg \in C$.  
 Notice that the equality $A_{rs} = A'$ follows from this, indeed, for $g\in \EP_s(R, I)$ one has

### 2018-01-30 paper.tex
Greatly improved readability of the proof of Theorem 1

@@
 \[ \Sigma^\pm_{I \cup J} = \Sigma^\pm_I\cup\Sigma^\pm_J, \quad \Delta_{I\cup J} = \Delta_I \cap \Delta_J. \]
-We omit curly braces in the above notations when $J$ is a one- or two-element set, e.\,g.
-$\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
-We call $\shape(\{s\}, \beta)$ the $s$-shape of $\beta$.
+We omit curly braces in the above notations when $J$ is a one- or two-element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
+We call $\shape(\{s\}, \beta)$ simply the $s$-shape of $\beta$.
 
@@
 
-Denote by $N_{rs}$ the submonoid of $\E(\Phi, R)$, consisting of the elements which normalize the subset $A_{rs}$, i.\,e.
-\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \subseteq A_{rs} \right\}. \]
+Denote by $N_{rs}$ the subgroup of $\E(\Phi, R)$, consisting of elements normalizing the subset $A_{rs}$, i.\,e.
+\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \cup g^{-1} \cdot A_{rs} \cdot g \subseteq A_{rs}\right\}. \]
 
 \begin{lemma}\label{lemma:dv-normal} 
-For every $\alpha \in \Delta_{r, s} \cup (\Phi^+ \setminus (\Sigma^+_r \cap \Sigma^+_s))$ one has $X_\alpha(R) \subseteq N_{rs}$. \end{lemma}
+For every $\alpha \in \Delta_{r, s} \cup \Phi^+ $ one has $X_\alpha(R) \subseteq N_{rs}$. \end{lemma}
 \begin{proof}
 Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
-Since $\U(\Sigma_r^- \cap \Sigma_s^-, I)$ is normalized by $\E(\Delta_{\{r, s\}}, R)$, we obtain the result for $\alpha \in \Delta_{r, s}$.
+Since $\E(\Delta_{r, s}, R)$ normalizes $\U(\Sigma_r^- \cap \Sigma_s^-, I)$, we obtain the assertion for $\alpha \in \Delta_{r, s}$.
 
-Now if $\alpha$ lies in $\Phi^+ \setminus (\Sigma_r^+ \cap \Sigma_s^+)$, it is contained either in $\Delta_r$ or $\Delta_s$.
-Assume, for example, the latter. By the Levi decomposition we have $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$,
-which again implies the assertion of the lemma.
+Now let $\alpha$ be a positive simple root. It is clear that $\alpha$ lies either in $\Delta_r$ or $\Delta_s$.
+Assume, for example, the latter. From the Levi decomposition we get $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$,
+consequently $X_{\alpha}(R) \subseteq N_{rs}$.
+Now it is clear that $N_{rs}$ contains the subgroup $\U(\Phi^+, R)$ generated by $X_{\alpha}(R)$, $\alpha\in\Pi$, which implies the assertion.
+%TODO: Why the positive unipotent radical is generated by simple root subgroups???
 \end{proof}
@@
 
-Denote by $L_{rs}$ the set consisting of elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
+Denote by $L_{rs}$ the monoid consisting of elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
 It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
-\begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
+\begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \cdot g^{-1} \cdot g \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
 
-The first step of the proof is to show that $N_{rs}$ contains sufficiently many elements. 
-This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke the stability conditions for the first time.
-We show that $N_{rs}$ contains the root subgroup $X_{-\alpha\ssub{r}}(R)$, which together with \cref{lemma:dv-normal} and \cref{item-egen} immediately implies that $N_{rs}$ contains the Levi subgroup $\E(\Delta_s, R)$ and hence the extended Weyl group $\widetilde{W}(\Delta_s)$.
+First of all notice that $N_{rs}$ is sufficiently large.
+\cref{lemma:Stein_reduction} below guarantees that $N_{rs}$ contains the root subgroup $X_{-\alpha_{r}}(R)$, which together with~\cref{lemma:dv-normal} 
+ implies that $\EP_s(R) \subseteq N_{rs}$ and consequently that $\EP_s(R, I) \subseteq L_{rs}$. Indeed for $g\in \EP_s(R, I) \subseteq \EP_s(R)$ one has
+$g \cdot L_{rs} = g \cdot L_{rs} \cdot g^{-1} \cdot g \subseteq L_{rs} \cdot g \subseteq L_{rs}.$
 
-Our next goal is to demonstrate the inclusion $\U(\Sigma_s^+, R) \subseteq N_{rs}$ (which would imply $\EP_s(R) \subseteq N_{rs}$).
+%This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke the stability conditions for the first time.
+%which together with \cref{lemma:dv-normal} implies that $N_{rs}$ contains the Levi subgroup $\E(\Delta_s, R)$.
+% 
+ %$\EP_s(R) \subseteq N_{rs}$
+
+The next step of the proof is to show that $\U(\Sigma_s^-, I) \subseteq L_{rs}$.
 All the possibilities for $\Phi$, $s$ and $r$ fall into one of the following three cases:
@@
  \item \textit{Case $m_s(\alpha_{\mathrm{max}})=1$ and $\Phi$ is simply laced.}
-  In this case all the roots of $\Sigma^+_s$ have the same $s$-shape and length, hence the assertion follows from \cref{item-trans2}, \eqref{rel:NnormL} and the fact that we already have the inclusion $X_{\alpha_s}(R) \subseteq N_{rs}$.
- \item \textit{Case $\Phi = \rB_\ell$.} Using the argument from the previous case, we get that $N_{rs}$ contains the subgroup generated by the root subgroups $X_\alpha(R)$, where $\alpha$ varies over the long roots of $\Sigma_s^+$.
-  It remains to prove the inclusion $X_{1, 0}(R) \subset N_{rs}$.
-  From Chevalley commutator formula we obtain
-\begin{equation*} \label{rel:CCF-specBC}
-x_{1, 0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1, -2}(-a b^2).
-\end{equation*}
-  Since $X_{2, 0}(R)$, $X_{1, -2}(R)$ and $X_{1,2}(R)$ are contained in $N_{rs}$, the inclusion $X_{1, 0}(R) \subseteq N_{rs}$ follows.
- \item \textit{Case $\Phi = \rC_\ell$.}
- We settle the remaining case in \cref{lemma:DVST}, where we invoke the stability conditions one more time. 
- In fact, we prove a stronger assertion, namely that $N_{rs}$ contains $X_{-\alpha\ssub{s}}(R)$ and, consequently, that $N_{rs} = \E(\Phi, R)$.
+  In this case all the roots of $\Sigma^-_s$ have the same $s$-shape and length.
+  Since $\widetilde{W}(\Delta_s) \subseteq \E(\Delta_s, R) \subseteq N_{rs}$ and $X_{-\alpha_s}(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$,
+   the required inclusion $\U(\Sigma_s^-, I) \subseteq L_{rs}$ follows from \cref{item-trans2}.  
+ \item \textit{Case $\Phi = \rB_\ell$, $s=1$, $r=\ell$.} 
+  The argument from the previous case shows that $L_{\ell,1}$ contains root subgroups $X_\alpha(I)$, where $\alpha$ varies over the long roots of $\Sigma_1^-$. 
+  The inclusion $X_{0, 1}(I) \subseteq L_{\ell, 1}$ for the remaining short root follows from inclusions $X_{-1, 2}(I) \cup X_{2, 1}(I) \subseteq L_{\ell,1}$, $X_{2, 0}(R) \subseteq N_{\ell,1}$
+  using Chevalley commutator formula $x_{0, 1}(-ab) = [x_{-1,2}(a),\, x_{2,0}(b)] \cdot x_{2,1}(ab^2).$
+ \item \textit{Case $\Phi = \rC_\ell$, $s=1$, $r=\ell$.} 
+  Similarly, one can show that $L_{\ell,1}$ contains $X_\alpha(I)$ for all short $\alpha \in \Sigma_1^-$.
+  However, the inclusion $X_{-1, 1}(I) \subseteq L_{\ell, 1}$ for the remaining long root does not immediately follow from commutator formulae.
+  To verify it we invoke stability conditions once again.
+  From~\cref{lemma:DVST} we obtain that $N_{\ell, 1}$ contains $X_{-\alpha\ssub{1}}(R)$ and therefore coincides with the whole $\E(\Phi, R)$, which gives the required assertion.
 \end{enumerate}
 
-In view of \cite[Theorem~3.4]{S} to prove the theorem it suffices to show that $L_{rs}$ contains the generating set $\mathcal{Z}(\Sigma_s^-)$ of $\E(\Phi, R, I)$.
-From the inclusion $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)}$ and \eqref{rel:NnormL} it follows that we only need to verify that $\mathcal{X} \subseteq L_{rs}$.
-In turn, the last inclusion follows from the same transitivity argument as above if we use the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
-For $\Phi=\rB_\ell$ we need to apply Chevalley commutator formula once again:
-\[ X_{0, 1}(I) \subseteq X_{2, 1}(I) \cdot X_{2, 1}(I)^{x_{0, 2}(1)} \cdot X_{-2, 1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
+Thus, we have just shown that $\mathcal{X}\subseteq L_{rs}$. 
+Recall from~\cite[Theorem~3.4]{S} that the group $\E(\Phi, R, I)$ is generated by $\mathcal{Z}(\Sigma_s^-)$.
+On the other hand, from $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)} \subseteq L_{rs}^{N_{rs}} \subseteq L_{rs}$ we conclude that 
+ $\E(\Phi, R, I) \subseteq L_{rs}$, which implies the assertion of the theorem.
+%Thus, to prove our assertion it suffices to show that $L_{rs}$ contains $\mathcal{Z}(\Sigma_s^-)$.
+%From the inclusion  and \eqref{rel:NnormL} it follows that we only need to verify the inclusion $\mathcal{X} \subseteq L_{rs}$.
+%In turn, the last inclusion follows from the same transitivity argument as above if we use the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
+%For $\Phi=\rB_\ell$ we need to apply Chevalley commutator formula once again:
+%\[ X_{0, 1}(I) \subseteq X_{2, 1}(I) \cdot X_{2, 1}(I)^{x_{0, 2}(1)} \cdot X_{-2, 1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
 \end{proof}

### 2018-01-30 paper.tex
Invented simpler proof in the case F_4

@@
  \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
+ \item $\sr(I) \leqslant d$ for $\Phi = \rF_4$ with $\{r,s\} = \{1, 4\}$.
 \end{thmlist}
@@
 \rE_\ell, \ \ell=6, 7                  & \ell &2      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
-\rE_\ell, \ \ell=6, 7                  & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1  \end{array}\]
+\rE_\ell, \ \ell=6, 7                  & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1 \\
+\rF_4,                                 & 4    & 1     & 26              & \text{minimal}       & \rC_{3}                  & 6              & 3 \end{array}\]
  \caption{List of representations used in the proof of \cref{thm:DennisVaserstein}.} \label{table:dv-reps}
@@
 
-First of all notice that $N_{rs}$ is sufficiently large.
 \cref{lemma:Stein_reduction} below guarantees that $N_{rs}$ contains the root subgroup $X_{-\alpha_{r}}(R)$, which together with~\cref{lemma:dv-normal} 
@@
  \item \textit{Case $\Phi = \rB_\ell$, $s=1$, $r=\ell$.} 
-  The argument from the previous case shows that $L_{\ell,1}$ contains root subgroups $X_\alpha(I)$, where $\alpha$ varies over the long roots of $\Sigma_1^-$. 
-  The inclusion $X_{0, 1}(I) \subseteq L_{\ell, 1}$ for the remaining short root follows from inclusions $X_{-1, 2}(I) \cup X_{2, 1}(I) \subseteq L_{\ell,1}$, $X_{2, 0}(R) \subseteq N_{\ell,1}$
-  using Chevalley commutator formula $x_{0, 1}(-ab) = [x_{-1,2}(a),\, x_{2,0}(b)] \cdot x_{2,1}(ab^2).$
+  The argument from the previous case shows that $L_{rs}$ contains root subgroups $X_\alpha(I)$, where $\alpha$ varies over the long roots of $\Sigma_1^-$.
+  Consider the following two roots of $\Phi$:
+  \begin{equation}\nonumber \beta = \alpha_2 + \ldots + \alpha_\ell,\ \gamma = -\alpha_1 - 2\alpha_2 - \ldots -2\alpha_\ell.\end{equation}
+  We need to verify the inclusion $X_{\beta+\gamma}(I) \subseteq L_{rs}$ for the remaining short root of $\Sigma_1^-$.
+  But the latter follows from $X_{\gamma}(I) \cup X_{-\alpha_1}(I) \subseteq L_{rs}$, $X_{\beta}(R) \subseteq N_{rs}$ using Chevalley commutator formula:
+  \begin{equation} \label{eq:CCF} x_{\beta+\gamma}(-ab) = [x_{\gamma}(a),\, x_{\beta}(b)] \cdot x_{\gamma + 2\beta}(ab^2). \end{equation}
+ \item \textit{Case $\Phi = \rF_4$, $s=4$, $r=1$.} In this case there are three possibilities for the $s$-shape and length of a root from $\Sigma_4^-$: 
+ \begin{itemize}
+  \item $\shape(s, \alpha) = 1$, $\alpha$ is short (there are 8 such roots);
+  \item $\shape(s, \alpha) = 2$, $\alpha$ is long (there are 6 such roots);
+  \item $\shape(s, \alpha) = 2$, $\alpha$ is short (there is only one such root: $\delta = -\alpha_1 -2\alpha_2-3\alpha_3-2\alpha_4$).
+ \end{itemize}
+ Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, we have the neccessary inclusions for the root subgroups of corresponding type via the same argument as above.
+ To verify the inclusion for the remaining short root subgroup invoke~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{\mathrm{max}}$. 
  \item \textit{Case $\Phi = \rC_\ell$, $s=1$, $r=\ell$.} 
-  Similarly, one can show that $L_{\ell,1}$ contains $X_\alpha(I)$ for all short $\alpha \in \Sigma_1^-$.
-  However, the inclusion $X_{-1, 1}(I) \subseteq L_{\ell, 1}$ for the remaining long root does not immediately follow from commutator formulae.
-  To verify it we invoke stability conditions once again.
-  From~\cref{lemma:DVST} we obtain that $N_{\ell, 1}$ contains $X_{-\alpha\ssub{1}}(R)$ and therefore coincides with the whole $\E(\Phi, R)$, which gives the required assertion.
+  Similarly, one can show that $L_{rs}$ contains $X_\alpha(I)$ for all short $\alpha \in \Sigma_1^-$.
+  However, the inclusion $X_{-1, 1}(I) \subseteq L_{rs}$ for the remaining long root does not immediately follow from commutator formulae and to verify it we need to invoke stability conditions once again.
+  From~\cref{lemma:DVST} we obtain that $N_{rs}$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$, which gives the required assertion.
 \end{enumerate}
@@
 On the other hand, from $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)} \subseteq L_{rs}^{N_{rs}} \subseteq L_{rs}$ we conclude that 
- $\E(\Phi, R, I) \subseteq L_{rs}$, which implies the assertion of the theorem.
+ $\E(\Phi, R, I) \subseteq L_{rs}$, which completes the proof.
 %Thus, to prove our assertion it suffices to show that $L_{rs}$ contains $\mathcal{Z}(\Sigma_s^-)$.

### 2018-02-02 paper.tex
More work on Theorem 1

@@
 \begin{thm}[Dennis--Vaserstein decomposition]\label{thm:DennisVaserstein}
-Let $\Phi$ be a either a classical irreducible root system of rank $\ell\geqslant 2$ or $\Phi=\rE_7, \rE_8$. 
-Let $\{ r, s \}$ be a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
-Denote the distance between $r$ and $s$ by $d$.
+Let $\Phi$ be an irreducible root system of rank $\ell\geqslant 2$ and $\{ r, s \}$ be a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
+Denote by $d$ the distance between $r$ and $s$ on the Dynkin diagram.
 Assume that $\Phi$, $I$ and $\{r, s\}$ satisfy either of the following assumptions:
 \begin{thmlist}
- \item $\sr(I) \leqslant d$ for classical $\Phi$,
- \item $\sr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{ 2, \ell \}$,
  \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
- \item $\sr(I) \leqslant d$ for $\Phi = \rF_4$ with $\{r,s\} = \{1, 4\}$.
+ \item $\sr(I) \leqslant d$ otherwise.
 \end{thmlist}
@@
 In what follows, $r$ and $s$ are two distinct integers such that $1 \leqslant r, s \leqslant \ell$.
+We may assume $\ell>2$ because otherwise $\sr(I)=1$ and \cref{thm:DennisVaserstein} is a corollary of the stronger Gauss decomposition (see~\cref{thm:srRI1} below).
 From the Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
@@
 
-Denote by $N_{rs}$ the subgroup of $\E(\Phi, R)$, consisting of elements normalizing the subset $A_{rs}$, i.\,e.
+Denote by $N_{rs}$ the subgroup of $\E(\Phi, R)$, consisting of elements normalizing the above subset:
 \[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \cup g^{-1} \cdot A_{rs} \cdot g \subseteq A_{rs}\right\}. \]
@@
 \begin{proof} [Proof of \cref{thm:DennisVaserstein}]
-Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the possibilities for $\Phi$, $s$, $r$ listed in~\cref{table:dv-reps}.
+Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$: % listed in~\cref{table:dv-reps}.
 \begin{table}[htb]
@@
 \rD_\ell, \ \ell\geqslant 4           & \ell &\ell-1 & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
-\rE_\ell, \ \ell=6, 7                  & \ell &2      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
-\rE_\ell, \ \ell=6, 7                  & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1 \\
+\rE_\ell, \ \ell=6, 7, 8              & \ell &2      & 27, 56, 248    & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
+\rE_\ell, \ \ell=6, 7, 8              & \ell &1      & 27, 56, 248    & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1 \\
 \rF_4,                                 & 4    & 1     & 26             & \text{minimal}       & \rC_{3}                  & 6              & 3 \end{array}\]
@@
 
-%This is accomplished in~\cref{lemma:Stein_reduction} below, where we invoke the stability conditions for the first time.
-%which together with \cref{lemma:dv-normal} implies that $N_{rs}$ contains the Levi subgroup $\E(\Delta_s, R)$.
-% 
- %$\EP_s(R) \subseteq N_{rs}$
-
-The next step of the proof is to show that $\U(\Sigma_s^-, I) \subseteq L_{rs}$.
-All the possibilities for $\Phi$, $s$ and $r$ fall into one of the following three cases:
+Our next goal is to verify the inclusion $\U(\Sigma_s^-, I) \subseteq L_{rs}$. Our main tools will be formula~\eqref{rel:NnormL} and \cref{item-trans2}.
+Since $\widetilde{W}(\Delta_s) \subseteq \E(\Delta_s, R) \subseteq N_{rs}$ and 
+ $X_{\alpha}(I) \subseteq L_{rs}$ for $\alpha \in \Sigma^-_s\cap \Delta_r$, 
+we immediately obtain that $L_{rs}$ contains root subgroups $X_\alpha(I)$ corresponding to $\alpha$
+ lying in the orbit $O = W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
+Thus, we are left to consider four cases in which $O$ does not coincide with $\Sigma^-_s$. 
+%All the possibilities for $\Phi$, $s$ and $r$ for which $O \neq \Sigma_s^-$ fall into one of the following cases:
 \begin{enumerate}
- \item \textit{Case $m_s(\alpha_{\mathrm{max}})=1$ and $\Phi$ is simply laced.}
-  In this case all the roots of $\Sigma^-_s$ have the same $s$-shape and length.
-  Since $\widetilde{W}(\Delta_s) \subseteq \E(\Delta_s, R) \subseteq N_{rs}$ and $X_{-\alpha_s}(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$,
-   the required inclusion $\U(\Sigma_s^-, I) \subseteq L_{rs}$ follows from \cref{item-trans2}.  
+ %\item \textit{Case $m_s(\alpha_{\mathrm{max}})=1$ and $\Phi$ is simply laced.}  In this case $O = \Sigma_s^-$ and there is nothing else to prove.
+ \item \textit{Case $\Phi = \rE_8$, $s=8$, $r=1,2$.} 
+ %The argument from the previous case shows that $L_{rs}$ contains root subgroups $X_\alpha(I)$, where $\alpha$ varies over the roots of $\Sigma_8^-$ having $8$-shape $1$.
+ In this case there is only one root in $\Sigma_8^-$ not lying in $O$, namely $-\alpha_\mathrm{max}$ with $\shape(8,-\alpha_\mathrm{max}) = -2$.
+ Since $X_{-\alpha_8}(R) \subseteq N_{rs}$, $X_{\alpha_8-\alpha_\mathrm{max}}(I) \subseteq L_{rs}$ the desired inclusion
+  follows from Chevalley commutator formula $x_{\alpha_\mathrm{max}}(\pm ab)=[x_{\alpha_8-\alpha_\mathrm{max}}(a), x_{\alpha_8}(b)].$
+
  \item \textit{Case $\Phi = \rB_\ell$, $s=1$, $r=\ell$.} 
-  The argument from the previous case shows that $L_{rs}$ contains root subgroups $X_\alpha(I)$, where $\alpha$ varies over the long roots of $\Sigma_1^-$.
-  Consider the following two roots of $\Phi$:
+ In this case only the sole short root of $\Sigma_1^-$ is not contained in $O$. Consider the following two roots of $\Phi$:
  \begin{equation}\nonumber \beta = \alpha_2 + \ldots + \alpha_\ell,\ \gamma = -\alpha_1 - 2\alpha_2 - \ldots -2\alpha_\ell.\end{equation}
-  We need to verify the inclusion $X_{\beta+\gamma}(I) \subseteq L_{rs}$ for the remaining short root of $\Sigma_1^-$.
-  But the latter follows from $X_{\gamma}(I) \cup X_{-\alpha_1}(I) \subseteq L_{rs}$, $X_{\beta}(R) \subseteq N_{rs}$ using Chevalley commutator formula:
+ We need to verify $X_{\beta+\gamma}(I) \subseteq L_{rs}$, but this follows from $X_{\gamma}(I) \cup X_{-\alpha_1}(I) \subseteq L_{rs}$, $X_{\beta}(R) \subseteq N_{rs}$ using Chevalley commutator formula:
   \begin{equation} \label{eq:CCF} x_{\beta+\gamma}(-ab) = [x_{\gamma}(a),\, x_{\beta}(b)] \cdot x_{\gamma + 2\beta}(ab^2). \end{equation}
@@
  \begin{itemize}
-  \item $\shape(s, \alpha) = 1$, $\alpha$ is short (there are 8 such roots);
-  \item $\shape(s, \alpha) = 2$, $\alpha$ is long (there are 6 such roots);
-  \item $\shape(s, \alpha) = 2$, $\alpha$ is short (there is only one such root: $\delta = -\alpha_1 -2\alpha_2-3\alpha_3-2\alpha_4$).
+  \item $\shape(4, \alpha) = 1$, $\alpha$ is short (there are 8 such roots);
+  \item $\shape(4, \alpha) = 2$, $\alpha$ is long (there are 6 such roots);
+  \item $\shape(4, \alpha) = 2$, $\alpha$ is short (there is only one such root: $\delta = -\alpha_1 -2\alpha_2-3\alpha_3-2\alpha_4$).
  \end{itemize}
- Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, we have the neccessary inclusions for the root subgroups of corresponding type via the same argument as above.
- To verify the inclusion for the remaining short root subgroup invoke~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{\mathrm{max}}$. 
+ Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, we 
+  only need to verify $X_\delta(I) \subseteq L_{rs}$, but the latter again follows from~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{\mathrm{max}}$. 
  \item \textit{Case $\Phi = \rC_\ell$, $s=1$, $r=\ell$.} 
-  Similarly, one can show that $L_{rs}$ contains $X_\alpha(I)$ for all short $\alpha \in \Sigma_1^-$.
-  However, the inclusion $X_{-1, 1}(I) \subseteq L_{rs}$ for the remaining long root does not immediately follow from commutator formulae and to verify it we need to invoke stability conditions once again.
-  From~\cref{lemma:DVST} we obtain that $N_{rs}$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$, which gives the required assertion.
+  %Similarly, one can show that $L_{rs}$ contains $X_\alpha(I)$ for all short $\alpha \in \Sigma_1^-$.
+  In this case the inclusion $X_{-\alpha_\mathrm{max}}(I) \subseteq L_{rs}$ does not immediately follow from commutator formulae
+   and we need to invoke stability conditions once again.
+  From~\cref{lemma:DVST} we obtain that $N_{rs}$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$, which implies the assertion.
 \end{enumerate}
@@
 Denote by $(\pi', V')$ the irreducible component of the restriction of $\pi$ to $\G(\Delta_r, R)$ that contains the highest weight vector $v^+$ of $\pi$.
-In all the cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta, R)$.
+In all the cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta_r, R)$.
 Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$

### 2018-02-02 paper.tex
Minor fixes

@@
 
-\def\ssub#1{\mathchoice
-   {_{\lower2pt\hbox{$\scriptstyle #1$}}}
-   {_{\lower2pt\hbox{$\scriptstyle #1$}}}
-   {_{\lower1.5pt\hbox{$\scriptscriptstyle #1$}}}
-   {_{\!\lower1.5pt\hbox{$\scriptscriptstyle #1$}}}}
-
 \title[Decompositions of congruence subgroups of Chevalley groups]{Decompositions of congruence subgroups \\ of Chevalley groups}
@@
 w_\alpha(\varepsilon) x_{\beta}(\xi) w_\alpha(\varepsilon)^{-1} =
-x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\cdot\varepsilon^{-\langle\beta, \alpha \rangle}\xi\right), \quad \varepsilon\in R^*, \ \xi\in R.
+x_{\sigma_{\alpha}\beta} \left(\eta_{\alpha, \beta}\cdot\varepsilon^{-\langle\beta, \alpha \rangle}\xi\right), \quad \varepsilon\in R^*, \ \xi\in R.
 \end{equation}
@@
 \item \label{item-egen} The elementary group $\E(\Phi, R)$  is generated as an abstract group by the root subgroups $X_{\alpha}(R)$, $\alpha \in \Pi \cup -\Pi$.
-\item \label{item-trans2} Assume that $\alpha_s\in \Pi$ is a fundamental root of $\Phi$ such that $m_s(\alpha_\mathrm{max}) = 1$. 
+\item \label{item-trans2} Assume that $\alpha_s\in \Pi$ is a fundamental root of $\Phi$ such that $m_s(\alpha_{\max}) = 1$. 
 Then for $\alpha, \beta \in \Sigma^\pm_s$ of the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$. \end{lemlist}
@@
 Let $\pi$ be a basic fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
-Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then $g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
+Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi_{s}}=1$, then $g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
 \end{lemma}
@@
 \textsc{Case $\Phi=\rD_\ell$.} From the proof of \cref{item:asrUnipD} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.
-Clearly, for $v'' = z_{-\alpha\ssub{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$, hence by \cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
-$g'=h_2 \cdot z_{-\alpha\ssub{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fixes $v^+$. 
+Clearly, for $v'' = z_{-\alpha_{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$, hence by \cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
+$g'=h_2 \cdot z_{-\alpha_{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fixes $v^+$. 
 Using the Levi decomposition we can write $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
@@
 In what follows, $r$ and $s$ are two distinct integers such that $1 \leqslant r, s \leqslant \ell$.
-We may assume $\ell>2$ because otherwise $\sr(I)=1$ and \cref{thm:DennisVaserstein} is a corollary of the stronger Gauss decomposition (see~\cref{thm:srRI1} below).
+We may assume $\ell>2$ because otherwise $\sr(I)=1$ and \cref{thm:DennisVaserstein} follows the stronger Gauss decomposition (see~\cref{thm:srRI1} below).
 From the Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
@@
 Denote by $L_{rs}$ the monoid consisting of elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
-It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N\ssub{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
+It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N_{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
 \begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \cdot g^{-1} \cdot g \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
@@
 Thus, we are left to consider four cases in which $O$ does not coincide with $\Sigma^-_s$. 
-%All the possibilities for $\Phi$, $s$ and $r$ for which $O \neq \Sigma_s^-$ fall into one of the following cases:
 \begin{enumerate} 
- %\item \textit{Case $m_s(\alpha_{\mathrm{max}})=1$ and $\Phi$ is simply laced.}  In this case $O = \Sigma_s^-$ and there is nothing else to prove.
  \item \textit{Case $\Phi = \rE_8$, $s=8$, $r=1,2$.}  
- %The argument from the previous case shows that $L_{rs}$ contains root subgroups $X_\alpha(I)$, where $\alpha$ varies over the roots of $\Sigma_8^-$ having $8$-shape $1$.
- In this case there is only one root in $\Sigma_8^-$ not lying in $O$, namely $-\alpha_\mathrm{max}$ with $\shape(8,-\alpha_\mathrm{max}) = -2$.
- Since $X_{-\alpha_8}(R) \subseteq N_{rs}$, $X_{\alpha_8-\alpha_\mathrm{max}}(I) \subseteq L_{rs}$ the desired inclusion
-  follows from Chevalley commutator formula $x_{\alpha_\mathrm{max}}(\pm ab)=[x_{\alpha_8-\alpha_\mathrm{max}}(a), x_{\alpha_8}(b)].$
+ There is only one root in $\Sigma_8^-$ not lying in $O$, namely $-\alpha_{\max}$ with $\shape(8,-\alpha_{\max}) = -2$.
+ Since $X_{-\alpha_8}(R) \subseteq N_{rs}$, $X_{\alpha_8-\alpha_{\max}}(I) \subseteq L_{rs}$ the desired inclusion
+  follows from Chevalley commutator formula $x_{\alpha_{\max}}(\pm ab)=[x_{\alpha_8-\alpha_{\max}}(a), x_{\alpha_8}(b)].$
 
  \item \textit{Case $\Phi = \rB_\ell$, $s=1$, $r=\ell$.} 
- In this case only the sole short root of $\Sigma_1^-$ is not contained in $O$. Consider the following two roots of $\Phi$:
+ Only the sole short root of $\Sigma_1^-$ is not contained in $O$. Consider the following two roots of $\Phi$:
  \begin{equation}\nonumber \beta = \alpha_2 + \ldots + \alpha_\ell,\ \gamma = -\alpha_1 - 2\alpha_2 - \ldots -2\alpha_\ell.\end{equation}
@@
   \begin{equation} \label{eq:CCF} x_{\beta+\gamma}(-ab) = [x_{\gamma}(a),\, x_{\beta}(b)] \cdot x_{\gamma + 2\beta}(ab^2). \end{equation}
- \item \textit{Case $\Phi = \rF_4$, $s=4$, $r=1$.} In this case there are three possibilities for the $s$-shape and length of a root from $\Sigma_4^-$: 
+ \item \textit{Case $\Phi = \rF_4$, $s=4$, $r=1$.} There are three possibilities for the $s$-shape and length of $\alpha\in \Sigma_4^-$: 
  \begin{itemize}
@@
  Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, we 
-  only need to verify $X_\delta(I) \subseteq L_{rs}$, but the latter again follows from~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{\mathrm{max}}$. 
+  only need to verify $X_\delta(I) \subseteq L_{rs}$, but the latter again follows from~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{{\max}}$. 
  \item \textit{Case $\Phi = \rC_\ell$, $s=1$, $r=\ell$.} 
   %Similarly, one can show that $L_{rs}$ contains $X_\alpha(I)$ for all short $\alpha \in \Sigma_1^-$.
-  In this case the inclusion $X_{-\alpha_\mathrm{max}}(I) \subseteq L_{rs}$ does not immediately follow from commutator formulae
+  In this case the inclusion $X_{-\alpha_{\max}}(I) \subseteq L_{rs}$ does not immediately follow from commutator formulae
    and we need to invoke stability conditions once again.
@@
 \begin{lemma}\label{lemma:dv_unipotent} For any $1\leq i\leq n$ the following statements hold. 
-\begin{thmlist} \item \label{item-dvu1} $\U(\Phi^+, I) = X_{\alpha\ssub{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I) = \U(\Phi^+\setminus\{\alpha\ssub{i}\}, I)\cdot X_{\alpha\ssub{i}}(I)$;
-\item \label{item-dvu2} For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha\ssub{i}}(\xi)} \subseteq \U(\Phi^+, I)$;
-\item \label{item-dvu3} $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha\ssub{i}}(I) \cdot X_{-\alpha\ssub{i}}(I)$.
+\begin{thmlist} \item \label{item-dvu1} $\U(\Phi^+, I) = X_{\alpha_{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha_{i}\}, I) = \U(\Phi^+\setminus\{\alpha_{i}\}, I)\cdot X_{\alpha_{i}}(I)$;
+\item \label{item-dvu2} For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha_{i}}(\xi)} \subseteq \U(\Phi^+, I)$;
+\item \label{item-dvu3} $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha_{i}}(I) \cdot X_{-\alpha_{i}}(I)$.
 \end{thmlist} \end{lemma}
@@
 After the removal of all bonds marked $r$ the weight diagram of $\pi$ splits into several connected components.
-The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram that contains the vertex marked $\varpi_s$.
+The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram that contains the vertex corresponding to the highest weight.
 Clearly, $\Gamma$ consists of the weights of $\Lambda(\pi')$ incident to the removed bonds.
@@
 Consequently, one has
-\[ X_{-\alpha\ssub{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I), \]
+\[ X_{-\alpha_{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I), \]
 which implies the following inclusion:
@@
 Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$, we obtain the assertion of the lemma. Indeed,
-\begin{equation*} \label{rel:ninv} A^{X_{-\alpha\ssub{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha\ssub{r}}(R)} \cdot \EP_s(R, I) = A. \qedhere \end{equation*}
+\begin{equation*} \label{rel:ninv} A^{X_{-\alpha_{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha_{r}}(R)} \cdot \EP_s(R, I) = A. \qedhere \end{equation*}
 \end{proof}
@@
 Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits the following decomposition:
-\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi, I). \]
+\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I). \]
 \end{thm}
@@
 Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of the Bass--Kolster decomposition:
-\[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_\mathrm{max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]
-where $Z = Z_{\alpha_\mathrm{max}}(I)=\left\{z_{-\alpha_\mathrm{max}}(r, 1)\ \middle|\ r\in I \right\}$.
+\[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_{\max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]
+where $Z = Z_{\alpha_{\max}}(I)=\left\{z_{-\alpha_{\max}}(r, 1)\ \middle|\ r\in I \right\}$.
 \end{thm}
@@
 Notice that in each case it suffices to find $g' \in \U(\Phi^-, I) \cdot \U(\Phi^+, I) \cdot g$ such that 
-\begin{equation} \label{eq1} (g'\cdot v^+)_{1} = 1 + s \text{ and } (g'\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}} = s\ \text{for some}\ s\in I. \end{equation}
-Indeed, set $g'' = z_{-\alpha\ssub{max}}(-s, 1) \cdot g'$.
-Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi\ssub{1}-\alpha\ssub{max}}=0$ and the conclusion of the theorem follows from \cref{lemma:Chevalley-Matsumoto}.
+\begin{equation} \label{eq1} (g'\cdot v^+)_{1} = 1 + s \text{ and } (g'\cdot v^+)_{\varpi_{1}-\alpha_{max}} = s\ \text{for some}\ s\in I. \end{equation}
+Indeed, set $g'' = z_{-\alpha_{max}}(-s, 1) \cdot g'$.
+Obviously, one has $(g''\cdot v^+)_1 = 1$, $(g''\cdot v^+)_{\varpi_{1}-\alpha_{max}}=0$ and the conclusion of the theorem follows from \cref{lemma:Chevalley-Matsumoto}.
 
@@
 In the case $\Phi=\rD_\ell$ from the proof of \cref{thm:BassKolster} one obtains that
-\begin{equation*} \G(\Phi, R, I) =  \U(\Sigma_\ell^+, I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1, I) \cdot X_{-\alpha\ssub{\mathrm{max}}}(I) \cdot Z \cdot \U(\Sigma_1^-, I) \cdot \U(\Sigma_1^+, I) \cdot \G(\Delta_1, R, I).
+\begin{equation*} \G(\Phi, R, I) =  \U(\Sigma_\ell^+, I) \cdot X_{\alpha_1}(I) \cdot \U(\Sigma_2^-\cap\Delta_1, I) \cdot X_{-\alpha_{\max}}(I) \cdot Z \cdot \U(\Sigma_1^-, I) \cdot \U(\Sigma_1^+, I) \cdot \G(\Delta_1, R, I).
 \end{equation*}
@@
 In the remaining case $2k = \ell$ set $\Phi_k = \langle \alpha_\ell \rangle \cong \rA_1$.
-Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\,e. $\beta_k = \alpha_\mathrm{max}(\Phi_k)$, $k=1, \ldots, \lfloor \ell/2 \rfloor$.
+Now let $\beta_k$ be the maximal root of $\Phi_k$, i.\,e. $\beta_k = \alpha_{\max}(\Phi_k)$, $k=1, \ldots, \lfloor \ell/2 \rfloor$.
 Denote by $B$ the set of all $\beta_k$. From the definition it is clear that the elements of $B$ are mutually orthogonal to each other.
@@
 \begin{proof}
-\textsc{Case $\ell=4$.} Set $w = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}} \circ \sigma_{\alpha\ssub{2} + \alpha\ssub{4}}$.
+\textsc{Case $\ell=4$.} Set $w = \sigma_{\alpha_{1} + \alpha_{2}} \circ \sigma_{\alpha_{2} + \alpha_{4}}$.
 Straightforward computation shows that 
 \begin{align*}
-& w(\beta_1) = w(\alpha_\mathrm{max}) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \\
-& w(\beta_2) = w(\alpha_4) = \sigma_{\alpha\ssub{1} + \alpha\ssub{2}}(- \alpha_2) = \alpha_1,
+& w(\beta_1) = w(\alpha_{\max}) = \sigma_{\alpha_{1} + \alpha_{2}}(\alpha_1 + \alpha_2 + \alpha_3) = \alpha_3, \\
+& w(\beta_2) = w(\alpha_4) = \sigma_{\alpha_{1} + \alpha_{2}}(- \alpha_2) = \alpha_1,
 \end{align*}

### 2018-02-02 paper.tex
Minor

@@
 \item \label{item-trans1} For every two roots $\alpha, \beta \in \Phi$ of the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
-\item \label{item-egen} The elementary group $\E(\Phi, R)$  is generated as an abstract group by the root subgroups $X_{\alpha}(R)$, $\alpha \in \Pi \cup -\Pi$.
-\item \label{item-trans2} Assume that $\alpha_s\in \Pi$ is a fundamental root of $\Phi$ such that $m_s(\alpha_{\max}) = 1$. 
-Then for $\alpha, \beta \in \Sigma^\pm_s$ of the same length there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$. \end{lemlist}
+\item \label{item-trans2} Let $\alpha_s\in \Pi$ be a fundamental root and $\alpha, \beta \in \Sigma^\pm_s$ be two roots having the same length and $s$-shape.
+ Then there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$. \end{lemlist}
 \end{lemma}
@@
 The first assertion follows from \eqref{rel:R3} and the well-known fact that $W(\Phi)$ acts transitively on the set of roots of the same length.
-The same argument combined with \cref{lemma:abs} also proves the third assertion. Indeed, by the assumption all roots of the same length lying in $\Sigma_s$ have the same $s$-shape.
-
-To prove the second assertion notice that the subgroup $\langle X_\alpha(R) \mid \alpha \in \Pi \cup -\Pi \rangle$ contains $\widetilde{W}(\Phi)$ and therefore contains all other root subgroups $X_\alpha(R)$, $\alpha\in \Phi$.
+The second assertion follows from \eqref{rel:R3} and \cref{lemma:abs}.
 \end{proof}
@@
 Now it is clear that $N_{rs}$ contains the subgroup $\U(\Phi^+, R)$ generated by $X_{\alpha}(R)$, $\alpha\in\Pi$, which implies the assertion.
-%TODO: Why the positive unipotent radical is generated by simple root subgroups???
 \end{proof}
@@
  \item \textit{Case $\Phi = \rC_\ell$, $s=1$, $r=\ell$.} 
-  %Similarly, one can show that $L_{rs}$ contains $X_\alpha(I)$ for all short $\alpha \in \Sigma_1^-$.
   In this case the inclusion $X_{-\alpha_{\max}}(I) \subseteq L_{rs}$ does not immediately follow from commutator formulae
    and we need to invoke stability conditions once again.
-  From~\cref{lemma:DVST} we obtain that $N_{rs}$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$, which implies the assertion.
+  From~\cref{lemma:DVST} we obtain that $N_{rs}$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$.
+  The required inclusion now follows from this and~\cref{item-trans1}.
 \end{enumerate}
@@
  $\E(\Phi, R, I) \subseteq L_{rs}$, which completes the proof.
-%Thus, to prove our assertion it suffices to show that $L_{rs}$ contains $\mathcal{Z}(\Sigma_s^-)$.
-%From the inclusion  and \eqref{rel:NnormL} it follows that we only need to verify the inclusion $\mathcal{X} \subseteq L_{rs}$.
-%In turn, the last inclusion follows from the same transitivity argument as above if we use the fact that $X_\alpha(I) \subseteq \EP_r(R, I) \subseteq L_{rs}$ for $\alpha \in \Delta_r \cup \Sigma_r$.
-%For $\Phi=\rB_\ell$ we need to apply Chevalley commutator formula once again:
-%\[ X_{0, 1}(I) \subseteq X_{2, 1}(I) \cdot X_{2, 1}(I)^{x_{0, 2}(1)} \cdot X_{-2, 1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}. \qedhere \] 
 \end{proof}
@@
 \subsection{Relative Bass--Kolster decompositions}\label{sec:bass-kolster}
-The next theorem is a relative version of the so-called Bass--Kolster decomposition \cite[Theorem~2.1]{St78}.
+The next theorem is a relative version of the so-called Bass--Kolster decomposition (cf.~\cite[Theorem~2.1]{St78}).
 \begin{thm}\label{thm:BassKolster}
@@
 \end{array}\]
-Then the principal congruence subgroup $\G(\Phi, R, I)$ admits the following relative version of the Bass--Kolster decomposition:
+Then the principal congruence subgroup $\G(\Phi, R, I)$ admits decomposition:
 \[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_{\max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]

### 2018-02-05 paper.tex
Minor fixes

@@
 \address{Department of Mathematics and Mechanics, St. Petersburg State University, St. Petersburg, Russia}
-\email{ andrei.smolensky {\it at} gmail.com}
+\email{andrei.smolensky {\it at} gmail.com}
 \thanks{The authors of the present paper acknowledge the financial support of the Russian Science Foundation grant 14-11-00297}
@@
 In what follows, $r$ and $s$ are two distinct integers such that $1 \leqslant r, s \leqslant \ell$.
-We may assume $\ell>2$ because otherwise $\sr(I)=1$ and \cref{thm:DennisVaserstein} follows the stronger Gauss decomposition (see~\cref{thm:srRI1} below).
 From the Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
@@
 \begin{proof} [Proof of \cref{thm:DennisVaserstein}]
+First of all, notice that Dennis--Vaserstein decomposition follows the stronger Gauss decomposition (see~\cref{thm:srRI1} below).
+Thus, we may assume that $\ell>2$ and, in particular, that $\Phi\neq \mathsf{G}_2$.
+
 Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$: % listed in~\cref{table:dv-reps}.
@@
 \cref{lemma:Stein_reduction} below guarantees that $N_{rs}$ contains the root subgroup $X_{-\alpha_{r}}(R)$, which together with~\cref{lemma:dv-normal} 
- implies that $\EP_s(R) \subseteq N_{rs}$ and consequently that $\EP_s(R, I) \subseteq L_{rs}$. Indeed for $g\in \EP_s(R, I) \subseteq \EP_s(R)$ one has
+ implies that $\EP_s(R) \subseteq N_{rs}$ and consequently, that $\EP_s(R, I) \subseteq L_{rs}$. Indeed for $g\in \EP_s(R, I) \subseteq \EP_s(R)$ one has
 $g \cdot L_{rs} = g \cdot L_{rs} \cdot g^{-1} \cdot g \subseteq L_{rs} \cdot g \subseteq L_{rs}.$
@@
  Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, we 
-  only need to verify $X_\delta(I) \subseteq L_{rs}$, but the latter again follows from~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{{\max}}$. 
+  only need to verify $X_\delta(I) \subseteq L_{rs}$, which again follows from~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{{\max}}$. 
  \item \textit{Case $\Phi = \rC_\ell$, $s=1$, $r=\ell$.} 
@@
    and we need to invoke stability conditions once again.
-  From~\cref{lemma:DVST} we obtain that $N_{rs}$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$.
+  Using~\cref{lemma:DVST} below we obtain that $N_{rs}$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$.
   The required inclusion now follows from this and~\cref{item-trans1}.
@@
 \end{thmlist} \end{lemma}
-\begin{proof} The first two statements easily follow from the Chevalley commutator formula while the third one is a formal consequence of the first two. \end{proof}
+\begin{proof} The first two statements easily follow from the Chevalley commutator formula, while the third one is a formal consequence of the first two. \end{proof}
 
@@
 After the removal of all bonds marked $r$ the weight diagram of $\pi$ splits into several connected components.
-The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram that contains the vertex corresponding to the highest weight.
+The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram containing the vertex corresponding to the highest weight.
 Clearly, $\Gamma$ consists of the weights of $\Lambda(\pi')$ incident to the removed bonds.
@@
 \subsection{Relative Gauss decomposition}\label{sec:gauss}
-The proof of the Gauss decomposition presented below is similar to the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
+The proof of the Gauss decomposition presented below is similar to the proof in the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
 \begin{prop}\label{thm:Gauss}
@@
 two reductive subsystems of $\Phi$, corresponding to the endnodes of the Dynkin diagram of $\Phi$.
-Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit the triangular decomposition with $N$ triangular factors:
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit triangular decomposition with $N$ triangular factors:
 \[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I), \quad i=1, \ell. \]
-Then the ambient group $\E(\Phi, R, I)$ admits the decomposition with the same number of factors:
+Then the group $\E(\Phi, R, I)$ admits decomposition with the same number of factors:
 \[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm, I). \]
@@
 Denote by $Y$ the product of subgroups in the right-hand side of the above equality.
-To show that $Y=\E(\Phi, R, I)$ it suffices to check that
+To show that $Y=\E(\Phi, R, I)$ we need to verify the following assertions:
 \begin{enumerate}
@@
 To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for any $\alpha\in \pm \Pi$, $\xi\in R$.
-Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or for $i=\ell$, and we can expand $Y$ as follows:
+Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or for $i=\ell$, and we can factor $Y$ as follows:
 \[ Y=\Hh(\Phi, R, I) \cdot \U(\Delta_i^+, I) \cdot \ldots \cdot \U^\pm(\Delta_i, I) \cdot \U(\Sigma_i^+, I) \cdot \ldots \cdot \U(\Sigma_i^\pm, I). \]
-For every  $h \in \Hh(\Phi, R, I)$ one has for some $s\in I$
+For every  $h \in \Hh(\Phi, R, I)$ for some $s\in I$ one has
 \[ x_\alpha(\xi)\cdot h = h\cdot x_\alpha((1+s)\xi)=h\cdot x_\alpha(\xi)\, x_\alpha(s\xi). \]
@@
 Let $\Phi$ be a root system, let $I$ be an ideal of an arbitrary commutative ring $R$, and assume that $\sr(I)=1$.
-Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits the following decomposition:
+Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits Gauss decomposition:
 \[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I). \]
@@
 \begin{proof}
-In view of \cref{thm:Gauss} it suffices to prove that the Gauss decomposition of length $3$ holds for $\Phi=\rA_1$.
+In view of \cref{thm:Gauss} it suffices to show that Gauss decomposition holds in the special case $\Phi=\rA_1$.
 Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}$ be an element of $\SL(2, R, I)$.
@@
 \begin{alignat*}{2}
-& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\ell + 1 & \text{ if } \Phi=\rA_\ell, \rC_\ell, \\
-& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \ell + 1 & \text{ if } \Phi=\rB_\ell, \rD_\ell.
+& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 3|\Phi^+| + 2\ell + 1 & \text{ for } \Phi=\rA_\ell, \rC_\ell, \\
+& W(\E(\Phi, R, I), \mathcal{Z}(\Sigma_\ell^-))\leqslant 4|\Phi^+| + \ell + 1 & \text{ for } \Phi=\rB_\ell, \rD_\ell.
 \end{alignat*}

### 2018-02-12 paper.tex
More fixes

@@
 We omit curly braces in the above notations when $J$ is a one- or two-element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
-We call $\shape(\{s\}, \beta)$ simply the $s$-shape of $\beta$.
+We call $\shape(\{\alpha_s\}, \beta)$ simply the $s$-shape of $\beta$.
 
@@
 \section{Relative parabolic factorizations} \label{sec:factorizations}
-In this section we formulate and prove the relative versions of the decompositions from~\cite{St78}, which will be the main technical tools throughout the next section.
+In this section we formulate and prove relative versions of the decompositions from~\cite{St78}, which will be our main technical tools throughout the next section.
+
+Let $G$ be a group and $A$ its subset. Denote by $L(A)$, $R(A)$ and $N(A)$ the left and the right stabilizers of $A$ and the normalizer of $A$:
+\begin{align*} 
+ L(A) & =  \left\{ g\in G\ \middle |\ g \cdot A \cup g^{-1} \cdot A \subseteq A \right\}\!,\\
+ R(A) & =  \left\{ g\in G\ \middle |\ A \cdot g \cup A \cdot g^{-1} \subseteq A \right\}\!,\\
+ N(A) & =  \left\{ g\in G\ \middle |\ g \cdot A \cdot g^{-1} \cup g^{-1} \cdot A \cdot g \subseteq A \right\}.
+\end{align*}
+It is easy to see that $L(A)$, $R(A)$ and $N(A)$ are subgroups of $G$. The following obvious lemma will be useful in the sequel.
+\begin{lemma} \label{lem:LN} The subgroup $L(A)$ is normalized by $N(A)$. Moreover, one has $R(A) \cap N(A) \subseteq L(A)$, $L(A) \cap N(A) \subseteq R(A)$. \end{lemma}
+\begin{comment}
+\begin{proof}
+Let $h \in L(A)$, $g \in N(A)$. The first claim follows from the following chain of inclusions:
+\begin{equation} h^g \cdot A = g^{-1} \cdot h \cdot g \cdot A \cdot g^{-1} \cdot g \subseteq g^{-1} \cdot h \cdot A \cdot g \subseteq {A}^g \subseteq A. \end{equation} 
+Now if, in addition, $g \in R(A)$ we obtain
+$g \cdot A = g \cdot A \cdot g^{-1} \cdot g \subseteq A \cdot g \subseteq A,$ which implies the second claim.
+\end{proof}
+\end{comment}
 
 \subsection{Relative Dennis--Vaserstein decompositions}\label{sec:dennis-vaserstein}
-Let $\Phi$ be an irreducible root system of rank $\ell$.
-In what follows, $r$ and $s$ are two distinct integers such that $1 \leqslant r, s \leqslant \ell$.
-From the Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
+Let $\Phi$ be an irreducible root system of rank $\ell$ and $r$ and $s$ be two distinct integers such that $1 \leqslant r, s \leqslant \ell$.
+From Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
 \begin{multline*}
-A_{rs} \coloneqq \U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
+\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \\
 = \U(\Sigma_r^+, I)\cdot \U(\Sigma^-_r, I) \cdot \E(\Delta_r, R, I) \cdot \EP_s(R, I) = \hspace{5em} \\
@@
 \end{multline*}
-
-Denote by $N_{rs}$ the subgroup of $\E(\Phi, R)$, consisting of elements normalizing the above subset:
-\[ N_{rs} = \left\{ g\in \E(\Phi, R)\ \middle|\ g \cdot A_{rs} \cdot g^{-1} \cup g^{-1} \cdot A_{rs} \cdot g \subseteq A_{rs}\right\}. \]
+Denote the above subset by $A_{rs}$.
 
 \begin{lemma}\label{lemma:dv-normal} 
-For every $\alpha \in \Delta_{r, s} \cup \Phi^+ $ one has $X_\alpha(R) \subseteq N_{rs}$. \end{lemma}
+For every $\alpha \in \Delta_{r, s} \cup \Phi^+ $ one has $X_\alpha(R) \subseteq N(A_{rs})$. \end{lemma}
 \begin{proof}
 Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
-Since $\E(\Delta_{r, s}, R)$ normalizes $\U(\Sigma_r^- \cap \Sigma_s^-, I)$, we obtain the assertion for $\alpha \in \Delta_{r, s}$.
+Since $\E(\Delta_{r, s}, R)$ normalizes $\U(\Sigma_r^- \cap \Sigma_s^-, I)$, we obtain the required assertion for $\alpha \in \Delta_{r, s}$.
 
 Now let $\alpha$ be a positive simple root. It is clear that $\alpha$ lies either in $\Delta_r$ or $\Delta_s$.
-Assume, for example, the latter. From the Levi decomposition we get $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$,
-consequently $X_{\alpha}(R) \subseteq N_{rs}$.
-Now it is clear that $N_{rs}$ contains the subgroup $\U(\Phi^+, R)$ generated by $X_{\alpha}(R)$, $\alpha\in\Pi$, which implies the assertion.
+Assume, for example, the latter.
+From the Levi decomposition we obtain $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$, therefore $X_{\alpha}(R) \subseteq N(A_{rs})$.
+Thus, $N(A_{rs})$ contains the subgroup $\U(\Phi^+, R)$ generated by $X_{\alpha}(R)$, $\alpha\in\Pi$, which completes the proof.
 \end{proof}
@@
 \begin{proof} [Proof of \cref{thm:DennisVaserstein}]
-First of all, notice that Dennis--Vaserstein decomposition follows the stronger Gauss decomposition (see~\cref{thm:srRI1} below).
-Thus, we may assume that $\ell>2$ and, in particular, that $\Phi\neq \mathsf{G}_2$.
-
-Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the following possibilities for $\Phi$, $s$, $r$: % listed in~\cref{table:dv-reps}.
+First of all, notice that in the case $\ell=2$, $\sr(I)=1$ Dennis--Vaserstein decomposition can be deduced from Gauss decomposition given by~\cref{thm:srRI1} below.
+Thus, without loss of generality we may assume $\ell>2$ and, in particular, that $\Phi\neq \mathsf{G}_2$.
+
+Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the possibilities for $\Phi$, $s$, $r$ listed in~\cref{table:dv-reps} below.
 \begin{table}[htb]
@@
 \rE_\ell, \ \ell=6, 7, 8              & \ell &1      & 27, 56, 248    & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1 \\
+\rE_\ell, \ \ell=6, 7, 8              & 1    &2      & 27, 133, 3875  & \text{???}           & \rA_{\ell-1}              & ?              & ? \\
 \rF_4,                                & 4    & 1     & 26             & \text{minimal}       & \rC_{3}                   & 6              & 3 \end{array}\]
@@
 
-Denote by $L_{rs}$ the monoid consisting of elements $g\in \E(\Phi, R, I)$ such that $g \cdot A_{rs} \subseteq A_{rs}$.
-It is easy to see that $L_{rs}$ contains $\EP_r(R, I)$ and is normalized by $N_{rs}$, i.\,e. ${L_{rs}}^{N_{rs}}\subseteq L_{rs}$. Indeed, for $g\in N_{rs}$, $h\in L_{rs}$ one has
-\begin{equation}\label{rel:NnormL} h^g \cdot A_{rs} = g^{-1} \cdot h \cdot g \cdot A_{rs} \cdot g^{-1} \cdot g \subseteq g^{-1} \cdot h \cdot A_{rs} \cdot g \subseteq {A_{rs}}^g \subseteq A_{rs}.\end{equation}
-
-\cref{lemma:Stein_reduction} below guarantees that $N_{rs}$ contains the root subgroup $X_{-\alpha_{r}}(R)$, which together with~\cref{lemma:dv-normal} 
- implies that $\EP_s(R) \subseteq N_{rs}$ and consequently, that $\EP_s(R, I) \subseteq L_{rs}$. Indeed for $g\in \EP_s(R, I) \subseteq \EP_s(R)$ one has
-$g \cdot L_{rs} = g \cdot L_{rs} \cdot g^{-1} \cdot g \subseteq L_{rs} \cdot g \subseteq L_{rs}.$
-
-Our next goal is to verify the inclusion $\U(\Sigma_s^-, I) \subseteq L_{rs}$. Our main tools will be formula~\eqref{rel:NnormL} and \cref{item-trans2}.
-Since $\widetilde{W}(\Delta_s) \subseteq \E(\Delta_s, R) \subseteq N_{rs}$ and 
- $X_{\alpha}(I) \subseteq L_{rs}$ for $\alpha \in \Sigma^-_s\cap \Delta_r$, 
-we immediately obtain that $L_{rs}$ contains root subgroups $X_\alpha(I)$ corresponding to $\alpha$
- lying in the orbit $O = W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
+From \cref{lemma:Stein_reduction} below it follows that $N(A_{rs})$ contains root subgroup $X_{-\alpha_{r}}(R)$, which together with~\cref{lemma:dv-normal} 
+ implies that $\EP_s(R) \subseteq N(A_{rs})$, and hence by~\cref{lem:LN} that $\EP_s(R, I) \subseteq L(A_{rs})$.
+
+Our next goal is to verify the inclusion $\U(\Sigma_s^-, I) \subseteq L(A_{rs})$. Our main tools will be~\cref{lem:LN} and \cref{item-trans2}.
+Since $\widetilde{W}(\Delta_s) \subseteq \E(\Delta_s, R) \subseteq N(A_{rs})$ and 
+ $X_{\alpha}(I) \subseteq L(A_{rs})$ for $\alpha \in \Sigma^-_s\cap \Delta_r$, 
+we immediately obtain that $L(A_{rs})$ contains root subgroups $X_\alpha(I)$ for all $\alpha$ lying in the orbit $O = W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
 Thus, we are left to consider four cases in which $O$ does not coincide with $\Sigma^-_s$.
@@
  \item \textit{Case $\Phi = \rE_8$, $s=8$, $r=1,2$.}  
- There is only one root in $\Sigma_8^-$ not lying in $O$, namely $-\alpha_{\max}$ with $\shape(8,-\alpha_{\max}) = -2$.
- Since $X_{-\alpha_8}(R) \subseteq N_{rs}$, $X_{\alpha_8-\alpha_{\max}}(I) \subseteq L_{rs}$ the desired inclusion
+ There is only one root in $\Sigma_8^-$ not lying in $O$, namely $-\alpha_{\max}$ with $\shape(\{\alpha_8\}, -\alpha_{\max}) = -2$.
+ Since $X_{-\alpha_8}(R) \subseteq N(A_{rs})$, $X_{\alpha_8-\alpha_{\max}}(I) \subseteq L(A_{rs})$ the desired inclusion
   follows from Chevalley commutator formula $x_{\alpha_{\max}}(\pm ab)=[x_{\alpha_8-\alpha_{\max}}(a), x_{\alpha_8}(b)].$
-
+ \item \textit{Case $\Phi = \rE_7, \rE_8$, $s=1$, $r=2$.} ???
  \item \textit{Case $\Phi = \rB_\ell$, $s=1$, $r=\ell$.} 
@@
  \begin{equation}\nonumber \beta = \alpha_2 + \ldots + \alpha_\ell,\ \gamma = -\alpha_1 - 2\alpha_2 - \ldots -2\alpha_\ell.\end{equation}
- We need to verify $X_{\beta+\gamma}(I) \subseteq L_{rs}$, but this follows from $X_{\gamma}(I) \cup X_{-\alpha_1}(I) \subseteq L_{rs}$, $X_{\beta}(R) \subseteq N_{rs}$ using Chevalley commutator formula:
+ We need to verify $X_{\beta+\gamma}(I) \subseteq L(A_{rs})$, but this follows from $X_{\gamma}(I) \cup X_{-\alpha_1}(I) \subseteq L_{rs}$,
+  $X_{\beta}(R) \subseteq N(A_{rs})$ using Chevalley commutator formula:
   \begin{equation} \label{eq:CCF} x_{\beta+\gamma}(-ab) = [x_{\gamma}(a),\, x_{\beta}(b)] \cdot x_{\gamma + 2\beta}(ab^2). \end{equation}
@@
  \begin{itemize}
-  \item $\shape(4, \alpha) = 1$, $\alpha$ is short (there are 8 such roots);
-  \item $\shape(4, \alpha) = 2$, $\alpha$ is long (there are 6 such roots);
-  \item $\shape(4, \alpha) = 2$, $\alpha$ is short (there is only one such root: $\delta = -\alpha_1 -2\alpha_2-3\alpha_3-2\alpha_4$).
+  \item $\shape(\{\alpha_4\}, \alpha) = 1$, $\alpha$ is short (there are 8 such roots);
+  \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is long (there are 6 such roots);
+  \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is short (there is only one such root: $\delta = -\alpha_1 -2\alpha_2-3\alpha_3-2\alpha_4$).
  \end{itemize}
- Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, we 
-  only need to verify $X_\delta(I) \subseteq L_{rs}$, which again follows from~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{{\max}}$. 
+ Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, we only need to verify $X_\delta(I) \subseteq L(A_{rs})$. 
+ But the latter inclusion follows from formula~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{{\max}}$. 
  \item \textit{Case $\Phi = \rC_\ell$, $s=1$, $r=\ell$.} 
-  In this case the inclusion $X_{-\alpha_{\max}}(I) \subseteq L_{rs}$ does not immediately follow from commutator formulae
-   and we need to invoke stability conditions once again.
-  Using~\cref{lemma:DVST} below we obtain that $N_{rs}$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$.
-  The required inclusion now follows from this and~\cref{item-trans1}.
+  In this case the inclusion $X_{-\alpha_{\max}}(I) \subseteq L(A_{rs})$ does not follow from commutator formulae, therefore we need to invoke stability assumptions one more time.
+  From~\cref{lemma:DVST} below we obtain that $N(A_{rs})$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$.
+  The required inclusion now follows~\cref{item-trans1}.
 \end{enumerate}
 
-Thus, we have just shown that $\mathcal{X}\subseteq L_{rs}$. 
-Recall from~\cite[Theorem~3.4]{S} that the group $\E(\Phi, R, I)$ is generated by $\mathcal{Z}(\Sigma_s^-)$.
-On the other hand, from $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)} \subseteq L_{rs}^{N_{rs}} \subseteq L_{rs}$ we conclude that 
- $\E(\Phi, R, I) \subseteq L_{rs}$, which completes the proof.
+Thus, we have just shown that $\mathcal{X}\subseteq L(A_{rs})$. 
+Recall from~\cite[Theorem~3.4]{S} that the group $\E(\Phi, R, I)$ is generated by the subset $\mathcal{Z}(\Sigma_s^-)$.
+On the other hand, from $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)} \subseteq L(A_{rs})^{N(A_{rs})} \subseteq L(A_{rs})$ we conclude that 
+ $\E(\Phi, R, I) \subseteq L(A_{rs})$, which completes the proof.
 \end{proof}
@@
 \end{thmlist} \end{lemma}
-\begin{proof} The first two statements easily follow from the Chevalley commutator formula, while the third one is a formal consequence of the first two. \end{proof}
+\begin{proof} The first two assertions follow from Chevalley commutator formula, while the third one is a consequence of the first two. \end{proof}
 
@@
 The proof of the Gauss decomposition presented below is similar to the proof in the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
-\begin{prop}\label{thm:Gauss}
+
+\begin{prop} \label{thm:Gauss}
+Let $\Phi$ be a reduced irreducible root system of rank $\ell > 1$ and let $\Delta_k$, $\Delta_l$ be
+the reductive subsystems of $\Phi$ corresponding to a pair of distinct simple roots $\alpha_k$, $\alpha_l \in \Pi$.
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=k, l$ admit Gauss decomposition:
+\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \U(\Delta^+_i, I), \quad i=k, l. \]
+Then $\E(\Phi, R, I)$ also admits Gauss decomposition:
+\begin{equation} \label{eq:gauss1} \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I). \end{equation}
+\end{prop}
+\begin{proof}
+For a closed subset of roots $S \subseteq \Phi^+$ set $A(S, I) = \U(S, I) \cdot \U(-S, I) \cdot \U(S, I)$ (here by $-S$ we denote the corresponding subset of opposite roots).
+Notice that from Levi decomposition it follows that $A(\Phi^+, I) = A(\Delta_i^+, I) \cdot A(\Sigma_i^+, I)$.
+
+Denote by $A$ the product of subgroups in the right-hand side of~\eqref{eq:gauss1}.
+First of all, notice that for $h \in \Hh(\Phi, R, I)$, $\beta \in \Phi$ and $\xi \in R$ one has $x_\beta(\xi)^h = x_\beta(\xi + s\xi)$ for some $s\in I$.
+From this and the assumption of the proposition for $\alpha \in \Delta_k \cup \Delta_l$ we obtain that
+\begin{multline} \nonumber
+ A^{x_\alpha(\xi)} = (\Hh(\Phi, R, I) \cdot A(\Phi^+, I))^{X_\alpha(R)} \subseteq (\Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot A(\Sigma_i^+, I))^{x_\alpha(\xi)} \subseteq \\
+  \subseteq \Hh(\Phi, R, I) X_{\alpha}(I) \cdot \E(\Delta_i, R, I) \cdot A(\Sigma_i^+, I) \subseteq \Hh(\Phi, R, I) \cdot \Hh(\Delta_i, R, I) A(\Delta_i^+, I) \cdot A(\Sigma_i^+, I) \subseteq A.
+\end{multline}
+On the other hand, for $\beta \in \Phi^+$ we have
+\begin{equation} \nonumber
+ X_{\beta}(I) \cdot A \subseteq \Hh(\Phi, R, I) \cdot X_{\beta}(I) A(\Phi^+, I) \subseteq A.
+\end{equation}
+Thus, $A$ is normalized by root subgroups $X_\alpha(R)$, $\alpha \in \Delta_k \cup \Delta_l$ and hence is normalized by $\E(\Phi, R)$.
+On the other hand, from $\U(\Phi^+, I) \cdot A \subseteq A$ and~\cref{lem:LN} we conclude that $\mathcal{X} \cdot Y \subseteq Y$ and, finally,
+ that $\E(\Phi, R, I) \cdot Y \subseteq Y$.
+\end{proof}
+\begin{comment}
+\begin{prop}\label{thm:Gauss2}
 Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1$, $\Delta_\ell$ be
@@
 \end{proof}
+\end{comment}
 \begin{thm}\label{thm:srRI1}

### 2018-02-13 paper.tex
link DOIs against preferred resolver
Rewriting Dennis-Vaserstein

@@
 \end{align*}
-It is easy to see that $L(A)$, $R(A)$ and $N(A)$ are subgroups of $G$. The following obvious lemma will be useful in the sequel.
+It is easy to see that $L(A)$, $R(A)$ and $N(A)$ are subgroups of $G$. The following obvious lemma will be used several times in the sequel.
 \begin{lemma} \label{lem:LN} The subgroup $L(A)$ is normalized by $N(A)$. Moreover, one has $R(A) \cap N(A) \subseteq L(A)$, $L(A) \cap N(A) \subseteq R(A)$. \end{lemma}
@@
 \subsection{Relative Dennis--Vaserstein decompositions}\label{sec:dennis-vaserstein}
-Let $\Phi$ be an irreducible root system of rank $\ell$ and $r$ and $s$ be two distinct integers such that $1 \leqslant r, s \leqslant \ell$.
-From Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following four subsets of $\E(\Phi, R, I)$ are equal:
+Let $\Phi$ be an irreducible root system of rank $\ell\geq 2$.
+Let $\{r, s\}$ be the indices of a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
+
+Before we proceed with the proof of~\cref{thm:DennisVaserstein} let us remark that in the special case $\ell=2$
+ $\E(\Phi, R, I)$ admits Gauss decomposition (see~\cref{thm:srRI1} below).
+It is not hard to see that Dennis--Vaserstein decomposition follows from Gauss decomposition, 
+ therefore, in the sequel we may assume, without loss of generality, that $\ell > 2$.
+
+From Levi decomposition~\eqref{rel:Levi-decomp} we obtain the following equality of subsets of $\E(\Phi, R, I)$:
 \begin{multline*}
@@
 Denote the above subset by $A_{rs}$. 
-
-\begin{lemma}\label{lemma:dv-normal} 
-For every $\alpha \in \Delta_{r, s} \cup \Phi^+ $ one has $X_\alpha(R) \subseteq N(A_{rs})$. \end{lemma}
-\begin{proof}
-Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
-Since $\E(\Delta_{r, s}, R)$ normalizes $\U(\Sigma_r^- \cap \Sigma_s^-, I)$, we obtain the required assertion for $\alpha \in \Delta_{r, s}$.
-
-Now let $\alpha$ be a positive simple root. It is clear that $\alpha$ lies either in $\Delta_r$ or $\Delta_s$.
-Assume, for example, the latter.
-From the Levi decomposition we obtain $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$, therefore $X_{\alpha}(R) \subseteq N(A_{rs})$.
-Thus, $N(A_{rs})$ contains the subgroup $\U(\Phi^+, R)$ generated by $X_{\alpha}(R)$, $\alpha\in\Pi$, which completes the proof.
-\end{proof}
-
-\begin{proof} [Proof of \cref{thm:DennisVaserstein}]
-First of all, notice that in the case $\ell=2$, $\sr(I)=1$ Dennis--Vaserstein decomposition can be deduced from Gauss decomposition given by~\cref{thm:srRI1} below.
-Thus, without loss of generality we may assume $\ell>2$ and, in particular, that $\Phi\neq \mathsf{G}_2$.
-
-Since the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, it suffices to consider only the possibilities for $\Phi$, $s$, $r$ listed in~\cref{table:dv-reps} below.
+Notice that if the equality $A_{rs} = \E(\Phi, R, I)$ implies the ``symmetric'' equality $A_{sr} = \E(\Phi, R, I)$, 
+ therefore it suffices to consider only the possibilities for $\Phi$, $s$, $r$ listed in~\cref{table:dv-reps} below.
+
 \begin{table}[htb]
@@
 \end{table}
-
-From \cref{lemma:Stein_reduction} below it follows that $N(A_{rs})$ contains root subgroup $X_{-\alpha_{r}}(R)$, which together with~\cref{lemma:dv-normal} 
- implies that $\EP_s(R) \subseteq N(A_{rs})$, and hence by~\cref{lem:LN} that $\EP_s(R, I) \subseteq L(A_{rs})$.
+The key step in the proof of~\cref{thm:DennisVaserstein} is to verify that the normalizer $N(A_{rs})$ is suffiently large.
+This is accomplished in a series of lemmas. The following lemma identifies the ``obvious'' elements of $N(A_{rs})$.
+\begin{lemma}\label{lemma:dv-normal} 
+For every $\alpha \in \Delta_{r, s} \cup \Phi^+ $ one has $X_\alpha(R) \subseteq N(A_{rs})$. \end{lemma}
+\begin{proof}
+Notice that for every $i$ the group $\EP_i(R, I)$ is normalized by $\EP_i(R)$, hence it is normalized by $X_\alpha(R)$, $\alpha \in S_i^+$.
+Since $\E(\Delta_{r, s}, R)$ normalizes $\U(\Sigma_r^- \cap \Sigma_s^-, I)$, we obtain the required assertion for $\alpha \in \Delta_{r, s}$.
+
+Now let $\alpha$ be a positive simple root. It is clear that $\alpha$ lies either in $\Delta_r$ or $\Delta_s$.
+Assume, for example, the latter.
+Using Levi decomposition we obtain that $\U(\Sigma_r^- \cap \Sigma_s^-, I)^{X_\alpha(R)} \subseteq \U(\Sigma_s^-, I) \subseteq A_{rs}$, therefore $X_{\alpha}(R) \subseteq N(A_{rs})$.
+Thus, $N(A_{rs})$ contains the subgroup $\U(\Phi^+, R)$ generated by $X_{\alpha}(R)$, $\alpha\in\Pi$, which completes the proof.
+\end{proof}
+
+\begin{lemma}\label{lemma:dv_unipotent} For any $1\leq i\leq n$ the following statements hold. 
+\begin{thmlist} \item \label{item-dvu1} $\U(\Phi^+, I) = X_{\alpha_{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha_{i}\}, I) = \U(\Phi^+\setminus\{\alpha_{i}\}, I)\cdot X_{\alpha_{i}}(I)$;
+\item \label{item-dvu2} For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha_{i}}(\xi)} \subseteq \U(\Phi^+, I)$;
+\item \label{item-dvu3} $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha_{i}}(I) \cdot X_{-\alpha_{i}}(I)$.
+\end{thmlist} \end{lemma}
+\begin{proof} The first two assertions follow from Chevalley commutator formula, while the third one is a consequence of the first two. \end{proof}
+
+The following lemma is the key point of the proof where stability assumptions are invoked.
+\begin{lemma}\label{lemma:Stein_reduction}
+Under the assumptions of \cref{thm:DennisVaserstein} one has $X_{-\alpha_r}(R) \subseteq N(A_{rs}).$
+\end{lemma}
+\begin{proof}
+Let $\pi$ be the fundamental representation of $\G(\Phi, R)$ corresponding to the highest weight $\varpi_s$ (see Table~\ref{table:dv-reps}).
+Denote by $\Lambda(\pi)$ its set of weights.
+We will be mainly concerned with the action of root unipotents $x_\alpha(\xi)$ on weight spaces $V_\lambda$, $\lambda \in \Lambda(\pi)$.
+Perhaps the most intuitive way to visualize this action is to use the technique of {\it weight diagrams}.
+We refer the reader to~\cite{PSV98}, where this technique is introduced properly and where the weight diagrams have been drawn for 
+ almost all the representations appearing in~\cref{table:dv-reps}.
+
+Notice that $\Delta_r$ is an irreducible classical root system of type $\rA_\ell$, $\rC_\ell$ or $\rD_\ell$.
+Denote by $(\pi', V')$ the irreducible component of the restriction of $\pi$ to $\G(\Delta_r, R)$ containing the highest weight vector $v^+$ of $\pi$.
+In all cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta_r, R)$.
+
+Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
+We can visualize $\Gamma$ using {\it weight diagrams}  in the following manner.
+After removing all bonds marked $r$, the weight diagram of $\pi$ splits into several connected components.
+The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram containing the vertex corresponding to the highest weight.
+Clearly, $\Gamma$ consists of the weights of $\Lambda(\pi')$ incident to the removed bonds.
+From the consideration of weight diagrams it is easy to determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
+
+Denote by $B$ the subset of $\E(\Delta_r, R, I)$ consisting of elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
+Set $A\coloneqq\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
+Let $g$ be an element of $\E(\Delta_r, R, I)$. Applying \cref{lemma:uraction} to the subsystem $\Delta_r$, we find
+$x\in\U(\Delta_r^+, I)$ and $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
+This shows that $A = A_{rs}$, indeed:
+\begin{equation*} \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B.
+\end{equation*}
+
+Notice that by the definition of $\Gamma$ and Matsumoto lemma~\cite[Lemma~2.3]{Ma69} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$.
+Consequently, one has
+\[ X_{-\alpha_{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I), \]
+which implies the following inclusion:
+\begin{multline*}
+X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
+X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
+\subseteq B \cdot \U(\Sigma_r^+, I) \cdot \EP_s(R, I) =
+B \cdot \EP_s(R, I),
+\end{multline*}
+which together with the third statement of \cref{lemma:dv_unipotent} implies that
+\begin{equation*} \label{rel:sred}
+A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).
+\end{equation*}
+Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$, we obtain the assertion of the lemma. Indeed,
+\begin{equation*} \label{rel:ninv} A^{X_{-\alpha_{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha_{r}}(R)} \cdot \EP_s(R, I) = A. \qedhere \end{equation*}
+\end{proof}
+
+\begin{proof} [Proof of \cref{thm:DennisVaserstein}]
+From Lemmas~\ref{lemma:Stein_reduction} and~\ref{lemma:dv-normal} it follows that $N(A_{rs})$ contains $\EP_s(R)$, 
+ hence by~\cref{lem:LN} we obtain that $\EP_s(R, I) \subseteq L(A_{rs})$.
 
@@
 we immediately obtain that $L(A_{rs})$ contains root subgroups $X_\alpha(I)$ for all $\alpha$ lying in the orbit $O = W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
-Thus, we are left to consider four cases in which $O$ does not coincide with $\Sigma^-_s$.
+Thus, we are left to consider five cases when $O$ does not coincide with $\Sigma^-_s$.
 \begin{enumerate} 
@@
   follows from Chevalley commutator formula $x_{\alpha_{\max}}(\pm ab)=[x_{\alpha_8-\alpha_{\max}}(a), x_{\alpha_8}(b)].$
- \item \textit{Case $\Phi = \rE_7, \rE_8$, $s=1$, $r=2$.} ???
+ \item \textit{Case $\Phi = \rE_7,$ (resp. $\Phi= \rE_8$), $s=1$, $r=2$.}
+ There is only one (resp. there are $14$) roots in $\Sigma_1^-$ with $1$-shape $-2$, which are not contained in $O$ for this reason.
+ Denote by $\beta$ the maximal root of $\Phi$ (resp. the maximal root of $\Delta_8 \cong \rE_7$).
+ It is easy to check that $\shape(\{\alpha_1\}, \beta) = 2$ but $-\beta+\alpha_1 \in O$, therefore the assertion can be obtained via the same argument. 
  \item \textit{Case $\Phi = \rB_\ell$, $s=1$, $r=\ell$.} 
@@
 
-\begin{lemma}\label{lemma:dv_unipotent} For any $1\leq i\leq n$ the following statements hold. 
-\begin{thmlist} \item \label{item-dvu1} $\U(\Phi^+, I) = X_{\alpha_{i}}(I)\cdot \U(\Phi^+\setminus\{\alpha_{i}\}, I) = \U(\Phi^+\setminus\{\alpha_{i}\}, I)\cdot X_{\alpha_{i}}(I)$;
-\item \label{item-dvu2} For any $\xi\in R$ one has $\U(\Phi^+\setminus\{\alpha_i\}, I)^{x_{-\alpha_{i}}(\xi)} \subseteq \U(\Phi^+, I)$;
-\item \label{item-dvu3} $\U(\Phi^+, I)\cdot \U(\Phi^-, I) \subseteq \U(\Phi^+\setminus \{\alpha_i\}, I) \cdot \U(\Phi^-, I) \cdot X_{\alpha_{i}}(I) \cdot X_{-\alpha_{i}}(I)$.
-\end{thmlist} \end{lemma}
-\begin{proof} The first two assertions follow from Chevalley commutator formula, while the third one is a consequence of the first two. \end{proof}
-
-\begin{lemma}\label{lemma:Stein_reduction}
-Under the assumptions of \cref{thm:DennisVaserstein} one has $X_{-\alpha_r}(R) \subseteq N_{rs}.$
-\end{lemma}
-\begin{proof}
-Let $\pi$ be the irreducible representation of $\G(\Phi, R)$ with the highest weight $\varpi_s$ (see Table~\ref{table:dv-reps}).
-Notice that $\Delta_r$ is an irreducible classical root system of type $\rA_\ell$, $\rC_\ell$ or $\rD_\ell$.
-Denote by $(\pi', V')$ the irreducible component of the restriction of $\pi$ to $\G(\Delta_r, R)$ that contains the highest weight vector $v^+$ of $\pi$.
-In all the cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta_r, R)$.
-Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
-
-The set $\Gamma$ can be visualized using the weight diagrams (see~\cite{PSV98}) in the following manner.
-After the removal of all bonds marked $r$ the weight diagram of $\pi$ splits into several connected components.
-The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram containing the vertex corresponding to the highest weight.
-Clearly, $\Gamma$ consists of the weights of $\Lambda(\pi')$ incident to the removed bonds.
-By a consideration of the weight diagrams it is easy to determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
-
-Consider the subset $B \subset \E(\Delta_r, R, I)$, consisting of all elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
-Set $A\coloneqq\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
-
-Let $g$ be an element of $\E(\Delta_r, R, I)$. Applying \cref{lemma:uraction} to the subsystem $\Delta_r$, we find
-$x\in\U(\Delta_r^+, I)$ and $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
-Consequenty, this shows that $A = A_{rs}$, indeed:
-\begin{equation*} \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B.
-\end{equation*}
-
-Notice that by the definition of $\Gamma$ and Matsumoto lemma~\cite[Lemma~2.3]{Ma69} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$.
-Consequently, one has
-\[ X_{-\alpha_{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I), \]
-which implies the following inclusion:
-\begin{multline*}
-X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
-X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
-\subseteq B \cdot \U(\Sigma_r^+, I) \cdot \EP_s(R, I) =
-B \cdot \EP_s(R, I).
-\end{multline*}
-Together with the third statement of \cref{lemma:dv_unipotent} this shows that
-\begin{equation*} \label{rel:sred}
-A = \U(\Phi^+\setminus\{\alpha_r\}, I) \cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).
-\end{equation*}
-Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$, we obtain the assertion of the lemma. Indeed,
-\begin{equation*} \label{rel:ninv} A^{X_{-\alpha_{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha_{r}}(R)} \cdot \EP_s(R, I) = A. \qedhere \end{equation*}
-\end{proof}
-
 \begin{lemma}\label{lemma:DVST}
@@
 First of all, notice that for $h \in \Hh(\Phi, R, I)$, $\beta \in \Phi$ and $\xi \in R$ one has $x_\beta(\xi)^h = x_\beta(\xi + s\xi)$ for some $s\in I$.
-From this and the assumption of the proposition for $\alpha \in \Delta_k \cup \Delta_l$ we obtain that
+From this and the assumption of the proposition we obtain for $\alpha \in \Delta_k \cup \Delta_l$ that
 \begin{multline} \nonumber
@@
 \end{equation}
-Thus, $A$ is normalized by root subgroups $X_\alpha(R)$, $\alpha \in \Delta_k \cup \Delta_l$ and hence is normalized by $\E(\Phi, R)$.
-On the other hand, from $\U(\Phi^+, I) \cdot A \subseteq A$ and~\cref{lem:LN} we conclude that $\mathcal{X} \cdot Y \subseteq Y$ and, finally,
- that $\E(\Phi, R, I) \cdot Y \subseteq Y$.
-\end{proof}
-\begin{comment}
-\begin{prop}\label{thm:Gauss2}
-Let $\Phi$ be a reduced irreducible root system of rank $\ell$ and let $\Delta_1$, $\Delta_\ell$ be
-two reductive subsystems of $\Phi$, corresponding to the endnodes of the Dynkin diagram of $\Phi$.
-Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit triangular decomposition with $N$ triangular factors:
-\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \ldots \cdot \U(\Delta^\pm_i, I), \quad i=1, \ell. \]
-Then the group $\E(\Phi, R, I)$ admits decomposition with the same number of factors:
-\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \ldots \cdot \U(\Phi^\pm, I). \]
-\end{prop}
-\begin{proof}
-Denote by $Y$ the product of subgroups in the right-hand side of the above equality.
-To show that $Y=\E(\Phi, R, I)$ we need to verify the following assertions:
-\begin{enumerate}
-\item $Y$ is normalized by $\E(\Phi, R)$, i.\,e. $Y^{\E(\Phi, R)}\subseteq Y$;
-\item there exists a set $X$, generating $\E(\Phi, R, I)$ as a \emph{normal} subgroup of $\E(\Phi, R)$ such that $XY\subseteq Y$.
-\end{enumerate}
-To prove the first assertion it suffices to show that $Y^{x_\alpha(\xi)} \subseteq Y$ for any $\alpha\in \pm \Pi$, $\xi\in R$.
-Fix a root $\alpha\in\pm\Pi$. Clearly, $\alpha \in \Delta_i$ for $i=1$ or for $i=\ell$, and we can factor $Y$ as follows:
-\[ Y=\Hh(\Phi, R, I) \cdot \U(\Delta_i^+, I) \cdot \ldots \cdot \U^\pm(\Delta_i, I) \cdot \U(\Sigma_i^+, I) \cdot \ldots \cdot \U(\Sigma_i^\pm, I). \]
-For every  $h \in \Hh(\Phi, R, I)$ for some $s\in I$ one has
-\[ x_\alpha(\xi)\cdot h = h\cdot x_\alpha((1+s)\xi)=h\cdot x_\alpha(\xi)\, x_\alpha(s\xi). \]
-
-Therefore by the assumption of the theorem
-\begin{multline*}
-Y^{x_\alpha(\xi)} \subseteq \Hh(\Phi, R, I) \cdot x_\alpha(-\xi) \cdot X_{\alpha}(I) \cdot \E(\Delta_i, R, I)\cdot x_\alpha(\xi) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) =\\
-= \Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot \U(\Sigma^+_i, I) \cdot \ldots \cdot \U(\Sigma^\pm_i, I) = Y.
-\end{multline*}
-
-Now set $X=\left\{x_\alpha(\xi)\ \middle|\ \alpha\in\Pi, \ \xi\in I \right\}$. 
-Every root is a conjugate of some fundamental root under the action of $W(\Phi)$.
-Since $\E(\Phi, R)$ contains the normalizer of the torus, the set $X^{\E(\Phi, R)}$ contains all the generators of the group $\E(\Phi, I) = \langle x_\alpha(\xi), \  \alpha\in\Phi, \ \xi\in I \rangle$.
-Finally, the inclusion $XY \subseteq Y$ follows from the fact that $\Hh(\Phi, R, I)$ normalizes every root subgroup $X_\alpha(I)$.
-\end{proof}
-\end{comment}
+Thus, $A$ is normalized by root subgroups $X_\alpha(R)$, $\alpha \in \Delta_k \cup \Delta_l$ and therefore is normalized by $\E(\Phi, R)$.
+On the other hand, from $\U(\Phi^+, I) \cdot A \subseteq A$ and~\cref{lem:LN} we conclude that $\mathcal{X} \cdot A \subseteq A$ and hence
+ that $\E(\Phi, R, I) \cdot A \subseteq A$.
+\end{proof}
+
 \begin{thm}\label{thm:srRI1}

### 2018-02-13 paper.tex
Restored old statement of DV; swapped DV and Gauss; slicker proof of DV

@@
 \renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
-\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
+\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://doi.org/\thefield{doi}}{#1}}}
 \DeclareFieldFormat[article, inproceedings, inbook, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
@@
 \begin{thmlist}
- \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
- \item $\sr(I) \leqslant d$ otherwise.
+ \item $\sr(I) \leqslant d$ for $\Phi$ classical or $\Phi=\rG_2, \rF_4$;
+ \item $\sr(I) \leqslant d$ for $\Phi=\rE_6,\rE_7$ with $\{r, s\} = \{2, \ell\}$;
+ \item $\asr(I) \leqslant d$ for $\Phi=\rE_6,\rE_7$ with $\{r, s\} = \{1, \ell \}$, 
 \end{thmlist}
@@
 
+\subsection{Relative Gauss decomposition}\label{sec:gauss}
+The proof of the Gauss decomposition presented below is similar to the proof in the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
+
+\begin{prop} \label{thm:Gauss}
+Let $\Phi$ be a reduced irreducible root system of rank $\ell > 1$ and let $\Delta_k$, $\Delta_l$ be
+the reductive subsystems of $\Phi$ corresponding to a pair of distinct simple roots $\alpha_k$, $\alpha_l \in \Pi$.
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=k, l$ admit Gauss decomposition:
+\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \U(\Delta^+_i, I), \quad i=k, l. \]
+Then $\E(\Phi, R, I)$ also admits Gauss decomposition:
+\begin{equation} \label{eq:gauss1} \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I). \end{equation}
+\end{prop}
+\begin{proof}
+For a closed subset of roots $S \subseteq \Phi^+$ set $A(S, I) = \U(S, I) \cdot \U(-S, I) \cdot \U(S, I)$ (here by $-S$ we denote the corresponding subset of opposite roots).
+Notice that from Levi decomposition it follows that $A(\Phi^+, I) = A(\Delta_i^+, I) \cdot A(\Sigma_i^+, I)$.
+
+Denote by $A$ the product of subgroups in the right-hand side of~\eqref{eq:gauss1}.
+First of all, notice that for $h \in \Hh(\Phi, R, I)$, $\beta \in \Phi$ and $\xi \in R$ one has $x_\beta(\xi)^h = x_\beta(\xi + s\xi)$ for some $s\in I$.
+From this and the assumption of the proposition we obtain for $\alpha \in \Delta_k \cup \Delta_l$ that
+\begin{multline} \nonumber
+ A^{x_\alpha(\xi)} = (\Hh(\Phi, R, I) \cdot A(\Phi^+, I))^{X_\alpha(R)} \subseteq (\Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot A(\Sigma_i^+, I))^{x_\alpha(\xi)} \subseteq \\
+  \subseteq \Hh(\Phi, R, I) X_{\alpha}(I) \cdot \E(\Delta_i, R, I) \cdot A(\Sigma_i^+, I) \subseteq \Hh(\Phi, R, I) \cdot \Hh(\Delta_i, R, I) A(\Delta_i^+, I) \cdot A(\Sigma_i^+, I) \subseteq A.
+\end{multline}
+On the other hand, for $\beta \in \Phi^+$ we have
+\begin{equation} \nonumber
+ X_{\beta}(I) \cdot A \subseteq \Hh(\Phi, R, I) \cdot X_{\beta}(I) A(\Phi^+, I) \subseteq A.
+\end{equation}
+Thus, $A$ is normalized by root subgroups $X_\alpha(R)$, $\alpha \in \Delta_k \cup \Delta_l$ and therefore is normalized by $\E(\Phi, R)$.
+On the other hand, from $\U(\Phi^+, I) \cdot A \subseteq A$ and~\cref{lem:LN} we conclude that $\mathcal{X} \cdot A \subseteq A$ and hence
+ that $\E(\Phi, R, I) \cdot A \subseteq A$.
+\end{proof}
+
+\begin{thm}\label{thm:srRI1}
+Let $\Phi$ be a root system, let $I$ be an ideal of an arbitrary commutative ring $R$, and assume that $\sr(I)=1$.
+Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits Gauss decomposition:
+\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I). \]
+\end{thm}
+\begin{proof}
+In view of \cref{thm:Gauss} it suffices to show that Gauss decomposition holds in the special case $\Phi=\rA_1$.
+Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}$ be an element of $\SL(2, R, I)$.
+The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
+Multiplying $A$ on the left by $x_{12}(z)$, we get a matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible element $a'$ in the top-left corner.
+After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
+Thus we have obtained a relative Gauss decomposition for $A$:
+\begin{equation*}
+A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
+\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
+\cdot x_{12}(b'/a')=x_{12}(-z)\cdot
+\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
+\cdot x_{21}(y) \cdot x_{12}(b'/a'), 
+\end{equation*}
+where $\varepsilon\in 1+I$ and $y\in I$. \end{proof}
+
 \subsection{Relative Dennis--Vaserstein decompositions}\label{sec:dennis-vaserstein}
@@
 
-Before we proceed with the proof of~\cref{thm:DennisVaserstein} let us remark that in the special case $\ell=2$
- $\E(\Phi, R, I)$ admits Gauss decomposition (see~\cref{thm:srRI1} below).
+Before we proceed with the proof of~\cref{thm:DennisVaserstein} let us remark that in the special case $\ell=2$, $\sr(I)\leq 1$
+ we already known that $\E(\Phi, R, I)$ admits Gauss decomposition.
 It is not hard to see that Dennis--Vaserstein decomposition follows from Gauss decomposition, 
@@
 \rD_\ell, \ \ell\geqslant 4           & \ell &\ell-1 & 2^{\ell-1}     & \text{half-spinor}   & \rA_{\ell-1}              & \ell           & \ell-2  \\
-\rE_\ell, \ \ell=6, 7, 8              & \ell &2      & 27, 56, 248    & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
-\rE_\ell, \ \ell=6, 7, 8              & \ell &1      & 27, 56, 248    & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1 \\
-\rE_\ell, \ \ell=6, 7, 8              & 1    &2      & 27, 133, 3875  & \text{???}           & \rA_{\ell-1}              & ?              & ? \\
+\rE_\ell, \ \ell=6, 7                 & \ell &2      & 27, 56         & \text{minimal}       & \rA_{\ell-1}              & \ell           & 3       \\ 
+\rE_\ell, \ \ell=6, 7                 & \ell &1      & 27, 56         & \text{minimal}       & \rD_{\ell-1}              & 2(\ell-1)      & \ell-1 \\
 \rF_4,                                & 4    & 1     & 26             & \text{minimal}       & \rC_{3}                   & 6              & 3 \end{array}\]
@@
 
-\begin{proof} [Proof of \cref{thm:DennisVaserstein}]
-From Lemmas~\ref{lemma:Stein_reduction} and~\ref{lemma:dv-normal} it follows that $N(A_{rs})$ contains $\EP_s(R)$, 
- hence by~\cref{lem:LN} we obtain that $\EP_s(R, I) \subseteq L(A_{rs})$.
-
-Our next goal is to verify the inclusion $\U(\Sigma_s^-, I) \subseteq L(A_{rs})$. Our main tools will be~\cref{lem:LN} and \cref{item-trans2}.
-Since $\widetilde{W}(\Delta_s) \subseteq \E(\Delta_s, R) \subseteq N(A_{rs})$ and 
- $X_{\alpha}(I) \subseteq L(A_{rs})$ for $\alpha \in \Sigma^-_s\cap \Delta_r$, 
-we immediately obtain that $L(A_{rs})$ contains root subgroups $X_\alpha(I)$ for all $\alpha$ lying in the orbit $O = W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
-Thus, we are left to consider five cases when $O$ does not coincide with $\Sigma^-_s$.
+We will need one more root-theoretic lemma before we proceed with the proof of~\cref{thm:DennisVaserstein}.
+Let $\Phi$, $r$ and $s$ be as in~\cref{table:dv-reps}.
+Denote by $O$ the subset of roots of $\Sigma_s^-$ lying in the orbit $W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
+\begin{lemma} \label{lemma:root-lemma}
+Suppose that $\Phi \neq \rC_\ell$. The following alternative holds: either $O$ coincides with $\Sigma_s^-$ or
+$\Phi=\rB_\ell, \rF_4$ and $\Sigma_s^- \setminus O$ consists of the sole short root $\gamma$, which can be presented as a sum 
+ $\gamma = \alpha + \beta$ for some short root $\alpha \in \Phi^+$ and some long root $\beta \in O$ satisfying $\beta + 2\alpha \in O$. 
+\end{lemma}
+\begin{proof}
+From \cref{lemma:abs} it follows that $O$ does not coincide with $\Sigma^-_s$ only in the following two cases.
  \begin{enumerate} 
- \item \textit{Case $\Phi = \rE_8$, $s=8$, $r=1,2$.}  
- There is only one root in $\Sigma_8^-$ not lying in $O$, namely $-\alpha_{\max}$ with $\shape(\{\alpha_8\}, -\alpha_{\max}) = -2$.
- Since $X_{-\alpha_8}(R) \subseteq N(A_{rs})$, $X_{\alpha_8-\alpha_{\max}}(I) \subseteq L(A_{rs})$ the desired inclusion
-  follows from Chevalley commutator formula $x_{\alpha_{\max}}(\pm ab)=[x_{\alpha_8-\alpha_{\max}}(a), x_{\alpha_8}(b)].$
- \item \textit{Case $\Phi = \rE_7,$ (resp. $\Phi= \rE_8$), $s=1$, $r=2$.}
- There is only one (resp. there are $14$) roots in $\Sigma_1^-$ with $1$-shape $-2$, which are not contained in $O$ for this reason.
- Denote by $\beta$ the maximal root of $\Phi$ (resp. the maximal root of $\Delta_8 \cong \rE_7$).
- It is easy to check that $\shape(\{\alpha_1\}, \beta) = 2$ but $-\beta+\alpha_1 \in O$, therefore the assertion can be obtained via the same argument. 
  \item \textit{Case $\Phi = \rB_\ell$, $s=1$, $r=\ell$.} 
- Only the sole short root of $\Sigma_1^-$ is not contained in $O$. Consider the following two roots of $\Phi$:
- \begin{equation}\nonumber \beta = \alpha_2 + \ldots + \alpha_\ell,\ \gamma = -\alpha_1 - 2\alpha_2 - \ldots -2\alpha_\ell.\end{equation}
- We need to verify $X_{\beta+\gamma}(I) \subseteq L(A_{rs})$, but this follows from $X_{\gamma}(I) \cup X_{-\alpha_1}(I) \subseteq L_{rs}$,
-  $X_{\beta}(R) \subseteq N(A_{rs})$ using Chevalley commutator formula:
-  \begin{equation} \label{eq:CCF} x_{\beta+\gamma}(-ab) = [x_{\gamma}(a),\, x_{\beta}(b)] \cdot x_{\gamma + 2\beta}(ab^2). \end{equation}
+ Only the sole short root of $\Sigma_1^-$ is not contained in $O$, denote it by $\gamma$. Set $\alpha = \alpha_2 + \ldots + \alpha_\ell,\ \beta = -\alpha_1 - 2\alpha_2 - \ldots -2\alpha_\ell.$
+ It is clear that $\alpha \in \Phi^+$, $\beta, \beta + 2\alpha \in O$.
  \item \textit{Case $\Phi = \rF_4$, $s=4$, $r=1$.} There are three possibilities for the $s$-shape and length of $\alpha\in \Sigma_4^-$: 
@@
   \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is long (there are 6 such roots);
-  \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is short (there is only one such root: $\delta = -\alpha_1 -2\alpha_2-3\alpha_3-2\alpha_4$).
+  \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is short (there is only one such root, denote it $\gamma$).
  \end{itemize}
- Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, we only need to verify $X_\delta(I) \subseteq L(A_{rs})$. 
- But the latter inclusion follows from formula~\eqref{eq:CCF} with $\beta = \alpha_2 + \alpha_3,\ \gamma = -\alpha_{{\max}}$. 
+ Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, only $\gamma$ is not contained in $O$.
+ Clearly, $\gamma = -\alpha_1 -2\alpha_2-3\alpha_3-2\alpha_4 = \alpha + \beta$ for $\alpha = \alpha_2 + \alpha_3\in \Phi^+,$ $\beta = -\alpha_{{\max}} \in O$. \qedhere
+\end{enumerate}
+\end{proof}
+
+\begin{proof} [Proof of \cref{thm:DennisVaserstein}]
+From Lemmas~\ref{lemma:Stein_reduction} and~\ref{lemma:dv-normal} it follows that $N(A_{rs})$ contains $\EP_s(R)$.
+Thus, by~\cref{lem:LN} we obtain that $\EP_s(R, I) \subseteq L(A_{rs})$.
+
+Our next goal is to verify the inclusion $\U(\Sigma_s^-, I) \subseteq L(A_{rs})$.
+Since $\widetilde{W}(\Delta_s) \subseteq \E(\Delta_s, R) \subseteq N(A_{rs})$ and 
+ $X_{\alpha}(I) \subseteq L(A_{rs})$ for $\alpha \in \Sigma^-_s\cap \Delta_r$, 
+we obtain from~\cref{lem:LN} and \cref{item-trans2} that $L(A_{rs})$ contains root subgroups $X_\alpha(I)$ for $\alpha \in O = W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
+Thus, by~\cref{lemma:root-lemma} we are left to consider two cases when $O$ does not coincide with $\Sigma^-_s$. 
+\begin{enumerate} 
+  \item \textit{Case $\Phi = \rB_\ell, \rF_4$.} Let $\alpha, \beta, \gamma$ be as in~\cref{lemma:root-lemma}.
+  Since $X_{\beta}(I), X_{\beta+2\alpha}(I) \subseteq L(A_{rs})$ and $X_{\alpha}(R) \subseteq N(A_{rs})$ we obtain the required inclusion
+   $X_{\gamma}(I)$ using Chevalley commutator formula:
+   \begin{equation} \nonumber x_{\gamma}(\pm ab) = [x_{\beta}(a),\, x_{\alpha}(b)] \cdot x_{\beta + 2\alpha}(ab^2). \end{equation}
  \item \textit{Case $\Phi = \rC_\ell$, $s=1$, $r=\ell$.} 
-  In this case the inclusion $X_{-\alpha_{\max}}(I) \subseteq L(A_{rs})$ does not follow from commutator formulae, therefore we need to invoke stability assumptions one more time.
+  In this case we need to invoke stability assumptions one more time.
   From~\cref{lemma:DVST} below we obtain that $N(A_{rs})$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$.
@@
 \end{enumerate}
-
-Thus, we have just shown that $\mathcal{X}\subseteq L(A_{rs})$. 
+Thus, we have shown that $\mathcal{X}\subseteq L(A_{rs})$. 
 Recall from~\cite[Theorem~3.4]{S} that the group $\E(\Phi, R, I)$ is generated by the subset $\mathcal{Z}(\Sigma_s^-)$.
@@
 \begin{proof}
-Denoteb by $C$ the set consisting of elements $g \in \EP_s(R, I)$ for which matrix entries $(g_{i, 2})$, $i=2, \ldots, \ell$ form an $I$-unimodular column of height $\ell-1$
+Denote by $C$ the set consisting of elements $g \in \EP_s(R, I)$ for which matrix entries $(g_{i, 2})$, $i=2, \ldots, \ell$ form an $I$-unimodular column of height $\ell-1$
 
@@
 \end{proof}
-
-\subsection{Relative Gauss decomposition}\label{sec:gauss}
-The proof of the Gauss decomposition presented below is similar to the proof in the absolute case (cf.~\cite[Theorem~5.1]{Sm12}).
-
-\begin{prop} \label{thm:Gauss}
-Let $\Phi$ be a reduced irreducible root system of rank $\ell > 1$ and let $\Delta_k$, $\Delta_l$ be
-the reductive subsystems of $\Phi$ corresponding to a pair of distinct simple roots $\alpha_k$, $\alpha_l \in \Pi$.
-Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=k, l$ admit Gauss decomposition:
-\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \U(\Delta^+_i, I), \quad i=k, l. \]
-Then $\E(\Phi, R, I)$ also admits Gauss decomposition:
-\begin{equation} \label{eq:gauss1} \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I). \end{equation}
-\end{prop}
-\begin{proof}
-For a closed subset of roots $S \subseteq \Phi^+$ set $A(S, I) = \U(S, I) \cdot \U(-S, I) \cdot \U(S, I)$ (here by $-S$ we denote the corresponding subset of opposite roots).
-Notice that from Levi decomposition it follows that $A(\Phi^+, I) = A(\Delta_i^+, I) \cdot A(\Sigma_i^+, I)$.
-
-Denote by $A$ the product of subgroups in the right-hand side of~\eqref{eq:gauss1}.
-First of all, notice that for $h \in \Hh(\Phi, R, I)$, $\beta \in \Phi$ and $\xi \in R$ one has $x_\beta(\xi)^h = x_\beta(\xi + s\xi)$ for some $s\in I$.
-From this and the assumption of the proposition we obtain for $\alpha \in \Delta_k \cup \Delta_l$ that
-\begin{multline} \nonumber
- A^{x_\alpha(\xi)} = (\Hh(\Phi, R, I) \cdot A(\Phi^+, I))^{X_\alpha(R)} \subseteq (\Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot A(\Sigma_i^+, I))^{x_\alpha(\xi)} \subseteq \\
-  \subseteq \Hh(\Phi, R, I) X_{\alpha}(I) \cdot \E(\Delta_i, R, I) \cdot A(\Sigma_i^+, I) \subseteq \Hh(\Phi, R, I) \cdot \Hh(\Delta_i, R, I) A(\Delta_i^+, I) \cdot A(\Sigma_i^+, I) \subseteq A.
-\end{multline}
-On the other hand, for $\beta \in \Phi^+$ we have
-\begin{equation} \nonumber
- X_{\beta}(I) \cdot A \subseteq \Hh(\Phi, R, I) \cdot X_{\beta}(I) A(\Phi^+, I) \subseteq A.
-\end{equation}
-Thus, $A$ is normalized by root subgroups $X_\alpha(R)$, $\alpha \in \Delta_k \cup \Delta_l$ and therefore is normalized by $\E(\Phi, R)$.
-On the other hand, from $\U(\Phi^+, I) \cdot A \subseteq A$ and~\cref{lem:LN} we conclude that $\mathcal{X} \cdot A \subseteq A$ and hence
- that $\E(\Phi, R, I) \cdot A \subseteq A$.
-\end{proof}
-
-\begin{thm}\label{thm:srRI1}
-Let $\Phi$ be a root system, let $I$ be an ideal of an arbitrary commutative ring $R$, and assume that $\sr(I)=1$.
-Then the relative elementary Chevalley group $\E(\Phi, R, I)$ admits Gauss decomposition:
-\[ \E(\Phi, R, I) = \Hh(\Phi, R, I) \cdot \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot \U(\Phi^+, I). \]
-\end{thm}
-\begin{proof}
-In view of \cref{thm:Gauss} it suffices to show that Gauss decomposition holds in the special case $\Phi=\rA_1$.
-Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}$ be an element of $\SL(2, R, I)$.
-The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
-Multiplying $A$ on the left by $x_{12}(z)$, we get a matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible element $a'$ in the top-left corner.
-After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
-Thus we have obtained a relative Gauss decomposition for $A$:
-\begin{equation*}
-A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
-\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
-\cdot x_{12}(b'/a')=x_{12}(-z)\cdot
-\begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
-\cdot x_{21}(y) \cdot x_{12}(b'/a'), 
-\end{equation*}
-where $\varepsilon\in 1+I$ and $y\in I$. \end{proof}
 

### 2018-02-13 paper.tex
Minor fixes

@@
 \begin{prop} \label{thm:Gauss}
-Let $\Phi$ be a reduced irreducible root system of rank $\ell > 1$ and let $\Delta_k$, $\Delta_l$ be
-the reductive subsystems of $\Phi$ corresponding to a pair of distinct simple roots $\alpha_k$, $\alpha_l \in \Pi$.
-Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=k, l$ admit Gauss decomposition:
-\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \U(\Delta^+_i, I), \quad i=k, l. \]
+Let $\Phi$ be a reduced irreducible root system of rank $\ell > 1$ and let $\Delta_1$, $\Delta_\ell$ be
+the reductive subsystems of $\Phi$ corresponding to the endnodes of the Dynkin diagram of $\Phi$.
+Suppose that both relative elementary subgroups $\E(\Delta_i, R, I)$, $i=1, \ell$ admit Gauss decomposition:
+\[ \E(\Delta_i, R, I) = \Hh(\Delta_i, R, I) \cdot \U(\Delta^+_i, I) \cdot \U(\Delta^-_i, I) \cdot \U(\Delta^+_i, I), \quad i=1, \ell. \]
 Then $\E(\Phi, R, I)$ also admits Gauss decomposition:
@@
 First of all, notice that for $h \in \Hh(\Phi, R, I)$, $\beta \in \Phi$ and $\xi \in R$ one has $x_\beta(\xi)^h = x_\beta(\xi + s\xi)$ for some $s\in I$.
-From this and the assumption of the proposition we obtain for $\alpha \in \Delta_k \cup \Delta_l$ that
+From this and the assumption of the proposition we obtain for $\alpha \in \Delta_1 \cup \Delta_\ell$, $\xi \in R$ that
 \begin{multline} \nonumber
- A^{x_\alpha(\xi)} = (\Hh(\Phi, R, I) \cdot A(\Phi^+, I))^{X_\alpha(R)} \subseteq (\Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot A(\Sigma_i^+, I))^{x_\alpha(\xi)} \subseteq \\
+ A^{x_\alpha(\xi)} = (\Hh(\Phi, R, I) \cdot A(\Phi^+, I))^{x_\alpha(\xi)} \subseteq (\Hh(\Phi, R, I) \cdot \E(\Delta_i, R, I) \cdot A(\Sigma_i^+, I))^{x_\alpha(\xi)} \subseteq \\
   \subseteq \Hh(\Phi, R, I) X_{\alpha}(I) \cdot \E(\Delta_i, R, I) \cdot A(\Sigma_i^+, I) \subseteq \Hh(\Phi, R, I) \cdot \Hh(\Delta_i, R, I) A(\Delta_i^+, I) \cdot A(\Sigma_i^+, I) \subseteq A.
@@
 \end{equation}
-Thus, $A$ is normalized by root subgroups $X_\alpha(R)$, $\alpha \in \Delta_k \cup \Delta_l$ and therefore is normalized by $\E(\Phi, R)$.
+Thus, $A$ is normalized by root subgroups $X_\alpha(R)$, $\alpha \in \Delta_1 \cup \Delta_\ell$ and therefore is normalized by $\E(\Phi, R)$.
 On the other hand, from $\U(\Phi^+, I) \cdot A \subseteq A$ and~\cref{lem:LN} we conclude that $\mathcal{X} \cdot A \subseteq A$ and hence
@@
 \begin{proof}
-Let $\pi$ be the fundamental representation of $\G(\Phi, R)$ corresponding to the highest weight $\varpi_s$ (see Table~\ref{table:dv-reps}).
-Denote by $\Lambda(\pi)$ its set of weights.
+Let $\pi$ be the representation of $\G(\Phi, R)$ wit the highest weight $\varpi_s$ (see Table~\ref{table:dv-reps}).
+Denote by $\Lambda(\pi)$ the set of weights of $\pi$.
 We will be mainly concerned with the action of root unipotents $x_\alpha(\xi)$ on weight spaces $V_\lambda$, $\lambda \in \Lambda(\pi)$.
 Perhaps the most intuitive way to visualize this action is to use the technique of {\it weight diagrams}.
-We refer the reader to~\cite{PSV98}, where this technique is introduced properly and where the weight diagrams have been drawn for 
- almost all the representations appearing in~\cref{table:dv-reps}.
+We refer the reader to~\cite{PSV98}, where this technique is introduced properly and where the weight diagrams for the representations appearing in~\cref{table:dv-reps} have been depicted.
 
@@
 
-Notice that by the definition of $\Gamma$ and Matsumoto lemma~\cite[Lemma~2.3]{Ma69} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$.
-Consequently, one has
-\[ X_{-\alpha_{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I), \]
-which implies the following inclusion:
-\begin{multline*}
-X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq 
-X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \cdot \EP_s(R, I) \subseteq \\
-\subseteq B \cdot \U(\Sigma_r^+, I) \cdot \EP_s(R, I) =
-B \cdot \EP_s(R, I),
-\end{multline*}
+Notice that by the definition of $\Gamma$ and Matsumoto lemma~\cite[Lemma~2.3]{Ma69} for any $s\in I$, $ g\in B$ one has $x_{-\alpha_r}(s) \cdot g \cdot v^+ = g \cdot v^+$, therefore
+\[ X_{-\alpha_{r}}(I)^{B} \subseteq \U(\Phi^-, I) \cap \Stab(v^+) \subseteq \U(\Delta_s^-, I) \subseteq \EP_s(R, I). \]
+From the above inclusion we immediately obtain that
+\begin{equation*} X_{\alpha_r}(I) \cdot X_{-\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq X_{\alpha_r}(I) \cdot B \cdot \EP_s(R, I) \subseteq B \cdot \U(\Sigma_r^+, I) \cdot \EP_s(R, I) = B \cdot \EP_s(R, I), \end{equation*}
 which together with the third statement of \cref{lemma:dv_unipotent} implies that
@@
 \end{equation*}
-Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$, we obtain the assertion of the lemma. Indeed,
+Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$, we obtain the required assertion, indeed:
 \begin{equation*} \label{rel:ninv} A^{X_{-\alpha_{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha_{r}}(R)} \cdot \EP_s(R, I) = A. \qedhere \end{equation*}

### 2018-02-13 paper.tex
Minor fixes

@@
 \end{table}
-The key step in the proof of~\cref{thm:DennisVaserstein} is to verify that the normalizer $N(A_{rs})$ is suffiently large.
-This is accomplished in a series of lemmas. The following lemma identifies the ``obvious'' elements of $N(A_{rs})$.
+It is essential for the proof of~\cref{thm:DennisVaserstein} that the normalizer $N(A_{rs})$ is suffiently large.
+The following lemma describes the ``obvious'' root subgroups which are contained $N(A_{rs})$ for arbitrary $R$.
 \begin{lemma}\label{lemma:dv-normal} 

### 2018-02-14 paper.tex
Minor fixes

@@
   Since $X_{\beta}(I), X_{\beta+2\alpha}(I) \subseteq L(A_{rs})$ and $X_{\alpha}(R) \subseteq N(A_{rs})$ we obtain the required inclusion
-   $X_{\gamma}(I)$ using Chevalley commutator formula:
+   $X_{\gamma}(I) \subseteq L(A_{rs})$ using Chevalley commutator formula:
    \begin{equation} \nonumber x_{\gamma}(\pm ab) = [x_{\beta}(a),\, x_{\alpha}(b)] \cdot x_{\beta + 2\alpha}(ab^2). \end{equation}
@@
 \begin{lemma}\label{lemma:DVST}
-Assume that $\Phi=\rC_\ell$ and $\sr(I) \leq \ell-1$, then $X_{-\alpha_s}(R) \subseteq N_{rs}$.
+Assume that $\Phi=\rC_\ell$ and $\sr(I) \leq \ell-1$, then $X_{-\alpha_s}(R) \subseteq N(A_{rs})$.
 \end{lemma}

### 2018-02-14 paper.tex
One more revision in the proof of DV

@@
 
-We will need one more root-theoretic lemma before we proceed with the proof of~\cref{thm:DennisVaserstein}.
-Let $\Phi$, $r$ and $s$ be as in~\cref{table:dv-reps}.
-Denote by $O$ the subset of roots of $\Sigma_s^-$ lying in the orbit $W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
-\begin{lemma} \label{lemma:root-lemma}
-Suppose that $\Phi \neq \rC_\ell$. The following alternative holds: either $O$ coincides with $\Sigma_s^-$ or
-$\Phi=\rB_\ell, \rF_4$ and $\Sigma_s^- \setminus O$ consists of the sole short root $\gamma$, which can be presented as a sum 
- $\gamma = \alpha + \beta$ for some short root $\alpha \in \Phi^+$ and some long root $\beta \in O$ satisfying $\beta + 2\alpha \in O$. 
-\end{lemma}
-\begin{proof}
-From \cref{lemma:abs} it follows that $O$ does not coincide with $\Sigma^-_s$ only in the following two cases.
+\begin{lemma}\label{lemma:DVST}
+Assume that $\Phi=\rC_\ell$, $s=1$, $r=\ell$ and that $\sr(I) \leq \ell-1$. Then $X_{-\alpha_1}(R) \subseteq N(A_{\ell 1})$.
+\end{lemma}
+\begin{proof}
+Denote by $C$ the set consisting of elements $g \in \EP_1(R, I)$ for which matrix entries $(g_{i, 2})$, $i=2, \ldots, \ell$ form an $I$-unimodular column of height $\ell-1$.
+Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot C$.
+Applying \cref{item:asrUnipC} we can find for every $g \in \EP_1(R, I)$ some element $x \in \U(\Sigma_\ell^+ \cap \Delta_1, I)$ such that $xg \in C$.  
+The equality $A_{\ell 1} = A'$ follows from this, indeed, for $g\in \EP_1(R, I)$ one has
+\begin{equation*} \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq 
+ \EP_\ell(R, I)x^{-1}  \cdot \U(\Sigma_1^-, I) \cdot xg \subseteq A'. \end{equation*}
+
+By the definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_1^+ \cap \Delta_\ell, I)$ such that $(y \cdot g)_{1, 2} = 0$.
+Consequently, for every $g\in C$ one has
+\[
+ \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq \EP_\ell(R, I) y^{-1} \cdot \U(\Sigma_\ell^-\cap \Sigma_1^-, I)^{y^{-1}} \cdot y g
+  \subseteq \EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot y g.
+\]
+Notice that the matrix entry $(yg)_{1, 1}$ is invertible.
+From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1 \coloneqq (yg)^{x_{-\alpha_1}(\xi)}$
+satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$.
+Consequently, one has
+\begin{multline*} {A_{\ell 1}}^{X_{-\alpha_{1}}(R)} \subseteq \EP_\ell(R, I)^{X_{-\alpha_1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{-\alpha_1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\
+\subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell 1}, \end{multline*} as claimed.
+\end{proof}
+
+Now we are all set to prove the main result of this subsection.
+\begin{proof} [Proof of \cref{thm:DennisVaserstein}]
+From Lemmas~\ref{lemma:Stein_reduction} and~\ref{lemma:dv-normal} it follows that $N(A_{rs})$ contains $\EP_s(R)$.
+Thus, by~\cref{lem:LN} we obtain that $\EP_s(R, I) \subseteq L(A_{rs})$.
+
+Our next goal is to verify the inclusion $\U(\Sigma_s^-, I) \subseteq L(A_{rs})$.
+Since $\widetilde{W}(\Delta_s) \subseteq \E(\Delta_s, R) \subseteq N(A_{rs})$ and 
+ $X_{\alpha}(I) \subseteq L(A_{rs})$ for $\alpha \in \Sigma^-_s\cap \Delta_r$, 
+we obtain from~\cref{lem:LN} and \cref{item-trans2} that $L(A_{rs})$ contains root subgroups $X_\alpha(I)$ for $\alpha$ lying in the orbit $O = W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
+Thus we are left to consider three cases when $O$ does not coincide with $\Sigma^-_s$. 
 \begin{enumerate} 
   \item \textit{Case $\Phi = \rB_\ell$, $s=1$, $r=\ell$.} 
- Only the sole short root of $\Sigma_1^-$ is not contained in $O$, denote it by $\gamma$. Set $\alpha = \alpha_2 + \ldots + \alpha_\ell,\ \beta = -\alpha_1 - 2\alpha_2 - \ldots -2\alpha_\ell.$
+ Only the sole short root of $\Sigma_1^-$ is not contained in $O$, denote it by $\gamma$.
+ Set $\alpha = \alpha_2 + \ldots + \alpha_\ell,\ \beta = -\alpha_1 - 2\alpha_2 - \ldots -2\alpha_\ell.$
  It is clear that $\alpha \in \Phi^+$, $\beta, \beta + 2\alpha \in O$.
- \item \textit{Case $\Phi = \rF_4$, $s=4$, $r=1$.} There are three possibilities for the $s$-shape and length of $\alpha\in \Sigma_4^-$: 
+ Since $X_{\beta}(I), X_{\beta+2\alpha}(I) \subseteq L(A_{rs})$ and $X_{\alpha}(R) \subseteq N(A_{rs})$ we obtain the required inclusion $X_{\gamma}(I) \subseteq L(A_{rs})$ using Chevalley commutator formula:
+ \begin{equation} \nonumber x_{\gamma}(\pm ab) = [x_{\beta}(a),\, x_{\alpha}(b)] \cdot x_{\beta + 2\alpha}(ab^2). \end{equation}
+ \item \textit{Case $\Phi = \rF_4$, $s=4$, $r=1$.}
+ There are three possibilities for the $s$-shape and length of $\alpha\in \Sigma_4^-$: 
  \begin{itemize}
@@
   \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is long (there are 6 such roots);
-  \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is short (there is only one such root, denote it $\gamma$).
+  \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is short (there is only one such root, denote it by $\gamma$).
  \end{itemize}
  Since $\Delta_r \cap \Sigma_s^-$ contains roots of the first two types, only $\gamma$ is not contained in $O$.
- Clearly, $\gamma = -\alpha_1 -2\alpha_2-3\alpha_3-2\alpha_4 = \alpha + \beta$ for $\alpha = \alpha_2 + \alpha_3\in \Phi^+,$ $\beta = -\alpha_{{\max}} \in O$. \qedhere
-\end{enumerate}
-\end{proof}
-
-\begin{proof} [Proof of \cref{thm:DennisVaserstein}]
-From Lemmas~\ref{lemma:Stein_reduction} and~\ref{lemma:dv-normal} it follows that $N(A_{rs})$ contains $\EP_s(R)$.
-Thus, by~\cref{lem:LN} we obtain that $\EP_s(R, I) \subseteq L(A_{rs})$.
-
-Our next goal is to verify the inclusion $\U(\Sigma_s^-, I) \subseteq L(A_{rs})$.
-Since $\widetilde{W}(\Delta_s) \subseteq \E(\Delta_s, R) \subseteq N(A_{rs})$ and 
- $X_{\alpha}(I) \subseteq L(A_{rs})$ for $\alpha \in \Sigma^-_s\cap \Delta_r$, 
-we obtain from~\cref{lem:LN} and \cref{item-trans2} that $L(A_{rs})$ contains root subgroups $X_\alpha(I)$ for $\alpha \in O = W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
-Thus, by~\cref{lemma:root-lemma} we are left to consider two cases when $O$ does not coincide with $\Sigma^-_s$. 
-\begin{enumerate} 
-  \item \textit{Case $\Phi = \rB_\ell, \rF_4$.} Let $\alpha, \beta, \gamma$ be as in~\cref{lemma:root-lemma}.
-  Since $X_{\beta}(I), X_{\beta+2\alpha}(I) \subseteq L(A_{rs})$ and $X_{\alpha}(R) \subseteq N(A_{rs})$ we obtain the required inclusion
-   $X_{\gamma}(I) \subseteq L(A_{rs})$ using Chevalley commutator formula:
-   \begin{equation} \nonumber x_{\gamma}(\pm ab) = [x_{\beta}(a),\, x_{\alpha}(b)] \cdot x_{\beta + 2\alpha}(ab^2). \end{equation}
+ Clearly, $\gamma = -\alpha_1 -2\alpha_2-3\alpha_3-2\alpha_4 = \alpha + \beta$ for $\alpha = \alpha_1 + \alpha_2 + \alpha_3\in \Phi^+,$ $\beta = -\alpha_{{\max}} \in O$.
+ Since $\alpha \in \Phi^+$, $\beta, \beta + 2\alpha \in O$ we obtain the inclusion $X_{\gamma}(I) \subseteq L(A_{rs})$ by the same token as in the previous case.
  \item \textit{Case $\Phi = \rC_\ell$, $s=1$, $r=\ell$.} 
   In this case we need to invoke stability assumptions one more time.
-  From~\cref{lemma:DVST} below we obtain that $N(A_{rs})$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$.
+  From~\cref{lemma:DVST} we obtain that $N(A_{rs})$ contains $X_{-\alpha_1}(R)$ and therefore coincides with $\E(\Phi, R)$.
   The required inclusion now follows~\cref{item-trans1}.
@@
  $\E(\Phi, R, I) \subseteq L(A_{rs})$, which completes the proof.
-\end{proof}
-
-\begin{lemma}\label{lemma:DVST}
-Assume that $\Phi=\rC_\ell$ and $\sr(I) \leq \ell-1$, then $X_{-\alpha_s}(R) \subseteq N(A_{rs})$.
-\end{lemma}
-\begin{proof}
-Denote by $C$ the set consisting of elements $g \in \EP_s(R, I)$ for which matrix entries $(g_{i, 2})$, $i=2, \ldots, \ell$ form an $I$-unimodular column of height $\ell-1$
-
-Set $A' = \EP_\ell(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot C$.
-Applying \cref{item:asrUnipC} we find for every $g \in \EP_s(R, I)$ an element $x \in \U(\Sigma_r^+ \cap \Delta_s, I)$ such that $xg \in C$.  
-Notice that the equality $A_{rs} = A'$ follows from this, indeed, for $g\in \EP_s(R, I)$ one has
-\begin{equation*} \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq 
- \EP_r(R, I)x^{-1}  \cdot \U(\Sigma_s^-, I) \cdot xg \subseteq A'. \end{equation*}
-
-By the definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_s^+ \cap \Delta_r, I)$ such that $(y \cdot g)_{\varpi_s, \varpi_s - \alpha_s} = 0$.
-Consequently, for every $g\in C$ one has
-\[
- \EP_r(R, I) \cdot \U(\Sigma_s^- \cap \Sigma_r^-, I) \cdot g \subseteq \EP_r(R, I) y^{-1} \cdot \U(\Sigma_r^-\cap \Sigma_s^-, I)^{y^{-1}} \cdot y g
-  \subseteq \EP_r(R, I) \cdot \U(\Sigma_r^-, I) \cdot y g.
-\]
-Notice that the matrix entry $(yg)_{\varpi_s, \varpi_s}$ is invertible.
-From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1 \coloneqq (yg)^{x_{-\alpha_s}(\xi)}$
-satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_s^-, I)$, $h \in \EP_s(R, I)$.
-Consequently, one has
-\begin{multline*} {A_{rs}}^{X_{-\alpha_{s}}(R)} \subseteq \EP_r(R, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_r^-, I)^{X_{-\alpha_{s}}(R)} \cdot \U(\Sigma_s^-, I) \cdot \EP_s(R, I) \subseteq \\
-\subseteq \EP_r(R, I) \cdot \U(\Phi^-, I) \cdot \EP_s(R, I) \subseteq A_{rs}, \end{multline*}
-as claimed.
 \end{proof}

### 2018-02-15 paper.tex
Modifying introduction

@@
 \title[Decompositions of congruence subgroups of Chevalley groups]{Decompositions of congruence subgroups \\ of Chevalley groups}
-\keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, subsystem factorization, product decomposition. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
+\keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, subsystem factorization, product decomposition. {\em Mathematical Subject Classification (2010):} 20G35, 19B14}
 \author{Sergey Sinchuk}
@@
  upper estimates of the width of principal congruence subgroups in terms of Tits--Vaserstein generators.
-Some of our results are new even in the absolute case and were previously studied only for groups over finite fields.
+%Some of our results are new even in the absolute case and were previously studied only for groups over finite fields.
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-The aim of this paper is to generalize several decompositions of Chevalley groups over rings 
- to their principal congruence subgroups and relative elementary subgroups.
-We focus on the so-called ``parabolic decompositions'', i.e. decompositions involving parabolic and unipotent factors. 
-One of our main results is the following theorem.
-\begin{thm}[Dennis--Vaserstein decomposition]\label{thm:DennisVaserstein}
-Let $\Phi$ be an irreducible root system of rank $\ell\geqslant 2$ and $\{ r, s \}$ be a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
+This paper studies decompositions of Chevalley groups over commutative rings (see e.\,g.~\cite{VP} and references therein for the introduction to the theory of Chevalley groups over rings).
+Recall that classical decompositions of Chevalley groups over fields such as e.\,g. Bruhat decomposition do not generalize to groups over more general classes of rings.
+Nevertheless, Chevalley groups over rings of {\it finite stable rank} do admit several remarkable ``parabolic decompositions'', i.\,e.
+decompositions formulated in terms of parabolic and unipotent subgroups.
+Main interest in these decompositions comes mainly from the study of stability problems for $\K_1$-function modeled on Chevalley groups (see e.\,g.~\cite{St78, Si13}).
+
+The first goal of this paper is to prove analogues of these decompositions for congruence subgroups of Chevalley groups of level $I \trianglelefteq R$
+ while making ring-theoretic assumptions only about the ideal $I$ and not the ring $R$ itself.
+One of our main results is the following theorem, which is, essentially, a version of Dennis--Vaserstein decomposition for the relative elementary group $\E(\Phi, R, I)$
+ (cf.~\cite[Theorems~2.5 and~4.1]{St78},~\cite[Theorem~1.2]{Si13}).
+\begin{thm}\label{thm:DennisVaserstein}
+Let $\Phi \neq \rE_8$ be an irreducible root system of rank $\ell\geqslant 2$ and $\{ r, s \}$ be a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
 Denote by $d$ the distance between $r$ and $s$ on the Dynkin diagram.
@@
 \end{thm}
-Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5 and~4.1]{St78}.
-The condition $\asr(I) \leq d$ is a relative version of the \emph{absolute stable range} condition of D.~Estes and J.~Ohm, which depends only on the ideal $I$ (see section~\ref{sec:rel-asr}).
-Another results of the paper are relative analogues of Gauss and Bass--Kolster decompositions (see~\cref{thm:srRI1,thm:BassKolster}).
-
-We apply our decompositions to several problems.
-First, we obtain upper estimates of the number of factors in the presentation of a Chevalley group as a product of its subsystem subgroups of type $\rA_\ell$.
-For example, in~\cref{thm:SL2width} such estimates are given for relative classical groups and products of subgroups $\SL(2, R, I)$.
-Our another result is the decomposition in terms of subgroups of type $\rA_\ell$ of submaximal rank. 
-Using~\cref{thm:DennisVaserstein} we prove the following theorem inspired by the main result of~\cite{Nik07}.
+The notation for the groups and ring-theoretic invariants appearing in the above statement is introduced in Sections~\ref{sec:preliminaries} and~\ref{sec:stability-conditions}.
+
+Our further results in this direction are relative analogues of Gauss and Bass--Kolster decompositions (see~\cref{thm:srRI1,thm:BassKolster}).
+%TODO: For what?
+Another goal of this paper is to apply parabolic decompositions for obtaining the estimates of the width of relative Chevalley groups in terms of certain generating sets.
+For example, in~\cref{thm:width} we obtain upper estimates on the width of $\E(\Phi, R, I)$ with respect to Tits--Vaserstein generators for several small-dimensional rings. 
+Also, as a corollary of Bass--Kolster decomposition we obtain upper estimates of the number of factors in the presentation of a classical Chevalley group
+ as a product of its subsystem subgroups $\SL(2, R, I)$, see~\cref{thm:SL2width}.
+Moreover, as a corollary of~\cref{thm:DennisVaserstein} we obtain the following theorem, which is inspired by the main result of~\cite{Nik07}.
 \begin{thm}\label{thm:spin-sln-prod}
@@
 \end{thm}
-
-Finally, we obtain upper bounds on the width of $\E(\Phi, R, I)$ with respect to Tits--Vaserstein generators for several important classes of small-dimensional rings (see~\cref{thm:width}).
 
@@
 \begin{lemma}\label{lemma:Chevalley-Matsumoto}
-Let $\pi$ be a basic fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
+Let $\pi$ be a basic fundamental representation of $\G_{sc}(\Phi, R)$ with highest weight $\varpi_s$.
 Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi_{s}}=1$, then $g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
@@
 After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
-Thus we have obtained a relative Gauss decomposition for $A$:
+Thus, we have obtained a relative Gauss decomposition for $A$:
 \begin{equation*}
@@
 we obtain from~\cref{lem:LN} and \cref{item-trans2} that $L(A_{rs})$ contains root subgroups $X_\alpha(I)$ for $\alpha$ lying in the orbit $O = W(\Delta_s) \cdot (\Sigma^-_s\cap \Delta_r)$.
-Thus we are left to consider three cases when $O$ does not coincide with $\Sigma^-_s$. 
+Thus, we are left to consider three cases when $O$ does not coincide with $\Sigma^-_s$. 
 \begin{enumerate} 

### 2018-02-16 paper.tex
More fixes

@@
 \section{Introduction}\label{sec:intro}
-This paper studies decompositions of Chevalley groups over commutative rings (see e.\,g.~\cite{VP} and references therein for the introduction to the theory of Chevalley groups over rings).
-Recall that classical decompositions of Chevalley groups over fields such as e.\,g. Bruhat decomposition do not generalize to groups over more general classes of rings.
+This paper studies decompositions of Chevalley groups over commutative rings (see e.\,g.~\cite{VP} for the introduction to Chevalley groups over rings).
+Recall that classical decompositions of Chevalley groups over fields such as Bruhat decomposition do not generalize to groups over more general rings.
 Nevertheless, Chevalley groups over rings of {\it finite stable rank} do admit several remarkable ``parabolic decompositions'', i.\,e.
 decompositions formulated in terms of parabolic and unipotent subgroups.
-Main interest in these decompositions comes mainly from the study of stability problems for $\K_1$-function modeled on Chevalley groups (see e.\,g.~\cite{St78, Si13}).
-
-The first goal of this paper is to prove analogues of these decompositions for congruence subgroups of Chevalley groups of level $I \trianglelefteq R$
- while making ring-theoretic assumptions only about the ideal $I$ and not the ring $R$ itself.
+The interest in these decompositions comes, in particular, from the study of stability problems for $\K_1$-functors modeled on Chevalley groups (see e.\,g.~\cite{St78, Si13}).
+
+The first goal of this paper is to obtain analogues of these parabolic decompositions for congruence subgroups of Chevalley groups.
 One of our main results is the following theorem, which is, essentially, a version of Dennis--Vaserstein decomposition for the relative elementary group $\E(\Phi, R, I)$
@@
 \end{thm}
-The notation for the groups and ring-theoretic invariants appearing in the above statement is introduced in Sections~\ref{sec:preliminaries} and~\ref{sec:stability-conditions}.
-
-Our further results in this direction are relative analogues of Gauss and Bass--Kolster decompositions (see~\cref{thm:srRI1,thm:BassKolster}).
-%TODO: For what?
-Another goal of this paper is to apply parabolic decompositions for obtaining the estimates of the width of relative Chevalley groups in terms of certain generating sets.
-For example, in~\cref{thm:width} we obtain upper estimates on the width of $\E(\Phi, R, I)$ with respect to Tits--Vaserstein generators for several small-dimensional rings. 
-Also, as a corollary of Bass--Kolster decomposition we obtain upper estimates of the number of factors in the presentation of a classical Chevalley group
+The notation for the groups and ring-theoretic invariants appearing in the statement of the above theorem is introduced in sections~\ref{sec:preliminaries} and~\ref{sec:stability-conditions}.
+Other relative decompositions studied in this article are Gauss and Bass--Kolster decompositions (see~\cref{thm:srRI1,thm:BassKolster}).
+
+As an application of parabolic factorizations, we deduce several {\it subgroup factorizations} of finite width for relative Chevalley groups.
+For example, as a corollary of Bass--Kolster decomposition we obtain upper estimates of the number of factors in the presentation of a classical Chevalley group
  as a product of its subsystem subgroups $\SL(2, R, I)$, see~\cref{thm:SL2width}.
-Moreover, as a corollary of~\cref{thm:DennisVaserstein} we obtain the following theorem, which is inspired by the main result of~\cite{Nik07}.
-\begin{thm}\label{thm:spin-sln-prod}
-Assume that $\sr(I) \leqslant 2$. Then the group $\Epin(2\ell, R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ regularly embedded subgroups of type $\rA_{\ell-1}$.
+As an application of~\cref{thm:DennisVaserstein} we prove the following theorem inspired by the main result of~\cite{Nik07}.
+\begin{thm}\label{thm:spin-sln-prod} Assume that $\sr(I) \leqslant 2$.
+Then the group $\Epin(2\ell, R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ regularly embedded subgroups of type $\rA_{\ell-1}$.
 \end{thm}
+As another application, we obtain results on the bounded generation of the relative elementary group.
+Recall from~\cite[Theorem~2]{Va86} that $\E(\Phi, R, I)$ can be generated by the set of Tits--Vaserstein generators
+ $z_\alpha(s, \xi) =  x_{-\alpha}(-\xi) x_\alpha(s) x_{-\alpha}(\xi)$, where $s\in I$ and $\xi\in R$
+(in fact, a smaller generating set suffices, see~\cref{prop:Stepanov-theorem}).
+As a further application of parabolic factorizations, we obtain in~\cref{thm:width} estimates of the width $\E(\Phi, R, I)$  
+ with respect to this generating set in several special cases.
 
@@
 i.\,e. the subgroup generated by the elementary root unipotents $x_\alpha(\xi)$, $\alpha\in\Phi$, $\xi\in R$, see~\cite{VP, St78, S}.
+
 For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{principal congruence subgroup} of level $I$.
-
-The \emph{relative elementary Chevalley subgroup} $\E(\Phi, R, I) \leqslant \G(\Phi, R, I)$ is defined as the normal closure in $\E(\Phi, R)$ of the subgroup $\E(\Phi, I)$ generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi, \ \xi \in I \}$.
-
-Set $z_\alpha(s, \xi) = x_{\alpha}(s)^{x_{-\alpha}(\xi)}$, $s\in I$, $\xi\in R$.
-It is a classical result of J.~Tits and L.~Vaserstein (see~\cite{Tits76}, \cite[Theorem~2]{Va86}) that the relative elementary subgroup $\E(\Phi, R, I)$ is generated by the set of elements $\mathcal{Z}(\Phi)$.
-Here for a subset of roots $S\subseteq\Phi$ we denote by $\mathcal{Z}(S)$ the set
-\[ \mathcal{Z}(S) =  \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in S\}.\]
+Recall that the \emph{relative elementary Chevalley subgroup} $\E(\Phi, R, I) \leqslant \G(\Phi, R, I)$ is defined as the normal closure in $\E(\Phi, R)$ of the subgroup $\E(\Phi, I)$ generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi, \ \xi \in I \}$.
+
+For a subset of roots $S\subseteq\Phi$ denote by $\mathcal{Z}(S)$ the union of $\mathcal{X}$ and $\{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in S\}.$
+The following result describes generating sets of $\E(\Phi, R, I)$.
+\begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov-theorem} Let $\Phi$ be an irreducible root system of rank $\geq 2$ and $S \subseteq \Phi$ be an arbitrary parabolic subset of roots with special part $\Sigma_S$.
+ Then the relative elementary subgroup $\E(\Phi, R, I)$ is generated as an abstract group by $\mathcal{Z}(\Sigma_S)$. \end{prop}
+Denote by $I^{\indexbox{2}}$ the ideal of $R$ generated by all squares $a^2$, where $a\in I$.
  \begin{lemma}[{\cite[Corollary~3.3]{S}}]\label{lemma:Stepanov-ideal}
@@
 \end{lemma}
-Here $I^{\indexbox{2}}$ denotes the ideal generated by the squares $a^2$, where $a\in I$.
-
 For $\varepsilon\in R^*$ set $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_{\alpha}(\varepsilon).$
@@
 Denote the above subset by $A_{rs}$. 
-Notice that if the equality $A_{rs} = \E(\Phi, R, I)$ implies the ``symmetric'' equality $A_{sr} = \E(\Phi, R, I)$, 
- therefore it suffices to consider only the possibilities for $\Phi$, $s$, $r$ listed in~\cref{table:dv-reps} below.
+Notice that the equality $A_{rs} = \E(\Phi, R, I)$ implies symmetric equality $A_{sr} = \E(\Phi, R, I)$, 
+ therefore it suffices to consider only the following possibilities for $\Phi$, $s$, $r$.
 
@@
 \end{table}
-It is essential for the proof of~\cref{thm:DennisVaserstein} that the normalizer $N(A_{rs})$ is suffiently large.
-The following lemma describes the ``obvious'' root subgroups which are contained $N(A_{rs})$ for arbitrary $R$.
+For the proof~\cref{thm:DennisVaserstein} we need to show that the normalizer $N(A_{rs})$ is a sufficiently large subgroup.
+This is accomplished in the series of lemmas below. For example, the following lemma describes root subgroups 
+ contained in $N(A_{rs})$ regardless of whether the stability conditions of~\cref{thm:DennisVaserstein} are satisfied.
 \begin{lemma}\label{lemma:dv-normal} 
@@
 \end{proof}
-
+We also need a separate lemma to deal with the symplectic case.
 \begin{lemma}\label{lemma:DVST}
@@
 Thus, we have shown that $\mathcal{X}\subseteq L(A_{rs})$. 
-Recall from~\cite[Theorem~3.4]{S} that the group $\E(\Phi, R, I)$ is generated by the subset $\mathcal{Z}(\Sigma_s^-)$.
+Recall from~\cref{prop:Stepanov-theorem} that $\E(\Phi, R, I)$ is generated by $\mathcal{Z}(\Sigma_s^-)$.
 On the other hand, from $\mathcal{Z}(\Sigma_s^-) \subseteq \mathcal{X}^{\EP_s(R)} \subseteq L(A_{rs})^{N(A_{rs})} \subseteq L(A_{rs})$ we conclude that 
@@
 Recall from~\cite{LNS11, V13} that a Chevalley group over a field $\G(\Phi, F)$ can be presented as a product of at most $3|\Phi^+|$ of its subgroups $\SL(2, F)$.
-As an easy corollary of the relative Bass--Kolster decomposition we get that a similar factorization exists for relative groups over a rather general class of commutative rings.
+As an easy corollary of Bass--Kolster decomposition we get that a similar factorization also holds for relative groups over rings of small stable rank.
 \begin{thm}\label{thm:SL2width}
-Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system of rank $\ell$ satisfying one the following 4 conditions:
+Let $I\trianglelefteq R$ be an ideal, $\Phi$ be an irreducible classical root system of rank $\ell$ satisfying one the following conditions:
 \[\begin{array}{l@{\quad}l@{\quad}l}
@@
 The above lemmas together with \cref{cor:bass-kolster-count,thm:Gauss} imply the following result
- which is a quantitative analogue of \cite[Theorem~3.4]{S} and an analogue of the results of~\cite{VseUnitrZ1p, VavSmSuUnitrEng, Tavgen91} for relative groups.
+ which is an analogue of the results of~\cite{VseUnitrZ1p, VavSmSuUnitrEng, Tavgen91} for relative groups.
 \begin{thm}\label{thm:width} Let $I$ be an ideal of a commutative ring $R$.

### 2018-02-16 paper.tex
Minor fixes

@@
 These decompositions are used to obtain factorizations in terms of subsystem subgroups of type $\rA_\ell$ and 
- upper estimates of the width of principal congruence subgroups in terms of Tits--Vaserstein generators.
+ upper estimates of the width of principal congruence subgroups with respect to Tits--Vaserstein generators.
 %Some of our results are new even in the absolute case and were previously studied only for groups over finite fields.
@@
 As a further application of parabolic factorizations, we obtain in~\cref{thm:width} estimates of the width $\E(\Phi, R, I)$  
- with respect to this generating set in several special cases.
+ with respect to this generating set for some special rings $R$.
 

### 2018-02-19 paper.tex
Minor fixes

@@
 For an ideal $I \trianglelefteq R$ we denote by $\G(\Phi, R, I)$ the \emph{principal congruence subgroup} of level $I$.
-Recall that the \emph{relative elementary Chevalley subgroup} $\E(\Phi, R, I) \leqslant \G(\Phi, R, I)$ is defined as the normal closure in $\E(\Phi, R)$ of the subgroup $\E(\Phi, I)$ generated by the set $\mathcal{X} = \{x_\alpha(\xi) \mid \alpha\in \Phi, \ \xi \in I \}$.
+Recall that the \emph{relative elementary Chevalley subgroup} $\E(\Phi, R, I) \leqslant \G(\Phi, R, I)$ is defined as the normal closure in $\E(\Phi, R)$ of the subgroup 
+$\E(\Phi, I)$ generated by the set $\mathcal{X} = \{x_\alpha(s) \mid \alpha\in \Phi, \ s \in I \}$.
 
 For a subset of roots $S\subseteq\Phi$ denote by $\mathcal{Z}(S)$ the union of $\mathcal{X}$ and $\{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in S\}.$
-The following result describes generating sets of $\E(\Phi, R, I)$.
+%The following result describes generating sets of $\E(\Phi, R, I)$.
 \begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov-theorem} Let $\Phi$ be an irreducible root system of rank $\geq 2$ and $S \subseteq \Phi$ be an arbitrary parabolic subset of roots with special part $\Sigma_S$.
  Then the relative elementary subgroup $\E(\Phi, R, I)$ is generated as an abstract group by $\mathcal{Z}(\Sigma_S)$. \end{prop}
-Denote by $I^{\indexbox{2}}$ the ideal of $R$ generated by all squares $a^2$, where $a\in I$.
+For an ideal $I$ denote by $I^{\indexbox{2}}$ the ideal of $R$ generated by the squares of elements of $I$.
  \begin{lemma}[{\cite[Corollary~3.3]{S}}]\label{lemma:Stepanov-ideal}
@@
 \begin{proof}
-The first assertion follows from \eqref{rel:R3} and the well-known fact that $W(\Phi)$ acts transitively on the set of roots of the same length.
+The first assertion follows from \eqref{rel:R3} and the fact that $W(\Phi)$ acts transitively on the set of roots of the same length.
 The second assertion follows from \eqref{rel:R3} and \cref{lemma:abs}.
@@
 
-Define the semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
-The elements $h_\alpha(\varepsilon)$ satisfy the following relation:
+Recall that semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ are defined as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
+These elements satisfy the following relation:
 \begin{alignat}{2} 
@@
 
-For a special subset of roots $\Sigma\subseteq \Phi$ we denote by $\U(\Sigma, I)$ the subgroup spanned by all $x_{\alpha}(I)$ for $\alpha\in \Sigma$. 
+For a special subset of roots $\Sigma\subseteq \Phi$ we denote by $\U(\Sigma, I)$ the subgroup spanned by root subgroups $X_{\alpha}(I)$ for $\alpha\in \Sigma$. 
 For $J\subset\Pi$ the subgroup $\U(\Sigma_J^+, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I)$ is a subgroup, which we call a \emph{standard elementary parabolic subgroup}.
-The following two equalities will be referred to in the sequel as \emph{Levi decomposition}:
+In the sequel the following two identities will be referred to as \emph{Levi decomposition}:
 \begin{equation} \label{rel:Levi-decomp} \EP_J(R, I) = \U(\Sigma_J^+, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J^+, I). \end{equation}
-When $J = \{ \alpha_s \}$ for some $1 \leq s\leq \ell$, we use the shorthand $\EP_s(R, I)$ for $\EP_{\{s\}}(R, I)$.
-In the case $I=R$, we also write $\EP_J(R)$ instead of $\EP_J(R, R)$.
+When $J = \{ \alpha_s \}$ for some $1 \leq s\leq \ell$, we write $\EP_s(R, I)$ as a shorthand for $\EP_{\{s\}}(R, I)$.
+We also use the notation $\EP_J(R)$ instead of $\EP_J(R, R)$.
 

### 2018-02-22 paper.tex
Minor improvements

@@
 As a further application of parabolic factorizations, we obtain in~\cref{thm:width} estimates of the width $\E(\Phi, R, I)$  
- with respect to this generating set for some special rings $R$.
+ with respect to this generating set for some special rings having small stable rank.
 
 \section{Preliminaries}\label{sec:preliminaries}
-Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of fundamental roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
+Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
 We use the conventional numbering of basis vectors of $\Pi$ which follows Bourbaki (see~\cite[Table~1]{PSV98}).
-
 For a root $\alpha\in\Phi$ we denote by $m_i(\alpha)$ the $i$-th coefficient in the expansion of $\alpha$ in $\Pi$,
@@
 We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\beta, \beta)$.
-Let $\varpi_1, \ldots, \varpi_\ell$ be the \emph{fundamental weights }of $\Phi$.
-
-Denote by $W(\Phi)$ the subgroup of isometries of $\Phi$ generated by all simple reflections $\sigma_\alpha$, $\alpha\in\Phi$.
+The fundamental weights $P=\{\varpi_1,\ldots\varpi_\ell\}$ are defined as the basis dual to the simple coroots, i.\,e. $\langle \varpi_i, \alpha_j^{\vee} \rangle = \delta_{ij}$.
+
+Denote by $W(\Phi)$ the Weyl group, i.\,e. subgroup of isometries of $\Phi$ generated by all simple reflections $\sigma_\alpha$, $\alpha\in\Phi$.
 For a reductive subset $\Delta\subseteq \Phi$ denote by $W(\Delta)$ the subgroup of $W(\Phi)$ generated by $\sigma_\alpha$ for $\alpha\in\Delta$.
 
-Let $J\subseteq \Pi$ be a subset of fundamental roots. Define
+For a nonempty $J\subseteq \Pi$ consider the following subsets of roots:
 \begin{align*}
-& \shape(J, \beta)=\sum\nolimits_{i\in J} m_i(\beta) \alpha_i, \\
 & \Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\}, \\
@@
 We omit curly braces in the above notations when $J$ is a one- or two-element set, e.\,g. $\Delta_k=\Delta_{\{k\}}$ and $\Sigma_{i, j}^\pm=\Sigma_{\{i, j\}}^\pm$, etc.
-We call $\shape(\{\alpha_s\}, \beta)$ simply the $s$-shape of $\beta$.
-
+
+Define the $J$-shape of a root $\beta\in\Phi$ by the formula: $\shape(J, \beta)=\sum\nolimits_{i\in J} m_i(\beta) \alpha_i.$
 \begin{lemma}[{\cite[Lemma~1]{ABS}}]\label{lemma:abs}
-Let $\alpha, \beta \in \Sigma^\pm_J$ be a pair of roots having the same length such that $\shape(J, \alpha)=\shape(J, \beta)\neq 0$.
+Let $\alpha, \beta \in \Sigma^\pm_J$ be a pair of roots of the same length such that $\shape(J, \alpha)=\shape(J, \beta)\neq 0$.
 Then $\alpha$ and $\beta$ are conjugate under the action of $W(\Delta_J)$.
@@
 For a subset of roots $S\subseteq\Phi$ denote by $\mathcal{Z}(S)$ the union of $\mathcal{X}$ and $\{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in S\}.$
-%The following result describes generating sets of $\E(\Phi, R, I)$.
 \begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov-theorem} Let $\Phi$ be an irreducible root system of rank $\geq 2$ and $S \subseteq \Phi$ be an arbitrary parabolic subset of roots with special part $\Sigma_S$.
@@
 \item \label{item-trans1} For every two roots $\alpha, \beta \in \Phi$ of the same length there exists $w \in \widetilde{W}(\Phi)$ such that $X_{\alpha}(I)^w = X_\beta(I)$.
-\item \label{item-trans2} Let $\alpha_s\in \Pi$ be a fundamental root and $\alpha, \beta \in \Sigma^\pm_s$ be two roots having the same length and $s$-shape.
+\item \label{item-trans2} Let $\alpha_s\in \Pi$ be a fundamental root and $\alpha, \beta \in \Sigma^\pm_s$ be a pair of roots of the same length such that $m_s(\alpha) = m_s(\beta)$.
  Then there exists $w\in \widetilde{W}(\Delta_s)$ such that $X_\alpha(I)^w = X_\beta(I)$. \end{lemlist}
@@
 \[ \Hh(\Phi, R, I) = \Hh(\Phi, R)\cap\G(\Phi, R, I)=\langle h_\alpha(\varepsilon), \ \alpha\in\Phi, \ \varepsilon\in R^*\cap(1+I)\rangle. \]
-Consider an element $\varepsilon\in R^*\cap(1+I)$, and rewrite it as $\varepsilon=1+s$, $s\in I$. The element $h_\alpha(\varepsilon)$ can be expressed as
+It is not hard to see that $\Hh(\Phi, R, I) \leqslant \E(\Phi, R, I)$.
+Indeed, if $s\in I$ is such that $1+s\in R^*$, then $(1+s)^{-1}-1 \in I$ and we can factor $h_\alpha(\varepsilon)$ into a product of elements of $\E(\Phi, R, I)$ as follows:
 \begin{multline} \label{eq:rel-tor-elementary}
@@
 \end{multline}
-Notice that $(1+s)^{-1}\in 1+I$ hence all the above factors lie in $\E(\Phi, R, I)$. 
-This shows, in particular, that $\Hh(\Phi, R, I) \leqslant \E(\Phi, R, I)$.
-
-The following lemma is, in essence, a relative version of the classical Chevalley--Matsumoto decomposition.
-It can be easily deduced from the absolute statement (see e.\,g.~\cite[Theorem~1.3]{St78}).
+
+In the sequel we use elementary facts about representations of Chevalley groups (see e.\,g.~\cite{PSV98,VP} for a more detailed introduction).
+Let $L$ be the complex simple Lie algebra of type $\Phi$.
+To each element $\mu$ of the cone of dominants weights $\mathbb{Z}_{\geq 0}\langle P\rangle$
+ one can associate an irreducible finite dimensional complex representation $\pi \colon L \to \mathrm{gl}(V)$ with highest weight $\mu$.
+For our purposes it suffices to restrict our attention only to fundamental representations of $L$ (i.\,e. representations with highest weight $\varpi_i$),
+ which, moreover, we can assume to be {\it basic} in the sense of~\cite[\S~I.2]{Ma69}.
+
+Denote by $\Lambda(\pi)$ the set of weights of $\pi$. Recall that $V$ admits weight decomposition $V = V_0\oplus \bigoplus_{0\neq\lambda\in \Lambda(\pi)} V_\lambda$,
+ moreover, thanks to our assumptions, all $V_\lambda$'s corresponding to nonzero $\lambda$ are $1$-dimensional.
+By Chevalley--Ree theorem in any finite-dimensional representation $(\pi, V)$ of $L$ one can choose a basis $v_\lambda \in V_\lambda$,
+ with the property that $\pi(e_\alpha^{(m)})(v_\lambda)$ is an integral combination of $v_\lambda$ for every $m\in \mathbb{Z}_{\geq 0}$, $\alpha\in \Phi$.
+
+Consequently one can construct a representation $\G_{sc}(\Phi, R)$ on the free $R$-module $V_\mathbb{Z}\otimes R$ called a {\it Weyl module}.
+For us it will only be relevant that in the case of a basic representation, there are particularly nice formulae describing the action
+ of elementary root unipotents $x_\alpha(\xi)$ on weight spaces $V_\lambda$, $\lambda \in \Lambda(\pi)$, see~\cite[Lemme~2.3]{Ma69},
+ which can be, moreover, visualized using the technique of {\it weight diagrams} from \cite{PSV98}.
+
+The following lemma is, in essence, a relative version of Chevalley--Matsumoto decomposition which can be easily deduced from the absolute version (cf. \cite[Theorem~1.3]{St78}).
 \begin{lemma}\label{lemma:Chevalley-Matsumoto}
 Let $\pi$ be a basic fundamental representation of $\G_{sc}(\Phi, R)$ with highest weight $\varpi_s$.
-Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi_{s}}=1$, then $g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
-\end{lemma}
+Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi_{s}}=1$, then $g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$. \end{lemma}
+Here by $v^+$ we denote the highest vector of $\pi$ and by $v_\varpi$ the coordinate of $ $
 
@@
 In view of \cref{thm:Gauss} it suffices to show that Gauss decomposition holds in the special case $\Phi=\rA_1$.
-Let $A=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}$ be an element of $\SL(2, R, I)$.
-The first column of $A$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
-Multiplying $A$ on the left by $x_{12}(z)$, we get a matrix $A'=x_{12}(z)\cdot A=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible element $a'$ in the top-left corner.
-After multiplying $A'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
-Thus, we have obtained a relative Gauss decomposition for $A$:
+Let $g=\begin{psmallmatrix}a & b \\ c & d\end{psmallmatrix}$ be an element of $\SL(2, R, I)$.
+The first column of $g$ is $I$-unimodular, therefore there exists $z\in I$ such that $a+cz\in R^*$.
+Multiplying $g$ on the left by $x_{12}(z)$, we get a matrix $g'=x_{12}(z)\cdot g=\begin{psmallmatrix}a' & b' \\ c & d\end{psmallmatrix}$ with invertible element $a'$ in the top-left corner.
+After multiplying $g'$ on the left by $x_{21}(-c/a')$ and on the right by $x_{12}(-b'/a')$ we get a diagonal matrix. 
+Thus, we have obtained the sought Gauss decomposition for $g$:
 \begin{equation*}
-A=x_{12}(-z)\cdot x_{21}(c/a')\cdot
+g=x_{12}(-z)\cdot x_{21}(c/a')\cdot
 \begin{pmatrix} \varepsilon & 0 \\ 0 & 1/\varepsilon \end{pmatrix}
@@
 \end{equation*}
-where $\varepsilon\in 1+I$ and $y\in I$. \end{proof}
+for some $\varepsilon\in 1+I$ and $y\in I$. \end{proof}
 
@@
 \[\begin{array}{l @{\qquad} l @{\qquad} c @{\quad} c @{\quad} c @{\qquad} c @{\qquad} c @{\qquad} c}
-\Phi                                  & s    &r      & |\Lambda(\pi)| & \text{type of $\pi$} & \text{type of $\Delta_r$} & |\Lambda(\pi')|& |\Gamma|  \\ \hline\vphantom{\Bigl(}
+\Phi                                  & s    &r      & \mathrm{dim}(\pi) & \text{type} & \text{$\Delta_r$} & \mathrm{dim}(\pi') & |\Gamma|  \\ \hline\vphantom{\Bigl(}
 \rA_\ell, \ \ell\geqslant 2           & 1    &\ell   & \ell+1         & \text{natural}       & \rA_{\ell-1}              & \ell           & 1  \\     
@@
 \begin{proof}
-Let $\pi$ be the representation of $\G(\Phi, R)$ wit the highest weight $\varpi_s$ (see Table~\ref{table:dv-reps}).
-Denote by $\Lambda(\pi)$ the set of weights of $\pi$.
-We will be mainly concerned with the action of root unipotents $x_\alpha(\xi)$ on weight spaces $V_\lambda$, $\lambda \in \Lambda(\pi)$.
-Perhaps the most intuitive way to visualize this action is to use the technique of {\it weight diagrams}.
-We refer the reader to~\cite{PSV98}, where this technique is introduced properly and where the weight diagrams for the representations appearing in~\cref{table:dv-reps} have been depicted.
-
-Notice that $\Delta_r$ is an irreducible classical root system of type $\rA_\ell$, $\rC_\ell$ or $\rD_\ell$.
-Denote by $(\pi', V')$ the irreducible component of the restriction of $\pi$ to $\G(\Delta_r, R)$ containing the highest weight vector $v^+$ of $\pi$.
+Let $\Phi$, $r$ and $s$ be as in Table~\ref{table:dv-reps} and let $\pi \colon \G(\Phi, R) \to \mathrm{GL}(V_R)$ be the Weyl module with highest weight $\varpi_s$.
+The type and the dimension of $\pi$ are listed in Table~\ref{table:dv-reps}. %, see also~\cite{PSV98} where the weight diagrams of these representations are depicted.
+
+Notice that $\Delta_r$ is an irreducible classical root system of type $\rA_{\ell-1}$, $\rC_{\ell-1}$ or $\rD_{\ell-1}$.
+The restriction of $\pi$ to the subgroup $\G(\Delta_r, R)$ decomposes into a sum of Weyl modules for $\G(\Delta_r, R)$,
+ moreover, each such summand corresponds to a connected component of the weight diagram of $\pi_R$ in which all bonds marked $r$ are removed. 
+Denote by $(\pi', V')$ the summand containing the highest weight vector $v^+$ of $\pi$,
+ i.\,e. the summand corresponding to the top-left connected component of the diagram and denote by $\Lambda(\pi')$ the subset of weights belonging to this component.
 In all cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta_r, R)$.
 
-Set $\Gamma = \{\lambda \in \Lambda(\pi') \mid \lambda - \alpha_r \in \Lambda(\pi) \}.$
-We can visualize $\Gamma$ using {\it weight diagrams}  in the following manner.
-After removing all bonds marked $r$, the weight diagram of $\pi$ splits into several connected components.
-The subset $\Lambda(\pi') \subseteq \Lambda(\pi)$ corresponds to the component of the diagram containing the vertex corresponding to the highest weight.
-Clearly, $\Gamma$ consists of the weights of $\Lambda(\pi')$ incident to the removed bonds.
-From the consideration of weight diagrams it is easy to determine the number of elements in $\Lambda(\pi')$ and $\Gamma$ (see~Table~\ref{table:dv-reps}).
-
-Denote by $B$ the subset of $\E(\Delta_r, R, I)$ consisting of elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$.
-Set $A\coloneqq\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I).$
+Denote by $\Gamma$ the subset of weights $\lambda \in \Lambda(\pi')$ incident to the removed bonds (i.\,e. such that $\lambda - \alpha_r \in \Lambda(\pi)$).
+From the consideration of weight diagrams it is easy to determine the number of elements in $\Gamma$ (see~Table~\ref{table:dv-reps}).
+Denote by $B$ the subset of $\E(\Delta_r, R, I)$ consisting of elements $g$ such that $(g \cdot v^+)_\lambda = 0$ for all $\lambda\in\Gamma$ and
+set $A\coloneqq\U(\Phi^+, I)\cdot \U(\Phi^-, I) \cdot B \cdot \EP_s(R, I) \subseteq A_{rs}.$
+
+Now let us show that $A = A_{rs}$.
 Let $g$ be an element of $\E(\Delta_r, R, I)$. Applying \cref{lemma:uraction} to the subsystem $\Delta_r$, we find
-$x\in\U(\Delta_r^+, I)$ and $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
-This shows that $A = A_{rs}$, indeed:
+$x\in\U(\Delta_r^+, I)$ and $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$, therefore
 \begin{equation*} \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B.
@@
  \item \textit{Case $\Phi = \rF_4$, $s=4$, $r=1$.}
- There are three possibilities for the $s$-shape and length of $\alpha\in \Sigma_4^-$: 
+ For a root $\alpha\in \Sigma_4^-$ there are only $3$ possibilities for its length and the value of $m_4(-)$:
  \begin{itemize}
-  \item $\shape(\{\alpha_4\}, \alpha) = 1$, $\alpha$ is short (there are 8 such roots);
-  \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is long (there are 6 such roots);
-  \item $\shape(\{\alpha_4\}, \alpha) = 2$, $\alpha$ is short (there is only one such root, denote it by $\gamma$).
+  \item $m_4(\alpha) = -1$, $\alpha$ is short (there are 8 such roots);
+  \item $m_4(\alpha) = - 2$, $\alpha$ is long (there are 6 such roots);
+  \item $m_4(\alpha) = - 2$, $\alpha$ is short (there is only one such root, denote it by $\gamma$).
  \end{itemize}

### 2018-02-24 paper.tex
Improved treatment of representations

@@
 We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\beta, \beta)$.
-The fundamental weights $P=\{\varpi_1,\ldots\varpi_\ell\}$ are defined as the basis dual to the simple coroots, i.\,e. $\langle \varpi_i, \alpha_j^{\vee} \rangle = \delta_{ij}$.
+Recall that fundamental weights $\varpi_1,\ldots,\varpi_\ell$ are characterized by the property that $\langle \varpi_i, \alpha_j \rangle = \delta_{ij}$.
 
@@
 In the sequel we use elementary facts about representations of Chevalley groups (see e.\,g.~\cite{PSV98,VP} for a more detailed introduction).
-Let $L$ be the complex simple Lie algebra of type $\Phi$.
-To each element $\mu$ of the cone of dominants weights $\mathbb{Z}_{\geq 0}\langle P\rangle$
- one can associate an irreducible finite dimensional complex representation $\pi \colon L \to \mathrm{gl}(V)$ with highest weight $\mu$.
-For our purposes it suffices to restrict our attention only to fundamental representations of $L$ (i.\,e. representations with highest weight $\varpi_i$),
- which, moreover, we can assume to be {\it basic} in the sense of~\cite[\S~I.2]{Ma69}.
-
-Denote by $\Lambda(\pi)$ the set of weights of $\pi$. Recall that $V$ admits weight decomposition $V = V_0\oplus \bigoplus_{0\neq\lambda\in \Lambda(\pi)} V_\lambda$,
- moreover, thanks to our assumptions, all $V_\lambda$'s corresponding to nonzero $\lambda$ are $1$-dimensional.
-By Chevalley--Ree theorem in any finite-dimensional representation $(\pi, V)$ of $L$ one can choose a basis $v_\lambda \in V_\lambda$,
- with the property that $\pi(e_\alpha^{(m)})(v_\lambda)$ is an integral combination of $v_\lambda$ for every $m\in \mathbb{Z}_{\geq 0}$, $\alpha\in \Phi$.
-
-Consequently one can construct a representation $\G_{sc}(\Phi, R)$ on the free $R$-module $V_\mathbb{Z}\otimes R$ called a {\it Weyl module}.
-For us it will only be relevant that in the case of a basic representation, there are particularly nice formulae describing the action
- of elementary root unipotents $x_\alpha(\xi)$ on weight spaces $V_\lambda$, $\lambda \in \Lambda(\pi)$, see~\cite[Lemme~2.3]{Ma69},
- which can be, moreover, visualized using the technique of {\it weight diagrams} from \cite{PSV98}.
-
-The following lemma is, in essence, a relative version of Chevalley--Matsumoto decomposition which can be easily deduced from the absolute version (cf. \cite[Theorem~1.3]{St78}).
+Recall that, by definition, the {\it cone of dominant weights} $P_{++}(\Phi)$ consists of all nonnegative integral linear combinations of fundamental weights $\varpi_1,\ldots \varpi_\ell$.
+To each element $\mu \in P_{++}(\Phi)$ one can associate a representation $\pi$ of $\G(\Phi, R)$ on a free $R$-module $V = V(\mu)$, called {\it Weyl module}.
+For our purposes it suffices to restrict attention to representations with fundamental highest weight (i.\,e.
+$\mu=\varpi_i$ for some $i$), which are, moreover, {\it basic} in the sense of~\cite[\S~I.2]{Ma69}.
+The latter condition guarantees, in particular, that all weight subspaces $V^\lambda \leq V$ corresponding to nonzero weights $\lambda$ have dimension $1$.
+Denote by $\Lambda(\pi)$ the set of weights of $\pi$ with multiplicities (i.\,e. the zero weight is repeated $\dim(V^0)$ times).
+
+By the very construction of $V(\mu)$, there is a basis $\{e_\lambda\}$, $e_\lambda\in V^\lambda$ parameterized by elements $\lambda\in\Lambda(\pi)$ called {\it admissible basis}.
+The key property of basic representations which we use in the sequel is that there are particularly simple formulae describing the action
+ of elementary root unipotents $x_\alpha(\xi)$ on the vectors of admissible basis (see~\cite[Lemme~2.3]{Ma69}),
+ which, moreover, can be visualized using the technique of {\it weight diagrams} (see e.\,g.~\cite{PSV98}).
+
+We denote by $v^+$ the {\it highest weight vector}, i.\,e. the basis vector $e_\mu$ corresponding to the highest weight $\mu$ of $V(\mu)$.
+For $v\in V(\mu)$ we denote by $v_\lambda$ the coordinate of $v$ in the expansion of $v$ in $\{e_\lambda\}$, moreover if $\pi$ is a faithful representation we can 
+identify $g\in \G(\Phi, R)$ with the matrix $(g_{\lambda, \nu})$, where $g_{\lambda, \nu} = (\pi(g)\cdot e_\nu)_{\lambda}$.
+The following lemma is, in essence, a relative version of Chevalley--Matsumoto decomposition which can be easily deduced from the absolute statement (cf. \cite[Theorem~1.3]{St78}).
 \begin{lemma}\label{lemma:Chevalley-Matsumoto}
-Let $\pi$ be a basic fundamental representation of $\G_{sc}(\Phi, R)$ with highest weight $\varpi_s$.
-Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi_{s}}=1$, then $g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$. \end{lemma}
-Here by $v^+$ we denote the highest vector of $\pi$ and by $v_\varpi$ the coordinate of $ $
+Let $\pi$ be a basic fundamental representation of $\G_{sc}(\Phi, R)$ with highest weight $\mu = \varpi_s$.
+Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\mu}=1$, then $g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$. \end{lemma}
 
@@
 
-In this section we work with standard vector representations of classical groups (i.\,e. representations with highest weight $\varpi_1$).
+In this section we work with natural representations of classical groups (i.\,e. representations with highest weight $\varpi_1$).
 It will be convenient for us to number the weights of these representations as in~\cite[\S~1B]{St78}:
@@
 Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ such that $\lambda_1-\lambda_2\in \Phi$.
-It will be convenient for us to write $x_{\lambda_1, \lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
-For example, for $\Phi=\rA_\ell$ we have $x_{1, 2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
+For notational convenience we write $x_{\lambda_1, \lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
+For example, for $\Phi=\rA_\ell$ the notation $x_{1, 2}(\xi)$ has the same meaning as $x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
 
@@
 \begin{proof}
-Let $\Phi$, $r$ and $s$ be as in Table~\ref{table:dv-reps} and let $\pi \colon \G(\Phi, R) \to \mathrm{GL}(V_R)$ be the Weyl module with highest weight $\varpi_s$.
+Let $\Phi$, $r$ and $s$ be as in Table~\ref{table:dv-reps} and let $\pi$ be the representation of $\G(\Phi, R)$ on the Weyl module $V(\mu)$ with highest weight $\mu=\varpi_s$.
 The type and the dimension of $\pi$ are listed in Table~\ref{table:dv-reps}. %, see also~\cite{PSV98} where the weight diagrams of these representations are depicted.
@@
 
-Now let us show that $A = A_{rs}$.
-Let $g$ be an element of $\E(\Delta_r, R, I)$. Applying \cref{lemma:uraction} to the subsystem $\Delta_r$, we find
-$x\in\U(\Delta_r^+, I)$ and $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$, therefore
+We claim that $A = A_{rs}$. Indeed, let $g$ be an element of $\E(\Delta_r, R, I)$. 
+Applying \cref{lemma:uraction} to the subsystem $\Delta_r$, we find $x\in\U(\Delta_r^+, I)$ and $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
+Consequently we have the following inclusion:
 \begin{equation*} \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B.
@@
 Let $\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and let $I$ be an ideal of $\mathcal{O}_S$.
-
 \begin{lemma}\label{lemma:width-dedekind}
@@
 By \cref{lemma:Stepanov-ideal} the group $\E\left(\Phi, \mathcal{O}_S, I^2\right)$ is contained in $\E(\Phi, I)$ for any root system $\Phi\neq\rC_\ell$ of rank $\geqslant2$.
-Notice that under the assumptions of the lemma it is known that $\E(\Phi, I)$ has finite width with respect to $\mathcal{X}$, see~\cite[Theorem~3.3]{TavgenThesis}.
+Notice that under the assumptions of the lemma a deep result of O.~Tavgen asserts that $\E(\Phi, I)$ has finite width with respect to $\mathcal{X}$, see~\cite[Theorem~3.3]{TavgenThesis}.
 

### 2018-02-25 paper.tex
More fixes

@@
 (in fact, a smaller generating set suffices, see~\cref{prop:Stepanov-theorem}).
-As a further application of parabolic factorizations, we obtain in~\cref{thm:width} estimates of the width $\E(\Phi, R, I)$  
- with respect to this generating set for some special rings having small stable rank.
+In section~\ref{sec:boundgen} we deduce from an earlier result of O.~Tavgen that the width $\E(\Phi, R, I)$ with respect to this generating set is
+ finite for Dedeking rings of arithmetic type having a real embedding.
+Moreover, as a further application of parabolic factorizations, we obtain in~\cref{thm:width} concrete estimates of such width
+ for ideals of the ring $\mathbb{Z}[\sfrac{1}{p}]$ and also for ideals of stable rank $1$.
 
@@
 Next, in section~\ref{sec:rel-asr} we define relative version of the absolute stable range condition introduced in~\cite{EO, MKV}.
-Finally, we formulate and prove several technical lemmas describing the action of certain unipotent subgroups on unimodular columns under the assumption of suitable stability conditions.
+Finally, we formulate and prove several technical lemmas about the action of certain unipotent subgroups on unimodular columns under suitable stability assumptions.
 
@@
 We denote the set of all $I$-unimodular rows (resp. columns) by $\Umd(n, I)$ (resp. $\Ums(n, I)$).
-When $I=R$, we refer to $R$-unimodular rows and columns as simply \emph{unimodular}.
+We refer to $R$-unimodular rows and columns as simply \emph{unimodular}.
 It is not hard to show that for an $I$-unimodular row $a$ there exists an $I$-unimodular column $b$ such that $ab=1$ (see~\cite[\S2]{Va69}).
@@
 An $I$-unimodular row $a=(a_1, \ldots, a_{n+1})$ is called \emph{stable} if one can choose $b_1, \ldots, b_n\in I$ such that the row $(a_1+a_{n+1}b_1, \ldots, a_n+a_{n+1}b_n)$ is also $I$-unimodular. 
-We say that $I$ satisfies the stable range condition $\SR_n(I)$ if any $I$-unimodular row of length $n+1$ is stable.
+We say that $I$ satisfies the condition $\SR_n(I)$ if any $I$-unimodular row of length $n+1$ is stable.
 For $m \geqslant n$ the condition $\SR_n(I)$ implies $\SR_m(I)$, see~\cite[Theorem~1]{Va71}.
-It is also clear that the condition $\SR_n(I)$ does not depend on the choice of the ambient ring $R$.
+It is also clear that the condition $\SR_n(I)$ does not depend on the choice of the ring $R$.
 By definition, the \emph{stable rank} of $I$ (denoted $\sr(I)$) is the smallest natural number $n$ such that $\SR_n(I)$ holds (we set $\sr(I)=\infty$ if no such $n$ exists).
@@
 \subsection{Action of unipotent radicals}\label{sec:ur-action}
-
 In this section we work with natural representations of classical groups (i.\,e. representations with highest weight $\varpi_1$).
@@
 \begin{lemma}\label{lemma:asrUnip}
-For any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$ there exists $g\in\U(\Sigma^+_\ell, I) \leq \E(\Phi, R, I)$ 
-such that $(g \cdot v)_+ \in \Ums(\ell, I)$ under the following assumptions on $\Phi$ and $I$.
+Assume that one of the following holds:
 \begin{lemlist}
@@
 \end{lemlist}
+Then for any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$ there exists $g\in\U(\Sigma^+_\ell, I) \leq \E(\Phi, R, I)$ 
+such that $(g \cdot v)_+ \in \Ums(\ell, I)$.
 \end{lemma}
@@
 \textsc{Case $\Phi=\rC_\ell$.}
-Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are on the skew-diagonal, i.\,e. $p_{ij}=\delta_{i, \ell-j+1}$. 
+Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are located on the skew-diagonal, i.\,e. $p_{ij}=\delta_{i, \ell-j+1}$. 
 For $b \in M(\ell, I)$ set $g(b)=\left(\begin{smallmatrix} e_\ell & p \cdot b \\ 0 & e_{\ell} \end{smallmatrix}\right)$.
@@
 \textsc{Case $\Phi=\rD_\ell$.} Denote by $J$ the ideal of $R$ spanned by the components of $v_{-}$. Clearly, $J \subseteq I$.
-Since $\sr(I/J) \leqslant \ell-1$, the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see~\cite[Theorem~2.3c]{Va69}). 
+Since $\sr(I/J) \leqslant \ell-1$, the elementary group $\E(\rA_{\ell-1}, R/J, I/J)$ acts transitively on $\Ums(\ell, I/J)$ (see e.\,g.~\cite[Theorem~2.3c]{Va69}). 
 This implies the existence of an element $h\in \E(\Delta_\ell, R, I)$ such that the vector $v' = h \cdot v$ satisfies $v'_i \equiv \delta_{i1} \pmod J$ for $i=1, \ldots, \ell$.
@@
 \end{lemma}
-\begin{proof} Denote by $v$ the image of the highest weight vector $v^+$ under $g$.
-
-\textsc{Case $\Phi=\rA_\ell$.} From the definition of the relative stable rank it follows that we can find 
+\begin{proof} Denote by $v$ the first column of $g$ (i.\,e. $v=\pi(g)\cdot v^+$).
+
+\textsc{Case $\Phi=\rA_\ell$.} From the definition of relative stable rank it follows that we can find 
 $x= \left(\begin{smallmatrix} e_k & a \\ 0 & e_{n-k} \end{smallmatrix}\right) \in \U(\Sigma_k^+, I)$ such that 
@@
 
-Let $G$ be a group and $A$ its subset. Denote by $L(A)$, $R(A)$ and $N(A)$ the left and the right stabilizers of $A$ and the normalizer of $A$:
+Let $G$ be a group and $A$ its subset. Denote by $L(A)$, $R(A)$ the left and the right stabilizers of $A$ and by $N(A)$ the normalizer of $A$:
 \begin{align*} 
- L(A) & =  \left\{ g\in G\ \middle |\ g \cdot A \cup g^{-1} \cdot A \subseteq A \right\}\!,\\
- R(A) & =  \left\{ g\in G\ \middle |\ A \cdot g \cup A \cdot g^{-1} \subseteq A \right\}\!,\\
+ L(A) & =  \left\{ g\in G\ \middle |\ g \cdot A = A \right\}\!,\\
+ R(A) & =  \left\{ g\in G\ \middle |\ A \cdot g = A \right\}\!,\\
  N(A) & =  \left\{ g\in G\ \middle |\ g \cdot A \cdot g^{-1} \cup g^{-1} \cdot A \cdot g \subseteq A \right\}.
@@
 \subsection{Relative Dennis--Vaserstein decompositions}\label{sec:dennis-vaserstein}
-Let $\Phi$ be an irreducible root system of rank $\ell\geq 2$.
-Let $\{r, s\}$ be the indices of a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
-
-Before we proceed with the proof of~\cref{thm:DennisVaserstein} let us remark that in the special case $\ell=2$, $\sr(I)\leq 1$
+Let $\Phi$ be an irreducible root system of rank $\ell\geq 2$ and $\{r, s\}$ be a pair of distinct endnodes of the Dynkin diagram of $\Phi$.
+
+Before we proceed with the proof of~\cref{thm:DennisVaserstein} let us remark that in the special case $\ell=2$, $\sr(I)= 1$
  we already known that $\E(\Phi, R, I)$ admits Gauss decomposition.
-It is not hard to see that Dennis--Vaserstein decomposition follows from Gauss decomposition, 
- therefore, in the sequel we may assume, without loss of generality, that $\ell > 2$.
-
-From Levi decomposition~\eqref{rel:Levi-decomp} we obtain the following equality of subsets of $\E(\Phi, R, I)$:
+It is not hard to see that Dennis--Vaserstein decomposition follows from Gauss decomposition.
+Thus, in the sequel we may assume, without loss of generality, that $\ell > 2$.
+
+From Levi decomposition~\eqref{rel:Levi-decomp} it follows that the following subsets of $\E(\Phi, R, I)$ are equal:
 \begin{multline*}
@@
 Denote the above subset by $A_{rs}$. 
-Notice that the equality $A_{rs} = \E(\Phi, R, I)$ implies symmetric equality $A_{sr} = \E(\Phi, R, I)$, 
- therefore it suffices to consider only the following possibilities for $\Phi$, $s$, $r$.
+Notice that the equality $A_{rs} = \E(\Phi, R, I)$ implies $A_{sr} = \E(\Phi, R, I)$, 
+ therefore it suffices to consider only the possibilities for $\Phi$, $s$, $r$ listed in~\cref{table:dv-reps}.
 
@@
 This is accomplished in the series of lemmas below. For example, the following lemma describes root subgroups 
- contained in $N(A_{rs})$ regardless of whether the stability conditions of~\cref{thm:DennisVaserstein} are satisfied.
+ which are contained in $N(A_{rs})$ for obvious reasons.
 \begin{lemma}\label{lemma:dv-normal} 
@@
 Denote by $(\pi', V')$ the summand containing the highest weight vector $v^+$ of $\pi$,
- i.\,e. the summand corresponding to the top-left connected component of the diagram and denote by $\Lambda(\pi')$ the subset of weights belonging to this component.
+ i.\,e. the summand corresponding to the top-left connected component of the diagram. Denote by $\Lambda(\pi')$ the subset of weights belonging to this component.
 In all cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta_r, R)$.
 
-Denote by $\Gamma$ the subset of weights $\lambda \in \Lambda(\pi')$ incident to the removed bonds (i.\,e. such that $\lambda - \alpha_r \in \Lambda(\pi)$).
+Denote by $\Gamma$ the subset of weights $\lambda \in \Lambda(\pi')$ incident to the removed bonds (i.\,e. $\lambda$ such that $\lambda - \alpha_r \in \Lambda(\pi)$).
 From the consideration of weight diagrams it is easy to determine the number of elements in $\Gamma$ (see~Table~\ref{table:dv-reps}).
@@
 Applying \cref{lemma:uraction} to the subsystem $\Delta_r$, we find $x\in\U(\Delta_r^+, I)$ and $y\in \U(\Delta_r^-, I)$ such that $yx\cdot g \in B$.
-Consequently we have the following inclusion:
+Consequently we obtain the required inclusion:
 \begin{equation*} \U(\Sigma^+_r, I) \cdot \U(\Sigma^-_r, I) \cdot g = \U(\Sigma^+_r, I) x^{-1} \cdot \U(\Sigma^-_r, I)^{x^{-1}} y^{-1} (yxg) \subseteq \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B.
@@
 \end{equation*}
-Finally, since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$, we obtain the required assertion, indeed:
+Since $[B, X_{-\alpha_r}(R)] \subseteq \U(\Sigma_r^-, R) \cap \E(\Phi, R, I) = \U(\Sigma_r^-, I)$, we obtain the assertion of the lemma, indeed:
 \begin{equation*} \label{rel:ninv} A^{X_{-\alpha_{r}}(R)} = \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot B ^{X_{-\alpha_{r}}(R)} \cdot \EP_s(R, I) = A. \qedhere \end{equation*}
@@
 satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$.
-Consequently, one has
+Thus, we obtain the assertion of the lemma, indeed:
 \begin{multline*} {A_{\ell 1}}^{X_{-\alpha_{1}}(R)} \subseteq \EP_\ell(R, I)^{X_{-\alpha_1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{-\alpha_1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\
-\subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell 1}, \end{multline*} as claimed.
+\subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell 1}. \qedhere \end{multline*}
 \end{proof}
@@
 \begin{proof}
- As in the proof of \cref{cor:bass-kolster-iterated}, one has to iteratively apply \cref{thm:BassKolster}.
+ As in the proof of \cref{cor:bass-kolster-iterated}, the assertion is obtained via iterative application of~\cref{thm:BassKolster}.
  To reduce the number of $\SL_2$-factors involved in the decompositoin one has to group into a single $\SL_2$-factor a pair of opposite root subgroups $X_{\alpha}(I)$, $X_{-\alpha}(I)$ (or $Z_{\pm\alpha}(I)$) appearing on each
  of the $3$ junctions between the positive and negative unipotent subgroups in the Bass--Kolster decomposition.
- Since a total of $\ell-1$ reductions are used, we get the estimate $N \leq N' - 3(\ell - 1) + 1$ and the assertion of \cref{thm:SL2width} follows.
+ Since a total of $\ell-1$ reductions are used, we get the required estimate $N \leq N' - 3(\ell - 1) + 1$.
 \end{proof}
@@
 \]
-Take an element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ and decompose it as $u=vw$, where $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $w\in\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$.
+Every element $u\in\U(\Sigma_2^-\cap\Delta_\ell, I)$ can be decomposed as $u=vw$ for some $v\in\U(\Sigma_1^-\cap\Sigma_2^-\cap\Delta_\ell, I)$ and $w\in\U(\Sigma_2^-\cap\Delta_{1, \ell}, I)$.
 Using the identity
@@
 \begin{proof}
-Take an element $g\in\E(\Phi,R,I)$ and decompose it into $g=u_1 h v_2 u_3$, where $h\in\Hh(\Phi,R,I)$, $u_1,u_3\in\U(\Phi,I)$, $v_2\in\U(\Phi^-,I)$. 
+Every element $g\in\E(\Phi,R,I)$ can be written as a product $g=u_1 h v_2 u_3$ for some $h\in\Hh(\Phi,R,I)$, $u_1,u_3\in\U(\Phi,I)$, $v_2\in\U(\Phi^-,I)$. 
 Write $h=\prod_{i=1}^\ell h_{\alpha_i}(\varepsilon_i)$, $\varepsilon\in1+I$. 
-Each $h_{\alpha_i}(\varepsilon_i)$ decomposes into $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$ 
-(see \eqref{eq:rel-tor-elementary}), and since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we can decompose $g$ as follows:
-\[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I), \]
-and the estimate follows.
-\end{proof}
+In view of formula~\eqref{eq:rel-tor-elementary} the element $h_{\alpha_i}(\varepsilon_i)$ can be factored as 
+ $h_{\alpha_i}(\varepsilon_i) = x_{\alpha_i}(*) z_{-\alpha_i}(*,*) x_{-\alpha_i}(*)$.
+Since the torus normalizes each of $X_\alpha(I)$ (see formula~\eqref{rel:h-w}), we can rewrite $g$ in the following manner, from which the estimate follows:
+\[ g\in\U(\Phi,I)\cdot\prod_{i=1}^\ell\bigl(x_{\alpha_i}(*)z_{-\alpha_i}(*,*)\bigr)\cdot \U^-(\Phi,I) \U(\Phi,I). \qedhere \] \end{proof}
 
@@
 \begin{lemma}
-Let $p$ be a rational prime, let $c$, $d$ be a pair of coprime integers such that $p \perp d$.
+Let $p$ be a rational prime and $c$, $d$ be a pair of coprime integers such that $p \perp d$.
 Then under the assumption of the Generalized Riemann Hypothesis there exist infinitely many primes $q\equiv c\pmod{d}$ such that $p$ is a primitive root modulo $q$.
@@
 Under the assumption of the GRH the width of $\SL(2, R, I)$ with respect to the generating set
-\[ \mathcal{Z}(\{-\alpha_1\})=X_{12}(I)\cup X_{21}(I) \cup \{z_{21}(s, \xi) \mid s\in I,\ \xi\in R\} \]
+$\mathcal{Z}(\{-\alpha_1\})=X_{12}(I)\cup X_{21}(I) \cup \{z_{21}(s, \xi) \mid s\in I,\ \xi\in R\}$
 does not exceed $6$.
@@
 One can choose $k>\beta-\alpha$.
-Then $k+\alpha>-k+\beta$ and
-\[ h_{12}\left(p^k\right)\cdot g =
+Then $k+\alpha>-k+\beta$ and we obtain that
+\[ h_{12} (p^k)\cdot g =
 \begin{pmatrix} p^k & 0 \\ 0 & p^{-k} \end{pmatrix}
@@
 
-For the rest of this subsection $k$ denotes a global field and $S$ some finite set of places on $k$. 
+For the rest of this subsection $k$ denotes a global field and $S$ is a finite set of places on $k$. 
 Let $\mathcal{O}_S$ be the Dedekind ring of arithmetic type defined by $S$ and let $I$ be an ideal of $\mathcal{O}_S$.
@@
 From $\det(g)=1$ we conclude that $a+d=bc-ad\in I^2$. 
-Recall that the Vaserstein's congruence subgroup is defined as
+Recall that Vaserstein's congruence subgroup is defined as
 \[ G(I, I)=\left\{ \begin{pmatrix}1+a & b \\ c & 1+d\end{pmatrix}\in\SL(2, \mathcal{O}_S)\;\middle|\; a, d\in I^2, \ b, c\in I \right\}. \]
-Notice that $g_1=g\cdot z_{21}(a, 1)$ is contained in $G(I, I)$, indeed,
+Notice that $g_1=g\cdot z_{21}(a, 1)$ is contained in $G(I, I)$
 \[ \begin{pmatrix} 1+a & b \\ c & 1+d \end{pmatrix} \cdot \begin{pmatrix} 1-a & -a \\ a & 1+a \end{pmatrix} = \begin{pmatrix} 1+ba-a^2 & b-a-ba-a^2 \\ c+a+ad-ac & 1+bc-ac \end{pmatrix} \in G(I, I). \]
-For any matrix $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I, I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)$ lies in $\SL\left(2, \mathcal{O}_S, I^2\right)$.
+For any $g'=\begin{psmallmatrix}1+a & b \\ c & 1+d\end{psmallmatrix}\in G(I, I)$ the matrix $x_{21}(-c)\cdot g'\cdot x_{12}(-b)$ lies in $\SL\left(2, \mathcal{O}_S, I^2\right)$.
 
@@
 \[ \det(g_1)=a^3d-3a^2bc+a^2bd+ab^2c+a^3+a^2b+a^2d+2abc-abd+1. \]
-This means that
+Consequently we obtain that
 \[ g_2=x_{21}(-a-c)\cdot g_1\cdot x_{12}(a-b)\equiv
@@
 \end{pmatrix}\bmod II^{\indexbox{2}}. \]
-Now for $g_3=g_2\cdot z_{12}\left(a^2-ab, 1\right)$ we have that
+Now for $g_3=g_2\cdot z_{12}\left(a^2-ab, 1\right)$ the following congruences hold:
 \begin{align*}
@@
 \end{align*}
-Thus $g_4\cdot x_{21}(*)\in\SL\left(2, \mathcal{O}_S, II^{\indexbox{2}}\right)$ is contained in $\E(\rC_\ell, I)$ by \cref{lemma:Stepanov-ideal} and therefore can be expressed as a bounded product of $x_\alpha$.
+Thus $g_4\cdot x_{21}(*)\in\SL(2, \mathcal{O}_S, II^{\indexbox{2}})$ is contained in $\E(\rC_\ell, I)$ by \cref{lemma:Stepanov-ideal} and therefore
+can be expressed as a bounded product of elements $x_\alpha(*)$.
 \end{proof}

### 2018-02-25 paper.tex
More fixes

@@
 In section~\ref{sec:boundgen} we deduce from an earlier result of O.~Tavgen that the width $\E(\Phi, R, I)$ with respect to this generating set is
- finite for Dedeking rings of arithmetic type having a real embedding.
+ finite for Dedekind rings of arithmetic type having a real embedding.
 Moreover, as a further application of parabolic factorizations, we obtain in~\cref{thm:width} concrete estimates of such width
@@
 Using the Levi decomposition we can write $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
-It is clear that $x$, $y$ are the desired elements.
+It is clear that $x$, $y$ are the required elements.
 \end{proof}
@@
 Let $G$ be a group and $A$ its subset. Denote by $L(A)$, $R(A)$ the left and the right stabilizers of $A$ and by $N(A)$ the normalizer of $A$:
-\begin{align*} 
- L(A) & =  \left\{ g\in G\ \middle |\ g \cdot A = A \right\}\!,\\
- R(A) & =  \left\{ g\in G\ \middle |\ A \cdot g = A \right\}\!,\\
- N(A) & =  \left\{ g\in G\ \middle |\ g \cdot A \cdot g^{-1} \cup g^{-1} \cdot A \cdot g \subseteq A \right\}.
-\end{align*}
+\[ L(A) =  \left\{ g\in G\ \middle |\ g \cdot A = A \right\}\!,\ \ R(A) =  \left\{ g\in G\ \middle |\ A \cdot g = A \right\}\!,\ \ N(A) =  \left\{ g\in G\ \middle |\ g \cdot A \cdot g^{-1} = A \right\}.\]
 It is easy to see that $L(A)$, $R(A)$ and $N(A)$ are subgroups of $G$. The following obvious lemma will be used several times in the sequel.
@@
 \begin{proof}
-Let $h \in L(A)$, $g \in N(A)$. The first claim follows from the following chain of inclusions:
-\begin{equation} h^g \cdot A = g^{-1} \cdot h \cdot g \cdot A \cdot g^{-1} \cdot g \subseteq g^{-1} \cdot h \cdot A \cdot g \subseteq {A}^g \subseteq A. \end{equation} 
-Now if, in addition, $g \in R(A)$ we obtain
-$g \cdot A = g \cdot A \cdot g^{-1} \cdot g \subseteq A \cdot g \subseteq A,$ which implies the second claim.
+Let $h \in L(A)$, $g \in N(A)$. The first claim follows from the following chain of equalities:
+\begin{equation} h^g \cdot A = g^{-1} \cdot h \cdot g \cdot A \cdot g^{-1} \cdot g = g^{-1} \cdot h \cdot A \cdot g = {A}^g = A. \end{equation} 
+Now if $g \in R(A) \cap N(A)$, we obtain
+$g \cdot A = g \cdot A \cdot g^{-1} \cdot g = A \cdot g = A,$ which implies the second claim.
 \end{proof}
@@
 \end{multline}
+Thus, $A$ is normalized by root subgroups $X_\alpha(R)$, $\alpha \in \Delta_1 \cup \Delta_\ell$ and therefore is normalized by $\E(\Phi, R)$.
 On the other hand, for $\beta \in \Phi^+$ we have
@@
 \end{equation}
-Thus, $A$ is normalized by root subgroups $X_\alpha(R)$, $\alpha \in \Delta_1 \cup \Delta_\ell$ and therefore is normalized by $\E(\Phi, R)$.
-On the other hand, from $\U(\Phi^+, I) \cdot A \subseteq A$ and~\cref{lem:LN} we conclude that $\mathcal{X} \cdot A \subseteq A$ and hence
+Thus, from $\U(\Phi^+, I) \subseteq L(A)$ and~\cref{lem:LN} we obtain that $\mathcal{X} \cdot A \subseteq A$ and hence
  that $\E(\Phi, R, I) \cdot A \subseteq A$.
@@
 The restriction of $\pi$ to the subgroup $\G(\Delta_r, R)$ decomposes into a sum of Weyl modules for $\G(\Delta_r, R)$,
- moreover, each such summand corresponds to a connected component of the weight diagram of $\pi_R$ in which all bonds marked $r$ are removed. 
+ moreover, each such summand corresponds to a connected component of the diagram obtained from the weight diagram of $\pi_R$ by removing all bonds marked $r$. 
 Denote by $(\pi', V')$ the summand containing the highest weight vector $v^+$ of $\pi$,
- i.\,e. the summand corresponding to the top-left connected component of the diagram. Denote by $\Lambda(\pi')$ the subset of weights belonging to this component.
+ i.\,e. the summand corresponding to the top-left connected component of the diagram. Denote by $\Lambda(\pi') \subseteq \Lambda(\pi)$ the subset of weights belonging to this component.
 In all cases under consideration, $\pi'$ is isomorphic to the natural representation of $\G(\Delta_r, R)$.
 
-Denote by $\Gamma$ the subset of weights $\lambda \in \Lambda(\pi')$ incident to the removed bonds (i.\,e. $\lambda$ such that $\lambda - \alpha_r \in \Lambda(\pi)$).
+Denote by $\Gamma$ the subset of weights $\lambda \in \Lambda(\pi')$ such that $\lambda - \alpha_r \in \Lambda(\pi)$,
+ in other words, $\Gamma$ consists of weights corresponding to vertices of the weight diagram which are incident to the removed bonds.
 From the consideration of weight diagrams it is easy to determine the number of elements in $\Gamma$ (see~Table~\ref{table:dv-reps}).

### 2018-02-25 paper.tex
Minor fix

@@
 As another application, we obtain results on the bounded generation of the relative elementary group.
-Recall from~\cite[Theorem~2]{Va86} that $\E(\Phi, R, I)$ can be generated by the set of Tits--Vaserstein generators
+Recall from~\cite[Theorem~2]{Va86} that $\E(\Phi, R, I)$ can be generated by the set of Stein--Tits--Vaserstein generators
  $z_\alpha(s, \xi) =  x_{-\alpha}(-\xi) x_\alpha(s) x_{-\alpha}(\xi)$, where $s\in I$ and $\xi\in R$

### 2018-06-26 paper.tex
More fixes

@@
 
-\newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label={\rm(\arabic{thmlisti})}, ref=\thethm.(\roman{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
-\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label={\rm(\arabic{lemlisti})}, ref=\thelemma.(\roman{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
+\newlist{thmlist}{enumerate}{1} \setlist[thmlist]{label={\rm(\arabic{thmlisti})}, ref=\thethm.(\arabic{thmlisti}),noitemsep} \Crefname{thmlisti}{Theorem}{Theorems}
+\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label={\rm(\arabic{lemlisti})}, ref=\thelemma.(\arabic{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
 
@@
 \section{Preliminaries}\label{sec:preliminaries}
-Let $\Phi$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
+Let $\Phi \subseteq \mathbb{R}^\ell$ be a reduced irreducible root system of rank $\ell$ with a fixed basis of simple roots $\Pi=\{\alpha_1, \ldots, \alpha_l\}$.
 We use the conventional numbering of basis vectors of $\Pi$ which follows Bourbaki (see~\cite[Table~1]{PSV98}).
@@
 We denote by $(\alpha, \beta)$ the scalar product of roots and by $\langle \alpha, \beta\rangle$ the integer $2(\alpha, \beta)/(\beta, \beta)$.
-Recall that fundamental weights $\varpi_1,\ldots,\varpi_\ell$ are characterized by the property that $\langle \varpi_i, \alpha_j \rangle = \delta_{ij}$.
+Recall that fundamental weights $\varpi_1,\ldots,\varpi_\ell$ are the vectors of $\mathbb{R}^\ell$ that are characterized by the property that $\langle \varpi_i, \alpha_j \rangle = \delta_{ij}$.
 
@@
 & \Delta_J = \{\alpha \in \Phi \mid \shape(J, \alpha)=0\}, \\
-& \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha) \in \mathbb{Z}_{\geqslant0} \Phi^\pm \}, \\
-& S_J^\pm = \Delta_J \sqcup \Sigma_J^\pm.
+& \Sigma^\pm_J = \{\alpha \in \Phi \mid \shape(J, \alpha) \in \mathbb{Z}_{>0} \Phi^\pm \}, \\
+& S_J^\pm = \Delta_J \sqcup \Sigma_J^\pm,
 \end{align*}
+where the $J$-shape of a root $\beta\in \Phi$ is defined by the formula: $\shape(J, \beta)=\sum\nolimits_{i\in J} m_i(\beta) \alpha_i.$
 Clearly, $\Delta_J$ is a reductive subset, while $S^\pm_J$ and $\Sigma^\pm_J$ are parabolic and special subsets, respectively.
@@
 
-Define the $J$-shape of a root $\beta\in\Phi$ by the formula: $\shape(J, \beta)=\sum\nolimits_{i\in J} m_i(\beta) \alpha_i.$
 \begin{lemma}[{\cite[Lemma~1]{ABS}}]\label{lemma:abs}
@@
 \begin{equation*}
-a_{ij} = b_{ij} v_{j} + b_{ji} v_{i},\ j\neq i,\quad a_{ii} = b_{ii} v_{i} - \sum\limits_{\mathclap{j=1,\ j\neq i}}^\ell b_{ji} v_{j}. \qedhere
+a_{ij} = b_{ij} v_{j} + b_{ji} v_{i},\ j\neq i,\quad a_{ii} = b_{ii} v_{i} - \sum\limits_{\mathclap{j=1,\ j\neq i}}^n b_{ji} v_{j}. \qedhere
 \end{equation*}
@@
 
-Clearly, $(v'_1, v'_{-\ell}, \ldots, v'_{-1})$ is $I$-unimodular.
+Clearly, $(v'_1, v'_{-\ell}, \ldots, v'_{-1})^t$ is $I$-unimodular.
 Applying \cref{asr-bak-like}, we find $c_2, \ldots, c_\ell\in I$ such that for $v''= \prod_{i=2}^{\ell}x_{-i, -1}(c_i)\cdot v'$ one has
-$(v''_1, v''_{-\ell},\ldots, v''_{-2})\in\Ums(\ell+1, I)$.
+$(v''_1, v''_{-\ell},\ldots, v''_{-2})^t\in\Ums(\ell+1, I)$.
 Now, applying the condition $\sr(I) \leqslant \ell-1$ once again, we find
-$d_1, d_3, \ldots, d_{\ell}\in I$ such that the entries $(v'''_1, v'''_{-\ell}, \ldots, v'''_{-3})$
-of $v'''=x_{-2, 1}(d_1) \cdot \prod_{i=3}^{\ell} x_{-2, -i}(d_i) \cdot v''$ form an $I$-unimodular column.
+$d_1, d_3, \ldots, d_{\ell}\in I$ such that the entries $(v'''_1, v'''_{-\ell}, \ldots, v'''_{-3})^t$
+of $v'''=x_{1, -2}(d_1) \cdot \prod_{i=3}^{\ell} x_{-i, -2}(d_i) \cdot v''$ form an $I$-unimodular column.
 
 We can find $f_1, f_3,\ldots, f_\ell \in R$ such that $f_1v'''_1+\sum_{i=3}^\ell f_i v'''_{-i} = 1$.
-Set $\xi = v'''_1-v'''_2-1 \in I$, $v^{(4)}=x_{1,2}(\xi f_1) \cdot \prod_{i=3}^\ell x_{-i,2}(\xi f_i) \cdot v'''$.
+Set $\xi = v'''_1-v'''_2-1 \in I$, $v^{(4)}=x_{2, 1}(\xi f_1) \cdot \prod_{i=3}^\ell x_{2,-i}(\xi f_i) \cdot v'''$.
 Clearly $v^{(4)}_2 = v^{(4)}_1-1$, therefore $v^{(4)}_+$ is $I$-unimodular.
@@
 \textsc{Case $\Phi=\rD_\ell$.} From the proof of \cref{item:asrUnipD} it follows that there exists $h_1 \in \EP_\ell(R, I)$ such that for $v'=h_1\cdot v$ one has $v'_2=v'_1-1\in I$.
-Clearly, for $v'' = z_{-\alpha_{2}}(-v'_2, 1)\cdot v'$ one has $v''_1=1$, hence by \cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
-$g'=h_2 \cdot z_{-\alpha_{2}}(-v'_2, 1) \cdot h_1 \cdot g$ fixes $v^+$. 
+Clearly, for $v'' = z_{-\alpha_{1}}(-v'_2, -1)\cdot v'$ one has $v''_1=1$, hence by \cref{lemma:Chevalley-Matsumoto} there exists $h_2 \in \U(\Phi^-, I)$ such that the element
+$g'=h_2 \cdot z_{-\alpha_{1}}(-v'_2, -1) \cdot h_1 \cdot g$ fixes $v^+$. 
 Using the Levi decomposition we can write $g'=h \cdot y \cdot x \cdot g$ for some $y\in\U(\Sigma^-_\ell, I)$, $x \in \U(\Sigma^+_\ell, I)$, $h\in\E(\Delta_\ell, R, I)$.
@@
 For the proof~\cref{thm:DennisVaserstein} we need to show that the normalizer $N(A_{rs})$ is a sufficiently large subgroup.
-This is accomplished in the series of lemmas below. For example, the following lemma describes root subgroups 
+This is accomplished in a series of lemmas below. For example, the following lemma describes root subgroups 
  which are contained in $N(A_{rs})$ for obvious reasons.
@@
 \begin{proof}
-The assertion can be obtained by iteratively applying (for a total of $\ell-1$ times) the decomposition of \cref{thm:BassKolster}.
+The assertion can be obtained by iteratively applying (for a total of $\ell-1$ times) the decomposition of \cref{thm:BassKolster} (see also Fig.~1 below).
 The improved estimate for $\Phi=\rA_\ell$ (resp.

### 2018-12-07 paper.tex
Fixed 3 typos

@@
 \usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, enumitem, graphicx, mathtools, xfrac, tikz-cd, microtype, nameref, thmtools}
-\usepackage[breaklinks=true]{hyperref}
+%\usepackage{hyperref}
 \usepackage[capitalize]{cleveref}
@@
 
-\usepackage[hyperref=true, backend=bibtex, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
+\usepackage[hyperref=true, backend=biber, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
 \addbibresource{paper.bib}
@@
 Before we proceed with the proof of~\cref{thm:DennisVaserstein} let us remark that in the special case $\ell=2$, $\sr(I)= 1$
- we already known that $\E(\Phi, R, I)$ admits Gauss decomposition.
+ we already know that $\E(\Phi, R, I)$ admits Gauss decomposition.
 It is not hard to see that Dennis--Vaserstein decomposition follows from Gauss decomposition.
@@
 \[ \G(\Phi, R, I)=  \U(\Phi^+, I) \cdot \U(\Phi^-, I) \cdot Z \cdot \U(\Sigma_1^-\setminus\{-\alpha_{\max}\}, I) \cdot \U(\Sigma_1, I) \cdot \G(\Delta_1, R, I), \]
-where $Z = Z_{\alpha_{\max}}(I)=\left\{z_{-\alpha_{\max}}(r, 1)\ \middle|\ r\in I \right\}$.
+where $Z = Z_{-\alpha_{\max}}(I)=\left\{z_{-\alpha_{\max}}(r, 1)\ \middle|\ r\in I \right\}$.
 \end{thm}
@@
 
-In remains to consider the case $\Phi=\rC_\ell$. First of all, notice that $2abc-abd\in II^{\indexbox{2}}$, indeed,
+It remains to consider the case $\Phi=\rC_\ell$. First of all, notice that $2abc-abd\in II^{\indexbox{2}}$, indeed,
 \[ \det(g_1)=a^3d-3a^2bc+a^2bd+ab^2c+a^3+a^2b+a^2d+2abc-abd+1. \]
